### 2018-08-27 SEDs/notes.tex
starting new repo

\documentclass[11pt,a4paper]{article}
\input{format}

\begin{document}

   \title{Very high-$z$ Quasars: SED notes}
 \date{\today}
\maketitle

\section{Notes from \citet{Roseboom2013}}
There is clear evidence that all powerful AGN are surrounded by a
geometrically thick distribution of optically thick material 
\citep{Rowan-Robinson 1977, Lawrence_Elvis1982, Antonucci_Miller1985, 
Edelson1987, Elvis1994, Richards2006b}.

\section{Caballero et al. 2016}
%% Caballero_2016_MNRAS_463_2064
\citet{Caballero2016}

\begin{tabular}{ l l l l }
\hline \hline
measure	   &	unit	&	typical ranges		&	e.g. figure in R06b  \\
\hline
f$_{\nu}$		    &    uJy		  & from 0.1 to $\sim$100,000d &     Fig 9 \\
log(f$_{\nu}$)	    & ergs/s/cm2/Hz  &	-32 to -24  	     	&	Fig 10, top panel \\
$\nu$f$_{\nu}$     &	ergs/s/cm2        & 	-16 to -12		&	Fig 11, bottom panel  \\
$\nu$L$_{\nu}$     &  ergs/s	           &  43 to  47		&	Fig 12. \\
\hline \hline
\end{tabular}

\bibliographystyle{mn2e}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}

\end{document}

### 2018-08-27 Lz/Lz.py

@@ -1,0 +1,239 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+from matplotlib.ticker import AutoMinorLocator
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from astropy.cosmology import FlatLambdaCDM
+# In this case we just need to define the matter density 
+# and hubble parameter at z=0.
+# Note the default units for the hubble parameter H0 are km/s/Mpc. 
+# You can also pass an astropy `Quantity` with the units specified. 
+cosmo = FlatLambdaCDM(H0=67.7, Om0=0.307)  #Banados thesis
+
+import astropy.units as u
+ages = np.array([13, 10, 8, 6, 5, 4, 3, 2, 1.5, 1.2, 1, 0.8, 0.70])*u.Gyr
+from astropy.cosmology import z_at_value
+ageticks = [z_at_value(cosmo.age, age) for age in ages]
+
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+infile = 'THE_TABLE_v0pnt97.dat'
+readin = path+infile
+all_VHzQs  = ascii.read(readin, delimiter=r'\s')
+
+## The four ATLAS QSOs
+#ATLAS = ascii.read(path+'ATLAS_Quasar_TABLE.dat', delimiter=r'\s', guess=False)
+#GTO =  ascii.read('JWST_GTO_VeryHighZ_Quasar_targets_byRA.dat', delimiter=r'\s', guess=False)
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+z_all = all_VHzQs['redshift']
[…]

### 2018-08-27 Lz/older_py/Lz_20180601.py

@@ -1,0 +1,226 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from astropy.cosmology import FlatLambdaCDM
+# In this case we just need to define the matter density 
+# and hubble parameter at z=0.
+# Note the default units for the hubble parameter H0 are km/s/Mpc. 
+# You can also pass an astropy `Quantity` with the units specified. 
+#cosmo = FlatLambdaCDM(H0=68, Om0=0.27)
+cosmo = FlatLambdaCDM(H0=67.7, Om0=0.307)  #Banados thesis
+
+import astropy.units as u
+ages = np.array([13, 10, 8, 6, 5, 4, 3, 2, 1.5, 1.2, 1, 0.8, 0.70])*u.Gyr
+from astropy.cosmology import z_at_value
+ageticks = [z_at_value(cosmo.age, age) for age in ages]
+
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+infile = 'THE_TABLE_v0pnt97.dat'
+readin = path+infile
+#all_VHzQs  = ascii.read(readin, delimiter=r'\s', guess=False)
+all_VHzQs  = ascii.read(readin, delimiter=r'\s')
+
+## The four ATLAS QSOs
+#ATLAS = ascii.read(path+'ATLAS_Quasar_TABLE.dat', delimiter=r'\s', guess=False)
+#GTO =  ascii.read('JWST_GTO_VeryHighZ_Quasar_targets_byRA.dat', delimiter=r'\s', guess=False)
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
[…]

### 2018-08-27 Lz/older_py/W1W2_vs_redshift.py

@@ -1,0 +1,216 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.table import Table
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from astropy.cosmology import FlatLambdaCDM
+# In this case we just need to define the matter density 
+# and hubble parameter at z=0.
+# Note the default units for the hubble parameter H0 are km/s/Mpc. 
+# You can also pass an astropy `Quantity` with the units specified. 
+#cosmo = FlatLambdaCDM(H0=68, Om0=0.27)
+cosmo = FlatLambdaCDM(H0=67.7, Om0=0.307)  #Banados thesis
+
+
+import astropy.units as u
+ages = np.array([13, 10, 8, 6, 5, 4, 3, 2, 1.5, 1.2, 1, 0.8, 0.70])*u.Gyr
+from astropy.cosmology import z_at_value
+ageticks = [z_at_value(cosmo.age, age) for age in ages]
+
+
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+
+## na desig        ra_hms  dec_dms ra      dec     redshift        mag     M1450   errM1450        ra_WISE dec_WISE        w1mag w1err w1snr       w2mag w2err w2snr       w3mag w3err w3snr       w4mag w4err w4snr       ref
+#all_VHzQs  = ascii.read(path+'THE_TABLE_byRA.dat', delimiter=r'\s', guess=False)
+## Just for "clean" plotting purposes!!   (126 quasars in the full file...)
+all_VHzQs  = ascii.read(path+'THE_TABLE_byRA_zge5pnt00.dat', delimiter=r'\s', guess=False)
+
+## The four ATLAS QSOs
+ATLAS = ascii.read(path+'ATLAS_Quasar_TABLE.dat', delimiter=r'\s', guess=False)
+
[…]

### 2018-08-27 SEDs/RestWavelength_flux.py

@@ -1,0 +1,259 @@
+'''
+RestWavelength_flux April 6, 2018
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+## 
+## Composite quasar spectra
+##
+## The Vanden Berk et al. (2001) composite
+path = '/cos_pc19a_npr/data/SDSS/VdB01/'
+infile = 'Vanden_Berk_2001_Table1.dat'
+table = path+infile
+VdB01_comp = ascii.read(table)
+VdB01_wave = VdB01_comp['Wavelength']
+VdB01_flux = VdB01_comp['Flux']
+
+## The Glikman et al. (2006) composites
+path = '/cos_pc19a_npr/data/Glikman2006/'
+infile = 'Glikman_2006_ApJ_Table3.dat'
+#file = 'Glikman_2006_ApJ_Table7.dat'
+table = path+infile
+Glikman_comp = ascii.read(table)
+Glik_wave = Glikman_comp['Wavelength']
+Glik_flux = Glikman_comp['Flux']
+
+## Hernan-Caballero et al. (2016)
+path = '/cos_pc19a_npr/data/SEDs/Hernan-Caballero_2016/'
+infile = 'table3.dat'
+table = path+infile
+HernanCab_comp= ascii.read(table)
+HernCab_wave = HernanCab_comp['Wavelength']
+HernCab_tot  = HernanCab_comp['Fnu_tot']
+HernCab_disk = HernanCab_comp['Fnu_disk']
+HernCab_dust = HernanCab_comp['Fnu_dust']
+
+## Assef et al. 2010, range of templates
+##  1 uJy = 10^-17 erg s^-1 cm2 Hz1
+path = '/cos_pc19a_npr/data/SEDs/Assef2010/'
+infile = 'Assef_2010_Table1.dat'
+table = path+infile
+Assef2010_all = ascii.read(table)
+Assef_wave = Assef2010_all['Wavelength']
[…]

### 2018-08-27 SEDs/RestWavelength_flux_withLoop.py

@@ -1,0 +1,261 @@
+'''
+RestWavelength_flux April 6, 2018
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+## 
+## Composite quasar spectra
+##
+## The Vanden Berk et al. (2001) composite
+path = '/cos_pc19a_npr/data/SDSS/VdB01/'
+infile = 'Vanden_Berk_2001_Table1.dat'
+table = path+infile
+VdB01_comp = ascii.read(table)
+VdB01_wave = VdB01_comp['Wavelength']
+VdB01_flux = VdB01_comp['Flux']
+
+## The Glikman et al. (2006) composites
+path = '/cos_pc19a_npr/data/Glikman2006/'
+infile = 'Glikman_2006_ApJ_Table3.dat'
+#file = 'Glikman_2006_ApJ_Table7.dat'
+table = path+infile
+Glikman_comp = ascii.read(table)
+Glik_wave = Glikman_comp['Wavelength']
+Glik_flux = Glikman_comp['Flux']
+
+## Hernan-Caballero et al. (2016)
+path = '/cos_pc19a_npr/data/SEDs/Hernan-Caballero_2016/'
+infile = 'table3.dat'
+table = path+infile
+HernanCab_comp= ascii.read(table)
+HernCab_wave = HernanCab_comp['Wavelength']
+HernCab_tot  = HernanCab_comp['Fnu_tot']
+HernCab_disk = HernanCab_comp['Fnu_disk']
+HernCab_dust = HernanCab_comp['Fnu_dust']
+
+## Assef et al. 2010, range of templates
+##  1 uJy = 10^-17 erg s^-1 cm2 Hz1
+path = '/cos_pc19a_npr/data/SEDs/Assef2010/'
+infile = 'Assef_2010_Table1.dat'
+table = path+infile
+Assef2010_all = ascii.read(table)
+Assef_wave = Assef2010_all['Wavelength']
[…]

### 2018-08-27 SEDs/dust/RestWavelength_flux.py

@@ -1,0 +1,216 @@
+'''
+RestWavelength_flux April 6, 2018
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+## 
+## Composite quasar spectra
+##
+## The Vanden Berk et al. (2001) composite
+path = '/cos_pc19a_npr/data/SDSS/VdB01/'
+file = 'Vanden_Berk_2001_Table1.dat'
+table = path+file
+VdB01_comp = ascii.read(table)
+VdB01_wave = VdB01_comp['Wavelength']
+VdB01_flux = VdB01_comp['Flux']
+
+## The Glikman et al. (2006) composites
+path = '/cos_pc19a_npr/data/Glikman2006/'
+file = 'Glikman_2006_ApJ_Table3.dat'
+#file = 'Glikman_2006_ApJ_Table7.dat'
+table = path+file
+Glikman_comp = ascii.read(table)
+Glik_wave = Glikman_comp['Wavelength']
+Glik_flux = Glikman_comp['Flux']
+
+## Hernan-Caballero et al. (2016)
+path = '/cos_pc19a_npr/data/SEDs/Hernan-Caballero_2016/'
+file = 'table3.dat'
+table = path+file
+HernanCab_comp= ascii.read(table)
+HernCab_wave = HernanCab_comp['Wavelength']
+HernCab_tot  = HernanCab_comp['Fnu_tot']
+HernCab_disk = HernanCab_comp['Fnu_disk']
+HernCab_dust = HernanCab_comp['Fnu_dust']
+
+## Assef et al. 2010, range of templates
+##  1 uJy = 10^-17 erg s^-1 cm2 Hz1
+path = '/cos_pc19a_npr/data/SEDs/Assef2010/'
+file = 'Assef_2010_Table1.dat'
+table = path+file
+Assef2010_all = ascii.read(table)
+Assef_wave = Assef2010_all['Wavelength']
[…]

### 2018-08-27 SEDs/filters_UKIRT-WFCAM.py

@@ -1,0 +1,248 @@
+'''
+A wavelength vs. wide-area survey filters plot.
+For e.g. Pan-STARRS, UKIRT/UKIDSS, VISTA/VHS and WISE.
+
+To reproduce something akin to the Spectral Bands plot at::
+https://blog.backyardworlds.org/2018/04/24/guest-blog-post-by-peter-jalowiczor/
+
+Filter curves from e.g.
+http://www.mso.anu.edu.au/~brad/filters.html
+'''
+
+import matplotlib
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+
+##
+## READ-IN THE DATA FILE(S)
+##
+## FILTERS
+path = '/cos_pc19a_npr/data/filter_curves/'
+
+##
+##      UKIRT
+##      http://www.mso.anu.edu.au/~brad/Filters/UKIRT[ZYJHK]
+##
+infile = 'UKIRT/UKIRT_Z.dat'
+table = path+infile
+UKIRT_Zband      = ascii.read(table)
+UKIRT_Zband_wave = UKIRT_Zband['wavelength']
+UKIRT_Zband_thru = UKIRT_Zband['throughput']
+infile = 'UKIRT/UKIRT_Y.dat'
+table = path+infile
+UKIRT_Yband      = ascii.read(table)
+UKIRT_Yband_wave = UKIRT_Yband['wavelength']
+UKIRT_Yband_thru = UKIRT_Yband['throughput']
+infile = 'UKIRT/UKIRT_J.dat'
+table = path+infile
+UKIRT_Jband      = ascii.read(table)
+UKIRT_Jband_wave = UKIRT_Jband['wavelength']
+UKIRT_Jband_thru = UKIRT_Jband['throughput']
+infile = 'UKIRT/UKIRT_H.dat'
+table = path+infile
+UKIRT_Hband      = ascii.read(table)
+UKIRT_Hband_wave = UKIRT_Hband['wavelength']
+UKIRT_Hband_thru = UKIRT_Hband['throughput']
+infile = 'UKIRT/UKIRT_K.dat'
+table = path+infile
+UKIRT_Kband      = ascii.read(table)
[…]

### 2018-08-27 SEDs/filters_vs_QSOstars.py

@@ -1,0 +1,418 @@
+'''
+A wavelength vs. wide-area survey filters plot.
+For e.g. Pan-STARRS, UKIRT/UKIDSS, VISTA/VHS and WISE.
+
+To reproduce something akin to the Spectral Bands plot at::
+https://blog.backyardworlds.org/2018/04/24/guest-blog-post-by-peter-jalowiczor/
+
+Filter curves from e.g.
+http://www.mso.anu.edu.au/~brad/filters.html
+'''
+
+import matplotlib
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+##
+## FILTERS
+path = '/cos_pc19a_npr/data/filter_curves/'
+
+##     D E C a m
+infile = 'DECam/DES_uband.dat'
+table = path+infile
+DES_uband      = ascii.read(table)
+DES_uband_wave = DES_uband['wavelength']
+DES_uband_thru = DES_uband['throughput']
+infile = 'DECam/DES_gband.dat'
+table = path+infile
+DES_gband      = ascii.read(table)
+DES_gband_wave = DES_gband['wavelength']
+DES_gband_thru = DES_gband['throughput']
+infile = 'DECam/DES_rband.dat'
+table = path+infile
+DES_rband      = ascii.read(table)
+DES_rband_wave = DES_rband['wavelength']
+DES_rband_thru = DES_rband['throughput']
+infile = 'DECam/DES_iband.dat'
+table = path+infile
+DES_iband      = ascii.read(table)
+DES_iband_wave = DES_iband['wavelength']
+DES_iband_thru = DES_iband['throughput']
+infile = 'DECam/DES_zband.dat'
+table = path+infile
+DES_zband      = ascii.read(table)
+DES_zband_wave = DES_zband['wavelength']
+DES_zband_thru = DES_zband['throughput']
+infile = 'DECam/DES_Yband.dat'
+table = path+infile
[…]

### 2018-08-27 SEDs/old_python/RestWavelength_flux_20180406.py

@@ -1,0 +1,136 @@
+'''
+RestWavelength_flux April 6, 2018
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+## na desig        ra_hms  dec_dms ra      dec     redshift        mag     M1450   errM
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt96.dat', delimiter=r'\s', guess=False)
+
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+redshift = all_VHzQs['redshift']
+M1450    = all_VHzQs['M1450']
+
+## Figures 6 and 7 from Wright et al. 2018 W1_band_min = 2.8
+W1_band_med = 3.4
+W1_band_max = 3.9
+W2_band_min = 4.0
+W2_band_med = 4.6
+W2_band_max = 5.3
+W3_band_min = 7.5
+W3_band_med = 12.0
+W3_band_max = 18.0
+W4_band_min = 19.0
+W4_band_med = 23.0 ## M.Brown et al. (2013) W4_band_max = 27.5
+
+## Wright et al. (2010) Figure 9
+w1mag_limit = 17.2
+w2mag_limit = 15.8
+w3mag_limit = 11.4
+w4mag_limit =  8.0
+
+##  1 Jy =10-26Wm-2Hz1 = 1023ergs1cm2Hz1
+##  http://wise2.ipac.caltech.edu/docs/release/allwise/faq.html
+##  http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html
+
+## nu^-2
+fc_W1 = 1.000; fc_W2 = 1.000; fc_W3 = 1.000; fc_W4 = 1.000;
+
+## Flux_nu0 is the flux density for sources with constant power-law spectra:
[…]

### 2018-08-27 SEDs/old_python/RestWavelength_flux_20180409.py

@@ -1,0 +1,218 @@
+'''
+RestWavelength_flux April 6, 2018
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+## 
+## Composite quasar spectra
+##
+## The Vanden Berk et al. (2001) composite
+path = '/cos_pc19a_npr/data/SDSS/VdB01/'
+file = 'Vanden_Berk_2001_Table1.dat'
+table = path+file
+VdB01_comp = ascii.read(table)
+VdB01_wave = VdB01_comp['Wavelength']
+VdB01_flux = VdB01_comp['Flux']
+
+## The Glikman et al. (2006) composites
+path = '/cos_pc19a_npr/data/Glikman2006/'
+file = 'Glikman_2006_ApJ_Table3.dat'
+#file = 'Glikman_2006_ApJ_Table7.dat'
+table = path+file
+Glikman_comp = ascii.read(table)
+Glik_wave = Glikman_comp['Wavelength']
+Glik_flux = Glikman_comp['Flux']
+
+## Hernan-Caballero et al. (2016)
+path = '/cos_pc19a_npr/data/SEDs/Hernan-Caballero_2016/'
+file = 'table3.dat'
+table = path+file
+HernanCab_comp= ascii.read(table)
+HernCab_wave = HernanCab_comp['Wavelength']
+HernCab_tot  = HernanCab_comp['Fnu_tot']
+HernCab_disk = HernanCab_comp['Fnu_disk']
+HernCab_dust = HernanCab_comp['Fnu_dust']
+
+## Assef et al. 2010, range of templates
+##  1 uJy = 10^-17 erg s^-1 cm2 Hz1
+path = '/cos_pc19a_npr/data/SEDs/Assef2010/'
+file = 'Assef_2010_Table1.dat'
+table = path+file
+Assef2010_all = ascii.read(table)
+Assef_wave = Assef2010_all['Wavelength']
[…]

### 2018-08-27 color_color/Best_3by2_color_type.py

@@ -1,0 +1,203 @@
+'''
+  Banados 2016 figures (3)
+  Carnall z-W1, W1-W2 (1)
+  W123 (1) 
+  HSC SHELLQS plots (??)
+  In the ‘exact’ style of the Banado2016 figures...
+'''
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#filename ='THE_TABLE_v0pnt96.dat'
+filename  ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+redshift = VHzQ['redshift']
+g_PS1 = VHzQ['gMag']
+r_PS1 = VHzQ['rMag']
+i_PS1 = VHzQ['iMag']
+z_PS1 = VHzQ['zMag']
+y_PS1 = VHzQ['yMag']
+Ymag  = VHzQ['Yapermag']
+Jmag  = VHzQ['Jmag']
+Hmag  = VHzQ['Hmag']
+Kmag  = VHzQ['Kmag']
+W1mag = VHzQ['W1mag']
+W2mag = VHzQ['W2mag']
+W3mag = VHzQ['W3mag']
+W4mag = VHzQ['W4mag']
+
+'''
+7.5400
+g -1.000     -1.000
+r -1.000     -1.000
+i -1.000     -1.000
+z -1.000     -1.000
+y -1.000     -1.000
+
+Y 20.840      0.191
+J 19.816      0.108
+H 18.639      0.119
+K 18.132      0.123
+
+17.471    0.146    7.400
+16.769    0.295    3.700
+12.834    0.498    2.200
+9.256   -9.990   -1.100
+
+(z-J) = 
+
+'''
+
+##  Making the plot(s)
+plt.rcParams.update({'font.size': 14})
+#matplotlib.rc('text', usetex=True)
+
+## https://matplotlib.org/examples/pylab_examples/subplots_demo.html
+fig, ((ax1, ax2), (ax4, ax5), (ax7, ax8)) = plt.subplots(3, 2, figsize=(14, 16), num=None, dpi=80, facecolor='w', edgecolor='k')
[…]

### 2018-08-27 color_color/W1W2W3_hexplots.py

@@ -1,0 +1,76 @@
+import numpy as np
+from astropy.io import fits
+from astropy.io import ascii
+
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+
+##
+## DR14Q
+##
+path = '/cos_pc19a_npr/data/SDSS/DR14Q/'
+filename ='DR14Q_v4_4.fits'
+#filename ='DR14Q_v4_4_W4good.fits'
+infile = path+filename
+data = fits.getdata(infile, 1)
+dr14q = Table(data)
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+filename ='THE_TABLE_v0pnt96.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+
+
+##  Making the plot(s)
+## 
+##  W2-W3  vs.  W1-W2 
+##
+plt.rcParams.update({'font.size': 14})
+fig, ax = plt.subplots(figsize=(10, 7), num=None, dpi=80, facecolor='w', edgecolor='k')
+
+## Blain et al. (2013), Figure 1
+ymin = -0.2
+ymax =  2.0 
+## W2-W3 vs. W1-W2
+xmin =  1.7   
+xmax =  4.7
+##    W2 vs. W1-W2
+#xmin =  10.0   
+#xmax =  17.3
+
+xmin=1.0; xmax=6.0; ymin=-0.5; ymax=2.5
+
+#cmap = plt.cm.RdBu_r
+#cmap = plt.cm.inferno
+cmap = plt.cm.rainbow
+
+ax.axis([xmin, xmax, ymin, ymax])
+
+hb = ax.hexbin( (dr14q['W2MAG']- dr14q['W3MAG']), (dr14q['W1MAG'] - dr14q['W2MAG']), C=dr14q['Z'],
+            gridsize=180, mincnt=25, marginals=False, cmap=cmap, vmin=0.00, vmax=3.00)
+cb = fig.colorbar(hb, ax=ax)
+cb.set_label('redshift')
+
+ax.scatter((VHzQ['w2mag'] -  VHzQ['w3mag']),  (VHzQ['w1mag'] - VHzQ['w2mag']), color='k')
+
+## The vertical dashed line at W 2 − W3 = 5.3 is one of the selection
+## criteria for W1W2-dropouts; some are bluer than this because they
+## satisfied the W2 − W4 > 8.2 criterion.
+lw = 2.0
[…]

### 2018-08-27 color_color/W1W2_vs_zW2_Carnall.py

@@ -1,0 +1,137 @@
+'''
+   Carnall z-W1, W1-W2 (1)
+'''
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+from time import sleep
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#filename ='THE_TABLE_v0pnt96.dat'
+filename ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+#VHzQ = VHzQ[np.where( (VHzQ['redshift'] >= 5.7) & (VHzQ['redshift'] <= 6.7))]
+
+
+redshift = VHzQ['redshift']
+g_PS1 = VHzQ['gMag']
+r_PS1 = VHzQ['rMag']
+i_PS1 = VHzQ['iMag']
+z_PS1 = VHzQ['zMag']
+y_PS1 = VHzQ['yMag']
+Ymag  = VHzQ['Yapermag']
+Jmag  = VHzQ['Jmag']
+Hmag  = VHzQ['Hmag']
+Kmag  = VHzQ['Kmag']
+W1mag = VHzQ['W1mag']
+W2mag = VHzQ['W2mag']
+W3mag = VHzQ['W3mag']
+W4mag = VHzQ['W4mag']
+
+'''
+https://blog.backyardworlds.org/page/2/
+'''
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Ldwarfs_photom_v1pnt00.dat'
+table=path+filename
+Ldwarfs = ascii.read(table)
+#Ldwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
+
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Tdwarfs_photom_v1pnt00.dat'
+table=path+filename
+Tdwarfs = ascii.read(table)
+#Tdwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
+
+##
+##  Making the plot(s)
+##
+plt.rcParams.update({'font.size': 14})
+#matplotlib.rc('text', usetex=True)
+
[…]

### 2018-08-27 color_color/color_color_bluer.py

@@ -1,0 +1,273 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+    http://docs.astropy.org/en/stable/table/
+    http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+'''
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+## 2MASS
+J_tm  = table['Jmag']
+H_tm  = table['Hmag']
+Ks_tm = table['Ksmag']
+W1mag = table['W1mag']
+W2mag = table['W2mag']
+W3mag = table['W3mag']
+W4mag = table['W4mag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+
+## Just figuring out how many stars of a given Type
[…]

### 2018-08-27 color_color/color_color_redder.py

@@ -1,0 +1,273 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+    http://docs.astropy.org/en/stable/table/
+    http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+'''
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+## 2MASS
+J_tm  = table['Jmag']
+H_tm  = table['Hmag']
+Ks_tm = table['Ksmag']
+W1_star = table['W1mag']
+W2_star = table['W2mag']
+W3_star = table['W3mag']
+W4_star = table['W4mag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+
+## Just figuring out how many stars of a given Type
[…]

### 2018-08-27 color_color/zJ_vs_JW1.py

@@ -1,0 +1,119 @@
+'''
+  Banados 2016 figures (3)
+  Carnall z-W1, W1-W2 (1)
+  W123 (1) 
+  HSC SHELLQS plots (??)
+  In the ‘exact’ style of the Banado2016 figures...
+'''
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#filename ='THE_TABLE_v0pnt96.dat'
+filename ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+redshift = VHzQ['redshift']
+g_PS1 = VHzQ['gMag']
+r_PS1 = VHzQ['rMag']
+i_PS1 = VHzQ['iMag']
+z_PS1 = VHzQ['zMag']
+y_PS1 = VHzQ['yMag']
+Ymag  = VHzQ['Yapermag']
+Jmag  = VHzQ['Jmag']
+Hmag  = VHzQ['Hmag']
+Kmag  = VHzQ['Kmag']
+W1mag = VHzQ['W1mag']
+W2mag = VHzQ['W2mag']
+W3mag = VHzQ['W3mag']
+W4mag = VHzQ['W4mag']
+
+
+'''
+https://blog.backyardworlds.org/page/2/
+'''
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Ldwarfs_photom_v1pnt00.dat'
+table=path+filename
+Ldwarfs = ascii.read(table)
+
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Tdwarfs_photom_v1pnt00.dat'
+table=path+filename
+Tdwarfs = ascii.read(table)
+
+
+##  Making the plot(s)
+plt.rcParams.update({'font.size': 14})
+#matplotlib.rc('text', usetex=True)
+
+## https://matplotlib.org/examples/pylab_examples/subplots_demo.html
[…]

### 2018-08-27 color_redshift/SpecType_vs_NIRcolors_v0pnt8.py

@@ -1,0 +1,280 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+    http://docs.astropy.org/en/stable/table/
+    http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+'''
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+## 2MASS
+J_tm  = table['Jmag']
+H_tm  = table['Hmag']
+Ks_tm = table['Ksmag']
+W1mag = table['W1mag']
+W2mag = table['W2mag']
+W3mag = table['W3mag']
+W4mag = table['W4mag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+sum_ii=0
+## Just figuring out how many stars of a given Type
[…]

### 2018-08-27 color_redshift/SpecType_vs_Optcolors.py

@@ -1,0 +1,258 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+    http://docs.astropy.org/en/stable/table/
+    http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+'''
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+
+## Just figuring out how many stars of a given Type
+no_types = int((table['SpT-opt-n'].max() - table['SpT-opt-n'].min()))
+for ii in range(no_types):
+    w =table[np.where(table['SpT-opt-n'] == ii) ]
+    if (len(w)) > 0:
+        print(ii, w['SpT-opt'][0], len(w))
+
[…]

### 2018-08-27 color_redshift/SpecType_vs_W1W2_W2W3colors_v0pnt8.py

@@ -1,0 +1,182 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+    http://docs.astropy.org/en/stable/table/
+    http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+'''
+
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+## 2MASS
+J_tm  = table['Jmag']
+H_tm  = table['Hmag']
+Ks_tm = table['Ksmag']
+W1mag = table['W1mag']
+W2mag = table['W2mag']
+W3mag = table['W3mag']
+W4mag = table['W4mag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+sum_ii=0
[…]

### 2018-08-27 color_redshift/VHzQs_color_redshift.py

@@ -1,0 +1,207 @@
+'''
+  Banados 2016 figures (3)
+  Carnall z-W1, W1-W2 (1)
+  W123 (1) 
+  HSC SHELLQS plots (??)
+  In the ‘exact’ style of the Banado2016 figures...
+'''
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#filename ='THE_TABLE_v0pnt96.dat'
+filename ='temp2.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+redshift = VHzQ['redshift']
+g_PS1 = VHzQ['gMag']
+r_PS1 = VHzQ['rMag']
+i_PS1 = VHzQ['iMag']
+z_PS1 = VHzQ['zMag']
+y_PS1 = VHzQ['yMag']
+Ymag  = VHzQ['Yapermag']
+Jmag  = VHzQ['Jmag']
+Hmag  = VHzQ['Hmag']
+Kmag  = VHzQ['Kmag']
+W1mag = VHzQ['W1mag']
+W2mag = VHzQ['W2mag']
+W3mag = VHzQ['W3mag']
+W4mag = VHzQ['W4mag']
+
+'''
+7.5400
+g -1.000     -1.000
+r -1.000     -1.000
+i -1.000     -1.000
+z -1.000     -1.000
+y -1.000     -1.000
+
+Y 20.840         0.191
+J 19.816      0.108
+H 18.639      0.119
+K 18.132      0.123
+
+17.471    0.146    7.400
+16.769    0.295    3.700
+12.834    0.498    2.200
+9.256   -9.990   -1.100
+
+(z-J) = 
+
+'''
+
+##  Making the plot(s)
+plt.rcParams.update({'font.size': 14})
+#matplotlib.rc('text', usetex=True)
+
+## https://matplotlib.org/examples/pylab_examples/subplots_demo.html
+#fig, (ax1, ax2, ax3, ax4, ax5, ax6, ax7, ax8, ax9) = plt.subplots(9, figsize=(10, 14), num=None, dpi=80, facecolor='w', edgecolor='k', sharex=True)
[…]

### 2018-08-27 color_redshift/older_py/SpecType_vs_NIRcolors.py

@@ -1,0 +1,226 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+
+'''
+import numpy as np
+
+import matplotlib
+import matplotlib.pyplot as plt
+
+from astropy.table import Table
+from astropy.io import ascii
+
+
+##http://docs.astropy.org/en/stable/table/
+#t = Table(rows=data_rows, names=('a', 'b', 'c'),
+#          meta={'name': 'first table'}, dtype=('i4', 'f8', 'S1'))
+#
+#df = pd.read_table('Best_2018_Table1.txt', sep=r"\s*")
+
+
+## http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+## http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag  = table['PS1gmag'] 
+rmag  = table['PS1rmag']
+imag  = table['PS1imag']
+zmag  = table['PS1zmag']
+ymag  = table['PS1ymag']
+## 2MASS
+J_tm  = table['Jmag']
+H_tm  = table['Hmag']
+Ks_tm = table['Ksmag']
+W1mag = table['W1mag']
+W2mag = table['W2mag']
+W3mag = table['W3mag']
+W4mag = table['W4mag']
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+
+no_types = int((table['SpT-opt-n'].max() - table['SpT-opt-n'].min()))
[…]

### 2018-08-27 color_redshift/older_py/SpecType_vs_Optcolors_v1pnt0.py

@@ -1,0 +1,275 @@
+'''
+Aim:: To read in Table 1 from Best et al. (2018, ApJS, 234, 1)
+      http://adsabs.harvard.edu/abs/2018ApJS..234....1B
+      Photometry and Proper Motions of M, L, and T Dwarfs from the Pan-STARRS1 3π Survey
+
+Good/useful links/URLs::      
+    http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+    http://vizier.u-strasbg.fr/doc/catstd.htx
+    https://github.com/astropy/astropy/blob/master/docs/io/unified.rst
+    http://cds.u-strasbg.fr/doc/catstd.htx
+    https://mail.scipy.org/pipermail/astropy/2016-May/004207.html
+
+'''
+import numpy as np
+
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+from matplotlib.ticker import AutoMinorLocator
+
+from astropy.table import Table
+from astropy.io import ascii
+
+
+##http://docs.astropy.org/en/stable/table/
+#t = Table(rows=data_rows, names=('a', 'b', 'c'),
+#          meta={'name': 'first table'}, dtype=('i4', 'f8', 'S1'))
+#
+#df = pd.read_table('Best_2018_Table1.txt', sep=r"\s*")
+
+
+## http://jakevdp.github.io/astropy/api/astropy.io.ascii.Cds.html
+## http://docs.astropy.org/en/v0.2.1/_generated/astropy.io.ascii.cds.Cds.html
+path   = '/cos_pc19a_npr/data/MLandT_dwarfs/'
+infile = 'Best_2018_Table1_full.txt'
+readin = path+infile
+table = ascii.read(readin)
+
+## grizy from PS1
+gmag = table['PS1gmag'] 
+rmag = table['PS1rmag']
+imag = table['PS1imag']
+zmag = table['PS1zmag']
+ymag = table['PS1ymag']
+
+
+SpT_optn = table['SpT-opt-n']
+SpT_nirn = table['SpT-nir-n']
+#SpT_opt = table['SpT-opt-n']
+
+
+no_types = int((table['SpT-opt-n'].max() - table['SpT-opt-n'].min()))
[…]

### 2018-08-27 detections/comparisons.py

@@ -1,0 +1,36 @@
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+#import matplotlib
+import matplotlib as mpl
+
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from mpl_toolkits.axes_grid1.axes_divider  import make_axes_locatable
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
+from mpl_toolkits.axes_grid1.colorbar      import colorbar
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+m1  = ascii.read(path+'THE_TABLE_v0pnt971.dat', delimiter=r'\s', guess=False)
+m2  = ascii.read(path+'THE_TABLE_v0pnt97_WISE_coverage.dat', delimiter=r'\s', guess=False)
+
+for ii in range(len(m1)):
+    diff_w1 = (m1['w1mag'][ii] - m2['w1mpro'][ii])
+    diff_w2 = (m1['w2mag'][ii] - m2['w2mpro'][ii])
+    diff_w3 = (m1['w3mag'][ii] - m2['w3mpro'][ii])
+    diff_w4 = (m1['w4mag'][ii] - m2['w4mpro'][ii])
+
+    print(diff_w1, diff_w2, diff_w3, diff_w4)    
+    if  ((diff_w4 < 800.0) and (diff_w4 <0.0)):
+        print(ii, m1['na'][ii], m1['desig'][ii], diff_w1)
+        print(ii, m1['ra'][ii], m1['dec'][ii], m1['w1mag'][ii], m1['w1snr'][ii],  m1['w2mag'][ii],  m1['w2snr'][ii] )
+        print(ii, m2['ra'][ii], m2['dec'][ii], m2['w1mpro'][ii], m2['w1snr'][ii], m2['w2mpro'][ii], m2['w2snr'][ii])
+        print()
+#    if  ((diff > 0.0) or (diff >0.0)): print(ii,diff)

### 2018-08-27 detections/detections_vs_SNR.py

@@ -1,0 +1,99 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+infile = 'THE_TABLE_v0pnt97.dat'
+readin= path+infile
+all_VHzQs  = ascii.read(readin, delimiter=r'\s')
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+z_all = all_VHzQs['redshift']
+M1450_all = all_VHzQs['M1450']
+
+
+##
+## May fave new line ;-=)
+#plt.style.use('dark_background')
+matplotlib.rc('text', usetex=True)
+
+plt.rcParams.update({'font.size': 14})
+fig, ax = plt.subplots(figsize=(8.0, 8.0))
+
+
+## define the colormap
+#cmap = plt.cm.viridis
+cmap = plt.cm.plasma_r  ## Good for W1-W2
+
+
+##  
+xmin =   -5.0   ## -11.2  
+xmax =   42.0
+ymin =    -5.0    ## -11.2
+ymax =   42.0
+
+ls = 'solid'
+lw = 1.0
+ms_large = 250*1.75
+ms = ms_large/3.
+fontsize=22
+
+#main_ax.scatter(z_GTO,   w1mag_GTO,   c='r', marker="P", s=ms_large)
+#hdl=main_ax.scatter(z_all, M1450_all , c=w1snr,        cmap=cmap, s=ms, alpha=0.85)
[…]

### 2018-08-27 detections/detections_vs_WISE_nos.py

@@ -1,0 +1,64 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import numpy as np
+import math
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#all_VHzQs  = ascii.read(path+'THE_TABLES/v0pnt97/THE_TABLE_v0pnt97.dat', delimiter=r'\s', guess=False)
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt971.dat', delimiter=r'\s', guess=False)
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+z_all = all_VHzQs['redshift']
+M1450_all = all_VHzQs['M1450']
+
+snr_limit = 2.0
+
+## Some conditions, values etc.
+w_forw1 = all_VHzQs[np.where((w1snr > snr_limit))]
+w_forw2 = all_VHzQs[np.where((w2snr > snr_limit))]
+w_forw3 = all_VHzQs[np.where((w3snr > snr_limit))]
+w_forw4 = all_VHzQs[np.where((w4snr > snr_limit))]
+
+w_forw1w2 = all_VHzQs[np.where((w1snr > snr_limit)  & (w2snr > snr_limit  ))]
+w_forw1w3 = all_VHzQs[np.where((w1snr > snr_limit)  & (w3snr > snr_limit  ))]
+w_forw2w3 = all_VHzQs[np.where((w2snr > snr_limit)  & (w3snr > snr_limit  ))]
+
+w_notw1w2       = all_VHzQs[np.where((w1snr < snr_limit)  & (w2snr < snr_limit  ) )   ]
[…]

### 2018-08-27 detections/detections_vs_WISEcoverage_plots.py

@@ -1,0 +1,160 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+#import matplotlib
+import matplotlib as mpl
+
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from mpl_toolkits.axes_grid1.axes_divider  import make_axes_locatable
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
+from mpl_toolkits.axes_grid1.colorbar      import colorbar
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt97_WISE_coverage.dat', delimiter=r'\s', guess=False)
+
+## Setting up the variables for easier use
+w1mpro = all_VHzQs['w1mpro']
+w2mpro = all_VHzQs['w2mpro']
+w3mpro = all_VHzQs['w3mpro']
+w4mpro = all_VHzQs['w4mpro']
+w1snr = all_VHzQs['w1snr']
+w2snr = all_VHzQs['w2snr']
+w3snr = all_VHzQs['w3snr']
+w4snr = all_VHzQs['w4snr']
+w1cov = all_VHzQs['w1cov']
+w2cov = all_VHzQs['w2cov']
+w3cov = all_VHzQs['w3cov']
+w4cov = all_VHzQs['w4cov']
+
+
+
+##
+##  Making thesplot
+##
+##  May fave new line ;-=)
+#plt.style.use('dark_background')
+
+## 4 plots all in (one) row
+#fig, (ax1, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(14.0, 5.0))
+## If 1 by 4:: 
+left   = 0.04   # the left side of the subplots of the figure
+right  = 0.96   # the right side of the subplots of the figure
+bottom = 0.10   # the bottom of the subplots of the figure
+top    = 0.90   # the top of the subplots of the figure
+wspace = 0.48   # the amount of width reserved for blank space between subplots
+hspace = 0.20   # the amount of height reserved for white space between subplots
+
[…]

### 2018-08-27 detections/detections_vs_WISEmagM1450_plots.py

@@ -1,0 +1,110 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
+from mpl_toolkits.axes_grid1.colorbar import colorbar
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt97.dat', delimiter=r'\s', guess=False)
+
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+redshift = all_VHzQs['redshift']
+M1450_all = all_VHzQs['M1450']
+
+
+##
+##  Making thesplot
+##
+##  May fave new line ;-=)
+#plt.style.use('dark_background')
+
+fig, ((ax1, ax2), (ax3, ax4)) = plt.subplots(2, 2, figsize=(8.0, 8.0))
+
+## define the colormap
+cmap = plt.cm.inferno
+
+ls = 'solid'
+lw = 1.0
+ms = 100.
+ms_large = ms*3.
+fontsize=26
+
+xmin =   0.00; xmax =  40.00; ymin = -21.00; ymax =  40.00
+ax1.scatter(w1snr, M1450_all, s=ms, c=redshift, cmap= cmap, alpha=0.85, label='237 VHzQs')
+#ax1.legend(loc='upper left', fontsize=fontsize/1.3, frameon='True')
+ax1.set_xlim((xmin, xmax))
+ax1.set_ylim((ymin, ymax))
[…]

### 2018-08-27 detections/detections_vs_WISEmagsnr_plots.py

@@ -1,0 +1,207 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
+from mpl_toolkits.axes_grid1.colorbar import colorbar
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt97.dat', delimiter=r'\s', guess=False)
+
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+z_all = all_VHzQs['redshift']
+M1450_all = all_VHzQs['M1450']
+
+
+##
+no_bins = 101
+w1mag_limit   = np.empty(no_bins)
+w2mag_limit   = np.empty(no_bins)
+w3mag_limit   = np.empty(no_bins)
+w4mag_limit   = np.empty(no_bins)
+
+w1mag_percent = np.empty(no_bins)
+w2mag_percent = np.empty(no_bins)
+w3mag_percent = np.empty(no_bins)
+w4mag_percent = np.empty(no_bins)
+
+w1snr_limit   = np.empty(no_bins)
+w2snr_limit   = np.empty(no_bins)
+w3snr_limit   = np.empty(no_bins)
+w4snr_limit   = np.empty(no_bins)
+
+w1snr_percent = np.empty(no_bins)
+w2snr_percent = np.empty(no_bins)
+w3snr_percent = np.empty(no_bins)
[…]

### 2018-08-27 detections/detections_vs_WISEsnr_plots.py

@@ -1,0 +1,206 @@
+'''
+WISE detections and colors of Very High redshift quasars
+'''
+
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
+from mpl_toolkits.axes_grid1.axes_divider  import make_axes_locatable
+from mpl_toolkits.axes_grid1.colorbar import colorbar
+
+## READ-IN THE DATA FILE(S)
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+all_VHzQs  = ascii.read(path+'THE_TABLE_v0pnt971.dat', delimiter=r'\s', guess=False)
+
+
+## Setting up the variables for easier use
+w1mag = all_VHzQs['w1mag']
+w2mag = all_VHzQs['w2mag']
+w3mag = all_VHzQs['w3mag']
+w4mag = all_VHzQs['w4mag']
+w1snr   = all_VHzQs['w1snr']
+w2snr   = all_VHzQs['w2snr']
+w3snr   = all_VHzQs['w3snr']
+w4snr   = all_VHzQs['w4snr']
+w1_min_w2_all = (w1mag-w2mag)
+w2_min_w3_all = (w1mag-w2mag)
+w3_min_w4_all = (w1mag-w2mag)
+
+redshift  = all_VHzQs['redshift']
+M1450_all = all_VHzQs['M1450']
+
+
+##
+##  Making thesplot
+##
+##  May fave new line ;-=)
+#plt.style.use('dark_background')
+
+## 4 plots all in (one) row
+#fig, (ax1, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=(14.0, 5.0))
+## If 1 by 4:: 
+left   = 0.04   # the left side of the subplots of the figure
+right  = 0.96   # the right side of the subplots of the figure
+bottom = 0.10   # the bottom of the subplots of the figure
+top    = 0.90   # the top of the subplots of the figure
+wspace = 0.48   # the amount of width reserved for blank space between subplots
+hspace = 0.20   # the amount of height reserved for white space between subplots
+
+## 4 plots all 2x2 grid
[…]

### 2018-08-27 whatlines_whatredshift/EmissionLine_redshifts_passbands_MIRI_MRS.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+'''
+Python code to figure out/state when various (quasar) emission lines 
+move in and out of various SDSS/UKIDSS/WISE and JWST passbands
+'''
+
+import numpy as np
+
+np.set_printoptions(precision=3)
+
+
+## Table 9, Peth et al. (2011, AJ, 141, 105)
+Channel_1 = np.array([ 4.89,  5.65,  7.66])
+Channel_2 = np.array([ 7.49,  8.65,  11.71])
+Channel_3 = np.array([11.53, 13.37,  18.05])
+Channel_4 = np.array([17.66, 20.54,  28.45])
+
+## VdB01, Table 2, lambda_lab IN MICRONS!
+Lya_lambda    = 0.121567
+CIV_lambda    = 0.154906        
+MgII_lambda   = 0.279875
+Halpha_lambda = 0.656461
+## Figre from Glikman et al. 2006, ApJ, 640, 579
+## e.g. Table 6 and Fig. 1 etc. 
+## Balmer, Paschen, and Brackett     # Flux / Flux_Halpha
+O_one_lambda         = 0.8446         #  3.78
+S_three_lambda       = 0.9069         #  0.25
+Fe_two_lambda        = 0.9202         #  1.10
+Pa_epsilon_lambda    = 0.9545         #  2.02
+Pa_delta_lambda      = 1.0049        #  5.72
+## See also, Selsing et al, 2016, A&A, 585A, 87
+He_one_lambda        = 1.0830        # 10.05
+Pa_gamma_lambda      = 1.0941        #  1.85
+O_one_prime_lambda   = 1.1287        #  0.89
+Pa_beta_lambda       = 1.2820        #  4.82
+Pa_alpha_lambda      = 1.8756        #  3.10
+He_20k_lambda        = 2.0580        #  1.89
+Br_gamma_lambda      = 2.1654
+Br_beta_lambda       = 2.6260
+
+Channel_1_Lya = (Channel_1/Lya_lambda)-1
+Channel_2_Lya = (Channel_2/Lya_lambda)-1
+Channel_3_Lya = (Channel_3/Lya_lambda)-1
+Channel_4_Lya = (Channel_4/Lya_lambda)-1
+    
+Channel_1_CIV = (Channel_1/CIV_lambda)-1
[…]

### 2018-08-27 whatlines_whatredshift/EmissionLine_redshifts_passbands_YJHK.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+'''
+Python code to figure out/state when various (quasar) emission lines 
+move in and out of various SDSS/UKIDSS/WISE and JWST passbands
+'''
+
+import numpy as np
+
+np.set_printoptions(precision=3)
+
+
+## Table 9, Peth et al. (2011, AJ, 141, 105)
+Y_UKIDSS = np.array([ 0.9790,  1.0305,  1.0810])
+J_UKIDSS = np.array([ 1.16909, 1.2483,  1.3280])
+H_UKIDSS = np.array([ 1.4920,  1.6313,  1.7840])
+K_UKIDSS = np.array([ 2.0290,  2.2010,  2.3800])
+
+## VdB01, Table 2, lambda_lab IN MICRONS!
+Lya_lambda    = 0.121567
+CIV_lambda    = 0.154906        
+MgII_lambda   = 0.279875
+Halpha_lambda = 0.656461
+## Figre from Glikman et al. 2006, ApJ, 640, 579
+## e.g. Table 6 and Fig. 1 etc. 
+## Balmer, Paschen, and Brackett     # Flux / Flux_Halpha
+O_one_lambda         = 0.8446         #  3.78
+S_three_lambda       = 0.9069         #  0.25
+Fe_two_lambda        = 0.9202         #  1.10
+Pa_epsilon_lambda    = 0.9545         #  2.02
+Pa_delta_lambda      = 1.0049        #  5.72
+## See also, Selsing et al, 2016, A&A, 585A, 87
+He_one_lambda        = 1.0830        # 10.05
+Pa_gamma_lambda      = 1.0941        #  1.85
+O_one_prime_lambda   = 1.1287        #  0.89
+Pa_beta_lambda       = 1.2820        #  4.82
+Pa_alpha_lambda      = 1.8756        #  3.10
+He_20k_lambda        = 2.0580        #  1.89
+Br_gamma_lambda      = 2.1654
+Br_beta_lambda       = 2.6260
+
[…]

### 2018-08-27 tex/VHzQ_colorcolor/colorplot.tex
README.md and tex directory added

\documentclass[11pt,a4paper]{article}
\input{format}

\begin{document}

   \title{Colour-colour plots for VH$z$Q Selection}
 \date{\today}
\maketitle

\section{(z-J) vs. (J-W1)}
    \begin{figure}
      \centering
      % trim={<left> <lower> <right> <upper>}
      \includegraphics[width=16.0cm, trim={0.5cm 0 0 0},clip]
      {Wang2017_Fig1.jpeg}
      \caption[]{\citet{Wang2017}}
      \label{fig:Wang2017}
    \end{figure}

\section{(z-y) vs. (y-J)}

    \begin{figure}
      \begin{center}
      \includegraphics[width=16.0cm,  trim={1.5cm 0 0 0},clip]
      {Mazzucchelli_2017_Fig1.jpeg}
     \caption[]{\citet{Mazzucchelli2017}}
      \label{fig:Mazzucchelli2017}
      \end{center}
    \end{figure}

\section{(i-z) vs. (z-y)}
    \begin{figure}
      \centering
      \includegraphics[width=16.0cm,  trim={1.5cm 0 0 0},clip]
      {Matsuoka_2016_Fig1.jpeg}
      \caption[]{\citet{Matsuoka2016}}
      \label{fig:Matsuoka2016}
    \end{figure}

    \begin{figure}
      \centering
      \includegraphics[width=16.0cm,  trim={1.5cm 0 0 0},clip]
      {Matsuoka_2018_Fig11.jpeg}
      \caption[]{\citet{Matsuoka2018}}
      \label{fig:Matsuoka2018}
    \end{figure}

\section{(z-y) vs. (i-z)}

    \begin{figure}
      \centering
%      \includegraphics[width=16.0cm,  trim={1.5cm 0 0 0},clip, angle=90]
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]
      {Banados_2014_Fig1.jpeg}
      \caption[]{\citet{Banados2014}. 
        Right: color–color diagram showing the criteria used to select quasar
        candidates (long-dashed line, upper left corner). The dot-dashed line
        is used for candidates with upper limits in the iP1 band. The thick
        black line shows the expected color of the quasar template from
        \citet{Decarli2010} redshifted from $z=5.0$ to $z=6.5$ in steps of
        $\Delta z = 0.1$ (see left panel). The M/L/T dwarfs from \citet{Dupuy_Liu2012}  that have a PS1 counterpart are shown with stars. Blue squares are
        published quasars at 5.7 < z < 6.4 satisfying our S/N and coverage
        criteria. Fourteen of them were included in our candidate list. Green
        triangles represent the PS1 colors of unpublished spectroscopically
        confirmed z ∼ 6 quasars (S. J. Warren et al., in preparation). Three
        of them were part of our candidate list (see Tables 4 and 5). The red
        diamonds are the new quasars presented in this paper (see Table
        2). They are labeled with the following letters: a = PSO
        J340.2041–18.6621 (z = 6.00), b = PSO J007.0273+04.9571 (z = 5.99), c
        = PSO J037.9706–28.8389 (z = 5.99), d = PSO J187.3050+04.3243 (z =
        5.89), e = PSO J213.3629–22.5617 (z = 5.88), f = PSO J183.2991–12.7676
        (z = 5.86), g = PSO J210.8722–12.0094 (z = 5.84), h = PSO
        J215.1514–16.0417 (z = 5.73), and i = PSO J045.1840–22.5408 (z =
        5.70).
}
      \label{fig:Banados2014}
    \end{figure}

    \begin{figure}
      \centering
%      \includegraphics[width=16.0cm,  trim={1.5cm 0 0 0},clip, angle=90]
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]{f1_ps1_color_selection.pdf}
      \caption[]{\citet{Banados2016}.} 
      \label{fig:Banados2016}
    \end{figure}

\section{(W1 - W2) vs. (z - W2)}
    \begin{figure}
      \centering
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]{Carnall_2015_Fig1.jpeg}
      \caption[]{\citet{Banados2016}.} 
      \label{fig:Banados2016}
    \end{figure}

\newpage
    \begin{figure}
      \centering
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]{f4_yj_selection.pdf}
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]{f6_ntt_colors.pdf}
      \includegraphics[width=16.0cm,  trim={0.0cm 0 0 0},clip, angle=0]{f5_wise_prioritization.pdf}
      \caption[]{\citet{Banados2016}.} 
      \label{fig:Banados2016_3panels}
    \end{figure}

\bibliographystyle{mn2e}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}

\end{document}

### 2018-08-27 tex/WW4C_VHzQ.tex
README.md and tex directory added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                           
%%  
%%									    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[usenatbib]{mnras}

\input {format}

\begin{document}

\title[Very high-$z$ Quasars]
        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
\author[Ross \& Cross]
       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
\\ 
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
}

\maketitle
\begin{abstract}
In this paper, we, for the first time since the discovery of $z\geq5$
quasars, assemble all spectroscopically confirmed very high redshift
quasars in one catalogue.  In particular we present the near
($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
all 424 spectroscopically confirmed redshift $z\geq5.00$ quasars.
Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
photometric variability in the near-infrared that might be expected
from Super-Eddington accretion and find {\it blah}.  We present a
comprehensive series of colour-redshift and colour-colour plots and
make inferences into the hot dust properties of the very high-redshift
quasar population. Extrapolating the known quasar luminosity function
we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
current datasets have been discovered.
\end{abstract}

\begin{keywords}
Astronomical data bases: surveys -- 
Quasars: general -- 
galaxies: evolution -- 
galaxies: infrared.
\end{keywords}

\iffalse
\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Concentrate on reporting NIR and W1/W2 figures and tables
\item SED dust plots 
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check for NIR and MIR variabilty with the Wu quasar
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
\end{itemize}

\noindent
{\bf For NJGC: }
\begin{itemize}
\item Write the NIR data section(s) 
\end{itemize}

\noindent
{\bf For Both: }
\begin{itemize}
\item Need to decide what mags and mag system we are reporting, especially in the 
NIR...
\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
\end{itemize}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Very high redshift quasars (VH$z$Q; defined here to have redshifts
$z\geq5.00$) are excellent probes of the early Universe. This includes
studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.

Super-Eddington (also called super-critical) accretion is a viable
physical mechanism to explain the high luminosity and rapid growth of
supermassive black holes in the early universe
\citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
one might well expect VH$z$Qs to vary in luminosity as they
potentially go through phases of Super-Eddington accretion and these
signatures of photometric variablity should be looked for, especially
when the e.g. near-infrared $K$-band is sampling rest-frame
$\approx$3670, 3145, 2750\AA\ at redshifts $z=5, 6$ and 7,
respectively.

Quasars are also known to be prodigious emitters of infrared emission,
thought to be from the thermal emission of dust grains heated by
continuum emission from the accretion disc
\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m allow
discrimination between AGN\footnote{Historically, ``quasars'' and
``Active Galactic Nuclei (AGN)'' have described different
luminosity/classes of objects, but here we use these terms
interchangeably (with a preference for quasar) in recognition of the
fact that they both describe accreting supermassive black holes
\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
Timlin2016} as well as AGN and star-forming galaxies due to the
presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
\citep[e.g., ][]{Yan2007, Tielens2008}.

\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
a quasar without hot-dust emission in a sample of 21 $z\approx6$
quasars. Such apparently hot-dust-free quasars have no counterparts at
low redshift. Moreover, those authors demonstrate that the hot-dust
abundance in the 21 quasars builds up in tandem with the growth of the
central black hole.

WISE mapped the sky in 4 passbands, in bands centered at wavelengths
of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
``ALLWISE'' catalog, contains nearly 750 million detections at
high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
detections of 17 (55\%) of the then known 31 quasars at $z >
6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
data release, as opposed to the superior ``AllWISE'' catalogs. That
sample only examined the 31 known $z>6$ quasars; our sample has 148
objects with redshift $z \geq 6.00$.

Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
with Table 8 of][]{Banados2016}. Our motivations are numerous and
include: {\it (i)} establishing the first complete catalogue of
$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
reporting homogenous near-infrared photometry for the quasars; {\it
(iii)} making the first study of NIR variability of the VHzQ
population and {\it (iv)} establishing the photometric properties for
upcoming surveys and telescopes, e.g. the Large Synoptic Survey
Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
ESA {\it
Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
and the {\it James Webb Space Telescope}
(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}

This paper can be considered an update of \citet{Blain2013} and also
an extension of parts of \citet{Banados2016}, with the latter study
reporting WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey
Telescope and Rapid Response System 1 \citep[Pan-STARRS1,
PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation
into the reddest WISE waveband for the VH$z$Qs.  \citet{Banados2016}
reports and investigates the W1, W2 and W3 properties of quasars at $z
> 5.6$. We chose redshift $z=5.00$ as our lower redshift limit due to
a combination of garnishing a large sample, adequately spanning
physical properties (e.g. luminosity, age of the Universe) and to
incorporate what knowledge we have gained over the last couple of
decades since $z>5$ quasars were discovered.

This paper is organized as follows.  In Section 2, we present the
assembled list of the 424 $z\leq5.00$ VH$z$Qs that we have
compiled. We then give a high-level overview of the photometric
surveys and datasets we use and present the photometry of the VH$z$Qs.
In Section 3 we In Section 4 we and we then note our Conclusions in
Section 5.

We make the somewhat unconventional decision to present all our
photometry and magnitudes on the AB zero-point system
\citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared,
as well as the mid-infrared magnitudes.  Because of established
conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point
system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
magnitudes are calibrated on the Vega system (Wright et al. 2010). For
WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339,
5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about
Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
Filter. We make use of the Explanatory Supplement to the WISE All-Sky
Data Release, as well as the WISE AllWISE Data Release Products
online.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km
s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} =
0.693$ (Planck Collaboration et al. 2016) in order to be consistent
with \citet{Banados2016}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

\vspace{-16pt}
\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and 
we have assembled this in the following manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

We then obtain optical, near-infrared and mid-infrared photometry for the
spectral dataset. The optical data comes from the 
Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.

Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
delivering exquisite multi-band photometry data
\citep[][]{Aihara2018b} the five broad bands $grizy$.

The near-infrared data comes from two primary sources. First, the Wide
Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
\citep[Visible and Infrared Survey Telescope for
Astronomy;][]{Emerson2006, Dalton2006}.

We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.

Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
of the filters in question.

\input{THE_TABLE_v0pnt96_TOP10_betterformat}

\subsection{Spectroscopy} 
We have obtained a list of 424 spectroscopically confirmed 
quasars with redshifts $z\geq5.00$.

In Table~\ref{tab:THE_TABLE}  we give the discovery reference for the
VH$z$Qs noting that some objects were discovered independently and
contemporaneously.  The redshifts for the VH$z$Qs generally come from
the measurement of broad UV/optical emission lines. Where 
there are far infra-red emission lines e.g. \cii~158 micron, we report 
these, but at the level of our current analysis broadline redshifts are
sufficient.

Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
\citet{Fan2003}, \citet{Fan2004}, \citet{Mahabal2005},
\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
and \citet{Matsuoka2018b}.

Table~\ref{tab:THE_TABLE} gives the salient details for the objects
used in this study. We use all the $z\geq5.00$ quasars that
have been discovered and spectroscopically confirmed as of the time of
writing (2018 June). We report near-infrared ($yYJHK$-bands)
and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
$M_{1450}$.

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey   & \# VH$z$Qs & Notes/Survey reference  \\
\hline  
  ATLAS      &     4    &  \citet{Shanks2015} \\
  CFHQS     &   20    &  \citet{Willott2007} \\
  DELS        &     2    &  \citet{Dey2018} \\
  ELAIS       &     1    &  \citet{Vaisanen2000} \\
  FIRST       &     1    &  \citet{Becker1995} \\
%  HSC         &     8    &  \\
  IMS          &     1     &  \citet{Kim2015} \\
  MMT        &   12    &  \citet{McGreer2013} \\
  NDWFS    &     1     &  \citet{JD1999} \\
  PSO          &   84    &   \citet{Kaiser2002, Kaiser2010} \\
  RD           &     1       &  \cite{Mahabal2005} \\
  SDSS        & 156       & \citet{EDR} \\
  SDUV       &   20       & \citet{Yang2017} \\
  SDWISE    &   27    &     \citet{Wang2016} \\
  SHELLQs  &  $^{a}$63   &  \citet{Matsuoka2016}\\  %% includes 8 objects from the first HSC paper..
  ULAS       &   10   & \citet{Lawrence2007} \\
  VDES       &   11   &  \citet{Reed2017} \\
  VIK          &     9   &  \citet{Edge2013} \\
  VIMOS     &     1   &  \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference. 
$^{a}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018}  
designation.
}
      \label{tab:surveys}
\end{table}

\subsection{Optical Photometry}
    \subsubsection{Pan-STARRS1 (PS1)} 
    We query the Panoramic Survey Telescope and Rapid Response System
    (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
    Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
    service at
    \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
    The PS1 survey observed the 30,000 deg$^{2}$ of sky north of
    declination $-30$ degrees in five filters $grizy$.  Pan-STARRS1 (PS1)
    is the first part of Pan-STARRS to be completed and is the basis for
    the DR1.  \citet{Chambers2016}, \citet{Magnier2016a},
    \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
    \citet{Flewelling2016} describe the instrument, survey, and data
    analyses.  The principal science product of the PS1 survey is the
    catalog accessible through the CasJobs interface.

    We query and return the mean PSF magnitudes from the $grizy$ filters
    ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
    sample. Details of our SQL and links to the main tables are given
    in Appendix~\ref{sec:PS1_SQL}.

    \iffalse
    \subsubsection{DECam} 
    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
    is a wide-field imager with a 2.2 degree diameter field of view 
    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
    at the Cerro Tololo International Observatory. We use data 
    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
    \fi

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.

We query the WFCAM Science Archive
\citep[\href{http://wsa.roe.ac.uk/}{WSA}; ][]{Hambly2008} which
reports NIR photometry from the Wide Field Camera \citep[WFCAM;
][]{Casali2007} on the United Kingdom Infrared Telescope (UKIRT).
Data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
\citep[Visible and Infrared Survey Telescope for Astronomy;
][]{Emerson2006, Dalton2006} is also given in the WSA.

Quasars are known to vary (both photometrically and spectroscopically)
and very high-$z$ quasars under going super-Eddington accretion during
a rapid BH growth phase are prime candidates for this variation.
Therefore, with repeat observations over many epochs availble via the
WSA, we have a choice to make for how we report the photometry. After
tests, we decide to give the NIR photometry averaged on 4 week
observed timescales. This time bracket is chosen as a good compromise
between maximising signal-to-noise while keeping the cadence high. At
our observed redshifts, we sample $\lesssim1$week in the rest-frame
and luminous quasars are not expected to vary on timescales quicker
than this \citep[e.g., ][]{Lawrence2016_ASPC}.

We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.

The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

In this paper we include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017 and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (200910..) to 1st April 2016, to get as much coverage as
possible. Hence, the NIR is extremely heterogeneous.

The data was processed using a forced photometry, or matched-aperture
photometry. A pipeline for this has been developed by WFAU, but
has not yet been incorporated into the main VDFS pipeline. Full details of the
matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
2018, in prep, and has also been discussed in \citet{Cross2013}.  
%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS.
We will give the pertinent points of the MAP and specific details of these data sets below.

    \subsubsection{UKIDSS LAS} 
    In a bit more detail, use:\\
    dr10plus\\
    lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
    424 results returned. Of which...

    \subsubsection{VISTA VHS} 
    In a bit more detail, use:\\
    VH5DR5 \\
    sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
    424 results returned.  Of which...

    {\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...

    The first step of the process was to ingest the catalogue of VHzQs into
    the WSA/VSA. These data are in the table \verb+finalQsoCatalogue+. Next we set
    up new programmes WSERV1000, VSERV1000 in the WSA and VSA respectively. We
    assign all frames that contain the high-z QSO based on WCS information in the
    WSA to WSERV1000, but adding a new line to the table \verb+ProgrammeFrame+ and
    same in VSA for VSERV1000. Assigning these frames to a separate programme allows
    us to process them together and put them into a single release.

    \subsubsection{Setup Matched Aperture Product}

    Add a new entry \verb+RequiredMatchedApertureProduct+

    \begin{itemize}
    \item mapID	archiveName	programmeID	extractor	mapType	name	description	selection	finalProductTable	addSurveyList
    \item 1	1	WSA	10999	CASU	2	highzQsoMap	Variability via matched apertures for set of high-z QSOs	SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue	highzQsoMapVariability	NONE
    \end{itemize}

    Explain

    Entries in \verb+RequiredMapAverages+

    Add table?
    \begin{table*}
      \begin{center}
        \setlength{\tabcolsep}{4pt}
        \begin{tabular}{lll lll lll l}
          \hline \hline
          &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
          \hline
          1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
          2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
          3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
          4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
          5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
          6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
          \hline \hline
          \label{tab:The_Numbers}
        \end{tabular}
        \caption{}
      \end{center}
    \end{table*}

    \subsubsection{Processing MAP data and Forced photometry} 
    A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
    the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
    seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
    but the layer is a general abstraction that allows multiple sources of
    catalogue, and multiple types\ldots
    Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent

    CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
    the input list equal to objects selected to be within \ldots of the multiframe
    centre. In this case, where there are 424 QSOs spread across the sky, there is
    typically 1 object per multiframe, but many have two and one,
    multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
    is a multi-extension FITS binary table, with identical columns to the CASU FITS
    binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
    VISTA survey products and also familiar to many astronomers through the INTWFS, 
    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
    Since forced photometry can be run
    in many ways on a particular image, a single science frame is not
    necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
    information on what processing stage they are at ({\bf bitProcessingFlag}),
    whether they have been ingested ({\bf isIngested}), or what quality control has
    been run on them ({\bf ppErrBitsStatus}).

    For matched aperture measurements, we process these binary tables using the same
    software, as the standard extracted catalogues, but implement a few different
    processes. We calculate both Luptitudes \citep{Luptitudes}, and calibrated fluxes,
    see Eqn~\ref{eq:jky}.

    \begin{equation}
      F^{calib} = f\times10^{-0.4*(ZP+VAB-8.90+corr)} 
      \label{eq:jky}
    \end{equation}

    \noindent where $f$ is the measured flux in ADU, $ZP$ is the zeropoint of
    frame, $VAB$ is the Vega-to-AB correction for the filter, and $corr$ are the
    various correction terms, e.g. distortion correction, scattered light
    correction, aperture correction, see \citep{Hambly2008, Cross2012}.

    Once all data is processed, the data are ingested into
    \verb+wserv1000MapRemeasurement+ and \verb+vserv1000MapRemeasurement+
    respectively. These tables are similar in structure to \verb+lasDetection+
    described in \citep{Hambly2008} or other UKIDSS or VISTA detection tables. One of
    the main differences is the primary key which is ({\bf apertureID},{\bf
      catalogueID}) rather than ({\bf multiframeID},{\bf extNum},{\bf seqNum}),
    reflecting the fact that these are forced photometry on a known set of apertures
    and a set of catalogues, rather than detections above a threshold in a set of
    detector extensions to image multiframes.

    \subsubsection{Averaging matched photometry}
    Unfortunately the photometry in a single epoch image often has low
    signal-to-noise. The advantage of matched aperture photometry on QSOs is that
    co-adding is relatively simple: if each epoch is taken in the same aperture
    (assuming the astrometry is correct) and the aperture photometry has been
    corrected to total: the standard aperture corrections work well for point
    sources then averaging the calibrated photometry should give as good as
    extracting from a deep stack. In fact it will almost certainly do better, since
    the images in some cases are taken from multiple projects with different
    pointings. In addition, corrections such as scattered light, pixel distortion
    and aperture corrections will be more complex, if not impossible to apply to
    deep-stacks but will be automatically applied in the averaging of forced
    photometry.

    We average the aperture corrected calibrated fluxes (e.g. {\bf aperJky3}), and
    then convert to magnitudes or luptitudes. Since we do not have a deep image for
    each set of averages, we cannot calculate non-aperture corrected values, so the
    photometry is only appropriate for point-sources.

    \begin{equation}
      \bar{F} = \frac{\sum_i^N (w_i\,F_i)}{\sum_i^N w_i}  
      \label{eq:avg}
    \end{equation}

    \noindent where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
    averaged such as the aperture corrected calibrated flux in a $1\arcsec$ aperture
    ({\bf aperJky3}) and $\bar{F}$ is the weighted mean average of this parameter.
    The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
    $w_i=0$ if an epoch is excluded for quality control purposes. We exclude inputs
    where the bitwise quality flag, {\bf ppErrBits}>256, and additionally, in the
    case of VISTA, we exclude data on detector 16 ({\bf extNum=17}), where the 
    quantum efficiency is variable. If all remeasurements are excluded, then one  of
    the ones with the lowest {\bf ppErrBits} is used. In this case the averages 
    will be equal to the original measurement, and the reader may wonder why we 
    bother to duplicate the data. It is important to do this to simplify queries 
    for users who will then not have to set up complex queries to work out where 
    the data is, and only around $2\%$ of VISTA MAP measurements were excluded  so
    the fraction of duplications is very low. The average data is stored in 
    \verb+wserv1000MapRemeasAver+ for WFCAM and \verb+vserv1000MapRemeasAver+ for 
    VISTA, which again are organised with a primary key of ({\bf apertureID},{\bf catalogueID}).
    Some parameters that are averaged do not have an error $\sigma_{F}$, so in these
    cases we weight them using the {\bf averageConf} parameter, which has a median
    of 100. In the case of WFCAM where this is not calculated, we set each epoch to
    have an {\bf averageConf}$=100$. The {\bf sumWeights} parameter in the
    \verb+MapRemeasAver+ tables is the sum of all the {\bf averageConf} values that
    went into the calculation and the \verb+vserv1000MapAverageWeights+ table gives
    the weights for each epoch, linked to each average for VSERV1000.

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 28, 183 days, over 10 epochs and finally over all epochs. The
    averaging process starts at the first epoch and works on. Possible future
    refinements could first look for denser groupings that satisfied the criteria so
    that these were not split into two groups.

    Each averaged catalogue has a separate entry in
    \verb+MapFrameStatus+ and is linked to each original epoch remeasured catalogue
    through \verb+MapProvenance+, which contains the averaged catalogue
    identifier {\bf combiCatID}, the epoch catalogue identifier {\bf catalogueID}
    and the averaging setup ID {\bf avSetupID}.

    The code to calculate variability statistics as described in \cite{Cross2009} has
    not yet been completed to run with the matched aperture pipeline, so these are
    not included.

\subsection{MIR data}
The MIR data for this study comes exclusively from the Wide-field
Infrared Survey Explorer (WISE) mission. Since we are only concerned
here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
exploration of the VH$z$Q population in e.g. the large Spitzer areal
surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.

We use data from the the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fourth-year of NEOWISE-R
operations \citep[2017 December;]{Mainzer2011}. More specifically, we
use the data from the
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
program and catalogue, which combines data from the WISE cryogenic and
NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
phases. For the our variability investigations, we supplement the
ALLWISE data with data from the
\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
(W1 and W2) single-exposure images and extracted source information
that were acquired between 2016 December 13 and 2017 December 13 UTC,
which was the fourth year of survey operations of the Near-Earth
Object Wide-field Infrared Survey Explorer Reactivation Mission
(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
data products are concatenated with those from the first three years
(originally released on March 26, 2015, March 23, 2016 and June 1,
2017) into a single archive.

The WISE scan pattern leads to coverage of the full- sky approximately
once every six months (a``sky pass''), but the satellite was placed in
hibernation in 2011 February and then reactivated in 2013
October. Hence, our light curves have a cadence of 6 months with a 32
month sampling gap.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Having collated the sample of 424 VH$z$Qs, and obtained their optical,
near- and mid-infrared photometry we report here the various
photometric properites of the quasars.

First, we will concentrate on detection rate in the infrared, go on to
report on the color-redshift and color-color properties of our sample
and then report on how the current sample populates the
luminosity-redshift $Lz$-plane.

    %\subsection{Detection Rates in the optical}

    \subsection{Detection Rates in the NIR}
    Table~\ref{tab:nir_detection} gives the detection rates for the 
    VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
    The first thing to note is that the coverage of the NIR surveys 
    for example from the UKIDSS LAS and VISTA VHS, does
    not overlap the full area for where the VH$z$Qs are detected.

    \begin{table}
          \centering

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($YJHK/K_{s}$   &  394  ( ) \\
        $Y$-band    &    ( ) \\
        $J$-band    &    ( ) \\
        $H$-band    &    ( ) \\
        $K$ or $Ks$-band    &    ( ) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

        \subsubsection{Comparing WFCAM and VISTA}
        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
        objects on the same AB system, and for each object compared the two
        measurements. First, the calculated weighted average (calibrated flux)
        in each filter of both and calculated the ratio and difference between
        each measurement and the average.  Then for each filter we calculated
        the weighted average of the differences (in mag) for each instrument
        to see if there were significant offsets. The results are given in
        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
        offset is the $Y$-band. All of the VISTA averages are negative and all
        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
        slightly dodgy, given the different shapes of the filters.
        \begin{table}
          \centering
          \begin{tabular}{l r r}
            \hline  \hline
            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
            -  WFCAM)      &                                        &  objects \\
            \hline
            $Z$                 &  19.3 	& 2 \\
            $Y$                 &  66.2 	& 48 \\
            $J$                  &    3.2 	& 105 \\
            $H$                 &  19.3     &  89 \\
            $K_{\rm s}$/$K$ &  12.7     & 93 \\
            \hline  \hline
          \end{tabular}
          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
          \label{tab:WFCAM_vs_VISTA}
        \end{table}

    \subsection{Detection Rates in the MIR}
    Unlike the NIR coverage, the WISE
    satellite and mission performed an all-sky survey, so the location of
    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
    ALLWISE survey depends heavily on sky location, with locations near
    the Ecliptic Poles having the highest number of exposures.

    Before reporting on the detection rates, we investigate this
    effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
    versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
    coverage depth, in each corresponding band. In the two shorter bands
    W1/2 we see the clear and expected trend for brighter objects to have
    larger SNR, and also for the higher signal to noise for objects with
    more exposures at a given magnitude. The behaviour for the W3/4 bands
    is different, with two populations clearly evident in W3 and although
    a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
    no obvious R.A./Declination dependence seen, this behaviour is
    explained by the fact that there are non-detectiopns in W3/4 for
    objects (with high W1/2 SNR) that are reported in the ALLWISE
    catalogue.

    For the 278 VH$z$Q with coverage detections, the mean number of
    exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
    minimum number of exposures 17 and 12, and the maximum number or
    exposures being 114 (for both bands).  For the W3/4 filters, the
    corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
    5.8 and 6.8 and 69 (for both bands). These values are direclty from
    the {\tt w$x$cov} enteries in the 
    \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.

    \begin{figure}
      %% trim=l b r t
      \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
      \centering
      \vspace{-14pt}
      \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
        colour coded by w$x$cov the mean coverage depth, in each corresponding band.
      }
      \label{fig:WISEmag_vs_coverage}
    \end{figure}

    Table~\ref{tab:mir_detection} gives the detection rates for the
    VH$z$Qs in the MIR WISE W1-4 bands. 
    \begin{table}
      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        W1 SNR $> 2.0$   &  275  (64.9) \\
        W2 SNR $> 2.0$   &   255 (60.1) \\
        W1 \&\& W2 SNR $> 2.0$  &  \\
        W3 SNR $> 2.0$   &  99    (23.3) \\
        W4 SNR $> 2.0$   &  29    (6.8) \\
        Any W1/2/3/4 SNR $>2.0$ & \\
        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
        \hline  \hline
      \end{tabular}
      \caption{ATLAS \citet{Shanks2015}; }
      \label{tab:mir_detection}
    \end{table}

    \begin{figure}
      %% trim=l b r t
      \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
      \centering
      \vspace{-14pt}
      \caption[]{WISE signal-to-noise measures for the four bands, as well
        as for (W1-W2) colour.  The points are colour coded by redshift.}
      \label{fig:WISEmag_vs_coverage}
    \end{figure}

    \citet{Blain2013} Cras in laoreet mauris. Vivamus nec nulla a dui
    commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet
    auctor ligula ultricies. Phasellus condimentum gravida
    tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et
    augue id purus gravida sagittis quis in sem. Phasellus quis risus
    bibendum eros luctus auctor.

    Recently, \citet{Assef2018} released two large catalogues of AGN 
    candidates identified across 30,000 deg$^2$ of extragalactic sky 
    from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
    contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
    AGN candidates per deg$^2$) while the ``C75'' catalog 
    consists of 20.9M AGN candidates at 75\% completeness (and 
    ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
    out catalogue of 424 VH$z$Qs with these catalogues, produces 
    42 matches with	the R90 sample and 98 matches with the C75 sample. 
    Both catalogues unsurprisingly match to the ultraluminous quasar 
    SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
    mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
    matches J1342+0928 \citep{Banados2018}.

    %\subsubsection{
    Very High-$z$ Quasars Detected in WISE W3 and W4.
    Proin non tempus velit. Etiam laoreet, enim nec scelerisque
    dictum, tortor massa tempor enim, id pretium justo quam ac
    lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
    et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
    eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
    velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
    purus.

    \subsection{Variability}
    VH$z$Qs, if accreting at, or above the Eddington Limit, might well
    have have large values of changing mass accretion rate, $\ddot{m_{\rm
        accr}}$. A consequence of this would be that these quasar exhibit signs
    of variability, most likely showing up in their UV/optical rest-frame
    spectra.

    We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs. As a guide, \civ  enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the $H$-band at redshift  $z=4.33$ and exits at $z=5.37$ and enters the $K$-band at redshift  $z=6.25$ and exits at  $7.50$.

    Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we unc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu at orci egestas convallis. Aenean quam velit, aliquam vitae viverra in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla. Nullam eu augue id purus mollis dignissim sed et libero. Phasellus eget justo sed neque pellentesque egestas nec id arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel neque id mi ultrices tristique. Integer quam libero, ornare vel gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi. Vestibulum nec mi justo, eget dapibus velit.

   Looking at the lighcurves

\subsection{Colours}
Pellentesque vel elit neque, in interdum lacus. Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a nisl. Ut sit amet sapien a risus dapibus sagittis. Cras sed ultricies erat. Donec id metus sed urna lacinia convallis vel sed enim. Proin nisi libero, ornare vel bibendum eu, sollicitudin sed leo. Cras tincidunt aliquet ultricies. Cras pretium velit leo, in malesuada enim. Duis sagittis ultricies interdum. Proin sit amet sem nec metus feugiat pharetra.

Figure~\ref{fig:Opt_colourredshift} presents the optical
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
   \centering
   \caption[]
   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
bigger gaps between subplots??}}
   \label{fig:Opt_colourredshift}
 \end{figure*}

Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
the blue or red end respectively. Hmmm....}
   \label{fig:SpecType_vs_NIRcolors}
 \end{figure*}

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
}
   \label{fig:SpecType_vs_W1W2_W2W3colors}
 \end{figure*}

\subsection{L-$z$ Plane}
Having obtained an as-near-to-homogenous set of photometry as we can, 
we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
sample and in particulare the absolute magnitude at rest-frame 1450\AA'\, $M_{1450}$, 
which is a key physical quantity and goes directly towards the quasar luminosity 
function and thus the reionization of hydrogen calculation.

At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
i.e., in the $z$-band, while at

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:Lz}
\end{figure*}

\subsection{SEDs and Dust properties of the VH$z$Qs}
There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
However, they are, for our purposes all roughly the same.

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:RestWavelength_SEDs}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, ompiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

%%
We can gain a good appreciation for what these missions will discover
by collating the datasets we currently have.

\begin{itemize}
    \item Lorem ipsum dolor sit amet, consectetur adipiscing
      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
      convallis ac. 
    \item Fusce pellentesque condimentum dolor, quis vehicula
      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
      diam eu blandit. Donec in lacinia libero.
    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
      euismod. Cras vel auctor neque. Nam quis diam risus.
\end{itemize}
Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
eu elit massa. Nulla vel lacus lorem. Proin et lobortis
tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
eget tempor elementum, lectus urna feugiat nisi, eget sagittis.

\section*{Acknowledgements}
NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.

We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.

This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
\citep[][]{Taylor2005, Taylor2011}.

This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
a community-developed core Python package for Astronomy 
\citep{AstropyCollaboration2013, AstropyCollaboration2018}.

The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
been made possible through contributions by the Institute for
Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
the Max-Planck Society and its participating institutes, the Max
Planck Institute for Astronomy, Heidelberg and the Max Planck
Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
University, Durham University, the University of Edinburgh, the
Queen's University Belfast, the Harvard-Smithsonian Center for
Astrophysics, the Las Cumbres Observatory Global Telescope Network
Incorporated, the National Central University of Taiwan, the Space
Telescope Science Institute, the National Aeronautics and Space
Administration under Grant No. NNX08AR22G issued through the Planetary
Science Division of the NASA Science Mission Directorate, the National
Science Foundation Grant No. AST-1238877, the University of Maryland,
Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
and the Gordon and Betty Moore Foundation.

This project used data obtained with the Dark Energy Camera (DECam)
and the NOAO Data Lab, The Data Lab is operated by the National
Optical Astronomy Observatory, the national center for ground-based
nighttime astronomy in the United States operated by the Association
of Universities for Research in Astronomy (AURA) under cooperative
agreement with the National Science Foundation.

CasJobs was originally developed by the Johns Hopkins University/
Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
used version 3.5.16 to construct CasJobs-based tools for GALEX,
Kepler, the Hubble Source Catalog, and PanSTARRS.

This publication makes use of data products from the Wide-field
Infrared Survey Explorer, which is a joint project of the University
of California, Los Angeles, and the Jet Propulsion
Laboratory/California Institute of Technology, and NEOWISE, which is a
project of the Jet Propulsion Laboratory/California Institute of
Technology. WISE and NEOWISE are funded by the National Aeronautics
and Space Administration.

This research has made use of the SVO Filter Profile Service
(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
MINECO through grant AyA2014-55216 
%%
The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
describes the Spanish VO Filter Profile Service. 
The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html

\newpage

\appendix
\section{Filter Curves} 
FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.

\section{A. Photometric Bands and Conversions}
    Due to the differing normalizations between the
    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
    our data in the  purest sense, all the NIR magnitudes from UKIDSS
    (originally AB magnitudes)  were corrected to Vega magnitudes as
    suggested in \citet{Hewett2006}.

    Although ULAS magnitudes are reported in terms of Vega and SDSS
    magnitudes are reported in AB terms for the most part whenever an
    optical-NIR color was calculated both magnitudes were left in their
    default term.

\begin{table*}
  \begin{center}
   \caption{Adapted from Table 9 of \citet{Peth2011}. 
CTIO/DECam, PanSTARRS/PS1, LSST
%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
Filter only values. 
All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 
%%
%%
From \citet{GonzalezFernandez2018} 
$Z_{\rm AB}   -  Z_{\rm Vega}  = 0.502$;  
$Y_{\rm AB}  -  Y_{\rm Vega}    = 0.600 $;
$J_{\rm AB}   -  J_{\rm Vega}    = 0.916  $;
$H_{\rm AB}  -  H_{\rm Vega}    = 1.366 $;
$Ks_{\rm AB}  -  Ks_{\rm Vega}  = 1.827 $;
%%
and the CASU Vega to AB conversions v1.3:: 
	Z,Y,J,H,Ks were: 0.524, 0.618, 0.937, 1.384, 1.839. 
%%
So, $\Delta$(vs. Gonzalez-Fernandez)::
	(11.2,     1.1,    5.4,     1.6,    0.1) millimags. 
$\Delta$(vsCASU v1.3)::
	(-10.8, -16.9, -15.6,  -16.4, -11.9) millimags. 
}
    \setlength{\tabcolsep}{4pt}
     \begin{tabular}{l r r r  c l l}
      %% https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
      %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
      \hline
      \hline
      Band & $\lambda_{\rm eff}  $ 
              &  $\lambda_{\rm min} $ 
              & $\lambda_{\rm max} $ 
              & W$_{\rm eff}$
              & \multicolumn{2}{c}{AB - Vega  Transformations} \\
      \hline
      % {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
      % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\
      $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
      $g_{\rm DECam}$  &      4734     &   3939    &    5528   &   1133        &  $g_{\rm DECam} $    &$  = g_{\rm AB} + 0.083 $ \\	     
       $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
      &&&&&&\\
      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\
      $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
      $r_{\rm LSST}$       &     6139    &	  5375    &    7055   &   1338      &  $r_{\rm LSST}   $       &$    = r_{\rm AB} - 0.155 $ \\	
      $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
      &&&&&&\\
      $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
      $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6
      $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
      &&&&&&\\
      $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
      $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = z_{\rm AB} - 0.513 $     \\
      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = z_{\rm AB} - 0.514 $     \\
      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = z_{\rm AB} - 0.512$     \\
      $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
      &&&&&&\\
      $y_{\rm PS1}$       &       9603    &  9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
      $y_{\rm LSST}$      &       9677   &	 9089    &    10859  &     810         &  $y_{\rm LSST}  $      &$    = y_{\rm AB} - 0.546 $ \\
      $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\
      $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
      &&&&&&\\
      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.921  $         \\
      $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
      &&&&&&\\
      $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
      &&&&&&\\
      $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
      &&&&&&\\
      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K$s$_{AB} - 1.83  $          \\ 
      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800   &   3510     & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
      &&&&&&\\
      WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\
      WISE W2               &    46028    &    39633  &    53414   &  10423    & W2                        &   = W2$_{\rm AB} - 3.339$ \\
      WISE W3               &  115608    &    74430  &  172613   &  55056    & W3                        &   = W3$_{\rm AB} - 5.174$ \\
      WISE W4               &  228172    &  195201  &  279107   &  41017    & W4                        &   = W4$_{\rm AB} - 6.66$ \\
      \hline
      \hline
      \label{tab:filter_details}
    \end{tabular}
     \end{center}
\end{table*}
https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes

\section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}
The PS1 Casjobs SQL Server is located at
\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
The top level documentation is given
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
while the description of tables is given
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}. The
main tables are the
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
objectThin}} and
\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
meanObject}} tables.

\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
Here we give the receipe and SQL that returned the near-infrared photometry 
for the VH$z$Qs.

\begin{enumerate}
\item http://wsa.roe.ac.uk/ 
\item Login
\item {\tt username:	WSERV1000;  password: 	highzqso;   community: 	nonSurvey} 
\item Freeform SQL Query with  WSERV1000v20180327
\end{enumerate}

\input{SQL_examples}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliographystyle{apj}
\bibliographystyle{mn2e}
\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}

\end{document}

### 2018-08-27 tex/older_tex/SMBH_buildup.tex
README.md and tex directory added

The build-up of SMBHs via accretion is important due to the desire to
understand the evolution of the black hole mass function (BHMF) and
since there is a remarkable similarity between cosmic star-formation
rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
BHAR trace each other \citep[with a normalisation factor of
$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
at higher redshift, $z>4$. The physical reasons for this are currently very poorly
understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
stellar mass of the bulge and galaxy total stellar mass,
respectively. The evolution and potential importance of the SFRD and BHAR 
link is a key outstanding problem in contemporary astrophysics, 
potentially explaining the galaxy-black hole scaling relations. 
However, there may also simply be a non-causal origin of the black-hole 
galaxy scaling relations \citep{Jahnke2011}.

\subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
From a study of 69 {\it Herschel}-detected broad-line active galactic
nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
for the $z>6$ measured from the e.g. \mgii line, are generally
correct, then the galaxy total stellar mass for the $z>6$ objects
should be...

\citet{YangG2018} calculate the long-term SMBH accretion rate as a
function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
Our BHAR(M⋆,z) is constrained by high-quality survey data
(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
function and the X-ray luminosity function.  This BHAR/SFR dependence
on $M_{\star}$ does not support the scenario that SMBH and galaxy
growth are in lockstep.

### 2018-08-27 tex/older_tex/WW4C_VHzQ_20180729.tex
README.md and tex directory added

--- 2018-08-27 tex/WW4C_VHzQ.tex
@@
 \title[Very high-$z$ Quasars]
-        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
+        {Near and mid-infrared properties of known $z\geq5$ Quasars}
 \author[Ross \& Cross]
@@
 \begin{abstract}
-In this paper, we, for the first time since the discovery of $z\geq5$
-quasars, assemble all spectroscopically confirmed very high redshift
-quasars in one catalogue.  In particular we present the near
-($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
-all 424 spectroscopically confirmed redshift $z\geq5.00$ quasars.
-Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
-photometric variability in the near-infrared that might be expected
-from Super-Eddington accretion and find {\it blah}.  We present a
-comprehensive series of colour-redshift and colour-colour plots and
-make inferences into the hot dust properties of the very high-redshift
-quasar population. Extrapolating the known quasar luminosity function
-we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
+Very high redshift quasars are excellent probes of physics the early
+Universe.  Understanding how billion solar mass black holes
+formed, evolve and accrete in the first billion years is a key
+outstanding problem in contemporary astrophysics, and one that wil lbe
+directly addressed by upcoming missions such as ESA {\it Euclid} and
+the {\it James Webb Space Telescope}.
+%%
+We can gain a good appreciation for what these missions will discover
+by collating the datasets we currently have, and in this paper, we,
+for the first time since the discovery of $z\geq5.00$ quasars assemble all spectroscopically confirmed very high redshift quasars in
+one catalogue.
+%%
+In particular we present the near ($z/Z, y/Y, J, H, K_{s}$ and $K$)
+infrared and mid-infrared (WISE) properties of all 424
+spectroscopically known redshift $z\geq5$ quasars.  Using archival public
+WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
+in the near-infrared and find blah.  We present a comprehensive series
+of colour-redshift and colour-colour plots and make inferences into
+the hot dust properties of the very high-redshift quasar
+population. Extrapolating the known quasar luminosity function we
+suggest that 80\% of the possibly detected $z\geq5$ quasars in the
 current datasets have been discovered.
@@
 \begin{itemize}
-\item Concentrate on reporting NIR and W1/W2 figures and tables
-\item SED dust plots 
+\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
+\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
 \item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
-\item Check for NIR and MIR variabilty with the Wu quasar
 \item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
-%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
+\item Concentrate on NIR and W1/W2
+\item SED dust plot with just W1/W2...
+\item Check vs. Assef R90/C75 catalog.
 \end{itemize}
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts
+Very high redshift quasars (VH$z$Q; and defined here to have redshifts
 $z\geq5.00$) are excellent probes of the early Universe. This includes
@@
 \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
-one might well expect VH$z$Qs to vary in luminosity as they
-potentially go through phases of Super-Eddington accretion and these
-signatures of photometric variablity should be looked for, especially
+Volonteri2015, Pezzulli2016, Lupi2016} Thus, one might well expect
+VH$z$Qs to vary in luminosity as they potentially go through phases of
+Super-Eddington accretion and these should be looked for, especially
 when the e.g.  near-infrared $K$-band is sampling rest-frame
@@
 
+The build-up of SMBHs via accretion is important due to the desire to
+understand the evolution of the black hole mass function (BHMF) and
+since there is a remarkable similarity between cosmic star-formation
+rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
+BHAR trace each other \citep[with a normalisation factor of
+$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
+$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
+suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
+at higher redshift, $z>4$. The physical reasons for this are currently very poorly
+understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
+have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
+$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
+][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
+in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
+where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
+stellar mass of the bulge and galaxy total stellar mass,
+respectively. The evolution and potential importance of the SFRD and BHAR 
+link is a key outstanding problem in contemporary astrophysics, 
+potentially explaining the galaxy-black hole scaling relations. 
+However, there may also simply be a non-causal origin of the black-hole 
+galaxy scaling relations \citep{Jahnke2011}.
+
 Quasars are also known to be prodigious emitters of infrared emission,
 thought to be from the thermal emission of dust grains heated by
-continuum emission from the accretion disc
-\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
-Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m allow
-discrimination between AGN\footnote{Historically, ``quasars'' and
+continuum emission from the accretion disc \citep[][]{Hill2014,
+Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
+allow discrimination between AGN\footnote{Historically, ``quasars'' and
 ``Active Galactic Nuclei (AGN)'' have described different
@@
 
+We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
+of garnishing a large sample, adequately spanning physical properties 
+(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
+we have gained over the last couple of decades since $z>5$ quasars were 
+discovered.
+
 This paper can be considered an update of \citet{Blain2013} and also
-an extension of parts of \citet{Banados2016}, with the latter study
-reporting WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey
-Telescope and Rapid Response System 1 \citep[Pan-STARRS1,
-PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation
-into the reddest WISE waveband for the VH$z$Qs.  \citet{Banados2016}
-reports and investigates the W1, W2 and W3 properties of quasars at $z
-> 5.6$. We chose redshift $z=5.00$ as our lower redshift limit due to
-a combination of garnishing a large sample, adequately spanning
-physical properties (e.g. luminosity, age of the Universe) and to
-incorporate what knowledge we have gained over the last couple of
-decades since $z>5$ quasars were discovered.
+an extension of parts of \citet{Banados2016}, with the latter study reporting
+WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey Telescope and Rapid Response System 1 
+\citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no  
+further investigation into the reddest WISE waveband for the VH$z$Qs.
+%%
+\citet{Banados2016} reports and investigates the W1, W2 and W3 properties
+of quasars at $z > 5.6$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\section{Data}
+
+\begin{figure*}
 %%trim=l b r t
-%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
-  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
+  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
   {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
   \centering
-  \vspace{-12pt}
   \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.
-    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
-    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
-    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
-    The WISE passbands  W1-4 are also presented.
-    The quasar spectrum is a composite based on \citet{VdB2001} and 
-    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
-  }
+  {The spectral bands used by different survey telescopes and that are relevant here.}
   \label{fig:filters}
-\end{figure}
-
-\vspace{-16pt}
-\section{Data}
-In Table~\ref{tab:THE_TABLE} we present our dataset and 
-we have assembled this in the following manner.  First
+\end{figure*}
+
+We assemble our dataset in a relatively straightforwad manner.  First
 we compile the list of all known, spectroscopically confirmed quasars
@@
 We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset. The optical data comes from the 
+spectral dataset.
+
+The optical data comes from the 
 Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
@@
 
-Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
-on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
-delivering exquisite multi-band photometry data
-\citep[][]{Aihara2018b} the five broad bands $grizy$.
-
-The near-infrared data comes from two primary sources. First, the Wide
-Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
-Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
-the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
-\citep[Visible and Infrared Survey Telescope for
-Astronomy;][]{Emerson2006, Dalton2006}.
-
-We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
-the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
-In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
-
-Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
-of the filters in question.
-
-\input{THE_TABLE_v0pnt96_TOP10_betterformat}
-
-\subsection{Spectroscopy} 
-We have obtained a list of 424 spectroscopically confirmed 
-quasars with redshifts $z\geq5.00$.
-
+The near-infrared data comes from the Wide Field Camera (WFCAM) on 
+the United Kingdom Infra-Red Telescope
+
+\subsection{Very high redshift quasars}
 In Table~\ref{tab:THE_TABLE} we give the discovery reference for the
@@
 Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003}, \citet{Fan2004}, \citet{Mahabal2005},
+\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
 \citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
@@
 
+\input{THE_TABLE_v0pnt96_TOP10_betterformat}
+
 Table~\ref{tab:THE_TABLE} gives the salient details for the objects
@@
 and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$.
+$M_{1450}$
 
@@
 \hline  \hline
-Survey   & \# VH$z$Qs & Notes/Survey reference  \\
+Survey   & \# VH$z$Qs & Notes  \\
 \hline  
-  ATLAS      &     4    &  \citet{Shanks2015} \\
-  CFHQS     &   20    &  \citet{Willott2007} \\
-  DELS        &     2    &  \citet{Dey2018} \\
-  ELAIS       &     1    &  \citet{Vaisanen2000} \\
-  FIRST       &     1    &  \citet{Becker1995} \\
-%  HSC         &     8    &  \\
-  IMS          &     1     &  \citet{Kim2015} \\
-  MMT        &   12    &  \citet{McGreer2013} \\
-  NDWFS    &     1     &  \citet{JD1999} \\
-  PSO          &   84    &   \citet{Kaiser2002, Kaiser2010} \\
-  RD           &     1       &  \cite{Mahabal2005} \\
-  SDSS        & 156       & \citet{EDR} \\
-  SDUV       &   20       & \citet{Yang2017} \\
-  SDWISE    &   27    &     \citet{Wang2016} \\
-  SHELLQs  &  $^{a}$63   &  \citet{Matsuoka2016}\\  %% includes 8 objects from the first HSC paper..
-  ULAS       &   10   & \citet{Lawrence2007} \\
-  VDES       &   11   &  \citet{Reed2017} \\
-  VIK          &     9   &  \citet{Edge2013} \\
-  VIMOS     &     1   &  \citet{LeFevre2003} \\
+  ATLAS      &    4    &  \\
+  CFHQS     &  20    &  \\
+  DELS        &    2    &  \\
+  ELAIS       &    1    &  \\
+  FIRST       &    1    &  \\
+  HSC         &    8    &  \\
+  IMS          &   1     &  \\
+  MMT        &  12    &  \\
+  NDWFS    &  1      &  \\
+  PSO          &    84  & \\
+  RD           &  1       & \\
+  SDSS        & 156       & \\
+  SOUV       & 20       & \\
+  SDWISE    & 27& \\
+  SHELLQs  & 55 & \\
+  ULAS       & 10& \\
+  VDES       & 11& \\
+  VIK          & 9 &\\
+  VIMOS     & 1& \\
 \hline  \hline
 \end{tabular}
-\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference. 
-$^{a}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018}  
-designation.
-}
+\caption{ATLAS \citet{Shanks2015}; }
       \label{tab:surveys}
@@
     sample. Details of our SQL and links to the main tables are given
-    in Appendix~\ref{sec:PS1_SQL}.
-
-    \iffalse
+    in~\ref{sec:PS1_SQL}.
+
     \subsubsection{DECam}
-    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
-    is a wide-field imager with a 2.2 degree diameter field of view 
-    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
-    at the Cerro Tololo International Observatory. We use data 
-    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
-    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
-    \fi
-
-\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
+
+%\newpage
+\subsection{Near-infrared photometry}
 Due to their selection of being very faint/undetected in the
@@
 
+\section{NIR Data}
+
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
@@
 matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
-2018, in prep, and has also been discussed in \citet{Cross2013}.  
-%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS.
+2018, in prep, and has also been discussed in \citet{Cross2013} and \citet{Cross2017}.
 We will give the pertinent points of the MAP and specific details of these data sets below.
 
-    \subsubsection{UKIDSS LAS} 
-    In a bit more detail, use:\\
-    dr10plus\\
-    lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
-    424 results returned. Of which...
-
-    \subsubsection{VISTA VHS} 
-    In a bit more detail, use:\\
-    VH5DR5 \\
-    sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
-    424 results returned.  Of which...
-
-    {\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
+\subsection{Selection of NIR}
 
@@
 
-    \subsubsection{Setup Matched Aperture Product}
+\subsection{Setup Matched Aperture Product}
 
@@
 
-    \subsubsection{Processing MAP data and Forced photometry} 
+\subsection{Processing MAP data}
+
 A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
@@
 
+\subsubsection{Forced photometry}
 CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
@@
 binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
-    VISTA survey products and also familiar to many astronomers through the INTWFS, 
-    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
-    Since forced photometry can be run
+VISTA survey products and also familiar to many astronomers through the INTWFS
+\citep{}, and VST-ATLAS and -VPHAS \citep{}. Since forced photometry can be run
 in many ways on a particular image, a single science frame is not
@@
 \subsubsection{Averaging matched photometry}
+
 Unfortunately the photometry in a single epoch image often has low
@@
 
+\subsubsection{\ldots}
+
 The code to calculate variability statistics as described in \cite{Cross2009} has
@@
 
-\subsection{MIR data}
-The MIR data for this study comes exclusively from the Wide-field
-Infrared Survey Explorer (WISE) mission. Since we are only concerned
-here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
-exploration of the VH$z$Q population in e.g. the large Spitzer areal
-surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
-][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
-\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
-\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
-include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.
-
-We use data from the the beginning of the WISE mission \citep[2010
-January; ][]{Wright2010} through the fourth-year of NEOWISE-R
-operations \citep[2017 December;]{Mainzer2011}. More specifically, we
-use the data from the
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
-program and catalogue, which combines data from the WISE cryogenic and
-NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
-phases. For the our variability investigations, we supplement the
-ALLWISE data with data from the
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
-2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
-(W1 and W2) single-exposure images and extracted source information
-that were acquired between 2016 December 13 and 2017 December 13 UTC,
-which was the fourth year of survey operations of the Near-Earth
-Object Wide-field Infrared Survey Explorer Reactivation Mission
-(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
-data products are concatenated with those from the first three years
-(originally released on March 26, 2015, March 23, 2016 and June 1,
-2017) into a single archive.
-
-The WISE scan pattern leads to coverage of the full- sky approximately
-once every six months (a``sky pass''), but the satellite was placed in
-hibernation in 2011 February and then reactivated in 2013
-October. Hence, our light curves have a cadence of 6 months with a 32
-month sampling gap.
+\subsubsection{UKIDSS LAS} 
+Use:\\
+%lasDetection \\
+dr10plus\\
+lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
+424 results returned. Of which...
+
+\subsubsection{VISTA VHS} 
+Use:\\
+%lasDetection \\
+VH5DR5 \\
+sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
+424 results returned.  Of which...
+
+{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
+
+\iffalse
+\subsection{Filter and Survey choices} 
+We make some choices when reporting our archival photometry. 
+This includes:
+\begin{itemize}
+\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
+\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
+\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
+\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
+\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
+\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
+\item Due to lack of coverage, do not report WFCAM $Z$-band. 
+\end{itemize}
+\fi
+
+%    \begin{equation}
+%      \label{equ:simple_prob}
+%      dP = n \, dV.
+%    \end{equation}
+
+%    \begin{eqnarray}
+%      \xi_{LS}(s) &=& 1 + \left(\frac{N_{rd}}{N} \right)^{2} \frac{DD(s)}{RR(s)} -
+%      2   \left( \frac{N_{rd}}{N} \right) \frac{DR(s)}{RR(s)} \\
+%      &\equiv&  \frac{DD(s)-2DR(s)+RR(s)}{RR(s)},
+%      \label{lseq}
+%    \end{eqnarray}
+
+%% http://www-astro.physics.ox.ac.uk/~kmb/latex_colour.html
+%{\color{red} ...bit of LaTeX text...}
+%an example of making an equation the colour DarkSeaGreen (rather a sophisticated shade, I think) one types the following:
+%\begin{equation}
+%{\color{DarkSeaGreen} x = \log_{10} (\nu/\rm MHz) }
+%\end{equation}
+
+%\subsection{Dust Overview}
+%http://arxiv.org/pdf/1605.06671.pdf
 
@@
 \section{Results}
-Having collated the sample of 424 VH$z$Qs, and obtained their optical,
-near- and mid-infrared photometry we report here the various
-photometric properites of the quasars.
-
-First, we will concentrate on detection rate in the infrared, go on to
-report on the color-redshift and color-color properties of our sample
-and then report on how the current sample populates the
-luminosity-redshift $Lz$-plane.
-
-    %\subsection{Detection Rates in the optical}
-
-    \subsection{Detection Rates in the NIR}
-    Table~\ref{tab:nir_detection} gives the detection rates for the 
-    VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
-    The first thing to note is that the coverage of the NIR surveys 
-    for example from the UKIDSS LAS and VISTA VHS, does
-    not overlap the full area for where the VH$z$Qs are detected.
-
-    \begin{table}
-          \centering
-
-      \begin{tabular}{l r l}
-        \hline  \hline
-        Selection   & number detected (\%) \\
-        \hline  
-        Any band ($YJHK/K_{s}$   &  394  ( ) \\
-        $Y$-band    &    ( ) \\
-        $J$-band    &    ( ) \\
-        $H$-band    &    ( ) \\
-        $K$ or $Ks$-band    &    ( ) \\
-        \hline  \hline
-      \end{tabular}
-      \caption{Detection rate of VH$z$Qs in the near-infrared.}
-      \label{tab:nir_detection}
-    \end{table}
-
-        \subsubsection{Comparing WFCAM and VISTA}
-        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
-        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
-        objects on the same AB system, and for each object compared the two
-        measurements. First, the calculated weighted average (calibrated flux)
-        in each filter of both and calculated the ratio and difference between
-        each measurement and the average.  Then for each filter we calculated
-        the weighted average of the differences (in mag) for each instrument
-        to see if there were significant offsets. The results are given in
-        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
-        offset is the $Y$-band. All of the VISTA averages are negative and all
-        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
-        slightly dodgy, given the different shapes of the filters.
-        \begin{table}
-          \centering
-          \begin{tabular}{l r r}
-            \hline  \hline
-            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
-            -  WFCAM)      &                                        &  objects \\
-            \hline
-            $Z$                 &  19.3 	& 2 \\
-            $Y$                 &  66.2 	& 48 \\
-            $J$                  &    3.2 	& 105 \\
-            $H$                 &  19.3     &  89 \\
-            $K_{\rm s}$/$K$ &  12.7     & 93 \\
-            \hline  \hline
-          \end{tabular}
-          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
-          \label{tab:WFCAM_vs_VISTA}
-        \end{table}
-
-    \subsection{Detection Rates in the MIR}
-    Unlike the NIR coverage, the WISE
-    satellite and mission performed an all-sky survey, so the location of
-    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
-    ALLWISE survey depends heavily on sky location, with locations near
-    the Ecliptic Poles having the highest number of exposures.
-
-    Before reporting on the detection rates, we investigate this
-    effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
-    versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
-    coverage depth, in each corresponding band. In the two shorter bands
-    W1/2 we see the clear and expected trend for brighter objects to have
-    larger SNR, and also for the higher signal to noise for objects with
-    more exposures at a given magnitude. The behaviour for the W3/4 bands
-    is different, with two populations clearly evident in W3 and although
-    a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
-    no obvious R.A./Declination dependence seen, this behaviour is
-    explained by the fact that there are non-detectiopns in W3/4 for
-    objects (with high W1/2 SNR) that are reported in the ALLWISE
-    catalogue.
-
-    For the 278 VH$z$Q with coverage detections, the mean number of
-    exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
-    minimum number of exposures 17 and 12, and the maximum number or
-    exposures being 114 (for both bands).  For the W3/4 filters, the
-    corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
-    5.8 and 6.8 and 69 (for both bands). These values are direclty from
-    the {\tt w$x$cov} enteries in the 
-    \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.
-
-    \begin{figure}
-      %% trim=l b r t
-      \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
-      \centering
-      \vspace{-14pt}
-      \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
-        colour coded by w$x$cov the mean coverage depth, in each corresponding band.
-      }
-      \label{fig:WISEmag_vs_coverage}
-    \end{figure}
-
-    Table~\ref{tab:mir_detection} gives the detection rates for the
-    VH$z$Qs in the MIR WISE W1-4 bands. 
-    \begin{table}
-      \begin{tabular}{l r l}
-        \hline  \hline
-        Selection   & number detected (\%) \\
-        \hline  
-        W1 SNR $> 2.0$   &  275  (64.9) \\
-        W2 SNR $> 2.0$   &   255 (60.1) \\
-        W1 \&\& W2 SNR $> 2.0$  &  \\
-        W3 SNR $> 2.0$   &  99    (23.3) \\
-        W4 SNR $> 2.0$   &  29    (6.8) \\
-        Any W1/2/3/4 SNR $>2.0$ & \\
-        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
-        \hline  \hline
-      \end{tabular}
-      \caption{ATLAS \citet{Shanks2015}; }
-      \label{tab:mir_detection}
-    \end{table}
-
-    \begin{figure}
-      %% trim=l b r t
-      \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
-      \centering
-      \vspace{-14pt}
-      \caption[]{WISE signal-to-noise measures for the four bands, as well
-        as for (W1-W2) colour.  The points are colour coded by redshift.}
-      \label{fig:WISEmag_vs_coverage}
-    \end{figure}
-
-    \citet{Blain2013} Cras in laoreet mauris. Vivamus nec nulla a dui
-    commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet
-    auctor ligula ultricies. Phasellus condimentum gravida
-    tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et
-    augue id purus gravida sagittis quis in sem. Phasellus quis risus
-    bibendum eros luctus auctor.
-
-    Recently, \citet{Assef2018} released two large catalogues of AGN 
-    candidates identified across 30,000 deg$^2$ of extragalactic sky 
-    from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
-    contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
-    AGN candidates per deg$^2$) while the ``C75'' catalog 
-    consists of 20.9M AGN candidates at 75\% completeness (and 
-    ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-    out catalogue of 424 VH$z$Qs with these catalogues, produces 
-    42 matches with	the R90 sample and 98 matches with the C75 sample. 
-    Both catalogues unsurprisingly match to the ultraluminous quasar 
-    SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
-    mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
-    matches J1342+0928 \citep{Banados2018}.
-
-    %\subsubsection{
-    Very High-$z$ Quasars Detected in WISE W3 and W4.
-    Proin non tempus velit. Etiam laoreet, enim nec scelerisque
-    dictum, tortor massa tempor enim, id pretium justo quam ac
-    lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
-    et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
-    eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
-    velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
-    purus.
+ Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam porta sodales est, vel cursus risus porta non.
+Vivamus vel pretium velit.
+Sed fringilla suscipit felis, nec iaculis lacus convallis ac.
+Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Etiam interdum tristique diam eu blandit.
+Donec in lacinia libero.
+
+\subsection{Detection Rates}
+%\begin{table}
+ % \begin{center}
+  %  \setlength{\tabcolsep}{4pt}
+   % \begin{tabular}{lrrr}
+     % \hline       \hline
+    %  Sample Description  & Number in sample & North & South   \\
+     % \hline
+     % \hline \hline
+%      \label{tab:The_Numbers}
+ %   \end{tabular}
+  %  \caption{}
+  %\end{center}
+%\end{table}
 
 \subsection{Variability}
-    VH$z$Qs, if accreting at, or above the Eddington Limit, might well
-    have have large values of changing mass accretion rate, $\ddot{m_{\rm
-        accr}}$. A consequence of this would be that these quasar exhibit signs
-    of variability, most likely showing up in their UV/optical rest-frame
-    spectra.
-
-    We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
-As a guide, \civ  enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57.
-\mgii enters the $H$-band at redshift  $z=4.33$ and exits at $z=5.37$ and enters the $K$-band at redshift  $z=6.25$ and exits at  $7.50$.
-
-    Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we unc semper quam et leo interdum vulputate eu quis magna.
+Sed elit massa, eleifend non sodales a, commodo ut felis.
+Sed id pretium felis.
+Vestibulum et turpis vitae quam aliquam convallis.
+Sed id ligula eu nulla ultrices tempus.
+Phasellus mattis erat quis metus dignissim malesuada.
+Nulla tincidunt quam volutpat nibh facilisis euismod.
+Cras vel auctor neque.
+Nam quis diam risus.
+
+Nunc semper quam et leo interdum vulputate eu quis magna.
 Sed nec arcu at orci egestas convallis.
@@
 
-   Looking at the lighcurves
+\subsection{Very High-$z$ Quasars Detected in WISE}
+\citet{Blain2013} 
+Cras in laoreet mauris.
+Vivamus nec nulla a dui commodo adipiscing.
+Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies.
+Phasellus condimentum gravida tincidunt.
+Phasellus et mauris ac nibh vestibulum vehicula.
+Morbi et augue id purus gravida sagittis quis in sem.
+Phasellus quis risus bibendum eros luctus auctor.
+
+\subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
+Proin non tempus velit.
+Etiam laoreet, enim nec scelerisque dictum, tortor massa tempor enim, id pretium justo quam ac lectus.
+Maecenas diam nibh, interdum at lobortis sit amet, dignissim et quam.
+Sed tincidunt faucibus risus, congue tempus nisl consectetur eget.
+Suspendisse venenatis turpis ut risus aliquam interdum.
+In at velit sed ligula dictum dignissim ut et dui.
+Curabitur ac scelerisque purus.
 
@@
 the blue or red end respectively. Hmmm....}
-   \label{fig:SpecType_vs_NIRcolors}
+   \label{fig:filters}
  \end{figure*}
@@
 }
-   \label{fig:SpecType_vs_W1W2_W2W3colors}
+   \label{fig:filters}
  \end{figure*}
+
+%\subsection{Number Density of High-$z$ Sources}
+
+\subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
+From a study of 69 {\it Herschel}-detected broad-line active galactic
+nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
+- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
+$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
+range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
+for the $z>6$ measured from the e.g. \mgii line, are generally
+correct, then the galaxy total stellar mass for the $z>6$ objects
+should be...
+
+\citet{YangG2018} calculate the long-term SMBH accretion rate as a
+function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
+ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
+Our BHAR(M⋆,z) is constrained by high-quality survey data
+(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
+function and the X-ray luminosity function.  This BHAR/SFR dependence
+on $M_{\star}$ does not support the scenario that SMBH and galaxy
+growth are in lockstep.
 
@@
   {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:Lz}
+  \label{fig:filters}
 \end{figure*}
@@
   {The rest-frame properties of the VH$z$Qs. }
-  \label{fig:RestWavelength_SEDs}
+  \label{fig:filters}
 \end{figure*}
@@
 objects, given their detection rates and SEDs. We find that:
-
-%%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have.
 
@@
 
-This project used data obtained with the Dark Energy Camera (DECam)
-and the NOAO Data Lab, The Data Lab is operated by the National
-Optical Astronomy Observatory, the national center for ground-based
-nighttime astronomy in the United States operated by the Association
-of Universities for Research in Astronomy (AURA) under cooperative
-agreement with the National Science Foundation.
-
 CasJobs was originally developed by the Johns Hopkins University/
@@
 MINECO through grant AyA2014-55216 
-%%
+%\citet{} 
 The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
@@
     (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett2006}.
+    suggested in \citet{Hewett06}.
 
@@
 
-\begin{table*}
+\begin{table*}[h*]
   \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth2011}. 
+   \caption{Adapted from Table 9 of \citet{Peth11}. 
 CTIO/DECam, PanSTARRS/PS1, LSST
@@
 Filter only values. 
-All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 
-%%
-%%
-From \citet{GonzalezFernandez2018} 
-$Z_{\rm AB}   -  Z_{\rm Vega}  = 0.502$;  
-$Y_{\rm AB}  -  Y_{\rm Vega}    = 0.600 $;
-$J_{\rm AB}   -  J_{\rm Vega}    = 0.916  $;
-$H_{\rm AB}  -  H_{\rm Vega}    = 1.366 $;
-$Ks_{\rm AB}  -  Ks_{\rm Vega}  = 1.827 $;
-%%
-and the CASU Vega to AB conversions v1.3:: 
-	Z,Y,J,H,Ks were: 0.524, 0.618, 0.937, 1.384, 1.839. 
-%%
-So, $\Delta$(vs. Gonzalez-Fernandez)::
-	(11.2,     1.1,    5.4,     1.6,    0.1) millimags. 
-$\Delta$(vsCASU v1.3)::
-	(-10.8, -16.9, -15.6,  -16.4, -11.9) millimags. 
 }
@@
       \hline
-      Band & $\lambda_{\rm eff}  $ 
-              &  $\lambda_{\rm min} $ 
-              & $\lambda_{\rm max} $ 
-              & W$_{\rm eff}$
+      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
+              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
+              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
+              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
               & \multicolumn{2}{c}{AB - Vega  Transformations} \\
@@
       % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\
       $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
@@
       $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
-      &&&&&&\\
-      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\
       $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
@@
       $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
-      &&&&&&\\
       $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
       $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
-      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6
       $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
-      &&&&&&\\
       $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
       $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = z_{\rm AB} - 0.513 $     \\
-      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = z_{\rm AB} - 0.514 $     \\
-      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = z_{\rm AB} - 0.512$     \\
       $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
-      &&&&&&\\
       $y_{\rm PS1}$      &       9603    &	 9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
@@
       $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
-      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\
       $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
-      &&&&&&\\
-      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.921  $         \\
+      $Y_{\rm VISTA}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
       $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      &&&&&&\\
+      $J_{\rm VISTA} $     &     10184   &      9427   &    10977   &     905     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.938  $         \\
       $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
-      &&&&&&\\
       $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
-      &&&&&&\\
-      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K$s$_{AB} - 1.83  $          \\ 
+      $H_{\rm VISTA}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
+      $K$s$_{\rm VISTA}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K_{AB} - 1.83  $          \\ 
       $K_{\rm WFCAM}$     &    22010     &    20290 &    23800   &   3510     & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
-      &&&&&&\\
       WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\

### 2018-08-29 tex/WW4C_VHzQ.tex
wDee updates on the .tex

@@
 abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole.
+central black hole. Thus understanding how dust first forms and appears 
+in the central engine remains an open question.
 
@@
 In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{wise2.ipac.caltech.edu/docs/release/allwise/}}.
 
@@
 
-    \citet{Blain2013} Cras in laoreet mauris. Vivamus nec nulla a dui
-    commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet
-    auctor ligula ultricies. Phasellus condimentum gravida
-    tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et
-    augue id purus gravida sagittis quis in sem. Phasellus quis risus
-    bibendum eros luctus auctor.
+    \citet{Blain2013}
 
@@
     Very High-$z$ Quasars Detected in WISE W3 and W4.
-    Proin non tempus velit. Etiam laoreet, enim nec scelerisque
-    dictum, tortor massa tempor enim, id pretium justo quam ac
-    lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
-    et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
-    eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
-    velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
-    purus.
+
+    \begin{figure}
+      \centering
+      \includegraphics[width=8.5cm]
+      {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+      \vspace{-16pt}
+      \caption[]
+      {Histogram showing the number of NEOWISE-R epochs and detections there are for each 
+        VH$z$Q.} 
+      \label{fig:MIR_LC_epochs}
+    \end{figure}
 
 \subsection{Variability}
-    VH$z$Qs, if accreting at, or above the Eddington Limit, might well
-    have have large values of changing mass accretion rate, $\ddot{m_{\rm
-        accr}}$. A consequence of this would be that these quasar exhibit signs
-    of variability, most likely showing up in their UV/optical rest-frame
-    spectra.
-
+VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m_{\rm accr}}$.
+A consequence of this would be that these quasar exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra.
 We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
@@
 
-    Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we unc semper quam et leo interdum vulputate eu quis magna.
-Sed nec arcu at orci egestas convallis.
-Aenean quam velit, aliquam vitae viverra in, elementum vel elit.
-Nunc suscipit aliquet sapien a suscipit.
-Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla.
-Nullam eu augue id purus mollis dignissim sed et libero.
-Phasellus eget justo sed neque pellentesque egestas nec id arcu.
-Donec facilisis pulvinar sapien et fringilla.
-Suspendisse vestibulum rhoncus sapien id laoreet.
-Morbi et orci vitae tortor imperdiet imperdiet.
-In hac habitasse platea dictumst.
-Vivamus vel neque id mi ultrices tristique.
-Integer quam libero, ornare vel gravida in, feugiat a ante.
-Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi.
-Vestibulum nec mi justo, eget dapibus velit.
-
-   Looking at the lighcurves
+Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we
+
+\begin{figure}
+  \includegraphics[width=8.5cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
+  \centering
+  \caption[]
+  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
+    Red points are the W1 band; cyan points the W2 band.} 
+  \label{fig::MIR_LC_3egs}
+\end{figure}
+
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lighcurves and associated colour changes. Here we show 
+J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
 
 \subsection{Colours}
+Currently, very high-redshift quasars are identified by their morphology, flux and colours in 
+optical and infrared imaging data \citet{Fan1999, Mortlock2012}
+Quasars are generally selected to be point sources, but 
+be outliers from the stellar locus in colour space. For VH$z$Qs, the main technique is to 
+look for objects with extreme optical-to-near-infrared colours
+The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
+
 Pellentesque vel elit neque, in interdum lacus.
@@
 
+\subsection*{Author Contributions}   
+N.P.R.
+initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
+
+N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
+
+\subsection*{Availability of Data and computer analysis codes} 
+All materials, data, code and analysis algorithms are fully 
+available at: 
+\href{https://github.com/d80b2t/VHzQ}{\tt https://github.com/d80b2t/VHzQ}
+
 \section*{Acknowledgements}
@@
 
-We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
+We thank Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA), and 
+also the VISTA Science Archive (VSA). We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
 
@@
 \citep[][]{Taylor2005, Taylor2011}.
-
+%%
 This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
@@
 
-CasJobs was originally developed by the Johns Hopkins University/
-Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
-used version 3.5.16 to construct CasJobs-based tools for GALEX,
-Kepler, the Hubble Source Catalog, and PanSTARRS.
-
 This publication makes use of data products from the Wide-field
@@
 and Space Administration.
+
+CasJobs was originally developed by the Johns Hopkins University/
+Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
+used version 3.5.16 to construct CasJobs-based tools for GALEX,
+Kepler, the Hubble Source Catalog, and PanSTARRS.
 
@@
 
+\onecolumn
+\begin{lstlisting}[
+language=SQL,
+           showspaces=false,
+           basicstyle=\ttfamily,
+           numbers=left,
+           numberstyle=\tiny,
+           commentstyle=\color{gray}
+        ]
+SELECT s.ra, s.decl, 
+       o.objID, o.raMean, o.decMean, 
+       o.nDetections, o.ng, o.nr, o.ni, o.nz, o.ny, 
+       m.gMeanPSFMag, m.gMeanPSFMagErr,  m.gMeanPSFMagStd, 
+       m.rMeanPSFMag, m.rMeanPSFMagErr,  m.rMeanPSFMagStd, 
+       m.iMeanPSFMag, m.iMeanPSFMagErr,  m.iMeanPSFMagStd, 
+       m.zMeanPSFMag, m.zMeanPSFMagErr,  m.zMeanPSFMagStd, 
+       m.yMeanPSFMag, m.yMeanPSFMagErr,  m.yMeanPSFMagStd, 
+       s.jmag, s.jmag_error, s.hmag, s.hmag_error, s.kmag, s.kmag_error into mydb.MyTable_0 from MyDB.Ldwarfs as s
+
+cross apply fGetNearbyObjEq(s.ra,s.decl,2.0/60.0) nb
+inner join ObjectThin o on o.objid=nb.objid and o.nDetections>1 
+inner join MeanObject m on o.objid=m.objid  and o.uniquePspsOBid=m.uniquePspsOBid
+\end{lstlisting}
+\twocolumn
+
 \section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
@@
 
+\onecolumn
 \input{SQL_examples}
+\twocolumn
 

### 2018-09-03 tex/WW4C_VHzQ.tex
Update WW4C_VHzQ.tex
Some updates to text. Minor corrections, queries ([NJC: ...]) and modifying the NIR data section. More to come

@@
 $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-reporting homogenous near-infrared photometry for the quasars; {\it
+analysing all the WFCAM and VISTA [NJC: homogeneous isn't the write term. The NIR data is very heterogeneous] near-infrared photometry for the quasars; {\it
 (iii)} making the first study of NIR variability of the VHzQ
@@
 an extension of parts of \citet{Banados2016}, with the latter study
-reporting WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey
+reporting WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey
 Telescope and Rapid Response System 1 \citep[Pan-STARRS1,
@@
 This paper is organized as follows.  In Section 2, we present the
-assembled list of the 424 $z\leq5.00$ VH$z$Qs that we have
+assembled list of the 424 $z\geq5.00$ VH$z$Qs that we have
 compiled. We then give a high-level overview of the photometric
 surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we In Section 4 we and we then note our Conclusions in
+\textbf{In Section 3 we } In Section 4 we and we then note our Conclusions in
 Section 5.
 
-We make the somewhat unconventional decision to present all our
+We make the somewhat unconventional decision [NJC: Is this unconventional?] to present all our
 photometry and magnitudes on the AB zero-point system
@@
 as well as the mid-infrared magnitudes.  Because of established
-conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point
+conventions, we report SDSS [NJC: PanSTARRS/DES rather than SDSS?] $ugriz$ magnitudes on the AB zero-point
 system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
@@
 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
-Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about
+Brown2014b}. WFCAM and VISTA \citep{Hodgkin2009;GonzalezFernandez2018} are also calibrated on a Vega system (WFCAM), or near Vega system (VISTA). \citet{Brown2014b}, in PASA, is the paper about
 Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
@@
     The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
+    [NJC: Do we use the W-band anywhere?]
     The WISE passbands  W1-4 are also presented.
@@
 
-We query the WFCAM Science Archive
-\citep[\href{http://wsa.roe.ac.uk/}{WSA}; ][]{Hambly2008} which
-reports NIR photometry from the Wide Field Camera \citep[WFCAM;
-][]{Casali2007} on the United Kingdom Infrared Telescope (UKIRT).
-Data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
-\citep[Visible and Infrared Survey Telescope for Astronomy;
-][]{Emerson2006, Dalton2006} is also given in the WSA.
-
-Quasars are known to vary (both photometrically and spectroscopically)
-and very high-$z$ quasars under going super-Eddington accretion during
-a rapid BH growth phase are prime candidates for this variation.
-Therefore, with repeat observations over many epochs availble via the
-WSA, we have a choice to make for how we report the photometry. After
-tests, we decide to give the NIR photometry averaged on 4 week
-observed timescales. This time bracket is chosen as a good compromise
-between maximising signal-to-noise while keeping the cadence high. At
-our observed redshifts, we sample $\lesssim1$week in the rest-frame
-and luminous quasars are not expected to vary on timescales quicker
-than this \citep[e.g., ][]{Lawrence2016_ASPC}.
-
-We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
-
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
@@
 science verification (200910..) to 1st April 2016, to get as much coverage as
-possible. Hence, the NIR is extremely heterogeneous.
+possible. Hence, the NIR coverage is extremely heterogeneous.
 
@@
 2018, in prep, and has also been discussed in \citet{Cross2013}.  
-%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS.
+%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS. [NJC: this was a conference proceeding
+%% from ADASS2016. They just contacted me about the copyright. They are so slow even though we 
+%% had to submit our proceedings before the conference. I had assumed it was already published.]
 We will give the pertinent points of the MAP and specific details of these data sets below.
 
-    \subsubsection{UKIDSS LAS} 
-    In a bit more detail, use:\\
-    dr10plus\\
-    lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
-    424 results returned. Of which...
-
-    \subsubsection{VISTA VHS} 
-    In a bit more detail, use:\\
-    VH5DR5 \\
-    sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
-    424 results returned.  Of which...
-
-    {\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
-
 The first step of the process was to ingest the catalogue of VHzQs into
-    the WSA/VSA. These data are in the table \verb+finalQsoCatalogue+. Next we set
+the WSA/VSA. These data are stored in the table \verb+finalQsoCatalogue+. Next we set
 up new programmes WSERV1000, VSERV1000 in the WSA and VSA respectively. We
-    assign all frames that contain the high-z QSO based on WCS information in the
+assign all frames that potentially contain the high-z QSO based on WCS information in the
 WSA to WSERV1000, but adding a new line to the table \verb+ProgrammeFrame+ and
@@
     detector extensions to image multiframes.
+
+    Quasars are known to vary (both photometrically and spectroscopically)
+and very high-$z$ quasars under going super-Eddington accretion during
+a rapid BH growth phase are prime candidates for this variation.
+Therefore, with repeat observations over many epochs available via the
+WSA, we have a choice to make for how we report the photometry. After
+tests, we decide to give the NIR photometry averaged on 4 week
+observed timescales. This time bracket is chosen as a good compromise
+between maximising signal-to-noise while keeping the cadence high. At
+our observed redshifts, we sample $\lesssim1$week in the rest-frame
+and luminous quasars are not expected to vary on timescales quicker
+than this \citep[e.g., ][]{Lawrence2016_ASPC}.
+
+We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
 

### 2018-09-07 tex/WW4C_VHzQ.tex
Update WW4C_VHzQ.tex
Updated discussion about processing of aperture photometry and averaging

@@
           \hline \hline
-          \label{tab:The_Numbers}
+          \label{tab:reqMapAvg}
         \end{tabular}
@@
     \subsubsection{Processing MAP data and Forced photometry} 
-    A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
-    the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
+    A set of apertures to do forced photometry with were created in 
+    \verb+MapApertureIDshighzQsoMap+, based on the \verb+RequiredMatchedApertureProduct+ 
+    {\it selection} value, which in this case is to use the known positions of $z>5$ QSOs. This may
     seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
-    but the layer is a general abstraction that allows multiple sources of
-    catalogue, and multiple types\ldots
-    Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent
+    but the layer is a general abstraction that allows multiple selections of data, including complex queries
+    or input images.
 
@@
     centre. In this case, where there are 424 QSOs spread across the sky, there is
-    typically 1 object per multiframe, but many have two and one,
-    multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
+    typically 1 object per multiframe, but many have two and one frame,
+    multiframeID=2614475 in the VSA (a J-band stack from a P90 PI programme), has 3 objects. 
+    The output of \verb+imcore_list+
     is a multi-extension FITS binary table, with identical columns to the CASU FITS
-    binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
-    VISTA survey products and also familiar to many astronomers through the INTWFS, 
-    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
-    Since forced photometry can be run
-    in many ways on a particular image, a single science frame is not
+    binary tables produced using the CASU \verb+imcore+\footnote{http://casu.ast.cam.ac.uk/surveys-projects/vista/technical/catalogue-generation}, the basis of all WFCAM and
+    VISTA survey catalogue products and also familiar to many astronomers through the INTWFS, 
+    VST-ATLAS and VPHAS. Since forced photometry can be run
+    in many ways on a particular image depending on the input catalogue, a single science frame is not
     necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
-    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
-    information on what processing stage they are at ({\bf bitProcessingFlag}),
-    whether they have been ingested ({\bf isIngested}), or what quality control has
-    been run on them ({\bf ppErrBitsStatus}).
-
+    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}).
     For matched aperture measurements, we process these binary tables using the same
@@
 a rapid BH growth phase are prime candidates for this variation.
+[NJC: This is better placed somewhere else.
+We first used it to justify averaging over ~4 weeks, but then decided to average over many periods and select later.]
 Therefore, with repeat observations over many epochs available via the
-WSA, we have a choice to make for how we report the photometry. After
-tests, we decide to give the NIR photometry averaged on 4 week
-observed timescales. This time bracket is chosen as a good compromise
-between maximising signal-to-noise while keeping the cadence high. At
-our observed redshifts, we sample $\lesssim1$week in the rest-frame
-and luminous quasars are not expected to vary on timescales quicker
-than this \citep[e.g., ][]{Lawrence2016_ASPC}.
-
-We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
+WSA, we have a choice to make for how we report the photometry. The remeasured photometry is averaged to
+improve signal-to-noise over all the averaging schemes setup in Table~\ref{tab:reqMapAvg}. This allows us to get the best combination of signal-to-noise and number of epochs for different QSOs.
 
@@
     the images in some cases are taken from multiple projects with different
-    pointings. In addition, corrections such as scattered light, pixel distortion
+    pointings, and orientations and exposures, so stacking may not be optimal. 
+    In addition, corrections such as scattered light, pixel distortion
     and aperture corrections will be more complex, if not impossible to apply to
@@
     on the requirements in \verb+RequiredMapAverages+, in these cases over time
-    spans of 7, 14, 28, 183 days, over 10 epochs and finally over all epochs. The
+    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and over all epochs,
+    see Tab.~\ref{tab:reqMapAvg}. The
     averaging process starts at the first epoch and works on. Possible future
     refinements could first look for denser groupings that satisfied the criteria so
-    that these were not split into two groups.
+    that these were not split into two groups. For this high-z QSO project we have averaged over overlaps, 
+    because in several cases data for one source comes from multiple original projects that have slightly 
+    different pointings.
 
@@
 
+We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
+
     The code to calculate variability statistics as described in \cite{Cross2009} has
     not yet been completed to run with the matched aperture pipeline, so these are
-    not included.
+    not included. Variables were selected ...
 

### 2018-09-09 tex/WW4C_VHzQ.tex
Update WW4C_VHzQ.tex
Small subsection on selection of variable sources in NIR data. 
A subsection will be added to the results later.

--- 2018-09-03 tex/WW4C_VHzQ.tex
@@
     not included.
+
+\subsubsection{Selection of NIR variables}
+
+To select potentially variable QSOs we first did a selection like Appendix D(??), selecting the photometry averaged over the whole time span to assess the overall signal-to-noise, total timespan and number of measurements.
+For each QSO in each filter measured by each instrument, our initial selection for potential variables was $N_{\rm meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at least five measurements.
+An estimate was made of the number of useful epochs, such that $N_{\rm epc}=\min(N_{\rm meas},\frac{SNR}{sqrt{3.}}$.
+This in turn was used to estimate a typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm tot}}{N_{\rm meas}}$.
+
+We select average photometry where $(T_{\rm avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$, a setup that should give the best combination of more epochs to resolve the variation and signal-to-noise per epoch.
+For each setup which satisfies this criteria, we get the averaged photometry and check the statistics.
+We calculate the median, and the median-absolute-deviation (MAD), and calculate the ratio of the standard deviation to the typical error, $r=\frac{1.48MAD}{ {\overline{error}/sqrt(N_{\rm epochs}}$.
+Likely variables have $rat\geq3.$ and $N_{\rm epoch}\geq4$.
+Using this selection, we found two potential variables, xx and yy, both of which show variability in VISTA, with timescales of xn and ym, respectively.
+[Put in results]
+
+As stated before, 114 QSOs have both WFCAM and VISTA data, and so some variables with fewer measurements in each, may also be variables.
+We took all of the intially selected variables that had both WFCAM and VISTA data, and looked for potential timescales in either WFCAM or VISTA, and if there was at least one good timescale, appropriate timescales were applied to both WFCAM and VISTA photometry: i.e.
+if a timescale of 30 days was found for WFCAM and 90 days for VISTA then the combined light curve would be averaged over 30 days for WFCAM and 90 days for VISTA; if only a 90 day average timescale for VISTA was found, then both WFCAM and VISTA would be averaged by 90 days, and if multiple averaging timescales were found, all suitable combinations would be tested.
+The same analysis of median and MAD was applied to the combined light-curves to find any additional potential variables.
+2 more potential variables were found.
 

### 2018-09-13 tex/WW4C_VHzQ.tex

--- 2018-09-03 tex/WW4C_VHzQ.tex
@@
 non-proprietary VISTA data, which covers all public surveys and PI projects from
-science verification (200910..) to 1st April 2016, to get as much coverage as
+science verification (20091015) to 1st April 2016, to get as much coverage as
 possible. Hence, the NIR coverage is extremely heterogeneous.
@@
 
-    Add a new entry \verb+RequiredMatchedApertureProduct+
-
+To create matched aperture products it is first necessary to define the product. We do this in two requirements tables, \verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+ that
+tell the \textbf{ProgrammeBuilder} software which tables to create and what type of product is being created. These requirements tables also drive the pipeline.
+
+\verb+RequiredMatchedApertureProduct+ contains the following attributes for the High-z QSO MAP product.
 \begin{itemize}
-    \item mapID	archiveName	programmeID	extractor	mapType	name	description	selection	finalProductTable	addSurveyList
-    \item 1	1	WSA	10999	CASU	2	highzQsoMap	Variability via matched apertures for set of high-z QSOs	SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue	highzQsoMapVariability	NONE
+    \item mapID, Identifier of the MAP product, value=1	
+    \item archiveName, Main archive of product, value='VSA'/'WSA' 	
+    \item programmeID, UID of programme, in this case a combined programme, value=10999
+    \item extractor, Extractor used for forced photometry, value='CASU' (imcore_list)
+    \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
+    \item name, Name of MAP product, value='highzQsoMap'
+    \item description, Description of MAP product, 'Variability via matched apertures for set of high-z QSOs'	
+    \item selection, Selection, e.g. File, pseudo-SQL, FITS image that is used to give input list, value='SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue'	
+    \item finalProductTable, Name of final product table, value='highzQsoMapVariability'
+    \item addSurveyList, List of additional archive/surveys that data comes from, value='NONE'
 \end{itemize}
 
-    Explain
-
-    Entries in \verb+RequiredMapAverages+
+\verb+RequiredMatchedApertureProduct+ gives all of the information such as the {\it programmeID} (identifying which data), the {\it mapType} (type of processing), the {\it extractor} to use, the input list {\it selection}, which in this case is the IDs and positions of the QSOs in \verb+finalQsoCatalogue+ which contains all the literature data and pre-derived parameters for the 424 QSOs.
+
+\verb+RequiredMapAverages+ is used to setup the averaging of the MAP photometry from several images.
+We can average the epochs in multiple ways: over all the input images to a deep image, or similarly the input pawprint images to tile image in VISTA.
+Alternatively we can average over a fixed number of epochs or a fixed duration in time.
+Multiple setups can be defined in \verb+RequiredMapAverages+, and the different averages selected using the defined {\it setupID}.
 
@@
         \setlength{\tabcolsep}{4pt}
-        \begin{tabular}{lll lll lll l}
+        \begin{tabular}{ll lll lll l}
           \hline \hline
-          &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
+   programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
           \hline
-          1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
-          2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
-          3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
-          4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
-          5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
-          6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
+10999	& 1 & 0 & Average over whole time & 0 &	NONE &	-1.000000 &	-99999999 &	1 \\
+10999	& 1 & 1 & Average over a week &	0 & NONE & +7.000000 &	-99999999 &	1\\
+10999	& 1 & 2	& Average over a fortnight & 0 & NONE &	+14.000000 & -99999999 & 1\\
+10999	& 1 & 3	& Average over a month & 0 & NONE & +30.000000 & -99999999 & 1\\
+10999	& 1 & 4	& Average over 10 epochs & 0 & NONE & -9.999995E008 & 10 & 1\\
+10999	& 1 & 5 & Average over 6 months	& 0 & NONE & +183.000000 & -99999999 & 1 \\
+10999	& 1 & 6	& Average over 1 year &	0 & NONE & +365.000000 & -99999999 & 1 \\
+10999	& 1 & 7	& Average over 2 years & 0 & NONE & +730.000000	& -99999999 & 1 \\
+10999	& 1 & 8 & Average over 3 months & 0 & NONE & +91.000000	& -99999999 & 1 \\
           \hline \hline

### 2018-09-13 tex/WW4C_VHzQ.tex

@@
     not included. Variables were selected ...
+
+\subsubsection{Selection of NIR variables}
+
+To select potentially variable QSOs we first did a selection like Appendix D(??), selecting the photometry averaged over the whole time span to assess the overall signal-to-noise, total timespan and number of measurements.
+For each QSO in each filter measured by each instrument, our initial selection for potential variables was $N_{\rm meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at least five measurements.
+An estimate was made of the number of useful epochs, such that $N_{\rm epc}=\min(N_{\rm meas},\frac{SNR}{sqrt{3.}}$.
+This in turn was used to estimate a typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm tot}}{N_{\rm meas}}$.
+
+We select average photometry where $(T_{\rm avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$, a setup that should give the best combination of more epochs to resolve the variation and signal-to-noise per epoch.
+For each setup which satisfies this criteria, we get the averaged photometry and check the statistics.
+We calculate the median, and the median-absolute-deviation (MAD), and calculate the ratio of the standard deviation to the typical error, $r=\frac{1.48MAD}{ {\overline{error}/sqrt(N_{\rm epochs}}$.
+Likely variables have $rat\geq3.$ and $N_{\rm epoch}\geq4$.
+Using this selection, we found two potential variables, xx and yy, both of which show variability in VISTA, with timescales of xn and ym, respectively.
+[Put in results]
+
+As stated before, 114 QSOs have both WFCAM and VISTA data, and so some variables with fewer measurements in each, may also be variables.
+We took all of the intially selected variables that had both WFCAM and VISTA data, and looked for potential timescales in either WFCAM or VISTA, and if there was at least one good timescale, appropriate timescales were applied to both WFCAM and VISTA photometry: i.e.
+if a timescale of 30 days was found for WFCAM and 90 days for VISTA then the combined light curve would be averaged over 30 days for WFCAM and 90 days for VISTA; if only a 90 day average timescale for VISTA was found, then both WFCAM and VISTA would be averaged by 90 days, and if multiple averaging timescales were found, all suitable combinations would be tested.
+The same analysis of median and MAD was applied to the combined light-curves to find any additional potential variables.
+2 more potential variables were found.
 

### 2018-09-25 tex/older_tex/WW4C_VHzQ_20180913.tex
mainly MIR_LC updates

--- 2018-09-13 tex/WW4C_VHzQ.tex
@@
 \subsubsection{Setup Matched Aperture Product}
-
-To create matched aperture products it is first necessary to define the product. We do this in two requirements tables, \verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+ that
-tell the \textbf{ProgrammeBuilder} software which tables to create and what type of product is being created. These requirements tables also drive the pipeline.
+To create matched aperture products it is first necessary to define
+the product. We do this in two requirements tables,
+\verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+
+that tell the \textbf{ProgrammeBuilder} software which tables to
+create and what type of product is being created. These requirements
+tables also drive the pipeline.
 
@@
     \item programmeID, UID of programme, in this case a combined programme, value=10999
-    \item extractor, Extractor used for forced photometry, value='CASU' (imcore_list)
+    \item extractor, Extractor used for forced photometry, value='CASU' (imcore\_list)
     \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
@@
 \subsubsection{Selection of NIR variables}
-
-To select potentially variable QSOs we first did a selection like Appendix D(??), selecting the photometry averaged over the whole time span to assess the overall signal-to-noise, total timespan and number of measurements.
-For each QSO in each filter measured by each instrument, our initial selection for potential variables was $N_{\rm meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at least five measurements.
-An estimate was made of the number of useful epochs, such that $N_{\rm epc}=\min(N_{\rm meas},\frac{SNR}{sqrt{3.}}$.
-This in turn was used to estimate a typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm tot}}{N_{\rm meas}}$.
-
-We select average photometry where $(T_{\rm avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$, a setup that should give the best combination of more epochs to resolve the variation and signal-to-noise per epoch.
-For each setup which satisfies this criteria, we get the averaged photometry and check the statistics.
-We calculate the median, and the median-absolute-deviation (MAD), and calculate the ratio of the standard deviation to the typical error, $r=\frac{1.48MAD}{ {\overline{error}/sqrt(N_{\rm epochs}}$.
-Likely variables have $rat\geq3.$ and $N_{\rm epoch}\geq4$.
-Using this selection, we found two potential variables, xx and yy, both of which show variability in VISTA, with timescales of xn and ym, respectively.
-[Put in results]
-
-As stated before, 114 QSOs have both WFCAM and VISTA data, and so some variables with fewer measurements in each, may also be variables.
-We took all of the intially selected variables that had both WFCAM and VISTA data, and looked for potential timescales in either WFCAM or VISTA, and if there was at least one good timescale, appropriate timescales were applied to both WFCAM and VISTA photometry: i.e.
-if a timescale of 30 days was found for WFCAM and 90 days for VISTA then the combined light curve would be averaged over 30 days for WFCAM and 90 days for VISTA; if only a 90 day average timescale for VISTA was found, then both WFCAM and VISTA would be averaged by 90 days, and if multiple averaging timescales were found, all suitable combinations would be tested.
-The same analysis of median and MAD was applied to the combined light-curves to find any additional potential variables.
-2 more potential variables were found.
+To select potentially variable QSOs we first did a selection like
+Appendix D(??), selecting the photometry averaged over the whole time
+span to assess the overall signal-to-noise, total timespan and number
+of measurements. For each QSO in each filter measured by each
+instrument, our initial selection for potential variables was $N_{\rm
+meas}\geq8$, $T_{\rm tot}=\max{mjd}-\min{mjd}>30.$ days, $F>0.$ Jky
+and SNR>8, to give a signal-to-noise of $\sim\geq3$ per epoch and at
+least five measurements. An estimate was made of the number of useful
+epochs, such that $N_{\rm epc}=\min(N_{\rm
+meas},\frac{SNR}{sqrt{3.}}$. This in turn was used to estimate a
+typical time-scale for averaging, $T_{\rm avg}=\frac{T_{\rm
+tot}}{N_{\rm meas}}$.
+
+We select average photometry where $(T_{\rm
+avg}/2.)\leq\verb+RequiredMapAverages.timeScale+\leq(2.*T_{\rm avg})$,
+a setup that should give the best combination of more epochs to
+resolve the variation and signal-to-noise per epoch. For each setup
+which satisfies this criteria, we get the averaged photometry and
+check the statistics. We calculate the median, and the
+median-absolute-deviation (MAD), and calculate the ratio of the
+standard deviation to the typical error, 
+$r=\frac{1.48MAD} {{\overline{error}/\sqrt(N_{\rm epochs})}}$. Likely variables have
+$rat\geq3.$ and $N_{\rm epoch}\geq4$. Using this selection, we found
+two potential variables, xx and yy, both of which show variability in
+VISTA, with timescales of xn and ym, respectively. [Put in results]
+
+As stated before, 114 QSOs have both WFCAM and VISTA data, and so some
+variables with fewer measurements in each, may also be variables. We
+took all of the intially selected variables that had both WFCAM and
+VISTA data, and looked for potential timescales in either WFCAM or
+VISTA, and if there was at least one good timescale, appropriate
+timescales were applied to both WFCAM and VISTA photometry: i.e. if a
+timescale of 30 days was found for WFCAM and 90 days for VISTA then
+the combined light curve would be averaged over 30 days for WFCAM and
+90 days for VISTA; if only a 90 day average timescale for VISTA was
+found, then both WFCAM and VISTA would be averaged by 90 days, and if
+multiple averaging timescales were found, all suitable combinations
+would be tested. The same analysis of median and MAD was applied to
+the combined light-curves to find any additional potential
+variables. 2 more potential variables were found.
 

### 2018-09-25 MIR_LCs/NEOWISER_LCs_2cols.py

@@ -38,8 +38,8 @@ alpha    = 1.00
 plot_num = 321
 totes    = 0
 
-#for x in range(upto_this):
-for x in range(10):
+for x in range(upto_this):
+#for x in range(10):
     x=x+1
     data_one = data[np.where(data['cntr_01'] == x)]
 
@@ -54,10 +54,9 @@ for x in range(10):
         dec = data_one['dec'][0]
 
         ## Setting up a 3 panel, "triptych" style plot
-        fig, (ax1, ax2, ax3) = plt.subplots(1,3, figsize=(21.5, 8.5), gridspec_kw = {'width_ratios':[3, 1, 1]}) # inches
+        fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(21.5, 8.5), gridspec_kw = {'width_ratios':[2, 1]}) # inches
         #ax1 = plt.subplot(131, figsize=(12.0, 8.5) )
         #ax2 = plt.subplot(132, figsize=(5.0, 8.5))
-        #ax3 = plt.subplot(133, figsize=(5.0, 8.5), sharey=ax2)
 
         left   = 0.06   # the left side of the subplots of the figure
         right  = 0.98   # the right side of the subplots of the figure
@@ -66,7 +65,6 @@ for x in range(10):
         wspace = 0.26   # the amount of width reserved for blank space between subplots
         hspace = 0.06   # the amount of height reserved for white space between subplots
         plt.subplots_adjust(left=left, bottom=bottom, right=right, top=top, wspace=wspace, hspace=hspace)
-
 
         ## W1/2 Light-curves, y-axis reverse
         ##
@@ -93,25 +91,20 @@ for x in range(10):
         ax1.tick_params('y', direction='in', which='both', bottom='True', top='True', left='True', right='True', labelsize=fontsize)
 
         ## W1 vs. color to look for color-changes...
-        ax2.scatter(data_one['w1mpro'], (data_one['w1mpro']-data_one['w2mpro']),color='k', alpha=alpha, s=ms*1.8)
-        ax2.scatter(data_one['w1mpro'], (data_one['w1mpro']-data_one['w2mpro']),color='r', alpha=alpha, s=ms)
-        ax2.set_xlabel('W1 magnitude',                   fontsize=fontsize)
+        #ax2.scatter(data_one['w1mpro'], (data_one['w1mpro']-data_one['w2mpro']),color='k', alpha=alpha, s=ms*1.8)
[…]

### 2018-09-25 MIR_LCs/NEOWISER_LCs_2rows.py

@@ -1,0 +1,140 @@
+'''
+http://blog.marmakoide.org/?p=94
+'''
+
+from astropy.io import ascii
+from matplotlib import pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+
+import numpy as np
+import random
+
+path='/cos_pc19a_npr/data/highest_z_QSOs/'
+file = 'NEOWISER-R_SingleExposure_L1bs.tbl'
+
+data = ascii.read(path+file) 
+type(data)
+upto_this = data['cntr_01'].max()
+
+out_pdf = 'NEOWISER_LCs_VHzQs_temp.pdf'
+pdf_pages = PdfPages(out_pdf)
+
+
+ALLWISE_MJD_min = 55210.     #  2010-January-14 
+ALLWISE_MJD_max = 55593.
+ALLWISE_MJD_mid = ((ALLWISE_MJD_max + ALLWISE_MJD_min))/2.
+mjd_range_ALLWISE=[ALLWISE_MJD_min,ALLWISE_MJD_max]
+
+
+## define the colormap
+cmap = plt.cm.inferno_r
+
+ls       = 'solid'
+lw       = 2.0
+s        = 60.
+s_large  = s*5.
+ms       = 6.0
+fontsize = 24
+alpha    = 1.00
+plot_num = 321
+totes    = 0
+
+#for x in range(upto_this):
+for x in range(10):
+    x=x+1
+    data_one = data[np.where(data['cntr_01'] == x)]
+
+    if len(data_one) < 1:
+          print('0')
+          
+    if len(data_one) > 0:  
+#        print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
+        print(len(data_one))
+        totes = totes + len(data_one)
+        ra = data_one['ra'][0]
+        dec = data_one['dec'][0]
+
+        ## Setting up a 3 panel, "triptych" style plot
+        fig, (ax1, ax2) = plt.subplots(2, 1, figsize=(14.0, 8.5),sharex=True, gridspec_kw = {'height_ratios':[5, 3]}) # inches
+        #ax1 = plt.subplot(131, figsize=(12.0, 8.5) )
+        #ax2 = plt.subplot(132, figsize=(5.0, 8.5))
+
+        left   = 0.10   # the left side of the subplots of the figure
+        right  = 0.98   # the right side of the subplots of the figure
+        bottom = 0.10   # the bottom of the subplots of the figure
[…]

### 2018-09-25 MIR_LCs/older_py/NEOWISER_LCs_v1pnt0.py

@@ -3,10 +3,15 @@ http://blog.marmakoide.org/?p=94
 '''
 
 from astropy.io import ascii
+
+import numpy as np
+
+#import matplotlib.backends.backend_pdf
+#import matplotlib.pyplot as plt
+
 from matplotlib import pyplot as plt
 from matplotlib.backends.backend_pdf import PdfPages
 
-import numpy as np
 import random
 
 path='/cos_pc19a_npr/data/highest_z_QSOs/'
@@ -16,30 +21,31 @@ data = ascii.read(path+file)
 type(data)
 upto_this = data['cntr_01'].max()
 
+##pdf_pages = PdfPages('my-fancy-document.pdf')
 out_pdf = 'NEOWISER_LCs_VHzQs_temp.pdf'
+#pdfs = matplotlib.backends.backend_pdf.PdfPages(out_pdf)
 pdf_pages = PdfPages(out_pdf)
 
+#cnt = 0
+#figs = plt.figure()
 
-ALLWISE_MJD_min = 55210.     #  2010-January-14 
-ALLWISE_MJD_max = 55593.
-ALLWISE_MJD_mid = ((ALLWISE_MJD_max + ALLWISE_MJD_min))/2.
-mjd_range_ALLWISE=[ALLWISE_MJD_min,ALLWISE_MJD_max]
+#fig = plt.figure(figsize=(10, 10)) # inches
+plot_num = 321
+totes = 0
 
 
 ## define the colormap
 cmap = plt.cm.inferno_r
 
-ls       = 'solid'
-lw       = 2.0
-ms       = 60.
-ms_large = ms*5.
-fontsize = 24
-alpha    = 1.00
-plot_num = 321
-totes    = 0
+ls = 'solid'
+lw = 1.0
+ms = 60.
+ms_large = ms*3.
+fontsize=24
+alpha=1.00
 
-#for x in range(upto_this):
-for x in range(10):
+for x in range(upto_this):
+#for x in range(10):
     x=x+1
     data_one = data[np.where(data['cntr_01'] == x)]
 
@@ -54,11 +60,8 @@ for x in range(10):
         dec = data_one['dec'][0]
 
         ## Setting up a 3 panel, "triptych" style plot
-        fig, (ax1, ax2, ax3) = plt.subplots(1,3, figsize=(21.5, 8.5), gridspec_kw = {'width_ratios':[3, 1, 1]}) # inches
[…]

### 2018-09-26 tex/WW4C_VHzQ.tex
data IRSA files update

@@
         W2 SNR $> 2.0$                                            &   255 (60.1) \\
-        W1 \&\& W2 SNR $> 2.0$  &  \\
+        W1 $\land$ W2 SNR $> 2.0$                         &  \\
         W3 SNR $> 2.0$                                            &  99    (23.3) \\
@@
       \caption{ATLAS \citet{Shanks2015}; }
+      \label{tab:mir_detection}
+    \end{table}
+
+    \begin{table}
+      \begin{tabular}{l r l}
+        \hline  \hline
+         \multirow{2}{*}{Selection}   & number detected \\ 
+                                                   & (\% of full specrta) \\
+        \hline  
+        From ``Source'', ``Rejects'',                    & 245, 40  (67.2) \\
+        W1 SNR $> 2.0$                                       &  279  (65.8) \\
+        W2 SNR $> 2.0$                                       &  258 (60.8) \\
+        W1 $\land$ W2 SNR $> 2.0$                    & 253   (59.7)  \\
+        W3 SNR $> 2.0$                                     &  97    (22.9) \\
+        W4 SNR $> 2.0$                                     &  33    (7.8) \\
+%        Any W1/2/3/4 SNR $>2.0$                            & \\
+        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ &  3 (0.7)\\
+        \hline  \hline
+      \end{tabular}
+      \caption{Data from the AllWISE Source Catalog and AllWISE Reject Table, from the 
+\href{https://irsa.ipac.caltech.edu/cgi-bin/Gator/nph-scan?submit=Select&projshort=WISE} {{\tt NASA/IPAC  Infrared Science Archive}}}
       \label{tab:mir_detection}

### 2018-10-16 tex/WW4C_VHzQ.tex
tester.bib added

--- 2018-09-13 tex/WW4C_VHzQ.tex
@@
 In this paper we include all non-proprietary WFCAM data, which covers all
-public surveys and PI projects from Semester 05A to 1st January 2017 and all
+public surveys and PI projects from Semester 05A to 1st January 2017, and all
 non-proprietary VISTA data, which covers all public surveys and PI projects from
-science verification (20091015) to 1st April 2016, to get as much coverage as
-possible. Hence, the NIR coverage is extremely heterogeneous.
-
-The data was processed using a forced photometry, or matched-aperture
-photometry. A pipeline for this has been developed by WFAU, but
-has not yet been incorporated into the main VDFS pipeline. Full details of the
-matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
-2018, in prep, and has also been discussed in \citet{Cross2013}.  
-%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS. [NJC: this was a conference proceeding
-%% from ADASS2016. They just contacted me about the copyright. They are so slow even though we 
-%% had to submit our proceedings before the conference. I had assumed it was already published.]
-We will give the pertinent points of the MAP and specific details of these data sets below.
-
-The first step of the process was to ingest the catalogue of VHzQs into
-the WSA/VSA. These data are stored in the table \verb+finalQsoCatalogue+. Next we set
-up new programmes WSERV1000, VSERV1000 in the WSA and VSA respectively. We
-assign all frames that potentially contain the high-z QSO based on WCS information in the
-WSA to WSERV1000, but adding a new line to the table \verb+ProgrammeFrame+ and
-same in VSA for VSERV1000. Assigning these frames to a separate programme allows
-us to process them together and put them into a single release.
-
-\subsubsection{Setup Matched Aperture Product}
-
-To create matched aperture products it is first necessary to define the product. We do this in two requirements tables, \verb+RequiredMatchedApertureProduct+ and \verb+RequiredMapAverages+ that
-tell the \textbf{ProgrammeBuilder} software which tables to create and what type of product is being created. These requirements tables also drive the pipeline.
-
-\verb+RequiredMatchedApertureProduct+ contains the following attributes for the High-z QSO MAP product.
-\begin{itemize}
-    \item mapID, Identifier of the MAP product, value=1	
-    \item archiveName, Main archive of product, value='VSA'/'WSA' 	
-    \item programmeID, UID of programme, in this case a combined programme, value=10999
-    \item extractor, Extractor used for forced photometry, value='CASU' (imcore_list)
-    \item mapType, Type of MAP product (options 0 internal band-merged, 1 band-merged across surveys, 2 multi-epoch), value=2 
-    \item name, Name of MAP product, value='highzQsoMap'
-    \item description, Description of MAP product, 'Variability via matched apertures for set of high-z QSOs'	
-    \item selection, Selection, e.g. File, pseudo-SQL, FITS image that is used to give input list, value='SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue'	
-    \item finalProductTable, Name of final product table, value='highzQsoMapVariability'
-    \item addSurveyList, List of additional archive/surveys that data comes from, value='NONE'
-\end{itemize}
-
-\verb+RequiredMatchedApertureProduct+ gives all of the information such as the {\it programmeID} (identifying which data), the {\it mapType} (type of processing), the {\it extractor} to use, the input list {\it selection}, which in this case is the IDs and positions of the QSOs in \verb+finalQsoCatalogue+ which contains all the literature data and pre-derived parameters for the 424 QSOs.
-
-\verb+RequiredMapAverages+ is used to setup the averaging of the MAP photometry from several images.
-We can average the epochs in multiple ways: over all the input images to a deep image, or similarly the input pawprint images to tile image in VISTA.
-Alternatively we can average over a fixed number of epochs or a fixed duration in time.
-Multiple setups can be defined in \verb+RequiredMapAverages+, and the different averages selected using the defined {\it setupID}.
-
-    Add table?
-    \begin{table*}
-      \begin{center}
-        \setlength{\tabcolsep}{4pt}
-        \begin{tabular}{ll lll lll l}
-          \hline \hline
-   programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
-          \hline
-10999	& 1 & 0 & Average over whole time & 0 &	NONE &	-1.000000 &	-99999999 &	1 \\
-10999	& 1 & 1 & Average over a week &	0 & NONE & +7.000000 &	-99999999 &	1\\
-10999	& 1 & 2	& Average over a fortnight & 0 & NONE &	+14.000000 & -99999999 & 1\\
-10999	& 1 & 3	& Average over a month & 0 & NONE & +30.000000 & -99999999 & 1\\
-10999	& 1 & 4	& Average over 10 epochs & 0 & NONE & -9.999995E008 & 10 & 1\\
-10999	& 1 & 5 & Average over 6 months	& 0 & NONE & +183.000000 & -99999999 & 1 \\
-10999	& 1 & 6	& Average over 1 year &	0 & NONE & +365.000000 & -99999999 & 1 \\
-10999	& 1 & 7	& Average over 2 years & 0 & NONE & +730.000000	& -99999999 & 1 \\
-10999	& 1 & 8 & Average over 3 months & 0 & NONE & +91.000000	& -99999999 & 1 \\
-          \hline \hline
-          \label{tab:reqMapAvg}
-        \end{tabular}
-        \caption{}
-      \end{center}
-    \end{table*}
-
-    \subsubsection{Processing MAP data and Forced photometry} 
-    A set of apertures to do forced photometry with were created in 
-    \verb+MapApertureIDshighzQsoMap+, based on the \verb+RequiredMatchedApertureProduct+ 
-    {\it selection} value, which in this case is to use the known positions of $z>5$ QSOs. This may
-    seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
-    but the layer is a general abstraction that allows multiple selections of data, including complex queries
-    or input images.
-
-    CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
-    the input list equal to objects selected to be within \ldots of the multiframe
-    centre. In this case, where there are 424 QSOs spread across the sky, there is
-    typically 1 object per multiframe, but many have two and one frame,
-    multiframeID=2614475 in the VSA (a J-band stack from a P90 PI programme), has 3 objects. 
-    The output of \verb+imcore_list+
-    is a multi-extension FITS binary table, with identical columns to the CASU FITS
-    binary tables produced using the CASU \verb+imcore+\footnote{http://casu.ast.cam.ac.uk/surveys-projects/vista/technical/catalogue-generation}, the basis of all WFCAM and
-    VISTA survey catalogue products and also familiar to many astronomers through the INTWFS, 
-    VST-ATLAS and VPHAS. Since forced photometry can be run
-    in many ways on a particular image depending on the input catalogue, a single science frame is not
-    necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
-    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}).
-    For matched aperture measurements, we process these binary tables using the same
-    software, as the standard extracted catalogues, but implement a few different
-    processes. We calculate both Luptitudes \citep{Luptitudes}, and calibrated fluxes,
-    see Eqn~\ref{eq:jky}.
-
-    \begin{equation}
-      F^{calib} = f\times10^{-0.4*(ZP+VAB-8.90+corr)} 
-      \label{eq:jky}
-    \end{equation}
-
-    \noindent where $f$ is the measured flux in ADU, $ZP$ is the zeropoint of
-    frame, $VAB$ is the Vega-to-AB correction for the filter, and $corr$ are the
-    various correction terms, e.g. distortion correction, scattered light
-    correction, aperture correction, see \citep{Hambly2008, Cross2012}.
-
-    Once all data is processed, the data are ingested into
-    \verb+wserv1000MapRemeasurement+ and \verb+vserv1000MapRemeasurement+
-    respectively. These tables are similar in structure to \verb+lasDetection+
-    described in \citep{Hambly2008} or other UKIDSS or VISTA detection tables. One of
-    the main differences is the primary key which is ({\bf apertureID},{\bf
-      catalogueID}) rather than ({\bf multiframeID},{\bf extNum},{\bf seqNum}),
-    reflecting the fact that these are forced photometry on a known set of apertures
-    and a set of catalogues, rather than detections above a threshold in a set of
-    detector extensions to image multiframes.
-
-    Quasars are known to vary (both photometrically and spectroscopically)
-and very high-$z$ quasars under going super-Eddington accretion during
-a rapid BH growth phase are prime candidates for this variation.
-[NJC: This is better placed somewhere else.
-We first used it to justify averaging over ~4 weeks, but then decided to average over many periods and select later.]
-Therefore, with repeat observations over many epochs available via the
-WSA, we have a choice to make for how we report the photometry. The remeasured photometry is averaged to
-improve signal-to-noise over all the averaging schemes setup in Table~\ref{tab:reqMapAvg}. This allows us to get the best combination of signal-to-noise and number of epochs for different QSOs.
+science verification (20091015) to 1st April 2016.
+
+The data was processed using a matched-aperture photometry method
+where flux is recovered at the spectroscopic position of the quasar,
+without necessarily knowing if there is a formal detection in the NIR
+photometry beforehand.  Full details of the matched-aperture pipeline
+will appear in a forthcoming paper, Cross et al.  2018, in prep, and
+has also been discussed in \citet{Cross2013}.
+
+We query the WSA and VSA performing matched-aperature photometry at
+the positions of our 424 VH$z$Qs. We return a database with $xxxx$
+entries. This database is world-readable and we give the full receipe
+and relevant SQL queries in Appendix~\ref{sec:SQL}.
 
     \subsubsection{Averaging matched photometry}
-    Unfortunately the photometry in a single epoch image often has low
-    signal-to-noise. The advantage of matched aperture photometry on QSOs is that
-    co-adding is relatively simple: if each epoch is taken in the same aperture
-    (assuming the astrometry is correct) and the aperture photometry has been
-    corrected to total: the standard aperture corrections work well for point
-    sources then averaging the calibrated photometry should give as good as
-    extracting from a deep stack. In fact it will almost certainly do better, since
-    the images in some cases are taken from multiple projects with different
-    pointings, and orientations and exposures, so stacking may not be optimal. 
-    In addition, corrections such as scattered light, pixel distortion
-    and aperture corrections will be more complex, if not impossible to apply to
-    deep-stacks but will be automatically applied in the averaging of forced
-    photometry.
+    The photometry in a single epoch image often has low
+    signal-to-noise.  The advantage of matched aperture photometry on QSOs
+    is that co-adding is relatively simple if each epoch is taken in the
+    same aperture and the aperture photometry has been corrected to
+    total. Indeed, the standard aperture corrections work well for point
+    sources. Coadding using the matched-aperature photometry, where the
+    individual epochs are taken from multiple projects with different
+    pointings and orientations, should help with issues such as scattered
+    light, pixel distortion and aperture corrections.
 
     We average the aperture corrected calibrated fluxes (e.g. {\bf aperJky3}), and
-    then convert to magnitudes or luptitudes. Since we do not have a deep image for
+    then convert to magnitudes. Since we do not have a deep image for
     each set of averages, we cannot calculate non-aperture corrected values, so the
@@
     \end{equation}
-
-    \noindent where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
+    where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
     averaged such as the aperture corrected calibrated flux in a $1\arcsec$ aperture
@@
     The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
-    $w_i=0$ if an epoch is excluded for quality control purposes. We exclude inputs
-    where the bitwise quality flag, {\bf ppErrBits}>256, and additionally, in the
-    case of VISTA, we exclude data on detector 16 ({\bf extNum=17}), where the 
-    quantum efficiency is variable. If all remeasurements are excluded, then one  of
-    the ones with the lowest {\bf ppErrBits} is used. In this case the averages 
-    will be equal to the original measurement, and the reader may wonder why we 
-    bother to duplicate the data. It is important to do this to simplify queries 
-    for users who will then not have to set up complex queries to work out where 
-    the data is, and only around $2\%$ of VISTA MAP measurements were excluded  so
-    the fraction of duplications is very low. The average data is stored in 
-    \verb+wserv1000MapRemeasAver+ for WFCAM and \verb+vserv1000MapRemeasAver+ for 
-    VISTA, which again are organised with a primary key of ({\bf apertureID},{\bf catalogueID}).
-    Some parameters that are averaged do not have an error $\sigma_{F}$, so in these
-    cases we weight them using the {\bf averageConf} parameter, which has a median
-    of 100. In the case of WFCAM where this is not calculated, we set each epoch to
-    have an {\bf averageConf}$=100$. The {\bf sumWeights} parameter in the
-    \verb+MapRemeasAver+ tables is the sum of all the {\bf averageConf} values that
-    went into the calculation and the \verb+vserv1000MapAverageWeights+ table gives
-    the weights for each epoch, linked to each average for VSERV1000.
+    $w_i=0$ if an epoch is excluded for quality control purposes.
 
@@
     see Tab.~\ref{tab:reqMapAvg}. The
-    averaging process starts at the first epoch and works on. Possible future
-    refinements could first look for denser groupings that satisfied the criteria so
-    that these were not split into two groups. For this high-z QSO project we have averaged over overlaps, 
-    because in several cases data for one source comes from multiple original projects that have slightly 
-    different pointings.
-
-    Each averaged catalogue has a separate entry in
-    \verb+MapFrameStatus+ and is linked to each original epoch remeasured catalogue
-    through \verb+MapProvenance+, which contains the averaged catalogue
-    identifier {\bf combiCatID}, the epoch catalogue identifier {\bf catalogueID}
-    and the averaging setup ID {\bf avSetupID}.
-
-We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
-
-    The code to calculate variability statistics as described in \cite{Cross2009} has
-    not yet been completed to run with the matched aperture pipeline, so these are
-    not included. Variables were selected ...
+    averaging process starts at the first epoch and works on.
+    %%
+    We give examples of the SQL queries syntax in Appendix~\ref{sec:SQL}.
+
+    114 quasars have both WFCAM and VISTA data.
 
@@
       \includegraphics[width=8.5cm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+      {/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
       \vspace{-16pt}
@@
   \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
   \centering
@@
       &&&&&&\\
+      $J_{\rm 2MASS}$       &   12350   &       10806  & 	14068  &  1624       &  $J_{\rm 2MASS}  $     & $= J_{AB}    - 0.894  $         \\
       $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.921  $         \\
@@
       $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
+      $H_{\rm 2MASS}$      & 16620        & 	14787  &   18231   & 2509      & $H_{\rm 2MASS}$      & $= H_{AB}  - 1.374 $        \\
       &&&&&&\\
       $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K$s$_{AB} - 1.83  $          \\ 
+      $K$s$_{\rm 2MASS}$     &   21590    & 	19544  &   23552        &   2619      & $K$s$_{\rm 2MASS}$      & $ = K$s$_{AB} -  1.84  $          \\ 
       $K_{\rm WFCAM}$     &    22010     &    20290 &    23800         &   3510          & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
@@
 
-\begin{enumerate}
-\item http://wsa.roe.ac.uk/ 
-\item Login
-\item {\tt username:	WSERV1000;  password: 	highzqso;   community: 	nonSurvey} 
-\item Freeform SQL Query with  WSERV1000v20180327
-\end{enumerate}
+The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
+Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
+with these credentials::
+\begin{itemize}
+    \item Username: {\tt WSERV1000}
+    \item password: {\tt highzqso}
+    \item community: {\tt nonsurvey}
+\end{itemize}
+Then going to the \href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{[\tt Free Form SQL 
+Query} page the Database release {\tt WSERV1000v20180716} can be accessed which 
+contains all the data we use here.
 
@@
 \bibliographystyle{mn2e}
-\bibliography{/cos_pc19a_npr/LaTeX/tester_mnras}
+\bibliography{tester_mnras}
 

### 2018-10-16 tex/WW4C_VHzQ.tex
Small changes
Continued investigations into WSA outputs

@@
 \end{itemize}
-Then going to the \href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{[\tt Free Form SQL 
-Query} page the Database release {\tt WSERV1000v20180716} can be accessed which 
-contains all the data we use here.
+Then going to the
+\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
+Query}} page the Database release {\tt WSERV1000v20180716} can be
+accessed which contains all the data we use here.
+
+We {\it nota bene} a few things. First, the quantity {\tt aperJky3}
+and {\tt aperJky3Err} are found in the {\tt wserv1000MapRemeasAver}
+and {\tt wserv1000MapRemeasurement}, so care has to be taken to return
+unique column names (otherwise e.g.
+\href{http://docs.astropy.org/en/stable/io/fits/}{astropy.io.fits}
+will crash).  As such, we alias {\tt aver.aperJky3} to {\tt
+aperJky3Aver} and likewise for the error quantity. Aliases will be
+necessary in some cases anyway, because some queries can be done
+sensibly on multiple instances of the same table. Other times, one may
+join tables on quantities such as {\tt catalogueID} or {\tt
+apertureID}, where you are meaning the same thing, but aliases would
+again be sensible.
+
+Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians.
 

### 2018-10-16 data/WSA/No_entries_per_quasar.py
WSA files and new python code for tracking unique entries

@@ -1,0 +1,100 @@
+'''
+Taking the WSA data for the VHzQ sample and looking at how many
+enteries there are per object.
+'''
+
+from astropy.io import fits
+import numpy as np
+import matplotlib.pyplot as plt
+
+## Reading in the data
+path = '/cos_pc19a_npr/programs/quasars/highest_z/data/WSA/'
+filename = 'results16_20_2_38_44430.fits'
+fits_table=path+filename
+
+## open a FITS file
+hdul = fits.open(fits_table)  
+
+## assume the first extension is a table
+data = hdul[1].data  
+## Saying what the columns are::
+data.columns
+
+## Converting from radians to degrees
+data.RA  = data.RA  * (180./np.pi)
+data.DEC = data.DEC * (180./np.pi)
+
+## Looking for unique entries per column
+print('No. of unique enteries by QSONAME::         ', len(np.unique(data.QSONAME)))
+print('No. of unique enteries by RA::              ', len(np.unique(data.RA)))
+print('No. of unique enteries by DEC::             ', len(np.unique(data.DEC)))
+print('No. of unique enteries by APERTUREID::      ', len(np.unique(data.APERTUREID)))
+print('No. of unique enteries by APERJKY3AVER::    ', len(np.unique(data.APERJKY3AVER)))
+print('No. of unique enteries by APERJKY3AVERERR:: ', len(np.unique(data.APERJKY3AVERERR)))
+print('No. of unique enteries by SUMWEIGHT::       ', len(np.unique(data.SUMWEIGHT)))
+print('No. of unique enteries by MJDOBS::          ', len(np.unique(data.MJDOBS)))
+print('No. of unique enteries by FILTERID::        ', len(np.unique(data.FILTERID)))
+print('No. of unique enteries by APERJKY3::        ', len(np.unique(data.APERJKY3)))
+print('No. of unique enteries by APERJKY3ERR::     ', len(np.unique(data.APERJKY3ERR)))
+print('No. of unique enteries by WEIGHT::          ', len(np.unique(data.WEIGHT)))
+print('No. of unique enteries by PPERRBITS::       ', len(np.unique(data.PPERRBITS)))
+print('No. of unique enteries by PROJECT::         ', len(np.unique(data.PROJECT)))
+
+
+## Check if two to get unique values from list
+##
+# function to get unique values 
+def unique(list1): 
+  
+    # intilize a null list 
[…]

### 2018-10-17 tex/WW4C_VHzQ.tex
Small changes
VSA notes updated

@@
 
-In this paper we include all non-proprietary WFCAM data, which covers all
+We access both the WSA and the VSA and include all non-proprietary WFCAM data, which covers all
 public surveys and PI projects from Semester 05A to 1st January 2017, and all
@@
 entries. This database is world-readable and we give the full receipe
-and relevant SQL queries in Appendix~\ref{sec:SQL}.
+and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.
 
@@
     averaging process starts at the first epoch and works on.
-    %%
-    We give examples of the SQL queries syntax in Appendix~\ref{sec:SQL}.
-
-    114 quasars have both WFCAM and VISTA data.
+
+    We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are detected in the VISTA VSA database with 114 objects in common with both WFCAM and VISTA data.
+We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
 
@@
 Here we give the receipe and SQL that returned the near-infrared photometry 
-for the VH$z$Qs.
+for the VH$z$Qs from the  WFCAM Science Archive.
 
@@
 
-Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians.
+Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
+used directly. To return values in degrees, use a selection with an alias, e.g. 
+{\tt RA as RADeg} and {\tt DEC as DECDeg}.
 
 \onecolumn
-\input{SQL_examples}
+\input{SQL_examples_WSA}
+\twocolumn
+
+\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL}
+In a very similar manner to the WSA, we give here the details on how to access
+the VISTA Science Archive (VSA)
+
+At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
+with these credentials::
+\begin{itemize}
+    \item Username: {\tt VSERV1000} 
+    \item password: {\tt highzqso} 
+    \item community: {\tt proprietary}
+\end{itemize}
+Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20180716}.
+
+\onecolumn
+\input{SQL_examples_VSA}
 \twocolumn

### 2018-10-17 data/WSA/No_entries_per_quasar.py

@@ -20,14 +20,10 @@ data = hdul[1].data
 ## Saying what the columns are::
 data.columns
 
-## Converting from radians to degrees
-data.RA  = data.RA  * (180./np.pi)
-data.DEC = data.DEC * (180./np.pi)
-
 ## Looking for unique entries per column
 print('No. of unique enteries by QSONAME::         ', len(np.unique(data.QSONAME)))
-print('No. of unique enteries by RA::              ', len(np.unique(data.RA)))
-print('No. of unique enteries by DEC::             ', len(np.unique(data.DEC)))
+print('No. of unique enteries by RA::              ', len(np.unique(data.RAJ2000)))
+print('No. of unique enteries by DEC::             ', len(np.unique(data.DECJ2000)))
 print('No. of unique enteries by APERTUREID::      ', len(np.unique(data.APERTUREID)))
 print('No. of unique enteries by APERJKY3AVER::    ', len(np.unique(data.APERJKY3AVER)))
 print('No. of unique enteries by APERJKY3AVERERR:: ', len(np.unique(data.APERJKY3AVERERR)))
@@ -59,7 +55,7 @@ def unique(list1):
         print(x)
 
 ## Look at the unique RAs
-#unique(data.RA)
+#unique(data.RAJ2000)
 
 unique_elements, counts_elements = np.unique(data.QSONAME, return_counts=True)
 print("Frequency of unique values of the said array:")

### 2018-11-05 tex/older_tex/WW4C_VHzQ_20181019.tex
Good, major update of the Introduction

--- 2018-10-17 tex/WW4C_VHzQ.tex
@@
 $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-analysing all the WFCAM and VISTA [NJC: homogeneous isn't the write term. The NIR data is very heterogeneous] near-infrared photometry for the quasars; {\it
-(iii)} making the first study of NIR variability of the VHzQ
-population and {\it (iv)} establishing the photometric properties for
-upcoming surveys and telescopes, e.g. the Large Synoptic Survey
+analysing all the WFCAM and VISTA near-infrared photometry for the quasars;
+{\it (iii)} making the first study of NIR variability of the VHzQ population 
+and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes, e.g. the Large Synoptic Survey
 Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
@@
 observed-frame optical but bright in the observed frame near-infrared,
-VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
-\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.
+VH$z$Qs are generally detected in the near-infrared $ZYJHK(s)$-bands
+\citep[$\approx$0.83-2.38$\mu$m; e.g., ][]{Peth2011}.
 
@@
 The data was processed using a matched-aperture photometry method
-where flux is recovered at the spectroscopic position of the quasar,
+where flux is measured at the spectroscopic position of the quasar,
 without necessarily knowing if there is a formal detection in the NIR
@@
 We query the WSA and VSA performing matched-aperature photometry at
-the positions of our 424 VH$z$Qs. We return a database with $xxxx$
-entries. This database is world-readable and we give the full receipe
+the positions of our 424 VH$z$Qs. This database is world-readable and we give the full receipe
 and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.
@@
     on the requirements in \verb+RequiredMapAverages+, in these cases over time
-    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and over all epochs,
-    see Tab.~\ref{tab:reqMapAvg}. The
-    averaging process starts at the first epoch and works on.
-
-    We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are detected in the VISTA VSA database with 114 objects in common with both WFCAM and VISTA data.
-We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
+    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
+    over all epochs. {\bf NJC: Should we add this table to suplemental online
+    only material?} The averaging process starts at the first epoch and works on.
+
+    We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are 
+    detected in the VISTA VSA database with 114 objects in common with both
+    WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
 
@@
         \hline  
-        Any band ($YJHK/K_{s}$   &  394  ( ) \\
-        $Y$-band    &    ( ) \\
-        $J$-band    &    ( ) \\
-        $H$-band    &    ( ) \\
-        $K$ or $Ks$-band    &    ( ) \\
+        Any band ($ZYJHK/K_{s}$   &  394  (92.9) \\
+        $Z$-band    &  72  (17.0) \\
+        $Y$-band    &  249  (58.7) \\
+        $J$-band    &  391  (92.2) \\
+        $H$-band    &  258  (60.8) \\
+        $K$ or $Ks$-band    &  297  ( ) \\
         \hline  \hline
@@
 Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
-Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lighcurves and associated colour changes. Here we show 
-J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and
+associated colour changes. Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
+{\bf NJC: What about NIR light-curves / combined light-curves}
 

### 2018-11-05 tex/older_tex/WW4C_VHzQ_20181105.tex
Another medium update to the .tex

--- 2018-11-05 tex/older_tex/WW4C_VHzQ_20181019.tex
@@
 
-Super-Eddington (also called super-critical) accretion is a viable
-physical mechanism to explain the high luminosity and rapid growth of
-supermassive black holes in the early universe
-\citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
+Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a
+viable mechanism to explain the high, potentially super-Eddington,
+luminosity and rapid growth of supermassive black holes in the early
+universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
 Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
 one might well expect VH$z$Qs to vary in luminosity as they
-potentially go through phases of Super-Eddington accretion and these
-signatures of photometric variablity should be looked for, especially
-when the e.g. near-infrared $K$-band is sampling rest-frame
-$\approx$3670, 3145, 2750\AA\ at redshifts $z=5, 6$ and 7,
-respectively.
-
-Quasars are also known to be prodigious emitters of infrared emission,
+potentially go through phases of super-critical accretion and these
+signatures of photometric variability should be looked for, noting the
+rest-frame optical emission is redshifted into the observed
+near-infrared (NIR) at redshifts $z>5$. Fortunately, data are now in
+place from deep, wide-field NIR instruments and surveys such as the
+Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red
+Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed
+CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for
+Astronomy (VISTA) in the Southern Hemisphere, that are necessary for
+identifying VH$z$Qs.
+
+Quasars are known to be prodigious emitters of infrared emission,
 thought to be from the thermal emission of dust grains heated by
@@
 luminosity/classes of objects, but here we use these terms
-interchangeably (with a preference for quasar) in recognition of the
+interchangeably, with a preference for quasar, in recognition of the
 fact that they both describe accreting supermassive black holes
@@
 ][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
-Timlin2016} as well as AGN and star-forming galaxies due to the
-presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
-\citep[e.g., ][]{Yan2007, Tielens2008}.
+Timlin2016} as well as between AGN and star-forming galaxies due to
+the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
+>3\mu$m \citep[e.g., ][]{Yan2007, Tielens2008}.
 
@@
 abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole. Thus understanding how dust first forms and appears 
+central black hole. But understanding how dust first forms and appears
 in the central engine remains an open question.
@@
 WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
-``ALLWISE'' catalog, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
-\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
-detections of 17 (55\%) of the then known 31 quasars at $z >
-6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
-data release, as opposed to the superior ``AllWISE'' catalogs. That
-sample only examined the 31 known $z>6$ quasars; our sample has 148
-objects with redshift $z \geq 6.00$.
+of 3.4, 4.6, 12, and 23$\mu$m. The all sky ``ALLWISE'' catalog
+release, contains nearly 750 million detections at
+high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
+of which over 4.5M AGN candidates have been identified with 90\%
+reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
+mid-infrared (MIR) detections of 17 (55\%) of the then known 31
+quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
+WISE `All-Sky' data release, as opposed to the superior ``AllWISE''
+catalogs. That sample only examined the 31 known $z>6$ quasars; our
+sample has 148 ({\bf NPR to Double Check!}) objects with redshift $z
+\geq 6.00$.
+
+Critically, we now have available to us new W1 and W2 photometry from
+the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
+WISE-selected catalog that is based on significantly deeper imaging
+and has a more extensive modeling of crowded regions than the ALLWISE
+release. For the first time in a catalog, unWISE takes advantage of
+the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
+Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
+achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
+additional depth is a significant advantage in the detection and study
+of VH$z$Qs in the 3-5 micron regime.
 
@@
 $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-analysing all the WFCAM and VISTA near-infrared photometry for the quasars;
-{\it (iii)} making the first study of NIR variability of the VHzQ population 
-and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes, e.g. the Large Synoptic Survey
-Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
+analyzing all the WFCAM and VISTA near-infrared photometry for the
+quasars; {\it (iii)} making the first study of NIR variability of the
+VHzQ population and {\it (iv)} establishing the photometric properties
+for upcoming surveys and telescopes, e.g. the Large Synoptic Survey
+Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}},
 ESA {\it
@@
 and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
-\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
-\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
-\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}
+(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
 
@@
 surveys and datasets we use and present the photometry of the VH$z$Qs.
-\textbf{In Section 3 we } In Section 4 we and we then note our Conclusions in
-Section 5.
-
-We make the somewhat unconventional decision [NJC: Is this unconventional?] to present all our
-photometry and magnitudes on the AB zero-point system
-\citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared,
-as well as the mid-infrared magnitudes.  Because of established
-conventions, we report SDSS [NJC: PanSTARRS/DES rather than SDSS?] $ugriz$ magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
-magnitudes are calibrated on the Vega system (Wright et al. 2010). For
-WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339,
-5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
-Brown2014b}. WFCAM and VISTA \citep{Hodgkin2009;GonzalezFernandez2018} are also calibrated on a Vega system (WFCAM), or near Vega system (VISTA). \citet{Brown2014b}, in PASA, is the paper about
-Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
-Filter. We make use of the Explanatory Supplement to the WISE All-Sky
-Data Release, as well as the WISE AllWISE Data Release Products
-online.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km
-s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} =
-0.693$ (Planck Collaboration et al. 2016) in order to be consistent
-with \citet{Banados2016}.
+In Section 3 we ... and In Section 4 we ... We conclude in Section 5 
+and present all the necessary details to obtain our dataset in the 
+Appendices.
+
+We make the decision to present all our photometry and magnitudes on
+the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.  This
+includes the near-infrared, as well as the mid-infrared magnitudes.
+Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide
+range of optical, NIR and MIR filters. We use a flat $\Lambda$CDM
+cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$,
+and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in
+order to be consistent with \citet{Banados2016}.
 
@@
 their broad Ly$\alpha$ emission line, \nv emission and characteristic
-shape blueward of 1215\AA\ observed. As we shall see, some of the more
+shape blueward of 1215\AA\ rest. As we shall see, some of the more
 recently discovered objects are close to the galaxy luminosity
@@
 7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into espectral features and line strengths, and take as given 
-the published spectra.
+discussion into spectral features and line strengths, and take as given 
+the published spectra and identifications.
 
@@
 \appendix
-\section{Filter Curves} 
+\section{Filter Curves}\label{sec:filters} 
 FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.

### 2018-11-05 tex/WW4C_VHzQ.tex
updated references

@@
 abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole. Thus understanding how dust first forms and appears 
-in the central engine remains an open question.
+central black hole. But understanding how dust first forms and appears
+in the central engine remains an open question \citep{WangR2008, WangR2011}.
 
 WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
-``ALLWISE'' catalog, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
-\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
-detections of 17 (55\%) of the then known 31 quasars at $z >
-6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
-data release, as opposed to the superior ``AllWISE'' catalogs. That
-sample only examined the 31 known $z>6$ quasars; our sample has 148
-objects with redshift $z \geq 6.00$.
+of 3.4, 4.6, 12, and 23$\mu$m. The all sky ``ALLWISE'' catalog
+release, contains nearly 750 million detections at
+high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
+of which over 4.5M AGN candidates have been identified with 90\%
+reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
+mid-infrared (MIR) detections of 17 (55\%) of the then known 31
+quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
+WISE `All-Sky' data release, as opposed to the superior ``AllWISE''
+catalogs. That sample only examined the 31 known $z>6$ quasars; our
+sample has 148 ({\bf NPR to Double Check!}) objects with redshift $z
+\geq 6.00$.
+
+Critically, we now have available to us new W1 and W2 photometry from
+the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
+WISE-selected catalog that is based on significantly deeper imaging
+and has a more extensive modeling of crowded regions than the ALLWISE
+release. For the first time in a catalog, unWISE takes advantage of
+the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
+Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
+achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
+additional depth is a significant advantage in the detection and study
+of VH$z$Qs in the 3-5 micron regime.
 
@@
 $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-analysing all the WFCAM and VISTA [NJC: homogeneous isn't the write term. The NIR data is very heterogeneous] near-infrared photometry for the quasars; {\it
-(iii)} making the first study of NIR variability of the VHzQ
-population and {\it (iv)} establishing the photometric properties for
-upcoming surveys and telescopes, e.g. the Large Synoptic Survey
-Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
+analyzing all the WFCAM and VISTA near-infrared photometry for the
+quasars; {\it (iii)} making the first study of NIR variability of the
+VHzQ population and {\it (iv)} establishing the photometric properties
+for upcoming surveys and telescopes, e.g. the Large Synoptic Survey
+Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}},
 ESA {\it
@@
 \section{Data}
-In Table~\ref{tab:THE_TABLE} we present our dataset and 
-we have assembled this in the following manner.  First
-we compile the list of all known, spectroscopically confirmed quasars
-from the literature. Most of these objects are easily identified by
-their broad Ly$\alpha$ emission line, \nv emission and characteristic
-shape blueward of 1215\AA\ observed. As we shall see, some of the more
-recently discovered objects are close to the galaxy luminosity
+In Table~\ref{tab:THE_TABLE} we present our dataset and we have
+assembled this in the following manner.  First we compile the list of
+all known, spectroscopically confirmed quasars from the
+literature. Most of these objects are easily identified by their broad
+Ly$\alpha$ emission line, \nv emission and characteristic shape
+blueward of 1215\AA\ in the rest-frame. As we shall see, some of the
+more recently discovered objects are close to the galaxy luminosity
 function characteristic luminosity $M^{*}$, and some have relatively
@@
 7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into espectral features and line strengths, and take as given 
-the published spectra.
-
-We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset. The optical data comes from the 
-Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
-survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
-including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
-the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.
-
-Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
-on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
-delivering exquisite multi-band photometry data
-\citep[][]{Aihara2018b} the five broad bands $grizy$.
-
-The near-infrared data comes from two primary sources. First, the Wide
-Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
-Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
-the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
-\citep[Visible and Infrared Survey Telescope for
-Astronomy;][]{Emerson2006, Dalton2006}.
-
-We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
-the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
-In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{wise2.ipac.caltech.edu/docs/release/allwise/}}.
-
-Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
+discussion into spectral features and line strengths, and take as
+given the published spectra and identifications.
+
+We then obtain optical, near-infrared and mid-infrared photometry for
+the spectral dataset. The optical data comes from the Panoramic Survey
+Telescope and Rapid Response System (Pan-STARRS) survey
+\citep{Chambers2016}. The near-infrared data comes from two sources:
+first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but
+not exclusively, as part of the UKIRT Infrared Deep Sky Survey
+\citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on
+the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared,
+$\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared
+Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+
+For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
 of the filters in question.
@@
 
-Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003}, \citet{Fan2004}, \citet{Mahabal2005},
-\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
-\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
-\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
-\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
-\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
-\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
-\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
-\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
-\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
-\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
-\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
-\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
-\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
-\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
-\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
-\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
-\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
-and \citet{Matsuoka2018b}.
+Specifically, we use data from: 
+\citet{Banados2014, Banados2016, Banados2018}, 
+\citet{Becker2015}, 
+\citet{Calura2014}, 
+\citet{Carilli2007, Carilli2010}, 
+\citet{Carnall2015}, 
+\citet{Cool2006}, 
+\citet{DeRosa2011}, 
+\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
+\citet{Goto2006}, 
+\citet{Ikeda2017}, 
+\citet{Jiang2008, Jiang2009, Jiang2015},  
+\citet{Kashikawa2015}, 
+\citet{Koptelova2017}, 
+\citet{Kim2015}, 
+\citet{Kurk2007, Kurk2009}, 
+\citet{Leipski2014}, 
+\citet{Mahabal2005}, 
+\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
+\citet{Mazzucchelli2017}, 
+\citet{Morganson2012}, 
+\citet{Mortlock2009, Mortlock2011},
+\citet{McGreer2006, McGreer2013},  
+\citet{Reed2015, Reed2017}, 
+\citet{Stern2007},  
+\citet{Tang2017}, 
+\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
+\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
+\citet{Willott2007, Willott2009, Willott2010a, Willott2010b, Willott2013b, Willott2015}, 
+\citet{Wu2015} 
+\citet{YangJ2018}  
+and 
+\citet{Zeimann2011},
 
 Table~\ref{tab:THE_TABLE} gives the salient details for the objects
-used in this study. We use all the $z\geq5.00$ quasars that
-have been discovered and spectroscopically confirmed as of the time of
-writing (2018 June). We report near-infrared ($yYJHK$-bands)
-and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$.
+used in this study. We use all the $z\geq5.00$ quasars that have been
+discovered and spectroscopically confirmed as of the time of writing
+(2018 November). We report near-infrared ($yYJHK$-bands) and
+mid-infrared (WISE W1/2/3/4) photometry.
+% and give our caculcated $M_{1450}$.
 
@@
   FIRST              &     1       &  \citet{Becker1995} \\
-%  HSC         &     8    &  \\
   IMS                 &     1        &  \citet{Kim2015} \\
@@
   PSO                 &   84         &   \citet{Kaiser2002, Kaiser2010} \\
-  RD           &     1       &  \cite{Mahabal2005} \\
+  RD                   &     1         &  \citet{Mahabal2005} \\
   SDSS                & 156         & \citet{EDR} \\
-  SDUV       &   20       & \citet{Yang2017} \\
-  SDWISE    &   27    &     \citet{Wang2016} \\
-  SHELLQs  &  $^{a}$63   &  \citet{Matsuoka2016}\\  %% includes 8 objects from the first HSC paper..
+  SDUV$^{a}$       &   20         & \citet{YangJ2017} \\
+ SDWISE$^{b}$    &   27         &   \citet{WangF2016} \\
+  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% includes 8 objects from the first HSC paper..
   ULAS               &   10          & \citet{Lawrence2007} \\
@@
 \caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference.  
-$^{a}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018}  
-designation.
-}
+  $^{a}$SDUV  = SDSS+ULAS+VHS; 
+  $^{b}$SDWISE = SDSS+WISE; 
+  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.}
       \label{tab:surveys}
@@
 \subsection{Optical Photometry}
-    \subsubsection{Pan-STARRS1 (PS1)} 
+%\subsubsection{Pan-STARRS1 (PS1)} 
 We query the Panoramic Survey Telescope and Rapid Response System
@@
 service at
-    \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-    The PS1 survey observed the 30,000 deg$^{2}$ of sky north of
-    declination $-30$ degrees in five filters $grizy$.  Pan-STARRS1 (PS1)
-    is the first part of Pan-STARRS to be completed and is the basis for
-    the DR1.  \citet{Chambers2016}, \citet{Magnier2016a},
-    \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
-    \citet{Flewelling2016} describe the instrument, survey, and data
-    analyses.  The principal science product of the PS1 survey is the
-    catalog accessible through the CasJobs interface.
+\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The
+Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of
+declination $-30$ degrees in five filters $grizy$.  PS1 is the first
+part of Pan-STARRS to be completed and is the basis for the DR1.
+\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016},
+\citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016}
+describe the instrument, survey, and data analyses.  The principal
+science product of the PS1 survey is the catalog accessible through
+the CasJobs interface.
 
@@
 ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
-    sample. Details of our SQL and links to the main tables are given
-    in Appendix~\ref{sec:PS1_SQL}.
+sample. Details of our SQL and links to the main tables are given in
+Appendix~\ref{sec:PS1_SQL}.
 
@@
 \subsection{Near-infrared photometry}~\label{sec:NIR_data} 
-Due to their selection of being very faint/undetected in the
-observed-frame optical but bright in the observed frame near-infrared,
-VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
-\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.
-
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's

### 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180530.tex
VHzQs figures big update

--- 2018-08-27 tex/older_tex/WW4C_VHzQ_20180729.tex
@@
         {Near and mid-infrared properties of known $z\geq5$ Quasars}
-\author[Ross \& Cross]
-       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
+\author[N.P. Ross et al.]
+       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk} and Nicholas J. Cross$^{1}$
 \\ 
@@
 \begin{abstract}
-Very high redshift quasars are excellent probes of physics the early
-Universe.  Understanding how billion solar mass black holes
-formed, evolve and accrete in the first billion years is a key
-outstanding problem in contemporary astrophysics, and one that wil lbe
-directly addressed by upcoming missions such as ESA {\it Euclid} and
-the {\it James Webb Space Telescope}.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
+sodales est, vel cursus risus porta non. Vivamus vel pretium
+velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
+ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
+hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
+conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
+eu blandit. Donec in lacinia libero.
 %%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have, and in this paper, we,
-for the first time since the discovery of $z\geq5.00$ quasars assemble all spectroscopically confirmed very high redshift quasars in
-one catalogue.
-%%
-In particular we present the near ($z/Z, y/Y, J, H, K_{s}$ and $K$)
-infrared and mid-infrared (WISE) properties of all 424
-spectroscopically known redshift $z\geq5$ quasars.  Using archival public
-WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
-in the near-infrared and find blah.  We present a comprehensive series
-of colour-redshift and colour-colour plots and make inferences into
-the hot dust properties of the very high-redshift quasar
-population. Extrapolating the known quasar luminosity function we
-suggest that 80\% of the possibly detected $z\geq5$ quasars in the
-current datasets have been discovered.
+Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 \end{abstract}
@@
 \end{keywords}
-
-\iffalse
-\section*{TO DOs}
-{\bf For NPR: }
-\begin{itemize}
-\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
-\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
-\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
-\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-\item Concentrate on NIR and W1/W2
-\item SED dust plot with just W1/W2...
-\item Check vs. Assef R90/C75 catalog.
-\end{itemize}
-
-\noindent
-{\bf For NJGC: }
-\begin{itemize}
-\item Write the NIR data section(s) 
-\end{itemize}
-
-\noindent
-{\bf For Both: }
-\begin{itemize}
-\item Need to decide what mags and mag system we are reporting, especially in the 
-NIR...
-\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
-\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
-\end{itemize}
-\fi
 
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; and defined here to have redshifts
-$z\geq5.00$) are excellent probes of the early Universe. This includes
+Very high redshift quasars (VH$z$Qs, defined here to have redshifts
+$z\gtrsim5$) are excellent probes of the early Universe. This includes
 studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
@@
 
-Super-Eddington (also called super-critical) accretion is a viable
-physical mechanism to explain the high luminosity and rapid growth of
-supermassive black holes in the early universe
-\citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016} Thus, one might well expect
-VH$z$Qs to vary in luminosity as they potentially go through phases of
-Super-Eddington accretion and these should be looked for, especially
-when the e.g.  near-infrared $K$-band is sampling rest-frame
-$\approx$3670, 3145, 2750\AA\ at redshifts $z=5, 6$ and 7,
-respectively.
-
-The build-up of SMBHs via accretion is important due to the desire to
-understand the evolution of the black hole mass function (BHMF) and
-since there is a remarkable similarity between cosmic star-formation
-rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
-BHAR trace each other \citep[with a normalisation factor of
-$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
-$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
-suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
-at higher redshift, $z>4$. The physical reasons for this are currently very poorly
-understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
-have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
-$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
-][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
-in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
-where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
-stellar mass of the bulge and galaxy total stellar mass,
-respectively. The evolution and potential importance of the SFRD and BHAR 
-link is a key outstanding problem in contemporary astrophysics, 
-potentially explaining the galaxy-black hole scaling relations. 
-However, there may also simply be a non-causal origin of the black-hole 
-galaxy scaling relations \citep{Jahnke2011}.
+%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR).
+The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.
+However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.
+For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}.
+%%However, we also note the potential for the non-causal origins of the
+%%black-hole galaxy scaling relations \citep{Jahnke2011}.
 
@@
 Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
-allow discrimination between AGN\footnote{Historically, ``quasars'' and
+allow discrimation between AGN\footnote{Historically, ``quasars'' and
 ``Active Galactic Nuclei (AGN)'' have described different
@@
 quasars. Such apparently hot-dust-free quasars have no counterparts at
-low redshift. Moreover, those authors demonstrate that the hot-dust
-abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole.
+low redshift. Moreover, we demonstrate that the hot-dust abundance in
+the 21 quasars builds up in tandem with the growth of the central
+black hole,
 
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
-``ALLWISE'' catalog, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
-\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
-detections of 17 (55\%) of the then known 31 quasars at $z >
-6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
-data release, as opposed to the superior ``AllWISE'' catalogs. That
-sample only examined the 31 known $z>6$ quasars; our sample has 148
-objects with redshift $z \geq 6.00$.
+\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
+(55\%) of the then known 31 quasars at $z > 6$. However,
+\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
+as opposed to the superior ``AllWISE'' catalogs. That sample only
+examined the 31 known $z>6$ quasars; our sample has 148 objects with
+redshift $z\geq6.00$.
 
-Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
-with Table 8 of][]{Banados2016}. Our motivations are numerous and
-include: {\it (i)} establishing the first complete catalogue of
-$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-reporting homogenous near-infrared photometry for the quasars; {\it
-(iii)} making the first study of NIR variability of the VHzQ
-population and {\it (iv)} establishing the photometric properties for
-upcoming surveys and telescopes, e.g. the Large Synoptic Survey
-Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
-ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
-and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
-\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
-\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
-\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}
+Here we update \citet{Jiang2010}  and \citet{Blain2013} 
+\citep[along with Table 8 of][]{Banados2016}.
 
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
+We chose redshift $z=5.0$ as our lower redshift limit due to a combination 
 of garnishing a large sample, adequately spanning physical properties 
 (e.g. luminosity, age of the Universe) and to incorporate what knowledge 
-we have gained over the last couple of decades since $z>5$ quasars were 
+we've gained over the last couple of decades since $z>5$ quasars were 
 discovered.
+
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
+In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
+\citet{Assef2013}, \citet{Stern2012}
+
+In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).
+The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys.
+%%
+
+\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter,
 
@@
 
-This paper is organized as follows.  In Section 2, we present the
-assembled list of the 424 $z\leq5.00$ VH$z$Qs that we have
-compiled. We then give a high-level overview of the photometric
-surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we In Section 4 we and we then note our Conclusions in
-Section 5.
+$M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass, stellar mass of the bulge and 
+ galaxy total stellar mass, respectively.
 
-We make the somewhat unconventional decision to present all our
-photometry and magnitudes on the AB zero-point system
-\citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared,
-as well as the mid-infrared magnitudes.  Because of established
-conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
-magnitudes are calibrated on the Vega system (Wright et al. 2010). For
-WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339,
-5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
-Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about
-Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
-Filter. We make use of the Explanatory Supplement to the WISE All-Sky
-Data Release, as well as the WISE AllWISE Data Release Products
-online.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km
-s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} =
-0.693$ (Planck Collaboration et al. 2016) in order to be consistent
-with \citet{Banados2016}.
+Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al.
+2010).
+For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}.
+We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online.
+All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.
+We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
+2016) in order to be consistent with \citet{Banados2016}.
 
@@
 
-\begin{figure*}
-%%trim=l b r t
-  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
-  \centering
-  \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:filters}
-\end{figure*}
+\input{THE_TABLE_v0pnt96_TOP10}
 
-We assemble our dataset in a relatively straightforwad manner.  First
-we compile the list of all known, spectroscopically confirmed quasars
-from the literature. Most of these objects are easily identified by
-their broad Ly$\alpha$ emission line, \nv emission and characteristic
-shape blueward of 1215\AA\ observed. As we shall see, some of the more
-recently discovered objects are close to the galaxy luminosity
-function characteristic luminosity $M^{*}$, and some have relatively
-weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
-7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into espectral features and line strengths, and take as given 
-the published spectra.
-
-We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset.
-
-The optical data comes from the 
-Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
-survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
-including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
-the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.
-
-The near-infrared data comes from the Wide Field Camera (WFCAM) on 
-the United Kingdom Infra-Red Telescope
+Table~\ref{tab:THE_TABLE} gives the salient details for the objects
+used in this study. We use all the $z\geq5.00$ quasars that
+have been discovered and spectroscopically confirmed as of the time of
+writing (2018 June). We report near-infrared ($yYJHK$-bands)
+and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
+$M_{1450}$
 
@@
 
+%% From Banado2016
+%% Fan et al.
+(2000) [2000AJ....120.1167F];     3 = Fan et al.
+(2001) [2001AJ....122.2833F];     4 = Fan et al.
+(2003) [2003AJ....125.1649F];     5 = Fan et al.
+(2004) [2004AJ....128..515F];     6 = Mahabal et al.
+(2005) [2005ApJ...634L...9M];     7 = Cool et al.
+(2006) [2006AJ....132..823C];     8 = Fan et al.
+(2006a) [2006AJ....131.1203F];     9 = Goto et al.
+(2006) [2006MNRAS.371..769G];    10 = Mcgreer et al.
+(2006) [2006ApJ...652..157M];    11 = Carilli et al.
+(2007) [2007ApJ...666L...9C];   12 = Kurk et al.
+(2007) [2007ApJ...669...32K];    13 = Stern et al.
+(2007) [2007ApJ...663..677S];    14 = Venemans et al.
+(2007a) [2007MNRAS.376...76V];    15 = Willott et al.
+(2007) [2007AJ....134.2435W];    16 = Jiang et al.
+(2008) [2008AJ....135.1057J];    17 = Wang et al.
+(2008b) [2008ApJ...687..848W];    18 = Jiang et al.
+(2009) [2009AJ....138..305J];    19 = Kurk et al.
+(2009) [2009ApJ...702..833K];    20 = Mortlock et al.
+(2009) [2009A&A...505...97M];    21 = Willott et al.
+(2009) [2009AJ....137.3541W];    22 = Carilli et al.
+(2010) [2010ApJ...714..834C];   23 = Wang et al.
+(2010) [2010ApJ...714..699W];    24 = Willott et al.
+(2010a) [2010AJ....140..546W];    25 = Willott et al.
+(2010b) [2010AJ....139..906W];    26 = Derosa et al.
+(2011) [2011ApJ...739...56D];    27 = Mortlock et al.
+(2011) [2011Natur..474..616M];   28 = Wang et al.
+(2011) [2011ApJ...739L..34W];   29 = Zeimann et al.
+(2011) [2011ApJ...736...57Z];    30 = Morganson et al.
+(2012) [2012AJ....143..142M];    31 = Venemans et al.
+(2012) [2012ApJ...751L..25V];   32 = Mcgreer et al.
+(2013) [2013ApJ...768..105M];    33 = Venemans et al.
+(2013) [2013ApJ...779...24V];   34 = Wang et al.
+(2013) [2013ApJ...773...44W];   35 = Willott et al.
+(2013b) [2013ApJ...770...13W];    36 = Banados et al.
+(2014) [2014AJ....148...14B];    37 = Calura et al.
+(2014) [2014MNRAS.438.2765C];    38 = Leipski et al.
+(2014) [2014ApJ...785..154L];   39 = Banados et al.
+(2015a) [2015ApJ...805L...8B];   40 = Banados et al.
+(2015b) [2015ApJ...804..118B];   41 = Becker et al.
+(2015) [2015PASA...32...45B];    42 = Carnall et al.
+(2015) [2015MNRAS.451...16C];    43 = Jiang et al.
+(2015) [2015AJ....149..188J];    44 = Kashikawa et al.
+(2015) [2015ApJ...798...28K];   45 = Kim et al.
+(2015) [2015ApJ...813L..35K];   46 = Reed et al.
+(2015) [2015MNRAS.454.3952R];    47 = Venemans et al.
+(2015a) [2015MNRAS.453.2259V];    48 = Venemans et al.
+(2015b) [2015ApJ...801L..11V];   49 = Willott et al.
+(2015) [2015ApJ...801..123W];   50 = Wu et al.
+(2015) [2015Natur..518..512W];    51 = Venemans et al.
+(2016) [2016ApJ...816...37V];   52 = Wang-Feige et al.
+(2016) [labaApJ...819...24W];   53 = Matsuoka et al.
+(2016) [2016arXiv160302281M];   54 = Wang et al.
+(2016) [2016arXiv160609634W];
 Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
@@
 \citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
-\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
-\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
-\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
-\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
-\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
-\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
-\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
-\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
-\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
-\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
-\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
+\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
+\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
+\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
+\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
+\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
+\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
+\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
+\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
+\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
+\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
+\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
+\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
+\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
 \citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
@@
 and \citet{Matsuoka2018b}.
-
-\input{THE_TABLE_v0pnt96_TOP10_betterformat}
-
-Table~\ref{tab:THE_TABLE} gives the salient details for the objects
-used in this study. We use all the $z\geq5.00$ quasars that
-have been discovered and spectroscopically confirmed as of the time of
-writing (2018 June). We report near-infrared ($yYJHK$-bands)
-and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$
-
-\begin{table}
-\begin{tabular}{l r l}
-\hline  \hline
-Survey   & \# VH$z$Qs & Notes  \\
-\hline  
-  ATLAS      &    4    &  \\
-  CFHQS     &  20    &  \\
-  DELS        &    2    &  \\
-  ELAIS       &    1    &  \\
-  FIRST       &    1    &  \\
-  HSC         &    8    &  \\
-  IMS          &   1     &  \\
-  MMT        &  12    &  \\
-  NDWFS    &  1      &  \\
-  PSO          &    84  & \\
-  RD           &  1       & \\
-  SDSS        & 156       & \\
-  SOUV       & 20       & \\
-  SDWISE    & 27& \\
-  SHELLQs  & 55 & \\
-  ULAS       & 10& \\
-  VDES       & 11& \\
-  VIK          & 9 &\\
-  VIMOS     & 1& \\
-\hline  \hline
-\end{tabular}
-\caption{ATLAS \citet{Shanks2015}; }
-      \label{tab:surveys}
-\end{table}
 
@@
 We query and return the mean PSF magnitudes from the $grizy$ filters
-    ({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
+({\tt MeanPSFMag}) which are in the AB system for our 425 VH$z$Q
 sample. Details of our SQL and links to the main tables are given
 in~\ref{sec:PS1_SQL}.
-
-    \subsubsection{DECam}
 
@@
 We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
-
-\section{NIR Data}
-
-The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
-(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
-\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
-\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
-\citep[VDFS][]{VDFS}.
-
-In this paper we include all non-proprietary WFCAM data, which covers all
-public surveys and PI projects from Semester 05A to 1st January 2017 and all
-non-proprietary VISTA data, which covers all public surveys and PI projects from
-science verification (200910..) to 1st April 2016, to get as much coverage as
-possible. Hence, the NIR is extremely heterogeneous.
-
-The data was processed using a forced photometry, or matched-aperture
-photometry. A pipeline for this has been developed by WFAU, but
-has not yet been incorporated into the main VDFS pipeline. Full details of the
-matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
-2018, in prep, and has also been discussed in \citet{Cross2013} and \citet{Cross2017}.
-We will give the pertinent points of the MAP and specific details of these data sets below.
-
-\subsection{Selection of NIR}
-
-The first step of the process was to ingest the catalogue of VHzQs into
-the WSA/VSA. These data are in the table \verb+finalQsoCatalogue+. Next we set
-up new programmes WSERV1000, VSERV1000 in the WSA and VSA respectively. We
-assign all frames that contain the high-z QSO based on WCS information in the
-WSA to WSERV1000, but adding a new line to the table \verb+ProgrammeFrame+ and
-same in VSA for VSERV1000. Assigning these frames to a separate programme allows
-us to process them together and put them into a single release.
-
-\subsection{Setup Matched Aperture Product}
-
-Add a new entry \verb+RequiredMatchedApertureProduct+
-
-\begin{itemize}
-\item mapID	archiveName	programmeID	extractor	mapType	name	description	selection	finalProductTable	addSurveyList
-\item 1	1	WSA	10999	CASU	2	highzQsoMap	Variability via matched apertures for set of high-z QSOs	SELECTSTR qsoID,ra,dec FROMSTR finalQsoCatalogue	highzQsoMapVariability	NONE
-\end{itemize}
-
-Explain
-
-Entries in \verb+RequiredMapAverages+
-
-Add table?
-\begin{table*}
-  \begin{center}
-    \setlength{\tabcolsep}{4pt}
-    \begin{tabular}{lll lll lll l}
-\hline \hline
-                &  programmeID &	mapID &	setupID  &	description               &	useDeeps  &	useHighProd &	timeScale	    &  nEpochs     &	overLaps\\
-\hline
-      1	& 10999	           &    1       &	1            &      Average over a week	 &     0        & 	NONE            &	+7.000000  &	-99999999 &	0\\
-      2	& 10999             & 	 1	  & 2   	     & Average over a fortnight &	0        &	NONE	&+14.000000	&-99999999 &	0\\
-      3	& 10999	           &    1  	 & 3	             & Average over a month	&      0        &	NONE	&+30.000000	&-99999999 &	0\\
-      4	& 10999             & 	 1	 & 4	              & Average over 10 epochs &	0        &	NONE	&-9.999995E008 &	10 &	0\\
-      5	& 10999             &	 1	 & 5	             & Average over 6 months   &	0        &	NONE	&+183.000000 &	-99999999 &	0\\
-      6	& 10999            &	 1	 & 6	           & Average over whole time  &	0        &	NONE	&-1.000000 &	-99999999 &	0\\
-      \hline \hline
-      \label{tab:The_Numbers}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{table*}
-
-\subsection{Processing MAP data}
-
-A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
-the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
-seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
-but the layer is a general abstraction that allows multiple sources of
-catalogue, and multiple types\ldots
-Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent
-
-\subsubsection{Forced photometry}
-CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
-the input list equal to objects selected to be within \ldots of the multiframe
-centre. In this case, where there are 424 QSOs spread across the sky, there is
-typically 1 object per multiframe, but many have two and one,
-multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
-is a multi-extension FITS binary table, with identical columns to the CASU FITS
-binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
-VISTA survey products and also familiar to many astronomers through the INTWFS
-\citep{}, and VST-ATLAS and -VPHAS \citep{}. Since forced photometry can be run
-in many ways on a particular image, a single science frame is not
-necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
-links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
-information on what processing stage they are at ({\bf bitProcessingFlag}),
-whether they have been ingested ({\bf isIngested}), or what quality control has
-been run on them ({\bf ppErrBitsStatus}).
-
-For matched aperture measurements, we process these binary tables using the same
-software, as the standard extracted catalogues, but implement a few different
-processes. We calculate both Luptitudes \citep{Luptitudes}, and calibrated fluxes,
-see Eqn~\ref{eq:jky}.
-
-\begin{equation}
-F^{calib} = f\times10^{-0.4*(ZP+VAB-8.90+corr)} 
-\label{eq:jky}
-\end{equation}
-
-\noindent where $f$ is the measured flux in ADU, $ZP$ is the zeropoint of
-frame, $VAB$ is the Vega-to-AB correction for the filter, and $corr$ are the
-various correction terms, e.g. distortion correction, scattered light
-correction, aperture correction, see \citep{Hambly2008, Cross2012}.
-
-Once all data is processed, the data are ingested into
-\verb+wserv1000MapRemeasurement+ and \verb+vserv1000MapRemeasurement+
-respectively. These tables are similar in structure to \verb+lasDetection+
-described in \citep{Hambly2008} or other UKIDSS or VISTA detection tables. One of
-the main differences is the primary key which is ({\bf apertureID},{\bf
-catalogueID}) rather than ({\bf multiframeID},{\bf extNum},{\bf seqNum}),
-reflecting the fact that these are forced photometry on a known set of apertures
-and a set of catalogues, rather than detections above a threshold in a set of
-detector extensions to image multiframes.
-
-\subsubsection{Averaging matched photometry}
-
-Unfortunately the photometry in a single epoch image often has low
-signal-to-noise. The advantage of matched aperture photometry on QSOs is that
-co-adding is relatively simple: if each epoch is taken in the same aperture
-(assuming the astrometry is correct) and the aperture photometry has been
-corrected to total: the standard aperture corrections work well for point
-sources then averaging the calibrated photometry should give as good as
-extracting from a deep stack. In fact it will almost certainly do better, since
-the images in some cases are taken from multiple projects with different
-pointings. In addition, corrections such as scattered light, pixel distortion
-and aperture corrections will be more complex, if not impossible to apply to
-deep-stacks but will be automatically applied in the averaging of forced
-photometry.
-
-We average the aperture corrected calibrated fluxes (e.g. {\bf aperJky3}), and
-then convert to magnitudes or luptitudes. Since we do not have a deep image for
-each set of averages, we cannot calculate non-aperture corrected values, so the
-photometry is only appropriate for point-sources.
-
-\begin{equation}
-\bar{F} = \frac{\sum_i^N (w_i\,F_i)}{\sum_i^N w_i}  
-\label{eq:avg}
-\end{equation}
-
-\noindent where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
-averaged such as the aperture corrected calibrated flux in a $1\arcsec$ aperture
-({\bf aperJky3}) and $\bar{F}$ is the weighted mean average of this parameter.
-The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
-$w_i=0$ if an epoch is excluded for quality control purposes. We exclude inputs
-where the bitwise quality flag, {\bf ppErrBits}>256, and additionally, in the
-case of VISTA, we exclude data on detector 16 ({\bf extNum=17}), where the 
-quantum efficiency is variable. If all remeasurements are excluded, then one  of
-the ones with the lowest {\bf ppErrBits} is used. In this case the averages 
-will be equal to the original measurement, and the reader may wonder why we 
-bother to duplicate the data. It is important to do this to simplify queries 
-for users who will then not have to set up complex queries to work out where 
-the data is, and only around $2\%$ of VISTA MAP measurements were excluded  so
-the fraction of duplications is very low. The average data is stored in 
-\verb+wserv1000MapRemeasAver+ for WFCAM and \verb+vserv1000MapRemeasAver+ for 
-VISTA, which again are organised with a primary key of ({\bf apertureID},{\bf catalogueID}).
-Some parameters that are averaged do not have an error $\sigma_{F}$, so in these
-cases we weight them using the {\bf averageConf} parameter, which has a median
-of 100. In the case of WFCAM where this is not calculated, we set each epoch to
-have an {\bf averageConf}$=100$. The {\bf sumWeights} parameter in the
-\verb+MapRemeasAver+ tables is the sum of all the {\bf averageConf} values that
-went into the calculation and the \verb+vserv1000MapAverageWeights+ table gives
-the weights for each epoch, linked to each average for VSERV1000.
-
-We calculate a set of averaged catalogues, for each pointing and filter, based
-on the requirements in \verb+RequiredMapAverages+, in these cases over time
-spans of 7, 14, 28, 183 days, over 10 epochs and finally over all epochs. The
-averaging process starts at the first epoch and works on. Possible future
-refinements could first look for denser groupings that satisfied the criteria so
-that these were not split into two groups.
-
-Each averaged catalogue has a separate entry in
-\verb+MapFrameStatus+ and is linked to each original epoch remeasured catalogue
-through \verb+MapProvenance+, which contains the averaged catalogue
-identifier {\bf combiCatID}, the epoch catalogue identifier {\bf catalogueID}
-and the averaging setup ID {\bf avSetupID}.
-
-\subsubsection{\ldots}
-
-The code to calculate variability statistics as described in \cite{Cross2009} has
-not yet been completed to run with the matched aperture pipeline, so these are
-not included.
 
@@
 \fi
+
+%    \begin{figure}
+%      \includegraphics[height=8.0cm,width=8.0cm]
+%      {pdf/SDSS_Quasar_Nofz.pdf}
+%      \centering
+%      \caption[he selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands]
+%              {The selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands.}
+%      \label{fig:fig1}
+%    \end{figure}
+
+%    \begin{table}
+%    \begin{center}
+%    \setlength{\tabcolsep}{4pt}
+%    \begin{tabular}{lrrr}
+%    Sample Description  & Number in sample & North & South   \\
+%    \hline
+%    \label{tab:The_LRG_numbers}
+%    \end{tabular}
+%    \caption{}
+%    \end{center}
+%    \end{table}
 
@@
 \section{Results}
- Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam porta sodales est, vel cursus risus porta non.
-Vivamus vel pretium velit.
-Sed fringilla suscipit felis, nec iaculis lacus convallis ac.
-Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-Etiam interdum tristique diam eu blandit.
-Donec in lacinia libero.
-
-\subsection{Detection Rates}
-%\begin{table}
- % \begin{center}
-  %  \setlength{\tabcolsep}{4pt}
-   % \begin{tabular}{lrrr}
-     % \hline       \hline
-    %  Sample Description  & Number in sample & North & South   \\
-     % \hline
-     % \hline \hline
-%      \label{tab:The_Numbers}
- %   \end{tabular}
-  %  \caption{}
-  %\end{center}
-%\end{table}
-
-\subsection{Variability}
-Sed elit massa, eleifend non sodales a, commodo ut felis.
-Sed id pretium felis.
-Vestibulum et turpis vitae quam aliquam convallis.
-Sed id ligula eu nulla ultrices tempus.
-Phasellus mattis erat quis metus dignissim malesuada.
-Nulla tincidunt quam volutpat nibh facilisis euismod.
-Cras vel auctor neque.
-Nam quis diam risus.
-
-Nunc semper quam et leo interdum vulputate eu quis magna.
-Sed nec arcu at orci egestas convallis.
-Aenean quam velit, aliquam vitae viverra in, elementum vel elit.
-Nunc suscipit aliquet sapien a suscipit.
-Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla.
-Nullam eu augue id purus mollis dignissim sed et libero.
-Phasellus eget justo sed neque pellentesque egestas nec id arcu.
-Donec facilisis pulvinar sapien et fringilla.
-Suspendisse vestibulum rhoncus sapien id laoreet.
-Morbi et orci vitae tortor imperdiet imperdiet.
-In hac habitasse platea dictumst.
-Vivamus vel neque id mi ultrices tristique.
-Integer quam libero, ornare vel gravida in, feugiat a ante.
-Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi.
-Vestibulum nec mi justo, eget dapibus velit.
 
@@
      \citet{Blain2013}
-Cras in laoreet mauris.
-Vivamus nec nulla a dui commodo adipiscing.
-Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies.
-Phasellus condimentum gravida tincidunt.
-Phasellus et mauris ac nibh vestibulum vehicula.
-Morbi et augue id purus gravida sagittis quis in sem.
-Phasellus quis risus bibendum eros luctus auctor.
 
     \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
-Proin non tempus velit.
-Etiam laoreet, enim nec scelerisque dictum, tortor massa tempor enim, id pretium justo quam ac lectus.
-Maecenas diam nibh, interdum at lobortis sit amet, dignissim et quam.
-Sed tincidunt faucibus risus, congue tempus nisl consectetur eget.
-Suspendisse venenatis turpis ut risus aliquam interdum.
-In at velit sed ligula dictum dignissim ut et dui.
-Curabitur ac scelerisque purus.
 
 \subsection{Colours}
-Pellentesque vel elit neque, in interdum lacus.
-Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a nisl.
-Ut sit amet sapien a risus dapibus sagittis.
-Cras sed ultricies erat.
-Donec id metus sed urna lacinia convallis vel sed enim.
-Proin nisi libero, ornare vel bibendum eu, sollicitudin sed leo.
-Cras tincidunt aliquet ultricies.
-Cras pretium velit leo, in malesuada enim.
-Duis sagittis ultricies interdum.
-Proin sit amet sem nec metus feugiat pharetra.
 
-Figure~\ref{fig:Opt_colourredshift} presents the optical
-colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
+%%\subsection{Mullaney SEDs}
 
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
-   \centering
-   \caption[]
-   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
-     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
-   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
-bigger gaps between subplots??}}
-   \label{fig:Opt_colourredshift}
- \end{figure*}
-
-Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
-colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
-There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
-the blue or red end respectively. Hmmm....}
-   \label{fig:filters}
- \end{figure*}
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-}
-   \label{fig:filters}
- \end{figure*}
-
-%\subsection{Number Density of High-$z$ Sources}
+\subsection{Number Density of High-$z$ Sources}
 
@@
 
-\subsection{L-$z$ Plane}
-Having obtained an as-near-to-homogenous set of photometry as we can, 
-we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
-sample and in particulare the absolute magnitude at rest-frame 1450\AA'\, $M_{1450}$, 
-which is a key physical quantity and goes directly towards the quasar luminosity 
-function and thus the reionization of hydrogen calculation.
-
-At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
-i.e., in the $z$-band, while at
-
-\begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
-  \centering
-  \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:filters}
-\end{figure*}
-
-\subsection{SEDs and Dust properties of the VH$z$Qs}
-There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
-However, they are, for our purposes all roughly the same.
-
-\begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
-  \centering
-  \caption[]
-  {The rest-frame properties of the VH$z$Qs. }
-  \label{fig:filters}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 ($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
-objects, given their detection rates and SEDs. We find that:
+objects, given their detection rates and SEDs. We find that::
 
 \begin{itemize}
-    \item Lorem ipsum dolor sit amet, consectetur adipiscing
-      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
-      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
-      convallis ac. 
-    \item Fusce pellentesque condimentum dolor, quis vehicula
-      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
-      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
-      diam eu blandit. Donec in lacinia libero.
-    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-      euismod. Cras vel auctor neque. Nam quis diam risus.
+    \item{This sample spans a redshift range of $0.28 < z < 4.36$ and has a bimodal distribution, with peaks 
+        at $z\sim0.8$ and $z\sim2.5$.}
+   \item{We recover a wide range of quasar spectra in this selection.  
+        The majority of the objects have spectra of reddened Type 1
+        quasars, Type 2 quasars (both at low and high redshift) and objects
+        with strong absorption features.} 
+    \item{There is a relatively high fraction of Type 2 objects at low redshift,
+        suggesting that a high optical-to-infrared colour can be an efficient
+        selection of narrow-line quasars.}
+    \item{There are three objects that are detected in the $W4$-band but
+        not $W1$ or $W2$ (i.e., ``W1W2-dropouts''), all of which are at
+        $z>2.6$.}
+    \item{We identify an intriguing class of objects at $z\simeq 2-3$ which are
+        characterized by equivalent widths of REW(C\,{\sc iv})
+        $\gtrsim150$\AA.  These objects often also have unusual line
+        properties.  We speculate that the large REWs may be caused by
+        suppressed continuum emission analogous to Type 2 quasars in the
+        Unified Model. However, there is no obvious mechanism in the Unified
+        Model to suppress the continuum without also suppressing the broad
+        emission lines, thus potentially providing an interesting challenge to
+        quasar models.} 
 \end{itemize}
@@
 ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
-eget tempor elementum, lectus urna feugiat nisi, eget sagittis.
+eget tempor elementum, lectus urna feugiat nisi, eget sagittis
 
@@
 
-This research has made use of the SVO Filter Profile Service
-(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
-MINECO through grant AyA2014-55216 
-%\citet{} 
-The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
-describes the Spanish VO Filter Profile Service. 
-The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html
-
 \newpage
@@
 \appendix
-\section{Filter Curves} 
-FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
-
-\section{A. Photometric Bands and Conversions}
-    Due to the differing normalizations between the
-    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
-    our data in the  purest sense, all the NIR magnitudes from UKIDSS
-    (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett06}.
-
-    Although ULAS magnitudes are reported in terms of Vega and SDSS
-    magnitudes are reported in AB terms for the most part whenever an
-    optical-NIR color was calculated both magnitudes were left in their
-    default term.
-
-\begin{table*}[h*]
-  \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth11}. 
-CTIO/DECam, PanSTARRS/PS1, LSST
-%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
-Filter only values. 
-}
-    \setlength{\tabcolsep}{4pt}
-     \begin{tabular}{l r r r  c l l}
-      %% https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
-      %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
-      \hline
-      \hline
-      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & \multicolumn{2}{c}{AB - Vega  Transformations} \\
-      \hline
-      % {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
-      % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-      $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
-      $g_{\rm DECam}$  &      4734     &   3939    &    5528   &   1133        &  $g_{\rm DECam} $    &$  = g_{\rm AB} + 0.083 $ \\	     
-      $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
-      $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
-      $r_{\rm LSST}$       &     6139    &	  5375    &    7055   &   1338      &  $r_{\rm LSST}   $       &$    = r_{\rm AB} - 0.155 $ \\	
-      $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
-      $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
-      $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
-      $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
-      $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
-      $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
-      $y_{\rm PS1}$      &       9603    &	 9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
-      $y_{\rm LSST}$      &      9677   &	 9089    &    10859  &     810         &  $y_{\rm LSST}  $      &$    = y_{\rm AB} - 0.546 $ \\
-      $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
-      $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VISTA}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
-      $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      $J_{\rm VISTA} $     &     10184   &      9427   &    10977   &     905     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.938  $         \\
-      $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
-      $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VISTA}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
-      $K$s$_{\rm VISTA}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K_{AB} - 1.83  $          \\ 
-      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800   &   3510     & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
-      WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\
-      WISE W2               &    46028    &    39633  &    53414   &  10423    & W2                        &   = W2$_{\rm AB} - 3.339$ \\
-      WISE W3               &  115608    &    74430  &  172613   &  55056    & W3                        &   = W3$_{\rm AB} - 5.174$ \\
-      WISE W4               &  228172    &  195201  &  279107   &  41017    & W4                        &   = W4$_{\rm AB} - 6.66$ \\
-      \hline
-      \hline
-      \label{tab:filter_details}
-    \end{tabular}
-     \end{center}
-\end{table*}
-https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
 

### 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180724.tex
VHzQs figures big update

--- 2018-08-27 tex/older_tex/WW4C_VHzQ_20180729.tex
@@
 
-\iffalse
 \section*{TO DOs}
@@
 \begin{itemize}
-\item Need to decide what mags and mag system we are reporting, especially in the 
+\item Need to decide what mags and mag system we are reporting, espeically in the 
 NIR...
 \item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
-\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
 \end{itemize}
-\fi
 
@@
 enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
-
-Super-Eddington (also called super-critical) accretion is a viable
-physical mechanism to explain the high luminosity and rapid growth of
-supermassive black holes in the early universe
-\citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016} Thus, one might well expect
-VH$z$Qs to vary in luminosity as they potentially go through phases of
-Super-Eddington accretion and these should be looked for, especially
-when the e.g.  near-infrared $K$-band is sampling rest-frame
-$\approx$3670, 3145, 2750\AA\ at redshifts $z=5, 6$ and 7,
-respectively.
 
@@
 (e.g. luminosity, age of the Universe) and to incorporate what knowledge 
-we have gained over the last couple of decades since $z>5$ quasars were 
+we've gained over the last couple of decades since $z>5$ quasars were 
 discovered.
@@
 
-This paper is organized as follows.  In Section 2, we present the
-assembled list of the 424 $z\leq5.00$ VH$z$Qs that we have
-compiled. We then give a high-level overview of the photometric
-surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we In Section 4 we and we then note our Conclusions in
-Section 5.
+Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al.
+2010).
+For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}.
+\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter.
+We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online.
+All optical ($ugriz$ bands) magnitudes are given in the AB system. 
+{\bf Need to decided 
+All near-infrared  ($y/YJHK$) are also given in the AB system.
 
-We make the somewhat unconventional decision to present all our
-photometry and magnitudes on the AB zero-point system
-\citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared,
-as well as the mid-infrared magnitudes.  Because of established
-conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4
-magnitudes are calibrated on the Vega system (Wright et al. 2010). For
-WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339,
-5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011,
-Brown2014b}. \citet{Brown2014b}, in PASA, is the paper about
-Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4
-Filter. We make use of the Explanatory Supplement to the WISE All-Sky
-Data Release, as well as the WISE AllWISE Data Release Products
-online.  We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km
-s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} =
-0.693$ (Planck Collaboration et al. 2016) in order to be consistent
-with \citet{Banados2016}.
+We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
+2016) in order to be consistent with \citet{Banados2016}.
 
@@
 \section{Data}
-
 \begin{figure*}
@@
 
-We assemble our dataset in a relatively straightforwad manner.  First
-we compile the list of all known, spectroscopically confirmed quasars
-from the literature. Most of these objects are easily identified by
-their broad Ly$\alpha$ emission line, \nv emission and characteristic
-shape blueward of 1215\AA\ observed. As we shall see, some of the more
-recently discovered objects are close to the galaxy luminosity
-function characteristic luminosity $M^{*}$, and some have relatively
-weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
-7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into espectral features and line strengths, and take as given 
-the published spectra.
-
-We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset.
-
-The optical data comes from the 
-Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
-survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
-including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
-the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.
-
-The near-infrared data comes from the Wide Field Camera (WFCAM) on 
-the United Kingdom Infra-Red Telescope
-
-\subsection{Very high redshift quasars}
-In Table~\ref{tab:THE_TABLE} we give the discovery reference for the
-VH$z$Qs noting that some objects were discovered independently and
-contemporaneously.  The redshifts for the VH$z$Qs generally come from
-the measurement of broad UV/optical emission lines. Where 
-there are far infra-red emission lines e.g. \cii~158 micron, we report 
-these, but at the level of our current analysis broadline redshifts are
-sufficient.
-
-Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
-\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
-\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
-\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
-\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
-\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
-\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
-\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
-\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
-\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
-\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
-\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
-\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
-\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
-\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
-\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
-\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
-\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
-and \citet{Matsuoka2018b}.
-
-\input{THE_TABLE_v0pnt96_TOP10_betterformat}
+\input{THE_TABLE_v0pnt96_TOP10}
 
@@
 
+\subsection{Very high redshift quasars}
+In Table~\ref{tab:THE_TABLE} we give the discovery reference for the
+VH$z$Qs noting that some objects were discovered independently and
+contemporaneously.  The redshifts for the VH$z$Qs generally come from
+the measurement of broad UV/optical emission lines. Where 
+there are far infra-red emission lines e.g. \cii~158 micron, we report 
+these, but at the level of our current analysis broadline redshifts are
+sufficient.
+
+Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
+\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
+\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
+\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
+\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
+\citet{Jiang2008}, \citet{Wang2008}, \citet{Jiang2009}, \citet{Kurk2009}, 
+\citet{Mortlock2009}, \citet{Willott2009}, \citet{Carilli2010}, 
+\citet{Wang2010}, \citet{Willott2010a}, \citet{Willott2010b}, 
+\citet{DeRosa2011}, \citet{Mortlock2011}, \citet{Wang2011}, 
+\citet{Zeimann2011}, \citet{Morganson2012}, \citet{Venemans2012}, 
+\citet{McGreer2013}, \citet{Venemans2013}, \citet{Wang2013}, 
+\citet{Willott2013b}, \citet{Banados2014}, \citet{Calura2014}, 
+\citet{Leipski2014}, \citet{Banados2015a}, \citet{Banados2015b}, 
+\citet{Becker2015}, \citet{Carnall2015}, \citet{Jiang2015}, 
+\citet{Kashikawa2015}, \citet{Kim2015}, \citet{Reed2015}, 
+\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Willott2015}, 
+\citet{Wu2015}, \citet{Venemans2016}, \citet{Wang2016_WISE}, 
+\citet{Matsuoka2016}, \citet{WangR2016}, \citet{Mortlock2011},
+\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
+\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
+\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
+\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
+\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a} 
+and \citet{Matsuoka2018b}.
+
 \subsection{Optical Photometry}
@@
 \end{table*}
+
+Explain
 
@@
     \setlength{\tabcolsep}{4pt}
-     \begin{tabular}{l r r r  c l l}
-      %% https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
-      %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
+    \begin{tabular}{lcllcl}
       \hline
@@
               & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & \multicolumn{2}{c}{AB - Vega  Transformations} \\
+              & AB - Vega Transformations \\
       \hline
@@
 %      {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-      $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
-      $g_{\rm DECam}$  &      4734     &   3939    &    5528   &   1133        &  $g_{\rm DECam} $    &$  = g_{\rm AB} + 0.083 $ \\	     
-      $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
-      $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
-      $r_{\rm LSST}$       &     6139    &	  5375    &    7055   &   1338      &  $r_{\rm LSST}   $       &$    = r_{\rm AB} - 0.155 $ \\	
-      $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
-      $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
-      $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
-      $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
-      $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
-      $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
-      $y_{\rm PS1}$      &       9603    &	 9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
-      $y_{\rm LSST}$      &      9677   &	 9089    &    10859  &     810         &  $y_{\rm LSST}  $      &$    = y_{\rm AB} - 0.546 $ \\
-      $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
-      $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VISTA}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
-      $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      $J_{\rm VISTA} $     &     10184   &      9427   &    10977   &     905     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.938  $         \\
-      $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
-      $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VISTA}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
-      $K$s$_{\rm VISTA}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K_{AB} - 1.83  $          \\ 
-      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800   &   3510     & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
-      WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\
-      WISE W2               &    46028    &    39633  &    53414   &  10423    & W2                        &   = W2$_{\rm AB} - 3.339$ \\
-      WISE W3               &  115608    &    74430  &  172613   &  55056    & W3                        &   = W3$_{\rm AB} - 5.174$ \\
-      WISE W4               &  228172    &  195201  &  279107   &  41017    & W4                        &   = W4$_{\rm AB} - 6.66$ \\
+      $g_{\rm LSST}$      &     4730   &	3877    &	   5665   &  1333   &  $g_{\rm LSST}      = g_{\rm AB} + x $ \\
+      $g_{\rm DECam}$  &     4734   & 	3939    &    5528   &   1133   &  $g_{\rm DECam}  = g_{\rm AB} + x $ \\	     
+      $g_{\rm PS1}$        &     4776   &    3943    &    5593   &   1167   &  $g_{\rm PS1}      = g_{\rm AB} + x $ \\
+      $r_{\rm PS1}$         &     6130  & 	5386    &    7036   &   1318   &  $r_{\rm PS1}       = r_{\rm AB} + y $ \\
+      $r_{\rm LSST}$       &     6139  &	5375    &    7055   &   1338   &  $r_{\rm LSST}      = r_{\rm AB} + x $ \\	
+      $r_{\rm DECam}$   &     6345  & 	5506    &	   7238   &   1379   &  $r_{\rm DECam}  = r_{\rm AB} + x $ \\	     
+      $i_{\rm PS1}$         &     7485  &     6778    &    8304   &   1243   &  $i_{\rm PS1}       = i_{\rm AB} + x $ \\
+      $i_{\rm LSST}$       &     7487  &	6765    &	   8325   &   1209   &  $i_{\rm LSST}      = i_{\rm AB} + x $ \\
+      $i_{\rm DECam}$   &     7750 &	6950    &    8646    &   1371   &  $i_{\rm DECam}  = i_{\rm AB} + x $ \\	   
+      $z_{\rm PS1}$        &     8658 &	8028    &    9346   &      966   &  $z_{\rm PS1}     = z_{\rm AB} + y $ \\
+      $z_{\rm LSST}$      &     8669 &	8035    &	   9375   &      994  &   $z_{\rm LSST}      = i_{\rm AB} + x $ \\
+
+      $z_{\rm DECam}$  &     9216 &	8360    &   10166   &   1502  &  $z_{\rm DECam}      = i_{\rm AB} + x $ \\
+      $y_{\rm LSST}$      &     9677 &	9089    &	  10859  &     810   &  $y_{\rm LSST}      = i_{\rm AB} + x $ \\
+      $Y_{\rm DECam}$   &   10061 &	9400    &   10805   &   1115  &  $Y_{\rm DECam}      = i_{\rm AB} + x $ \\
+                                        &            &                   &                 &          &  \\
+      $Y_{\rm UKIDSS}$   & 10305 &  9790 & 10810 & 1020 & $Y_{\rm UKIRT}$ = $Y_{AB}$  - 0.634           \\
+      $Y_{\rm VISTA}$   & - &  9790 & 10810 & 1020 & $Y_{\rm UKIRT}$ = $Y_{AB}$  - 0.634           \\
+      $J_{\rm UKIDSS} $ & 12483 & 11690 & 13280 & 1590 & $J$  = $J_{AB}$- 0.938           \\
+      $J_{\rm VISTA} $ & 12483 & 11690 & 13280 & 1590 & $J$  = $J_{AB}$- 0.938           \\
+      $W_{\rm Wircam}$ & 14530 &  & & 1020 & $Y$ = $Y_{AB}$  - 0.634           \\
+      $H_{\rm UKIDSS}$ & 16313 & 14920 & 17840 & 2920 & $H$ = $H_{AB}$ - 1.379          \\
+      $H_{\rm VISTA}$ & 16313 & 14920 & 17840 & 2920 & $H$ = $H_{AB}$ - 1.379          \\
+      $K_{\rm UKIDSS}$ & 22010 & 20290 & 23800 & 3510 & $K$ = $K_{AB}$ - 1.9            \\ 
+      $K_{\rm VISTA}$ & 22010 & 20290 & 23800 & 3510 & $K$ = $K_{AB}$ - 1.9            \\ 
       \hline
@@
 \end{table*}
-https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
 

### 2018-12-08 data/matching_LISTto_unWISE.py
VHzQs SEDs big update

@@ -8,18 +8,16 @@ import numpy as np
 from astropy.io import ascii
 from astropy.io import fits
 
-## `Super-set' list of VHzQs
+## `Super-set' of VHzQs, in that not of these will be unWISE
+## detections
 VHzQs = ascii.read("LIST_OF_VHzQs.dat") 
 
 ## unWISE magnitudes and fluxes
-unWISE_W1 = ascii.read("unWISE/unWISE_W1.dat")
-unWISE_W2 = ascii.read("unWISE/unWISE_W2.dat")
-
+unWISE_W1 = ascii.read("unWISE/unWISE_W1_20181204.dat")
+unWISE_W2 = ascii.read("unWISE/unWISE_W2_20181204.dat")
 
 ## matching distance in arcsecs
 dist = 2.75
-
-#matcher  =  VHzQs[np.where (  (VHzQs['ra'] - unWISE_W1['ra'][0]) < 1.0)]
 
 
 f = open('myfile', 'w')
@@ -31,6 +29,8 @@ counter_justW2_match  = 0
 counter_nomatch       = 0
 
 print('abcd count        RA           Dec   redshift  unW1_RA    unW1_Dec     unW2_RA    unW2_Dec     unW1_mag unW1_magerr    unW1_snr     unW2_mag unW2_magerr    unW2_snr idx_w1 idx_w2    sep_w1         sep_w2', file=f)
+## Looping over all the VHzQs and writing out R.A.s, Decls, redshifts.
+## Then figuring out/matching the VHzQs and unWISE objects
 for ii,jj,kk in zip(VHzQs['ra'], VHzQs['dec'], VHzQs['redshift'])  :
     counter = counter + 1
 
@@ -78,7 +78,8 @@ for ii,jj,kk in zip(VHzQs['ra'], VHzQs['dec'], VHzQs['redshift'])  :
             -99.999, -9.99, -99.999, 
             bm_w2['w2mpro'], bm_w2['w2sigmpro'], bm_w2['w2snr'], 
             idx_w1, idx_w2, delta_w1.min()*3600., delta_w2.min()*3600.,),  file=f)             
-              
+
+    ## neither W1 nor W2 matched    
     else:
[…]

### 2018-12-08 tex/WW4C_VHzQ.tex
WW4C_VHzQ .tex, .pdf udpated

@@
 \citet{Koptelova2017}, 
-\citet{Kim2015}, 
+\citet{Kim2015, Kim2018},  
 \citet{Kurk2007, Kurk2009}, 
@@
 \citet{Wu2015} 
-\citet{YangJ2018}  
+\citet{YangJ2018a, YangJ2018b}  
 and 
@@
   CFHQS            &   20       &  \citet{Willott2007} \\
-  DELS               &     2       &  \citet{Dey2018} \\
+  DELS               &   16       &  \citet{Dey2018} \\
   ELAIS              &     1       &  \citet{Vaisanen2000} \\
   FIRST              &     1       &  \citet{Becker1995} \\
-  IMS                 &     1        &  \citet{Kim2015} \\
+  HSC                 &    8        & \citet{Miyazaki2018} \\
+  IMS                 &     5        &  \citet{Kim2015} \\
   MMT               &   12        &  \citet{McGreer2013} \\
   NDWFS           &     1         &  \citet{JD1999} \\
-  PSO                 &   84         &   \citet{Kaiser2002, Kaiser2010} \\
+  PSO                 &   83         &   \citet{Kaiser2002, Kaiser2010} \\
   RD                   &     1         &  \citet{Mahabal2005} \\
-  SDSS                & 156         & \citet{EDR} \\
+  SDSS                &  170         & \citet{EDR} \\
   SDUV$^{a}$       &   20         & \citet{YangJ2017} \\
  SDWISE$^{b}$    &   27         &   \citet{WangF2016} \\
-  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% includes 8 objects from the first HSC paper..
+%  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
+  SHELLQs         &    55         &  \citet{Matsuoka2016}     \\  
+  UHS               &    1            &  \citet{Fan2018} \\
   ULAS               &   10          & \citet{Lawrence2007} \\
-  VDES              &   11          &  \citet{Reed2017} \\
+  VDES$^{c}$              &   17          &  \citet{Reed2017} \\
   VIK                 &     9          &  \citet{Edge2013} \\
@@
   $^{b}$SDWISE = SDSS+WISE; 
-  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.}
+  $^{c}$VDES = VHS/VIKING+DES; 
+%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
+}
       \label{tab:surveys}
@@
 \appendix
-\section{Filter Curves}\label{sec:filters} 
-FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
+%\section{Filter Curves}\label{sec:filters} 
+%From the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
 
@@
 
+%% \section{Notes on Individual Objects}
+%% \input{/cos_pc19a_npr/data/highest_z_QSOs/notes_on_individual_objects}
+
 \section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}

### 2018-12-08 tables_for_paper/survey_origin.py

@@ -1,14 +1,9 @@
-
-# coding: utf-8
-
-# In[1]:
-
-
-''' A simple little bit of code to figure out which survey the VHzQs came from.'''
-
-
-# In[2]:
-
+'''
+A simple little bit of code to figure out which survey the VHzQs came
+from.  I haven't gone "fully, fully" here's the plug in .tex, but
+could easily see that happening and would be happy for it!!
+v1.00    Wed Dec  5 19:14:34 GMT 2018
+'''
 
 import numpy as np
 import pandas as pd
@@ -17,61 +12,33 @@ from astropy.io    import fits
 from astropy.io    import ascii
 from astropy.table import Table
 
-
-# In[3]:
-
-
+##
 ##  V H z Q    data
+##
 path     = '../data/'
 filename = 'LIST_OF_VHzQs.dat'
 table    = path+filename
 
 VHzQ_list = ascii.read(table)
 
-
-# In[4]:
-
-
+## Just a little bit of info 
 print('type(VHzQ_list)', type(VHzQ_list))
 print('len(VHzQ_list)',   len(VHzQ_list))
-
-
-# In[5]:
-
-
 VHzQ_list.colnames
-
-
-# In[6]:
-
 
 ## Column 'na' has the original survey designations
 len(np.unique(VHzQ_list['na']))
-
-
-# In[7]:
-
-
+#type(np.unique(VHzQ_list['na']))
 np.unique(VHzQ_list['na'])
 
-
-# In[8]:
-
-
-type(np.unique(VHzQ_list['na']))
-
-
-# In[9]:
-
-
-#VHzQ_list.group_by('na').size().sort_values(ascending=False)
+## Nice, cute way to pick out the survey and the number of
+## objects from that survey -- thanks @nudomarinero !!
 survey, counts = np.unique(VHzQ_list["na"], return_counts=True)
 
-
-# In[11]:
-
-
 ## Loop through the number of entries the variable 'survey' has
+print()
 for x in range(len(survey)):
     print('{:7} & {:4d}'.format(survey[x], counts[x]))
+print()
+    
 

### 2018-12-10 tex/WW4C_VHzQ.tex
Another decent update for SEDs, Nofz directory

@@
 
-At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
-i.e., in the $z$-band, while at
+The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
+sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
+for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
+cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.
+
+%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
 

### 2018-12-10 Lz/make_M1450.py

@@ -1,8 +1,8 @@
-
-# coding: utf-8
-
-# In[1]:
-
+'''
+Some good ol' Distance Modulus code that
+(will ultimately) take in the e.g. z, y or J-band photometry
+of the VHzQs and return an Absolute Magnitude M_1450 value.
+'''
 
 from astropy.io import fits
 from astropy.io import ascii
@@ -85,81 +85,25 @@ z_kcorr_zband, kcorr_Lusso15_zband = np.loadtxt(kcorr_path+'kcorrz_l15.dat', use
 ## d is the distance to the object in parsecs
 
 
-# In[8]:
-
-
 cosmo
-
-
-# In[9]:
-
-
 cosmo.luminosity_distance(4)
-
-
-# In[10]:
-
-
 cosmo.luminosity_distance(all_VHzQs['redshift'])
 
-
-# In[11]:
-
-
 d_Mpc = cosmo.luminosity_distance(all_VHzQs['redshift'])
-
-
-# In[12]:
-
-
 #d_Mpc.value
-
-
-# In[13]:
-
 
 kcorr = 0.0
 
 
-# In[14]:
-
-
 Abs_Mag = (all_VHzQs['mag'])  - (5.*(np.log10(d_Mpc.value))) - 25. + kcorr
-#Abs_Mag
-
-
-# In[15]:
 
 
 delta_mags = Abs_Mag - all_VHzQs['M1450'] 
 
 
-# In[16]:
-
-
-Abs_Mag[0]
-
-
-# In[17]:
-
-
-all_VHzQs[1]
-
-
-# In[18]:
-
-
-Abs_Mag[1]
-
-
-# In[19]:
-
-
 z_slope_in = (np.arange(800)/100)
 z_slope = -2.5*(np.log10(1+z_slope_in))
 
-
-# In[20]:
 
 
 fig, ax = plt.subplots()
@@ -167,7 +111,7 @@ ax.scatter(all_VHzQs['redshift'], Abs_Mag, marker='.')
 ymin = -20.5
 ymax = -34.0
 ax.set_ylim((ymin, ymax))
-
+plt.show()
 
 # In[21]:
 
@@ -191,7 +135,7 @@ ax.set_xlim((xmin, xmax))
 ymin = -2.5
 ymax = -0.0
 ax.set_ylim((ymin, ymax))
-
+plt.show()
 
 # In[26]:
 
[…]

### 2018-12-10 SEDs/filters_forM1450.py

@@ -1,0 +1,336 @@
+'''
+A wavelength vs. wide-area survey filters plot.
+For e.g. Pan-STARRS, UKIRT/UKIDSS, VISTA/VHS and WISE.
+
+To reproduce something akin to the Spectral Bands plot at::
+https://blog.backyardworlds.org/2018/04/24/guest-blog-post-by-peter-jalowiczor/
+
+Filter curves from e.g.
+http://www.mso.anu.edu.au/~brad/filters.html
+'''
+
+import matplotlib
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+
+##
+## READ-IN THE DATA FILE(S)
+##
+
+##
+## FILTERS
+path = '/cos_pc19a_npr/data/filter_curves/'
+
+##     D E C a m
+infile = 'DECam/DES_uband.dat'
+table = path+infile
+DES_uband      = ascii.read(table)
+DES_uband_wave = DES_uband['wavelength']
+DES_uband_thru = DES_uband['throughput']
+infile = 'DECam/DES_gband.dat'
+table = path+infile
+DES_gband      = ascii.read(table)
+DES_gband_wave = DES_gband['wavelength']
+DES_gband_thru = DES_gband['throughput']
+infile = 'DECam/DES_rband.dat'
+table = path+infile
+DES_rband      = ascii.read(table)
+DES_rband_wave = DES_rband['wavelength']
+DES_rband_thru = DES_rband['throughput']
+infile = 'DECam/DES_iband.dat'
+table = path+infile
+DES_iband      = ascii.read(table)
+DES_iband_wave = DES_iband['wavelength']
+DES_iband_thru = DES_iband['throughput']
+infile = 'DECam/DES_zband.dat'
+table = path+infile
+DES_zband      = ascii.read(table)
+DES_zband_wave = DES_zband['wavelength']
+DES_zband_thru = DES_zband['throughput']
+infile = 'DECam/DES_Yband.dat'
+table = path+infile
[…]

### 2018-12-11 tex/WW4C_VHzQ.tex
tex/WW4C_VHzQ updated

@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
   \centering
@@
 \subsection{MIR data}
-The MIR data for this study comes exclusively from the Wide-field
-Infrared Survey Explorer (WISE) mission. Since we are only concerned
-here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
-exploration of the VH$z$Q population in e.g. the large Spitzer areal
-surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
-][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
-\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
-\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
-include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.
-
-We use data from the the beginning of the WISE mission \citep[2010
-January; ][]{Wright2010} through the fourth-year of NEOWISE-R
-operations \citep[2017 December;]{Mainzer2011}. More specifically, we
-use the data from the
+Since we are concerned here with the very large area ($\gg1000$ deg$^2$) surveys, we leave exploration of the VH$z$Q population in e.g.
+the large Spitzer areal surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES; ][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey \citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field \citep[SSDF; ][]{Ashby2013}, to future investigation.
+This will also include a detailed study of MIR spectra e.g.
+\citet{Lambrides2018}.
+
+The MIR data for this study comes exclusively from the Wide-field Infrared Survey Explorer (WISE) mission. 
 \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
@@
 
-The WISE scan pattern leads to coverage of the full- sky approximately
-once every six months (a``sky pass''), but the satellite was placed in
-hibernation in 2011 February and then reactivated in 2013
-October. Hence, our light curves have a cadence of 6 months with a 32
-month sampling gap.
+We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.
+More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}.
+The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+{\bf Few more words here on the unWISE catalog}.
+
+All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux.
+The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}.
+This inheritance depends on details of the PSF normalization at large radii, which is uncertain.
+Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
+
+Thus to convert unWISE Vega magnitudes onto the AB system, we have,   
+\begin{eqnarray*}
+        W1_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{W1}) - 0.004 + 2.699 \\
+        W2_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{W2}) - 0.032 + 3.339 
+\end{eqnarray*}
+%those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
+These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
+%We note though that 
+%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
+%- what the source of the trend is,
+%- which of unWISE and AllWISE is correct, or
+%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
+
+The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October.
+Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
 

### 2018-12-11 SEDs/filters_vs_QSOstars.py

@@ -22,14 +22,14 @@ from astropy.table import Table
 
 
 ##
-## READ-IN THE DATA FILE(S)
+##   READ-IN THE DATA FILE(S)
 ##
 
 ##
-## FILTERS
+##   FILTERS
 path = '/cos_pc19a_npr/data/filter_curves/'
 
-##     D E C a m
+##   D E C a m
 infile = 'DECam/DES_uband.dat'
 table = path+infile
 DES_uband      = ascii.read(table)
@@ -113,7 +113,6 @@ TwoMASS_Ksband      = ascii.read(table)
 TwoMASS_Ksband_wave = TwoMASS_Ksband['wavelength']
 TwoMASS_Ksband_thru = TwoMASS_Ksband['throughput']
 
-
 ##     WISE
 infile = 'WISE/RSR-W1.txt'
 table = path+infile
@@ -137,7 +136,7 @@ W4_band_wave = W4_band['W4']
 W4_band_thru = W4_band['RSR']
 
 ## 
-## Composite quasar spectra
+##  Composite quasar spectra
 ##
 ## The Vanden Berk et al. (2001) composite
 path = '/cos_pc19a_npr/data/SDSS/VdB01/'
@@ -147,7 +146,7 @@ VdB01_comp = ascii.read(table)
 VdB01_wave = VdB01_comp['Wavelength']
 VdB01_flux = VdB01_comp['Flux']
 
-## The Banados_2016_Table6 composite
+## The Banados et al. (2016) Table 6 composite
 path = '/cos_pc19a_npr/data/highest_z_QSOs/Banados_Tables/'
 infile = 'Banados_2016_Table6.dat'
 table = path+infile
@@ -156,7 +155,8 @@ Banados_wave        = Banados_2016_full['Wavelength']
 Banados_comp_flux   = Banados_2016_full['Flux_comp']
 Banados_strong_flux = Banados_2016_full['Flux_strong']
 Banados_weak_flux   = Banados_2016_full['Flux_weak']
-##
+
+## Glikman et al. (2006) Red/NIR composite
 path = '/cos_pc19a_npr/data/Glikman2006/'
 infile = 'Glikman_2006_ApJ_Table3.dat'
 table = path+infile
@@ -166,7 +166,7 @@ Glik_flux = Glikman_comp['Flux']
 Glik_flux = Glik_flux/Glik_flux.max()
 
 ##
-## L/T dwarf spectra; Cushing et al. (2008; ApJ, 678, 1372)
[…]

### 2018-12-11 tex/WW4C_VHzQ.tex
Big update with Nofz plots

@@
 ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
-all 424 spectroscopically confirmed redshift $z\geq5.00$ quasars.
+all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
 Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
@@
 This paper is organized as follows.  In Section 2, we present the
-assembled list of the 424 $z\geq5.00$ VH$z$Qs that we have
+assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
 compiled. We then give a high-level overview of the photometric
@@
 \subsection{Spectroscopy} 
-We have obtained a list of 424 spectroscopically confirmed 
-quasars with redshifts $z\geq5.00$.
-
-In Table~\ref{tab:THE_TABLE}  we give the discovery reference for the
-VH$z$Qs noting that some objects were discovered independently and
-contemporaneously.  The redshifts for the VH$z$Qs generally come from
-the measurement of broad UV/optical emission lines. Where 
-there are far infra-red emission lines e.g. \cii~158 micron, we report 
-these, but at the level of our current analysis broadline redshifts are
-sufficient.
-
+We have obtained a list of 463 spectroscopically confirmed quasars
+with redshifts $z\geq5.00$. We use all the $z\geq5.00$ quasars that
+have been discovered and spectroscopically confirmed as of the time of
+writing (2018 November).
+
+This list was complied from a range of surveys and papers. 
 Specifically, we use data from: 
@@
 \citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
-\citet{Willott2007, Willott2009, Willott2010a, Willott2010b, Willott2013b, Willott2015}, 
+\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
 \citet{Wu2015} 
@@
 \citet{Zeimann2011}, 
-
-Table~\ref{tab:THE_TABLE} gives the salient details for the objects
-used in this study. We use all the $z\geq5.00$ quasars that have been
-discovered and spectroscopically confirmed as of the time of writing
-(2018 November). We report near-infrared ($yYJHK$-bands) and
-mid-infrared (WISE W1/2/3/4) photometry.
-% and give our caculcated $M_{1450}$.
+The breakdown of how many VH$z$Q each survey reports is given in
+Table~\ref{tab:surveys}. We assume the reader is familiar with the
+Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in
+Table~\ref{tab:surveys}.  ) survey and these surveys alone identified
+over half (54.6\%) of the VH$z$Q population. Data from the
+Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for
+13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
+combination of surveys is also vital for identifying VH$z$Qs. The
+UKIDSS Large Area Survey (ULAS) on its own, or in combination with
+other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
+including the highest-$z$ object. Where more than one survey is used
+for the high-redshift identification (e.g. via shorter-band veto and
+longer wavelength detection) we follow the discovery paper naming
+convention.
 
 \begin{table}
-\begin{tabular}{l r l}
+\begin{tabular}{l r r l}
 \hline  \hline
-Survey              & \# VH$z$Qs & Notes/Survey reference  \\
+Survey              & \# VH$z$Qs & (\%) & Notes/Survey reference  \\
 \hline  
-  ATLAS             &     4       &  \citet{Shanks2015} \\
-  CFHQS            &   20       &  \citet{Willott2007} \\
-  DELS               &   16       &  \citet{Dey2018} \\
-  ELAIS              &     1       &  \citet{Vaisanen2000} \\
-  FIRST              &     1       &  \citet{Becker1995} \\
-  HSC                 &    8        & \citet{Miyazaki2018} \\
-  IMS                 &     5        &  \citet{Kim2015} \\
-  MMT               &   12        &  \citet{McGreer2013} \\
-  NDWFS           &     1         &  \citet{JD1999} \\
-  PSO                 &   83         &   \citet{Kaiser2002, Kaiser2010} \\
-  RD                   &     1         &  \citet{Mahabal2005} \\
-  SDSS                &  170         & \citet{EDR} \\
-  SDUV$^{a}$       &   20         & \citet{YangJ2017} \\
- SDWISE$^{b}$    &   27         &   \citet{WangF2016} \\
-%  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
-  SHELLQs         &    55         &  \citet{Matsuoka2016}     \\  
-  UHS               &    1            &  \citet{Fan2018} \\
-  ULAS               &   10          & \citet{Lawrence2007} \\
-  VDES$^{c}$              &   17          &  \citet{Reed2017} \\
-  VIK                 &     9          &  \citet{Edge2013} \\
-  VIMOS           &    1            &   \citet{LeFevre2003} \\
+  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
+  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
+  DELS               &   16    &   ( 3.46)    &  \citet{Dey2018} \\
+  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
+  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
+  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
+  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
+  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
+  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
+  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
+  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
+  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
+ SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
+%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
+  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
+  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
+  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
+  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
+  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
+  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
+  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
+  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
 \hline  \hline
@@
 \caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference.  
-  $^{a}$SDUV  = SDSS+ULAS+VHS; 
+  Recent survey name and acronyms include: 
+  $^{a}$DESI Legacy Imaging Survey; 
   $^{b}$SDWISE = SDSS+WISE; 
+  $^{a}$SUV  = SDSS-ULAS/VHS; 
   $^{c}$VDES = VHS/VIKING+DES; 
@@
 \end{table}
+
+\begin{figure}
+%%trim=l b r t
+  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/Nofz/Nofz_0pnt075bins_20181211.png}
+  \centering
+  \vspace{-12pt}
+  \caption[]
+  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
+    The bins are $\detla-z=0.075$ in width. }
+  \label{fig:Nofz}
+\end{figure}
+
+The redshifts for the VH$z$Qs generally come from the measurement of
+broad UV/optical emission lines. Where there are far infra-red
+emission lines e.g. \cii~158 micron, we report these, but at the level
+of our current analysis broadline redshifts are sufficient.
+
+\begin{table}
+\centering
+\begin{tabular}{l r  r}
+\hline \hline
+$z \geq$  & Age / Myr & No. of objects \\
+\hline 
+7.50         &    700         &   1   \\
+7.00         &    767         &   4   \\
+6.78         &    800         &  14   \\
+6.50         &    845         &  40   \\
+6.19         &   900          &  86   \\
+6.00         &   937          &  170   \\
+5.70         & 1000          &  267   \\
+5.00         & 1180          &  463   \\
+\hline \hline
+\end{tabular}
+\caption{The number of objects at or above a given redshift. 
+The age of the Universe in megayears is also given. }
+      \label{tab:ages}
+\end{table}
+
+The number of objects at or above various redshifts, along with the 
+corresponding age of the Universe is given in Table~\ref{tab:ages}.
+
+The $N(z)$ redshift histogram is given for the sample in Figure~\ref{fig:Nofz}. 
+We split the contribution up by survey. For clarity we show the individual 
+surveys of SDSS, PS1, HSC, the ULAS detection, and tally the remaining 
+surveys together (``various''). In Section~\ref{sec:Lz} we discuss the form 
+of the $N(z)$ as well as the coverage of the luminosity-redshift $L-z$ plane.
 
@@
 We query and return the mean PSF magnitudes from the $grizy$ filters
-({\tt MeanPSFMag}) which are in the AB system for our 424 VH$z$Q
+({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q
 sample. Details of our SQL and links to the main tables are given in
@@
 We query the WSA and VSA performing matched-aperature photometry at
-the positions of our 424 VH$z$Qs. This database is world-readable and we give the full receipe
+the positions of our 463 VH$z$Qs. This database is world-readable and we give the full receipe
 and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.
@@
 \section{Results}
-Having collated the sample of 424 VH$z$Qs, and obtained their optical,
+Having collated the sample of 463 VH$z$Qs, and obtained their optical,
 near- and mid-infrared photometry we report here the various
@@
     ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-    out catalogue of 424 VH$z$Qs with these catalogues, produces 
+    out catalogue of 463 VH$z$Qs with these catalogues, produces 
     42 matches with	the R90 sample and 98 matches with the C75 sample. 

### 2018-12-11 Nofz/Nofz.py

@@ -25,36 +25,24 @@ ATLAS   &    4     CFHQS   &   20     DELS    &   16
 ELAIS   &    1     FIRST   &    1     HSC     &    8
 IMS     &    5     MMT     &   12     NDWFS   &    1
 PSO     &   83     RD      &    1     SDSS    &  170
-SDUV    &   20     SDWISE  &   27     SHELLQs &   55
+SDWISE  &   27     SHELLQs &   55     SUV     &   20     
 UHS     &    1     ULAS    &   10     VDES    &   17
 VHS     &    1     VIK     &    9     VIMOS   &    1
 '''
 
 ## Make a separate list for each airline
-ATLAS  = list(VHzQs[VHzQs['na'] == 'ATLAS']['redshift'])      ## 4
-CFHQS  = list(VHzQs[VHzQs['na'] == 'CFHQS']['redshift'])      ## 20
-DELS   = list(VHzQs[VHzQs['na'] == 'DELS']['redshift'])       ## 16
 HSC    = list(VHzQs[(VHzQs['na'] == 'HSC') | (VHzQs['na'] == 'SHELLQs')]['redshift'])    ## 63
-IMS    = list(VHzQs[VHzQs['na'] == 'IMS']['redshift'])       ##  5
-MMT    = list(VHzQs[VHzQs['na'] == 'MMT']['redshift'])       ## 12
 PSO    = list(VHzQs[VHzQs['na'] == 'PSO']['redshift'])        
 SDSS   = list(VHzQs[VHzQs['na'] == 'SDSS']['redshift'])
-
-
-SDUV   = list(VHzQs[VHzQs['na'] == 'SDUV']['redshift'])
-SDWISE = list(VHzQs[VHzQs['na'] == 'SDWISE']['redshift'])
-SDplus = list(VHzQs[(VHzQs['na'] == 'SDUV') | (VHzQs['na'] == 'SDWISE')]['redshift']) 
-
-VDES   = list(VHzQs[VHzQs['na'] == 'VDES']['redshift'])
-ULAS   = list(VHzQs[VHzQs['na'] == 'ULAS']['redshift'])  
-VIK    = list(VHzQs[VHzQs['na'] == 'VIK']['redshift'])  
+ULASES = list(VHzQs[(VHzQs['na'] == 'ULAS') | (VHzQs['na'] == 'SUV')]['redshift']) 
 
 ## ELAIS+FIRST+NDWFS+RD+UHS+VHS+VIMOS
[…]

### 2018-12-11 tables_for_paper/survey_origin.py

@@ -23,7 +23,7 @@ VHzQ_list = ascii.read(table)
 
 ## Just a little bit of info 
 print('type(VHzQ_list)', type(VHzQ_list))
-print('len(VHzQ_list)',   len(VHzQ_list))
+
 VHzQ_list.colnames
 
 ## Column 'na' has the original survey designations
@@ -35,10 +35,13 @@ np.unique(VHzQ_list['na'])
 ## objects from that survey -- thanks @nudomarinero !!
 survey, counts = np.unique(VHzQ_list["na"], return_counts=True)
 
+percent_count = 0.00
 ## Loop through the number of entries the variable 'survey' has
 print()
 for x in range(len(survey)):
-    print('{:7} & {:4d}'.format(survey[x], counts[x]))
-print()
+    print('{:7}  &  {:4d}  &  ({:5.2f})'.format(survey[x], counts[x], (counts[x]/463.*100) )) 
+    percent_count = percent_count + (counts[x]/463.*100)
     
-
+print()
+print('...for a total of ', len(VHzQ_list), ' VHzQs (at ', percent_count,'%)')
+print()

### 2018-12-11 Nofz/Nofz_v1pnt00.py
Big update with Nofz plots, part 2

@@ -1,0 +1,153 @@
+'''
+Pretty simple wee bit of code to look at the N(z) of the VHzQs.
+   h/t to https://towardsdatascience.com/histograms-and-density-plots-in-python-f6bda88f5ac0
+          https://towardsdatascience.com/histograms-and-density-plots-in-python-f6bda88f5ac0
+          https://github.com/WillKoehrsen/Data-Analysis/blob/master/univariate_dist/Histogram%20and%20Density%20Plot.ipynb
+''' 
+
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+from matplotlib.patches import Rectangle
+from matplotlib         import colors as mcolors
+
+from astropy.io import ascii
+from astropy.io import fits
+
+
+datapath = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
+datafile = 'LIST_OF_VHzQs.dat'
+VHzQs = ascii.read(datapath+datafile)
+
+'''
+ATLAS   &    4     CFHQS   &   20     DELS    &   16 
+ELAIS   &    1     FIRST   &    1     HSC     &    8
+IMS     &    5     MMT     &   12     NDWFS   &    1
+PSO     &   83     RD      &    1     SDSS    &  170
+SDUV    &   20     SDWISE  &   27     SHELLQs &   55
+UHS     &    1     ULAS    &   10     VDES    &   17
+VHS     &    1     VIK     &    9     VIMOS   &    1
+'''
+
+## Make a separate list for each airline
+ATLAS  = list(VHzQs[VHzQs['na'] == 'ATLAS']['redshift'])      ## 4
+CFHQS  = list(VHzQs[VHzQs['na'] == 'CFHQS']['redshift'])      ## 20
+DELS   = list(VHzQs[VHzQs['na'] == 'DELS']['redshift'])       ## 16
+HSC    = list(VHzQs[(VHzQs['na'] == 'HSC') | (VHzQs['na'] == 'SHELLQs')]['redshift'])    ## 63
+IMS    = list(VHzQs[VHzQs['na'] == 'IMS']['redshift'])       ##  5
+MMT    = list(VHzQs[VHzQs['na'] == 'MMT']['redshift'])       ## 12
[…]

### 2018-12-14 tex/WW4C_VHzQ.tex
tex/WW4C_VHzQ update
continued updates

@@
 Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide
-range of optical, NIR and MIR filters. We use a flat $\Lambda$CDM
-cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$,
-and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in
-order to be consistent with \citet{Banados2016}.
+range of optical, NIR and MIR filters.
+
+We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
+2016) in order to be consistent with \citet{Banados2016} and all logarithms are to the
+base 10.
 
@@
 \section{Data}
-In Table~\ref{tab:THE_TABLE} we present our dataset and we have
-assembled this in the following manner.  First we compile the list of
-all known, spectroscopically confirmed quasars from the
-literature. Most of these objects are easily identified by their broad
-Ly$\alpha$ emission line, \nv emission and characteristic shape
-blueward of 1215\AA\ in the rest-frame. As we shall see, some of the
-more recently discovered objects are close to the galaxy luminosity
-function characteristic luminosity $M^{*}$, and some have relatively
-weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
-7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into spectral features and line strengths, and take as
-given the published spectra and identifications.
-
-We then obtain optical, near-infrared and mid-infrared photometry for
-the spectral dataset. The optical data comes from the Panoramic Survey
-Telescope and Rapid Response System (Pan-STARRS) survey
-\citep{Chambers2016}. The near-infrared data comes from two sources:
-first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but
-not exclusively, as part of the UKIRT Infrared Deep Sky Survey
-\citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on
-the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared,
-$\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared
-Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-
-For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
-of the filters in question.
-
+First we compile the list of all known, spectroscopically confirmed quasars from the literature.
+Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
+As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
+Figures 7 and 10 in][]{Banados2016}.
+We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and reshift identifications.
+
+We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
+The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}.
+The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
+And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}.
+The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+%%
+For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
+
+Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.  
 \input{THE_TABLE_v0pnt96_TOP10_betterformat}
@@
 \citet{Ikeda2017}, 
-\citet{Jiang2008, Jiang2009, Jiang2015},  
+\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
 \citet{Kashikawa2015}, 
@@
 \end{tabular}
-\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference.  
+\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
   Recent survey name and acronyms include: 
@@
   {The redshift distribution $N(z)$ of the VH$z$Q sample. 
-    The bins are $\detla-z=0.075$ in width. }
+    The bins are $\delta-z=0.075$ in width. }
   \label{fig:Nofz}
@@
 %\subsubsection{Pan-STARRS1 (PS1)} 
-We query the Panoramic Survey Telescope and Rapid Response System
-(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
-Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
-service at
-\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The
-Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of
-declination $-30$ degrees in five filters $grizy$.  PS1 is the first
-part of Pan-STARRS to be completed and is the basis for the DR1.
-\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016},
-\citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016}
-describe the instrument, survey, and data analyses.  The principal
-science product of the PS1 survey is the catalog accessible through
-the CasJobs interface.
-
-We query and return the mean PSF magnitudes from the $grizy$ filters
-({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q
-sample. Details of our SQL and links to the main tables are given in
-Appendix~\ref{sec:PS1_SQL}.
+We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
+The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.
+PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1.
+\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.
+The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.
+
+We query and return the mean PSF magnitudes from the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q sample.
+Details of our SQL and links to the main tables are given in Appendix~\ref{sec:PS1_SQL}.
 
@@
 
-The MIR data for this study comes exclusively from the Wide-field Infrared Survey Explorer (WISE) mission. 
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
-program and catalogue, which combines data from the WISE cryogenic and
-NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
-phases. For the our variability investigations, we supplement the
-ALLWISE data with data from the
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
-2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
-(W1 and W2) single-exposure images and extracted source information
-that were acquired between 2016 December 13 and 2017 December 13 UTC,
-which was the fourth year of survey operations of the Near-Earth
-Object Wide-field Infrared Survey Explorer Reactivation Mission
-(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
-data products are concatenated with those from the first three years
-(originally released on March 26, 2015, March 23, 2016 and June 1,
-2017) into a single archive.
+The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and NEOWISE (Mainzer et al.
+2011 ApJ, 731, 53) post-cryogenic survey phases.
 
@@
 
-Thus to convert unWISE Vega magnitudes onto the AB system, we have,   
+Thus to convert unWISE Vega magnitudes onto the AB system, we have    
 \begin{eqnarray*}
-        W1_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{W1}) - 0.004 + 2.699 \\
-        W2_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{W2}) - 0.032 + 3.339 
+        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
+        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339 
 \end{eqnarray*}
-%those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
+%Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
+those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
 These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
@@
 %- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
+
+For the our MIR variability investigations, we do not use the unWISE coadds, but instead use 
+the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE 2018 Data Release}.
+NEOWISE 2018 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired between 2016 December 13 and 2017 December 13 UTC, which was the fourth year of survey operations of the Near-Earth Object Wide-field Infrared Survey Explorer Reactivation Mission (NEOWISE; Mainzer et al.
+2014, ApJ, 792, 30).
+The fourth year NEOWISE data products are concatenated with those from the first three years into a single archive.
 
@@
       \end{tabular}
-      \caption{ATLAS \citet{Shanks2015}; }
+      \caption{}
       \label{tab:mir_detection}
@@
 \subsection{Colours}
-Currently, very high-redshift quasars are identified by their morphology, flux and colours in 
-optical and infrared imaging data \citet{Fan1999, Mortlock2012}
-Quasars are generally selected to be point sources, but 
-be outliers from the stellar locus in colour space. For VH$z$Qs, the main technique is to 
-look for objects with extreme optical-to-near-infrared colours
-The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
-
-Pellentesque vel elit neque, in interdum lacus.
-Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a nisl.
-Ut sit amet sapien a risus dapibus sagittis.
-Cras sed ultricies erat.
-Donec id metus sed urna lacinia convallis vel sed enim.
-Proin nisi libero, ornare vel bibendum eu, sollicitudin sed leo.
-Cras tincidunt aliquet ultricies.
-Cras pretium velit leo, in malesuada enim.
-Duis sagittis ultricies interdum.
-Proin sit amet sem nec metus feugiat pharetra.
+Currently, very high-redshift quasars are identified by their morphology, flux and colours in optical and infrared imaging data \citet{Fan1999, Mortlock2012} Quasars are generally selected to be point sources, but  be outliers from the stellar locus in colour space.
+For VH$z$Qs, the main technique is to look for objects with extreme optical-to-near-infrared colours The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
 
@@
 colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
-
 \begin{figure*}
@@
 
-Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
-colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
 \begin{figure*}
@@
 we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
-sample and in particulare the absolute magnitude at rest-frame 1450\AA'\, $M_{1450}$, 
+sample and in particulare the absolute magnitude at rest-frame 1450\AA\ , $M_{1450}$, 
 which is a key physical quantity and goes directly towards the quasar luminosity 
 function and thus the reionization of hydrogen calculation.
+
+We calculate the Distance Modulus in the normal fashion, 
+\begin{equation}
+m_{1450} - M_{1450} = 5 \log \left (    \frac{ D_{\rm L}(z)}{\rm Mpc}  \right )  + 25 + K_{\rm corr}(X,z)
+\end{equation}
+where $m_{1450}$ is the apparent magnitude at 1450\AA\ ,  
+%$M_{1450}$ is the absolute magnitude at 1450 \AA\ , 
+$D_{\rm L}(z)$ is the luminosity distance and 
+$K_{\rm corr}(X,z)$ is the $K$-correction which corrects for the effects of redshifting of the bandpass and the spectrum.
+
+The $m_{1450}$ apparent magnitude is derived from the $z-$, $y/Y-$ or $J-$band photometery.
 
@@
 
+\citet{Ross2013} has a detailed discussion of the $K$-correction (see that papers' Appendix B). 
+The key result in that paper is, if quasars are described as having a power-law slope, 
+$\alpha^{\nu}$ in spectral flux density, i.e., $f_\nu(\nu) \propto \nu^{\alpha_{\nu}}$ (as is conventional) 
+then 
+\begin{equation}
+K_{\rm corr}(z) = -2.5 (1 + \alpha_{\nu}) \log[1 + z].
+\end{equation}
+Here the $[-2.5 \log(1 + z)]$ term corrects for the effective narrowing of the filter width with redshift, (the ``bandpass correction'') and the $[-2.5 \alpha^{\nu} \log(1 + z)]$ term takes into account the spectral index correction.
+The bandpass correction is approximately $\approx -1.945$ at redshift $z=5$ decreasing to $-2.32$ at redshift $z=7.50$.
+
 %At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
@@
 
+\iffalse
 \subsection{SEDs and Dust properties of the VH$z$Qs}
@@
 \end{figure*}
+\fi
 
@@
 initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
-
+%%
 N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
+%%
 
 \subsection*{Availability of Data and computer analysis codes} 
-All materials, data, code and analysis algorithms are fully 
-available at: 
+All materials, databases, data tables and code are fully available at: 
 \href{https://github.com/d80b2t/VHzQ}{\tt https://github.com/d80b2t/VHzQ}

### 2018-12-14 data/AllWISE/make_IRSA_table.py
data AllWISE directory added

@@ -1,0 +1,33 @@
+'''
+A simple little bit of code to make the IPAC table for uploading to
+the IRSA WISE website.
+
+IPAC Table Validator:: 
+https://irsa.ipac.caltech.edu/applications/TblValidator/
+
+v1.00    Fri Dec 14 16:59:29 GMT 2018
+'''
+
+import numpy as np
+import pandas as pd
+
+from astropy.io    import fits
+from astropy.io    import ascii
+from astropy.table import Table
+
+##
+##  V H z Q    data
+##
+path     = '../'
+filename = 'LIST_OF_VHzQs.dat'
+table    = path+filename
+
+VHzQ_list = ascii.read(table)
+
+## Just a little bit of info 
+print('type(VHzQ_list)', type(VHzQ_list))
+
+VHzQ_list.colnames
+
+data = [VHzQ_list['ra'], VHzQ_list['dec']]
+ascii.write(data, 'VHzQs463_4IPAC_temp.tbl', format='ipac')

### 2018-12-14 data/AllWISE/match_unWISE_AllWISE.py

@@ -1,0 +1,49 @@
+'''
+Comparing the unWISE and the AllWISE detections.
+Takes advatage of the fact that the AllWISE catalogs
+return a number list of objects, missing out those
+non-detections. 
+
+'''
+
+
+import numpy as np
+from astropy.io import ascii
+from astropy.io import fits
+
+## `Super-set' of VHzQs, and not of these will be unWISE detections
+VHzQs = ascii.read("VHzQs463_unWISE_v1pnt00.dat")
+
+## AllWISE data.
+allwise = ascii.read("VHzQs463_AllWISE_W1234.tbl")
+
+
+f = open('output_temp.dat', 'w')
+
+print('#RA           Dec   redshift  unW1_mag unW1_magerr unW1_snr  w1mpro w1sigmpro  w1snr  ', file=f)
+## loop over the full VHzQs list...
+for ii in range(len(VHzQs['count'])):
+    #print(VHzQs['RA'][ii])
+    #print('unw, {: 4d} {: 14.8f} {: 14.8f}'.format(VHzQs['count'][ii], VHzQs['RA'][ii], VHzQs['Dec'][ii]))
+
+    matched = 0
+    ## Now loop over the list of AllWISE objects
+    for jj in range(len(allwise['cntr_01'])):
+
+        ## Check to see if List 1 = List 2...
+        if VHzQs['count'][ii] == allwise['cntr_01'][jj]:
+            print('{:11.7f} {:11.7f} {: 5.3f}   {:8.4f} {:8.4f} {:8.4f}  {: 8.3f} {: 7.2f} {: 6.1f}'.format(
+                VHzQs['RA'][ii], VHzQs['Dec'][ii], VHzQs['redshift'][ii],
+                VHzQs['unW1_mag'][ii], VHzQs['unW1_magerr'][ii], VHzQs['unW1_snr'][ii], 
+                allwise['w1mpro'][jj], allwise['w1sigmpro'][jj], allwise['w1snr'][jj]), 
+                file=f)
+            matched = 1
+
+    if matched == 0:
+        print('{:11.7f} {:11.7f} {: 5.3f}   {:8.4f} {:8.4f} {:8.4f}  {:8.3f} {:7.2f} {:6.1f}'.format(
+                VHzQs['RA'][ii], VHzQs['Dec'][ii], VHzQs['redshift'][ii], 
[…]

### 2018-12-20 tex/WW4C_VHzQ.tex
tex tables re-arrange
tex/WW4C_VHzQ update

@@
 Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
-\input{THE_TABLE_v0pnt96_TOP10_betterformat}
+
+\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+
+%\input{table_tex/THE_TABLE_v0pnt96_TOP10_redshifts}
+%\input{table_tex/THE_TABLE_v0pnt96_TOP10_NIR}
+%\input{table_tex/THE_TABLE_v0pnt96_TOP10_MIR}
 
@@
     WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
+
+    \subsubsection{Salient details of WSA and VSA}. 
+    %% N.B.!!!    WFAU archives more than just the NIR Surveys -- it archives *all* the WFCAM and VISTA programmes!!
+    In this study, we are not just quering the WSA or VSA data tables. 
+    We are taking a list of objects (positions) are performing matched aperature (``forced'') photometry on the NIR imaging data. 
+    As such, we generate a set of tables that are different in subtle ways to the regular ``Detection'' tables.
+
+    The two most important tables for our needs are the {\tt [w/v]serv1000MapRemeasurement} and {\tt [w/v]serv1000MapRemeasAver}.
+
+    Full documentation can be found at the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema Browser} 
+and the \href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema Browser}.
 

### 2019-02-10 light_curves/J110057_lightcurve_4paper.py
light_curves/ added (big update)

@@ -1,0 +1,290 @@
+'''
+Why doesn't matplotlib look as good as SM??!!!
+http://space.mit.edu/home/turnerm/python.html
+'''
+
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+#import image
+
+from matplotlib import colors as mcolors
+from astropy.io import ascii
+
+path = '/cos_pc19a_npr/data/J110057/photometry/'
+
+
+##
+##  P h o t o m e t r y    d a t a
+##
+## CRTS
+CRTS = ascii.read(path+'CRTS_LC.dat')
+## LINEAR
+LINEAR = ascii.read(path+'LINEAR_full.dat')
+
+## SSA - SuperCOSMOS Science Archive
+## For the Declination of your object, the plates scanned by SuperCOSMOS were UK-J, POSSI-e, UK-R, UK-I
+
+UK_J    = ascii.read(path+'SSA_UK-J.dat')
+POSSI_e = ascii.read(path+'SSA_POSS_Red1.dat')
+UK_R    = ascii.read(path+'SSA_UK-R_Red2.dat')
+UK_I    = ascii.read(path+'SSA_UK-I.dat')
+
+UK_J_mjd  =  UK_J['mjd']
+POSS_mjd  =  POSSI_e['mjd']         ## 1955, April
+UK_R_mjd  =  UK_R['mjd']
+UK_I_mjd  =  UK_I['mjd']
+
+## sCorMag's in Vega. 
+## https://www.astro.umd.edu/~ssm/ASTR620/mags.html
+## assume:
+##   UK-J ~ g;  POSSI_e and UK_R ~ r and UK_I ~ i
+SSA_B_AB  =  UK_J['sCorMagB']     - 0.103
+SSA_R1_AB =  POSSI_e['sCorMagR1'] + 0.146
+SSA_R2_AB =  UK_R['sCorMagR2']    + 0.146
+SSA_I_AB  =  UK_I['sCorMagI']     + 0.366
+
+## Pan-STARRS
+PS_g = ascii.read(path+'PanSTARRS_LC_g.dat')
+PS_r = ascii.read(path+'PanSTARRS_LC_r.dat')
+PS_i = ascii.read(path+'PanSTARRS_LC_i.dat')
+PS_z = ascii.read(path+'PanSTARRS_LC_z.dat')
+PS_y = ascii.read(path+'PanSTARRS_LC_y.dat')
+
+## SDSS 
[…]

### 2019-02-10 light_curves/MIR_LCs/NEOWISER_LCs_2cols.py

@@ -1,0 +1,122 @@
+'''
+http://blog.marmakoide.org/?p=94
+'''
+
+from astropy.io import ascii
+from matplotlib import pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+
+import numpy as np
+import random
+
+path='/cos_pc19a_npr/data/highest_z_QSOs/'
+file = 'NEOWISER-R_SingleExposure_L1bs.tbl'
+
+data = ascii.read(path+file) 
+type(data)
+upto_this = data['cntr_01'].max()
+
+out_pdf = 'NEOWISER_LCs_VHzQs_temp.pdf'
+pdf_pages = PdfPages(out_pdf)
+
+
+ALLWISE_MJD_min = 55210.     #  2010-January-14 
+ALLWISE_MJD_max = 55593.
+ALLWISE_MJD_mid = ((ALLWISE_MJD_max + ALLWISE_MJD_min))/2.
+mjd_range_ALLWISE=[ALLWISE_MJD_min,ALLWISE_MJD_max]
+
+
+## define the colormap
+cmap = plt.cm.inferno_r
+
+ls       = 'solid'
+lw       = 2.0
+ms       = 60.
+ms_large = ms*5.
+fontsize = 24
+alpha    = 1.00
+plot_num = 321
+totes    = 0
+
+for x in range(upto_this):
+#for x in range(10):
+    x=x+1
+    data_one = data[np.where(data['cntr_01'] == x)]
+
+    if len(data_one) < 1:
+          print('0')
+          
+    if len(data_one) > 0:  
+#        print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
+        print(len(data_one))
+        totes = totes + len(data_one)
+        ra = data_one['ra'][0]
+        dec = data_one['dec'][0]
+
+        ## Setting up a 3 panel, "triptych" style plot
+        fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(21.5, 8.5), gridspec_kw = {'width_ratios':[2, 1]}) # inches
+        #ax1 = plt.subplot(131, figsize=(12.0, 8.5) )
+        #ax2 = plt.subplot(132, figsize=(5.0, 8.5))
+
+        left   = 0.06   # the left side of the subplots of the figure
+        right  = 0.98   # the right side of the subplots of the figure
+        bottom = 0.10   # the bottom of the subplots of the figure
+        top    = 0.94   # the top of the subplots of the figure
[…]

### 2019-02-10 light_curves/MIR_LCs/NEOWISER_LCs_2rows.py

@@ -1,0 +1,141 @@
+'''
+http://blog.marmakoide.org/?p=94
+'''
+
+from astropy.io import ascii
+from matplotlib import pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+
+import numpy as np
+import random
+
+path='/cos_pc19a_npr/data/highest_z_QSOs/'
+file = 'NEOWISER-R_SingleExposure_L1bs.tbl'
+
+data = ascii.read(path+file) 
+type(data)
+upto_this = data['cntr_01'].max()
+
+out_pdf = 'NEOWISER_LCs_VHzQs_temp.pdf'
+pdf_pages = PdfPages(out_pdf)
+
+
+ALLWISE_MJD_min = 55210.     #  2010-January-14 
+ALLWISE_MJD_max = 55593.
+ALLWISE_MJD_mid = ((ALLWISE_MJD_max + ALLWISE_MJD_min))/2.
+mjd_range_ALLWISE=[ALLWISE_MJD_min,ALLWISE_MJD_max]
+
+
+## define the colormap
+plt.style.use('dark_background')
+cmap = plt.cm.inferno_r
+
+ls       = 'solid'
+lw       = 2.0
+s        = 60.
+s_large  = s*5.
+ms       = 6.0
+fontsize = 24
+alpha    = 1.00
+plot_num = 321
+totes    = 0
+
+for x in range(upto_this):
+#for x in range(10):
+    x=x+1
+    data_one = data[np.where(data['cntr_01'] == x)]
+
+    if len(data_one) < 1:
+          print('0')
+          
+    if len(data_one) > 0:  
+#        print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
+        print(len(data_one))
+        totes = totes + len(data_one)
+        ra = data_one['ra'][0]
+        dec = data_one['dec'][0]
+
+        ## Setting up a 3 panel, "triptych" style plot
+        fig, (ax1, ax2) = plt.subplots(2, 1, figsize=(14.0, 8.5),sharex=True, gridspec_kw = {'height_ratios':[5, 3]}) # inches
+        #ax1 = plt.subplot(131, figsize=(12.0, 8.5) )
+        #ax2 = plt.subplot(132, figsize=(5.0, 8.5))
+
+        left   = 0.10   # the left side of the subplots of the figure
+        right  = 0.98   # the right side of the subplots of the figure
+        bottom = 0.10   # the bottom of the subplots of the figure
[…]

### 2019-02-10 light_curves/lightcurve_plot.py

@@ -1,0 +1,207 @@
+'''
+Why doesn't matplotlib look as good as SM??!!!
+http://space.mit.edu/home/turnerm/python.html
+'''
+
+import math
+import numpy as np
+import inquirer
+import matplotlib.pyplot as plt
+
+from matplotlib import colors as mcolors
+from astropy.io import ascii
+
+path = '/cos_pc19a_npr/programs/quasars/highest_z/data/LightCurves/'
+
+
+choice = '4'
+## Ordered by qsoID number. 
+print()
+print('  1)   MMTJ0215-0529      (qsoID  54)')
+print('  2)   CFHQSJ0216-045     (qsoID  56; faint)')
+print('  3)   SHELLQsJ0220-0432  (qsoID  59; faint)') 
+print('  4)   SDSSJ0836+0054     (qsoID 121)')
+print('  5)   SDSSJ0959+0227     (qsoID 162; faint)')
+print()
+#choice = input('Which object? ')
+
+if choice == '1' : inputQuasar = 'MMTJ0215-0529'
+if choice == '2' : inputQuasar = 'CFHQSJ0216-0455'
+if choice == '3' : inputQuasar = 'SHELLQsJ0220-0432'
+if choice == '4' : inputQuasar = 'SDSSJ0836+0054'
+if choice == '5' : inputQuasar = 'SDSSJ0959+0227'
+
+print
+print(" Plotting W/VSA light curve for ", inputQuasar)
+print
+
+##
+##  P h o t o m e t r y    d a t a
+##
+
+##  WSA  - WFCAM Science Archive
+WSA_data = ascii.read(path+inputQuasar+'/WSA_lc.dat')
+
+## VSA - VISTA Science Archive
+VSA_data = ascii.read(path+inputQuasar+'/VSA_lc.dat')
+
+
+##  UID of combined filter (assigned in WSA: 1=Z,2=Y,3=J,4=H,5=K,6=H2,7=Br,8=blank)
+Z_WFCAM = WSA_data[(WSA_data['filterID'] == 1) & (WSA_data['aperMag3AverAB']>0)]
+Y_WFCAM = WSA_data[(WSA_data['filterID'] == 2) & (WSA_data['aperMag3AverAB']>0)]
[…]

### 2019-02-10 light_curves/variable_candidates/SDSSJ0100+2802/lightcurve.py

@@ -1,0 +1,345 @@
+'''
+Why doesn't matplotlib look as good as SM??!!!
+http://space.mit.edu/home/turnerm/python.html
+'''
+
+import math
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import pandas as pd
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import ascii
+from astropy.io import fits
+from pylab import plot, show
+
+redshift = 6.3
+one_plus_z = 1 #+ redshift
+
+mjd_offset = 50000  ## for 2MASS
+#mjd_offset = 55000  ## for 2MASS
+
+##
+##  P h o t o m e t r y    d a t a
+##
+path = '/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/variable_candidates/SDSSJ0100+2802/'
+
+## 2MASS
+filename = 'TWOMASS_v1.tbl'
+infile = path+filename
+twomass_data = ascii.read(filename)
+
+## 2MASS J, H and Ks bands with Vega magnitudes of 17.00 6 0.20, 15.98 6 0.19 and 15.20 6 0.16,
+## J2MASS = JAB − 0.894
+twomass_mjd   = twomass_data['jdate']-2400000.0
+twomass_JVega = twomass_data['j_m']
+twomass_HVega = twomass_data['h_m']
+twomass_KVega = twomass_data['k_m']
+twomass_Jerr  = twomass_data['j_cmsig']
+twomass_Herr  = twomass_data['h_cmsig']
+twomass_Kerr  = twomass_data['k_cmsig']
+
+twomass_J_AB  = twomass_JVega + 0.894
+twomass_H_AB  = twomass_HVega + 1.374
+twomass_K_AB  = twomass_KVega + 1.84
+
+
+##
+## UKIDSS LAS
+##
+filename   = 'qsoID22_setup1_light_curve_WSERV1000.fits'
+infile     = path+filename
+wfcam      = fits.open(infile)
+data_table = wfcam[1].data
+
+## Quick check on the format/dimensions of the FITS table file...
[…]

### 2019-02-10 light_curves/variable_candidates/SDSSJ0100+2802/lightcurve_darkBkG.py

@@ -1,0 +1,317 @@
+'''
+Why doesn't matplotlib look as good as SM??!!!
+http://space.mit.edu/home/turnerm/python.html
+'''
+
+import math
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+import pandas as pd
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+from astropy.io import ascii
+from astropy.io import fits
+from pylab import plot, show
+
+redshift = 6.3
+one_plus_z = 1 #+ redshift
+
+mjd_offset = 50000  ## for 2MASS
+#mjd_offset = 55000  ## for 2MASS
+
+##
+##  P h o t o m e t r y    d a t a
+##
+path = '/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/variable_candidates/SDSSJ0100+2802/'
+
+## 2MASS
+filename = 'TWOMASS_v1.tbl'
+infile = path+filename
+twomass_data = ascii.read(filename)
+
+## 2MASS J, H and Ks bands with Vega magnitudes of 17.00 6 0.20, 15.98 6 0.19 and 15.20 6 0.16,
+## J2MASS = JAB − 0.894
+twomass_mjd   = twomass_data['jdate']-2400000.0
+twomass_JVega = twomass_data['j_m']
+twomass_HVega = twomass_data['h_m']
+twomass_KVega = twomass_data['k_m']
+twomass_Jerr  = twomass_data['j_cmsig']
+twomass_Herr  = twomass_data['h_cmsig']
+twomass_Kerr  = twomass_data['k_cmsig']
+
+twomass_J_AB  = twomass_JVega + 0.894
+twomass_H_AB  = twomass_HVega + 1.374
+twomass_K_AB  = twomass_KVega + 1.84
+
+
+##
+## UKIDSS LAS
+##
+filename   = 'qsoID22_setup1_light_curve_WSERV1000.fits'
+infile     = path+filename
+wfcam      = fits.open(infile)
+data_table = wfcam[1].data
+
+## Quick check on the format/dimensions of the FITS table file...
[…]

### 2019-02-15 tex/older_tex/VHzQ_20181218.tex
noter big  tex/older_tex/VHzQ_pre201811 update

--- 2018-12-20 tex/WW4C_VHzQ.tex
@@
     As such, we generate a set of tables that are different in subtle ways to the regular ``Detection'' tables.
-
-    The two most important tables for our needs are the {\tt [w/v]serv1000MapRemeasurement} and {\tt [w/v]serv1000MapRemeasAver}.
-
-    Full documentation can be found at the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema Browser} 
-and the \href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema Browser}.
 

### 2019-02-15 tex/older_tex/VHzQ_pre201811/WW4C_VHzQ_20180303.tex
noter big  tex/older_tex/VHzQ_pre201811 update

--- 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180530.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                           
-%%  
-%%									    
+%                                                                           
+% Needs:  mn2e.cls, mn2e.bst, mn.sty, format.tex, psfig.sty
+%									    
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title[Very high-$z$ Quasars]
-        {Near and mid-infrared properties of known $z\geq5$ Quasars}
+\title[WW4C I: Very high-$z$ Quasars]
+      {The WISE $W4$ Compendium: I. Introducing the WW4C with $z>4$ Quasars}
 \author[N.P. Ross et al.]
-       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk} and Nicholas J. Cross$^{1}$
-\\ 
+       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk}\\ 
 $^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Qs, defined here to have redshifts
-$z\gtrsim5$) are excellent probes of the early Universe. This includes
-studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
-reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
-supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
-Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
-enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
+Very high redshift quasars (VH$z$Qs; $z\gtrsim5$) are excellent probes
+of the early Universe. This includes studies of the Epoch of
+Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review,
+Mortlock2016}, the formation and build-up of supermassive black holes
+\citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016,
+Valiante2018, Latif2018} and early metal enrichment \citep[see e.g.,
+][]{Simcoe2012, Chen2017, Bosman2017}.
 
-%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR).
-The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.
-However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.
-For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}.
-%%However, we also note the potential for the non-causal origins of the
-%%black-hole galaxy scaling relations \citep{Jahnke2011}.
+There is a remarkable similarity between cosmic star-formation rate
+density (SFRD) and black hole accretion rate (BHAR) trace each other
+\citep[with a normalisation factor of $\sim3000$,][]{Willott2013b,
+MadauDickinson2014} across redshifts $z=0-4$.  However, new results
+\citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR
+do not have the same evolutionary form at higher, $z>4$ redshifts, for
+reasons that are currently poorly understood.
+%% For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR.
 
@@
 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
-][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
-Timlin2016} as well as AGN and star-forming galaxies due to the
-presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
+][]{Eisenhardt1994, Lacy2004, Stern2005, Richards2006b, Timlin2016} as
+well as AGN and star-forming galaxies due to the presence of
+Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
 \citep[e.g., ][]{Yan2007, Tielens2008}.
 
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
-a quasar without hot-dust emission in a sample of 21 $z\approx6$
-quasars. Such apparently hot-dust-free quasars have no counterparts at
-low redshift. Moreover, we demonstrate that the hot-dust abundance in
-the 21 quasars builds up in tandem with the growth of the central
-black hole,
-
-\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
-(55\%) of the then known 31 quasars at $z > 6$. However,
-\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
-as opposed to the superior ``AllWISE'' catalogs. That sample only
-examined the 31 known $z>6$ quasars; our sample has 148 objects with
-redshift $z\geq6.00$.
-
-Here we update \citet{Jiang2010}  and \citet{Blain2013} 
-\citep[along with Table 8 of][]{Banados2016}.
-
-We chose redshift $z=5.0$ as our lower redshift limit due to a combination 
-of garnishing a large sample, adequately spanning physical properties 
-(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
-we've gained over the last couple of decades since $z>5$ quasars were 
-discovered.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
-In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths
+of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
+``ALLWISE'' catalog, contains nearly 750 million detections at
+high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
 \citet{Assef2013}, \citet{Stern2012}
-
-In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).
-The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys.
-%%
 
@@
 
+In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a
+detailed study into the objects that were detected in the longest
+waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey
+Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+%%
+This study will describe all 40 million objects that are detected in
+the WISE W4-band, but will concentrate on those objects most affected
+by radiating dust emission and well described by extragalactic, and
+AGN, spectral energy distributions (SEDs).  The motivations of the
+WW4C are numerous, but the primary science we will pursue is the
+identification of bolometric luminous AGN, especially those that might
+not be observered in X-ray/UV/optical surveys.
+%%
+However, we will aim to remain as agnostic as possible to the origin
+of the objects that are emit in the mid-infrared.
+
 This paper can be considered an update of \citet{Blain2013} and also
-an extension of parts of \citet{Banados2016}, with the latter study reporting
+an extension of \citet{Banados2014}, with the latter study reporting
 WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey Telescope and Rapid Response System 1 
@@
 of quasars at $z > 5.6$.
-
-$M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass, stellar mass of the bulge and 
- galaxy total stellar mass, respectively.
-
-Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al.
-2010).
-For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}.
-We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online.
-All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.
-We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) in order to be consistent with \citet{Banados2016}.
 
@@
 \section{Data}
-
-\input{THE_TABLE_v0pnt96_TOP10}
-
-Table~\ref{tab:THE_TABLE} gives the salient details for the objects
-used in this study. We use all the $z\geq5.00$ quasars that
-have been discovered and spectroscopically confirmed as of the time of
-writing (2018 June). We report near-infrared ($yYJHK$-bands)
-and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$
+\subsection{The WISE W4 Catalogue}
+There are 747,634,026 total entries in the AllWISE Source Catalog.  Of
+these, 40,939,966 (5.476\%) are W4-detected.
 
 \subsection{Very high redshift quasars}
-In Table~\ref{tab:THE_TABLE} we give the discovery reference for the
-VH$z$Qs noting that some objects were discovered independently and
-contemporaneously.  The redshifts for the VH$z$Qs generally come from
-the measurement of broad UV/optical emission lines. Where 
-there are far infra-red emission lines e.g. \cii~158 micron, we report 
-these, but at the level of our current analysis broadline redshifts are
-sufficient.
+
+\citet{Mortlock2011}, \citet{McGreer2013}, 
+\citet{Venemans2013}, 
+\citet{Venemans2013}, 
+\citet{Venemans2015a},  \citet{Venemans2015b}, \citet{Banados2016}, \citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017}, \citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Matsuoka2017}, \citet{Tang2017}, \citet{Koptelova2017}, \citet{Matsuoka2017}, \citet{Banados2018}
 
@@
 (2016) [2016arXiv160609634W];
-Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
-\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
-\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
-\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
-\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
-\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
-\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
-\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
-\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
-\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
-\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
-\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
-\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
-\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
-\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
-\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
-\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
-\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
-\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
-\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a}
-and \citet{Matsuoka2018b}.
-
-\subsection{Optical Photometry}
-\subsubsection{Pan-STARRS1 (PS1)} 
-We query the Panoramic Survey Telescope and Rapid Response System
-(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
-Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
-service at
-\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-The PS1 survey observed the 30,000 deg$^{2}$ of sky north of
-declination $-30$ degrees in five filters $grizy$.  Pan-STARRS1 (PS1)
-is the first part of Pan-STARRS to be completed and is the basis for
-the DR1.  \citet{Chambers2016}, \citet{Magnier2016a},
-\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
-\citet{Flewelling2016} describe the instrument, survey, and data
-analyses.  The principal science product of the PS1 survey is the
-catalog accessible through the CasJobs interface.
-
-We query and return the mean PSF magnitudes from the $grizy$ filters
-({\tt MeanPSFMag}) which are in the AB system for our 425 VH$z$Q
-sample. Details of our SQL and links to the main tables are given
-in~\ref{sec:PS1_SQL}.
-
-%\newpage
-\subsection{Near-infrared photometry}
-Due to their selection of being very faint/undetected in the
-observed-frame optical but bright in the observed frame near-infrared,
-VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
-\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.
-
-We query the WFCAM Science Archive
-\citep[\href{http://wsa.roe.ac.uk/}{WSA}; ][]{Hambly2008} which
-reports NIR photometry from the Wide Field Camera \citep[WFCAM;
-][]{Casali2007} on the United Kingdom Infrared Telescope (UKIRT).
-Data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
-\citep[Visible and Infrared Survey Telescope for Astronomy;
-][]{Emerson2006, Dalton2006} is also given in the WSA.
-
-Quasars are known to vary (both photometrically and spectroscopically)
-and very high-$z$ quasars under going super-Eddington accretion during
-a rapid BH growth phase are prime candidates for this variation.
-Therefore, with repeat observations over many epochs availble via the
-WSA, we have a choice to make for how we report the photometry. After
-tests, we decide to give the NIR photometry averaged on 4 week
-observed timescales. This time bracket is chosen as a good compromise
-between maximising signal-to-noise while keeping the cadence high. At
-our observed redshifts, we sample $\lesssim1$week in the rest-frame
-and luminous quasars are not expected to vary on timescales quicker
-than this \citep[e.g., ][]{Lawrence2016_ASPC}.
-
-We give our recipe and SQL query syntax in Appendix~\ref{sec:SQL}.
-
-\subsubsection{UKIDSS LAS} 
-Use:\\
-%lasDetection \\
-dr10plus\\
-lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned. Of which...
-
-\subsubsection{VISTA VHS} 
-Use:\\
-%lasDetection \\
-VH5DR5 \\
-sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned.  Of which...
-
-{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
 
 \iffalse
-\subsection{Filter and Survey choices} 
-We make some choices when reporting our archival photometry. 
-This includes:
-\begin{itemize}
-\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
-\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
-\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
-\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
-\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
-\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
-\item Due to lack of coverage, do not report WFCAM $Z$-band. 
-\end{itemize}
+Warning--I didn't find a database entry for "Kurk2007"
+Warning--I didn't find a database entry for "Leipski2014"
+Warning--I didn't find a database entry for "Morganson2012"
+Warning--I didn't find a database entry for "Reed2015"
+Warning--I didn't find a database entry for "Stern2007"
+Warning--I didn't find a database entry for "Wang-Feige2016"
+Warning--I didn't find a database entry for "Wang2008b"
+Warning--I didn't find a database entry for "Wu2015"
+Warning--I didn't find a database entry for "Zeimann2011"
 \fi
+
+\citet{Fan2000} 
+\citet{Fan2001c} 
+\citet{Fan2003} 
+\citet{Fan2004} 
+\citet{Mahabal2005}
+\citet{Cool2006}
+\citet{Fan2006} 
+\citet{Goto2006}          
+\citet{McGreer2006}       
+\citet{Carilli2007}       
+\citet{Kurk2007}          
+\citet{Stern2007}         
+\citet{Venemans2007}    
+\citet{Willott2007}       
+\citet{Jiang2008}         
+\citet{Wang2008}         
+\citet{Jiang2009}         
+\citet{Kurk2009}          
+\citet{Mortlock2009}      
+\citet{Willott2009}       
+\citet{Carilli2010}       
+\citet{Wang2010}          
+\citet{Willott2010a}      
+\citet{Willott2010b}      
+\citet{DeRosa2011}        
+\citet{Mortlock2011}     
+\citet{Wang2011}          
+\citet{Zeimann2011}       
+\citet{Morganson2012}    
+\citet{Venemans2012}      
+\citet{McGreer2013}       
+\citet{Venemans2013}      
+\citet{Wang2013}         
+\citet{Willott2013b}     
+\citet{Banados2014}       
+\citet{Calura2014}        
+\citet{Leipski2014}       
+\citet{Banados2015a}      
+\citet{Banados2015b}      
+\citet{Becker2015}        
+\citet{Carnall2015}       
+\citet{Jiang2015}        
+\citet{Kashikawa2015}    
+\citet{Kim2015}          
+\citet{Reed2015}          
+\citet{Venemans2015a}    
+\citet{Venemans2015b}    
+\citet{Willott2015}      
+\citet{Wu2015}           
+\citet{Venemans2016}      
+\citet{Wang2016_WISE}    
+\citet{Matsuoka2016}      
+\citet{WangR2016}
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l rr}
+      \hline
+      \hline
+      Description & \#  objects & \% of Total \\         
+      \hline  
+      AllWISE Source Catalog & 747,634,026  & 100.0000 \\
+      All W4 detections          &  40,939,966  &      5.4759 \\
+      W4 Only                        &         35,818  &      0.0048\\
+     \hline
+      \hline
+    \end{tabular}
+    \caption{}
+    \label{tab:ERQ_key_numbers}
+  \end{center}
+  \vspace{-8pt}
+\end{table}
 
@@
 %%
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
+%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
+%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
+%%  S E C T I O  N   5         S E C T I O  N   5           S E C T I O  N   5       S E C T I O  N   5
 %%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-    \subsection{Very High-$z$ Quasars Detected in WISE}
-     \citet{Blain2013}
-
-    \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
+\section{Very High-$z$ Quasars Detected in WISE W4}
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
+ridiculus mus. Mauris at diam quis arcu pretium dictum. Quisque id
+risus odio. Pellentesque posuere semper tempor. Donec volutpat quam ut
+urna rutrum venenatis dapibus nunc interdum. Sed quis diam ac mauris
+cursus accumsan. Maecenas sit amet libero in elit mattis iaculis sed
+quis elit. Pellentesque vitae mauris nunc.
 
 \subsection{Colours}
+Cras scelerisque egestas ante vitae lacinia. Nunc velit nunc, tempus
+congue lobortis auctor, pellentesque ac ipsum. Donec erat urna,
+interdum eget blandit non, malesuada nec tellus. Aliquam erat
+volutpat. Maecenas ut eros id lorem suscipit vulputate pulvinar quis
+libero. Phasellus ipsum libero, sollicitudin vel luctus in, faucibus
+at mauris. Fusce ultrices egestas turpis, eget mattis tellus
+pellentesque vel. Donec ut ligula id nisi commodo tristique. Etiam
+semper turpis eget purus rhoncus a malesuada massa ultrices. Fusce
+luctus vehicula sem, eget scelerisque lacus fermentum sed. Nulla
+facilisi. Aenean ut turpis sed quam ullamcorper mattis sit amet ut
+justo. Morbi lorem dui, aliquam et pharetra non, luctus eu enim. Nulla
+molestie hendrerit mi tincidunt interdum. Nunc a augue nunc.
 
-%%\subsection{Mullaney SEDs}
+\subsection{Mullaney SEDs}
 
 \subsection{Number Density of High-$z$ Sources}
-
-\subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
-From a study of 69 {\it Herschel}-detected broad-line active galactic
-nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
-- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
-$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
-range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
-for the $z>6$ measured from the e.g. \mgii line, are generally
-correct, then the galaxy total stellar mass for the $z>6$ objects
-should be...
-
-\citet{YangG2018} calculate the long-term SMBH accretion rate as a
-function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
-ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
-Our BHAR(M⋆,z) is constrained by high-quality survey data
-(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
-function and the X-ray luminosity function.  This BHAR/SFR dependence
-on $M_{\star}$ does not support the scenario that SMBH and galaxy
-growth are in lockstep.
+Cras quis nisl eget orci ultricies tempor quis id mi. Nullam ut
+sollicitudin justo. Maecenas posuere fermentum nunc et
+faucibus. Integer consectetur nibh a dolor blandit ornare. In et dui
+id sapien suscipit commodo eget vitae dolor. Cum sociis natoque
+penatibus et magnis dis parturient montes, nascetur ridiculus
+mus. Donec ut elit sed urna semper imperdiet nec ac lorem. Integer
+varius nibh a mauris posuere non convallis nibh commodo. Cras posuere
+lorem sit amet orci elementum sit amet dapibus risus lacinia. Morbi
+vitae lobortis dui. Nulla ac lacus tellus, a volutpat tortor.
 
@@
 \label{sec:conclusions}
-In this study, we have, for the first time, ompiled the list of all
-$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
-($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
-objects, given their detection rates and SEDs. We find that::
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
+ridiculus mus. Duis tempus, lectus nec ultricies mollis, mi orci
+feugiat nulla, a bibendum velit orci nec lacus. Duis a odio in nisi
+egestas dictum. Nullam vel quam mauris, eget consectetur orci. Morbi
+ac mi sit amet neque consectetur tempus ac eget est. Curabitur
+malesuada arcu sit amet metus dictum at dapibus arcu accumsan. Fusce
+sollicitudin luctus rutrum.
 
@@
 \section*{Acknowledgements}
-NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.
-
-We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
-
-This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
-\citep[][]{Taylor2005, Taylor2011}.
-
-This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
-a community-developed core Python package for Astronomy 
-\citep{AstropyCollaboration2013, AstropyCollaboration2018}.
-
-The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
-been made possible through contributions by the Institute for
-Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
-the Max-Planck Society and its participating institutes, the Max
-Planck Institute for Astronomy, Heidelberg and the Max Planck
-Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
-University, Durham University, the University of Edinburgh, the
-Queen's University Belfast, the Harvard-Smithsonian Center for
-Astrophysics, the Las Cumbres Observatory Global Telescope Network
-Incorporated, the National Central University of Taiwan, the Space
-Telescope Science Institute, the National Aeronautics and Space
-Administration under Grant No. NNX08AR22G issued through the Planetary
-Science Division of the NASA Science Mission Directorate, the National
-Science Foundation Grant No. AST-1238877, the University of Maryland,
-Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
-and the Gordon and Betty Moore Foundation.
-
-CasJobs was originally developed by the Johns Hopkins University/
-Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
-used version 3.5.16 to construct CasJobs-based tools for GALEX,
-Kepler, the Hubble Source Catalog, and PanSTARRS.
-
-This publication makes use of data products from the Wide-field
-Infrared Survey Explorer, which is a joint project of the University
-of California, Los Angeles, and the Jet Propulsion
-Laboratory/California Institute of Technology, and NEOWISE, which is a
-project of the Jet Propulsion Laboratory/California Institute of
-Technology. WISE and NEOWISE are funded by the National Aeronautics
-and Space Administration.
-
-\newpage
 
@@
 
-\section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}
-The PS1 Casjobs SQL Server is located at
-\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
-The top level documentation is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
-while the description of tables is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}. The
-main tables are the
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
-objectThin}} and
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
-meanObject}} tables.
-
-\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
-Here we give the receipe and SQL that returned the near-infrared photometry 
-for the VH$z$Qs.
-
-\begin{enumerate}
-\item http://wsa.roe.ac.uk/ 
-\item Login
-\item {\tt username:	WSERV1000;  password: 	highzqso;   community: 	nonSurvey} 
-\item Freeform SQL Query with  WSERV1000v20180327
-\end{enumerate}
-
-\input{SQL_examples}
+\section{Table of Very High-$z$ Quasars}
 

### 2019-02-15 tex/older_tex/VHzQ_pre2019/WW4C_VHzQ_20180430.tex
big udpate of tex/older_tex/VHzQ_pre2019/ and Lz/

--- 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180530.tex
@@
 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
-][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
-Timlin2016} as well as AGN and star-forming galaxies due to the
-presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
+][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b, Timlin2016} as
+well as AGN and star-forming galaxies due to the presence of
+Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda >3\mu$m
 \citep[e.g., ][]{Yan2007, Tielens2008}.
@@
 
-\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
-(55\%) of the then known 31 quasars at $z > 6$. However,
-\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
-as opposed to the superior ``AllWISE'' catalogs. That sample only
-examined the 31 known $z>6$ quasars; our sample has 148 objects with
-redshift $z\geq6.00$.
+However, \citet{Blain2013} was compiled with the WISE `All-Sky' 
+data release, as opposed to the superior ``AllWISE'' catalogs and 
+only examined the 31 known $z>6$ quasars. Our sample has 
+148 objects with redshift $z\geq6.00$.
 
@@
 
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
-In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths
+of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
+``ALLWISE'' catalog, contains nearly 750 million detections at
+high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
 \citet{Assef2013}, \citet{Stern2012}
-
-In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).
-The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys.
-%%
 
@@
 
-Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al.
-2010).
-For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}.
-We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online.
-All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.
-We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) in order to be consistent with \citet{Banados2016}.
+Because of established conventions, we report SDSS $ugriz$ magnitudes on
+the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, 
+while the WISE W1 − 4 magnitudes are calibrated on the Vega system
+(Wright et al. 2010). For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m =
+(2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively
+\citep{Cutri2011, Brown2014b}. We make use of the Explanatory Supplement to the
+WISE All-Sky Data Release, as well as the WISE AllWISE Data Release
+Products online.
+All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared 
+($y/YJHK$) are also given in the AB system. 
+Our chosen cosmology is: 
+%%
+We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, 
+$\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016).
+in order to be consistent with \citet{Banados2016}.
 
@@
 writing (2018 June). We report near-infrared ($yYJHK$-bands)
-and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$
+and mid-infrared (WISE W1/2/3/4) photometry.
 
@@
 sufficient.
+
+\citet{Mortlock2011}, \citet{McGreer2013}, \citet{Venemans2013},  \citet{Venemans2013}, \citet{Venemans2015a},  \citet{Venemans2015b}, \citet{Banados2016}, \citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017}, \citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Matsuoka2017}, \citet{Tang2017}, \citet{Koptelova2017}, \citet{Matsuoka2017}, \citet{Banados2018}
 
@@
 (2016) [2016arXiv160609634W];
-Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
-\citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
-\citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007},
-\citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007},
-\citet{Jiang2008}, \citet{Wang2008} \citet{Jiang2009} \citet{Kurk2009}
-\citet{Mortlock2009} \citet{Willott2009} \citet{Carilli2010}
-\citet{Wang2010} \citet{Willott2010a} \citet{Willott2010b}
-\citet{DeRosa2011} \citet{Mortlock2011} \citet{Wang2011}
-\citet{Zeimann2011} \citet{Morganson2012} \citet{Venemans2012}
-\citet{McGreer2013} \citet{Venemans2013} \citet{Wang2013}
-\citet{Willott2013b} \citet{Banados2014} \citet{Calura2014}
-\citet{Leipski2014} \citet{Banados2015a} \citet{Banados2015b}
-\citet{Becker2015} \citet{Carnall2015} \citet{Jiang2015}
-\citet{Kashikawa2015} \citet{Kim2015} \citet{Reed2015}
-\citet{Venemans2015a} \citet{Venemans2015b} \citet{Willott2015}
-\citet{Wu2015} \citet{Venemans2016} \citet{Wang2016_WISE}
-\citet{Matsuoka2016} \citet{WangR2016} , \citet{Mortlock2011},
-\citet{McGreer2013}, \citet{Venemans2013}, \citet{Venemans2013},
-\citet{Venemans2015a}, \citet{Venemans2015b}, \citet{Banados2016},
-\citet{Matsuoka2016}, \citet{Reed2017}, \citet{Wang2017},
-\citet{Mazzucchelli2017}, \citet{Ikeda2017}, \citet{Tang2017},
-\citet{Koptelova2017}, \citet{Banados2018}, \citet{Matsuoka2018a}
-and \citet{Matsuoka2018b}.
-
-\subsection{Optical Photometry}
-\subsubsection{Pan-STARRS1 (PS1)} 
-We query the Panoramic Survey Telescope and Rapid Response System
-(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
-Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
-service at
-\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-The PS1 survey observed the 30,000 deg$^{2}$ of sky north of
-declination $-30$ degrees in five filters $grizy$.  Pan-STARRS1 (PS1)
-is the first part of Pan-STARRS to be completed and is the basis for
-the DR1.  \citet{Chambers2016}, \citet{Magnier2016a},
-\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
-\citet{Flewelling2016} describe the instrument, survey, and data
-analyses.  The principal science product of the PS1 survey is the
-catalog accessible through the CasJobs interface.
-
-We query and return the mean PSF magnitudes from the $grizy$ filters
-({\tt MeanPSFMag}) which are in the AB system for our 425 VH$z$Q
-sample. Details of our SQL and links to the main tables are given
-in~\ref{sec:PS1_SQL}.
+\citet{Fan2000}, \citet{Fan2001c}, \citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005}, \citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006}, \citet{McGreer2006}, \citet{Carilli2007}, \citet{Kurk2007}, \citet{Stern2007}, \citet{Venemans2007}, \citet{Willott2007}, \citet{Jiang2008}, \citet{Wang2008}         \citet{Jiang2009}         \citet{Kurk2009}          \citet{Mortlock2009}      \citet{Willott2009}       \citet{Carilli2010}       \citet{Wang2010}          \citet{Willott2010a}      \citet{Willott2010b}      \citet{DeRosa2011}        \citet{Mortlock2011}     \citet{Wang2011}          \citet{Zeimann2011}       \citet{Morganson2012}    \citet{Venemans2012}      \citet{McGreer2013}       \citet{Venemans2013}      \citet{Wang2013}         \citet{Willott2013b}     \citet{Banados2014}       \citet{Calura2014}        \citet{Leipski2014}       \citet{Banados2015a}      \citet{Banados2015b}      \citet{Becker2015}        \citet{Carnall2015}       \citet{Jiang2015}        \citet{Kashikawa2015}    \citet{Kim2015}          \citet{Reed2015}          \citet{Venemans2015a}    \citet{Venemans2015b}    \citet{Willott2015}      \citet{Wu2015}           \citet{Venemans2016}      \citet{Wang2016_WISE}    \citet{Matsuoka2016}
+\citet{WangR2016}
 
@@
 
-\subsubsection{UKIDSS LAS} 
-Use:\\
-%lasDetection \\
-dr10plus\\
-lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned. Of which...
+\subsection{The WISE W4 Catalogue}
+There are 747,634,026 total entries in the AllWISE Source Catalog.  Of
+these, 40,939,966 (5.476\%) are W4-detected.
 
-\subsubsection{VISTA VHS} 
-Use:\\
-%lasDetection \\
-VH5DR5 \\
-sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned.  Of which...
-
-{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
-
-\iffalse
-\subsection{Filter and Survey choices} 
-We make some choices when reporting our archival photometry. 
-This includes:
-\begin{itemize}
-\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
-\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
-\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
-\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
-\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
-\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
-\item Due to lack of coverage, do not report WFCAM $Z$-band. 
-\end{itemize}
-\fi
+\begin{table}
+  \begin{center}
+    \begin{tabular}{l rr}
+      \hline
+      \hline
+      Description & \#  objects & \% of Total \\         
+      \hline  
+      AllWISE Source Catalog & 747,634,026  & 100.0000 \\
+      All W4 detections          &  40,939,966  &      5.4759 \\
+      W4 Only                        &         35,818  &      0.0048\\
+     \hline
+      \hline
+    \end{tabular}
+    \caption{}
+    \label{tab:ERQ_key_numbers}
+  \end{center}
+  \vspace{-8pt}
+\end{table}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Very High-$z$ Quasars Detected in WISE}
+\citet{Blain2013} 
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur
+ridiculus mus. Mauris at diam quis arcu pretium dictum. Quisque id
+risus odio. Pellentesque posuere semper tempor. Donec volutpat quam ut
+urna rutrum venenatis dapibus nunc interdum. Sed quis diam ac mauris
+cursus accumsan. Maecenas sit amet libero in elit mattis iaculis sed
+quis elit. Pellentesque vitae mauris nunc.
 
-    \subsection{Very High-$z$ Quasars Detected in WISE}
-     \citet{Blain2013}
-
-    \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
+\subsection{Very High-$z$ Quasars Detected in WISE W4}
 
 \subsection{Colours}
+Cras scelerisque egestas ante vitae lacinia. Nunc velit nunc, tempus
+congue lobortis auctor, pellentesque ac ipsum. Donec erat urna,
+interdum eget blandit non, malesuada nec tellus. Aliquam erat
+volutpat. Maecenas ut eros id lorem suscipit vulputate pulvinar quis
+libero. Phasellus ipsum libero, sollicitudin vel luctus in, faucibus
+at mauris. Fusce ultrices egestas turpis, eget mattis tellus
+pellentesque vel. Donec ut ligula id nisi commodo tristique. Etiam
+semper turpis eget purus rhoncus a malesuada massa ultrices. Fusce
+luctus vehicula sem, eget scelerisque lacus fermentum sed. Nulla
+facilisi. Aenean ut turpis sed quam ullamcorper mattis sit amet ut
+justo. Morbi lorem dui, aliquam et pharetra non, luctus eu enim. Nulla
+molestie hendrerit mi tincidunt interdum. Nunc a augue nunc.
 
-%%\subsection{Mullaney SEDs}
+\subsection{Mullaney SEDs}
 
 \subsection{Number Density of High-$z$ Sources}
+Cras quis nisl eget orci ultricies tempor quis id mi. Nullam ut
+sollicitudin justo. Maecenas posuere fermentum nunc et
+faucibus. Integer consectetur nibh a dolor blandit ornare. In et dui
+id sapien suscipit commodo eget vitae dolor. Cum sociis natoque
+penatibus et magnis dis parturient montes, nascetur ridiculus
+mus. Donec ut elit sed urna semper imperdiet nec ac lorem. Integer
+varius nibh a mauris posuere non convallis nibh commodo. Cras posuere
+lorem sit amet orci elementum sit amet dapibus risus lacinia. Morbi
+vitae lobortis dui. Nulla ac lacus tellus, a volutpat tortor.
 
 \subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
-From a study of 69 {\it Herschel}-detected broad-line active galactic
-nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
-- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
-$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
-range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
-for the $z>6$ measured from the e.g. \mgii line, are generally
-correct, then the galaxy total stellar mass for the $z>6$ objects
-should be...
+From a study of 69 {\it Herschel}-detected broad-line active galactic nuclei, 
+\citet{Sun2015} find there is no evolution in the $M_{\rm BH} - M_{\star}$ relation 
+from $z\sim2$ to $z\sim0$, with the ratio of $\log (M_{\rm BH} / M_{\star}$ constant
+at -2.85 across this redshift range. If this ratio holds to $z>5$, and we assume the 
+$M_{\rm BH}$ for the $z>6$ measured from the e.g. \mgii line, are generally correct, 
+then the galaxy total stellar mass for the $z>6$ objects should be...
 
-\citet{YangG2018} calculate the long-term SMBH accretion rate as a
-function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
-ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
-Our BHAR(M⋆,z) is constrained by high-quality survey data
-(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
-function and the X-ray luminosity function.  This BHAR/SFR dependence
-on $M_{\star}$ does not support the scenario that SMBH and galaxy
-growth are in lockstep.
+\citet{YangG2018} calculate the long-term SMBH accretion rate as a function of 
+$M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ 
+over ranges of 
+$\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$. 
+Our BHAR(M⋆,z) is constrained by high-quality survey data (GOODS-South, GOODS-North and COSMOS), and by the stellar mass function and the X-ray luminosity function.
+ This BHAR/SFR dependence on $M_{\star}$ does not support the scenario that SMBH and galaxy growth are in lockstep.
 
@@
 \section*{Acknowledgements}
-NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.
-
-We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
-
-This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
-\citep[][]{Taylor2005, Taylor2011}.
-
-This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
-a community-developed core Python package for Astronomy 
-\citep{AstropyCollaboration2013, AstropyCollaboration2018}.
-
-The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
-been made possible through contributions by the Institute for
-Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
-the Max-Planck Society and its participating institutes, the Max
-Planck Institute for Astronomy, Heidelberg and the Max Planck
-Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
-University, Durham University, the University of Edinburgh, the
-Queen's University Belfast, the Harvard-Smithsonian Center for
-Astrophysics, the Las Cumbres Observatory Global Telescope Network
-Incorporated, the National Central University of Taiwan, the Space
-Telescope Science Institute, the National Aeronautics and Space
-Administration under Grant No. NNX08AR22G issued through the Planetary
-Science Division of the NASA Science Mission Directorate, the National
-Science Foundation Grant No. AST-1238877, the University of Maryland,
-Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
-and the Gordon and Betty Moore Foundation.
-
-CasJobs was originally developed by the Johns Hopkins University/
-Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
-used version 3.5.16 to construct CasJobs-based tools for GALEX,
-Kepler, the Hubble Source Catalog, and PanSTARRS.
-
-This publication makes use of data products from the Wide-field
-Infrared Survey Explorer, which is a joint project of the University
-of California, Los Angeles, and the Jet Propulsion
-Laboratory/California Institute of Technology, and NEOWISE, which is a
-project of the Jet Propulsion Laboratory/California Institute of
-Technology. WISE and NEOWISE are funded by the National Aeronautics
-and Space Administration.
 
@@
 \appendix
-
-\section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}
-The PS1 Casjobs SQL Server is located at
-\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
-The top level documentation is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
-while the description of tables is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}. The
-main tables are the
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
-objectThin}} and
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
-meanObject}} tables.
-
 \section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}

### 2019-02-15 Lz/Lz.py

@@ -30,7 +30,7 @@ ageticks = [z_at_value(cosmo.age, age) for age in ages]
 
 ## READ-IN THE DATA FILE(S)
 path = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
-infile = 'THE_TABLE_v0pnt981_temp.ascii'
+infile = 'THE_TABLE_v0pnt971.ascii'
 readin = path+infile
 all_VHzQs  = ascii.read(readin, delimiter=r'\s')
 

### 2019-02-17 tex/VHzQ.tex
big VHzQ.tex update

--- 2018-12-20 tex/WW4C_VHzQ.tex
@@
 current datasets have been discovered. 
+All the data, analysis codes and plots used and generated here can be found at:
+\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
 \end{abstract}
@@
 supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
-Volonteri2010, Agarwal2016, Valiante2018, Latif2018} and early metal
-enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
+Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and
+early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017,
+Bosman2017}.
 
@@
 Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
-one might well expect VH$z$Qs to vary in luminosity as they
-potentially go through phases of super-critical accretion and these
-signatures of photometric variability should be looked for, noting the
-rest-frame optical emission is redshifted into the observed
-near-infrared (NIR) at redshifts $z>5$. Fortunately, data are now in
-place from deep, wide-field NIR instruments and surveys such as the
-Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red
-Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed
-CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for
-Astronomy (VISTA) in the Southern Hemisphere, that are necessary for
-identifying VH$z$Qs.
+one could expect VH$z$Qs to potentially vary in luminosity as they go
+through phases of super-critical accretion. These signatures of
+photometric variability should be looked for, noting the rest-frame
+optical emission is redshifted into the observed near-infrared (NIR)
+at redshifts $z>5$. Fortunately, data are now in place from deep,
+wide-field NIR instruments and surveys such as the Wide Field Camera
+(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
+in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
+the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
+Southern Hemisphere, that are necessary for identifying VH$z$Qs.
 
@@
 ``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects, but here we use these terms
-interchangeably, with a preference for quasar, in recognition of the
-fact that they both describe accreting supermassive black holes
+luminosity/classes of objects. In recognition of the
+fact that both terms describe accreting supermassive black holes, 
+we use these terms interchangeably, with a preference for quasar, 
+since we are generally in the higher-$L$ regime
 \citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
@@
 
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
-a quasar without hot-dust emission in a sample of 21 $z\approx6$
-quasars. Such apparently hot-dust-free quasars have no counterparts at
-low redshift. Moreover, those authors demonstrate that the hot-dust
-abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole. But understanding how dust first forms and appears
-in the central engine remains an open question \citep{WangR2008, WangR2011}.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m. The all sky ``ALLWISE'' catalog
-release, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
-of which over 4.5M AGN candidates have been identified with 90\%
-reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
-mid-infrared (MIR) detections of 17 (55\%) of the then known 31
-quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
-WISE `All-Sky' data release, as opposed to the superior ``AllWISE''
-catalogs. That sample only examined the 31 known $z>6$ quasars; our
-sample has 148 ({\bf NPR to Double Check!}) objects with redshift $z
-\geq 6.00$.
+\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of a quasar without hot-dust emission in a sample of 21 $z\approx6$ quasars.
+Such apparently hot-dust-free quasars have no counterparts at low redshift.
+Moreover, those authors demonstrate that the hot-dust abundance in the 21 quasars builds up in tandem with the growth of the central black hole.
+But understanding how dust first forms and appears in the central engine remains an open question \citep{WangR2008, WangR2011}.
+
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
+The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.
+\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$.
+However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues.
+That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$, with $xyz$ detected in WISE {\bf NPR to double check!!'}.
+\citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.
 
@@
 the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
-WISE-selected catalog that is based on significantly deeper imaging
+WISE-selected catalogue that is based on significantly deeper imaging
 and has a more extensive modeling of crowded regions than the ALLWISE
-release. For the first time in a catalog, unWISE takes advantage of
+release. For the first time in a catalogue, unWISE takes advantage of
 the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
@@
 
-Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
-with Table 8 of][]{Banados2016}. Our motivations are numerous and
-include: {\it (i)} establishing the first complete catalogue of
-$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-analyzing all the WFCAM and VISTA near-infrared photometry for the
-quasars; {\it (iii)} making the first study of NIR variability of the
-VHzQ population and {\it (iv)} establishing the photometric properties
-for upcoming surveys and telescopes, e.g. the Large Synoptic Survey
-Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}},
-ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
-and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
-
-This paper can be considered an update of \citet{Blain2013} and also
-an extension of parts of \citet{Banados2016}, with the latter study
-reporting WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey
-Telescope and Rapid Response System 1 \citep[Pan-STARRS1,
-PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation
-into the reddest WISE waveband for the VH$z$Qs.  \citet{Banados2016}
-reports and investigates the W1, W2 and W3 properties of quasars at $z
-> 5.6$. We chose redshift $z=5.00$ as our lower redshift limit due to
-a combination of garnishing a large sample, adequately spanning
-physical properties (e.g. luminosity, age of the Universe) and to
-incorporate what knowledge we have gained over the last couple of
-decades since $z>5$ quasars were discovered.
-
-This paper is organized as follows.  In Section 2, we present the
-assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
-compiled. We then give a high-level overview of the photometric
-surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we ... and In Section 4 we ... We conclude in Section 5 
-and present all the necessary details to obtain our dataset in the 
-Appendices.
-
-We make the decision to present all our photometry and magnitudes on
-the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.  This
-includes the near-infrared, as well as the mid-infrared magnitudes.
-Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide
-range of optical, NIR and MIR filters.
-
+Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars.
+Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
+We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
+luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars are still wait to be discovered.
+
+This paper is organized as follows.
+In Section 2, we present the assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have compiled.
+We then give a high-level overview of the photometric surveys and datasets we use and present the photometry of the VH$z$Qs.
+In Section 3 we ...
+and In Section 4 we ...
+We conclude in Section 5 and present all the necessary details to obtain our dataset in the Appendices.
+
+We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.
+This includes the near-infrared, as well as the mid-infrared magnitudes.
+Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters.
 We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) in order to be consistent with \citet{Banados2016} and all logarithms are to the
-base 10.
+2016) in order to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
 
@@
 \vspace{-16pt}
-\section{Data}
-First we compile the list of all known, spectroscopically confirmed quasars from the literature.
-Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
-As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
-Figures 7 and 10 in][]{Banados2016}.
-We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and reshift identifications.
-
+\section{Method and Data}
+Quasars are generally identified by photometric selection followed by
+spectroscopic confirmation. Here, we reverse this method obtaining
+first a list of spectroscopic quasars and then obtain photometric
+information.
+
+We have compiled a list of 463 quasars with redshifts $z\geq5.00$.
+We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018-Dec-31.
 We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
@@
 
-Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
-
-\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
-
-%\input{table_tex/THE_TABLE_v0pnt96_TOP10_redshifts}
-%\input{table_tex/THE_TABLE_v0pnt96_TOP10_NIR}
-%\input{table_tex/THE_TABLE_v0pnt96_TOP10_MIR}
-
 \subsection{Spectroscopy} 
-We have obtained a list of 463 spectroscopically confirmed quasars
-with redshifts $z\geq5.00$. We use all the $z\geq5.00$ quasars that
-have been discovered and spectroscopically confirmed as of the time of
-writing (2018 November).
-
-This list was complied from a range of surveys and papers. 
-Specifically, we use data from: 
+We compile the list of all known, spectroscopically confirmed
+quasars from the literature.  This list was complied from a range of
+surveys and papers.  Specifically, we use data from:
 \citet{Banados2014, Banados2016, Banados2018}, 
@@
 and 
-\citet{Zeimann2011}, 
+\citet{Zeimann2011}. 
+%We have obtained a list of 463 spectroscopically confirmed quasars with redshifts $z\geq5.00$.
+
+Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
+As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
+Figures 7 and 10 in][]{Banados2016}.
+We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and reshift identifications.
+
 The breakdown of how many VH$z$Q each survey reports is given in
@@
 
+Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
+
+\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
       \includegraphics[width=8.5cm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+      {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
       \vspace{-16pt}
@@
   \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/LightCurves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
   \centering
@@
       $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = z_{\rm AB} - 0.513 $     \\
-      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = z_{\rm AB} - 0.514 $     \\
-      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = z_{\rm AB} - 0.512$     \\
+      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = Z_{\rm AB} - 0.513 $     \\
+      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = Z_{\rm AB} - 0.514 $     \\
+      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = Z_{\rm AB} - 0.512$     \\
       $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
@@
       $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
+      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VIRCAM} $     &$ = Y_{AB}  - 0.601 $          \\
       &&&&&&\\
       $J_{\rm 2MASS}$       &   12350   &       10806  & 	14068  &  1624       &  $J_{\rm 2MASS}  $     & $= J_{AB}    - 0.894  $         \\
-      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.921  $         \\
+      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VIRCAM}  $     & $= J_{AB}    - 0.921  $         \\
       $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
@@
       $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
+      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VIRCAM}$      & $= H_{AB}  - 1.368 $        \\
       $H_{\rm 2MASS}$      & 16620        & 	14787  &   18231   & 2509      & $H_{\rm 2MASS}$      & $= H_{AB}  - 1.374 $        \\
       &&&&&&\\
-      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K$s$_{AB} - 1.83  $          \\ 
+      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VIRCAM}$      & $ = K$s$_{AB} - 1.83  $          \\ 
       $K$s$_{\rm 2MASS}$     &   21590    & 	19544  &   23552        &   2619      & $K$s$_{\rm 2MASS}$      & $ = K$s$_{AB} -  1.84  $          \\ 
-      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800         &   3510          & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
+      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800         &   3510          & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.90  $          \\ 
       &&&&&&\\

### 2019-02-17 tex/VHzQ.tex
further VHzQ.tex update

@@
 However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues.
-That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$, with $xyz$ detected in WISE {\bf NPR to double check!!'}.
+That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$ (with $x$ detected in WISE {\bf NPR to double check!!}).
 \citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.
@@
 We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
-luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars are still wait to be discovered.
+luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
 
@@
 
-Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
-As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
-Figures 7 and 10 in][]{Banados2016}.
-We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and reshift identifications.
-
-The breakdown of how many VH$z$Q each survey reports is given in
-Table~\ref{tab:surveys}. We assume the reader is familiar with the
-Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in
-Table~\ref{tab:surveys}.  ) survey and these surveys alone identified
-over half (54.6\%) of the VH$z$Q population. Data from the
-Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for
-13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
-combination of surveys is also vital for identifying VH$z$Qs. The
-UKIDSS Large Area Survey (ULAS) on its own, or in combination with
-other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
-including the highest-$z$ object. Where more than one survey is used
-for the high-redshift identification (e.g. via shorter-band veto and
-longer wavelength detection) we follow the discovery paper naming
-convention.
+Most of these objects are easily identified by their broad Ly$\alpha$
+emission line, \nv emission and characteristic shape blueward of
+1215\AA\ in the rest-frame. As we shall see, some of the recently
+discovered objects are close to the galaxy luminosity function
+characteristic luminosity $M^{*}$, and some have relatively weak or
+maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10
+in][]{Banados2016}. We leave aside detailed investigation and
+discussion into spectral features and line strengths, and take as
+given the published spectra and redshift identifications.
+
+The breakdown of how many VH$z$Q each survey reports is given in Table~\ref{tab:surveys}.
+The Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone identified over half (54.6\%) of the VH$z$Q population.
+Data from the Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for 13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}).
+The combination of surveys is also vital for identifying VH$z$Qs.
+The UKIDSS Large Area Survey (ULAS) on its own, or in combination with other surveys is responsible for 6.5\% of the sample (SUV+ULAS) including the highest-$z$ object.
+Where more than one survey is used for the high-redshift identification (e.g.
+via shorter-band veto and longer wavelength detection) we follow the discovery paper naming convention.
 
@@
 
-\section{A. Photometric Bands and Conversions}
+\section{A. Photometric Bands and Conversions}\label{sec:filters} 
     Due to the differing normalizations between the

### 2019-02-18 tex/VHzQ.tex
further tex/VHzQ updates

@@
 We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) in order to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
+2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
 
@@
 \hline  \hline
-Survey              & \# VH$z$Qs & (\%) & Notes/Survey reference  \\
+Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
 \hline  
@@
 The redshifts for the VH$z$Qs generally come from the measurement of
-broad UV/optical emission lines. Where there are far infra-red
-emission lines e.g. \cii~158 micron, we report these, but at the level
-of our current analysis broadline redshifts are sufficient.
+broad UV/optical emission lines. There are far infra-red emission
+lines e.g. \cii~158 micron available for several objects, but at the
+level of our current analysis broadline redshifts are sufficient.
 
@@
 \subsection{Optical Photometry}
-%\subsubsection{Pan-STARRS1 (PS1)} 
-We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.
-PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1.
-\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.
-The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.
-
-We query and return the mean PSF magnitudes from the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q sample.
-Details of our SQL and links to the main tables are given in Appendix~\ref{sec:PS1_SQL}.
-
-    \iffalse
-    \subsubsection{DECam} 
-    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
-    is a wide-field imager with a 2.2 degree diameter field of view 
-    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
-    at the Cerro Tololo International Observatory. We use data 
-    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
-    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
-    \fi
+We query the Panoramic Survey Telescope and Rapid Response System
+(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
+Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
+service at
+\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The
+Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of
+declination $\delta = -30$ degrees in the five $grizy$ filters.  PS1
+is the first part of Pan-STARRS to be completed and is the basis for
+the DR1. \citet{Chambers2016}, \citet{Magnier2016a},
+\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
+\citet{Flewelling2016} describe the instrument, survey, and data
+analyses.  The principal science product of the PS1 survey is the
+catalog accessible through the CasJobs interface.
+
+We query and return the mean PSF magnitudes from the $grizy$ filters
+({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q
+sample. Our SQL and links to the main PS1 DR1 tables are given in
+Appendix~\ref{sec:PS1_SQL}.
 
 \subsection{Near-infrared photometry}~\label{sec:NIR_data} 
-The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
-(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
-\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
-\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
-\citep[VDFS][]{VDFS}.
-
-We access both the WSA and the VSA and include all non-proprietary WFCAM data, which covers all
-public surveys and PI projects from Semester 05A to 1st January 2017, and all
-non-proprietary VISTA data, which covers all public surveys and PI projects from
-science verification (20091015) to 1st April 2016.
-
+The near-infrared data in this paper comes from the Wide Field
+Astronomy Unit's \href{https://www.roe.ac.uk/ifa/wfau/}{(WFAU)}
+Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
+\citep[WSA; ][]{Hambly2008} and VISTA-VIRCAM, the VISTA Science
+Archive \citep[VSA; ][]{Cross2012}. These archives were developed for
+the VISTA Data Flow System \citep[VDFS][]{VDFS}.
+
+We access both the WSA and the VSA and include all non-proprietary
+WFCAM data, which covers all public surveys and PI projects from
+Semester 05A to 2017-Jan-01, and all non-proprietary VISTA data, which
+covers all public surveys and PI projects from science verification on
+2009-Oct-15 to 2016-Apr-01.
+
+Here we are not just quering the WSA or VSA data tables. We are taking
+a list of objects (positions) are performing matched aperature
+(``forced'') photometry on the NIR imaging data. As such, we generate
+a set of tables that are different in subtle ways to the regular
+``Detection'' tables.  The two most important tables for our needs are
+the {\tt [w/v]serv1000MapRemeasurement} and {\tt
+[w/v]serv1000MapRemeasAver}.
+
+We produce and provide a two new databases with all the necessary
+quantaties and measurements to fully reproduce our tables, figures and
+results herein. Morever, these databases report considerably more
+information than we report here. Full documentation can be found at
+the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema
+Browser} and the
+\href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema
+Browser}.
+
+  \subsubsection{Averaging matched photometry}
   The data was processed using a matched-aperture photometry method
@@
   without necessarily knowing if there is a formal detection in the NIR
-photometry beforehand.  Full details of the matched-aperture pipeline
-will appear in a forthcoming paper, Cross et al.  2018, in prep, and
-has also been discussed in \citet{Cross2013}.
+  photometry beforehand. The matched-aperture pipeline is discussed in
+  \citet{Cross2013} and with fuller details to appear in a forthcoming
+  paper (Cross et al., 2019, in prep).
 
   We query the WSA and VSA performing matched-aperature photometry at
-the positions of our 463 VH$z$Qs. This database is world-readable and we give the full receipe
-and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.
-
-    \subsubsection{Averaging matched photometry}
+  the positions of our 463 VH$z$Qs. This database is world-readable and
+  we give the full receipe and relevant SQL queries for accessing both
+  databases in Appendix~\ref{sec:SQL} as well as online.
+
   The photometry in a single epoch image often has low
-    signal-to-noise.  The advantage of matched aperture photometry on QSOs
-    is that co-adding is relatively simple if each epoch is taken in the
-    same aperture and the aperture photometry has been corrected to
+  signal-to-noise.  The advantage of matched aperture photometry on
+  quasars is that co-adding is relatively simple if each epoch is taken
+  in the same aperture and the aperture photometry has been corrected to
   total. Indeed, the standard aperture corrections work well for point
@@
 
-    We average the aperture corrected calibrated fluxes (e.g. {\bf aperJky3}), and
-    then convert to magnitudes. Since we do not have a deep image for
-    each set of averages, we cannot calculate non-aperture corrected values, so the
-    photometry is only appropriate for point-sources.
+  We average the aperture corrected calibrated fluxes (e.g. {\bf
+  aperJky3}), and then convert to magnitudes. Since we do not have a
+  deep image for each set of averages, we cannot calculate non-aperture
+  corrected values, so the photometry is only appropriate for
+  point-sources.
 
@@
   spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
-    over all epochs. {\bf NJC: Should we add this table to suplemental online
-    only material?} The averaging process starts at the first epoch and works on.
+  over all epochs. The averaging process starts at the first epoch and works onwards 
+  from there. Again, we present these measurements in the new SQL tables.
 
@@
 
-    \subsubsection{Salient details of WSA and VSA}. 
-    %% N.B.!!!    WFAU archives more than just the NIR Surveys -- it archives *all* the WFCAM and VISTA programmes!!
-    In this study, we are not just quering the WSA or VSA data tables. 
-    We are taking a list of objects (positions) are performing matched aperature (``forced'') photometry on the NIR imaging data. 
-    As such, we generate a set of tables that are different in subtle ways to the regular ``Detection'' tables.
-
-    The two most important tables for our needs are the {\tt [w/v]serv1000MapRemeasurement} and {\tt [w/v]serv1000MapRemeasAver}.
-
-    Full documentation can be found at the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema Browser} 
-and the \href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema Browser}.
-
 \subsection{MIR data}
-Since we are concerned here with the very large area ($\gg1000$ deg$^2$) surveys, we leave exploration of the VH$z$Q population in e.g.
-the large Spitzer areal surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES; ][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey \citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field \citep[SSDF; ][]{Ashby2013}, to future investigation.
-This will also include a detailed study of MIR spectra e.g.
-\citet{Lambrides2018}.
-
-The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and NEOWISE (Mainzer et al.
-2011 ApJ, 731, 53) post-cryogenic survey phases.
+The MIR data for this study comes from the Wide-field Infrared Survey
+Explorer (WISE) mission, and we utlize data from the WISE cryogenic
+and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
+phases.
 
@@
 The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-{\bf Few more words here on the unWISE catalog}.
+%{\bf Few more words here on the unWISE catalog...}.
 
@@
 
-Figure~\ref{fig:Opt_colourredshift} presents the optical
-colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
-   \centering
-   \caption[]
-   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
-     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
-   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
-bigger gaps between subplots??}}
-   \label{fig:Opt_colourredshift}
- \end{figure*}
-
 \begin{figure*}
@@
 \end{figure*}
-
-\iffalse
-\subsection{SEDs and Dust properties of the VH$z$Qs}
-There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
-However, they are, for our purposes all roughly the same.
-
-\begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
-  \centering
-  \caption[]
-  {The rest-frame properties of the VH$z$Qs. }
-  \label{fig:RestWavelength_SEDs}
-\end{figure*}
-\fi
 

### 2019-02-18 tex/older_tex/VHzQ_20190218.tex
tex/older_tex/VHzQ_20190218.tex added

--- 2019-02-18 tex/VHzQ.tex
@@
 
+Figure~\ref{fig:Opt_colourredshift} presents the optical
+colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
+\begin{figure*}
+   \includegraphics[width=18.0cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
+   \centering
+   \caption[]
+   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
+     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
+   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
+bigger gaps between subplots??}}
+   \label{fig:Opt_colourredshift}
+ \end{figure*}
+
 \begin{figure*}
@@
 \end{figure*}
+
+\iffalse
+\subsection{SEDs and Dust properties of the VH$z$Qs}
+There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
+However, they are, for our purposes all roughly the same.
+
+\begin{figure*}
+  \includegraphics[width=18.0cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
+  \centering
+  \caption[]
+  {The rest-frame properties of the VH$z$Qs. }
+  \label{fig:RestWavelength_SEDs}
+\end{figure*}
+\fi
 

### 2019-02-18 tex/VHzQ.tex
tex/VHzQ.* update

@@
 \subsection{Optical Photometry}
-We query the Panoramic Survey Telescope and Rapid Response System
-(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
-Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
-service at
-\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The
-Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of
-declination $\delta = -30$ degrees in the five $grizy$ filters.  PS1
-is the first part of Pan-STARRS to be completed and is the basis for
-the DR1. \citet{Chambers2016}, \citet{Magnier2016a},
-\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
-\citet{Flewelling2016} describe the instrument, survey, and data
-analyses.  The principal science product of the PS1 survey is the
-catalog accessible through the CasJobs interface.
-
-We query and return the mean PSF magnitudes from the $grizy$ filters
-({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q
-sample. Our SQL and links to the main PS1 DR1 tables are given in
-Appendix~\ref{sec:PS1_SQL}.
+We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
+The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.
+PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1.
+\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.
+The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.
+
+The PS1 Casjobs SQL Server is located at
+\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
+The top level documentation is given
+\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
+while the description of tables is given
+\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}.
+
+The main tables are the
+\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
+objectThin}} and
+\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
+meanObject}} tables.  We query and return the mean PSF magnitudes from
+the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for
+our 463 VH$z$Q sample. Our SQL and links to the main PS1 DR1 tables
+are given at  Appendix~\ref{sec:PS1_SQL}.
 
@@
 
-%% \section{Notes on Individual Objects}
-%% \input{/cos_pc19a_npr/data/highest_z_QSOs/notes_on_individual_objects}
-
-\section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}
-The PS1 Casjobs SQL Server is located at
-\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
-The top level documentation is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
-while the description of tables is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}. The
-main tables are the
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
-objectThin}} and
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
-meanObject}} tables.
-
-\onecolumn
-\begin{lstlisting}[
-language=SQL,
-           showspaces=false,
-           basicstyle=\ttfamily,
-           numbers=left,
-           numberstyle=\tiny,
-           commentstyle=\color{gray}
-        ]
-SELECT s.ra, s.decl, 
-       o.objID, o.raMean, o.decMean, 
-       o.nDetections, o.ng, o.nr, o.ni, o.nz, o.ny, 
-       m.gMeanPSFMag, m.gMeanPSFMagErr,  m.gMeanPSFMagStd, 
-       m.rMeanPSFMag, m.rMeanPSFMagErr,  m.rMeanPSFMagStd, 
-       m.iMeanPSFMag, m.iMeanPSFMagErr,  m.iMeanPSFMagStd, 
-       m.zMeanPSFMag, m.zMeanPSFMagErr,  m.zMeanPSFMagStd, 
-       m.yMeanPSFMag, m.yMeanPSFMagErr,  m.yMeanPSFMagStd, 
-       s.jmag, s.jmag_error, s.hmag, s.hmag_error, s.kmag, s.kmag_error into mydb.MyTable_0 from MyDB.Ldwarfs as s
-
-cross apply fGetNearbyObjEq(s.ra,s.decl,2.0/60.0) nb
-inner join ObjectThin o on o.objid=nb.objid and o.nDetections>1 
-inner join MeanObject m on o.objid=m.objid  and o.uniquePspsOBid=m.uniquePspsOBid
-\end{lstlisting}
-\twocolumn
-
 \section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}

### 2019-04-22 tex/VHzQ.tex
wee tex/VHzQ.tex, .pdf update
VHzQ updated again

@@
 
+     There are 17 objects that have no NIR detections. 
+     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
+     have been observed, but are out of our queried time range. 
+     10 objects have not been observed (or at least the data is not in the WSA/VSA 
+     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
+     and cannot be observed.
+
         \subsubsection{Comparing WFCAM and VISTA}
@@
       %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
+       %%
+       %% http://svo2.cab.inta-csic.es/svo/theory/fps/index.php?mode=browse&gname=UKIRT&gname2=WFCAM
+      %%                                                                                     
+     %% emails around 16 Aug 2018, Carlos Rodrigo
+      %% 
+     %%     (-2.5)*(log10( ZP_in_Jy / 3631.0)) 
       \hline

### 2019-04-22 color_color/W1W2_hexplots.py

@@ -32,7 +32,10 @@ VHzQ = ascii.read(table)
 
 ##  Making the plot(s)
 ## 
-##     W2  vs.  W1-W2       (Assef et al. 2018 and the `R90' and `C75' samples) 
+##     W2  vs.  W1-W2
+##
+##    (e.g. Blain et al. 2013, Figure 1;
+##          Assef et al. 2018 and the `R90' and `C75' samples) 
 ##
 plt.rcParams.update({'font.size': 14})
 #plt.style.use('dark_background')

### 2019-05-08 tex/VHzQ.tex
VHzQ.tex update

@@
 %%                                                                           
-%%  
+%%   The `compliation' paper for all z>5 spec-z quasars, here called "Very High Redshift Quasars" (VHzQs) and 
+%%   looking into their IR properties. Motivations include putting a list of all the VHzQ in one place, looking for 
+%%   signs of super-critical accretion and having a super-set of objects and their given parameters ahead of 
+%%   JWST GO Cycle 1. 
 %%									    
@@
 
-\iffalse
-\section*{TO DOs}
-{\bf For NPR: }
-\begin{itemize}
-\item Concentrate on reporting NIR and W1/W2 figures and tables
-\item SED dust plots 
-\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
-\item Check for NIR and MIR variabilty with the Wu quasar
-\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
-%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
-\end{itemize}
-
-\noindent
-{\bf For NJGC: }
-\begin{itemize}
-\item Write the NIR data section(s) 
-\end{itemize}
-
-\noindent
-{\bf For Both: }
-\begin{itemize}
-\item Need to decide what mags and mag system we are reporting, especially in the 
-NIR...
-\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
-\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
-\end{itemize}
-\fi
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts
-$z\geq5.00$) are excellent probes of the early Universe. This includes
-studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
-reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
-supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
-Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and
-early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017,
-Bosman2017}.
-
-Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a
-viable mechanism to explain the high, potentially super-Eddington,
-luminosity and rapid growth of supermassive black holes in the early
-universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
-one could expect VH$z$Qs to potentially vary in luminosity as they go
-through phases of super-critical accretion. These signatures of
-photometric variability should be looked for, noting the rest-frame
-optical emission is redshifted into the observed near-infrared (NIR)
-at redshifts $z>5$. Fortunately, data are now in place from deep,
-wide-field NIR instruments and surveys such as the Wide Field Camera
-(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
-in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
-the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
-Southern Hemisphere, that are necessary for identifying VH$z$Qs.
-
-Quasars are known to be prodigious emitters of infrared emission,
-thought to be from the thermal emission of dust grains heated by
-continuum emission from the accretion disc
-\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
-Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m allow
-discrimination between AGN\footnote{Historically, ``quasars'' and
-``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects. In recognition of the
-fact that both terms describe accreting supermassive black holes, 
-we use these terms interchangeably, with a preference for quasar, 
-since we are generally in the higher-$L$ regime
-\citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the
-1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g.,
-][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b,
-Timlin2016} as well as between AGN and star-forming galaxies due to
-the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
+Very high redshift quasars (VH$z$Q; defined here to have redshifts $z\geq5.00$) are excellent probes of the early Universe.
+This includes studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review, Mortlock2016}, the formation and build-up of supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
+
+Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a viable mechanism to explain the high, potentially super-Eddington, luminosity and rapid growth of supermassive black holes in the early universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014, Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}.
+Thus, one could expect VH$z$Qs to potentially vary in luminosity as they go through phases of super-critical accretion.
+These signatures of photometric variability should be looked for, noting the rest-frame optical emission is redshifted into the observed near-infrared (NIR) at redshifts $z>5$.
+Fortunately, data are now in place from deep, wide-field NIR instruments and surveys such as the Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the Southern Hemisphere, that are necessary for identifying VH$z$Qs.
+
+Quasars are known to be prodigious emitters of infrared emission, thought to be from the thermal emission of dust grains heated by continuum emission from the accretion disc \citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
+Observations in the mid-infrared, e.g.
+$\sim$3-30$\mu$m allow discrimination between AGN\footnote{Historically, ``quasars'' and ``Active Galactic Nuclei (AGN)'' have described different
+luminosity/classes of objects.
+In recognition of the fact that both terms describe accreting supermassive black holes, we use these terms interchangeably, with a preference for quasar, since we are generally in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b, Timlin2016} as well as between AGN and star-forming galaxies due to the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
 >3\mu$m \citep[e.g., ][]{Yan2007, Tielens2008}.
@@
 
-Critically, we now have available to us new W1 and W2 photometry from
-the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
-WISE-selected catalogue that is based on significantly deeper imaging
-and has a more extensive modeling of crowded regions than the ALLWISE
-release. For the first time in a catalogue, unWISE takes advantage of
-the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
-Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
-achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
-additional depth is a significant advantage in the detection and study
-of VH$z$Qs in the 3-5 micron regime.
+Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
+For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
+This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
 
@@
 \section{Method and Data}
-Quasars are generally identified by photometric selection followed by
-spectroscopic confirmation. Here, we reverse this method obtaining
-first a list of spectroscopic quasars and then obtain photometric
-information.
+Quasars are generally identified by photometric selection followed by spectroscopic confirmation.
+Here, we reverse this method obtaining first a list of spectroscopic quasars and then obtain photometric information.
 
 We have compiled a list of 463 quasars with redshifts $z\geq5.00$.
-We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018-Dec-31.
+We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483).
 We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
@@
 The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-%%
 For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
@@
 
-Most of these objects are easily identified by their broad Ly$\alpha$
-emission line, \nv emission and characteristic shape blueward of
-1215\AA\ in the rest-frame. As we shall see, some of the recently
-discovered objects are close to the galaxy luminosity function
-characteristic luminosity $M^{*}$, and some have relatively weak or
-maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10
-in][]{Banados2016}. We leave aside detailed investigation and
-discussion into spectral features and line strengths, and take as
-given the published spectra and redshift identifications.
+Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
+As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
+Figures 7 and 10 in][]{Banados2016}.
+We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and redshift identifications.
 

### 2019-05-09 tex/VHzQ.tex
Updated NIR QSO numbers and photometric offsets

@@
 
-  We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are 
-  detected in the VISTA VSA database with 114 objects in common with both
+  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars are 
+  detected in the VISTA VSA database with 130 objects in common with both
   WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
@@
         \hline  
-        Any band ($ZYJHK/K_{s}$   &  394  (92.9) \\
-        $Z$-band    &  72  (17.0) \\
-        $Y$-band    &  249  (58.7) \\
-        $J$-band    &  391  (92.2) \\
-        $H$-band    &  258  (60.8) \\
-        $K$ or $Ks$-band    &  297  ( ) \\
+        Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
+        $Z$-band    &  75  (16.1) \\
+        $Y$-band    &  273  (59.0) \\
+        $J$-band    &  447  (96.5) \\
+        $H$-band    &  269  (58.1) \\
+        $K$ or $Ks$-band    &  322  (69.5) \\
         \hline  \hline
@@
 
-     There are 17 objects that have no NIR detections. 
-     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
+     There are 14 objects that have no NIR detections. 
+     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769, DELSJ0411-0907) 
      have been observed, but are out of our queried time range. 
-     10 objects have not been observed (or at least the data is not in the WSA/VSA 
+     6 objects have not been observed (or at least the data is not in the WSA/VSA 
      archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
@@
         \subsubsection{Comparing WFCAM and VISTA}
-        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
+        There are 130 overlapping QSOs between WFCAM and VISTA.  Using the
         {\tt VegaToAB} value\footnote{What is this exactly??} to put these
@@
             \hline
-            $Z$                 &  19.3 	& 2 \\
-            $Y$                 &  66.2 	& 48 \\
-            $J$                  &    3.2 	& 105 \\
-            $H$                 &  19.3     &  89 \\
-            $K_{\rm s}$/$K$ &  12.7     & 93 \\
+            $Z$                 &  23.2 	& 3 \\
+            $Y$                 &  57.3 	& 53 \\
+            $J$                  &    2.1 	& 106 \\
+            $H$                 &  45.8     &  96 \\
+            $K_{\rm s}$/$K$ &  25.2     & 110 \\
             \hline  \hline

### 2019-05-10 tex/VHzQ.tex
VHzQ.tex polish

@@
 
-Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
+Tables~\ref{tab:WSA_wWISE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
+
+\input{table_tex/WSA_wWISE}
 
@@
      There are 14 objects that have no NIR detections. 
-     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769, DELSJ0411-0907) 
-     have been observed, but are out of our queried time range. 
+     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) 
+     have been observed (by VHS) but are out of our queried time range. 
      6 objects have not been observed (or at least the data is not in the WSA/VSA 

### 2019-05-28 tex/VHzQ.tex
data data/WSA_VSA/BestVSA_magnitudes_v201* update

@@
 \begin{abstract}
-In this paper, we, for the first time since the discovery of $z\geq5$
-quasars, assemble all spectroscopically confirmed very high redshift
-quasars in one catalogue.  In particular we present the near
-($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
-all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
-Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
+%For the first time since the discovery of $z\geq5.00$ quasars, 
+%In this paper, 
+We assemble a catalogue of 463 
+spectroscopically confirmed very high ($z\geq5.00$) redshift 
+quasars %in one catalogue.  
+%In particular we present the near
+and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties. 
+%of all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
+Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for
 photometric variability in the near-infrared that might be expected
-from Super-Eddington accretion and find {\it blah}.  We present a
-comprehensive series of colour-redshift and colour-colour plots and
-make inferences into the hot dust properties of the very high-redshift
-quasar population. Extrapolating the known quasar luminosity function
+from super-Eddington accretion and find {\it blah}.  
+%%
+% We present a comprehensive series of colour-redshift and colour-colour plots and make inferences into the hot dust properties of the very high-redshift quasar population. aq
+Extrapolating the known quasar luminosity function
 we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
@@
 {\bf NJC: What about NIR light-curves / combined light-curves}
+
+%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
+
+%% I have also checked for QSOs with large differences in magnitude.
+At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
+In fact initially there were 100 QSO/filter combinations.
+However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
+and >5 average flux error.
+This removed 80-90\%.
+I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
+This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
+
+The two with large differences are:
+
+SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
+
+SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
 

### 2019-05-28 tex/VHzQ.tex
tables_for_paper update

@@
 \begin{abstract}
-%For the first time since the discovery of $z\geq5.00$ quasars, 
-%In this paper, 
-We assemble a catalogue of 463 
-spectroscopically confirmed very high ($z\geq5.00$) redshift 
-quasars %in one catalogue.  
-%In particular we present the near
-and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties. 
-%of all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
-Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for
-photometric variability in the near-infrared that might be expected
-from super-Eddington accretion and find {\it blah}.  
-%%
-% We present a comprehensive series of colour-redshift and colour-colour plots and make inferences into the hot dust properties of the very high-redshift quasar population. aq
-Extrapolating the known quasar luminosity function
-we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
-current datasets have been discovered. 
-All the data, analysis codes and plots used and generated here can be found at:
-\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
+We assemble a catalogue of 463 spectroscopically confirmed very high
+($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$
+and $K$) infrared and mid-infrared (WISE) properties.  Using archival
+WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
+in the near-infrared that might be expected from super-Eddington
+accretion and find {\it blah}.  Extrapolating the known quasar
+luminosity function we suggest that $x$\% of the possibly detected
+$z\geq5$ quasars in the current datasets have been discovered.  All
+the data, analysis codes and plots used and generated here can be
+found at: \href{https://github.com/d80b2t/VHzQ}{\tt
+github.com/d80b2t/VHzQ}.
 \end{abstract}
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts $z\geq5.00$) are excellent probes of the early Universe.
-This includes studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review, Mortlock2016}, the formation and build-up of supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
-
-Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a viable mechanism to explain the high, potentially super-Eddington, luminosity and rapid growth of supermassive black holes in the early universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014, Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}.
-Thus, one could expect VH$z$Qs to potentially vary in luminosity as they go through phases of super-critical accretion.
-These signatures of photometric variability should be looked for, noting the rest-frame optical emission is redshifted into the observed near-infrared (NIR) at redshifts $z>5$.
-Fortunately, data are now in place from deep, wide-field NIR instruments and surveys such as the Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the Southern Hemisphere, that are necessary for identifying VH$z$Qs.
-
-Quasars are known to be prodigious emitters of infrared emission, thought to be from the thermal emission of dust grains heated by continuum emission from the accretion disc \citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
-Observations in the mid-infrared, e.g.
-$\sim$3-30$\mu$m allow discrimination between AGN\footnote{Historically, ``quasars'' and ``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects.
-In recognition of the fact that both terms describe accreting supermassive black holes, we use these terms interchangeably, with a preference for quasar, since we are generally in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b, Timlin2016} as well as between AGN and star-forming galaxies due to the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
->3\mu$m \citep[e.g., ][]{Yan2007, Tielens2008}.
-
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of a quasar without hot-dust emission in a sample of 21 $z\approx6$ quasars.
-Such apparently hot-dust-free quasars have no counterparts at low redshift.
-Moreover, those authors demonstrate that the hot-dust abundance in the 21 quasars builds up in tandem with the growth of the central black hole.
-But understanding how dust first forms and appears in the central engine remains an open question \citep{WangR2008, WangR2011}.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
-The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.
-\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$.
-However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues.
-That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$ (with $x$ detected in WISE {\bf NPR to double check!!}).
-\citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.
-
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
-This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
-
-Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars.
-Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
-luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
-
-This paper is organized as follows.
-In Section 2, we present the assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have compiled.
-We then give a high-level overview of the photometric surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we ...
-and In Section 4 we ...
-We conclude in Section 5 and present all the necessary details to obtain our dataset in the Appendices.
-
-We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.
-This includes the near-infrared, as well as the mid-infrared magnitudes.
-Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters.
-We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
+Very high redshift quasars (VH$z$Q; defined here to have redshifts
+$z\geq5.00$) are excellent probes of the early Universe. This includes
+studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
+reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
+supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
+Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and
+early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017,
+Bosman2017}.
+
+Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a
+viable mechanism to explain the high, potentially super-Eddington,
+luminosity and rapid growth of supermassive black holes in the early
+universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
+Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
+one could expect VH$z$Qs to potentially vary in luminosity as they go
+through phases of super-critical accretion. These signatures of
+photometric variability should be looked for, noting the rest-frame
+optical emission is redshifted into the observed near-infrared (NIR)
+at redshifts $z>5$. Fortunately, data are now in place from deep,
+wide-field NIR instruments and surveys such as the Wide Field Camera
+(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
+in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
+the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
+Southern Hemisphere, that are necessary for identifying VH$z$Qs.
+
+Quasars are known to be prodigious emitters of infrared emission,
+thought to be from the thermal emission of dust grains heated by
+continuum emission from the accretion disc
+\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014,
+Hickox2017}. Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
+allow discrimination between AGN\footnote{Historically, ``quasars''
+and ``Active Galactic Nuclei (AGN)'' have described different
+luminosity/classes of objects. In recognition of the fact that both
+terms describe accreting supermassive black holes, we use these terms
+interchangeably, with a preference for quasar, since we are generally
+in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive
+galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at
+$z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004,
+Stern2005, Richards2006b, Timlin2016} as well as between AGN and
+star-forming galaxies due to the presence of Polycyclic Aromatic
+Hydrocarbon (PAHs) at $\lambda >3\mu$m \citep[e.g., ][]{Yan2007,
+Tielens2008}.
+
+\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
+a quasar without hot-dust emission in a sample of 21 $z\approx6$
+quasars. Such apparently hot-dust-free quasars have no counterparts at
+low redshift. Moreover, those authors demonstrate that the hot-dust
+abundance in the 21 quasars builds up in tandem with the growth of the
+central black hole. But understanding how dust first forms and appears
+in the central engine remains an open question \citep{WangR2008,
+WangR2011}.
+
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths
+of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue
+release, contains nearly 750 million detections at
+high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
+of which over 4.5M AGN candidates have been identified with 90\%
+reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
+mid-infrared (MIR) detections of 17 (55\%) of the then known 31
+quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
+WISE `All-Sky' data release, as opposed to the superior AllWISE
+catalogues. That sample only examined the 31 known $z>6$ quasars; our
+sample has 170 objects with redshift $z \geq 6.00$ (with 108 detected
+in WISE). \citet{Banados2016} reports WISE W1, W2, W3 and W4
+magnitudes for the Panoramic Survey Telescope and Rapid Response
+System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with
+no further investigation into the reddest WISE waveband for the
+VH$z$Qs.
+
+Critically, we now have available to us new W1 and W2 photometry from
+the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
+WISE-selected catalogue that is based on significantly deeper imaging
+and has a more extensive modeling of crowded regions than the ALLWISE
+release. For the first time in a catalogue, unWISE takes advantage of
+the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
+Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
+achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
+additional depth is a significant advantage in the detection and study
+of VH$z$Qs in the 3-5 micron regime.
+
+Here we present for the first time the combined near-infrared
+properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
+all the spectroscopically known $z\geq5.00$ quasars. Our motivations
+are numerous and include: {\it (i)} establishing the first complete
+catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
+{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
+available for the quasars; {\it (iii)} making the first study of near-
+and mid-IR variability of the VHzQ population and {\it (iv)}
+establishing the photometric properties for upcoming surveys and
+telescopes including the Large Synoptic Survey Telescope
+(LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it
+Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
+and the {\it James Webb Space Telescope}
+(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
+We
+chose redshift $z=5.00$ as our lower redshift limit due to a
+combination of garnishing a large sample, adequately spanning physical
+properties (e.g. luminosity, age of the Universe) and to highlight the
+parts of $L-z$ parameter space where $z>5$ quasars still wait to be
+discovered.
+
+This paper is organized as follows.  In Section 2, we present the
+assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
+compiled. We then give a high-level overview of the photometric
+surveys and datasets we use and present the photometry of the
+VH$z$Qs. In Section 3 we ... and In Section 4 we ... We conclude in
+Section 5 and present all the necessary details to obtain our dataset
+in the Appendices.
+
+We present all our photometry and magnitudes on the AB zero-point
+system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
+near-infrared, as well as the mid-infrared
+magnitudes. Appendix~\ref{sec:filters} gives the AB to Vega transforms
+for a wide range of optical, NIR and MIR filters. We use a flat
+$\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm
+M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et
+al. 2016) to be consistent with \citet{Banados2016} and all logarithms
+are to the base 10.
 
@@
 \section{Method and Data}
-Quasars are generally identified by photometric selection followed by spectroscopic confirmation.
-Here, we reverse this method obtaining first a list of spectroscopic quasars and then obtain photometric information.
-
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$.
-We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483).
-We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
-The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}.
-The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}.
-The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
+Quasars are generally identified by photometric selection followed by
+spectroscopic confirmation. Here, we reverse this method obtaining
+first a list of spectroscopic quasars and then obtain photometric
+information.
+
+We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
+use all the $z\geq5.00$ quasars that have been discovered,
+spectroscopically confirmed and published as of 2018 December 31 (MJD
+58483). We then obtain optical, near-infrared and mid-infrared
+photometry for the spectral dataset. The optical data comes from the
+Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)
+survey \citep{Chambers2016}. The near-infrared data comes from two
+sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
+primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
+Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
+VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
+mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
+Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
+Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
+the wavelength and normalised transmission of the filters in question.
 
@@
 \citet{Zeimann2011}.
-%We have obtained a list of 463 spectroscopically confirmed quasars with redshifts $z\geq5.00$.
-
-Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
-As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
-Figures 7 and 10 in][]{Banados2016}.
-We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and redshift identifications.
-
-The breakdown of how many VH$z$Q each survey reports is given in Table~\ref{tab:surveys}.
-The Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone identified over half (54.6\%) of the VH$z$Q population.
-Data from the Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for 13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}).
-The combination of surveys is also vital for identifying VH$z$Qs.
-The UKIDSS Large Area Survey (ULAS) on its own, or in combination with other surveys is responsible for 6.5\% of the sample (SUV+ULAS) including the highest-$z$ object.
-Where more than one survey is used for the high-redshift identification (e.g.
-via shorter-band veto and longer wavelength detection) we follow the discovery paper naming convention.
+
+Most of these objects are easily identified by their broad Ly$\alpha$
+emission line, \nv emission and characteristic shape blueward of
+1215\AA\ in the rest-frame. As we shall see, some of the recently
+discovered objects are close to the galaxy luminosity function
+characteristic luminosity $M^{*}$, and some have relatively weak or
+maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10
+in][]{Banados2016}. We leave aside detailed investigation and
+discussion into spectral features and line strengths, and take as
+given the published spectra and redshift identifications.
+
+The breakdown of how many VH$z$Q each survey reports is given in
+Table~\ref{tab:surveys}. The Sloan Digital Sky Survey (SDSS) and the
+Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone
+identified over half (54.6\%) of the VH$z$Q population. Data from the
+Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for
+13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
+combination of surveys is also vital for identifying VH$z$Qs. The
+UKIDSS Large Area Survey (ULAS) on its own, or in combination with
+other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
+including the highest-$z$ object. Where more than one survey is used
+for the high-redshift identification (e.g. via shorter-band veto and
+longer wavelength detection) we follow the discovery paper naming
+convention.
 
@@
 This inheritance depends on details of the PSF normalization at large radii, which is uncertain.
-Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
-
-Thus to convert unWISE Vega magnitudes onto the AB system, we have    
+Subtracting 4 millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
+
+Thus to convert unWISE Vega magnitudes onto the AB system, we have:     
 \begin{eqnarray*}
         {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
-        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339 
+        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339. 
 \end{eqnarray*}
 %Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
-those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
+%those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
 These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
-%We note though that 
-%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
-%- what the source of the trend is,
-%- which of unWISE and AllWISE is correct, or
-%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
+%%
+%% We note though that 
+%%  Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
+%%   - what the source of the trend is,
+%%   - which of unWISE and AllWISE is correct, or
+%%   - where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
 
@@
 
-\input{table_tex/WSA_wWISE}
-
-\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+%\input{table_tex/WSA_wWISE}
+
+%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+%\footnotesize
+%\tiny
+\begin{landscape}
+      \input{../tables_for_paper/output_table}
+\end{landscape}
+%\normalsize
 
@@
 
+%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
+
+%% I have also checked for QSOs with large differences in magnitude.
+At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
+In fact initially there were 100 QSO/filter combinations.
+However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
+and >5 average flux error.
+This removed 80-90\%.
+I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
+This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
+
+The two with large differences are:
+
+SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
+
+SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
+
+        We investigate the VH$z$Qs in the UltraVISTA field. 
+        UltraVISTA is...
+        %% 
+        One detail to note is that depths quoted in the UltraVISTA Data Releases are for more realistic 
+        1.8 arcsec diameter apertures (J. Dunlop, priv. comm.).
+
     \subsection{Detection Rates in the MIR}
@@
 
-%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
-
-%% I have also checked for QSOs with large differences in magnitude.
-At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
-In fact initially there were 100 QSO/filter combinations.
-However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
-and >5 average flux error.
-This removed 80-90\%.
-I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
-This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
-
-The two with large differences are:
-
-SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
-
-SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
-
-\subsection{Colours}
-Currently, very high-redshift quasars are identified by their morphology, flux and colours in optical and infrared imaging data \citet{Fan1999, Mortlock2012} Quasars are generally selected to be point sources, but  be outliers from the stellar locus in colour space.
-For VH$z$Qs, the main technique is to look for objects with extreme optical-to-near-infrared colours The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
-There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
-the blue or red end respectively. Hmmm....}
-   \label{fig:SpecType_vs_NIRcolors}
- \end{figure*}
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-}
-   \label{fig:SpecType_vs_W1W2_W2W3colors}
- \end{figure*}
-
-\subsection{L-$z$ Plane}
-Having obtained an as-near-to-homogenous set of photometry as we can, 
-we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
-sample and in particulare the absolute magnitude at rest-frame 1450\AA\ , $M_{1450}$, 
-which is a key physical quantity and goes directly towards the quasar luminosity 
-function and thus the reionization of hydrogen calculation.
-
-We calculate the Distance Modulus in the normal fashion, 
-\begin{equation}
-m_{1450} - M_{1450} = 5 \log \left (    \frac{ D_{\rm L}(z)}{\rm Mpc}  \right )  + 25 + K_{\rm corr}(X,z)
-\end{equation}
-where $m_{1450}$ is the apparent magnitude at 1450\AA\ ,  
-%$M_{1450}$ is the absolute magnitude at 1450 \AA\ , 
-$D_{\rm L}(z)$ is the luminosity distance and 
-$K_{\rm corr}(X,z)$ is the $K$-correction which corrects for the effects of redshifting of the bandpass and the spectrum.
-
-The $m_{1450}$ apparent magnitude is derived from the $z-$, $y/Y-$ or $J-$band photometery.
-
-The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
-sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
-for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
-cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.
-
-\citet{Ross2013} has a detailed discussion of the $K$-correction (see that papers' Appendix B). 
-The key result in that paper is, if quasars are described as having a power-law slope, 
-$\alpha^{\nu}$ in spectral flux density, i.e., $f_\nu(\nu) \propto \nu^{\alpha_{\nu}}$ (as is conventional) 
-then 
-\begin{equation}
-K_{\rm corr}(z) = -2.5 (1 + \alpha_{\nu}) \log[1 + z].
-\end{equation}
-Here the $[-2.5 \log(1 + z)]$ term corrects for the effective narrowing of the filter width with redshift, (the ``bandpass correction'') and the $[-2.5 \alpha^{\nu} \log(1 + z)]$ term takes into account the spectral index correction.
-The bandpass correction is approximately $\approx -1.945$ at redshift $z=5$ decreasing to $-2.32$ at redshift $z=7.50$.
-
-%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
-
-\begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
-  \centering
-  \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:Lz}
-\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% 
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Surface Density of VH$z$Qs}
 
@@
 
-\newpage
+%\newpage
 
 \appendix
-%\section{Filter Curves}\label{sec:filters} 
-%From the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
-
-\section{A. Photometric Bands and Conversions}\label{sec:filters} 
-    Due to the differing normalizations between the
-    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
-    our data in the  purest sense, all the NIR magnitudes from UKIDSS
-    (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett2006}.
-
-    Although ULAS magnitudes are reported in terms of Vega and SDSS
-    magnitudes are reported in AB terms for the most part whenever an
-    optical-NIR color was calculated both magnitudes were left in their
-    default term.
-
-\begin{table*}
-  \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth2011}. 
-CTIO/DECam, PanSTARRS/PS1, LSST
-%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
-Filter only values. 
-All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 
-%%
-%%
-From \citet{GonzalezFernandez2018} 
-$Z_{\rm AB}   -  Z_{\rm Vega}  = 0.502$;  
-$Y_{\rm AB}  -  Y_{\rm Vega}    = 0.600 $;
-$J_{\rm AB}   -  J_{\rm Vega}    = 0.916  $;
-$H_{\rm AB}  -  H_{\rm Vega}    = 1.366 $;
-$Ks_{\rm AB}  -  Ks_{\rm Vega}  = 1.827 $;
-%%
-and the CASU Vega to AB conversions v1.3:: 
-	Z,Y,J,H,Ks were: 0.524, 0.618, 0.937, 1.384, 1.839. 
-%%
-So, $\Delta$(vs. Gonzalez-Fernandez)::
-	(11.2,     1.1,    5.4,     1.6,    0.1) millimags. 
-$\Delta$(vsCASU v1.3)::
-	(-10.8, -16.9, -15.6,  -16.4, -11.9) millimags. 
-}
-    \setlength{\tabcolsep}{4pt}
-     \begin{tabular}{l r r r  c l l}
-      %% https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
-      %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
-       %%
-       %% http://svo2.cab.inta-csic.es/svo/theory/fps/index.php?mode=browse&gname=UKIRT&gname2=WFCAM
-      %%                                                                                     
-     %% emails around 16 Aug 2018, Carlos Rodrigo
-      %% 
-     %%     (-2.5)*(log10( ZP_in_Jy / 3631.0)) 
-      \hline
-      \hline
-      Band & $\lambda_{\rm eff}  $ 
-              &  $\lambda_{\rm min} $ 
-              & $\lambda_{\rm max} $ 
-              & W$_{\rm eff}$
-              & \multicolumn{2}{c}{AB - Vega  Transformations} \\
-      \hline
-      % {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
-      % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\
-      $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
-      $g_{\rm DECam}$  &      4734     &   3939    &    5528   &   1133        &  $g_{\rm DECam} $    &$  = g_{\rm AB} + 0.083 $ \\	     
-       $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
-      &&&&&&\\
-      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\
-      $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
-      $r_{\rm LSST}$       &     6139    &	  5375    &    7055   &   1338      &  $r_{\rm LSST}   $       &$    = r_{\rm AB} - 0.155 $ \\	
-      $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
-      &&&&&&\\
-      $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
-      $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
-      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6
-      $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
-      &&&&&&\\
-      $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
-      $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = Z_{\rm AB} - 0.513 $     \\
-      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = Z_{\rm AB} - 0.514 $     \\
-      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = Z_{\rm AB} - 0.512$     \\
-      $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
-      &&&&&&\\
-      $y_{\rm PS1}$       &       9603    &  9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
-      $y_{\rm LSST}$      &       9677   &	 9089    &    10859  &     810         &  $y_{\rm LSST}  $      &$    = y_{\rm AB} - 0.546 $ \\
-      $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
-      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\
-      $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VIRCAM} $     &$ = Y_{AB}  - 0.601 $          \\
-      &&&&&&\\
-      $J_{\rm 2MASS}$       &   12350   &       10806  & 	14068  &  1624       &  $J_{\rm 2MASS}  $     & $= J_{AB}    - 0.894  $         \\
-      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VIRCAM}  $     & $= J_{AB}    - 0.921  $         \\
-      $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      &&&&&&\\
-      $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
-      &&&&&&\\
-      $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VIRCAM}$      & $= H_{AB}  - 1.368 $        \\
-      $H_{\rm 2MASS}$      & 16620        & 	14787  &   18231   & 2509      & $H_{\rm 2MASS}$      & $= H_{AB}  - 1.374 $        \\
-      &&&&&&\\
-      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VIRCAM}$      & $ = K$s$_{AB} - 1.83  $          \\ 
-      $K$s$_{\rm 2MASS}$     &   21590    & 	19544  &   23552        &   2619      & $K$s$_{\rm 2MASS}$      & $ = K$s$_{AB} -  1.84  $          \\ 
-      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800         &   3510          & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.90  $          \\ 
-      &&&&&&\\
-      WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\
-      WISE W2               &    46028    &    39633  &    53414   &  10423    & W2                        &   = W2$_{\rm AB} - 3.339$ \\
-      WISE W3               &  115608    &    74430  &  172613   &  55056    & W3                        &   = W3$_{\rm AB} - 5.174$ \\
-      WISE W4               &  228172    &  195201  &  279107   &  41017    & W4                        &   = W4$_{\rm AB} - 6.66$ \\
-      \hline
-      \hline
-      \label{tab:filter_details}
-    \end{tabular}
-     \end{center}
-\end{table*}
-https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
 
@@
 
-\onecolumn
-\input{SQL_examples_VSA}
-\twocolumn
+%\onecolumn
+%\input{SQL_examples_VSA}
+%\twocolumn
 

### 2019-05-28 tables_for_paper/survey_origin.py

@@ -2,11 +2,11 @@
 A simple little bit of code to figure out which survey the VHzQs came
 from.  I haven't gone "fully, fully" here's the plug in .tex, but
 could easily see that happening and would be happy for it!!
+
 v1.00    Wed Dec  5 19:14:34 GMT 2018
 '''
 
 import numpy as np
-import pandas as pd
 
 from astropy.io    import fits
 from astropy.io    import ascii
@@ -21,9 +21,10 @@ table    = path+filename
 
 VHzQ_list = ascii.read(table)
 
-## Just a little bit of info 
+## just a little bit of info 
 print('type(VHzQ_list)', type(VHzQ_list))
 
+## the column names
 VHzQ_list.colnames
 
 ## Column 'na' has the original survey designations

### 2019-05-28 tex/DistanceModulus.tex
tex/DistanceModulus.tex added

--- 2019-05-08 tex/VHzQ.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                           
-%%   The `compliation' paper for all z>5 spec-z quasars, here called "Very High Redshift Quasars" (VHzQs) and 
-%%   looking into their IR properties. Motivations include putting a list of all the VHzQ in one place, looking for 
-%%   signs of super-critical accretion and having a super-set of objects and their given parameters ahead of 
-%%   JWST GO Cycle 1. 
-%%									    
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[usenatbib]{mnras}
-
-\input {format}
-
-\begin{document}
-
-\title[Very high-$z$ Quasars]
-        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
-\author[Ross \& Cross]
-       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
-\\ 
-$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
-}
-
-\maketitle
-\begin{abstract}
-In this paper, we, for the first time since the discovery of $z\geq5$
-quasars, assemble all spectroscopically confirmed very high redshift
-quasars in one catalogue.  In particular we present the near
-($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
-all 463 spectroscopically confirmed redshift $z\geq5.00$ quasars.
-Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
-photometric variability in the near-infrared that might be expected
-from Super-Eddington accretion and find {\it blah}.  We present a
-comprehensive series of colour-redshift and colour-colour plots and
-make inferences into the hot dust properties of the very high-redshift
-quasar population. Extrapolating the known quasar luminosity function
-we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
-current datasets have been discovered. 
-All the data, analysis codes and plots used and generated here can be found at:
-\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
-\end{abstract}
-
-\begin{keywords}
-Astronomical data bases: surveys -- 
-Quasars: general -- 
-galaxies: evolution -- 
-galaxies: infrared.
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts $z\geq5.00$) are excellent probes of the early Universe.
-This includes studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review, Mortlock2016}, the formation and build-up of supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
-
-Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a viable mechanism to explain the high, potentially super-Eddington, luminosity and rapid growth of supermassive black holes in the early universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014, Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}.
-Thus, one could expect VH$z$Qs to potentially vary in luminosity as they go through phases of super-critical accretion.
-These signatures of photometric variability should be looked for, noting the rest-frame optical emission is redshifted into the observed near-infrared (NIR) at redshifts $z>5$.
-Fortunately, data are now in place from deep, wide-field NIR instruments and surveys such as the Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the Southern Hemisphere, that are necessary for identifying VH$z$Qs.
-
-Quasars are known to be prodigious emitters of infrared emission, thought to be from the thermal emission of dust grains heated by continuum emission from the accretion disc \citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
-Observations in the mid-infrared, e.g.
-$\sim$3-30$\mu$m allow discrimination between AGN\footnote{Historically, ``quasars'' and ``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects.
-In recognition of the fact that both terms describe accreting supermassive black holes, we use these terms interchangeably, with a preference for quasar, since we are generally in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b, Timlin2016} as well as between AGN and star-forming galaxies due to the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
->3\mu$m \citep[e.g., ][]{Yan2007, Tielens2008}.
-
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of a quasar without hot-dust emission in a sample of 21 $z\approx6$ quasars.
-Such apparently hot-dust-free quasars have no counterparts at low redshift.
-Moreover, those authors demonstrate that the hot-dust abundance in the 21 quasars builds up in tandem with the growth of the central black hole.
-But understanding how dust first forms and appears in the central engine remains an open question \citep{WangR2008, WangR2011}.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
-The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.
-\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$.
-However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues.
-That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$ (with $x$ detected in WISE {\bf NPR to double check!!}).
-\citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.
-
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
-This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
-
-Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars.
-Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
-luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
-
-This paper is organized as follows.
-In Section 2, we present the assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have compiled.
-We then give a high-level overview of the photometric surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we ...
-and In Section 4 we ...
-We conclude in Section 5 and present all the necessary details to obtain our dataset in the Appendices.
-
-We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.
-This includes the near-infrared, as well as the mid-infrared magnitudes.
-Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters.
-We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-%%trim=l b r t
-%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
-  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
-  \centering
-  \vspace{-12pt}
-  \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.
-    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
-    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
-    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
-    [NJC: Do we use the W-band anywhere?]
-    The WISE passbands  W1-4 are also presented.
-    The quasar spectrum is a composite based on \citet{VdB2001} and 
-    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
-  }
-  \label{fig:filters}
-\end{figure}
-
-\vspace{-16pt}
-\section{Method and Data}
-Quasars are generally identified by photometric selection followed by spectroscopic confirmation.
-Here, we reverse this method obtaining first a list of spectroscopic quasars and then obtain photometric information.
-
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$.
-We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483).
-We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
-The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}.
-The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}.
-The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
-
-\subsection{Spectroscopy} 
-We compile the list of all known, spectroscopically confirmed
-quasars from the literature.  This list was complied from a range of
-surveys and papers.  Specifically, we use data from:
-\citet{Banados2014, Banados2016, Banados2018}, 
-\citet{Becker2015}, 
-\citet{Calura2014}, 
-\citet{Carilli2007, Carilli2010}, 
-\citet{Carnall2015}, 
-\citet{Cool2006}, 
-\citet{DeRosa2011}, 
-\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
-\citet{Goto2006}, 
-\citet{Ikeda2017}, 
-\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
-\citet{Kashikawa2015}, 
-\citet{Koptelova2017}, 
-\citet{Kim2015, Kim2018},  
-\citet{Kurk2007, Kurk2009}, 
-\citet{Leipski2014}, 
-\citet{Mahabal2005}, 
-\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
-\citet{Mazzucchelli2017}, 
-\citet{Morganson2012}, 
-\citet{Mortlock2009, Mortlock2011},
-\citet{McGreer2006, McGreer2013},  
-\citet{Reed2015, Reed2017}, 
-\citet{Stern2007},  
-\citet{Tang2017}, 
-\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
-\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
-\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
-\citet{Wu2015} 
-\citet{YangJ2018a, YangJ2018b}  
-and 
-\citet{Zeimann2011}. 
-%We have obtained a list of 463 spectroscopically confirmed quasars with redshifts $z\geq5.00$.
-
-Most of these objects are easily identified by their broad Ly$\alpha$ emission line, \nv emission and characteristic shape blueward of 1215\AA\ in the rest-frame.
-As we shall see, some of the recently discovered objects are close to the galaxy luminosity function characteristic luminosity $M^{*}$, and some have relatively weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g.
-Figures 7 and 10 in][]{Banados2016}.
-We leave aside detailed investigation and discussion into spectral features and line strengths, and take as given the published spectra and redshift identifications.
-
-The breakdown of how many VH$z$Q each survey reports is given in Table~\ref{tab:surveys}.
-The Sloan Digital Sky Survey (SDSS) and the Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone identified over half (54.6\%) of the VH$z$Q population.
-Data from the Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for 13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}).
-The combination of surveys is also vital for identifying VH$z$Qs.
-The UKIDSS Large Area Survey (ULAS) on its own, or in combination with other surveys is responsible for 6.5\% of the sample (SUV+ULAS) including the highest-$z$ object.
-Where more than one survey is used for the high-redshift identification (e.g.
-via shorter-band veto and longer wavelength detection) we follow the discovery paper naming convention.
-
-\begin{table}
-\begin{tabular}{l r r l}
-\hline  \hline
-Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
-\hline  
-  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
-  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
-  DELS               &   16    &   ( 3.46)    &  \citet{Dey2018} \\
-  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
-  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
-  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
-  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
-  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
-  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
-  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
-  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
-  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
- SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
-%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
-  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
-  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
-  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
-  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
-  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
-  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
-  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
-  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
-\hline  \hline
-\end{tabular}
-\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
-  Recent survey name and acronyms include: 
-  $^{a}$DESI Legacy Imaging Survey; 
-  $^{b}$SDWISE = SDSS+WISE; 
-  $^{a}$SUV  = SDSS-ULAS/VHS; 
-  $^{c}$VDES = VHS/VIKING+DES; 
-%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
-}
-      \label{tab:surveys}
-\end{table}
-
-\begin{figure}
-%%trim=l b r t
-  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Nofz/Nofz_0pnt075bins_20181211.png}
-  \centering
-  \vspace{-12pt}
-  \caption[]
-  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
-    The bins are $\delta-z=0.075$ in width. }
-  \label{fig:Nofz}
-\end{figure}
-
-The redshifts for the VH$z$Qs generally come from the measurement of
-broad UV/optical emission lines. There are far infra-red emission
-lines e.g. \cii~158 micron available for several objects, but at the
-level of our current analysis broadline redshifts are sufficient.
-
-\begin{table}
-\centering
-\begin{tabular}{l r  r}
-\hline \hline
-$z \geq$  & Age / Myr & No. of objects \\
-\hline 
-7.50         &    700         &   1   \\
-7.00         &    767         &   4   \\
-6.78         &    800         &  14   \\
-6.50         &    845         &  40   \\
-6.19         &   900          &  86   \\
-6.00         &   937          &  170   \\
-5.70         & 1000          &  267   \\
-5.00         & 1180          &  463   \\
-\hline \hline
-\end{tabular}
-\caption{The number of objects at or above a given redshift. 
-The age of the Universe in megayears is also given. }
-      \label{tab:ages}
-\end{table}
-
-The number of objects at or above various redshifts, along with the 
-corresponding age of the Universe is given in Table~\ref{tab:ages}.
-
-The $N(z)$ redshift histogram is given for the sample in Figure~\ref{fig:Nofz}. 
-We split the contribution up by survey. For clarity we show the individual 
-surveys of SDSS, PS1, HSC, the ULAS detection, and tally the remaining 
-surveys together (``various''). In Section~\ref{sec:Lz} we discuss the form 
-of the $N(z)$ as well as the coverage of the luminosity-redshift $L-z$ plane.
-
-\subsection{Optical Photometry}
-We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.
-PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1.
-\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.
-The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.
-
-The PS1 Casjobs SQL Server is located at
-\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
-The top level documentation is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
-while the description of tables is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}.
-
-The main tables are the
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
-objectThin}} and
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
-meanObject}} tables.  We query and return the mean PSF magnitudes from
-the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for
-our 463 VH$z$Q sample. Our SQL and links to the main PS1 DR1 tables
-are given at  Appendix~\ref{sec:PS1_SQL}.
-
-\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
-The near-infrared data in this paper comes from the Wide Field
-Astronomy Unit's \href{https://www.roe.ac.uk/ifa/wfau/}{(WFAU)}
-Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
-\citep[WSA; ][]{Hambly2008} and VISTA-VIRCAM, the VISTA Science
-Archive \citep[VSA; ][]{Cross2012}. These archives were developed for
-the VISTA Data Flow System \citep[VDFS][]{VDFS}.
-
-We access both the WSA and the VSA and include all non-proprietary
-WFCAM data, which covers all public surveys and PI projects from
-Semester 05A to 2017-Jan-01, and all non-proprietary VISTA data, which
-covers all public surveys and PI projects from science verification on
-2009-Oct-15 to 2016-Apr-01.
-
-Here we are not just quering the WSA or VSA data tables. We are taking
-a list of objects (positions) are performing matched aperature
-(``forced'') photometry on the NIR imaging data. As such, we generate
-a set of tables that are different in subtle ways to the regular
-``Detection'' tables.  The two most important tables for our needs are
-the {\tt [w/v]serv1000MapRemeasurement} and {\tt
-[w/v]serv1000MapRemeasAver}.
-
-We produce and provide a two new databases with all the necessary
-quantaties and measurements to fully reproduce our tables, figures and
-results herein. Morever, these databases report considerably more
-information than we report here. Full documentation can be found at
-the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema
-Browser} and the
-\href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema
-Browser}.
-
-  \subsubsection{Averaging matched photometry}
-  The data was processed using a matched-aperture photometry method
-  where flux is measured at the spectroscopic position of the quasar,
-  without necessarily knowing if there is a formal detection in the NIR
-  photometry beforehand. The matched-aperture pipeline is discussed in
-  \citet{Cross2013} and with fuller details to appear in a forthcoming
-  paper (Cross et al., 2019, in prep).
-
-  We query the WSA and VSA performing matched-aperature photometry at
-  the positions of our 463 VH$z$Qs. This database is world-readable and
-  we give the full receipe and relevant SQL queries for accessing both
-  databases in Appendix~\ref{sec:SQL} as well as online.
-
-  The photometry in a single epoch image often has low
-  signal-to-noise.  The advantage of matched aperture photometry on
-  quasars is that co-adding is relatively simple if each epoch is taken
-  in the same aperture and the aperture photometry has been corrected to
-  total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperature photometry, where the
-  individual epochs are taken from multiple projects with different
-  pointings and orientations, should help with issues such as scattered
-  light, pixel distortion and aperture corrections.
-
-  We average the aperture corrected calibrated fluxes (e.g. {\bf
-  aperJky3}), and then convert to magnitudes. Since we do not have a
-  deep image for each set of averages, we cannot calculate non-aperture
-  corrected values, so the photometry is only appropriate for
-  point-sources.
-
-  \begin{equation}
-    \bar{F} = \frac{\sum_i^N (w_i\,F_i)}{\sum_i^N w_i}  
-    \label{eq:avg}
-  \end{equation}
-  where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
-  averaged such as the aperture corrected calibrated flux in a $1\arcsec$ aperture
-  ({\bf aperJky3}) and $\bar{F}$ is the weighted mean average of this parameter.
-  The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
-  $w_i=0$ if an epoch is excluded for quality control purposes.
-
-  We calculate a set of averaged catalogues, for each pointing and filter, based
-  on the requirements in \verb+RequiredMapAverages+, in these cases over time
-  spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
-  over all epochs. The averaging process starts at the first epoch and works onwards 
-  from there. Again, we present these measurements in the new SQL tables.
-
-  We detect 304 unique quasars in the WFCAM WSA database, 203 quasars are 
-  detected in the VISTA VSA database with 114 objects in common with both
-  WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
-
-\subsection{MIR data}
-The MIR data for this study comes from the Wide-field Infrared Survey
-Explorer (WISE) mission, and we utlize data from the WISE cryogenic
-and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
-phases.
-
-We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.
-More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}.
-The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-%{\bf Few more words here on the unWISE catalog...}.
-
-All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux.
-The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}.
-This inheritance depends on details of the PSF normalization at large radii, which is uncertain.
-Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
-
-Thus to convert unWISE Vega magnitudes onto the AB system, we have    
-\begin{eqnarray*}
-        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
-        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339 
-\end{eqnarray*}
-%Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
-those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
-These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
-%We note though that 
-%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
-%- what the source of the trend is,
-%- which of unWISE and AllWISE is correct, or
-%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
-
-For the our MIR variability investigations, we do not use the unWISE coadds, but instead use 
-the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE 2018 Data Release}.
-NEOWISE 2018 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired between 2016 December 13 and 2017 December 13 UTC, which was the fourth year of survey operations of the Near-Earth Object Wide-field Infrared Survey Explorer Reactivation Mission (NEOWISE; Mainzer et al.
-2014, ApJ, 792, 30).
-The fourth year NEOWISE data products are concatenated with those from the first three years into a single archive.
-
-The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October.
-Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
-
-Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
-
-\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%  S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-Having collated the sample of 463 VH$z$Qs, and obtained their optical,
-near- and mid-infrared photometry we report here the various
-photometric properites of the quasars.
-
-First, we will concentrate on detection rate in the infrared, go on to
-report on the color-redshift and color-color properties of our sample
-and then report on how the current sample populates the
-luminosity-redshift $Lz$-plane.
-
-    %\subsection{Detection Rates in the optical}
-
-    \subsection{Detection Rates in the NIR}
-    Table~\ref{tab:nir_detection} gives the detection rates for the 
-    VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
-    The first thing to note is that the coverage of the NIR surveys 
-    for example from the UKIDSS LAS and VISTA VHS, does
-    not overlap the full area for where the VH$z$Qs are detected.
-
-    \begin{table}
-          \centering
-
-      \begin{tabular}{l r l}
-        \hline  \hline
-        Selection   & number detected (\%) \\
-        \hline  
-        Any band ($ZYJHK/K_{s}$   &  394  (92.9) \\
-        $Z$-band    &  72  (17.0) \\
-        $Y$-band    &  249  (58.7) \\
-        $J$-band    &  391  (92.2) \\
-        $H$-band    &  258  (60.8) \\
-        $K$ or $Ks$-band    &  297  ( ) \\
-        \hline  \hline
-      \end{tabular}
-      \caption{Detection rate of VH$z$Qs in the near-infrared.}
-      \label{tab:nir_detection}
-    \end{table}
-
-     There are 17 objects that have no NIR detections. 
-     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
-     have been observed, but are out of our queried time range. 
-     10 objects have not been observed (or at least the data is not in the WSA/VSA 
-     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
-     and cannot be observed.
-
-        \subsubsection{Comparing WFCAM and VISTA}
-        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
-        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
-        objects on the same AB system, and for each object compared the two
-        measurements. First, the calculated weighted average (calibrated flux)
-        in each filter of both and calculated the ratio and difference between
-        each measurement and the average.  Then for each filter we calculated
-        the weighted average of the differences (in mag) for each instrument
-        to see if there were significant offsets. The results are given in
-        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
-        offset is the $Y$-band. All of the VISTA averages are negative and all
-        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
-        slightly dodgy, given the different shapes of the filters.
-        \begin{table}
-          \centering
-          \begin{tabular}{l r r}
-            \hline  \hline
-            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
-            -  WFCAM)      &                                        &  objects \\
-            \hline
-            $Z$                 &  19.3 	& 2 \\
-            $Y$                 &  66.2 	& 48 \\
-            $J$                  &    3.2 	& 105 \\
-            $H$                 &  19.3     &  89 \\
-            $K_{\rm s}$/$K$ &  12.7     & 93 \\
-            \hline  \hline
-          \end{tabular}
-          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
-          \label{tab:WFCAM_vs_VISTA}
-        \end{table}
-
-    \subsection{Detection Rates in the MIR}
-    Unlike the NIR coverage, the WISE
-    satellite and mission performed an all-sky survey, so the location of
-    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
-    ALLWISE survey depends heavily on sky location, with locations near
-    the Ecliptic Poles having the highest number of exposures.
-
-    Before reporting on the detection rates, we investigate this
-    effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
-    versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
-    coverage depth, in each corresponding band. In the two shorter bands
-    W1/2 we see the clear and expected trend for brighter objects to have
-    larger SNR, and also for the higher signal to noise for objects with
-    more exposures at a given magnitude. The behaviour for the W3/4 bands
-    is different, with two populations clearly evident in W3 and although
-    a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
-    no obvious R.A./Declination dependence seen, this behaviour is
-    explained by the fact that there are non-detectiopns in W3/4 for
-    objects (with high W1/2 SNR) that are reported in the ALLWISE
-    catalogue.
-
-    For the 278 VH$z$Q with coverage detections, the mean number of
-    exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
-    minimum number of exposures 17 and 12, and the maximum number or
-    exposures being 114 (for both bands).  For the W3/4 filters, the
-    corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
-    5.8 and 6.8 and 69 (for both bands). These values are direclty from
-    the {\tt w$x$cov} enteries in the 
-    \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.
-
-    \begin{figure}
-      %% trim=l b r t
-      \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
-      \centering
-      \vspace{-14pt}
-      \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
-        colour coded by w$x$cov the mean coverage depth, in each corresponding band.
-      }
-      \label{fig:WISEmag_vs_coverage}
-    \end{figure}
-
-    Table~\ref{tab:mir_detection} gives the detection rates for the
-    VH$z$Qs in the MIR WISE W1-4 bands. 
-    \begin{table}
-      \begin{tabular}{l r l}
-        \hline  \hline
-        Selection   & number detected (\%) \\
-        \hline  
-        W1 SNR $> 2.0$                                             &  275  (64.9) \\
-        W2 SNR $> 2.0$                                            &   255 (60.1) \\
-        W1 $\land$ W2 SNR $> 2.0$                         &  \\
-        W3 SNR $> 2.0$                                            &  99    (23.3) \\
-        W4 SNR $> 2.0$                                            &  29    (6.8) \\
-        Any W1/2/3/4 SNR $>2.0$                           & \\
-        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
-        \hline  \hline
-      \end{tabular}
-      \caption{}
-      \label{tab:mir_detection}
-    \end{table}
-
-    \begin{table}
-      \begin{tabular}{l r l}
-        \hline  \hline
-         \multirow{2}{*}{Selection}   & number detected \\ 
-                                                   & (\% of full specrta) \\
-        \hline  
-        From ``Source'', ``Rejects'',                    & 245, 40  (67.2) \\
-        W1 SNR $> 2.0$                                       &  279  (65.8) \\
-        W2 SNR $> 2.0$                                       &  258 (60.8) \\
-        W1 $\land$ W2 SNR $> 2.0$                    & 253   (59.7)  \\
-        W3 SNR $> 2.0$                                     &  97    (22.9) \\
-        W4 SNR $> 2.0$                                     &  33    (7.8) \\
-%        Any W1/2/3/4 SNR $>2.0$                            & \\
-        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ &  3 (0.7)\\
-        \hline  \hline
-      \end{tabular}
-      \caption{Data from the AllWISE Source Catalog and AllWISE Reject Table, from the 
-\href{https://irsa.ipac.caltech.edu/cgi-bin/Gator/nph-scan?submit=Select&projshort=WISE} {{\tt NASA/IPAC  Infrared Science Archive}}}
-      \label{tab:mir_detection}
-    \end{table}
-
-    \begin{figure}
-      %% trim=l b r t
-      \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
-      \centering
-      \vspace{-14pt}
-      \caption[]{WISE signal-to-noise measures for the four bands, as well
-        as for (W1-W2) colour.  The points are colour coded by redshift.}
-      \label{fig:WISEmag_vs_coverage}
-    \end{figure}
-
-    \citet{Blain2013}
-
-    Recently, \citet{Assef2018} released two large catalogues of AGN 
-    candidates identified across 30,000 deg$^2$ of extragalactic sky 
-    from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
-    contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
-    AGN candidates per deg$^2$) while the ``C75'' catalog 
-    consists of 20.9M AGN candidates at 75\% completeness (and 
-    ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-    out catalogue of 463 VH$z$Qs with these catalogues, produces 
-    42 matches with	the R90 sample and 98 matches with the C75 sample. 
-    Both catalogues unsurprisingly match to the ultraluminous quasar 
-    SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
-    mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
-    matches J1342+0928 \citep{Banados2018}.
-
-    %\subsubsection{
-    Very High-$z$ Quasars Detected in WISE W3 and W4.
-
-    \begin{figure}
-      \centering
-      \includegraphics[width=8.5cm]
-      {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
-      \vspace{-16pt}
-      \caption[]
-      {Histogram showing the number of NEOWISE-R epochs and detections there are for each 
-        VH$z$Q.} 
-      \label{fig:MIR_LC_epochs}
-    \end{figure}
-
-\subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m_{\rm accr}}$.
-A consequence of this would be that these quasar exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra.
-We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
-As a guide, \civ enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57.
-\mgii enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
-
-Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we
-
-\begin{figure}
-  \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
-  \centering
-  \caption[]
-  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
-    Red points are the W1 band; cyan points the W2 band.} 
-  \label{fig::MIR_LC_3egs}
-\end{figure}
-
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
-Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and
-associated colour changes. Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
-{\bf NJC: What about NIR light-curves / combined light-curves}
-
-\subsection{Colours}
-Currently, very high-redshift quasars are identified by their morphology, flux and colours in optical and infrared imaging data \citet{Fan1999, Mortlock2012} Quasars are generally selected to be point sources, but  be outliers from the stellar locus in colour space.
-For VH$z$Qs, the main technique is to look for objects with extreme optical-to-near-infrared colours The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
-There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
-the blue or red end respectively. Hmmm....}
-   \label{fig:SpecType_vs_NIRcolors}
- \end{figure*}
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-}
-   \label{fig:SpecType_vs_W1W2_W2W3colors}
- \end{figure*}
-
-\subsection{L-$z$ Plane}
+\subsection{The L-$z$ Plane}
 Having obtained an as-near-to-homogenous set of photometry as we can, 
@@
 \end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Conclusions}
-\label{sec:conclusions}
-In this study, we have, for the first time, ompiled the list of all
-$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
-($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
-objects, given their detection rates and SEDs. We find that:
-
-%%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have.
-
-\begin{itemize}
-    \item Lorem ipsum dolor sit amet, consectetur adipiscing
-      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
-      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
-      convallis ac. 
-    \item Fusce pellentesque condimentum dolor, quis vehicula
-      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
-      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
-      diam eu blandit. Donec in lacinia libero.
-    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-      euismod. Cras vel auctor neque. Nam quis diam risus.
-\end{itemize}
-Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
-eu elit massa. Nulla vel lacus lorem. Proin et lobortis
-tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
-nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
-ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
-eget tempor elementum, lectus urna feugiat nisi, eget sagittis.
-
-\subsection*{Author Contributions}   
-N.P.R.
-initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
-%%
-N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
-%%
-
-\subsection*{Availability of Data and computer analysis codes} 
-All materials, databases, data tables and code are fully available at: 
-\href{https://github.com/d80b2t/VHzQ}{\tt https://github.com/d80b2t/VHzQ}
-
-\section*{Acknowledgements}
-NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.
-
-We thank Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA), and 
-also the VISTA Science Archive (VSA). We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
-
-This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
-\citep[][]{Taylor2005, Taylor2011}.
-%%
-This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
-a community-developed core Python package for Astronomy 
-\citep{AstropyCollaboration2013, AstropyCollaboration2018}.
-
-The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
-been made possible through contributions by the Institute for
-Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
-the Max-Planck Society and its participating institutes, the Max
-Planck Institute for Astronomy, Heidelberg and the Max Planck
-Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
-University, Durham University, the University of Edinburgh, the
-Queen's University Belfast, the Harvard-Smithsonian Center for
-Astrophysics, the Las Cumbres Observatory Global Telescope Network
-Incorporated, the National Central University of Taiwan, the Space
-Telescope Science Institute, the National Aeronautics and Space
-Administration under Grant No. NNX08AR22G issued through the Planetary
-Science Division of the NASA Science Mission Directorate, the National
-Science Foundation Grant No. AST-1238877, the University of Maryland,
-Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
-and the Gordon and Betty Moore Foundation.
-
-This project used data obtained with the Dark Energy Camera (DECam)
-and the NOAO Data Lab, The Data Lab is operated by the National
-Optical Astronomy Observatory, the national center for ground-based
-nighttime astronomy in the United States operated by the Association
-of Universities for Research in Astronomy (AURA) under cooperative
-agreement with the National Science Foundation.
-
-This publication makes use of data products from the Wide-field
-Infrared Survey Explorer, which is a joint project of the University
-of California, Los Angeles, and the Jet Propulsion
-Laboratory/California Institute of Technology, and NEOWISE, which is a
-project of the Jet Propulsion Laboratory/California Institute of
-Technology. WISE and NEOWISE are funded by the National Aeronautics
-and Space Administration.
-
-CasJobs was originally developed by the Johns Hopkins University/
-Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
-used version 3.5.16 to construct CasJobs-based tools for GALEX,
-Kepler, the Hubble Source Catalog, and PanSTARRS.
-
-This research has made use of the SVO Filter Profile Service
-(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
-MINECO through grant AyA2014-55216 
-%%
-The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
-describes the Spanish VO Filter Profile Service. 
-The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html
-
-\newpage
-
-\appendix
-%\section{Filter Curves}\label{sec:filters} 
-%From the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
-
-\section{A. Photometric Bands and Conversions}\label{sec:filters} 
-    Due to the differing normalizations between the
-    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
-    our data in the  purest sense, all the NIR magnitudes from UKIDSS
-    (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett2006}.
-
-    Although ULAS magnitudes are reported in terms of Vega and SDSS
-    magnitudes are reported in AB terms for the most part whenever an
-    optical-NIR color was calculated both magnitudes were left in their
-    default term.
-
-\begin{table*}
-  \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth2011}. 
-CTIO/DECam, PanSTARRS/PS1, LSST
-%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
-Filter only values. 
-All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 
-%%
-%%
-From \citet{GonzalezFernandez2018} 
-$Z_{\rm AB}   -  Z_{\rm Vega}  = 0.502$;  
-$Y_{\rm AB}  -  Y_{\rm Vega}    = 0.600 $;
-$J_{\rm AB}   -  J_{\rm Vega}    = 0.916  $;
-$H_{\rm AB}  -  H_{\rm Vega}    = 1.366 $;
-$Ks_{\rm AB}  -  Ks_{\rm Vega}  = 1.827 $;
-%%
-and the CASU Vega to AB conversions v1.3:: 
-	Z,Y,J,H,Ks were: 0.524, 0.618, 0.937, 1.384, 1.839. 
-%%
-So, $\Delta$(vs. Gonzalez-Fernandez)::
-	(11.2,     1.1,    5.4,     1.6,    0.1) millimags. 
-$\Delta$(vsCASU v1.3)::
-	(-10.8, -16.9, -15.6,  -16.4, -11.9) millimags. 
-}
-    \setlength{\tabcolsep}{4pt}
-     \begin{tabular}{l r r r  c l l}
-      %% https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
-      %% http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab
-       %%
-       %% http://svo2.cab.inta-csic.es/svo/theory/fps/index.php?mode=browse&gname=UKIRT&gname2=WFCAM
-      %%                                                                                     
-     %% emails around 16 Aug 2018, Carlos Rodrigo
-      %% 
-     %%     (-2.5)*(log10( ZP_in_Jy / 3631.0)) 
-      \hline
-      \hline
-      Band & $\lambda_{\rm eff}  $ 
-              &  $\lambda_{\rm min} $ 
-              & $\lambda_{\rm max} $ 
-              & W$_{\rm eff}$
-              & \multicolumn{2}{c}{AB - Vega  Transformations} \\
-      \hline
-      % {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
-      % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\
-      $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
-      $g_{\rm DECam}$  &      4734     &   3939    &    5528   &   1133        &  $g_{\rm DECam} $    &$  = g_{\rm AB} + 0.083 $ \\	     
-       $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
-      &&&&&&\\
-      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\
-      $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
-      $r_{\rm LSST}$       &     6139    &	  5375    &    7055   &   1338      &  $r_{\rm LSST}   $       &$    = r_{\rm AB} - 0.155 $ \\	
-      $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
-      &&&&&&\\
-      $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
-      $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
-      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6
-      $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
-      &&&&&&\\
-      $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
-      $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
-      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = Z_{\rm AB} - 0.513 $     \\
-      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = Z_{\rm AB} - 0.514 $     \\
-      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = Z_{\rm AB} - 0.512$     \\
-      $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
-      &&&&&&\\
-      $y_{\rm PS1}$       &       9603    &  9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
-      $y_{\rm LSST}$      &       9677   &	 9089    &    10859  &     810         &  $y_{\rm LSST}  $      &$    = y_{\rm AB} - 0.546 $ \\
-      $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
-      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\
-      $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VIRCAM} $     &$ = Y_{AB}  - 0.601 $          \\
-      &&&&&&\\
-      $J_{\rm 2MASS}$       &   12350   &       10806  & 	14068  &  1624       &  $J_{\rm 2MASS}  $     & $= J_{AB}    - 0.894  $         \\
-      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VIRCAM}  $     & $= J_{AB}    - 0.921  $         \\
-      $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      &&&&&&\\
-      $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
-      &&&&&&\\
-      $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VIRCAM}$      & $= H_{AB}  - 1.368 $        \\
-      $H_{\rm 2MASS}$      & 16620        & 	14787  &   18231   & 2509      & $H_{\rm 2MASS}$      & $= H_{AB}  - 1.374 $        \\
-      &&&&&&\\
-      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VIRCAM}$      & $ = K$s$_{AB} - 1.83  $          \\ 
-      $K$s$_{\rm 2MASS}$     &   21590    & 	19544  &   23552        &   2619      & $K$s$_{\rm 2MASS}$      & $ = K$s$_{AB} -  1.84  $          \\ 
-      $K_{\rm WFCAM}$     &    22010     &    20290 &    23800         &   3510          & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.90  $          \\ 
-      &&&&&&\\
-      WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\
-      WISE W2               &    46028    &    39633  &    53414   &  10423    & W2                        &   = W2$_{\rm AB} - 3.339$ \\
-      WISE W3               &  115608    &    74430  &  172613   &  55056    & W3                        &   = W3$_{\rm AB} - 5.174$ \\
-      WISE W4               &  228172    &  195201  &  279107   &  41017    & W4                        &   = W4$_{\rm AB} - 6.66$ \\
-      \hline
-      \hline
-      \label{tab:filter_details}
-    \end{tabular}
-     \end{center}
-\end{table*}
-https://www.gemini.edu/sciops/instruments/magnitudes-and-fluxes
-
-\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
-Here we give the receipe and SQL that returned the near-infrared photometry 
-for the VH$z$Qs from the  WFCAM Science Archive.
-
-The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
-Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
-with these credentials::
-\begin{itemize}
-    \item Username: {\tt WSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt nonsurvey}
-\end{itemize}
-Then going to the
-\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
-Query}} page the Database release {\tt WSERV1000v20180716} can be
-accessed which contains all the data we use here.
-
-We {\it nota bene} a few things. First, the quantity {\tt aperJky3}
-and {\tt aperJky3Err} are found in the {\tt wserv1000MapRemeasAver}
-and {\tt wserv1000MapRemeasurement}, so care has to be taken to return
-unique column names (otherwise e.g.
-\href{http://docs.astropy.org/en/stable/io/fits/}{astropy.io.fits}
-will crash).  As such, we alias {\tt aver.aperJky3} to {\tt
-aperJky3Aver} and likewise for the error quantity. Aliases will be
-necessary in some cases anyway, because some queries can be done
-sensibly on multiple instances of the same table. Other times, one may
-join tables on quantities such as {\tt catalogueID} or {\tt
-apertureID}, where you are meaning the same thing, but aliases would
-again be sensible.
-
-Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
-used directly. To return values in degrees, use a selection with an alias, e.g. 
-{\tt RA as RADeg} and {\tt DEC as DECDeg}.
-
-\onecolumn
-\input{SQL_examples_WSA}
-\twocolumn
-
-\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL}
-In a very similar manner to the WSA, we give here the details on how to access
-the VISTA Science Archive (VSA)
-
-At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
-with these credentials::
-\begin{itemize}
-    \item Username: {\tt VSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt proprietary}
-\end{itemize}
-Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20180716}.
-
-\onecolumn
-\input{SQL_examples_VSA}
-\twocolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\bibliographystyle{apj}
-\bibliographystyle{mn2e}
-\bibliography{tester_mnras}
-
-\end{document}

### 2019-05-28 tex/older_tex/VHzQ_20180527.tex
tex/older_tex/VHzQ_20180527.tex

--- 2019-05-08 tex/VHzQ.tex
@@
 
-Tables~\ref{tab:THE_TABLE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
-
-\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+Tables~\ref{tab:WSA_wWISE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
+
+%\input{table_tex/WSA_wWISE}
+
+%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
+
+\input{../tables_for_paper/output_table}
 
@@
 
-     There are 17 objects that have no NIR detections. 
-     2 of these (PSOJ053.9605-15.7956 and PSO J056.7168-16.4769) 
-     have been observed, but are out of our queried time range. 
-     10 objects have not been observed (or at least the data is not in the WSA/VSA 
+     There are 14 objects that have no NIR detections. 
+     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) 
+     have been observed (by VHS) but are out of our queried time range. 
+     6 objects have not been observed (or at least the data is not in the WSA/VSA 
      archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
@@
         \end{table}
+
+        We investigate the VH$z$Qs in the UltraVISTA field. 
+        UltraVISTA is...
+        %% 
+        One detail to note is that depths quoted in the UltraVISTA Data Releases are for more realistic 
+        1.8 arcsec diameter apertures (J. Dunlop, priv. comm.).
 

### 2019-05-28 tex/VHzQ.tex
wee tex/VHzQ.tex update

@@
 \section{Surface Density of VH$z$Qs}
+One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
+are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
+so, how many are still to be discovered and confirmed spectroscopcially?
+
+Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
+exponential decline to describe the space density of VH$z$Qs at high
+redshifts, e.g.
+\begin{equation}
+\rho(z, {\rm M}_{1450} \propto 10^{k (z)}
+\end{equation}
+where $z$ is the sample redshift. 
+%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
 

### 2019-05-29 tex/VHzQ.tex
VHzQ.tex update

@@
 
+At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.
+
+Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).
+
+Then calculate the clipped median and standard deviation, 
+\begin{equation}
+1.48 \times \sigma_{median} / \bar{epsilon}
+\end{equation}
+where $\bar{epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
+%%
+With this definition, although some of the objects have very well sampled, 
+`Average' light curves where you are averaging over e.g. a month, or two weeks.
+
+Longer time-series, better SNR and moreover, $(1+z)$. 
+Just selecting things that would
+%%
+Doing this independtly in each band...
+%Variation
+
+%% 
+%% Object numbers: 54 VSA   MMTJ0215-0529,
+%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
+%%
+objiD 164 is SDSSJ1000+0234, faint; very faint. 
+SHELLQsJ0220-0432: (qso59) show this too. 
+CFHQSJ0216-0455
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-30 tex/VHzQ.tex
Among other things VHzQ.tex updated; Sections 1 and 2 should be good to go

@@
 %%                                                                           
-%%   The `compliation' paper for all z>5 spec-z quasars, here called "Very High Redshift Quasars" (VHzQs) and 
-%%   looking into their IR properties. Motivations include putting a list of all the VHzQ in one place, looking for 
-%%   signs of super-critical accretion and having a super-set of objects and their given parameters ahead of 
-%%   JWST GO Cycle 1. 
+%%    The `compliation' paper for all z>5 spec-z quasars, here called
+%%    "Very High Redshift Quasars" (VHzQs) and looking into their IR
+%%    properties. Motivations include putting a list of all the VHzQ in one
+%%    place, looking for signs of super-critical accretion and having a
+%%    super-set of objects and their given parameters ahead of JWST GO Cycle 1.
 %%									    
@@
 surveys and datasets we use and present the photometry of the
-VH$z$Qs. In Section 3 we ... and In Section 4 we ... We conclude in
-Section 5 and present all the necessary details to obtain our dataset
-in the Appendices.
+VH$z$Qs. In Section 3 we investigate the variability properties of the
+VH$z$Qs, looking for evidence of super-critical accretion. In Section
+4 we calculate how many $z>5$ quasars we should expect to find in
+current datasets. We conclude in Section 5 and present all the
+necessary details to obtain our dataset in the Appendices.
 
@@
 surveys of SDSS, PS1, HSC, the ULAS detection, and tally the remaining 
-surveys together (``various''). In Section~\ref{sec:Lz} we discuss the form 
-of the $N(z)$ as well as the coverage of the luminosity-redshift $L-z$ plane.
-
-\subsection{Optical Photometry}
-We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}.
-The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.
-PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1.
-\citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.
-The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.
-
-The PS1 Casjobs SQL Server is located at
-\href{http://mastweb.stsci.edu/ps1casjobs}{mastweb.stsci.edu/ps1casjobs}.
-The top level documentation is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs}{here}
-while the description of tables is given
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+Source+extraction+and+catalogs#PS1Sourceextractionandcatalogs}{here}.
-
-The main tables are the
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+ObjectThin+table+fields}{{\tt
-objectThin}} and
-\href{https://outerspace.stsci.edu/display/PANSTARRS/PS1+MeanObject+table+fields}{{\tt
-meanObject}} tables.  We query and return the mean PSF magnitudes from
-the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for
-our 463 VH$z$Q sample. Our SQL and links to the main PS1 DR1 tables
-are given at  Appendix~\ref{sec:PS1_SQL}.
+surveys together (``various'').
 
@@
 
-We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.
-More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}.
-The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-%{\bf Few more words here on the unWISE catalog...}.
-
-All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux.
-The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}.
-This inheritance depends on details of the PSF normalization at large radii, which is uncertain.
-Subtracting 4 millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
+We use data from the the beginning of the WISE mission \citep[2010
+January; ][]{Wright2010} through the fourth-year of NEOWISE-R
+operations \citep[2017 December;]{Mainzer2011}.  More specifically, we
+utilise the recently released ``unWISE Catalog''
+\citet{Schlafly2019}. The unWISE effort\footnote{http://unwise.me/} is
+the unblurred coadds of the WISE imaging using the AllWISE and
+NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+All fluxes in the unWISE catalog are reported there are in ``Vega
+nanoMaggies'', with the Vega magnitude of a source is given by 
+\begin{equation}
+m_{\rm Vega} = 22.5 - 2.5\log(f),
+\end{equation} 
+where $f$ is the source flux. The absolute calibration for unWISE is
+ultimately inherited from AllWISE through the calibration of
+\citet{Meisner2017a}. This inheritance depends on details of the PSF
+normalization at large radii, which is uncertain. Subtracting 4
+millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes
+improves the agreement between unWISE and AllWISE fluxes.
 
@@
 \end{eqnarray*}
-%Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
-%those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
-These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
-%%
-%% We note though that 
-%%  Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
-%%   - what the source of the trend is,
-%%   - which of unWISE and AllWISE is correct, or
-%%   - where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
-
-For the our MIR variability investigations, we do not use the unWISE coadds, but instead use 
-the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE 2018 Data Release}.
-NEOWISE 2018 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired between 2016 December 13 and 2017 December 13 UTC, which was the fourth year of survey operations of the Near-Earth Object Wide-field Infrared Survey Explorer Reactivation Mission (NEOWISE; Mainzer et al.
-2014, ApJ, 792, 30).
-The fourth year NEOWISE data products are concatenated with those from the first three years into a single archive.
+For the our MIR variability investigations, we do not use the unWISE
+coadds, but instead use the
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
+catalogue and the
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
+2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
+(W1 and W2) single-exposure images and extracted source information
+that was acquired between 2016 December 13 and 2017 December 13 UTC,
+which was the fourth year of survey operations of the Near-Earth
+Object Wide-field Infrared Survey Explorer Reactivation Mission
+(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
+data products are concatenated with those from the first three years
+into a single archive.
 
@@
 
+\begin{table}
+\centering
+\begin{tabular}{l r  r}
+\hline \hline
+$z \geq$  & Age / Myr & No. of objects \\
+\hline 
+7.50         &    700         &   1   \\
+7.00         &    767         &   4   \\
+6.78         &    800         &  14   \\
+6.50         &    845         &  40   \\
+6.19         &   900          &  86   \\
+6.00         &   937          &  170   \\
+5.70         & 1000          &  267   \\
+5.00         & 1180          &  463   \\
+\hline \hline
+\end{tabular}
+\caption{The number of objects at or above a given redshift. 
+The age of the Universe in megayears is also given. }
+      \label{tab:ages}
+\end{table}
+
     \begin{figure}
@@
 \begin{equation}
-1.48 \times \sigma_{median} / \bar{epsilon}
+1.48 \times \sigma_{median} / \bar{\epsilon}
 \end{equation}
-where $\bar{epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
+where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
 %%
 With this definition, although some of the objects have very well sampled, 
-`Average' light curves where you are averaging over e.g. a month, or two weeks.
+`average' light curves where you are averaging over e.g. a month, or two weeks.
 
@@
 CFHQSJ0216-0455
+
+\begin{figure}[H]
+  \begin{subfigure}{}
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
+    \caption{MMTJ0215-0529}
+    \label{fig:1}
+  \end{subfigure}%
+  \begin{subfigure}{}
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
+    \caption{CFHQSJ0216-0455}
+    \label{fig:2}
+  \end{subfigure}
+  \begin{subfigure}{}\quad
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
+    \caption{SHELLQsJ0220-04323}
+    \label{fig:3}
+  \end{subfigure}
+  \medskip
+\end{figure}
 
@@
 %Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
+
+UHS J-band depth 19.6 \citep[Vega; ][]{Dye2018}
+
+VISTA HEMISPHERE SURVEY DATA RELEASE 1
+Release date (will be set by ESO)
+PROPOSAL ESO No.: 179.A-2010
+PRINCIPAL INVESTIGATOR: Richard McMahon
+Authors: R. McMahon, M. Banerji, N. Lodieu for the VHS Collaboration
+
+The aim of the Vista Hemisphere Survey (VHS) is to carry out a near
+Infra-Red survey, which when combined with other VISTA Public Surveys
+will result in coverage of the whole southern celestial hemisphere
+($\sim$20,000 deg$^2$) to a depth 30 times fainter than 2MASS/DENIS in
+at least two wavebands (J and K$_s$), with an exposure time of 60 seconds
+per waveband to produce median 5σ point source (Vega) limits of $J =
+20.2$ and $K_{S} = 18.1$. In the South Galactic Cap, $\sim$5000 deg$^{2}$ will be
+imaged deeper with an exposure time of 120 seconds and also including
+the H band producing median 5$\sigma$ point limits of: J = 20.6; H = 19.8; K$_{s}$ = 18.5. 
+In this 5000 deg$^{2}$ region of sky deep multi-band optical (grizY)
+imaging data will be provided by the Dark Energy Survey (DES). The
+remainder of the high galactic latitude ($|b|>$30$^{\circ}$) sky will be imaged
+in YJHK for 60sec per band to be combined with ugriz waveband
+observations from the VST ATLAS survey. \\
+
+VHS                   YJHK            99.99, 21.2,  21.2,  20.6,  20.0                (9) \\
+
+{\tt ABmagLimits} for each survey in the database. \\
 

### 2019-05-31 tex/VHzQ.tex
VHzQ and To Do list update

@@
     The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
-    [NJC: Do we use the W-band anywhere?]
     The WISE passbands  W1-4 are also presented.
@@
 58483). We then obtain optical, near-infrared and mid-infrared
-photometry for the spectral dataset. The optical data comes from the
-Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)
-survey \citep{Chambers2016}. The near-infrared data comes from two
+photometry for the spectral dataset. 
+%The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. 
+The near-infrared data comes from two
 sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
@@
 
-Tables~\ref{tab:WSA_wWISE}, \ref{tab:THE_TABLE_NIR} and~\ref{tab:THE_TABLE_MIR}, represent the culmination of this effort, and we now describe the assembly of their contents in more detail.
+Table~\ref{tab:output_table} represents the culmination of this effort, and we now describe the assembly of their contents in more detail.
 

### 2019-05-31 tex/VHzQ.tex
Corrections to sections 1/2

@@
 %%                                                                           
-%%    The `compliation' paper for all z>5 spec-z quasars, here called
+%%    The `compilation' paper for all z>5 spec-z quasars, here called
 %%    "Very High Redshift Quasars" (VHzQs) and looking into their IR
@@
 We present all our photometry and magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
+system \cites{Oke_Gunn1983, Fukugita1996}.  This includes the
 near-infrared, as well as the mid-infrared
@@
 for a wide range of optical, NIR and MIR filters. We use a flat
-$\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm
+$\Lambda$CDM cosmology with $H_0 = 67.7$ km s$^{-1}$ Mpc$^{−1}$, $\Omega_{\rm
 M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et
@@
 identified over half (54.6\%) of the VH$z$Q population. Data from the
-Hyper Suprime-Cam (HSC) on the Subaru telecope is responsible for
+Hyper Suprime-Cam (HSC) on the Subaru telescope is responsible for
 13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
@@
   CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
-  DELS               &   16    &   ( 3.46)    &  \citet{Dey2018} \\
+  DELS$^{a}$       &   16    &   ( 3.46)    &  \citet{Dey2018} \\
   ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
@@
   $^{b}$SDWISE = SDSS+WISE; 
-  $^{a}$SUV  = SDSS-ULAS/VHS; 
-  $^{c}$VDES = VHS/VIKING+DES; 
+  $^{c}$SUV  = SDSS-ULAS/VHS; 
+  $^{d}$VDES = VHS/VIKING+DES; 
 %  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
@@
 WFCAM data, which covers all public surveys and PI projects from
-Semester 05A to 2017-Jan-01, and all non-proprietary VISTA data, which
+Semester 05A (2005-05-01) to 2017-Jan-01, and all non-proprietary VISTA data, which
 covers all public surveys and PI projects from science verification on
-2009-Oct-15 to 2016-Apr-01.
-
-Here we are not just quering the WSA or VSA data tables. We are taking
-a list of objects (positions) are performing matched aperature
+2009-Oct-15 to 2017-Jan-01.
+
+Here we are not just querying the WSA or VSA data tables. We are taking
+a list of objects (positions) and are performing matched aperture
 (``forced'') photometry on the NIR imaging data. As such, we generate
@@
 We produce and provide a two new databases with all the necessary
-quantaties and measurements to fully reproduce our tables, figures and
-results herein. Morever, these databases report considerably more
+quantities and measurements to fully reproduce our tables, figures and
+results herein. Moreover, these databases report considerably more
 information than we report here. Full documentation can be found at
@@
 
-  We query the WSA and VSA performing matched-aperature photometry at
+  We query the WSA and VSA performing matched-aperture photometry at
   the positions of our 463 VH$z$Qs. This database is world-readable and
-  we give the full receipe and relevant SQL queries for accessing both
+  we give the full recipe and relevant SQL queries for accessing both
   databases in Appendix~\ref{sec:SQL} as well as online.
@@
   total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperature photometry, where the
-  individual epochs are taken from multiple projects with different
-  pointings and orientations, should help with issues such as scattered
-  light, pixel distortion and aperture corrections.
+  sources. Coadding using the matched-aperture photometry can give better results for the photometry, 
+  where the individual epochs are taken from multiple projects with different field-centres and orientations and point-spread functions since the individual epoch scattered light, pixel distortion and aperture corrections can be applied with the correct weighting.
 
   We average the aperture corrected calibrated fluxes (e.g. {\bf
-  aperJky3}), and then convert to magnitudes. Since we do not have a
-  deep image for each set of averages, we cannot calculate non-aperture
-  corrected values, so the photometry is only appropriate for
-  point-sources.
+  aperJky3}), and then convert to magnitudes.
 
@@
   The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
-  $w_i=0$ if an epoch is excluded for quality control purposes.
+  $w_i=0$ if an epoch is excluded for quality control purposes. The weights of each epoch in each averaged catalogue are tabulated in the {\tt [w\v]serv1000MapAverageWeights}.
 
@@
 The MIR data for this study comes from the Wide-field Infrared Survey
-Explorer (WISE) mission, and we utlize data from the WISE cryogenic
+Explorer (WISE) mission, and we utilize data from the WISE cryogenic
 and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey

### 2019-06-03 tables_for_paper/unWISE_redshift_det.py
data/WSA_VSA/VHS abMag Lim pngs

@@ -1,0 +1,166 @@
+'''
+So, some more wee bits of code that is just investigating the detection rates for 
+the unWISE and AllWISE VHzQ data, this time as a function of redshift. 
+
+unWISE both    matched ::  304 
+unWISE just W1 matched ::  58
+unWISE just W2 matched ::  4
+unWISE matched in W1   ::  362
+unWISE matched in W2   ::  308
+unWISE neither matched ::  97
+
+Total matched   =  463 
+'''
+
+import numpy as np
+
+from astropy.io    import fits
+from astropy.io    import ascii
+from astropy.table import Table
+
+## Data files and path
+#path     = '/cos_pc19a_npr/programs/quasars/highest_z/data/AllWISE/'
+#filename = 'VHzQs463_UNvALL_WISE_temp.dat'
+path     = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
+filename = 'VHzQs_ZYJHK_WISE.dat'
+VHzQs    = ascii.read(path+filename)
+
+## just a quick wee check
+len(VHzQs)
+
+## Setting up the variables just for me to use a bit easier
+##     BY    MAGNITUDES
+unW1            = VHzQs[np.where( VHzQs['unW1mag']>-1)]
+unW1_not_unW2   = VHzQs[np.where((VHzQs['unW1mag']>-1) & (VHzQs['unW2mag']<-1))]
+unW2            = VHzQs[np.where( VHzQs['unW2mag']>-1)]
+unW2_not_unW1   = VHzQs[np.where((VHzQs['unW2mag']>-1) & (VHzQs['unW1mag']<-1))]
+AllW3           = VHzQs[np.where( VHzQs['w3mpro']>-1)]
+AllW3_not_AllW4 = VHzQs[np.where((VHzQs['w3mpro']>-1)  & (VHzQs['w4mpro']<-1))]
+AllW4           = VHzQs[np.where( VHzQs['w4mpro']>-1)]
+AllW4_not_AllW3 = VHzQs[np.where((VHzQs['w4mpro']>-1)  & (VHzQs['w3mpro']<-1))]
+
+##     BY    SNR
+snr_cut = 2.0
+unW1            = VHzQs[np.where( VHzQs['unW1snr'] > snr_cut)]
+unW1_not_unW2   = VHzQs[np.where((VHzQs['unW1snr'] > snr_cut)  & (VHzQs['unW2mag'] < snr_cut))]
[…]

### 2019-06-03 tex/VHzQ.tex
VHzQ.pdf update

--- 2019-05-31 tex/VHzQ.tex
@@
         Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
-        $Z$-band    &  75  (16.1) \\
+        $Z$-band    &  75  (16.2) \\
         $Y$-band    &  273  (59.0) \\
@@
     \caption{MMTJ0215-0529}
-    \label{fig:1}
+    \label{fig:MMTJ0215-0529}
   \end{subfigure}%
@@
     \caption{CFHQSJ0216-0455}
-    \label{fig:2}
+    \label{fig:CFHQSJ0216-0455}
   \end{subfigure}
@@
     \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{SHELLQsJ0220-04323}
-    \label{fig:3}
+    \caption{SHELLQsJ0220-0432}
+    \label{fig:SHELLQsJ0220-0432}
   \end{subfigure}
@@
 so, how many are still to be discovered and confirmed spectroscopcially?
+
+VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
+$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
+Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
+$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.
+
+VIKING is more uniform, so I calculated the averages over the whole area:
+$Z$=22.7 mag, $Y$=21.9 mag, $J$=21.4 mag, $H$=21.2 mag, $Ks$=21.1 mag.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
+  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
+    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
+    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
+    Y and H are almost uniform, but the coverage is much less.}
+  \label{fig:1}
+\end{figure}
 

### 2019-06-03 SEDs/filters_vs_QSOstars.py
SEDs/filters_vs_QSOstars.py and Figure 1 update

@@ -79,6 +79,13 @@ CFHT_Wband = ascii.read(table)
 CFHT_Wband_wave = CFHT_Wband['col1']
 CFHT_Wband_flux = CFHT_Wband['col2']
 
+##     2MASS
+infile = '2MASS/2MASS_Ks.dat'
+table = path+infile
+TwoMASS_Ksband      = ascii.read(table)
+TwoMASS_Ksband_wave = TwoMASS_Ksband['wavelength']
+TwoMASS_Ksband_thru = TwoMASS_Ksband['throughput']
+
 ##      UKIRT
 infile = 'UKIRT/UKIRT_Z.dat'
 table = path+infile
@@ -106,12 +113,33 @@ UKIRT_Kband      = ascii.read(table)
 UKIRT_Kband_wave = UKIRT_Kband['wavelength']
 UKIRT_Kband_thru = UKIRT_Kband['throughput']
 
-##     2MASS
-infile = '2MASS/2MASS_Ks.dat'
+
+##  VIRCAM/VISTA  
+infile = 'VIRCAM/Paranal_VISTA.Z.dat'
 table = path+infile
-TwoMASS_Ksband      = ascii.read(table)
-TwoMASS_Ksband_wave = TwoMASS_Ksband['wavelength']
-TwoMASS_Ksband_thru = TwoMASS_Ksband['throughput']
+VISTA_Zband      = ascii.read(table)
+VISTA_Zband_wave = VISTA_Zband['wavelength']
+VISTA_Zband_thru = VISTA_Zband['throughput']
+infile = 'VIRCAM/Paranal_VISTA.Y.dat'
+table = path+infile
+VISTA_Yband      = ascii.read(table)
+VISTA_Yband_wave = VISTA_Yband['wavelength']
+VISTA_Yband_thru = VISTA_Yband['throughput']
+infile = 'VIRCAM/Paranal_VISTA.J.dat'
+table = path+infile
+VISTA_Jband      = ascii.read(table)
+VISTA_Jband_wave = VISTA_Jband['wavelength']
+VISTA_Jband_thru = VISTA_Jband['throughput']
+infile = 'VIRCAM/Paranal_VISTA.H.dat'
+table = path+infile
+VISTA_Hband      = ascii.read(table)
+VISTA_Hband_wave = VISTA_Hband['wavelength']
+VISTA_Hband_thru = VISTA_Hband['throughput']
[…]

### 2019-06-03 tex/VHzQ.tex
SEDs/filters_vs_QSOstars.py and Figure 1 update
big unWISE_redshift_det.py update

@@
 Here we present for the first time the combined near-infrared
-properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
+properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
 all the spectroscopically known $z\geq5.00$ quasars. Our motivations
@@
 system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
-near-infrared, as well as the mid-infrared
-magnitudes. Appendix~\ref{sec:filters} gives the AB to Vega transforms
-for a wide range of optical, NIR and MIR filters. We use a flat
-$\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm
-M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et
-al. 2016) to be consistent with \citet{Banados2016} and all logarithms
-are to the base 10.
+near-infrared, as well as the mid-infrared magnitudes. These
+magnitudes are {\it not} Galactic extinction corrected. We use a flat
+$\Lambda$CDM cosmology with $H_{\rm 0} = 67.7$ km s$^{-1}$ Mpc$^{-1}$,
+$\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$
+\citet{Planck2016} to be consistent with \citet{Banados2016} and all
+logarithms are to the base 10.
 
@@
 \begin{figure}
-%%trim=l b r t
+  %% trim=l b r t
   % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
   \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.
-    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
-    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
-    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
-    The WISE passbands  W1-4 are also presented.
+  {The spectral bands used in this paper. 
+    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
+    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
+    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration. 
     The quasar spectrum is a composite based on \citet{VdB2001} and 
-    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
-  }
+    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
   \label{fig:filters}
@@
 58483). We then obtain optical, near-infrared and mid-infrared
-photometry for the spectral dataset. 
-%The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. 
-The near-infrared data comes from two
-sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
+photometry for the spectral dataset. The near-infrared data comes from
+two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
 primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
@@
   {The redshift distribution $N(z)$ of the VH$z$Q sample. 
-    The bins are $\delta-z=0.075$ in width. }
+    The bins are $\delta z=0.075$ in width and have the data 
+    stacked on top of each other.}
   \label{fig:Nofz}
@@
 broad UV/optical emission lines. There are far infra-red emission
-lines e.g. \cii~158 micron available for several objects, but at the
+lines e.g. \cii 158 $\mu$m available for several objects, but at the
 level of our current analysis broadline redshifts are sufficient.
@@
 \hline 
+5.00         & 1180          &  463   \\
+5.70         & 1000          &  267   \\
+6.00         &   937          &  170   \\
+6.19         &   900          &  86   \\
+6.50         &    845         &  40   \\
+6.78         &    800         &  14   \\
+7.00         &    767         &   4   \\
 7.50         &    700         &   1   \\
-7.00         &    767         &   4   \\
-6.78         &    800         &  14   \\
-6.50         &    845         &  40   \\
-6.19         &   900          &  86   \\
-6.00         &   937          &  170   \\
-5.70         & 1000          &  267   \\
-5.00         & 1180          &  463   \\
 \hline \hline
@@
 \caption{The number of objects at or above a given redshift. 
-The age of the Universe in megayears is also given. }
+The age of the Universe in Megayears is also given. }
       \label{tab:ages}
@@
 surveys together (``various'').
+
+\begin{figure}
+%%trim=l b r t
+  \includegraphics[width=8.0cm, clip, trim=0mm 0mm 2mm 0mm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/data/WSA_VSA/CoverageMaps_VHzQ_forpaper.png}
+  \centering
+  \caption[]
+  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by white diamonds.}
+  \label{fig:coverage}
+\end{figure}
 
@@
 
-Here we are not just quering the WSA or VSA data tables. We are taking
-a list of objects (positions) are performing matched aperature
+Here we are not just querying the WSA or VSA data tables. We are taking a list of objects (positions) are performing matched aperture
 (``forced'') photometry on the NIR imaging data. As such, we generate
@@
   total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperature photometry, where the
+  sources. Coadding using the matched-aperture photometry, where the
   individual epochs are taken from multiple projects with different
@@
 
-  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars are 
-  detected in the VISTA VSA database with 130 objects in common with both
-  WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
+  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars
+  are detected in the VISTA VSA database with 130 objects in common with
+  both WFCAM and VISTA data.  We give the necessary SQL queries syntax
+  at
+  \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt
+    d80b2t/VHzQ}.
 
@@
 Explorer (WISE) mission, and we utlize data from the WISE cryogenic
-and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
-phases.
+and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011}
+post-cryogenic and NEOWISE Reactivation Mission
+\citep[NEOWISE-R][]{Mainzer2014} survey phases.
 
 We use data from the the beginning of the WISE mission \citep[2010
-January; ][]{Wright2010} through the fourth-year of NEOWISE-R
-operations \citep[2017 December;]{Mainzer2011}.  More specifically, we
+January; ][]{Wright2010} through the fifth-year of NEOWISE-R
+operations \citep[2018 December;]{Mainzer2011}.  More specifically, we
 utilise the recently released ``unWISE Catalog''
@@
 \end{eqnarray*}
-For the our MIR variability investigations, we do not use the unWISE
-coadds, but instead use the
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
-catalogue and the
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
-2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
-(W1 and W2) single-exposure images and extracted source information
-that was acquired between 2016 December 13 and 2017 December 13 UTC,
-which was the fourth year of survey operations of the Near-Earth
-Object Wide-field Infrared Survey Explorer Reactivation Mission
-(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
-data products are concatenated with those from the first three years
-into a single archive.
+For the our MIR variability investigations, we do not use the unWISE coadds, but instead use the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the NEOWISE \href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{2019 Data Release}.
+NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE.
+These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
 
@@
 
-Table~\ref{tab:output_table} represents the culmination of this effort, and we now describe the assembly of their contents in more detail.
-
-%\input{table_tex/WSA_wWISE}
-
-%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
-%\footnotesize
-%\tiny
+Table~\ref{tab:output_table} represents the culmination of this
+effort, and we now exam the assembly of its contents in more detail.
 \begin{landscape}
@@
 \end{landscape}
-%\normalsize
 
@@
 \section{Results}
-Having collated the sample of 463 VH$z$Qs, and obtained their optical,
-near- and mid-infrared photometry we report here the various
-photometric properites of the quasars.
+Having collated the sample of 463 VH$z$Qs, and obtained their near-
+and mid-infrared photometry we report here the various photometric
+properties of the quasars.
 
@@
 luminosity-redshift $Lz$-plane.
-
-    %\subsection{Detection Rates in the optical}
 
@@
   \centering
-
   \begin{tabular}{l r l}
@@
     \hline  
-        Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
+    Any band ($ZYJHK/K_{s}$)    &  449  (97.0) \\
     $Z$-band                            &  75  (16.2) \\
@@
 
-     There are 14 objects that have no NIR detections. 
-     3 of these (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) 
-     have been observed (by VHS) but are out of our queried time range. 
-     6 objects have not been observed (or at least the data is not in the WSA/VSA 
-     archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too far north for UKIRT 
-     and cannot be observed.
+There are 14 objects that have no NIR detections.  3 of these
+(PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
+been observed (by VHS) but are out of our queried time range.  6
+objects have not been observed (or at least the data is not in the
+WSA/VSA archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too
+far north for UKIRT and cannot be observed.
 
@@
   There are 130 overlapping QSOs between WFCAM and VISTA. Using the
-        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
-        objects on the same AB system, and for each object compared the two
-        measurements. First, the calculated weighted average (calibrated flux)
-        in each filter of both and calculated the ratio and difference between
-        each measurement and the average.  Then for each filter we calculated
-        the weighted average of the differences (in mag) for each instrument
-        to see if there were significant offsets. The results are given in
+  {\tt VegaToAB} value to put these objects on the same AB system, and
+  for each object compared the two measurements. First, the calculated
+  weighted average (calibrated flux) in each filter of both and
+  calculated the ratio and difference between each measurement and the
+  average.  Then for each filter we calculated the weighted average of
+  the differences (in mag) for each instrument to see if there were
+  significant offsets. The results are given in
   Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
@@
   of the WFCAM ones are positive. The $Ks$ versus $K$ band may be
-        slightly dodgy, given the different shapes of the filters.
+  lightly dodgy, given the different shapes of the filters.
   \begin{table}
@@
     \end{tabular}
-          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
+    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
+      VIRCAM/VISTA near-infrared bands.}
     \label{tab:WFCAM_vs_VISTA}
@@
 
-%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
-
-%% I have also checked for QSOs with large differences in magnitude.
-At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
-In fact initially there were 100 QSO/filter combinations.
-However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
-and >5 average flux error.
-This removed 80-90\%.
-I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
-This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
-
-The two with large differences are:
-
-SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
-
-SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
-
-        We investigate the VH$z$Qs in the UltraVISTA field. 
-        UltraVISTA is...
-        %% 
-        One detail to note is that depths quoted in the UltraVISTA Data Releases are for more realistic 
-        1.8 arcsec diameter apertures (J. Dunlop, priv. comm.).
+  We have also checked for quasars with large differences in magnitude
+  between the WSA and VSA. Objects were selected where the average flux
+  was $>0.$ and $>5$ average flux error. In order to account for large
+  errors in either the WFCAM or VISTA photometry, objects with deltaMag$
+  < 2 \times$ deltaMagErr in either WSA or VSA were removed. This
+  selects two quasars with large, $\delta$mag $>0.2$mag differences
+  between the WSA and VSA. These are SDSSJ0349+0034 and
+  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
+  19.13$\pm$-0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
+  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
+  = 19.38$\pm$0.04.
+
+\begin{table}
+  \centering
+  \begin{tabular}{l r r r r}
+    \hline \hline
+    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
+                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
+    \hline
+    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
+    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
+    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
+    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
+    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
+    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
+    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
+    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
+    \hline \hline
+  \end{tabular}
+  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
+    redshift. A signal-to-noise cut of W$x$snr$>3.0$ has been used for each band.}
+  \label{tab:WFCAM_vs_VISTA}
+\end{table}
 
 \subsection{Detection Rates in the MIR}
-    Unlike the NIR coverage, the WISE
-    satellite and mission performed an all-sky survey, so the location of
-    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
-    ALLWISE survey depends heavily on sky location, with locations near
-    the Ecliptic Poles having the highest number of exposures.
+Unlike the NIR coverage, the WISE satellite and mission performed an
+all-sky survey, so the location of every VH$z$Q in our dataset is
+covered. However, the depth of the WISE ALLWISE survey depends heavily
+on sky location, with locations near the Ecliptic Poles having the
+highest number of exposures.
 
@@
   \caption{}
-      \label{tab:mir_detection}
-    \end{table}
-
-    \begin{table}
-      \begin{tabular}{l r l}
-        \hline  \hline
-         \multirow{2}{*}{Selection}   & number detected \\ 
-                                                   & (\% of full specrta) \\
-        \hline  
-        From ``Source'', ``Rejects'',                    & 245, 40  (67.2) \\
-        W1 SNR $> 2.0$                                       &  279  (65.8) \\
-        W2 SNR $> 2.0$                                       &  258 (60.8) \\
-        W1 $\land$ W2 SNR $> 2.0$                    & 253   (59.7)  \\
-        W3 SNR $> 2.0$                                     &  97    (22.9) \\
-        W4 SNR $> 2.0$                                     &  33    (7.8) \\
-%        Any W1/2/3/4 SNR $>2.0$                            & \\
-        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ &  3 (0.7)\\
-        \hline  \hline
-      \end{tabular}
-      \caption{Data from the AllWISE Source Catalog and AllWISE Reject Table, from the 
-\href{https://irsa.ipac.caltech.edu/cgi-bin/Gator/nph-scan?submit=Select&projshort=WISE} {{\tt NASA/IPAC  Infrared Science Archive}}}
   \label{tab:mir_detection}

### 2019-06-03 tables_for_paper/unWISE_redshift_det.py

@@ -73,7 +73,7 @@ print('\hline \hline')
 ## By redshift
 redshift_array = np.array([5.00, 5.70, 6.00, 6.19, 6.50, 6.78, 7.00, 7.50])
 
-snr_cut = 2.0
+snr_cut = 3.0
 
 ## How many of the VHzQs are above a given redshift 
 N_zgt5pnt00 = np.count_nonzero(VHzQs['redshift'] >= redshift_array[0]) 
@@ -130,37 +130,43 @@ N_zgt7pnt50_ALLW4 = np.count_nonzero((VHzQs['redshift'] >= redshift_array[7]) & 
 
 print()
 print()
+print('\hline \hline')
+print(' $z \geq$ & unWISE W1 & unWISE W2 & ALLWISE W3 & ALLWISE W4  \\\ ')
+print('\hline')
 
-print(' 5.00   {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) '.format(N_zgt5pnt00_unW1,  ((N_zgt5pnt00_unW1  / N_zgt5pnt00)*100),
+print(' 5.00   & {:5d} ({:5.1f}\%)   & {:5d} ({:5.1f}\%)  & {:5d} ({:5.1f}\%)  & {:5d} ({:5.1f}\%) \\\ '.format(N_zgt5pnt00_unW1,  ((N_zgt5pnt00_unW1  / N_zgt5pnt00)*100),
                                                                                                 N_zgt5pnt00_unW2,  ((N_zgt5pnt00_unW2  / N_zgt5pnt00)*100),
                                                                                                 N_zgt5pnt00_ALLW3, ((N_zgt5pnt00_ALLW3 / N_zgt5pnt00)*100),
                                                                                                 N_zgt5pnt00_ALLW4, ((N_zgt5pnt00_ALLW4 / N_zgt5pnt00)*100)))
-print(' 5.70   {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) {:5d} ({:5.1f}\%) '.format(N_zgt5pnt70_unW1,  ((N_zgt5pnt70_unW1  / N_zgt5pnt70)*100),
[…]

### 2019-06-03 tex/VHzQ.tex
Continued wee progress

@@
 objects have not been observed (or at least the data is not in the
-WSA/VSA archives yet) and 5 objects at $\geq +60$ deg$^{2}$ are too
-far north for UKIRT and cannot be observed.
+WSA/VSA archives yet) and 5 objects at declination $\delta \geq +60$
+deg are too far north for UKIRT and cannot be observed.
 
@@
 5.8 and 6.8 and 69 (for both bands). These values are direclty from
-the {\tt w$x$cov} enteries in the 
-\href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.
+the {\tt w$x$cov} enteries in the WISE
+\href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
 
@@
   \label{tab:mir_detection}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{l r  r}
-\hline \hline
-$z \geq$  & Age / Myr & No. of objects \\
-\hline 
-7.50         &    700         &   1   \\
-7.00         &    767         &   4   \\
-6.78         &    800         &  14   \\
-6.50         &    845         &  40   \\
-6.19         &   900          &  86   \\
-6.00         &   937          &  170   \\
-5.70         & 1000          &  267   \\
-5.00         & 1180          &  463   \\
-\hline \hline
-\end{tabular}
-\caption{The number of objects at or above a given redshift. 
-The age of the Universe in megayears is also given. }
-      \label{tab:ages}
 \end{table}
@@
 
-    %\subsubsection{
 Very High-$z$ Quasars Detected in WISE W3 and W4.
@@
 \subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m_{\rm accr}}$.
-A consequence of this would be that these quasar exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra.
-We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
-As a guide, \civ enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57.
-\mgii enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
+VH$z$Qs, if accreting at, or above the Eddington Limit, might well
+have have large values of changing mass accretion rate, $\ddot{m}_{\rm
+accr}$. A consequence of this would be that these quasar exhibit signs
+of variability, most likely showing up in their UV/optical rest-frame
+spectra. We look for evidence of this variability signature in the NIR
+and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the
+$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
+$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
+$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
+$K$-band at redshift $z=6.25$ and exits at $7.50$.
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
+\begin{figure}
+  \centering
+  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_J_abMagLim.png}
   \caption{The calculated average {\tt AB MAGLIM} in the VHS.

### 2019-06-03 tex/VHzQ.tex
Added AM and ES acknowledgment

@@
 
-Critically, we now have available to us new W1 and W2 photometry from
-the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
-WISE-selected catalogue that is based on significantly deeper imaging
-and has a more extensive modeling of crowded regions than the ALLWISE
-release. For the first time in a catalogue, unWISE takes advantage of
-the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
-Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
-achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
-additional depth is a significant advantage in the detection and study
-of VH$z$Qs in the 3-5 micron regime.
+Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
+For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
+This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
 
@@
 
+We very much thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
+
 This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)

### 2019-06-04 tex/VHzQ.tex
tex/ update

@@
 telescopes including the Large Synoptic Survey Telescope
-(LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
+(LSST)\blindtext\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it
+Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};}
 and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
+(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
 We
@@
 
-Here we are not just querying the WSA or VSA data tables. We are taking a list of objects (positions) are performing matched aperture
+Here we are not just querying the WSA or VSA data tables. We are
+taking a list of objects (positions) are performing matched aperture
 (``forced'') photometry on the NIR imaging data. As such, we generate
@@
   both WFCAM and VISTA data.  We give the necessary SQL queries syntax
-  at
-  \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt
+  at \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt
     d80b2t/VHzQ}.
@@
 utilise the recently released ``unWISE Catalog''
-\citet{Schlafly2019}. The unWISE effort\footnote{http://unwise.me/} is
-the unblurred coadds of the WISE imaging using the AllWISE and
-NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+\citet{Schlafly2019}. The unWISE
+effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the
+unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R
+stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016}
+found that cross-matches performed with a radius of 2-3'' between the user
+catalogue and WISE was a good compromise between completeness and
+contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. 
+We thus use a cross-match radius of 2.75''.
+
+For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and 
+$\lambda_{\rm eff}$4.62$\mu$m W2 we use the deeper, unblurred unWISE coadd data. 
+For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m 
+we use the ALLWISE Data Release
+
+When querying the ALLWISE catalogs, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
+The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
+Investigating this in detail is very interesting but left to a future study.
+
+Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalog and also query the AllWISE Reject Table.
+However, with the exception of one object (SHELLQs   J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.
 
@@
 \end{eqnarray*}
-For the our MIR variability investigations, we do not use the unWISE coadds, but instead use the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the NEOWISE \href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{2019 Data Release}.
-NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE.
-These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
-
-The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October.
-Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
+For the our MIR variability investigations, we do not use the unWISE
+coadds, but instead use the
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
+catalogue and the NEOWISE
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{2019 Data
+Release}. NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2)
+single-exposure images and extracted source information that was
+acquired up until 2018 December 13 (MJD 58465) including the fifth
+year of survey operations of NEOWISE. These fifth year NEOWISE data
+products are concatenated with those from the first four years into a
+single archive from 2013 December 13 (MJD 56639).
+
+The WISE scan pattern leads to coverage of the full-sky approximately
+once every six months (a``sky pass''), but the satellite was placed in
+hibernation in 2011 February and then reactivated in 2013
+October. Hence, our light curves have a cadence of 6 months with a 32
+month sampling gap.
 
@@
   \end{tabular}
-  \caption{Detection rate of VH$z$Qs in the near-infrared.}
+  \caption{Detection rate of VH$z$Qs in the near-infrared. 
+For the 14 objects that have no NIR detections, 3 have 
+been observed but are not in our queried time range, 6 have 
+not been observed yet and 5 objects are too far north to be visible 
+by UKIRT. }
   \label{tab:nir_detection}
@@
   \caption{Detection rates in the mid-infrared bands from WISE as a function of 
-    redshift. A signal-to-noise cut of W$x$snr$>3.0$ has been used for each band.}
+    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
   \label{tab:WFCAM_vs_VISTA}
@@
 \subsection{Detection Rates in the MIR}
-Unlike the NIR coverage, the WISE satellite and mission performed an
-all-sky survey, so the location of every VH$z$Q in our dataset is
-covered. However, the depth of the WISE ALLWISE survey depends heavily
-on sky location, with locations near the Ecliptic Poles having the
-highest number of exposures.
-
-Before reporting on the detection rates, we investigate this
-effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
-versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
-coverage depth, in each corresponding band. In the two shorter bands
-W1/2 we see the clear and expected trend for brighter objects to have
-larger SNR, and also for the higher signal to noise for objects with
-more exposures at a given magnitude. The behaviour for the W3/4 bands
-is different, with two populations clearly evident in W3 and although
-a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
-no obvious R.A./Declination dependence seen, this behaviour is
-explained by the fact that there are non-detectiopns in W3/4 for
-objects (with high W1/2 SNR) that are reported in the ALLWISE
-catalogue.
-
-For the 278 VH$z$Q with coverage detections, the mean number of
-exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
-minimum number of exposures 17 and 12, and the maximum number or
-exposures being 114 (for both bands).  For the W3/4 filters, the
-corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
-5.8 and 6.8 and 69 (for both bands). These values are direclty from
-the {\tt w$x$cov} enteries in the WISE
-\href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
+Unlike the NIR coverage, the WISE satellite and mission performed an all-sky survey, so the location of every VH$z$Q in our dataset is covered.
+However, the depth of the WISE survey depends heavily on sky location, with locations near the Ecliptic Poles having the highest number of exposures.
+
+Before reporting on the detection rates, we investigate this effect.
+Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
+In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude.
+The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4.
+With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
+
+For the 278 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
+For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands).
+These values are direclty from the {\tt w$x$cov} enteries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
 
@@
 
-We very much thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
+We thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
+
+We thank Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion.
 

### 2019-06-05 tex/VHzQ.tex
VHzQ.tex update

@@
 
+\begin{figure*}
+    \centering
+    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png}} 
+    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}} 
+    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}}
+    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}}
+    \caption{(a) UHS J0439+1634 
+                 (b) SDSS J0100+280 
+               (c) SDSS J1443+3623 
+ (d) SDSS J1623+4705
+}
+    \label{fig:foobar}
+\end{figure*}
+\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
+
 \begin{figure}

### 2019-06-05 tex/older_tex/VHzQ_20190531.tex

--- 2019-05-28 tex/older_tex/VHzQ_20180527.tex
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts $z\geq5.00$) are excellent probes of the early Universe.
-This includes studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for reviews]{Fan2006review, Mortlock2016}, the formation and build-up of supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003, Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017, Bosman2017}.
-
-Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a viable mechanism to explain the high, potentially super-Eddington, luminosity and rapid growth of supermassive black holes in the early universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014, Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}.
-Thus, one could expect VH$z$Qs to potentially vary in luminosity as they go through phases of super-critical accretion.
-These signatures of photometric variability should be looked for, noting the rest-frame optical emission is redshifted into the observed near-infrared (NIR) at redshifts $z>5$.
-Fortunately, data are now in place from deep, wide-field NIR instruments and surveys such as the Wide Field Camera (WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT) in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the Southern Hemisphere, that are necessary for identifying VH$z$Qs.
-
-Quasars are known to be prodigious emitters of infrared emission, thought to be from the thermal emission of dust grains heated by continuum emission from the accretion disc \citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
-Observations in the mid-infrared, e.g.
-$\sim$3-30$\mu$m allow discrimination between AGN\footnote{Historically, ``quasars'' and ``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects.
-In recognition of the fact that both terms describe accreting supermassive black holes, we use these terms interchangeably, with a preference for quasar, since we are generally in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at $z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004, Stern2005, Richards2006b, Timlin2016} as well as between AGN and star-forming galaxies due to the presence of Polycyclic Aromatic Hydrocarbon (PAHs) at $\lambda
->3\mu$m \citep[e.g., ][]{Yan2007, Tielens2008}.
-
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of a quasar without hot-dust emission in a sample of 21 $z\approx6$ quasars.
-Such apparently hot-dust-free quasars have no counterparts at low redshift.
-Moreover, those authors demonstrate that the hot-dust abundance in the 21 quasars builds up in tandem with the growth of the central black hole.
-But understanding how dust first forms and appears in the central engine remains an open question \citep{WangR2008, WangR2011}.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
-The all sky `ALLWISE' catalogue release, contains nearly 750 million detections at high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}, of which over 4.5M AGN candidates have been identified with 90\% reliability \citep{Assef2018}.
-\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17 (55\%) of the then known 31 quasars at $z > 6$.
-However, \citet{Blain2013} was compiled with the WISE `All-Sky' data release, as opposed to the superior AllWISE catalogues.
-That sample only examined the 31 known $z>6$ quasars; our sample has 170 objects with redshift $z \geq 6.00$ (with $x$ detected in WISE {\bf NPR to double check!!}).
-\citet{Banados2016} reports WISE W1, W2, W3 and W4 magnitudes for the Panoramic Survey Telescope and Rapid Response System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation into the reddest WISE waveband for the VH$z$Qs.
-
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
-This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
-
-Here we present for the first time the combined near-infrared properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for all the spectroscopically known $z\geq5.00$ quasars.
-Our motivations are numerous and include: {\it (i)} establishing the first complete catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
-luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
-
-This paper is organized as follows.
-In Section 2, we present the assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have compiled.
-We then give a high-level overview of the photometric surveys and datasets we use and present the photometry of the VH$z$Qs.
-In Section 3 we ...
-and In Section 4 we ...
-We conclude in Section 5 and present all the necessary details to obtain our dataset in the Appendices.
-
-We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.
-This includes the near-infrared, as well as the mid-infrared magnitudes.
-Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters.
-We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
-2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.
+Very high redshift quasars (VH$z$Q; defined here to have redshifts
+$z\geq5.00$) are excellent probes of the early Universe. This includes
+studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
+reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
+supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
+Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and
+early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017,
+Bosman2017}.
+
+Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a
+viable mechanism to explain the high, potentially super-Eddington,
+luminosity and rapid growth of supermassive black holes in the early
+universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
+Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
+one could expect VH$z$Qs to potentially vary in luminosity as they go
+through phases of super-critical accretion. These signatures of
+photometric variability should be looked for, noting the rest-frame
+optical emission is redshifted into the observed near-infrared (NIR)
+at redshifts $z>5$. Fortunately, data are now in place from deep,
+wide-field NIR instruments and surveys such as the Wide Field Camera
+(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
+in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
+the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
+Southern Hemisphere, that are necessary for identifying VH$z$Qs.
+
+Quasars are known to be prodigious emitters of infrared emission,
+thought to be from the thermal emission of dust grains heated by
+continuum emission from the accretion disc
+\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014,
+Hickox2017}. Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
+allow discrimination between AGN\footnote{Historically, ``quasars''
+and ``Active Galactic Nuclei (AGN)'' have described different
+luminosity/classes of objects. In recognition of the fact that both
+terms describe accreting supermassive black holes, we use these terms
+interchangeably, with a preference for quasar, since we are generally
+in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive
+galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at
+$z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004,
+Stern2005, Richards2006b, Timlin2016} as well as between AGN and
+star-forming galaxies due to the presence of Polycyclic Aromatic
+Hydrocarbon (PAHs) at $\lambda >3\mu$m \citep[e.g., ][]{Yan2007,
+Tielens2008}.
+
+\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
+a quasar without hot-dust emission in a sample of 21 $z\approx6$
+quasars. Such apparently hot-dust-free quasars have no counterparts at
+low redshift. Moreover, those authors demonstrate that the hot-dust
+abundance in the 21 quasars builds up in tandem with the growth of the
+central black hole. But understanding how dust first forms and appears
+in the central engine remains an open question \citep{WangR2008,
+WangR2011}.
+
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths
+of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue
+release, contains nearly 750 million detections at
+high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
+of which over 4.5M AGN candidates have been identified with 90\%
+reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
+mid-infrared (MIR) detections of 17 (55\%) of the then known 31
+quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
+WISE `All-Sky' data release, as opposed to the superior AllWISE
+catalogues. That sample only examined the 31 known $z>6$ quasars; our
+sample has 170 objects with redshift $z \geq 6.00$ (with 108 detected
+in WISE). \citet{Banados2016} reports WISE W1, W2, W3 and W4
+magnitudes for the Panoramic Survey Telescope and Rapid Response
+System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with
+no further investigation into the reddest WISE waveband for the
+VH$z$Qs.
+
+Critically, we now have available to us new W1 and W2 photometry from
+the `unWISE Source Catalog' \citep[][]{Schlafly_Meisner2018}, a
+WISE-selected catalogue that is based on significantly deeper imaging
+and has a more extensive modeling of crowded regions than the ALLWISE
+release. For the first time in a catalogue, unWISE takes advantage of
+the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey
+Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and
+achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).  This
+additional depth is a significant advantage in the detection and study
+of VH$z$Qs in the 3-5 micron regime.
+
+Here we present for the first time the combined near-infrared
+properites (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
+all the spectroscopically known $z\geq5.00$ quasars. Our motivations
+are numerous and include: {\it (i)} establishing the first complete
+catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
+{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
+available for the quasars; {\it (iii)} making the first study of near-
+and mid-IR variability of the VHzQ population and {\it (iv)}
+establishing the photometric properties for upcoming surveys and
+telescopes including the Large Synoptic Survey Telescope
+(LSST)\footnote{\href{https://www.lsst.org}{{lsst.org}}}, ESA {\it
+Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
+and the {\it James Webb Space Telescope}
+(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}.
+We
+chose redshift $z=5.00$ as our lower redshift limit due to a
+combination of garnishing a large sample, adequately spanning physical
+properties (e.g. luminosity, age of the Universe) and to highlight the
+parts of $L-z$ parameter space where $z>5$ quasars still wait to be
+discovered.
+
+This paper is organized as follows. In Section 2, we present the
+assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
+compiled. We then give a high-level overview of the photometric
+surveys and datasets we use and present the photometry of the
+VH$z$Qs. In Section 3 we investigate the variability properties of the
+VH$z$Qs, looking for evidence of super-critical accretion. In Section
+4 we calculate how many $z>5$ quasars we should expect to find in
+current datasets. We conclude in Section 5 and present all the
+necessary details to obtain our dataset in the Appendices.
+
+We present all our photometry and magnitudes on the AB zero-point
+system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
+near-infrared, as well as the mid-infrared magnitudes. These
+magnitudes are {\it not} Galactic extinction corrected.
+%Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters. 
+We use a flat $\Lambda$CDM cosmology with $H_{\rm 0} = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm
+M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et
+al. 2016) to be consistent with \citet{Banados2016} and all logarithms
+are to the base 10.
 
@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
 \section{Method and Data}
-Quasars are generally identified by photometric selection followed by spectroscopic confirmation.
-Here, we reverse this method obtaining first a list of spectroscopic quasars and then obtain photometric information.
-
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$.
-We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483).
-We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset.
-The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}.
-The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}.
-The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
+Quasars are generally identified by photometric selection followed by
+spectroscopic confirmation. Here, we reverse this method obtaining
+first a list of spectroscopic quasars and then obtain photometric
+information.
+
+We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
+use all the $z\geq5.00$ quasars that have been discovered,
+spectroscopically confirmed and published as of 2018 December 31 (MJD
+58483). We then obtain optical, near-infrared and mid-infrared
+photometry for the spectral dataset. 
+%The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. 
+The near-infrared data comes from two
+sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
+primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
+Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
+VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
+mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
+Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
+Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
+the wavelength and normalised transmission of the filters in question.
 
@@
   detected in the VISTA VSA database with 130 objects in common with both
-  WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.
+  WFCAM and VISTA data.  
+  We give the necessary SQL queries syntax at 
+  \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt d80b2t/VHzQ}.
 
@@
 
-We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.
-More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}.
-The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-%{\bf Few more words here on the unWISE catalog...}.
-
-All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux.
-The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}.
-This inheritance depends on details of the PSF normalization at large radii, which is uncertain.
-Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.
-
-Thus to convert unWISE Vega magnitudes onto the AB system, we have    
+We use data from the the beginning of the WISE mission \citep[2010
+January; ][]{Wright2010} through the fourth-year of NEOWISE-R
+operations \citep[2017 December;]{Mainzer2011}.  More specifically, we
+utilise the recently released ``unWISE Catalog''
+\citet{Schlafly2019}. The unWISE effort\footnote{http://unwise.me/} is
+the unblurred coadds of the WISE imaging using the AllWISE and
+NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+All fluxes in the unWISE catalog are reported there are in ``Vega
+nanoMaggies'', with the Vega magnitude of a source is given by 
+\begin{equation}
+m_{\rm Vega} = 22.5 - 2.5\log(f),
+\end{equation} 
+where $f$ is the source flux. The absolute calibration for unWISE is
+ultimately inherited from AllWISE through the calibration of
+\citet{Meisner2017a}. This inheritance depends on details of the PSF
+normalization at large radii, which is uncertain. Subtracting 4
+millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes
+improves the agreement between unWISE and AllWISE fluxes.
+
+Thus to convert unWISE Vega magnitudes onto the AB system, we have:     
 \begin{eqnarray*}
         {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
-        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339 
+        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339. 
 \end{eqnarray*}
-%Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
-those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.
-These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
-%We note though that 
-%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
-%- what the source of the trend is,
-%- which of unWISE and AllWISE is correct, or
-%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).
-
-For the our MIR variability investigations, we do not use the unWISE coadds, but instead use 
-the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE 2018 Data Release}.
-NEOWISE 2018 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired between 2016 December 13 and 2017 December 13 UTC, which was the fourth year of survey operations of the Near-Earth Object Wide-field Infrared Survey Explorer Reactivation Mission (NEOWISE; Mainzer et al.
-2014, ApJ, 792, 30).
-The fourth year NEOWISE data products are concatenated with those from the first three years into a single archive.
+For the our MIR variability investigations, we do not use the unWISE
+coadds, but instead use the
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
+catalogue and the
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
+2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
+(W1 and W2) single-exposure images and extracted source information
+that was acquired between 2016 December 13 and 2017 December 13 UTC,
+which was the fourth year of survey operations of the Near-Earth
+Object Wide-field Infrared Survey Explorer Reactivation Mission
+(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
+data products are concatenated with those from the first three years
+into a single archive.
 
@@
 %\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
-
+%\footnotesize
+%\tiny
+\begin{landscape}
       \input{../tables_for_paper/output_table}
+\end{landscape}
+%\normalsize
 
@@
 
+%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
+
+%% I have also checked for QSOs with large differences in magnitude.
+At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
+In fact initially there were 100 QSO/filter combinations.
+However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
+and >5 average flux error.
+This removed 80-90\%.
+I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
+This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
+
+The two with large differences are:
+
+SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
+
+SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
+
         We investigate the VH$z$Qs in the UltraVISTA field. 
@@
 
-%% On May 13, 2019, at 5:25 PM, Nicholas Cross <njc@roe.ac.uk> wrote:
-
-%% I have also checked for QSOs with large differences in magnitude.
-At first I found loads of objects which appeared to have either the WFCAM or VISTA measurement more than 1 mag different from the mean.
-In fact initially there were 100 QSO/filter combinations.
-However, in many cases the average flux was less 0, or very close to zero, so I selected only objects where the average was >0.
-and >5 average flux error.
-This removed 80-90\%.
-I then found that many of the others had one of WFCAM or VISTA where the error bars were very large, so I removed ones where deltaMag<2.*deltaMagErr in either.
-This left me with 1 object or 2 if I reduced the change to 0.2 mag different from the mean:
-
-The two with large differences are:
-
-SDSSJ0349+0034, in K/Ks band: VSA = 18.36$\pm$0.10, WSA = 19.13$\pm$-0.24 and
-
-SDSSJ2220-0101, in J band: VSA = 19.38+/-0.04, WSA = 22.23+/-0.15
-
-\subsection{Colours}
-Currently, very high-redshift quasars are identified by their morphology, flux and colours in optical and infrared imaging data \citet{Fan1999, Mortlock2012} Quasars are generally selected to be point sources, but  be outliers from the stellar locus in colour space.
-For VH$z$Qs, the main technique is to look for objects with extreme optical-to-near-infrared colours The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
-There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
-the blue or red end respectively. Hmmm....}
-   \label{fig:SpecType_vs_NIRcolors}
- \end{figure*}
-
-\begin{figure*}
-   \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
-  \centering
-   \caption[]
-   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
-}
-   \label{fig:SpecType_vs_W1W2_W2W3colors}
- \end{figure*}
-
-\subsection{L-$z$ Plane}
-Having obtained an as-near-to-homogenous set of photometry as we can, 
-we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
-sample and in particulare the absolute magnitude at rest-frame 1450\AA\ , $M_{1450}$, 
-which is a key physical quantity and goes directly towards the quasar luminosity 
-function and thus the reionization of hydrogen calculation.
-
-We calculate the Distance Modulus in the normal fashion, 
+At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.
+
+Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).
+
+Then calculate the clipped median and standard deviation, 
 \begin{equation}
-m_{1450} - M_{1450} = 5 \log \left (    \frac{ D_{\rm L}(z)}{\rm Mpc}  \right )  + 25 + K_{\rm corr}(X,z)
+1.48 \times \sigma_{median} / \bar{\epsilon}
 \end{equation}
-where $m_{1450}$ is the apparent magnitude at 1450\AA\ ,  
-%$M_{1450}$ is the absolute magnitude at 1450 \AA\ , 
-$D_{\rm L}(z)$ is the luminosity distance and 
-$K_{\rm corr}(X,z)$ is the $K$-correction which corrects for the effects of redshifting of the bandpass and the spectrum.
-
-The $m_{1450}$ apparent magnitude is derived from the $z-$, $y/Y-$ or $J-$band photometery.
-
-The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
-sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
-for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
-cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.
-
-\citet{Ross2013} has a detailed discussion of the $K$-correction (see that papers' Appendix B). 
-The key result in that paper is, if quasars are described as having a power-law slope, 
-$\alpha^{\nu}$ in spectral flux density, i.e., $f_\nu(\nu) \propto \nu^{\alpha_{\nu}}$ (as is conventional) 
-then 
+where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
+%%
+With this definition, although some of the objects have very well sampled, 
+`average' light curves where you are averaging over e.g. a month, or two weeks.
+
+Longer time-series, better SNR and moreover, $(1+z)$. 
+Just selecting things that would
+%%
+Doing this independtly in each band...
+%Variation
+
+%% 
+%% Object numbers: 54 VSA   MMTJ0215-0529,
+%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
+%%
+objiD 164 is SDSSJ1000+0234, faint; very faint. 
+SHELLQsJ0220-0432: (qso59) show this too. 
+CFHQSJ0216-0455
+
+\begin{figure}[H]
+  \begin{subfigure}{}
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
+    \caption{MMTJ0215-0529}
+    \label{fig:MMTJ0215-0529}
+  \end{subfigure}%
+  \begin{subfigure}{}
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
+    \caption{CFHQSJ0216-0455}
+    \label{fig:CFHQSJ0216-0455}
+  \end{subfigure}
+  \begin{subfigure}{}\quad
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
+    \caption{SHELLQsJ0220-0432}
+    \label{fig:SHELLQsJ0220-0432}
+  \end{subfigure}
+  \medskip
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% 
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Surface Density of VH$z$Qs}
+One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
+are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
+so, how many are still to be discovered and confirmed spectroscopcially?
+
+VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
+$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
+Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
+$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.
+
+VIKING is more uniform, so I calculated the averages over the whole area:
+$Z$=22.7 mag, $Y$=21.9 mag, $J$=21.4 mag, $H$=21.2 mag, $Ks$=21.1 mag.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
+  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
+    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
+    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
+    Y and H are almost uniform, but the coverage is much less.}
+  \label{fig:1}
+\end{figure}
+
+Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
+exponential decline to describe the space density of VH$z$Qs at high
+redshifts, e.g.
 \begin{equation}
-K_{\rm corr}(z) = -2.5 (1 + \alpha_{\nu}) \log[1 + z].
+\rho(z, {\rm M}_{1450} \propto 10^{k (z)}
 \end{equation}
-Here the $[-2.5 \log(1 + z)]$ term corrects for the effective narrowing of the filter width with redshift, (the ``bandpass correction'') and the $[-2.5 \alpha^{\nu} \log(1 + z)]$ term takes into account the spectral index correction.
-The bandpass correction is approximately $\approx -1.945$ at redshift $z=5$ decreasing to $-2.32$ at redshift $z=7.50$.
-
-%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
-
-\begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
-  \centering
-  \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:Lz}
-\end{figure*}
+where $z$ is the sample redshift. 
+%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
+
+UHS J-band depth 19.6 \citep[Vega; ][]{Dye2018}
+
+VISTA HEMISPHERE SURVEY DATA RELEASE 1
+Release date (will be set by ESO)
+PROPOSAL ESO No.: 179.A-2010
+PRINCIPAL INVESTIGATOR: Richard McMahon
+Authors: R. McMahon, M. Banerji, N. Lodieu for the VHS Collaboration
+
+The aim of the Vista Hemisphere Survey (VHS) is to carry out a near
+Infra-Red survey, which when combined with other VISTA Public Surveys
+will result in coverage of the whole southern celestial hemisphere
+($\sim$20,000 deg$^2$) to a depth 30 times fainter than 2MASS/DENIS in
+at least two wavebands (J and K$_s$), with an exposure time of 60 seconds
+per waveband to produce median 5σ point source (Vega) limits of $J =
+20.2$ and $K_{S} = 18.1$. In the South Galactic Cap, $\sim$5000 deg$^{2}$ will be
+imaged deeper with an exposure time of 120 seconds and also including
+the H band producing median 5$\sigma$ point limits of: J = 20.6; H = 19.8; K$_{s}$ = 18.5. 
+In this 5000 deg$^{2}$ region of sky deep multi-band optical (grizY)
+imaging data will be provided by the Dark Energy Survey (DES). The
+remainder of the high galactic latitude ($|b|>$30$^{\circ}$) sky will be imaged
+in YJHK for 60sec per band to be combined with ugriz waveband
+observations from the VST ATLAS survey. \\
+
+VHS                   YJHK            99.99, 21.2,  21.2,  20.6,  20.0                (9) \\
+
+{\tt ABmagLimits} for each survey in the database. \\
 

### 2019-06-05 tex/VHzQ.tex
big udpate re: detecions with WISE ALLWISE

@@
 WFCAM data, which covers all public surveys and PI projects from
-Semester 05A to 2017-Jan-01, and all non-proprietary VISTA data, which
+Semester 05A (2005-05-01) to 2017-Jan-01, and all non-proprietary VISTA data, which
 covers all public surveys and PI projects from science verification on
-2009-Oct-15 to 2016-Apr-01.
+2009-Oct-15 to 2017-Jan-01.
 
@@
   total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperture photometry, where the
-  individual epochs are taken from multiple projects with different
-  pointings and orientations, should help with issues such as scattered
-  light, pixel distortion and aperture corrections.
+  sources. Coadding using the matched-aperture photometry can give better results for the photometry, 
+  where the individual epochs are taken from multiple projects with different field-centres and orientations and point-spread functions since the individual epoch scattered light, pixel distortion and aperture corrections can be applied with the correct weighting.
 
   We average the aperture corrected calibrated fluxes (e.g. {\bf
-  aperJky3}), and then convert to magnitudes. Since we do not have a
-  deep image for each set of averages, we cannot calculate non-aperture
-  corrected values, so the photometry is only appropriate for
-  point-sources.
+  aperJky3}), and then convert to magnitudes.
 
@@
 \subsection{MIR data}
-The MIR data for this study comes from the Wide-field Infrared Survey
-Explorer (WISE) mission, and we utlize data from the WISE cryogenic
-and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011}
-post-cryogenic and NEOWISE Reactivation Mission
-\citep[NEOWISE-R][]{Mainzer2014} survey phases.
-
-We use data from the the beginning of the WISE mission \citep[2010
-January; ][]{Wright2010} through the fifth-year of NEOWISE-R
-operations \citep[2018 December;]{Mainzer2011}.  More specifically, we
-utilise the recently released ``unWISE Catalog''
-\citet{Schlafly2019}. The unWISE
-effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the
-unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R
-stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-
-Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016}
-found that cross-matches performed with a radius of 2-3'' between the user
-catalogue and WISE was a good compromise between completeness and
-contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. 
+The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011} post-cryogenic and NEOWISE Reactivation Mission \citep[NEOWISE-R][]{Mainzer2014} survey phases.
+
+We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
+There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
+Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}.
+The AllWISE program combines the W1 and W2 Single-exposure data from all WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
+The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.
+For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.
+
+Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
+Figure 4 of ][]{Krawczyk2013}.
 We thus use a cross-match radius of 2.75''.
-
-For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and 
-$\lambda_{\rm eff}$4.62$\mu$m W2 we use the deeper, unblurred unWISE coadd data. 
-For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m 
-we use the ALLWISE Data Release
-
 When querying the ALLWISE catalogs, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
@@
 
-Before reporting on the detection rates, we investigate this effect.
+Before reporting on the detection rates, we investigate this effect 
+using the AllWISE Source Catalog. 
 Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
@@
 With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
+AllWISE Source Catalog
 
@@
 
+%% detections_vs_WISEcoverage_plots.py
 \begin{figure}
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_20190605.pdf}
   \centering
   \vspace{-14pt}
-  \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
-    colour coded by w$x$cov the mean coverage depth, in each corresponding band.
+  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise, 
+    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
   }

### 2019-06-05 detections/detections_vs_WISEcoverage_plots_20180821.py

@@ -1,14 +1,17 @@
 '''
 WISE detections and colors of Very High redshift quasars
 '''
-import numpy as np
 
 from astropy.io import fits
 from astropy.io import ascii
 from astropy.table import Table
 
+#import matplotlib
 import matplotlib as mpl
+
 import matplotlib.pyplot as plt
+import numpy as np
+import math
 
 from matplotlib import colors as mcolors
 from matplotlib import gridspec
@@ -16,7 +19,6 @@ from matplotlib import gridspec
 from mpl_toolkits.axes_grid1.axes_divider  import make_axes_locatable
 from mpl_toolkits.axes_grid1.inset_locator import inset_axes, zoomed_inset_axes
 from mpl_toolkits.axes_grid1.colorbar      import colorbar
-
 
 ## READ-IN THE DATA FILE(S)
 path = '/cos_pc19a_npr/programs/quasars/highest_z/data/WISE/'
@@ -37,16 +39,9 @@ w3cov = all_VHzQs['w3cov']
 w4cov = all_VHzQs['w4cov']
 
 
-print()
-print('  w1mpro min, max; {:7.3f} {:7.3f} '.format(w1mpro.min(), w1mpro.max()),  '    w1snr min, max;  {:7.3f} {:7.3f} '.format(w1snr.min(), w1snr.max()))
-print('  w2mpro min, max; {:7.3f} {:7.3f} '.format(w2mpro.min(), w2mpro.max()),  '    w2snr min, max;  {:7.3f} {:7.3f} '.format(w2snr.min(), w2snr.max()))
-print('  w3mpro min, max; {:7.3f} {:7.3f} '.format(w3mpro.min(), w3mpro.max()),  '    w3snr min, max;  {:7.3f} {:7.3f} '.format(w3snr.min(), w3snr.max()))
-print('  w4mpro min, max; {:7.3f} {:7.3f} '.format(w4mpro.min(), w4mpro.max()),  '    w4snr min, max;  {:7.3f} {:7.3f} '.format(w4snr.min(), w4snr.max()))
-print()
-
 
 ##
-##  Making the plot
+##  Making thesplot
 ##
 ##  May fave new line ;-=)
 #plt.style.use('dark_background')
[…]

### 2019-06-05 tex/VHzQ.tex
Corrections to English in Section 3.1

@@
 \subsection{MIR data}
-The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011} post-cryogenic and NEOWISE Reactivation Mission \citep[NEOWISE-R][]{Mainzer2014} survey phases.
-
-We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
-There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
-Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}.
-The AllWISE program combines the W1 and W2 Single-exposure data from all WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
-The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-
-For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.
-For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.
-
-Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
-Figure 4 of ][]{Krawczyk2013}.
+The MIR data for this study comes from the Wide-field Infrared Survey
+Explorer (WISE) mission, and we utlize data from the WISE cryogenic
+and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011}
+post-cryogenic and NEOWISE Reactivation Mission
+\citep[NEOWISE-R][]{Mainzer2014} survey phases.
+
+We use data from the the beginning of the WISE mission \citep[2010
+January; ][]{Wright2010} through the fifth-year of NEOWISE-R
+operations \citep[2018 December;]{Mainzer2011}.  More specifically, we
+utilise the recently released ``unWISE Catalog''
+\citet{Schlafly2019}. The unWISE
+effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the
+unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R
+stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016}
+found that cross-matches performed with a radius of 2-3'' between the user
+catalogue and WISE was a good compromise between completeness and
+contamination \citep[see e.g. Figure 4 of ][]{Krawczyk2013}. 
 We thus use a cross-match radius of 2.75''.
+
+For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and 
+$\lambda_{\rm eff}$4.62$\mu$m W2 we use the deeper, unblurred unWISE coadd data. 
+For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m 
+we use the ALLWISE Data Release
+
 When querying the ALLWISE catalogs, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
@@
 First, we will concentrate on detection rate in the infrared, go on to
-report on the color-redshift and color-color properties of our sample
+report on the colour-redshift and colour-colour properties of our sample
 and then report on how the current sample populates the
@@
 (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
-been observed (by VHS) but are out of our queried time range.  6
-objects have not been observed (or at least the data is not in the
-WSA/VSA archives yet) and 5 objects at declination $\delta \geq +60$
+been observed (by VHS) but are out of our queried time range 
+(for which the data is publicly available). 6 objects have not been 
+observed (or at least the data is not in the
+WSA/VSA archives yet) and 5 objects are at a declination $\delta \geq +60$
 deg are too far north for UKIRT and cannot be observed.
@@
   \subsubsection{Comparing WFCAM and VISTA}
-  There are 130 overlapping QSOs between WFCAM and VISTA. Using the
-  {\tt VegaToAB} value to put these objects on the same AB system, and
-  for each object compared the two measurements. First, the calculated
+  There are 130 overlapping QSOs between WFCAM and VISTA. We used the
+  {\tt VegaToAB} values to put these objects on the same AB system, and
+  for each object compared the two measurements. First, we calculated the
   weighted average (calibrated flux) in each filter of both and
@@
   offset is the $Y$-band. All of the VISTA averages are negative and all
-  of the WFCAM ones are positive. The $Ks$ versus $K$ band may be
-  lightly dodgy, given the different shapes of the filters.
+  of the WFCAM ones are positive. The $Ks$ versus $K$ band comparison may be
+  affected the different shapes of the filters, with $K$ being significantly wider than $K_s$.
   \begin{table}
@@
     7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
-    \hline \hline
+    \hline \line
   \end{tabular}
@@
 
-Before reporting on the detection rates, we investigate this effect 
-using the AllWISE Source Catalog. 
+Before reporting on the detection rates, we investigate this effect.
 Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
@@
 The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4.
-With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
-AllWISE Source Catalog
+With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
 
@@
 For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands).
-These values are direclty from the {\tt w$x$cov} enteries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
-
-%% detections_vs_WISEcoverage_plots.py
+These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
+
 \begin{figure}
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_20190605.pdf}
+  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
   \centering
   \vspace{-14pt}
-  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise, 
-    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
+  \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
+    colour coded by w$x$cov the mean coverage depth, in each corresponding band.
   }

### 2019-06-05 tex/VHzQ.tex
tex/VHzQ.tex

@@
 We thus use a cross-match radius of 2.75''.
-When querying the ALLWISE catalogs, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
+When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
 The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
@@
 
-Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalog and also query the AllWISE Reject Table.
+Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table.
 However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.
@@
 
-Before reporting on the detection rates, we investigate this effect.
-Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
+Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog.
+Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
 In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude.
 The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4.
-With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
+With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
+%%AllWISE Source Catalog
 
@@
 contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
-AGN candidates per deg$^2$) while the ``C75'' catalog 
+AGN candidates per deg$^2$) while the ``C75'' catalogue  
 consists of 20.9M AGN candidates at 75\% completeness (and 
@@
 
+%\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
 Very High-$z$ Quasars Detected in WISE W3 and W4.
@@
     \centering
-    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png}} 
-    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}} 
-    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}}
-    \subfigure[]{\includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}}
-    \caption{(a) UHS J0439+1634 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
+    \caption{ (a) UHS J0439+1634 
                  (b) SDSS J0100+280 
@@
 \end{figure*}
-\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
 

### 2019-06-05 tex/VHzQ.tex
VHzQ.tex, VHzQ.pdf update
Bilicki2016 reference added

@@
 
-Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilick2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
+Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
 Figure 4 of ][]{Krawczyk2013}.
@@
     7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
-    \hline \line
+    \hline \hline
   \end{tabular}

### 2019-06-05 tex/VHzQ.tex
tables_for_paper/unWISE_redshift_det.py and  tex/VHzQ.* updated

@@
 
-For the 278 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
+For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
 For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands).
@@
     \hline  
-    W1 SNR $> 2.0$                                             &  275  (64.9) \\
-    W2 SNR $> 2.0$                                            &   255 (60.1) \\
+    W1 SNR $> 3.0$                                             &  362  (xxz.9) \\
+    W2 SNR $> 3.0$                                            &   255 (60.1) \\
     W1 $\land$ W2 SNR $> 2.0$                         &  \\

### 2019-06-05 tables_for_paper/unWISE_redshift_det.py

@@ -29,6 +29,7 @@ VHzQs    = ascii.read(path+filename)
 len(VHzQs)
 
 ##  S N R   C U T 
+snr_cut = 3.0
 
 ##     BY    SNR
 unW1            = VHzQs[np.where( VHzQs['unW1snr'] > snr_cut)]
@@ -43,14 +44,14 @@ AllW4_not_AllW3 = VHzQs[np.where((VHzQs['w4snr']   > snr_cut)  & (VHzQs['w3snr']
 
 ## Setting up the variables just for me to use a bit easier
 ##     BY    MAGNITUDES
-unW1            = VHzQs[np.where( VHzQs['unW1mag']>-1)]
-unW1_not_unW2   = VHzQs[np.where((VHzQs['unW1mag']>-1) & (VHzQs['unW2mag']<-1))]
-unW2            = VHzQs[np.where( VHzQs['unW2mag']>-1)]
-unW2_not_unW1   = VHzQs[np.where((VHzQs['unW2mag']>-1) & (VHzQs['unW1mag']<-1))]
-AllW3           = VHzQs[np.where( VHzQs['w3mpro']>-1)]
-AllW3_not_AllW4 = VHzQs[np.where((VHzQs['w3mpro']>-1)  & (VHzQs['w4mpro']<-1))]
-AllW4           = VHzQs[np.where( VHzQs['w4mpro']>-1)]
-AllW4_not_AllW3 = VHzQs[np.where((VHzQs['w4mpro']>-1)  & (VHzQs['w3mpro']<-1))]
+#unW1            = VHzQs[np.where( VHzQs['unW1mag']>-1)]
+#unW1_not_unW2   = VHzQs[np.where((VHzQs['unW1mag']>-1) & (VHzQs['unW2mag']<-1))]
+#unW2            = VHzQs[np.where( VHzQs['unW2mag']>-1)]
+#unW2_not_unW1   = VHzQs[np.where((VHzQs['unW2mag']>-1) & (VHzQs['unW1mag']<-1))]
+#AllW3           = VHzQs[np.where( VHzQs['w3mpro']>-1)]
+#AllW3_not_AllW4 = VHzQs[np.where((VHzQs['w3mpro']>-1)  & (VHzQs['w4mpro']<-1))]
+#AllW4           = VHzQs[np.where( VHzQs['w4mpro']>-1)]
+#AllW4_not_AllW3 = VHzQs[np.where((VHzQs['w4mpro']>-1)  & (VHzQs['w3mpro']<-1))]
 
 
 
[…]

### 2019-06-06 tex/VHzQ.tex
tex/VHzQ.* update

@@
 two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
-primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
+primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
 Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
@@
 For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.
+Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}.
+The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.
 
@@
 Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table.
-However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.
+However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection information.
 
@@
 The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4.
-With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
+With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
 %%AllWISE Source Catalog
@@
 SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
-mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
+matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
 matches J1342+0928 \citep{Banados2018}.
@@
 
-Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).
+Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).
 
@@
 %%
-Doing this independtly in each band...
+Doing this independently in each band...
 %Variation
@@
 are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
-so, how many are still to be discovered and confirmed spectroscopcially?
-
-VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
+so, how many are still to be discovered and confirmed spectroscopically?
+
+VHS, Area 1: 150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:
 $Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
@@
 \label{sec:conclusions}
-In this study, we have, for the first time, ompiled the list of all
+In this study, we have, for the first time, compiled the list of all
 $z>5$ spectroscopically confirmed quasars. We have assemble the NIR
@@
 N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
-%%
 

### 2019-06-06 tex/VHzQ.tex
light_curves/MIR_LCs big update

@@
 
-For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
+%% For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
 For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands).

### 2019-06-06 light_curves/MIR_LCs/NEOWISER_LCs_singleObject.py

@@ -14,7 +14,8 @@ from matplotlib.backends.backend_pdf import PdfPages
 
 import random
 
-path='/cos_pc19a_npr/data/highest_z_QSOs/'
+#path='/cos_pc19a_npr/data/highest_z_QSOs/'
+path = '/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/'
 file = 'NEOWISER-R_SingleExposure_L1bs.tbl'
 
 data = ascii.read(path+file) 
@@ -48,10 +49,11 @@ for x in range(upto_this):
 #for x in range(10):
     x=x+1
     data_one = data[np.where(data['cntr_01'] == x)]
-    
-    if len(data_one) > 0:  
 
-        print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
+    if len(data_one) > 0:  
+    
+        #print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
+        print(len(data_one))
         totes = totes + len(data_one)
         ra = data_one['ra'][0]
         dec = data_one['dec'][0]
@@ -94,9 +96,17 @@ for x in range(upto_this):
         ax3.set_ylabel('W1 - W2', fontsize=fontsize)
         ax3.tick_params('x', direction='in', which='both', bottom='True', top='True', left='True', right='True',  labelsize=fontsize)
         ax3.tick_params('y', direction='in', which='both', bottom='True', top='True', left='True', right='False', labelsize=fontsize)
+
+    ## Putting in the `else' will give you enteries for 0 in NoOfEpochs_perQuasar.dat
+    ## and will also have the NEOWISER_LCs_VHzQs_temp.pdf be 463 pages long. However,
+    ## you get duplicate plots in NEOWISER_LCs_VHzQs_temp.pdf for the `else' objects. 
+    else:
+        print('0')
         
-        ## Done with the page
-        pdf_pages.savefig(fig)
+    ## Done with the page
+    pdf_pages.savefig(fig)
+
+                               
     
 ## Write the PDF document to the disk
 pdf_pages.close()   

### 2019-06-07 color_color/W1W2W3_hexplots.py
VHzQ; updating color_color directory

@@ -1,116 +1,0 @@
-'''
-Making the 'famous' W2-W3 vs. W1-W2 WISE color-color plot
-'''
-
-import numpy as np
-from astropy.io    import fits
-from astropy.io    import ascii
-from astropy.table import Table
-
-import matplotlib
-import matplotlib.pyplot as plt
-from matplotlib.ticker import MultipleLocator, FormatStrFormatter
-
-##
-## DR14Q
-##
-path = '/cos_pc19a_npr/data/SDSS/DR14Q/'
-filename ='DR14Q_v4_4.fits'
-#filename ='DR14Q_v4_4_W4good.fits'
-infile = path+filename
-data = fits.getdata(infile, 1)
-dr14q = Table(data)
-
-##
-##  V H z Q    data
-##
-path = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
-filename ='THE_TABLE_v0pnt971.dat'
-table=path+filename
-VHzQ = ascii.read(table)
-
-
-##  Making the plot(s)
-## 
-##  W2-W3  vs.  W1-W2 
-##
-plt.rcParams.update({'font.size': 14})
-fig, ax = plt.subplots(figsize=(10, 10), num=None, dpi=80, facecolor='w', edgecolor='k')
-
-## Blain et al. (2013), Figure 1:: 
-#xmin =  1.7; xmax =  4.7; ymin = -0.2; ymax =  2.0 
-## Wright et al. (2010), Figure 
-xmin=-1.0; xmax=7.0; ymin=-0.5; ymax=4.0
-
-#cmap = plt.cm.RdBu_r
-#cmap = plt.cm.inferno
-cmap = plt.cm.rainbow
-ls              = 24
-ticklength      = 18
-tickwidth       = 2.0
-pointsize       = 60
-pointsize_large = pointsize*1.2
-##
-## Plotting the   D R 1 4 Q    hexbins
-##
-hb = ax.hexbin( (dr14q['W2MAG']- dr14q['W3MAG']), (dr14q['W1MAG'] - dr14q['W2MAG']), C=dr14q['Z'],
-            gridsize=180, mincnt=25, marginals=False, cmap=cmap, vmin=0.00, vmax=3.00)
-cb = fig.colorbar(hb, ax=ax)
-cb.set_label('redshift')
-
-##
-## Plotting the    V H z Q    points
-##
[…]

### 2019-06-07 color_color/W1W2_colors.py

@@ -1,153 +1,0 @@
-'''
-  Banados 2016 figures (3)
-  Carnall z-W1, W1-W2 (1)
-  W123 (1) 
-  HSC SHELLQS plots (??)
-  In the ‘exact’ style of the Banado2016 figures...
-'''
-from astropy.io import fits
-from astropy.io import ascii
-from astropy.table import Table
-
-import matplotlib
-import matplotlib.pyplot as plt
-import numpy as np
-import math
-
-from matplotlib import colors as mcolors
-from matplotlib import gridspec
-
-
-##
-##  V H z Q    data
-##
-path = '/cos_pc19a_npr/data/highest_z_QSOs/'
-#filename ='THE_TABLE_v0pnt96.dat'
-filename  ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
-table=path+filename
-VHzQ = ascii.read(table)
-
-redshift = VHzQ['redshift']
-g_PS1 = VHzQ['gMag']
-r_PS1 = VHzQ['rMag']
-i_PS1 = VHzQ['iMag']
-z_PS1 = VHzQ['zMag']
-y_PS1 = VHzQ['yMag']
-Ymag  = VHzQ['Yapermag']
-Jmag  = VHzQ['Jmag']
-Hmag  = VHzQ['Hmag']
-Kmag  = VHzQ['Kmag']
-W1mag = VHzQ['W1mag']
-W2mag = VHzQ['W2mag']
-W3mag = VHzQ['W3mag']
-W4mag = VHzQ['W4mag']
-
-'''
-https://blog.backyardworlds.org/page/2/
-'''
-path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
-filename ='Ldwarfs_photom_v1pnt00.dat'
-table=path+filename
-Ldwarfs = ascii.read(table)
-Ldwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
-
-path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
-filename ='Tdwarfs_photom_v1pnt00.dat'
-table=path+filename
-Tdwarfs = ascii.read(table)
-#Tdwarfs = Ldwarfs[np.where( (Tdwarfs['W3snr'] > 3.0))]
-
-
-## 
-##  Making the plot(s)
-##
-plt.rcParams.update({'font.size': 14})
[…]

### 2019-06-07 color_color/W1W2_hexplots.py
color_color W1W2 update

@@ -1,139 +1,0 @@
-'''
-Making the 'famous' W2-W3 vs. W1-W2 WISE color-color plot
-'''
-
-import numpy as np
-from astropy.io    import fits
-from astropy.io    import ascii
-from astropy.table import Table
-
-import matplotlib
-import matplotlib.pyplot as plt
-from   matplotlib.ticker import MultipleLocator, FormatStrFormatter
-
-##
-## DR14Q
-##
-path = '/cos_pc19a_npr/data/SDSS/DR14Q/'
-filename ='DR14Q_v4_4.fits'
-#filename ='DR14Q_v4_4_W4good.fits'
-infile = path+filename
-data = fits.getdata(infile, 1)
-dr14q = Table(data)
-
-##
-##  V H z Q    data
-##
-path = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
-filename ='VHzQs463_unWISE_v1pnt00.dat'
-table=path+filename
-VHzQ = ascii.read(table)
-
-
-##  Making the plot(s)
-## 
-##     W2  vs.  W1-W2
-##
-##    (e.g. Blain et al. 2013, Figure 1;
-##          Assef et al. 2018 and the `R90' and `C75' samples) 
-##
-plt.rcParams.update({'font.size': 14})
-#plt.style.use('dark_background')
-
-## works well for xmin=13.6; xmax=16.9; ymin=-0.2; ymax=3.2:: 
-#fig, ax = plt.subplots(figsize=(10, 10), num=None, dpi=80, facecolor='w', edgecolor='k') 
-## works well for xmin=13.0; xmax=16.9; ymin=-0.2; ymax=3.2:: 
-fig, ax = plt.subplots(figsize=(14, 10), num=None, dpi=80, facecolor='w', edgecolor='k')  
-
-xmin=12.4; xmax=17.6; ymin=-0.5; ymax=2.6
-
-## Plotting setup
-ls              = 30.
-lw              = 2.0
-fontsize        = 30
-ticklength      = 18
-tickwidth       = 2.0
-pointsize       = 60
-pointsize_large = pointsize*1.2
-
-xmin = 12.4; xmax = 17.6; ymin = -0.5; ymax = 2.6   # decent enough
-xmin = 12.4; xmax = 18.4; ymin = -0.5; ymax = 2.6   # decent enough
-ax.axis([xmin, xmax, ymin, ymax])
-
-
-##
[…]

### 2019-06-07 color_color/W1W2_vs_zW2_Carnall.py

@@ -1,137 +1,0 @@
-'''
-   Carnall z-W1, W1-W2 (1)
-'''
-from astropy.io import fits
-from astropy.io import ascii
-from astropy.table import Table
-
-from time import sleep
-
-import matplotlib
-import matplotlib.pyplot as plt
-import numpy as np
-import math
-
-from matplotlib import colors as mcolors
-from matplotlib import gridspec
-
-##
-##  V H z Q    data
-##
-path = '/cos_pc19a_npr/data/highest_z_QSOs/'
-#filename ='THE_TABLE_v0pnt96.dat'
-filename ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
-table=path+filename
-VHzQ = ascii.read(table)
-#VHzQ = VHzQ[np.where( (VHzQ['redshift'] >= 5.7) & (VHzQ['redshift'] <= 6.7))]
-
-
-redshift = VHzQ['redshift']
-g_PS1 = VHzQ['gMag']
-r_PS1 = VHzQ['rMag']
-i_PS1 = VHzQ['iMag']
-z_PS1 = VHzQ['zMag']
-y_PS1 = VHzQ['yMag']
-Ymag  = VHzQ['Yapermag']
-Jmag  = VHzQ['Jmag']
-Hmag  = VHzQ['Hmag']
-Kmag  = VHzQ['Kmag']
-W1mag = VHzQ['W1mag']
-W2mag = VHzQ['W2mag']
-W3mag = VHzQ['W3mag']
-W4mag = VHzQ['W4mag']
-
-'''
-https://blog.backyardworlds.org/page/2/
-'''
-path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
-filename ='Ldwarfs_photom_v1pnt00.dat'
-table=path+filename
-Ldwarfs = ascii.read(table)
-#Ldwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
-
-path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
-filename ='Tdwarfs_photom_v1pnt00.dat'
-table=path+filename
-Tdwarfs = ascii.read(table)
-#Tdwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
-
-##
-##  Making the plot(s)
-##
-plt.rcParams.update({'font.size': 14})
-#matplotlib.rc('text', usetex=True)
-
[…]

### 2019-06-07 color_color/W1W2_plots/W1W2W3_hexplots.py
color_color/W1W2_plots/ update

@@ -1,0 +1,116 @@
+'''
+Making the 'famous' W2-W3 vs. W1-W2 WISE color-color plot
+'''
+
+import numpy as np
+from astropy.io    import fits
+from astropy.io    import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+
+##
+## DR14Q
+##
+path = '/cos_pc19a_npr/data/SDSS/DR14Q/'
+filename ='DR14Q_v4_4.fits'
+#filename ='DR14Q_v4_4_W4good.fits'
+infile = path+filename
+data = fits.getdata(infile, 1)
+dr14q = Table(data)
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
+filename ='THE_TABLE_v0pnt971.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+
+##  Making the plot(s)
+## 
+##  W2-W3  vs.  W1-W2 
+##
+plt.rcParams.update({'font.size': 14})
+fig, ax = plt.subplots(figsize=(10, 10), num=None, dpi=80, facecolor='w', edgecolor='k')
+
+## Blain et al. (2013), Figure 1:: 
+#xmin =  1.7; xmax =  4.7; ymin = -0.2; ymax =  2.0 
+## Wright et al. (2010), Figure 
+xmin=-1.0; xmax=7.0; ymin=-0.5; ymax=4.0
+
+#cmap = plt.cm.RdBu_r
+#cmap = plt.cm.inferno
+cmap = plt.cm.rainbow
+ls              = 24
+ticklength      = 18
+tickwidth       = 2.0
+pointsize       = 60
+pointsize_large = pointsize*1.2
+##
+## Plotting the   D R 1 4 Q    hexbins
+##
+hb = ax.hexbin( (dr14q['W2MAG']- dr14q['W3MAG']), (dr14q['W1MAG'] - dr14q['W2MAG']), C=dr14q['Z'],
+            gridsize=180, mincnt=25, marginals=False, cmap=cmap, vmin=0.00, vmax=3.00)
+cb = fig.colorbar(hb, ax=ax)
+cb.set_label('redshift')
+
+##
+## Plotting the    V H z Q    points
+##
[…]

### 2019-06-07 color_color/W1W2_plots/W1W2_colors.py

@@ -1,0 +1,153 @@
+'''
+  Banados 2016 figures (3)
+  Carnall z-W1, W1-W2 (1)
+  W123 (1) 
+  HSC SHELLQS plots (??)
+  In the ‘exact’ style of the Banado2016 figures...
+'''
+from astropy.io import fits
+from astropy.io import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import math
+
+from matplotlib import colors as mcolors
+from matplotlib import gridspec
+
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/data/highest_z_QSOs/'
+#filename ='THE_TABLE_v0pnt96.dat'
+filename  ='THE_TABLE_v0pnt97x_PS1_ULAS_VHS_photom_v2.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+redshift = VHzQ['redshift']
+g_PS1 = VHzQ['gMag']
+r_PS1 = VHzQ['rMag']
+i_PS1 = VHzQ['iMag']
+z_PS1 = VHzQ['zMag']
+y_PS1 = VHzQ['yMag']
+Ymag  = VHzQ['Yapermag']
+Jmag  = VHzQ['Jmag']
+Hmag  = VHzQ['Hmag']
+Kmag  = VHzQ['Kmag']
+W1mag = VHzQ['W1mag']
+W2mag = VHzQ['W2mag']
+W3mag = VHzQ['W3mag']
+W4mag = VHzQ['W4mag']
+
+'''
+https://blog.backyardworlds.org/page/2/
+'''
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Ldwarfs_photom_v1pnt00.dat'
+table=path+filename
+Ldwarfs = ascii.read(table)
+Ldwarfs = Ldwarfs[np.where( (Ldwarfs['W3snr'] > 3.0))]
+
+path = '/cos_pc19a_npr/data/highest_z_QSOs/LT_dwarfs/'
+filename ='Tdwarfs_photom_v1pnt00.dat'
+table=path+filename
+Tdwarfs = ascii.read(table)
+#Tdwarfs = Ldwarfs[np.where( (Tdwarfs['W3snr'] > 3.0))]
+
+
+## 
+##  Making the plot(s)
+##
+plt.rcParams.update({'font.size': 14})
[…]

### 2019-06-07 color_color/W1W2_plots/W1W2_hexplots.py

@@ -1,0 +1,139 @@
+'''
+Making the 'famous' W2-W3 vs. W1-W2 WISE color-color plot
+'''
+
+import numpy as np
+from astropy.io    import fits
+from astropy.io    import ascii
+from astropy.table import Table
+
+import matplotlib
+import matplotlib.pyplot as plt
+from   matplotlib.ticker import MultipleLocator, FormatStrFormatter
+
+##
+## DR14Q
+##
+path = '/cos_pc19a_npr/data/SDSS/DR14Q/'
+filename ='DR14Q_v4_4.fits'
+#filename ='DR14Q_v4_4_W4good.fits'
+infile = path+filename
+data = fits.getdata(infile, 1)
+dr14q = Table(data)
+
+##
+##  V H z Q    data
+##
+path = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
+filename ='VHzQs463_unWISE_v1pnt00.dat'
+table=path+filename
+VHzQ = ascii.read(table)
+
+
+##  Making the plot(s)
+## 
+##     W2  vs.  W1-W2
+##
+##    (e.g. Blain et al. 2013, Figure 1;
+##          Assef et al. 2018 and the `R90' and `C75' samples) 
+##
+plt.rcParams.update({'font.size': 14})
+#plt.style.use('dark_background')
+
+## works well for xmin=13.6; xmax=16.9; ymin=-0.2; ymax=3.2:: 
+#fig, ax = plt.subplots(figsize=(10, 10), num=None, dpi=80, facecolor='w', edgecolor='k') 
+## works well for xmin=13.0; xmax=16.9; ymin=-0.2; ymax=3.2:: 
+fig, ax = plt.subplots(figsize=(14, 10), num=None, dpi=80, facecolor='w', edgecolor='k')  
+
+xmin=12.4; xmax=17.6; ymin=-0.5; ymax=2.6
+
+## Plotting setup
+ls              = 30.
+lw              = 2.0
+fontsize        = 30
+ticklength      = 18
+tickwidth       = 2.0
+pointsize       = 60
+pointsize_large = pointsize*1.2
+
+xmin = 12.4; xmax = 17.6; ymin = -0.5; ymax = 2.6   # decent enough
+xmin = 12.4; xmax = 18.4; ymin = -0.5; ymax = 2.6   # decent enough
+ax.axis([xmin, xmax, ymin, ymax])
+
+
+##
[…]

### 2019-06-07 tables_for_paper/unWISE_redshift_det.py

@@ -30,6 +30,11 @@ len(VHzQs)
 
 ##  S N R   C U T 
 snr_cut = 3.0
+print()
+print()
+print(' S N R   C U T  is  >  ',  snr_cut)
+print()
+print()
 
 ##     BY    SNR
 unW1            = VHzQs[np.where( VHzQs['unW1snr'] > snr_cut)]
@@ -72,6 +77,15 @@ print()
 print('ALLWISE W4                 & ', len(AllW4),           '( {:5.2f})'.format(len(AllW4)/len(VHzQs)*100.), ' \\\ ')
 print('ALLWISE W4 and !AllWISE W3 & ', len(AllW4_not_AllW3), '( {:5.2f})'.format(len(AllW4_not_AllW3)/len(VHzQs)*100.), '  \\\ ')
 print('\hline \hline')
+
+
+## WISE W4 numbers
+AllW4_7thmag           = VHzQs[np.where((VHzQs['w4mpro']  < 8.00)     & (VHzQs['w4mpro']  > 0.00    ))]
+AllW4_8thmag           = VHzQs[np.where((VHzQs['w4mpro']  < 9.00)     & (VHzQs['w4mpro']  > 8.00    ))]
+print('WISE W4 numbers...')
+print('ALLWISE W4 with  w4snr > snr_cut    & ', len(AllW4),           '( {:5.2f})'.format(len(AllW4)/len(VHzQs)*100.), ' \\\ ')
+print('ALLWISE W4 with  w4mpro < 8.00 mag  & ', len(AllW4_7thmag),    '( {:5.2f})'.format(len(AllW4_7thmag)/len(VHzQs)*100.), ' \\\ ')
+print()
 
 
 ## By redshift

### 2019-06-07 tex/VHzQ.tex
color_color/W1W2_plots/ update
VHzQ.tex update

@@
 
+The VH$z$Q with the bluest colour in (W1 - W2) is 
+DELS J1048-0109 with (W1-W2) = 0.154 
+(see Figure~\ref{fig:DELS_J1048}).
+
 %\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
@@
 
-We thank Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA), and 
-also the VISTA Science Archive (VSA). We thank Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface.
-
-We thank Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
-
-We thank Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion.
+We thank:
+\begin{list}{$\circ$}{}  
+\item Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA) and the VISTA Science Archive (VSA). 
+\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
+\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
+\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
+\end{list}
 

### 2019-06-07 color_color/W1W2_plots/W1W2W3_hexplots.py
tex/mn2e removed

@@ -58,14 +58,19 @@ pointsize_large = pointsize*1.2
 ##
 hb = ax.hexbin( (dr14q['W2MAG']- dr14q['W3MAG']), (dr14q['W1MAG'] - dr14q['W2MAG']), C=dr14q['Z'],
             gridsize=180, mincnt=25, marginals=False, cmap=cmap, vmin=0.00, vmax=3.00)
-cb = fig.colorbar(hb, ax=ax)
-cb.set_label('redshift')
+#$cb = fig.colorbar(hb, ax=ax)
+#cb.set_label('redshift')
 
 ##
 ## Plotting the    V H z Q    points
 ##
-#ax.scatter((VHzQ['w2mag'] -  VHzQ['w3mag']),  (VHzQ['w1mag'] - VHzQ['w2mag']), color='k', s=pointsize )
-#ax.scatter(0,0, color='w', s=pointsize_large)
+cmap = plt.cm.inferno
+hb_VHzQ = ax.scatter((VHzQ['w2mag'] -  VHzQ['w3mag']),  (VHzQ['w1mag'] - VHzQ['w2mag']), c=VHzQ['redshift'], s=pointsize )
+ax.scatter(0,0, color='w', s=pointsize_large)
+
+cb = fig.colorbar(hb_VHzQ, ax=ax)
+cb.set_label('redshift')
+
 
 ## The vertical dashed line at W 2 − W3 = 5.3 is one of the selection
 ## criteria for W1W2-dropouts; some are bluer than this because they

### 2019-06-10 tex/VHzQ.tex
tex/mn2e removed
tex update

@@
 VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
-mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
+mid-infrared, $\lambda=3-30\mu$m wavelength data is from the 
 Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
@@
 
-We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
+We use data from the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
 There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
@@
 N.P.R.
-initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
-%%
+initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
+
 N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
@@
 %\bibliographystyle{apj}
-\bibliographystyle{mn2e}
+%\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{tester_mnras}

### 2019-06-10 tex/VHzQ.tex
Minor changes

--- 2019-06-06 tex/VHzQ.tex
@@
   of the WFCAM ones are positive. The $Ks$ versus $K$ band comparison may be
-  affected the different shapes of the filters, with $K$ being significantly wider than $K_s$.
+  affected the different shapes of the filters, with $K$ being significantly 
+  wider than $K_s$, able to detect light at longer wavelengths.
   \begin{table}
@@
   was $>0.$ and $>5$ average flux error. In order to account for large
-  errors in either the WFCAM or VISTA photometry, objects with deltaMag$
-  < 2 \times$ deltaMagErr in either WSA or VSA were removed. This
+  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
+  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
   selects two quasars with large, $\delta$mag $>0.2$mag differences
@@
   SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
-  19.13$\pm$-0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
+  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
   mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
@@
   \caption{Detection rates in the mid-infrared bands from WISE as a function of 
-    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
+    redshift. A signal-to-noise cut of {\tot w$x$snr}$>3.0$ has been used for each band.}
   \label{tab:WFCAM_vs_VISTA}
@@
 candidates identified across 30,000 deg$^2$ of extragalactic sky 
-from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
+from the WISE AllWISE Data Release. The ``R90'' catalogue, 
 contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
@@
 ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-out catalogue of 463 VH$z$Qs with these catalogues, produces 
+our catalogue of 463 VH$z$Qs with these catalogues, produces 
 42 matches with	the R90 sample and 98 matches with the C75 sample. 
@@
 matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
-matches J1342+0928 \citep{Banados2018}.
+matches to J1342+0928 \citep{Banados2018}.
+
+The VH$z$Q with the bluest colour in (W1 - W2) is 
+DELS J1048-0109 with (W1-W2) = 0.154 
+(see Figure~\ref{fig:DELS_J1048).
 
@@
     \caption{ (a) UHS J0439+1634 
-                 (b) SDSS J0100+280 
+                 (b) SDSS J0100+2802 
                (c) SDSS J1443+3623 
@@
 have have large values of changing mass accretion rate, $\ddot{m}_{\rm
-accr}$. A consequence of this would be that these quasar exhibit signs
+accr}$. A consequence of this would be that these quasars exhibit signs
 of variability, most likely showing up in their UV/optical rest-frame

### 2019-06-10 tex/older_tex/VHzQ_20190610.tex

--- 2019-06-10 tex/VHzQ.tex
@@
   %% trim=l b r t
-  \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
+  \includegraphics[width=8.6cm, clip, trim=2mm 0mm 2mm 0mm]
   {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
+    {../color_color/W1W2_plots/W1W2W3_hexplots_20190610v2.png} 
+  \vspace{-14pt}
+    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
+      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
+      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
+      (grey colour-scale). }
+    \label{fig:W1W2W3}
+\end{figure}
+
+\subsection{MIR Colours}
+Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
+space diagram showing the WISE colours for the 283 VH$z$Q that have
+reported w3mpro values (blue to red coloured points).  400,000 quasars
+at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
+colour-scale). 
+%%
 The VH$z$Q with the bluest colour in (W1 - W2) is 

### 2019-06-10 tex/VHzQ.tex
VHzQ.tex update

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
+    {../color_color/W1W2_plots/W1W2W3_hexplots_20190610v2.png} 
+  \vspace{-14pt}
+    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
+      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
+      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
+      (grey colour-scale). }
+    \label{fig:W1W2W3}
+\end{figure}
+
+\subsection{MIR Colours}
+
+%% 
+%%    (W1 - W2)    vs.  (W2 - W3) 
+%% Call W1 ~ 3-4um annd W2   4-5um and   W3 10-16um
+Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
+space diagram showing the WISE colours for the 283 VH$z$Q that have
+reported w3mpro values (blue to red coloured points).  400,000 quasars
+at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
+colour-scale). 
+W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
+W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
+W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars, 
+1
+
+%%
 The VH$z$Q with the bluest colour in (W1 - W2) is 
 DELS J1048-0109 with (W1-W2) = 0.154 
-(see Figure~\ref{fig:DELS_J1048).
+(see Figure~\ref{fig:DELS_J1048}).
 

### 2019-06-10 tex/VHzQ.tex
VHzQ.tex \tot back to \tt
tex/VHzQ update

@@
 %%trim=l b r t
-  \includegraphics[width=8.0cm, clip, trim=0mm 0mm 2mm 0mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/data/WSA_VSA/CoverageMaps_VHzQ_forpaper.png}
+  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
+  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
   \centering
   \caption[]
-  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by white diamonds.}
+  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
   \label{fig:coverage}
@@
   \caption{Detection rates in the mid-infrared bands from WISE as a function of 
-    redshift. A signal-to-noise cut of {\tot w$x$snr}$>3.0$ has been used for each band.}
+    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
   \label{tab:WFCAM_vs_VISTA}

### 2019-06-10 tables_for_paper/unWISE_redshift_det.py
data/WSA_VSA tidy

@@ -90,6 +90,7 @@ print()
 
 ## By redshift
 redshift_array = np.array([5.00, 5.70, 6.00, 6.19, 6.50, 6.78, 7.00, 7.50])
+#redshift_array = np.array([5.00, 5.70, 6.00, 6.19, 6.50, 6.70, 7.00, 7.50])
 
 ## How many of the VHzQs are above a given redshift 
 N_zgt5pnt00 = np.count_nonzero(VHzQs['redshift'] >= redshift_array[0]) 

### 2019-06-10 tex/older_tex/VHzQ_20190610.tex
big tex/VHzQ update

@@
     redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
-  \label{tab:WFCAM_vs_VISTA}
+  \label{tab:mir_detection}
 \end{table}
@@
 
-Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog.
-Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
-In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude.
-The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4.
-With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
-%%AllWISE Source Catalog
-
-%% For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).
-For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands).
-These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.
-
-%% detections_vs_WISEcoverage_plots.py
 \begin{figure}
@@
   \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise,
-    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
-  }
+    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
   \label{fig:WISEmag_vs_coverage}
 \end{figure}
+Before reporting on the detection rates, we investigate this effect
+using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
+shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
+by {\tt w$x$cov} the mean coverage depth, in each corresponding
+band. In the two shorter bands W1/2 we see the clear and expected
+trend for brighter objects to have larger SNR, and also for the higher
+signal to noise for objects with more exposures at a given
+magnitude. The behaviour for the W3/4 bands is different, with two
+populations clearly evident in W3 and although a bit more mixed, also
+in W4. With the suggested split at SNR$>2$, and no obvious
+R.A./Declination dependence seen, this behaviour is explained by the
+fact that there are non-detections in W3/4 for objects (with high W1/2
+SNR) that are reported in the ALLWISE catalogue.
 
 Table~\ref{tab:mir_detection} gives the detection rates for the
-VH$z$Qs in the MIR WISE W1-4 bands. 
-\begin{table}
-  \begin{tabular}{l r l}
-    \hline  \hline
-    Selection   & number detected (\%) \\
-    \hline  
-    W1 SNR $> 3.0$                                             &  362  (xxz.9) \\
-    W2 SNR $> 3.0$                                            &   255 (60.1) \\
-    W1 $\land$ W2 SNR $> 2.0$                         &  \\
-    W3 SNR $> 2.0$                                            &  99    (23.3) \\
-    W4 SNR $> 2.0$                                            &  29    (6.8) \\
-    Any W1/2/3/4 SNR $>2.0$                           & \\
-    W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
-    \hline  \hline
-  \end{tabular}
-  \caption{}
-  \label{tab:mir_detection}
-\end{table}
+VH$z$Qs in the MIR WISE W1-4 bands. The unWISE depths are impressive
+with nearly 80\% of all the VH$z$Qs being detected in unWISE W1. 12
+out of 14 (86\%) in unWISE W1 (9 our of 14; 64\% in unWISE W2) of the
+$z\geq6.78$ quasars are detected and moreover {\it all of the $z\geq7$
+quasars are detected in both unWISE W1 and W2}. This bodes very well
+for future, small mirror infrared missions \citep[e.g.][]{NEOCam_WP}.
 
@@
 
-\citet{Blain2013}
-
 Recently, \citet{Assef2018} released two large catalogues of AGN
-candidates identified across 30,000 deg$^2$ of extragalactic sky 
-from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
-contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
-AGN candidates per deg$^2$) while the ``C75'' catalogue  
-consists of 20.9M AGN candidates at 75\% completeness (and 
-($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-out catalogue of 463 VH$z$Qs with these catalogues, produces 
-42 matches with	the R90 sample and 98 matches with the C75 sample. 
-Both catalogues unsurprisingly match to the ultraluminous quasar 
-SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
-matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
-matches J1342+0928 \citep{Banados2018}.
+candidates identified across 30,000 deg$^2$ of extragalactic sky from
+the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
+AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
+per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
+candidates at 75\% completeness (and ($\approx$700 AGN candidates per
+deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
+catalogues, produces 42 matches with the R90 sample and 98 matches
+with the C75 sample. Both catalogues unsurprisingly match to the
+ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
+not the R90 catalogue matches to ULAS J1120+0641
+\citep{Mortlock2011}. Neither catalogue matches to J1342+0928
+\citep{Banados2018}.
 
@@
     \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {../color_color/W1W2_plots/W1W2W3_hexplots_20190610v2.png} 
+    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
   \vspace{-14pt}
@@
 \subsection{MIR Colours}
+%% The VH$z$Q with the bluest colour in (W1 - W2) is 
+DELS J1048-0109 with (W1-W2) = 0.154. 
+%(see Figure~\ref{fig:DELS_J1048}).
+%%
+%%    (W1 - W2)    vs.  (W2 - W3) 
+%%
+%%  Call W1 ~ 3-4um annd W2   4-5um and   W3 10-16um
 Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
@@
 colour-scale). 
-%%
-The VH$z$Q with the bluest colour in (W1 - W2) is 
-DELS J1048-0109 with (W1-W2) = 0.154 
-(see Figure~\ref{fig:DELS_J1048}).
-
+%W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
+%W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
+%W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars,
+
+%%
 %\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
-Very High-$z$ Quasars Detected in WISE W3 and W4.
+The are a set of VH$z$Q detected in WISE W3 and W4. 51 objects are detected in the broad W3 filter and 10 objects are formally 
+detected in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are presented in  \label{fig:VHzQ_W4s}.
+UHS J0439+1634 (Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by \citet{Fan2019}
+ and is a strongly lensed quasar at $z=$6.51. This high luminosity is most not intrinsic, but is 
+boosted by an intervening redshift $z\sim$0.7 galaxy. 
+SDSS J0100+2802 (redshift $z=6.33$) does not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4) but 
+as reported by \citet{Wu2015}, has a bright detections in the 2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
 
@@
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
     \caption{ (a) UHS J0439+1634 
-                 (b) SDSS J0100+280 
+                 (b) SDSS J0100+2802 
                (c) SDSS J1443+3623 
@@
 }
-    \label{fig:foobar}
+    \label{fig:VHzQ_W4s}
 \end{figure*}

### 2019-06-11 tex/VHzQ.tex
color_redshift/SpecType re-jig
things_still_todo

@@
 
+Figure~\ref{fig:coverage} shows the areal coverage of the ULAS, UHS,
+VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR11
+3,700 deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
+deg$^{2}$. The overlap between UHS DR1 and VHS DR6 is 28 deg. These
+four surveys together cover 33,000 deg$^{2}$.
+
   \subsubsection{Averaging matched photometry}
@@
 
-\citet{Blain2013}
-
 Recently, \citet{Assef2018} released two large catalogues of AGN
-candidates identified across 30,000 deg$^2$ of extragalactic sky 
-from the WISE AllWISE Data Release. The ``R90'' catalogue, 
-contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
-AGN candidates per deg$^2$) while the ``C75'' catalogue  
-consists of 20.9M AGN candidates at 75\% completeness (and 
-($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
-our catalogue of 463 VH$z$Qs with these catalogues, produces 
-42 matches with	the R90 sample and 98 matches with the C75 sample. 
-Both catalogues unsurprisingly match to the ultraluminous quasar 
-SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
-matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
-matches to J1342+0928 \citep{Banados2018}.
+candidates identified across 30,000 deg$^2$ of extragalactic sky from
+the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
+AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
+per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
+candidates at 75\% completeness (and ($\approx$700 AGN candidates per
+deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
+catalogues, produces 42 matches with the R90 sample and 98 matches
+with the C75 sample. Both catalogues unsurprisingly match to the
+ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
+not the R90 catalogue matches to ULAS J1120+0641
+\citep{Mortlock2011}. Neither catalogue matches to J1342+0928
+\citep{Banados2018}.
 
@@
 \subsection{MIR Colours}
-
+%% The VH$z$Q with the bluest colour in (W1 - W2) is 
+DELS J1048-0109 with (W1-W2) = 0.154. 
+%(see Figure~\ref{fig:DELS_J1048}).
 %%
 %%    (W1 - W2)    vs.  (W2 - W3) 
+%%
 %%  Call W1 ~ 3-4um annd W2   4-5um and   W3 10-16um
@@
 colour-scale). 
-W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
-W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
-W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars, 
-1
-
-%%
-The VH$z$Q with the bluest colour in (W1 - W2) is 
-DELS J1048-0109 with (W1-W2) = 0.154 
-(see Figure~\ref{fig:DELS_J1048}).
-
+% W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
+% W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
+% W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars,
+
+%%
 %\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
-Very High-$z$ Quasars Detected in WISE W3 and W4.
 
@@
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
     \caption{ (a) UHS J0439+1634 
@@
 }
-    \label{fig:foobar}
+    \label{fig:VHzQ_W4s}
 \end{figure*}
+The are a set of VH$z$Q detected in WISE W3 and W4. 51 objects are
+detected in the broad W3 filter and 10 objects are formally detected
+in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
+presented in \label{fig:VHzQ_W4s}. UHS J0439+1634
+(Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
+\citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
+luminosity is most not intrinsic, but is boosted by an intervening
+redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
+not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4)
+but as reported by \citet{Wu2015}, has a bright detections in the
+2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
 
@@
 \end{figure}
-
 \subsection{Variability}
@@
 associated colour changes. Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
-{\bf NJC: What about NIR light-curves / combined light-curves}
-
-At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.
-
+
+At least 8 original observations across at least 30 days in either WSA
+or VSA per band, calibrated flux greater than zero over the whole
+time, and the error on the average flux is 8 times lower than this.
+%%
 Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).
@@
 Longer time-series, better SNR and moreover, $(1+z)$. 
-Just selecting things that would
-%%
 Doing this independently in each band...
-%Variation
 
@@
 %%
-objiD 164 is SDSSJ1000+0234, faint; very faint. 
-SHELLQsJ0220-0432: (qso59) show this too. 
-CFHQSJ0216-0455
+
+%% 
+%% objiD 164 is SDSSJ1000+0234, faint; very faint. 
+%% SHELLQsJ0220-0432: (qso59) show this too. 
+%%
+
+%%
+%% CFHQSJ0216-0455
+%%
 
@@
 
-VHS, Area 1: 150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:
-$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
-Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
-$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.
-
-VIKING is more uniform, so I calculated the averages over the whole area:
-$Z$=22.7 mag, $Y$=21.9 mag, $J$=21.4 mag, $H$=21.2 mag, $Ks$=21.1 mag.
+In the North, we assume the UHS J-band depth of 19.6 \citep[Vega; ][]{Dye2018}. 
+In the South, one can use the report {\tt ABmagLimits} for each survey in the database, we
+can calculate the depths of the various NIR VISTA surveys.
+Fig.~\ref{fig:VHS_J_abMagLim} shows this calculated average {\tt AB
+MAGLIM} in the VHS.  As one can see, the VHS is not completely
+uniform; one area (150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:) has
+($Y$, $J$, $H$, $K_{s}$) = (21.1, 20.6, 20.3, 19.8) mag, while a
+second area (10$<$RA/deg$<$60, $-60<$Dec$<-40$) has ($Y$, $J$, $H$,
+$K_{s}$) = (??, 21.2, 20.6, 20.2) mag.  VIKING is more uniform, with
+average depths over the whole VIKING area of ($Z$, $Y$, $J$, $H$,
+$K_{s}$) = (22.7, 21.9, 21.4, 21.2, 21.1) mag.
 
@@
     Y and H are almost uniform, but the coverage is much less.}
-  \label{fig:1}
+  \label{fig:VHS_J_abMagLim}
 \end{figure}
@@
 \begin{equation}
-\rho(z, {\rm M}_{1450} \propto 10^{k (z)}
+\rho(z, {\rm M}_{1450}) \propto 10^{k (z)}
 \end{equation}
@@
 %Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
-
-UHS J-band depth 19.6 \citep[Vega; ][]{Dye2018}
-
-VISTA HEMISPHERE SURVEY DATA RELEASE 1
-Release date (will be set by ESO)
-PROPOSAL ESO No.: 179.A-2010
-PRINCIPAL INVESTIGATOR: Richard McMahon
-Authors: R. McMahon, M. Banerji, N. Lodieu for the VHS Collaboration
-
-The aim of the Vista Hemisphere Survey (VHS) is to carry out a near
-Infra-Red survey, which when combined with other VISTA Public Surveys
-will result in coverage of the whole southern celestial hemisphere
-($\sim$20,000 deg$^2$) to a depth 30 times fainter than 2MASS/DENIS in
-at least two wavebands (J and K$_s$), with an exposure time of 60 seconds
-per waveband to produce median 5σ point source (Vega) limits of $J =
-20.2$ and $K_{S} = 18.1$. In the South Galactic Cap, $\sim$5000 deg$^{2}$ will be
-imaged deeper with an exposure time of 120 seconds and also including
-the H band producing median 5$\sigma$ point limits of: J = 20.6; H = 19.8; K$_{s}$ = 18.5. 
-In this 5000 deg$^{2}$ region of sky deep multi-band optical (grizY)
-imaging data will be provided by the Dark Energy Survey (DES). The
-remainder of the high galactic latitude ($|b|>$30$^{\circ}$) sky will be imaged
-in YJHK for 60sec per band to be combined with ugriz waveband
-observations from the VST ATLAS survey. \\
-
-VHS                   YJHK            99.99, 21.2,  21.2,  20.6,  20.0                (9) \\
-
-{\tt ABmagLimits} for each survey in the database. \\
 

### 2019-06-11 tex/VHzQ.tex
tex/VHzQ.tex update; Figure 7 caption

@@
     \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
-    \caption{ (a) UHS J0439+1634 
-                 (b) SDSS J0100+2802 
-               (c) SDSS J1443+3623 
- (d) SDSS J1623+4705
-}
+    \caption{Four of the brightest MIR VH$z$Qs. 
+      The thumbnails are the RGB colour outputs using the ALLWISE W1W2W3 bands from the 
+      IRSA WISE Image Service, with a scale of 120'' on the side. 
+      {\it (a)} UHS J0439+1634 was discovered by
+      \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. 
+      {\it (b)} SDSS J0100+2802 is the \citet{Wu2015} object. 
+      {\it (c)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
+      {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).}
     \label{fig:VHzQ_W4s}

### 2019-06-11 tex/VHzQ.tex
tex/PhotometricBands_Conversions.tex update
Minor corrections to Sec3.2 text

@@
 \subsection{MIR Colours}
-%% The VH$z$Q with the bluest colour in (W1 - W2) is 
+The VH$z$Q with the bluest colour in (W1 - W2) is 
 DELS J1048-0109 with (W1-W2) = 0.154. 
 %(see Figure~\ref{fig:DELS_J1048}).
-%%
-%%    (W1 - W2)    vs.  (W2 - W3) 
-%%
-%%  Call W1 ~ 3-4um annd W2   4-5um and   W3 10-16um
+
 Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
@@
 \end{figure*}
-The are a set of VH$z$Q detected in WISE W3 and W4. 51 objects are
-detected in the broad W3 filter and 10 objects are formally detected
+The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
+detected in the broad W3 filter and 10 objects that are formally detected
 in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
@@
 \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
-luminosity is most not intrinsic, but is boosted by an intervening
+luminosity is mostly not intrinsic, but is boosted by an intervening
 redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
-not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4)
-but as reported by \citet{Wu2015}, has a bright detections in the
+not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
+but as reported by \citet{Wu2015}, has a bright detection in the
 2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.

### 2019-06-11 tex/VHzQ.tex
tex/VHzQ.tex

@@
 (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
-been observed (by VHS) but are out of our queried time range 
-(for which the data is publicly available). 6 objects have not been 
-observed (or at least the data is not in the
-WSA/VSA archives yet) and 5 objects are at a declination $\delta \geq +60$
-deg are too far north for UKIRT and cannot be observed.
+been observed (by VHS) but are out of our queried time range (for
+which the data is publicly available). 6 objects are at declination
+$\delta<0$ deg and have not been observed (or at least the data is not
+in the VSA archive yet). 5 objects are at a declination $\delta \geq
++60$ deg are too far north for UKIRT and cannot be observed.
 
   \subsubsection{Comparing WFCAM and VISTA}
-  There are 130 overlapping QSOs between WFCAM and VISTA. We used the
-  {\tt VegaToAB} values to put these objects on the same AB system, and
-  for each object compared the two measurements. First, we calculated the
-  weighted average (calibrated flux) in each filter of both and
-  calculated the ratio and difference between each measurement and the
-  average.  Then for each filter we calculated the weighted average of
-  the differences (in mag) for each instrument to see if there were
-  significant offsets. The results are given in
-  Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
-  offset is the $Y$-band. All of the VISTA averages are negative and all
-  of the WFCAM ones are positive. The $Ks$ versus $K$ band comparison may be
-  affected the different shapes of the filters, with $K$ being significantly 
-  wider than $K_s$, able to detect light at longer wavelengths.
+  There are 130 quasars observed in the overlapping area between WFCAM
+  and VISTA. We used the {\tt VegaToAB} values to put these objects on
+  the same AB system, and for each object compared the two
+  measurements. First, we calculated the weighted average (calibrated
+  flux) in each filter of both and calculated the ratio and difference
+  between each measurement and the average.  Then for each filter we
+  calculated the weighted average of the differences (in mag) for each
+  instrument to see if there were significant offsets. The results are
+  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
+  significant offset is the $Y$-band. All of the VISTA averages are
+  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
+  band comparison may be affected the different shapes of the filters,
+  with $K$ being significantly wider than $K_s$, able to detect light at
+  longer wavelengths.
   \begin{table}
@@
 \end{figure}
-Before reporting on the detection rates, we investigate this effect
-using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
-shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
-by {\tt w$x$cov} the mean coverage depth, in each corresponding
-band. In the two shorter bands W1/2 we see the clear and expected
+Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog.
+Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
+The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3 from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular area with a radius of 8.25'' centered on the position of this source.
+For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source Catalog \href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column Descriptions} has further details).
+The {\tt w$x$cov} value takes into account e.g., individual pixels in the measurement area that may be masked or otherwise unusable (reducing the effective pixel count and thus the mean coverage value) as well as pixels that are affected by distortions across the across the focal plane in single-exposure images (where this distortion is corrected when coadding to generate the Atlas Images).
+
+In the two shorter bands W1/2 we see the clear and expected
 trend for brighter objects to have larger SNR, and also for the higher
@@
     as for (W1-W2) colour.  The points are colour coded by redshift.}
-  \label{fig:WISEmag_vs_coverage}
+  \label{fig:WISEmag_vs_snr}
 \end{figure}
@@
 ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
-not the R90 catalogue matches to ULAS J1120+0641
-\citep{Mortlock2011}. Neither catalogue matches to J1342+0928
-\citep{Banados2018}.
+not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS J1120+0641
+\citep{Mortlock2011}. Neither catalogue matches to the current highest-redshift 
+object  J1342+0928 \citep{Banados2018}.
 
@@
 2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
+%%
+Other high-redshift quasars that are bright W3/4 objects may well 
+also so be lensed, but high-resolution follow-up is needed to confirm.
 

### 2019-06-11 tex/VHzQ.tex
removed WISE SNR figure 5
Section 3.4 Variability CLQ reference update

@@
 Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}.
-The AllWISE program combines the W1 and W2 Single-exposure data from all WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
+The AllWISE program combines the W1 and W2 Single-exposure data from all the WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
 The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
@@
 \end{figure}
-Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog.
-Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.
-The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3 from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular area with a radius of 8.25'' centered on the position of this source.
-For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source Catalog \href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column Descriptions} has further details).
-The {\tt w$x$cov} value takes into account e.g., individual pixels in the measurement area that may be masked or otherwise unusable (reducing the effective pixel count and thus the mean coverage value) as well as pixels that are affected by distortions across the across the focal plane in single-exposure images (where this distortion is corrected when coadding to generate the Atlas Images).
-
+Before reporting on the detection rates, we investigate this effect
+using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
+shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
+by {\tt w$x$cov} the mean coverage depth, in each corresponding
+band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
+from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
+area with a radius of 8.25'' centered on the position of this
+source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
+Catalog
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
+Descriptions} has further details). The {\tt w$x$cov} value takes into
+account e.g., individual pixels in the measurement area that may be
+masked or otherwise unusable (reducing the effective pixel count and
+thus the mean coverage value) as well as pixels that are affected by
+distortions across the across the focal plane in single-exposure
+images (where this distortion is corrected when coadding to generate
+the Atlas Images). 
 In the two shorter bands W1/2 we see the clear and expected
@@
 for future, small mirror infrared missions \citep[e.g.][]{NEOCam_WP}.
-
-\begin{figure}
-  %% trim=l b r t
-  \includegraphics[width=8.6cm, clip, trim=2mm 0mm 2mm 0mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
-  \centering
-  \vspace{-14pt}
-  \caption[]{WISE signal-to-noise measures for the four bands, as well
-    as for (W1-W2) colour.  The points are colour coded by redshift.}
-  \label{fig:WISEmag_vs_snr}
-\end{figure}
 
@@
 ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
-not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS J1120+0641
-\citep{Mortlock2011}. Neither catalogue matches to the current highest-redshift 
-object  J1342+0928 \citep{Banados2018}.
+not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS
+J1120+0641 \citep{Mortlock2011}. Neither catalogue matches to the
+current highest-redshift object J1342+0928 \citep{Banados2018}.
 
@@
 \end{figure}
-
 \subsection{MIR Colours}
@@
 
-Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
-space diagram showing the WISE colours for the 283 VH$z$Q that have
-reported w3mpro values (blue to red coloured points).  400,000 quasars
+Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs.
+(W2-W3) colour – colour space diagram showing the WISE colours for the 283 VH$z$Q that have reported {\tt w3mpro} values (blue to red coloured points), though we note that only 51(18\%) of these objects have {\tt w3snr} > 3.0.
+objects  400,000 quasars
 at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
@@
   \caption[]
-  {Histogram showing the number of NEOWISE-R epochs and detections there are for each 
-    VH$z$Q.} 
+  {Histogram showing the total number of exposures for each detected VH$z$Q
+    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
   \label{fig:MIR_LC_epochs}
@@
 spectra. We look for evidence of this variability signature in the NIR
-and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the
+and MIR light-curves of the VH$z$Qs.
+
+Quasars are known to have dramatically changing Balmer lines, especially 
+H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016,
+Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018,
+Ross2018, MacLeod2019, Graham2019}.
+As a guide, 
+What is less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
+\civ enters the
 $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the

### 2019-06-11 tex/VHzQ.tex
general update

@@
   \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
   \vspace{-16pt}
@@
 \subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington Limit, might well
-have have large values of changing mass accretion rate, $\ddot{m}_{\rm
-accr}$. A consequence of this would be that these quasars exhibit signs
-of variability, most likely showing up in their UV/optical rest-frame
-spectra. We look for evidence of this variability signature in the NIR
-and MIR light-curves of the VH$z$Qs.
-
-Quasars are known to have dramatically changing Balmer lines, especially 
-H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016,
-Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018,
-Ross2018, MacLeod2019, Graham2019}.
-As a guide, 
-What is less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
+VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m}_{\rm accr}$.
+A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra.
+We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
+
+Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018, Ross2018, MacLeod2019, Graham2019}.
+As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e.
+W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$.
+H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
+4.13$\mu$m at $z=7.50$. 
+%%
+Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
 \civ enters the
@@
 
-Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we
-
 \begin{figure}
@@
     Red points are the W1 band; cyan points the W2 band.} 
-  \label{fig::MIR_LC_3egs}
+  \label{fig:MIR_LC_3egs}
 \end{figure}
 
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
-Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and
-associated colour changes. Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
-
-At least 8 original observations across at least 30 days in either WSA
-or VSA per band, calibrated flux greater than zero over the whole
-time, and the error on the average flux is 8 times lower than this.
-%%
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes.
+Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
+
+Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 27 WFCAM and 16 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter.
+4 objects are in common to both, so this sample of 39 is our starting point for variability investigations.
+The four objects in common are: CFHQS J0216-4555; SDSS J0959+0227; SDSS J1000+0234; VIK J1148+0056.
+%% is SDSSJ0958+3524 special at all??
+
+At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.
 Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).

### 2019-06-11 tex/VHzQ.tex
tester_mnras.bib and things_still_todo update

@@
 \subsection{MIR Colours}
+%
+\citet{LaMassa2017, Glikman2018, LaMassa2019} 
+%
+
 The VH$z$Q with the bluest colour in (W1 - W2) is 
@@
 Other high-redshift quasars that are bright W3/4 objects may well 
-also so be lensed, but high-resolution follow-up is needed to confirm.
+also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, 
+but high-resolution follow-up is needed to confirm.
 
@@
 
-Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018, Ross2018, MacLeod2019, Graham2019}.
+Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}.
 As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e.

### 2019-06-11 tex/VHzQ.tex
Modifications to variability section

@@
 Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}.
-As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e.
+As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$m (i.e.
 W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$.
@@
 %%
-Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
+Less well understood is the temporal behaviour of the metal lines, in particular \civ and \mgii. 
 \civ enters the
@@
 
-Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 27 WFCAM and 16 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter.
-4 objects are in common to both, so this sample of 39 is our starting point for variability investigations.
-The four objects in common are: CFHQS J0216-4555; SDSS J0959+0227; SDSS J1000+0234; VIK J1148+0056.
+Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux.
+1 objects is in common to both, so this sample of 32 is our starting point for variability investigations.
+The common object is VIK J1148+0056.
 %% is SDSSJ0958+3524 special at all??

### 2019-06-12 tex/VHzQ.tex
update

@@
 %
-\citet{LaMassa2017, Glikman2018, LaMassa2019} 
+Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
+several investigations have looked at how WISE detects AGN 
+\citet[e.g][Secrest2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019} 
 %
@@
 The common object is VIK J1148+0056.
-%% is SDSSJ0958+3524 special at all??
 
@@
 
-Then calculate the clipped median and standard deviation, 
+The clipped median and standard deviation is then ncalculated, 
 \begin{equation}
@@
 With this definition, although some of the objects have very well sampled, 
-`average' light curves where you are averaging over e.g. a month, or two weeks.
+``average'' light curves where you are averaging over e.g. a month, or two weeks.
 

### 2019-06-12 color_redshift/redshift_vs_W1W2.py
color_redshift/redshift_vs_W1W2.py

@@ -174,6 +174,7 @@ plt.close()
 
 
 
+
 ###################################
 ##
 ##   S D S S

### 2019-06-12 tex/VHzQ.tex
color_redshift/redshift_vs_W1W2.py
tex/VHzQ.pdf

--- 2019-06-11 tex/VHzQ.tex
@@
 \subsection{MIR Colours}
-%
-\citet{LaMassa2017, Glikman2018, LaMassa2019} 
-%
+Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
+several investigations have looked at how WISE detects AGN 
+\citet[e.g][]{Secrest2015, Assef2015, Stern2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019}
 
@@
 % W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars,
-
-%%
-%\subsubsection{Individual VH$z$Qs with Interesting MIR properties}
 
@@
 
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes.
-Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
-
-Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux.
-1 objects is in common to both, so this sample of 32 is our starting point for variability investigations.
-The common object is VIK J1148+0056.
-%% is SDSSJ0958+3524 special at all??
-
-At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.
-Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).
-
-Then calculate the clipped median and standard deviation, 
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
+and detections there are for each VH$z$Q, while
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR
+lightcurves and associated colour changes. Here we show J0100+2802
+\citep{Wu2015}, J0224-4711 and J1626+2751.
+
+Using the extended datasets described in Section~\ref{sec:NIR_data}, 
+we select objects with at least 8
+measurements observed with durations over 30 days, in at least one
+filter and with the average calibrated flux is greater than 0 and at
+least $8\times$ the error on the average calibrated flux. 
+%At least 8 original observations across at least 30 days in either WSA or VSA per 
+% band, calibrated flux greater than zero over the whole time, and the
+% error on the average flux is 8 times lower than this. 
+A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
+then dependent on the averaging timescales (which as we see can vary).
+The clipped median and standard deviation is then calculated 
 \begin{equation}
@@
 \end{equation}
-where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
-%%
-With this definition, although some of the objects have very well sampled, 
-`average' light curves where you are averaging over e.g. a month, or two weeks.
-
-Longer time-series, better SNR and moreover, $(1+z)$. 
-Doing this independently in each band...
-
-%% 
-%% Object numbers: 54 VSA   MMTJ0215-0529,
-%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
-%%
-
-%% 
-%% objiD 164 is SDSSJ1000+0234, faint; very faint. 
-%% SHELLQsJ0220-0432: (qso59) show this too. 
-%%
-
-%%
-%% CFHQSJ0216-0455
-%%
-
-\begin{figure}[H]
+where $\bar{\epsilon}$ is the mean of the error in each point in the
+light curve, divided by the total number of points.
+%%
+With this definition, although some of the objects have very well sampled 
+with an ``average'' light curve sampling over e.g. a month, or two weeks. 
+%%
+With these criteria, there are 21 WFCAM and 12 VISTA objects 
+with 1 object (VIK J1148+0056 ) in common to both, and this sample of 32 is our starting point for variability investigations.
+
+We present four objects that are particularly well-sampled in the NIR; these are
+MMTJ0215-0529 (Figure~\ref{fig:MMTJ0215-0529}), 
+CFHQSJ0216-0455 (Figure~\ref{fig:CFHQSJ0216-0455}), 
+SHELLQsJ0220-0432 (Figure~\ref{fig:SHELLQsJ0220-0432}) and 
+SDSS J0959+0227 (Figure~\ref{fig:SDSS J0959+0227}). 
+We also incorporate the MIR NEOWISE-R light data where available.
+
+\begin{figure}
   \begin{subfigure}{}
@@
     \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
-    \caption{MMTJ0215-0529}
+    \caption{MMT J0215-0529}
     \label{fig:MMTJ0215-0529}
-  \end{subfigure}%
+  \end{subfigure} 
   \begin{subfigure}{}
@@
     \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
-    \caption{CFHQSJ0216-0455}
+    \caption{CFHQS J0216-0455}
     \label{fig:CFHQSJ0216-0455}
   \end{subfigure}
+\end{figure}
+
+\begin{figure}
   \begin{subfigure}{}\quad
@@
     \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{SHELLQsJ0220-0432}
+    \caption{SHELLQs J0220-0432}
     \label{fig:SHELLQsJ0220-0432}
+  \end{subfigure}
+  \begin{subfigure}{}\quad
+    \centering
+    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
+    \caption{SDSS J0959+0227}
+    \label{fig:SDSSJ0959+0227}
   \end{subfigure}
@@
 \end{figure}
+
+Longer time-series, better SNR and moreover, $(1+z)$. 
+Doing this independently in each band...
 

### 2019-06-12 tex/VHzQ.tex

@@
 
-We present four objects that are particularly well-sampled in the NIR; these are
-MMTJ0215-0529 (Figure~\ref{fig:MMTJ0215-0529}), 
-CFHQSJ0216-0455 (Figure~\ref{fig:CFHQSJ0216-0455}), 
-SHELLQsJ0220-0432 (Figure~\ref{fig:SHELLQsJ0220-0432}) and 
-SDSS J0959+0227 (Figure~\ref{fig:SDSS J0959+0227}). 
-We also incorporate the MIR NEOWISE-R light data where available.
-
-\begin{figure}
+We present four objects that are particularly well-samaple
+The light-curves, incorporating the NEOWISE-R light data where available 
+are presented in Figures~\refs fig:MMTJ0215-0529
+
+\begin{figure}[H]
   \begin{subfigure}{}
@@
     \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
-    \caption{MMT J0215-0529}
+    \caption{MMTJ0215-0529}
     \label{fig:MMTJ0215-0529}
-  \end{subfigure} 
+  \end{subfigure}%
   \begin{subfigure}{}
@@
     \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
-    \caption{CFHQS J0216-0455}
+    \caption{CFHQSJ0216-0455}
     \label{fig:CFHQSJ0216-0455}
   \end{subfigure}
-\end{figure}
-
-\begin{figure}
   \begin{subfigure}{}\quad
@@
     \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{SHELLQs J0220-0432}
+    \caption{SHELLQsJ0220-0432}
     \label{fig:SHELLQsJ0220-0432}
-  \end{subfigure}
-  \begin{subfigure}{}\quad
-    \centering
-    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{SDSS J0959+0227}
-    \label{fig:SDSSJ0959+0227}
   \end{subfigure}
@@
 Doing this independently in each band...
+
+%% 
+%% Object numbers: 54 VSA   MMTJ0215-0529,
+%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
+%%
+
+%% 
+%% objiD 164 is SDSSJ1000+0234, faint; very faint. 
+%% SHELLQsJ0220-0432: (qso59) show this too. 
+%%
+
+%%
+%% CFHQSJ0216-0455
+%%
 

### 2019-06-12 tex/VHzQ.tex
SDSSJ0959+0227LC_20190612.png now in .tex
VHzQ update

--- 2019-06-12 tex/VHzQ.tex
@@
 several investigations have looked at how WISE detects AGN 
-\citet[e.g][]{Secrest2015, Assef2015, Stern2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019}
+\citet[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
 
@@
 \subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m}_{\rm accr}$.
-A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra.
+VH$z$Qs, if accreting at, or above the Eddington limit, might well have changing mass accretion rates, $\dot{m}_{\rm accr}$.
+A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame emission.
 We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
@@
 Using the extended datasets described in Section~\ref{sec:NIR_data}, 
-we select objects with at least 8
-measurements observed with durations over 30 days, in at least one
-filter and with the average calibrated flux is greater than 0 and at
-least $8\times$ the error on the average calibrated flux. 
-%At least 8 original observations across at least 30 days in either WSA or VSA per 
-% band, calibrated flux greater than zero over the whole time, and the
-% error on the average flux is 8 times lower than this. 
+we select objects with at least 8 measurements observed with intervals of 
+at least 30 days, in at least one filter. 
+The signal-to-noise on the average calibrated flux is required to be $\geq8$. 
+%(i.e. {\tt aperJky3}$>0$. 
+%%(i.e. the average calibrated flux over all epochs must be >0) 
+%and 
+%{\tt aperJky3/aperJky3Err}$>=$8)
+%%
 A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
-then dependent on the averaging timescales (which as we see can vary).
+dependent on the averaging timescales is also required.
 The clipped median and standard deviation is then calculated 
 \begin{equation}
-     1.48 \times \sigma_{median} / \bar{\epsilon}
+      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
 \end{equation}
-where $\bar{\epsilon}$ is the mean of the error in each point in the
+where $var$ is the index of variation, 
+m.a.d. is the median absolute deivation, 
+and $\bar{\epsilon}$ is the mean of the error in each point in the
 light curve, divided by the total number of points.
-%%
-With this definition, although some of the objects have very well sampled 
-with an ``average'' light curve sampling over e.g. a month, or two weeks. 
 %%
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
+    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
     \caption{SDSS J0959+0227}

### 2019-06-12 tex/VHzQ.tex
VHzQ update

@@
 \subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington limit, might well have changing mass accretion rates, $\dot{m}_{\rm accr}$.
-A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame emission.
-We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.
-
-Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018, Ross2018, MacLeod2019, Graham2019}.
-As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$m (i.e.
-W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$.
-H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
-4.13$\mu$m at $z=7.50$. 
-%%
-Less well understood is the temporal behaviour of the metal lines, in particular \civ and \mgii. 
-\civ enters the
-$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
-$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
-$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
-$K$-band at redshift $z=6.25$ and exits at $7.50$.
+VH$z$Qs, if accreting at, or above the Eddington limit, might well
+have changing mass accretion rates, i.e., $\ddot{m}_{\rm accr}$. A
+consequence of this would be that these quasars exhibit signs of
+variability, most likely showing up in their UV/optical rest-frame
+emission. We look for evidence of this variability signature in the
+NIR and MIR light-curves of the VH$z$Qs.
+
+Quasars are known to have dramatically changing Balmer lines,
+especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016,
+Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018,
+Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$
+is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m,
+which is between the W2 and W3-bands at $z=7.50$.  H$\beta$ is
+redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$
+and 4.13$\mu$m at $z=7.50$. Less well understood is the temporal
+behaviour of the metal lines, in particular \civ and \mgii.  \civ
+enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
+enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
+enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
+enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
 
@@
 \end{figure}
-
 Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
@@
 at least 30 days, in at least one filter. 
-The signal-to-noise on the average calibrated flux is required to be $\geq8$. 
-%(i.e. {\tt aperJky3}$>0$. 
-%%(i.e. the average calibrated flux over all epochs must be >0) 
-%and 
-%{\tt aperJky3/aperJky3Err}$>=$8)
-%%
-A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
-dependent on the averaging timescales is also required.
+The the average calibrated flux over all epochs must be $>0$ 
+(i.e. {\tt aperJky3}$>0$) 
+with the signal-to-noise is required to be $\geq8$. 
+(i.e. {\tt aperJky3/aperJky3Err}$>=$8).
 The clipped median and standard deviation is then calculated 
@@
 \end{equation}
-where $var$ is the index of variation, 
-m.a.d. is the median absolute deivation, 
-and $\bar{\epsilon}$ is the mean of the error in each point in the
-light curve, divided by the total number of points.
-%%
-With these criteria, there are 21 WFCAM and 12 VISTA objects 
-with 1 object (VIK J1148+0056 ) in common to both, and this sample of 32 is our starting point for variability investigations.
-
-We present four objects that are particularly well-sampled in the NIR; these are
+where $var$ is the index of variation, m.a.d. is the median absolute
+deivation, and $\bar{\epsilon}$ is the mean of the error in each point
+in the light curve, divided by the total number of points.  With these
+criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
+J1148+0056) in common to both, and this sample of 32 is our starting
+point for variability investigations.
+
+We present four objects that are particularly well-sampled in the NIR. 
+These are: 
 MMTJ0215-0529 (Figure~\ref{fig:MMTJ0215-0529}), 
@@
 SHELLQsJ0220-0432 (Figure~\ref{fig:SHELLQsJ0220-0432}) and 
-SDSS J0959+0227 (Figure~\ref{fig:SDSS J0959+0227}). 
-We also incorporate the MIR NEOWISE-R light data where available.
+SDSS J0959+0227 (Figure~\ref{fig:SDSSJ0959+0227}). 
+We incorporate the MIR NEOWISE-R light curve data where available.
 
@@
     \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
-    \caption{MMT J0215-0529}
+    \caption{The infrared light curve for MMT J0215-0529 (}
     \label{fig:MMTJ0215-0529}
@@
 
-Longer time-series, better SNR and moreover, $(1+z)$. 
+Even with well sampled data across the 3000-4000 day observed time-scales that the WFCAM and VISTA surveys span, the $(1+z)$ time-dilation dramatically affects the sampled rest-frame timescales sampled.
+
+SDSS J0959+0227 is in the VH$z$Q sample from \citet{Wang2016} 
+%% Wang et al. 2016, ApJ, 819, 24, and their Table1. 
+but is first reported in \citet{Civano2011} as CID-2220 (CXOCJ095908.1+022707), 
+%2011, ApJ, 741, 91 
+a high-redshift, $z>3$ AGN in the Chandra-COSMOS field. 
+%%
+The spectrum from this object is presented in \citet{Ikeda2012} 
+% et al., 2012, ApJ, 756, 160, 
+and is called object ``No. 11'' in that papers' Table 1. 
+and it is a beauty!! Figure 2 with the spectrum is attached. 
+\citet{Ikeda2012} show SDSS J0959+0227 having a narrow Ly$\alpha$ line, 
+and would likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray source, 
+The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10 keV rest-frame, 
+so it is an AGN. This object is clearly not a regular broadline ``Type 1'' AGN, but  
+if there is even the slightest of variability, this could potentially be a high-$z$ 
+AGN transitioning from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
+
 Doing this independently in each band...

### 2019-06-12 light_curves/older_py/lightcurve_plot_20190612.py

@@ -1,0 +1,233 @@
+'''
+Why doesn't matplotlib look as good as SM??!!!
+http://space.mit.edu/home/turnerm/python.html
+'''
+import math
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+
+from astropy.io import ascii
+from matplotlib import colors as mcolors
+from matplotlib.font_manager import FontProperties
+
+
+## Setting up the path for the input data
+
+path = os.path.join(os.path.dirname(os.getcwd()),'data/light_curves/individual_objects')
+
+choice = '1'
+## Ordered by qsoID number. 
+print()
+print('  1)   MMTJ0215-0529      (qsoID  54)')
+print('  2)   CFHQSJ0216-045     (qsoID  56; faint)')
+print('  3)   SHELLQsJ0220-0432  (qsoID  59; faint)') 
+print('  4)   SDSSJ0836+0054     (qsoID 121)')
+print('  5)   SDSSJ0959+0227     (qsoID 162; faint)')
+print('  6)   SDSSJ1000+0234     (qsoID 164; faint)')
+print('  7)   SHELLQsJ1146+0124  (qsoID 206)')
+print('  8)   VIKJ1148+0056      (qsoID 214)')
+print('  9)   SDSSJ2216+0013     (qsoID 337)')
+print()
+choice = input('Which object? ')
+
+inputQuasar = None
+if choice == '1' : inputQuasar = 'MMTJ0215-0529'
+if choice == '2' : inputQuasar = 'CFHQSJ0216-0455'
+if choice == '3' : inputQuasar = 'SHELLQsJ0220-0432'
+if choice == '4' : inputQuasar = 'SDSSJ0836+0054'
+if choice == '5' : inputQuasar = 'SDSSJ0959+0227'
+if choice == '6' : inputQuasar = 'SDSSJ1000+0234'
+if choice == '7' : inputQuasar = 'SHELLQsJ1146+0124'
+if choice == '8' : inputQuasar = 'VIKJ1148+0056'
+if choice == '9' : inputQuasar = 'SDSSJ2216+0013'
+    
+
+print
+print(" Plotting W/VSA light curve for ", inputQuasar)
+print
+
+##
+##  P h o t o m e t r y    d a t a
+##
[…]

### 2019-06-12 tex/VHzQ.tex
tex/VHzQ update; light_curves/lightcurve_plot.py udpate

@@
 Using the extended datasets described in Section~\ref{sec:NIR_data},
-we select objects with at least 8 measurements observed with intervals of 
-at least 30 days, in at least one filter. 
-The the average calibrated flux over all epochs must be $>0$ 
-(i.e. {\tt aperJky3}$>0$) 
-with the signal-to-noise is required to be $\geq8$. 
-(i.e. {\tt aperJky3/aperJky3Err}$>=$8).
-The clipped median and standard deviation is then calculated 
+we select objects with at least 8 measurements observed with intervals
+of at least 30 days, in at least one filter. The the average
+calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
+with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
+aperJky3/aperJky3Err}$\geq$8). The clipped median and standard
+deviation is then calculated
 \begin{equation}
@@
 These are: 
-MMTJ0215-0529 (Figure~\ref{fig:MMTJ0215-0529}), 
-CFHQSJ0216-0455 (Figure~\ref{fig:CFHQSJ0216-0455}), 
-SHELLQsJ0220-0432 (Figure~\ref{fig:SHELLQsJ0220-0432}) and 
-SDSS J0959+0227 (Figure~\ref{fig:SDSSJ0959+0227}). 
+MMT J0215-0529       ($z=5.13$; Figure~\ref{fig:MMTJ0215-0529}), 
+CFHQS J0216-0455    ($z=6.01$; Figure~\ref{fig:CFHQSJ0216-0455}), 
+SHELLQs J0220-0432 ($z=5.90$; Figure~\ref{fig:SHELLQsJ0220-0432}) 
+and 
+SDSS J0959+0227 ($z=5.07$; Figure~\ref{fig:SDSSJ0959+0227}). 
 We incorporate the MIR NEOWISE-R light curve data where available.
@@
     \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
-    \caption{The infrared light curve for MMT J0215-0529 (}
+    \caption{The infrared light curve for MMT J0215-0529 with data from 
+      WFCAM (smaller solid cirlces), VIRCAM (hexagons) and NEOWISE-R (larger solid cirlces).}
     \label{fig:MMTJ0215-0529}
@@
     \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
-    \caption{CFHQS J0216-0455}
+    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
     \label{fig:CFHQSJ0216-0455}
@@
     \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{SHELLQs J0220-0432}
+    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
     \label{fig:SHELLQsJ0220-0432}
@@
     \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
-    \caption{SDSS J0959+0227}
+    \caption{The near infrared light curve for SDSS J0959+0227. Note, 
+      SDSS J0959+0227 is too faint in the MIR to be detected by ALLWISE or unnWISE.}
     \label{fig:SDSSJ0959+0227}
@@
 
-Even with well sampled data across the 3000-4000 day observed time-scales that the WFCAM and VISTA surveys span, the $(1+z)$ time-dilation dramatically affects the sampled rest-frame timescales sampled.
-
-SDSS J0959+0227 is in the VH$z$Q sample from \citet{Wang2016} 
-%% Wang et al. 2016, ApJ, 819, 24, and their Table1. 
-but is first reported in \citet{Civano2011} as CID-2220 (CXOCJ095908.1+022707), 
-%2011, ApJ, 741, 91 
-a high-redshift, $z>3$ AGN in the Chandra-COSMOS field. 
-%%
-The spectrum from this object is presented in \citet{Ikeda2012} 
-% et al., 2012, ApJ, 756, 160, 
-and is called object ``No. 11'' in that papers' Table 1. 
-and it is a beauty!! Figure 2 with the spectrum is attached. 
-\citet{Ikeda2012} show SDSS J0959+0227 having a narrow Ly$\alpha$ line, 
-and would likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray source, 
-The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10 keV rest-frame, 
-so it is an AGN. This object is clearly not a regular broadline ``Type 1'' AGN, but  
-if there is even the slightest of variability, this could potentially be a high-$z$ 
-AGN transitioning from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
-
-Doing this independently in each band...
+Even with well sampled data across the 3000-4000 day observed
+time-scales that the WFCAM and VISTA surveys span, the $(1+z)$
+time-dilation dramatically affects the sampled rest-frame timescales
+sampled. Indeed, when sharp changes in a accretion rate are expected
+on the system's dynamical timescale of several kiloyears
+\citep[e.g.,][]{Regan2019}, then seeing any variability signature is
+not expected. However, noting how in lower redshift quasars, which
+also have massive $>10^{8}$ M$_{\odot}$ black holes, dramatic changes
+in both continuum and line emission {\it is seen} on much shorter
+timescales, continued monitoring of these objects is warrented.
+
+We finally focus on SDSS J0959+0227 which is in the VH$z$Q sample from
+\citet{WangF2016} but is first reported in \citet{Civano2011} as
+CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
+field. The spectrum from this object is presented in \citet{Ikeda2012}
+and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
+likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
+source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
+keV rest-frame, so it is an AGN. This object is clearly not a regular
+broadline ``Type 1'' AGN, but if with the slightest hint of
+variability, this could potentially be a high-$z$ AGN transitioning
+from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
 

### 2019-06-12 light_curves/lightcurve_plot.py

@@ -14,7 +14,7 @@ from matplotlib.font_manager import FontProperties
 
 ## Setting up the path for the input data
 
-path = os.path.join(os.path.dirname(os.getcwd()),'data/light_curves/individual_objects')
+path = os.path.join(os.path.dirname(os.getcwd()),'data/light_curves/individual_objects/')
 
 choice = '1'
 ## Ordered by qsoID number. 
@@ -62,8 +62,8 @@ VSA_data_all = ascii.read(os.path.join(path,inputQuasar,'VSA_lc_all.dat'))
 VSA_data_30d = ascii.read(os.path.join(path,inputQuasar,'VSA_lc_30d.dat'))
 
 ## NEOWISE-R
-#if choice != '7':
-NEOWISER =  ascii.read(os.path.join(path,inputQuasar,'NEOWISER-R_SingleExp_L1b.dat'))
+if (choice != '7' and choice !='5'):
+    NEOWISER =  ascii.read(os.path.join(path,inputQuasar,'NEOWISER-R_SingleExp_L1b.dat'))
 #WISE_W1 = ascii.read(path+'WISE_W1_LC.dat')
 #WISE_W2 = ascii.read(path+'WISE_W2_LC.dat')
 #WISE_L1bs = ascii.read(path+'J110057_l1b.tbl')
@@ -96,8 +96,9 @@ H_VIRCAM_30d  = VSA_data_30d[(VSA_data_30d['filterID'] == 4) & (VSA_data_30d['ap
 Ks_VIRCAM_30d = VSA_data_30d[(VSA_data_30d['filterID'] == 5) & (VSA_data_30d['aperMag3Ab']>0)]
 
 ## For WISE, we adopt 2.699 and 3.339 as the conversions to AB from W1 and W2 Vega magnitudes,
-WISE_W1_AB = NEOWISER['w1mpro'] + 2.699
-WISE_W2_AB = NEOWISER['w2mpro'] + 3.339
+if choice != '7' & choice !='5':
+    WISE_W1_AB = NEOWISER['w1mpro'] + 2.699
+    WISE_W2_AB = NEOWISER['w2mpro'] + 3.339
 
 
 
@@ -172,7 +173,7 @@ ax.errorbar(Ks_VIRCAM_30d['mjd'], Ks_VIRCAM_30d['aperMag3Ab'],  yerr=Ks_VIRCAM_3
[…]

### 2019-06-12 tex/VHzQ.tex
tex/VHzQ Section 4 update

@@
 
-We finally focus on SDSS J0959+0227 which is in the VH$z$Q sample from
+We finally focus on SDSS J0959+0227 which is presented in
 \citet{WangF2016} but is first reported in \citet{Civano2011} as
@@
 keV rest-frame, so it is an AGN. This object is clearly not a regular
-broadline ``Type 1'' AGN, but if with the slightest hint of
-variability, this could potentially be a high-$z$ AGN transitioning
-from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
+broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
+SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
+rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
+rest-frame UV/very blue, so, so the regular blue QSO continuum could
+be emerging Thus, with the slightest hint of variability, this could
+potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
+2'' object to a broadline Type 1 quasar.
 
@@
 
-In the North, we assume the UHS J-band depth of 19.6 \citep[Vega; ][]{Dye2018}. 
-In the South, one can use the report {\tt ABmagLimits} for each survey in the database, we
-can calculate the depths of the various NIR VISTA surveys.
-Fig.~\ref{fig:VHS_J_abMagLim} shows this calculated average {\tt AB
-MAGLIM} in the VHS.  As one can see, the VHS is not completely
-uniform; one area (150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:) has
-($Y$, $J$, $H$, $K_{s}$) = (21.1, 20.6, 20.3, 19.8) mag, while a
-second area (10$<$RA/deg$<$60, $-60<$Dec$<-40$) has ($Y$, $J$, $H$,
-$K_{s}$) = (??, 21.2, 20.6, 20.2) mag.  VIKING is more uniform, with
-average depths over the whole VIKING area of ($Z$, $Y$, $J$, $H$,
-$K_{s}$) = (22.7, 21.9, 21.4, 21.2, 21.1) mag.
+In the North, we assume the UHS J-band depth of 19.6 \citep[Vega;
+][]{Dye2018}.  In the South, one can use the report {\tt ABmagLimits}
+for each survey in the database, we can calculate the depths of the
+various NIR VISTA surveys.  Fig.~\ref{fig:VHS_J_abMagLim} shows this
+calculated average {\tt AB MAGLIM} in the VHS.  As one can see, the
+VHS is not completely uniform. The area wrapping round
+310$\lesssim$RA/deg$\lesssim$90 and -70$\lesssim$ Decl./ deg
+$\lesssim$ -40 has a $J$-band depth of 21.2 AB mag, whereas the rest
+of the VHS area, the $J$-band depth is closer to 20.6 AB mag.
 

### 2019-06-12 tex/VHzQ.tex
Minor corrections to Section 4 text

@@
 with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
-aperJky3/aperJky3Err}$\geq$8). The clipped median and standard
+aperJky3/aperJky3Err}$\geq$8). The clipped median and median absolute
 deviation is then calculated
@@
 likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
-source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
+source, The X-ray luminosity is $\approx3\times10^44$ erg s$-1$ in the 2–10
 keV rest-frame, so it is an AGN. This object is clearly not a regular

### 2019-06-12 tex/VHzQ.tex
got rid of \blindtext lorem ipsumgist

@@
 
-Here we present for the first time the combined near-infrared
-properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
-all the spectroscopically known $z\geq5.00$ quasars. Our motivations
-are numerous and include: {\it (i)} establishing the first complete
-catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
-{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
-available for the quasars; {\it (iii)} making the first study of near-
-and mid-IR variability of the VHzQ population and {\it (iv)}
-establishing the photometric properties for upcoming surveys and
-telescopes including the Large Synoptic Survey Telescope
-(LSST)\blindtext\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};}
-and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
-We
-chose redshift $z=5.00$ as our lower redshift limit due to a
-combination of garnishing a large sample, adequately spanning physical
-properties (e.g. luminosity, age of the Universe) and to highlight the
-parts of $L-z$ parameter space where $z>5$ quasars still wait to be
-discovered.
+Here we present for the first time the combined near-infrared properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
+all the spectroscopically known $z\geq5.00$ quasars. Our motivations are numerous and include: {\it (i)} establishing the first complete
+catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
+available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
+We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
+luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
 
@@
 likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
-source, The X-ray luminosity is $\approx3\times10^44$ erg s$-1$ in the 2–10
-keV rest-frame, so it is an AGN. This object is clearly not a regular
-broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
-SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
-rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
-rest-frame UV/very blue, so, so the regular blue QSO continuum could
-be emerging Thus, with the slightest hint of variability, this could
-potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
-2'' object to a broadline Type 1 quasar.
+source, The X-ray luminosity is $\approx$3$\times10^{44}$ erg s$^{-1}$
+in the 2-10 keV rest-frame, so it is an AGN. This object is clearly
+not a regular broadline ``Type 1'' AGN. Noting that the redshift of
+$z=5.07$ for SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands
+correspond to rest-wavelengths of $\sim$1690, 2055, 2690,
+3515/3625\AA\ i.e. the rest-frame UV/very blue, so, so the regular
+blue QSO continuum could be emerging Thus, with the slightest hint of
+variability, this could potentially be a high-$z$ AGN transitioning
+from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
 

### 2019-06-12 tex/SurfaceDensity.tex
got rid of \blindtext lorem ipsumgist

--- 2019-06-12 tex/VHzQ.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                           
-%%    The `compilation' paper for all z>5 spec-z quasars, here called
-%%    "Very High Redshift Quasars" (VHzQs) and looking into their IR
-%%    properties. Motivations include putting a list of all the VHzQ in one
-%%    place, looking for signs of super-critical accretion and having a
-%%    super-set of objects and their given parameters ahead of JWST GO Cycle 1.
-%%									    
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[usenatbib]{mnras}
-
-\input {format}
-
-\begin{document}
-
-\title[Very high-$z$ Quasars]
-        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
-\author[Ross \& Cross]
-       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
-\\ 
-$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
-}
-
-\maketitle
-\begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high
-($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$
-and $K$) infrared and mid-infrared (WISE) properties.  Using archival
-WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
-in the near-infrared that might be expected from super-Eddington
-accretion and find {\it blah}.  Extrapolating the known quasar
-luminosity function we suggest that $x$\% of the possibly detected
-$z\geq5$ quasars in the current datasets have been discovered.  All
-the data, analysis codes and plots used and generated here can be
-found at: \href{https://github.com/d80b2t/VHzQ}{\tt
-github.com/d80b2t/VHzQ}.
-\end{abstract}
-
-\begin{keywords}
-Astronomical data bases: surveys -- 
-Quasars: general -- 
-galaxies: evolution -- 
-galaxies: infrared.
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%  S E C T I O  N   1         S E C T I O  N   1           S E C T I O  N   1       S E C T I O  N   1
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Very high redshift quasars (VH$z$Q; defined here to have redshifts
-$z\geq5.00$) are excellent probes of the early Universe. This includes
-studies of the Epoch of Reionization for hydrogen \citep[see e.g.][for
-reviews]{Fan2006review, Mortlock2016}, the formation and build-up of
-supermassive black holes \citep[e.g., ][]{Rees1984, WyitheLoeb2003,
-Volonteri2010, Agarwal2016, Valiante2018, Latif2018, Wise2019} and
-early metal enrichment \citep[see e.g., ][]{Simcoe2012, Chen2017,
-Bosman2017}.
-
-Super-critical accretion, where $\dot{M} > \dot{M}_{\rm Edd}$, is a
-viable mechanism to explain the high, potentially super-Eddington,
-luminosity and rapid growth of supermassive black holes in the early
-universe \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
-one could expect VH$z$Qs to potentially vary in luminosity as they go
-through phases of super-critical accretion. These signatures of
-photometric variability should be looked for, noting the rest-frame
-optical emission is redshifted into the observed near-infrared (NIR)
-at redshifts $z>5$. Fortunately, data are now in place from deep,
-wide-field NIR instruments and surveys such as the Wide Field Camera
-(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
-in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
-the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
-Southern Hemisphere, that are necessary for identifying VH$z$Qs.
-
-Quasars are known to be prodigious emitters of infrared emission,
-thought to be from the thermal emission of dust grains heated by
-continuum emission from the accretion disc
-\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014,
-Hickox2017}. Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
-allow discrimination between AGN\footnote{Historically, ``quasars''
-and ``Active Galactic Nuclei (AGN)'' have described different
-luminosity/classes of objects. In recognition of the fact that both
-terms describe accreting supermassive black holes, we use these terms
-interchangeably, with a preference for quasar, since we are generally
-in the higher-$L$ regime \citep[e.g.][]{Haardt2016book}.}  and passive
-galaxies due to the 1.6$\mu$m ``bump'' entering the MIR at
-$z\approx0.8-0.9$ \citep[e.g., ][]{Wright1994, Sawicki2002, Lacy2004,
-Stern2005, Richards2006b, Timlin2016} as well as between AGN and
-star-forming galaxies due to the presence of Polycyclic Aromatic
-Hydrocarbon (PAHs) at $\lambda >3\mu$m \citep[e.g., ][]{Yan2007,
-Tielens2008}.
-
-\citet{Jiang2006dust} and \citet{Jiang2010} report on the discovery of
-a quasar without hot-dust emission in a sample of 21 $z\approx6$
-quasars. Such apparently hot-dust-free quasars have no counterparts at
-low redshift. Moreover, those authors demonstrate that the hot-dust
-abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole. But understanding how dust first forms and appears
-in the central engine remains an open question \citep{WangR2008,
-WangR2011}.
-
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue
-release, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}},
-of which over 4.5M AGN candidates have been identified with 90\%
-reliability \citep{Assef2018}.  \citet{Blain2013} presented WISE
-mid-infrared (MIR) detections of 17 (55\%) of the then known 31
-quasars at $z > 6$. However, \citet{Blain2013} was compiled with the
-WISE `All-Sky' data release, as opposed to the superior AllWISE
-catalogues. That sample only examined the 31 known $z>6$ quasars; our
-sample has 170 objects with redshift $z \geq 6.00$ (with 108 detected
-in WISE). \citet{Banados2016} reports WISE W1, W2, W3 and W4
-magnitudes for the Panoramic Survey Telescope and Rapid Response
-System 1 \citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with
-no further investigation into the reddest WISE waveband for the
-VH$z$Qs.
-
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
-This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
-
-Here we present for the first time the combined near-infrared
-properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
-all the spectroscopically known $z\geq5.00$ quasars. Our motivations
-are numerous and include: {\it (i)} establishing the first complete
-catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
-{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
-available for the quasars; {\it (iii)} making the first study of near-
-and mid-IR variability of the VHzQ population and {\it (iv)}
-establishing the photometric properties for upcoming surveys and
-telescopes including the Large Synoptic Survey Telescope
-(LSST)\blindtext\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};}
-and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
-We
-chose redshift $z=5.00$ as our lower redshift limit due to a
-combination of garnishing a large sample, adequately spanning physical
-properties (e.g. luminosity, age of the Universe) and to highlight the
-parts of $L-z$ parameter space where $z>5$ quasars still wait to be
-discovered.
-
-This paper is organized as follows. In Section 2, we present the
-assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
-compiled. We then give a high-level overview of the photometric
-surveys and datasets we use and present the photometry of the
-VH$z$Qs. In Section 3 we investigate the variability properties of the
-VH$z$Qs, looking for evidence of super-critical accretion. In Section
-4 we calculate how many $z>5$ quasars we should expect to find in
-current datasets. We conclude in Section 5 and present all the
-necessary details to obtain our dataset in the Appendices.
-
-We present all our photometry and magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
-near-infrared, as well as the mid-infrared magnitudes. These
-magnitudes are {\it not} Galactic extinction corrected. We use a flat
-$\Lambda$CDM cosmology with $H_{\rm 0} = 67.7$ km s$^{-1}$ Mpc$^{-1}$,
-$\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$
-\citet{Planck2016} to be consistent with \citet{Banados2016} and all
-logarithms are to the base 10.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  %% trim=l b r t
-  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
-  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
-  \centering
-  \vspace{-12pt}
-  \caption[]
-  {The spectral bands used in this paper. 
-    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
-    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
-    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration. 
-    The quasar spectrum is a composite based on \citet{VdB2001} and 
-    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
-  \label{fig:filters}
-\end{figure}
-
-\vspace{-16pt}
-\section{Method and Data}
-Quasars are generally identified by photometric selection followed by
-spectroscopic confirmation. Here, we reverse this method obtaining
-first a list of spectroscopic quasars and then obtain photometric
-information.
-
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
-use all the $z\geq5.00$ quasars that have been discovered,
-spectroscopically confirmed and published as of 2018 December 31 (MJD
-58483). We then obtain optical, near-infrared and mid-infrared
-photometry for the spectral dataset. The near-infrared data comes from
-two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
-primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
-Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
-VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
-mid-infrared, $\lambda=3-30\mu$m wavelength data is from the 
-Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
-Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
-the wavelength and normalised transmission of the filters in question.
-
-\subsection{Spectroscopy} 
-We compile the list of all known, spectroscopically confirmed
-quasars from the literature.  This list was complied from a range of
-surveys and papers.  Specifically, we use data from:
-\citet{Banados2014, Banados2016, Banados2018}, 
-\citet{Becker2015}, 
-\citet{Calura2014}, 
-\citet{Carilli2007, Carilli2010}, 
-\citet{Carnall2015}, 
-\citet{Cool2006}, 
-\citet{DeRosa2011}, 
-\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
-\citet{Goto2006}, 
-\citet{Ikeda2017}, 
-\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
-\citet{Kashikawa2015}, 
-\citet{Koptelova2017}, 
-\citet{Kim2015, Kim2018},  
-\citet{Kurk2007, Kurk2009}, 
-\citet{Leipski2014}, 
-\citet{Mahabal2005}, 
-\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
-\citet{Mazzucchelli2017}, 
-\citet{Morganson2012}, 
-\citet{Mortlock2009, Mortlock2011},
-\citet{McGreer2006, McGreer2013},  
-\citet{Reed2015, Reed2017}, 
-\citet{Stern2007},  
-\citet{Tang2017}, 
-\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
-\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
-\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
-\citet{Wu2015} 
-\citet{YangJ2018a, YangJ2018b}  
-and 
-\citet{Zeimann2011}.
-
-Most of these objects are easily identified by their broad Ly$\alpha$
-emission line, \nv emission and characteristic shape blueward of
-1215\AA\ in the rest-frame. As we shall see, some of the recently
-discovered objects are close to the galaxy luminosity function
-characteristic luminosity $M^{*}$, and some have relatively weak or
-maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures 7 and 10
-in][]{Banados2016}. We leave aside detailed investigation and
-discussion into spectral features and line strengths, and take as
-given the published spectra and redshift identifications.
-
-The breakdown of how many VH$z$Q each survey reports is given in
-Table~\ref{tab:surveys}. The Sloan Digital Sky Survey (SDSS) and the
-Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone
-identified over half (54.6\%) of the VH$z$Q population. Data from the
-Hyper Suprime-Cam (HSC) on the Subaru telescope is responsible for
-13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
-combination of surveys is also vital for identifying VH$z$Qs. The
-UKIDSS Large Area Survey (ULAS) on its own, or in combination with
-other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
-including the highest-$z$ object. Where more than one survey is used
-for the high-redshift identification (e.g. via shorter-band veto and
-longer wavelength detection) we follow the discovery paper naming
-convention.
-
-\begin{table}
-\begin{tabular}{l r r l}
-\hline  \hline
-Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
-\hline  
-  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
-  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
-  DELS$^{a}$       &   16    &   ( 3.46)    &  \citet{Dey2018} \\
-  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
-  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
-  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
-  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
-  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
-  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
-  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
-  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
-  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
- SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
-%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
-  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
-  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
-  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
-  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
-  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
-  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
-  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
-  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
-\hline  \hline
-\end{tabular}
-\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
-  Recent survey name and acronyms include: 
-  $^{a}$DESI Legacy Imaging Survey; 
-  $^{b}$SDWISE = SDSS+WISE; 
-  $^{c}$SUV  = SDSS-ULAS/VHS; 
-  $^{d}$VDES = VHS/VIKING+DES; 
-%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
-}
-      \label{tab:surveys}
-\end{table}
-
-\begin{figure}
-%%trim=l b r t
-  \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Nofz/Nofz_0pnt075bins_20181211.png}
-  \centering
-  \vspace{-12pt}
-  \caption[]
-  {The redshift distribution $N(z)$ of the VH$z$Q sample. 
-    The bins are $\delta z=0.075$ in width and have the data 
-    stacked on top of each other.}
-  \label{fig:Nofz}
-\end{figure}
-
-The redshifts for the VH$z$Qs generally come from the measurement of
-broad UV/optical emission lines. There are far infra-red emission
-lines e.g. \cii 158 $\mu$m available for several objects, but at the
-level of our current analysis broadline redshifts are sufficient.
-
-\begin{table}
-\centering
-\begin{tabular}{l r  r}
-\hline \hline
-$z \geq$  & Age / Myr & No. of objects \\
-\hline 
-5.00         & 1180          &  463   \\
-5.70         & 1000          &  267   \\
-6.00         &   937          &  170   \\
-6.19         &   900          &  86   \\
-6.50         &    845         &  40   \\
-6.78         &    800         &  14   \\
-7.00         &    767         &   4   \\
-7.50         &    700         &   1   \\
-\hline \hline
-\end{tabular}
-\caption{The number of objects at or above a given redshift. 
-The age of the Universe in Megayears is also given. }
-      \label{tab:ages}
-\end{table}
-
-The number of objects at or above various redshifts, along with the 
-corresponding age of the Universe is given in Table~\ref{tab:ages}.
-
-The $N(z)$ redshift histogram is given for the sample in Figure~\ref{fig:Nofz}. 
-We split the contribution up by survey. For clarity we show the individual 
-surveys of SDSS, PS1, HSC, the ULAS detection, and tally the remaining 
-surveys together (``various'').
-
-\begin{figure}
-%%trim=l b r t
-  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
-  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
-  \centering
-  \caption[]
-  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
-  \label{fig:coverage}
-\end{figure}
-
-\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
-The near-infrared data in this paper comes from the Wide Field
-Astronomy Unit's \href{https://www.roe.ac.uk/ifa/wfau/}{(WFAU)}
-Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
-\citep[WSA; ][]{Hambly2008} and VISTA-VIRCAM, the VISTA Science
-Archive \citep[VSA; ][]{Cross2012}. These archives were developed for
-the VISTA Data Flow System \citep[VDFS][]{VDFS}.
-
-We access both the WSA and the VSA and include all non-proprietary
-WFCAM data, which covers all public surveys and PI projects from
-Semester 05A (2005-05-01) to 2017-Jan-01, and all non-proprietary VISTA data, which
-covers all public surveys and PI projects from science verification on
-2009-Oct-15 to 2017-Jan-01.
-
-Here we are not just querying the WSA or VSA data tables. We are
-taking a list of objects (positions) are performing matched aperture
-(``forced'') photometry on the NIR imaging data. As such, we generate
-a set of tables that are different in subtle ways to the regular
-``Detection'' tables.  The two most important tables for our needs are
-the {\tt [w/v]serv1000MapRemeasurement} and {\tt
-[w/v]serv1000MapRemeasAver}.
-
-We produce and provide a two new databases with all the necessary
-quantities and measurements to fully reproduce our tables, figures and
-results herein. Moreover, these databases report considerably more
-information than we report here. Full documentation can be found at
-the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema
-Browser} and the
-\href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema
-Browser}.
-
-Figure~\ref{fig:coverage} shows the areal coverage of the ULAS, UHS,
-VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR11
-3,700 deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
-deg$^{2}$. The overlap between UHS DR1 and VHS DR6 is 28 deg. These
-four surveys together cover 33,000 deg$^{2}$.
-
-  \subsubsection{Averaging matched photometry}
-  The data was processed using a matched-aperture photometry method
-  where flux is measured at the spectroscopic position of the quasar,
-  without necessarily knowing if there is a formal detection in the NIR
-  photometry beforehand. The matched-aperture pipeline is discussed in
-  \citet{Cross2013} and with fuller details to appear in a forthcoming
-  paper (Cross et al., 2019, in prep).
-
-  We query the WSA and VSA performing matched-aperture photometry at
-  the positions of our 463 VH$z$Qs. This database is world-readable and
-  we give the full recipe and relevant SQL queries for accessing both
-  databases in Appendix~\ref{sec:SQL} as well as online.
-
-  The photometry in a single epoch image often has low
-  signal-to-noise.  The advantage of matched aperture photometry on
-  quasars is that co-adding is relatively simple if each epoch is taken
-  in the same aperture and the aperture photometry has been corrected to
-  total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperture photometry can give better results for the photometry, 
-  where the individual epochs are taken from multiple projects with different field-centres and orientations and point-spread functions since the individual epoch scattered light, pixel distortion and aperture corrections can be applied with the correct weighting.
-
-  We average the aperture corrected calibrated fluxes (e.g. {\bf
-  aperJky3}), and then convert to magnitudes.
-
-  \begin{equation}
-    \bar{F} = \frac{\sum_i^N (w_i\,F_i)}{\sum_i^N w_i}  
-    \label{eq:avg}
-  \end{equation}
-  where $F_i$ is the $i^{th}$ epoch measurement of a parameter to be
-  averaged such as the aperture corrected calibrated flux in a $1\arcsec$ aperture
-  ({\bf aperJky3}) and $\bar{F}$ is the weighted mean average of this parameter.
-  The weight for each epoch $w_i=1/(\sigma_{F})^2$ if the epoch is included and 
-  $w_i=0$ if an epoch is excluded for quality control purposes. The weights of each epoch in each averaged catalogue are tabulated in the {\tt [w\v]serv1000MapAverageWeights}.
-
-  We calculate a set of averaged catalogues, for each pointing and filter, based
-  on the requirements in \verb+RequiredMapAverages+, in these cases over time
-  spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
-  over all epochs. The averaging process starts at the first epoch and works onwards 
-  from there. Again, we present these measurements in the new SQL tables.
-
-  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars
-  are detected in the VISTA VSA database with 130 objects in common with
-  both WFCAM and VISTA data.  We give the necessary SQL queries syntax
-  at \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt
-    d80b2t/VHzQ}.
-
-\subsection{MIR data}
-The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011} post-cryogenic and NEOWISE Reactivation Mission \citep[NEOWISE-R][]{Mainzer2014} survey phases.
-
-We use data from the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
-There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
-Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}.
-The AllWISE program combines the W1 and W2 Single-exposure data from all the WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
-The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-
-For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.
-For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.
-Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}.
-The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.
-
-Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
-Figure 4 of ][]{Krawczyk2013}.
-We thus use a cross-match radius of 2.75''.
-When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
-The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
-Investigating this in detail is very interesting but left to a future study.
-
-Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table.
-However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection information.
-
-All fluxes in the unWISE catalog are reported there are in ``Vega
-nanoMaggies'', with the Vega magnitude of a source is given by
-\begin{equation}
-m_{\rm Vega} = 22.5 - 2.5\log(f),
-\end{equation} 
-where $f$ is the source flux. The absolute calibration for unWISE is
-ultimately inherited from AllWISE through the calibration of
-\citet{Meisner2017a}. This inheritance depends on details of the PSF
-normalization at large radii, which is uncertain. Subtracting 4
-millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes
-improves the agreement between unWISE and AllWISE fluxes.
-
-Thus to convert unWISE Vega magnitudes onto the AB system, we have:     
-\begin{eqnarray*}
-        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
-        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339. 
-\end{eqnarray*}
-For the our MIR variability investigations, we do not use the unWISE
-coadds, but instead use the
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
-catalogue and the NEOWISE
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{2019 Data
-Release}. NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2)
-single-exposure images and extracted source information that was
-acquired up until 2018 December 13 (MJD 58465) including the fifth
-year of survey operations of NEOWISE. These fifth year NEOWISE data
-products are concatenated with those from the first four years into a
-single archive from 2013 December 13 (MJD 56639).
-
-The WISE scan pattern leads to coverage of the full-sky approximately
-once every six months (a``sky pass''), but the satellite was placed in
-hibernation in 2011 February and then reactivated in 2013
-October. Hence, our light curves have a cadence of 6 months with a 32
-month sampling gap.
-
-Table~\ref{tab:output_table} represents the culmination of this
-effort, and we now exam the assembly of its contents in more detail.
-\begin{landscape}
-      \input{../tables_for_paper/output_table}
-\end{landscape}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% 
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-Having collated the sample of 463 VH$z$Qs, and obtained their near-
-and mid-infrared photometry we report here the various photometric
-properties of the quasars.
-
-First, we will concentrate on detection rate in the infrared, go on to
-report on the colour-redshift and colour-colour properties of our sample
-and then report on how the current sample populates the
-luminosity-redshift $Lz$-plane.
-
-\subsection{Detection Rates in the NIR}
-Table~\ref{tab:nir_detection} gives the detection rates for the 
-VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
-The first thing to note is that the coverage of the NIR surveys 
-for example from the UKIDSS LAS and VISTA VHS, does
-not overlap the full area for where the VH$z$Qs are detected.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l r l}
-    \hline  \hline
-    Selection   & number detected (\%) \\
-    \hline  
-    Any band ($ZYJHK/K_{s}$)    &  449  (97.0) \\
-    $Z$-band                            &  75  (16.2) \\
-    $Y$-band                            &  273  (59.0) \\
-    $J$-band                              &  447  (96.5) \\
-    $H$-band                            &  269  (58.1) \\
-    $K$ or $Ks$-band                &  322  (69.5) \\
-    \hline  \hline
-  \end{tabular}
-  \caption{Detection rate of VH$z$Qs in the near-infrared. 
-For the 14 objects that have no NIR detections, 3 have 
-been observed but are not in our queried time range, 6 have 
-not been observed yet and 5 objects are too far north to be visible 
-by UKIRT. }
-  \label{tab:nir_detection}
-\end{table}
-
-There are 14 objects that have no NIR detections. 3 of these
-(PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
-been observed (by VHS) but are out of our queried time range (for
-which the data is publicly available). 6 objects are at declination
-$\delta<0$ deg and have not been observed (or at least the data is not
-in the VSA archive yet). 5 objects are at a declination $\delta \geq
-+60$ deg are too far north for UKIRT and cannot be observed.
-
-  \subsubsection{Comparing WFCAM and VISTA}
-  There are 130 quasars observed in the overlapping area between WFCAM
-  and VISTA. We used the {\tt VegaToAB} values to put these objects on
-  the same AB system, and for each object compared the two
-  measurements. First, we calculated the weighted average (calibrated
-  flux) in each filter of both and calculated the ratio and difference
-  between each measurement and the average.  Then for each filter we
-  calculated the weighted average of the differences (in mag) for each
-  instrument to see if there were significant offsets. The results are
-  given in Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a
-  significant offset is the $Y$-band. All of the VISTA averages are
-  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
-  band comparison may be affected the different shapes of the filters,
-  with $K$ being significantly wider than $K_s$, able to detect light at
-  longer wavelengths.
-  \begin{table}
-    \centering
-    \begin{tabular}{l r r}
-      \hline  \hline
-      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
-      -  WFCAM)      &                                        &  objects \\
-      \hline
-      $Z$                 &  23.2 	& 3 \\
-      $Y$                 &  57.3 	& 53 \\
-      $J$                  &    2.1 	& 106 \\
-      $H$                 &  45.8     &  96 \\
-      $K_{\rm s}$/$K$ &  25.2     & 110 \\
-      \hline  \hline
-    \end{tabular}
-    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
-      VIRCAM/VISTA near-infrared bands.}
-    \label{tab:WFCAM_vs_VISTA}
-  \end{table}
-
-  We have also checked for quasars with large differences in magnitude
-  between the WSA and VSA. Objects were selected where the average flux
-  was $>0.$ and $>5$ average flux error. In order to account for large
-  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
-  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
-  selects two quasars with large, $\delta$mag $>0.2$mag differences
-  between the WSA and VSA. These are SDSSJ0349+0034 and
-  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
-  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
-  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
-  = 19.38$\pm$0.04.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l r r r r}
-    \hline \hline
-    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
-                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
-    \hline
-    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
-    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
-    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
-    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
-    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
-    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
-    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
-    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
-    \hline \hline
-  \end{tabular}
-  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
-    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
-  \label{tab:mir_detection}
-\end{table}
-
-\subsection{Detection Rates in the MIR}
-Unlike the NIR coverage, the WISE satellite and mission performed an all-sky survey, so the location of every VH$z$Q in our dataset is covered.
-However, the depth of the WISE survey depends heavily on sky location, with locations near the Ecliptic Poles having the highest number of exposures.
-
-\begin{figure}
-  %% trim=l b r t
-  \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_20190605.pdf}
-  \centering
-  \vspace{-14pt}
-  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise,
-    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
-  \label{fig:WISEmag_vs_coverage}
-\end{figure}
-Before reporting on the detection rates, we investigate this effect
-using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
-shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
-by {\tt w$x$cov} the mean coverage depth, in each corresponding
-band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
-from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
-area with a radius of 8.25'' centered on the position of this
-source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
-Catalog
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
-Descriptions} has further details). The {\tt w$x$cov} value takes into
-account e.g., individual pixels in the measurement area that may be
-masked or otherwise unusable (reducing the effective pixel count and
-thus the mean coverage value) as well as pixels that are affected by
-distortions across the across the focal plane in single-exposure
-images (where this distortion is corrected when coadding to generate
-the Atlas Images). 
-In the two shorter bands W1/2 we see the clear and expected
-trend for brighter objects to have larger SNR, and also for the higher
-signal to noise for objects with more exposures at a given
-magnitude. The behaviour for the W3/4 bands is different, with two
-populations clearly evident in W3 and although a bit more mixed, also
-in W4. With the suggested split at SNR$>2$, and no obvious
-R.A./Declination dependence seen, this behaviour is explained by the
-fact that there are non-detections in W3/4 for objects (with high W1/2
-SNR) that are reported in the ALLWISE catalogue.
-
-Table~\ref{tab:mir_detection} gives the detection rates for the
-VH$z$Qs in the MIR WISE W1-4 bands. The unWISE depths are impressive
-with nearly 80\% of all the VH$z$Qs being detected in unWISE W1. 12
-out of 14 (86\%) in unWISE W1 (9 our of 14; 64\% in unWISE W2) of the
-$z\geq6.78$ quasars are detected and moreover {\it all of the $z\geq7$
-quasars are detected in both unWISE W1 and W2}. This bodes very well
-for future, small mirror infrared missions \citep[e.g.][]{NEOCam_WP}.
-
-Recently, \citet{Assef2018} released two large catalogues of AGN
-candidates identified across 30,000 deg$^2$ of extragalactic sky from
-the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
-AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
-per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
-candidates at 75\% completeness (and ($\approx$700 AGN candidates per
-deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
-catalogues, produces 42 matches with the R90 sample and 98 matches
-with the C75 sample. Both catalogues unsurprisingly match to the
-ultraluminous quasar SDSS J0100+2802 \citep{Wu2015} while the C75, but
-not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS
-J1120+0641 \citep{Mortlock2011}. Neither catalogue matches to the
-current highest-redshift object J1342+0928 \citep{Banados2018}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
-  \vspace{-14pt}
-    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
-      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
-      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
-      (grey colour-scale). }
-    \label{fig:W1W2W3}
-\end{figure}
-\subsection{MIR Colours}
-Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
-several investigations have looked at how WISE detects AGN 
-\citet[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
-
-The VH$z$Q with the bluest colour in (W1 - W2) is 
-DELS J1048-0109 with (W1-W2) = 0.154. 
-%(see Figure~\ref{fig:DELS_J1048}).
-
-Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs.
-(W2-W3) colour – colour space diagram showing the WISE colours for the 283 VH$z$Q that have reported {\tt w3mpro} values (blue to red coloured points), though we note that only 51(18\%) of these objects have {\tt w3snr} > 3.0.
-objects  400,000 quasars
-at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
-colour-scale). 
-% W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
-% W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
-% W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars,
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
-    \caption{Four of the brightest MIR VH$z$Qs. 
-      The thumbnails are the RGB colour outputs using the ALLWISE W1W2W3 bands from the 
-      IRSA WISE Image Service, with a scale of 120'' on the side. 
-      {\it (a)} UHS J0439+1634 was discovered by
-      \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. 
-      {\it (b)} SDSS J0100+2802 is the \citet{Wu2015} object. 
-      {\it (c)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
-      {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).}
-    \label{fig:VHzQ_W4s}
-\end{figure*}
-The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
-detected in the broad W3 filter and 10 objects that are formally detected
-in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
-presented in \label{fig:VHzQ_W4s}. UHS J0439+1634
-(Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
-\citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
-luminosity is mostly not intrinsic, but is boosted by an intervening
-redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
-not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
-but as reported by \citet{Wu2015}, has a bright detection in the
-2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
-%%
-Other high-redshift quasars that are bright W3/4 objects may well 
-also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, 
-but high-resolution follow-up is needed to confirm.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm]
-  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
-  \vspace{-16pt}
-  \caption[]
-  {Histogram showing the total number of exposures for each detected VH$z$Q
-    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
-  \label{fig:MIR_LC_epochs}
-\end{figure}
-\subsection{Variability}
-VH$z$Qs, if accreting at, or above the Eddington limit, might well
-have changing mass accretion rates, i.e., $\ddot{m}_{\rm accr}$. A
-consequence of this would be that these quasars exhibit signs of
-variability, most likely showing up in their UV/optical rest-frame
-emission. We look for evidence of this variability signature in the
-NIR and MIR light-curves of the VH$z$Qs.
-
-Quasars are known to have dramatically changing Balmer lines,
-especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016,
-Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018,
-Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$
-is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m,
-which is between the W2 and W3-bands at $z=7.50$.  H$\beta$ is
-redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$
-and 4.13$\mu$m at $z=7.50$. Less well understood is the temporal
-behaviour of the metal lines, in particular \civ and \mgii.  \civ
-enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
-enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
-enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
-enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
-
-\begin{figure}
-  \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
-  \centering
-  \caption[]
-  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
-    Red points are the W1 band; cyan points the W2 band.} 
-  \label{fig:MIR_LC_3egs}
-\end{figure}
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
-and detections there are for each VH$z$Q, while
-Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR
-lightcurves and associated colour changes. Here we show J0100+2802
-\citep{Wu2015}, J0224-4711 and J1626+2751.
-
-Using the extended datasets described in Section~\ref{sec:NIR_data},
-we select objects with at least 8 measurements observed with intervals
-of at least 30 days, in at least one filter. The the average
-calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
-with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
-aperJky3/aperJky3Err}$\geq$8). The clipped median and standard
-deviation is then calculated
-\begin{equation}
-      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
-\end{equation}
-where $var$ is the index of variation, m.a.d. is the median absolute
-deivation, and $\bar{\epsilon}$ is the mean of the error in each point
-in the light curve, divided by the total number of points.  With these
-criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
-J1148+0056) in common to both, and this sample of 32 is our starting
-point for variability investigations.
-
-We present four objects that are particularly well-sampled in the NIR. 
-These are: 
-MMT J0215-0529       ($z=5.13$; Figure~\ref{fig:MMTJ0215-0529}), 
-CFHQS J0216-0455    ($z=6.01$; Figure~\ref{fig:CFHQSJ0216-0455}), 
-SHELLQs J0220-0432 ($z=5.90$; Figure~\ref{fig:SHELLQsJ0220-0432}) 
-and 
-SDSS J0959+0227 ($z=5.07$; Figure~\ref{fig:SDSSJ0959+0227}). 
-We incorporate the MIR NEOWISE-R light curve data where available.
-
-\begin{figure}
-  \begin{subfigure}{}
-    \centering
-    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
-    \caption{The infrared light curve for MMT J0215-0529 with data from 
-      WFCAM (smaller solid cirlces), VIRCAM (hexagons) and NEOWISE-R (larger solid cirlces).}
-    \label{fig:MMTJ0215-0529}
-  \end{subfigure} 
-  \begin{subfigure}{}
-    \centering
-    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
-    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
-    \label{fig:CFHQSJ0216-0455}
-  \end{subfigure}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{}\quad
-    \centering
-    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
-    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
-    \label{fig:SHELLQsJ0220-0432}
-  \end{subfigure}
-  \begin{subfigure}{}\quad
-    \centering
-    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
-    \caption{The near infrared light curve for SDSS J0959+0227. Note, 
-      SDSS J0959+0227 is too faint in the MIR to be detected by ALLWISE or unnWISE.}
-    \label{fig:SDSSJ0959+0227}
-  \end{subfigure}
-  \medskip
-\end{figure}
-
-Even with well sampled data across the 3000-4000 day observed
-time-scales that the WFCAM and VISTA surveys span, the $(1+z)$
-time-dilation dramatically affects the sampled rest-frame timescales
-sampled. Indeed, when sharp changes in a accretion rate are expected
-on the system's dynamical timescale of several kiloyears
-\citep[e.g.,][]{Regan2019}, then seeing any variability signature is
-not expected. However, noting how in lower redshift quasars, which
-also have massive $>10^{8}$ M$_{\odot}$ black holes, dramatic changes
-in both continuum and line emission {\it is seen} on much shorter
-timescales, continued monitoring of these objects is warrented.
-
-We finally focus on SDSS J0959+0227 which is presented in
-\citet{WangF2016} but is first reported in \citet{Civano2011} as
-CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
-field. The spectrum from this object is presented in \citet{Ikeda2012}
-and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
-likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
-source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
-keV rest-frame, so it is an AGN. This object is clearly not a regular
-broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
-SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
-rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
-rest-frame UV/very blue, so, so the regular blue QSO continuum could
-be emerging Thus, with the slightest hint of variability, this could
-potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
-2'' object to a broadline Type 1 quasar.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Conclusions}
-\label{sec:conclusions}
-In this study, we have, for the first time, compiled the list of all
-$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
-($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
-objects, given their detection rates and SEDs. We find that:
-
-%%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have.
-
-\begin{itemize}
-    \item Lorem ipsum dolor sit amet, consectetur adipiscing
-      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
-      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
-      convallis ac. 
-    \item Fusce pellentesque condimentum dolor, quis vehicula
-      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
-      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
-      diam eu blandit. Donec in lacinia libero.
-    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-      euismod. Cras vel auctor neque. Nam quis diam risus.
-\end{itemize}
-Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
-eu elit massa. Nulla vel lacus lorem. Proin et lobortis
-tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
-nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
-ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
-eget tempor elementum, lectus urna feugiat nisi, eget sagittis.
-
-\subsection*{Author Contributions}   
-N.P.R.
-initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
-
-N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
-
-\subsection*{Availability of Data and computer analysis codes} 
-All materials, databases, data tables and code are fully available at: 
-\href{https://github.com/d80b2t/VHzQ}{\tt https://github.com/d80b2t/VHzQ}
-
-\section*{Acknowledgements}
-NPR acknowledges support from the STFC and the Ernest Rutherford Fellowship scheme.
-
-We thank:
-\begin{list}{$\circ$}{}  
-\item Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA) and the VISTA Science Archive (VSA). 
-\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
-\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
-\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
-\end{list}
-
-This paper heavily used \href{http://www.star.bris.ac.uk/~mbt/topcat/}{TOPCAT} (v4.4)
-\citep[][]{Taylor2005, Taylor2011}.
-%%
-This research made use of \href{http://www.astropy.org}{\tt Astropy}, 
-a community-developed core Python package for Astronomy 
-\citep{AstropyCollaboration2013, AstropyCollaboration2018}.
-
-The Pan-STARRS1 Surveys (PS1) and the PS1 public science archive have
-been made possible through contributions by the Institute for
-Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
-the Max-Planck Society and its participating institutes, the Max
-Planck Institute for Astronomy, Heidelberg and the Max Planck
-Institute for Extraterrestrial Physics, Garching, The Johns Hopkins
-University, Durham University, the University of Edinburgh, the
-Queen's University Belfast, the Harvard-Smithsonian Center for
-Astrophysics, the Las Cumbres Observatory Global Telescope Network
-Incorporated, the National Central University of Taiwan, the Space
-Telescope Science Institute, the National Aeronautics and Space
-Administration under Grant No. NNX08AR22G issued through the Planetary
-Science Division of the NASA Science Mission Directorate, the National
-Science Foundation Grant No. AST-1238877, the University of Maryland,
-Eotvos Lorand University (ELTE), the Los Alamos National Laboratory,
-and the Gordon and Betty Moore Foundation.
-
-This project used data obtained with the Dark Energy Camera (DECam)
-and the NOAO Data Lab, The Data Lab is operated by the National
-Optical Astronomy Observatory, the national center for ground-based
-nighttime astronomy in the United States operated by the Association
-of Universities for Research in Astronomy (AURA) under cooperative
-agreement with the National Science Foundation.
-
-This publication makes use of data products from the Wide-field
-Infrared Survey Explorer, which is a joint project of the University
-of California, Los Angeles, and the Jet Propulsion
-Laboratory/California Institute of Technology, and NEOWISE, which is a
-project of the Jet Propulsion Laboratory/California Institute of
-Technology. WISE and NEOWISE are funded by the National Aeronautics
-and Space Administration.
-
-CasJobs was originally developed by the Johns Hopkins University/
-Sloan Digital Sky Survey (JHU/SDSS) team. With their permission, MAST
-used version 3.5.16 to construct CasJobs-based tools for GALEX,
-Kepler, the Hubble Source Catalog, and PanSTARRS.
-
-This research has made use of the SVO Filter Profile Service
-(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
-MINECO through grant AyA2014-55216 
-%%
-The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
-describes the Spanish VO Filter Profile Service. 
-The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html
-
-%\newpage
-
-\appendix
-
-\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
-Here we give the receipe and SQL that returned the near-infrared photometry 
-for the VH$z$Qs from the  WFCAM Science Archive.
-
-The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
-Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
-with these credentials::
-\begin{itemize}
-    \item Username: {\tt WSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt nonsurvey}
-\end{itemize}
-Then going to the
-\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
-Query}} page the Database release {\tt WSERV1000v20180716} can be
-accessed which contains all the data we use here.
-
-We {\it nota bene} a few things. First, the quantity {\tt aperJky3}
-and {\tt aperJky3Err} are found in the {\tt wserv1000MapRemeasAver}
-and {\tt wserv1000MapRemeasurement}, so care has to be taken to return
-unique column names (otherwise e.g.
-\href{http://docs.astropy.org/en/stable/io/fits/}{astropy.io.fits}
-will crash).  As such, we alias {\tt aver.aperJky3} to {\tt
-aperJky3Aver} and likewise for the error quantity. Aliases will be
-necessary in some cases anyway, because some queries can be done
-sensibly on multiple instances of the same table. Other times, one may
-join tables on quantities such as {\tt catalogueID} or {\tt
-apertureID}, where you are meaning the same thing, but aliases would
-again be sensible.
-
-Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
-used directly. To return values in degrees, use a selection with an alias, e.g. 
-{\tt RA as RADeg} and {\tt DEC as DECDeg}.
-
-\onecolumn
-\input{SQL_examples_WSA}
-\twocolumn
-
-\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL}
-In a very similar manner to the WSA, we give here the details on how to access
-the VISTA Science Archive (VSA)
-
-At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
-with these credentials::
-\begin{itemize}
-    \item Username: {\tt VSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt proprietary}
-\end{itemize}
-Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20180716}.
-
-%\onecolumn
-%\input{SQL_examples_VSA}
-%\twocolumn
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\bibliographystyle{apj}
-%\bibliographystyle{mn2e}
-\bibliographystyle{mnras}
-\bibliography{tester_mnras}
-
-\end{document}

### 2019-06-12 tex/VHzQ.tex
got rid of \blindtext lorem ipsumgist

@@
 
+We note that sometimes the average flux is negative and so a default
+magnitude is reported.  This is apparent for the average $H$ and
+$K_{s}$ flux for CFHQS J0216-0455 at MJD=56900.  Interestingly this is
+evident in both the $H$ and $K_{s}$ filters, but with this quasar not
+much brighter than the detection limit, one must be very careful with
+any (over) interpretation.
+
 Even with well sampled data across the 3000-4000 day observed
@@
 %%
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Surface Density of VH$z$Qs}
-One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
-are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
-so, how many are still to be discovered and confirmed spectroscopically?
-
-In the North, we assume the UHS J-band depth of 19.6 \citep[Vega;
-][]{Dye2018}.  In the South, one can use the report {\tt ABmagLimits}
-for each survey in the database, we can calculate the depths of the
-various NIR VISTA surveys.  Fig.~\ref{fig:VHS_J_abMagLim} shows this
-calculated average {\tt AB MAGLIM} in the VHS.  As one can see, the
-VHS is not completely uniform. The area wrapping round
-310$\lesssim$RA/deg$\lesssim$90 and -70$\lesssim$ Decl./ deg
-$\lesssim$ -40 has a $J$-band depth of 21.2 AB mag, whereas the rest
-of the VHS area, the $J$-band depth is closer to 20.6 AB mag.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_J_abMagLim.png}
-  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
-    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
-    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
-    Y and H are almost uniform, but the coverage is much less.}
-  \label{fig:VHS_J_abMagLim}
-\end{figure}
-
-Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
-exponential decline to describe the space density of VH$z$Qs at high
-redshifts, e.g.
-\begin{equation}
-\rho(z, {\rm M}_{1450}) \propto 10^{k (z)}
-\end{equation}
-where $z$ is the sample redshift. 
-%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
 %%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Conclusions}
-\label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 In this study, we have, for the first time, compiled the list of all
@@
 
-%%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have.
-
 \begin{itemize}
-    \item Lorem ipsum dolor sit amet, consectetur adipiscing
-      elit. Aliquam porta sodales est, vel cursus risus porta non. Vivamus
-      vel pretium velit. Sed fringilla suscipit felis, nec iaculis lacus
-      convallis ac. 
-    \item Fusce pellentesque condimentum dolor, quis vehicula
-      tortor hendrerit sed. Class aptent taciti sociosqu ad litora torquent
-      per conubia nostra, per inceptos himenaeos. Etiam interdum tristique
-      diam eu blandit. Donec in lacinia libero.
-    \item Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-      pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-      id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-      dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-      euismod. Cras vel auctor neque. Nam quis diam risus.
+    \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;  
+    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
+      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
+    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
+    \item The 14 objects that are not detected in the NIR is due to lack of coverage rather than lack of depth; 
+   \item 362 ( 78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
+ \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
 \end{itemize}
-Nunc lacus nibh, convallis ac lobortis ut, tempus ac lectus. Maecenas
-eu elit massa. Nulla vel lacus lorem. Proin et lobortis
-tortor. Phasellus ultrices nisl non enim porttitor dictum. Curabitur
-nec nunc ac nibh ornare elementum. Nunc ultrices hendrerit
-ultricies. Aliquam dapibus semper est et gravida. Etiam cursus, massa
-eget tempor elementum, lectus urna feugiat nisi, eget sagittis.
+
+The science reach of $z>5$ quasars will continue to be important well into the next decade
+\citep{Fan2019_DecadalWP, Wang2019_DecadalWP}
+and will provide key insights into direct collapse black holes, hydrogen reionization and
+the physics of accretion in the first $\lesssim$700 million years of the Universe.
 

### 2019-06-12 tex/SurfaceDensity.tex
VHzQ_20190612 moved

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% 
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Surface Density of VH$z$Qs}
-One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
-are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
-so, how many are still to be discovered and confirmed spectroscopically?
+One interesting question to ask is given the compilation of VH$z$Qs
+assembled here, are there bright $z>5.00$ quasars that are in {\it
+current} photometric datasets, and if so, how many are still to be
+discovered and confirmed spectroscopically?
 
@@
 
+Having obtained an as-near-to-homogenous set of photometry as we can, 
+we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
+sample and in particulare the absolute magnitude at rest-frame 1450\AA\ , $M_{1450}$, 
+which is a key physical quantity and goes directly towards the quasar luminosity 
+function and thus the reionization of hydrogen calculation.
+
+We calculate the Distance Modulus in the normal fashion, 
+\begin{equation}
+m_{1450} - M_{1450} = 5 \log \left (    \frac{ D_{\rm L}(z)}{\rm Mpc}  \right )  + 25 + K_{\rm corr}(X,z)
+\end{equation}
+where $m_{1450}$ is the apparent magnitude at 1450\AA\ ,  
+%$M_{1450}$ is the absolute magnitude at 1450 \AA\ , 
+$D_{\rm L}(z)$ is the luminosity distance and 
+$K_{\rm corr}(X,z)$ is the $K$-correction which corrects for the effects of redshifting of the bandpass and the spectrum.
+
+The $m_{1450}$ apparent magnitude is derived from the $z-$, $y/Y-$ or $J-$band photometery.
+%%
+The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
+sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
+for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
+cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.
+
+\citet{Ross2013} has a detailed discussion of the $K$-correction (see that papers' Appendix B). 
+The key result in that paper is, if quasars are described as having a power-law slope, 
+$\alpha^{\nu}$ in spectral flux density, i.e., $f_\nu(\nu) \propto \nu^{\alpha_{\nu}}$ (as is conventional) 
+then 
+\begin{equation}
+K_{\rm corr}(z) = -2.5 (1 + \alpha_{\nu}) \log[1 + z].
+\end{equation}
+Here the $[-2.5 \log(1 + z)]$ term corrects for the effective narrowing of the filter width with redshift, (the ``bandpass correction'') and the $[-2.5 \alpha^{\nu} \log(1 + z)]$ term takes into account the spectral index correction.
+The bandpass correction is approximately $\approx -1.945$ at redshift $z=5$ decreasing to $-2.32$ at redshift $z=7.50$.
+
+%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$
+
+\iffalse
+\begin{figure*}
+  \includegraphics[width=18.0cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
+  \centering
+  \caption[]{The luminosity-redshift, $L-z$, plane for the VH$z$Qs. 
+    The evolution of $M^{\star}$, the characteristic magnitude 
+    for $z\simeq4–8$ galaxies is given by the long dashed line \citep{Bowler2015}. }
+  \label{fig:Lz}
+\end{figure*}
+\fi
+
 Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
@@
 where $z$ is the sample redshift.
-%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54

### 2019-06-12 tex/VHzQ.tex
more tex/ edits, updates

@@
 
-\title[Very high-$z$ Quasars]
+\title[Infrared properties Very high-$z$ Quasars]
   {Near and Mid-infrared properties of known $z\geq5$ Quasars}
 \author[Ross \& Cross]
-       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
-\\ 
-$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\
-}
+{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross\\ 
+Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }
 
@@
 %% 
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{SurfaceDensity}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
 %%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
@@
 
-The science reach of $z>5$ quasars will continue to be important well into the next decade
-\citep{Fan2019_DecadalWP, Wang2019_DecadalWP}
-and will provide key insights into direct collapse black holes, hydrogen reionization and
-the physics of accretion in the first $\lesssim$700 million years of the Universe.
+The science reach of $z>5$ quasars will continue to be important well
+into the next decade \citep{Becker2019_DecadalWP, Fan2019_DecadalWP,
+Wang2019_DecadalWP} and will provide key insights into direct collapse
+black holes, hydrogen reionization and the physics of accretion in the
+first $\lesssim$700 million years of the Universe.
 

### 2019-06-12 color_redshift/redshift_vs_W1W2.py
Kris Kross

@@ -155,7 +155,6 @@ minorLocator = MultipleLocator(0.1)
 ax.yaxis.set_major_locator(majorLocator)
 ax.yaxis.set_minor_locator(minorLocator)
 
-
 ## Grid lines to compare with Wright et al. (2010) Fig. 12
 ## Vertical lines
 for x in range(8): 

### 2019-06-12 tex/VHzQ.tex
Kris Kross
anoter wee update
Corrected text/ added a little more

@@
 \author[Ross \& Cross]
-{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross\\ 
+%\author[N. Ross, N. Cross \& C. Ross]
+{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross \\ 
+%{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk}, Nicholas J. G. Cross and Christine B. Ross \\ 
 Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }
@@
 where $var$ is the index of variation, m.a.d. is the median absolute
-deivation, and $\bar{\epsilon}$ is the mean of the error in each point
+deviation, and $\bar{\epsilon}$ is the mean of the error in each point
 in the light curve, divided by the total number of points.  With these
@@
     \caption{The infrared light curve for MMT J0215-0529 with data from 
-      WFCAM (smaller solid cirlces), VIRCAM (hexagons) and NEOWISE-R (larger solid cirlces).}
+      WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).}
     \label{fig:MMTJ0215-0529}
@@
 time-dilation dramatically affects the sampled rest-frame timescales
-sampled. Indeed, when sharp changes in a accretion rate are expected
+sampled, which are $\sim300-700$ days. Indeed, when sharp changes in a accretion rate are expected
 on the system's dynamical timescale of several kiloyears
@@
 in both continuum and line emission {\it is seen} on much shorter
-timescales, continued monitoring of these objects is warrented.
+timescales, continued monitoring of these objects is warranted.
 
@@
 In this study, we have, for the first time, compiled the list of all
-$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
+$z>5$ spectroscopically confirmed quasars. We have assembled the NIR
 ($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
@@
     \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
-    \item The 14 objects that are not detected in the NIR is due to lack of coverage rather than lack of depth; 
+    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
    \item 362 ( 78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
+ \item 32 of the QSOs had enough NIR measurements and a good enough signal-to-noise ratio to look for variability.
+Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529.
+2 other QSOs, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability.
 \end{itemize}
@@
 \citep{AstropyCollaboration2013, AstropyCollaboration2018}.
+
+The VISTA Data Flow System pipeline processing and science archive were used for the WFCAM and VISTA 
+near infrared data are described in Irwin et al (2004), Hambly et al (2008) and Cross et al. (2012).
 
@@
 
-%\newpage
+%% N.P.R. may have listened to Kris Kross during the preparation of this manuscript.
 
@@
 \section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
-Here we give the receipe and SQL that returned the near-infrared photometry 
+Here we give the recipe and SQL that returned the near-infrared photometry 
 for the VH$z$Qs from the  WFCAM Science Archive.
@@
 \href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
-Query}} page the Database release {\tt WSERV1000v20180716} can be
+Query}} page the Database release {\tt WSERV1000v20190507} can be
 accessed which contains all the data we use here.
@@
 join tables on quantities such as {\tt catalogueID} or {\tt
-apertureID}, where you are meaning the same thing, but aliases would
-again be sensible.
+apertureID}, where you are meaning the same thing, but aliases are then necessary 
+for SQLServer to correctly comprehend the query.
 
@@
 used directly. To return values in degrees, use a selection with an alias, e.g. 
-{\tt RA as RADeg} and {\tt DEC as DECDeg}.
+{\tt RA as RADeg} and {\tt DEC as DECDeg}. Other relevant query examples can be found in the
+GitHub repository, under WSA_VSA/SAMPLE_SQL_QUERIES, or the SQLCookbook in the WSA or VSA.
 
@@
 \end{itemize}
-Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20180716}.
+Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20190508}.
+The queries are the same as those used in the WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting with {\tt wserv1000} should be replaced with {\tt vserv1000}.
 

### 2019-06-13 color_redshift/redshift_vs_W1W2.py
color_redshift/redshift_vs_W1W2.py fitsio update

@@ -12,6 +12,9 @@ Good links::
 '''
 
 import numpy as np
+import fitsio
+
+from fitsio import FITS,FITSHDR
 from astropy.io    import fits
 from astropy.io    import ascii
 from astropy.table import Table
@@ -19,6 +22,11 @@ from astropy.table import Table
 import matplotlib
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+
+import time
+start_time = time.time()
+
+print("--- %s seconds ---" % (time.time() - start_time), ' to do the imports')
 
 ##
 ## DR14Q
@@ -28,10 +36,14 @@ filename   ='DR14Q_v4_4.fits'
 #filename  ='DR14Q_v4_4_W4good.fits'
 infile     = path+filename
 data       = fits.getdata(infile, 1)
+#data     = fitsio.read(infile,ext=1)  
 #dr14q_full = Table(data)
 dr14q      = Table(data)
 ## in case you want to select on e.g. SDSS survey
 #dr14q      = dr14q_full
+
+print("--- %s seconds ---" % (time.time() - start_time), ' to read-in data')
+
 
 ## Splitting up the DR14Q by intergral survey
 ##   from the DR12Q,  MJD.min() = 55176 and MJD.max() = 56837
@@ -45,6 +57,8 @@ eboss = dr14q[np.where( dr14q['MJD'] > 56837  )]
 ##    79,487 for SDSS-I/II;
 ##   286,686 for BOSS;
 ##   159,981 for SDSS-IV
+
+print("--- %s seconds ---" % (time.time() - start_time), ' to read-in data')
 
 
 boss_uband = boss['PSFMAG'][0:,0]
@@ -75,7 +89,6 @@ VHzQ_full = ascii.read(table)
 ## in case you want to select on e.g. snr
 VHzQ = VHzQ_full
 #VHzQ = VHzQ_full[np.where(VHzQ_full['w3snr'] >3.0)]
-
 
 
 
@@ -178,6 +191,7 @@ plt.savefig('redshift_vs_W1W2_temp.png', format='png')
 #plt.show()
 plt.close()
 
+print("--- %s seconds ---" % (time.time() - start_time), ' to do full plot')
 
 
 
@@ -218,6 +232,7 @@ for y in range(9):
 plt.savefig('redshift_vs_W1W2_sdss_temp.png', format='png')
 plt.close()
 
[…]

### 2019-06-13 tex/VHzQ.tex
Added more details to NIR variability results

@@
 calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
-with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
-aperJky3/aperJky3Err}$\geq$8). The clipped median and median absolute
-deviation is then calculated
+with the signal-to-noise is required to be $\geq8$ (i.e. {\tt
+aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 21 WFCAM 
+and 12 VISTA objects with 1 object (VIK J1148+0056) in common to both, 
+and this sample of 32 is our starting
+point for variability investigations.
+
+The clipped median and median absolute deviation is then calculated
 \begin{equation}
@@
 deviation, and $\bar{\epsilon}$ is the mean of the error in each point
-in the light curve, divided by the total number of points.  With these
-criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
-J1148+0056) in common to both, and this sample of 32 is our starting
-point for variability investigations.
+in the light curve, divided by the total number of points. We apply the criteria 
+$var>=3.$ to light-curves from the original measurements and also to light-curves 
+where measurements have been averaged over different time-scales to improve 
+the signal-to-noise. We found that two quasars showed signs of variability:
+MMT J0215-0529 in the Y-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
+SDSS J0959+0227 in the Y and H bands, with timescales of 1 year or 6 months 
+for Y only. The H-band amplitude was 0.9 mag and the Y-band amplitude was 1.2 mag if averaged over 6 months,
+or 0.9 mag if averaged over 1 year.
 

### 2019-06-13 tex/VHzQ.tex
tables_for_paper/output_table.tex update

@@
 \begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high
-($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$
-and $K$) infrared and mid-infrared (WISE) properties.  Using archival
-WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
-in the near-infrared that might be expected from super-Eddington
-accretion and find {\it blah}.  Extrapolating the known quasar
-luminosity function we suggest that $x$\% of the possibly detected
-$z\geq5$ quasars in the current datasets have been discovered.  All
-the data, analysis codes and plots used and generated here can be
+We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties.
+We find that SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample and that 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth for the objects that are not detected in the NIR.
+362 (78.2\%) VH$z$Qs are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all of the $z\geq7$ quasars are detected in both unWISE W1 and W2.
+Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability in the near-infrared that might be expected from super-Eddington accretion.
+We find 32 of the quasars have sufficient NIR measurements and signal-to-noise to look for variability.
+Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529.
+Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band.
+%% 
+%% Extrapolating the known quasar luminosity function we suggest that
+%% $x$\% of the possibly detected $z\geq5$ quasars in the current
+%% datasets have been discovered.
+All the data, analysis codes and plots used and generated here can be
 found at: \href{https://github.com/d80b2t/VHzQ}{\tt
@@
  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
- \item 32 of the QSOs had enough NIR measurements and a good enough signal-to-noise ratio to look for variability.
+ \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability.
 Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529.
-2 other QSOs, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability.
+2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability.
 \end{itemize}
@@
 {\tt RA as RADeg} and {\tt DEC as DECDeg}. Other relevant query examples can be found in the
-GitHub repository, under WSA_VSA/SAMPLE_SQL_QUERIES, or the SQLCookbook in the WSA or VSA.
+GitHub repository, under WSA\_VSA/SAMPLE\_SQL\_QUERIES, or the SQLCookbook in the WSA or VSA.
 

### 2019-06-13 tex/VHzQ.tex
updated Abstract

@@
 the signal-to-noise. We found that two quasars showed signs of variability:
-MMT J0215-0529 in the Y-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
-SDSS J0959+0227 in the Y and H bands, with timescales of 1 year or 6 months 
-for Y only. The H-band amplitude was 0.9 mag and the Y-band amplitude was 1.2 mag if averaged over 6 months,
+MMT J0215-0529 in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
+SDSS J0959+0227 in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
+for $Y$ only. The $H$-band amplitude was 0.9 mag and the $Y$-band amplitude was 1.2 mag if averaged over 6 months,
 or 0.9 mag if averaged over 1 year.

### 2019-06-13 tex/VHzQ.tex
paths to figures changed

@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
+  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/Nofz/Nofz_0pnt075bins_20181211.png}
+  {../Nofz/Nofz_0pnt075bins_20181211.png}
   \centering
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_20190605.pdf}
+  {../detections/WISEmag_vs_coverage_20190605.pdf}
   \centering
@@
   \includegraphics[width=8.5cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
+  {../light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
   \centering

### 2019-06-13 tex/VHzQ.tex
tex/VHzQ.tex and data/light_curves/individual_objects/MMTJ0215-0529/NEOWISER-R_SingleExp_L1b_redux.dat

@@
     \caption{The infrared light curve for MMT J0215-0529 with data from 
-      WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).}
+      WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
+MMT  J0215-0529 was identified by \citet{McGreer2018}, 
+% 02:15:23.27 −05:29:45.8
+%g_AB = 28.05 \pm 1.00 
+%r_AB = 22.69 \pm  0.01
+%           20.85 \pm  0.01 
+%           20.64 \pm 0.01
+% −25.7 5.13 MMT 
+}
     \label{fig:MMTJ0215-0529}

### 2019-06-13 light_curves/lightcurve_plot.py
ight_curves/lightcurve_plot.py update

@@ -2,6 +2,7 @@
 Why doesn't matplotlib look as good as SM??!!!
 http://space.mit.edu/home/turnerm/python.html
 '''
+
 import os
 import math
 import numpy as np
@@ -40,7 +41,6 @@ if choice == '7' : inputQuasar = 'SHELLQsJ1146+0124'
 if choice == '8' : inputQuasar = 'VIKJ1148+0056'
 if choice == '9' : inputQuasar = 'SDSSJ2216+0013'
     
-
 print
 print(" Plotting W/VSA light curve for ", inputQuasar)
 print

### 2019-06-13 tex/VHzQ.tex
MMTJ0215-0529 update
Added references to figures when discussing variability

@@
 the signal-to-noise. We found that two quasars showed signs of variability:
-MMT J0215-0529 in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
-SDSS J0959+0227 in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
+MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
+SDSS J0959+0227 (see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
 for $Y$ only. The $H$-band amplitude was 0.9 mag and the $Y$-band amplitude was 1.2 mag if averaged over 6 months,

### 2019-06-13 tex/VHzQ.tex
CFHQSJ0216-0455LC update

@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
+    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
     \caption{The infrared light curve for MMT J0215-0529 with data from 
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
+    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}

### 2019-06-13 light_curves/lightcurve_plot.py

@@ -96,8 +96,8 @@ Ks_VIRCAM_30d = VSA_data_30d[(VSA_data_30d['filterID'] == 5) & (VSA_data_30d['ap
 ## For WISE, we adopt 2.699 and 3.339 as the conversions to AB from W1 and W2 Vega magnitudes,
 #if choice != '7' & choice !='5':
 if choice !='5':
-    WISE_W1_AB = NEOWISER['w1mpro'] + 2.699
-    WISE_W2_AB = NEOWISER['w2mpro'] + 3.339
+    NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.699
+    NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.339
 
 
 
@@ -175,17 +175,18 @@ ax.errorbar(Ks_VIRCAM_30d['mjd'], Ks_VIRCAM_30d['aperMag3Ab'],  yerr=Ks_VIRCAM_3
 
 print('Creating plot, ...WISE labels...')
 if choice != '5' :
-    ## WISE W1/W2
-    ms = 6.
-    ax.errorbar(NEOWISER['mjd'], WISE_W1_AB, yerr=NEOWISER['w1sigmpro'], fmt='o', ms=ms, label='NEOWISE-R W1',
+    
+    ## NEOWISE-R  W1/W2
+    ms = 12.
+    ax.errorbar(NEOWISER['mjd'], NEOWISER_W1_AB, yerr=NEOWISER['w1sigmpro'], fmt='o', ms=ms, label='NEOWISE-R W1',
             markeredgecolor ='black', markeredgewidth = markeredgewidth, color='peru') #linestyle=ls, linewidth=lw*2.5, 
-    ax.errorbar(NEOWISER['mjd'], WISE_W2_AB, yerr=NEOWISER['w2sigmpro'], fmt='o', ms=ms, label='NEOWISE-R W2', 
+    ax.errorbar(NEOWISER['mjd'], NEOWISER_W2_AB, yerr=NEOWISER['w2sigmpro'], fmt='o', ms=ms, label='NEOWISE-R W2', 
            markeredgecolor ='black', markeredgewidth = markeredgewidth, color='orangered') #linestyle=ls, linewidth=lw*2.5,
-    ax.errorbar(NEOWISER['mjd'], WISE_W1_AB, yerr=NEOWISER['w1sigmpro'], fmt='o', ms=ms, label='',
[…]

### 2019-06-13 tex/VHzQ.tex
Fixed typo
big, late night update; SHELLQsJ0220-0432

@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
+    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
@@
 \begin{list}{$\circ$}{}  
-\item Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA) and the VISTA Science Archive (VSA). 
+\item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
 \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 

### 2019-06-13 light_curves/lightcurve_plot.py

@@ -59,12 +59,13 @@ WSA_data_30d = ascii.read(os.path.join(path,inputQuasar,'WSA_lc_30d.dat'))
 VSA_data_all = ascii.read(os.path.join(path,inputQuasar,'VSA_lc_all.dat'))
 VSA_data_30d = ascii.read(os.path.join(path,inputQuasar,'VSA_lc_30d.dat'))
 
+## ALLWISE
+if (choice == '3'):
+    ALLWISE =  ascii.read(os.path.join(path,inputQuasar,'ALLWISE_catalog.dat'))
+
 ## NEOWISE-R
 if (choice != '7' and choice !='5'):
     NEOWISER =  ascii.read(os.path.join(path,inputQuasar,'NEOWISER-R_SingleExp_L1b.dat'))
-#WISE_W1 = ascii.read(path+'WISE_W1_LC.dat')
-#WISE_W2 = ascii.read(path+'WISE_W2_LC.dat')
-#WISE_L1bs = ascii.read(path+'J110057_l1b.tbl')
 
 
 ##  Assigned in WSA: 1=Z,2=Y,3=J,4=H,5=K,6=H2,7=Br,8=blank)
@@ -95,7 +96,10 @@ Ks_VIRCAM_30d = VSA_data_30d[(VSA_data_30d['filterID'] == 5) & (VSA_data_30d['ap
 
 ## For WISE, we adopt 2.699 and 3.339 as the conversions to AB from W1 and W2 Vega magnitudes,
 #if choice != '7' & choice !='5':
-if choice !='5':
+if choice == '3':
+    ALLWISE_W1_AB = ALLWISE['w1mpro'] + 2.699
+    ALLWISE_W2_AB = ALLWISE['w2mpro'] + 3.339
+if choice !='5':    
     NEOWISER_W1_AB = NEOWISER['w1mpro'] + 2.699
     NEOWISER_W2_AB = NEOWISER['w2mpro'] + 3.339
 
@@ -174,8 +178,16 @@ ax.errorbar(Ks_VIRCAM_30d['mjd'], Ks_VIRCAM_30d['aperMag3Ab'],  yerr=Ks_VIRCAM_3
             markeredgecolor ='black', markeredgewidth = markeredgewidth, fmt='h', label='VIRCAM Ks', color='yellow',    ms=ms*1.4)
 
 print('Creating plot, ...WISE labels...')
-if choice != '5' :
+
+if choice == '3':
+    ## ALLWISE  W1/W2
+    ms = 12.
[…]

### 2019-06-14 tex/VHzQ.tex
Minor change to filters listed in abstract

@@
 \begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties.
+We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($ZYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties.
 We find that SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample and that 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth for the objects that are not detected in the NIR.

### 2019-06-14 tables_for_paper/format_for_tables.py
tables_for_paper/output_table.tex

@@ -27,7 +27,7 @@ VHzQ_list = ascii.read(table)
 print(type(VHzQ_list['ra']))
 
 ## Just the top 10 for demo purposes in the .tex manuscript
-VHzQ_Top10 = VHzQ_list[0:10]
+VHzQ_Top10 = VHzQ_list[0:46]
 
 
 ## Set-up the table header

### 2019-06-14 tables_for_paper/format_for_tables.py
tables_for_paper/output_table.tex

@@ -32,12 +32,14 @@ VHzQ_Top10 = VHzQ_list[0:46]
 
 ## Set-up the table header
 header = """\\begin{table*}
-\\begin{tabular}{ccccc ccccc cccc}
-  \hline \hline
+\\begin{tabular}{llrrc ccccc cccc}
+  \hline
+  \hline
   survey   & qsoName &  ra  & dec & redshift  &  
   Z        & Y       &  J   &  H  &  K & 
-  W1       & W2      & W3   & W4 
-  \hline \hline
+  W1       & W2      & W3   & W4 \\\ 
+  \hline
+  \hline
   \\\\\n"""
 
 print(header)

### 2019-06-14 tex/VHzQ.tex
tables_for_paper/output_table.tex

@@
 \title[Infrared properties Very high-$z$ Quasars]
-  {Near and Mid-infrared properties of known $z\geq5$ Quasars}
+  {Near and Mid-infrared properties of known redshift $z\geq5$ Quasars}
 \author[Ross \& Cross]
@@
 The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.
+Critically, we also note that
 
@@
 effort, and we now exam the assembly of its contents in more detail.
+
 \begin{landscape}
@@
 \item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
+ \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
 \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 

### 2019-06-14 tex/VHzQ.tex
tables_for_paper/output_table.tex update

@@
 WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m. The all sky `ALLWISE' catalogue
+of 3.4, 4.6, 12, and 23$\mu$m. The all sky `AllWISE' catalogue
 release, contains nearly 750 million detections at
@@
 
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the ALLWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than ALLWISE (in W1/2).
+Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the AllWISE release.
+For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than AllWISE (in W1/2).
 This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
@@
 For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.
-For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.
+For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the AllWISE Data Release.
 Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}.
@@
 We thus use a cross-match radius of 2.75''.
-When querying the ALLWISE catalogues, ``Cone Search Radius'' in the ALLWISE table search was set to 2.75'' for the Spatial Constraints.
+When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE table search was set to 2.75'' for the Spatial Constraints.
 The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
@@
 
-Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table.
-However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection information.
+Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the AllWISE catalogues and also query the AllWISE Reject Table.
+However, with the exception of one object (SHELLQs  J1208-0200), the AllWISE Reject Table does not contain any further W3/W4 detection information.
 
@@
 
+We note that although we are often working close to the magnitude
+limits of the surveys, Eddington bias is not a significant effect on
+our measurements, since we are not discovering new sources, but
+measuring properties of already known quasars. Indeed in the NIR
+WFCAM/VISTA data, using forced photometry reducing the Eddington bias
+to negligible levels since a flux will be measured regardless of
+whether the source is just bright enough or too faint to be detected
+above the background noise.
+
   \subsubsection{Comparing WFCAM and VISTA}
@@
     \hline \hline
-    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
+    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{AllWISE}   \\ 
                                              & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
@@
 using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage}
-shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded
+shows the WISE AllWISE magnitude versus signal-to-noise, colour coded
 by {\tt w$x$cov} the mean coverage depth, in each corresponding
@@
 fact that there are non-detections in W3/4 for objects (with high W1/2
-SNR) that are reported in the ALLWISE catalogue.
+SNR) that are reported in the AllWISE catalogue.
 
@@
     \caption{Four of the brightest MIR VH$z$Qs. 
-      The thumbnails are the RGB colour outputs using the ALLWISE W1W2W3 bands from the 
+      The thumbnails are the RGB colour outputs using the AllWISE W1W2W3 bands from the 
       IRSA WISE Image Service, with a scale of 120'' on the side. 
@@
   {Histogram showing the total number of exposures for each detected VH$z$Q
-    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
+    from the full combination of AllWISE, NEOWISE and NEOWISE-R.} 
   \label{fig:MIR_LC_epochs}
@@
 \end{figure}
+One key point to note when looking at the WISE variability is 
+that AllWISE (and 2MASS) source information included in the NEOWISE Source Database 
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/expsup/sec2_1f.html}{are associations not identifications}. 
+The NEOWISE-AllWISE match radius is 3''.
+
 Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
@@
     \caption{The near infrared light curve for SDSS J0959+0227. Note, 
-      SDSS J0959+0227 is too faint in the MIR to be detected by ALLWISE or unnWISE.}
+      SDSS J0959+0227 is too faint in the MIR to be detected by AllWISE or unWISE.}
     \label{fig:SDSSJ0959+0227}

### 2019-06-14 tables_for_paper/format_for_tables.py

@@ -1,10 +1,7 @@
 ''' 
-# coding: utf-8
-
-# A simple little bit of code to convert the 
-# [W/V]SA_wWISE.dat files into nicely formatted .tex tables. 
-# v0.01    Thu May  9 12:57:29 BST 2019
-# 
+ A simple little bit of code to convert the 
+ [W/V]SA_wWISE.dat files into nicely formatted .tex tables. 
+ v0.01    Thu May  9 12:57:29 BST 2019
 '''
 
 import numpy as np
@@ -13,31 +10,29 @@ from astropy.io    import fits
 from astropy.io    import ascii
 from astropy.table import Table
 
-
 ##
 ##  V H z Q    data
 ##
-path     = '/cos_pc19a_npr/programs/quasars/highest_z/tables_for_paper/'
-filename = 'WSA_wWISE.dat'
-table    = path+filename
-
+path      = '/cos_pc19a_npr/programs/quasars/highest_z/tables_for_paper/'
+filename  = 'WSA_wWISE.dat'
+table     = path+filename
 VHzQ_list = ascii.read(table)
 
-
+print()
 print(type(VHzQ_list['ra']))
+print()
 
-## Just the top 10 for demo purposes in the .tex manuscript
-VHzQ_Top10 = VHzQ_list[0:46]
+## Just the top 10 or 5\% for demo purposes in the .tex manuscript
+VHzQ_Top10 = VHzQ_list[0:23]
 
 
 ## Set-up the table header
-header = """\\begin{table*}
+header = """\\begin{table}
 \\begin{tabular}{llrrc ccccc cccc}
-  \hline
-  \hline
-  survey   & qsoName &  ra  & dec & redshift  &  
-  Z        & Y       &  J   &  H  &  K & 
-  W1       & W2      & W3   & W4 \\\ 
+ \hline
+ \hline
+  \multirow{2}{*}{Survey} &  \multirow{2}{*}{QsoName} &   R.A. / deg  &   Decl. / deg  &  \multirow{2}{*}{redshift} & \multirow{2}{*}{Z}  &  \multirow{2}{*}{Y}  &  \multirow{2}{*}{J}   &  \multirow{2}{*}{H}  &  \multirow{2}{*}{K}     &  \multicolumn{2}{c}{unWISE}  &  \multicolumn{2}{c}{AllWISE} \\\ 
[…]

### 2019-06-14 tables_for_paper/format_for_tables.py
tables_for_paper/output_table_top5pc.tex

@@ -14,7 +14,8 @@ from astropy.table import Table
 ##  V H z Q    data
 ##
 path      = '/cos_pc19a_npr/programs/quasars/highest_z/tables_for_paper/'
-filename  = 'WSA_wWISE.dat'
+#filename  = 'WSA_wWISE.dat'
+filename   = 'VHzQs_ZYJHK_WISE.dat' 
 table     = path+filename
 VHzQ_list = ascii.read(table)
 
@@ -28,16 +29,17 @@ VHzQ_Top10 = VHzQ_list[0:23]
 
 ## Set-up the table header
 header = """\\begin{table}
-\\begin{tabular}{llrrc ccccc cccc}
+\\begin{tabular}{llrrc cccc cccc}
  \hline
  \hline
-  \multirow{2}{*}{Survey} &  \multirow{2}{*}{QsoName} &   R.A. / deg  &   Decl. / deg  &  \multirow{2}{*}{redshift} & \multirow{2}{*}{Z}  &  \multirow{2}{*}{Y}  &  \multirow{2}{*}{J}   &  \multirow{2}{*}{H}  &  \multirow{2}{*}{K}     &  \multicolumn{2}{c}{unWISE}  &  \multicolumn{2}{c}{AllWISE} \\\ 
-                                     &                                            &   (J2000)       &  (J2000)         &                                        &                              &                               &                                &                                &                                  &                    W1       & W2        & W3   & W4 \\\ 
+  \multirow{2}{*}{Survey} &  \multirow{2}{*}{QsoName} &   R.A. / deg  &   Decl. / deg  &  \multirow{2}{*}{redshift}   &  \multirow{2}{*}{Y}  &  \multirow{2}{*}{J}   &  \multirow{2}{*}{H}  &  \multirow{2}{*}{K}     &  \multicolumn{2}{c}{unWISE}  &  \multicolumn{2}{c}{AllWISE} \\\ 
+                          &                           &   (J2000)     &  (J2000)       &                              &                      &                       &                      &                         &          W1       & W2       & W3   & W4 \\\ 
   \hline
   \hline
[…]

### 2019-06-14 tables_for_paper/format_for_tables.py
tables_for_paper/output_table_top5pc.tex

@@ -45,7 +45,10 @@ print(header)
 footer = """    \hline
     \hline
     \\end{tabular}
-    \caption{The first 23 (i.e. 5\%) of 463 very high-$z$ quasars with near and mid-infrared photometry.}
+    \caption{The first 23 (i.e. 5\%) of 463 very high-$z$ quasars in Right Ascension order with near and mid-infrared photometry. 
+                  The full table can be found \href{https://github.com/d80b2t/VHzQ/tree/master/data}{here}. 
+                  Since none of the first 23 objects have $Z$-band detections, we don't report that column here (but
+                  is reported in the main table).} 
      \label{tab:output_table}
      \\end{table}
      \n"""

### 2019-06-14 data/light_curves/NEOWISE-R/average_NEOWISE_lightcurves.py
Added code and data for NEOWISE averaged light-curves

@@ -1,0 +1,95 @@
+#! /usr/bin/env python
+#------------------------------------------------------------------------------
+# $Id: average_NEOWISE_lightcurves.py 11588 2017-02-12 21:38:25Z NicholasCross $
+"""
+   
+
+
+   @author: N.J.G.. Cross
+   @org:    WFAU, IfA, University of Edinburgh
+"""
+#------------------------------------------------------------------------------
+from __future__      import division, print_function
+from   operator             import attrgetter, itemgetter
+from   itertools            import groupby
+
+import math
+import os
+import sys
+import numpy
+from astropy.io import fits, ascii
+from astropy.table    import Table
+
+def getMjdRanges(mjdData):
+    """ Looks for groups of data separated by about 6 months, over a few days
+    """
+    startMjd=mjdData[0]
+    mjdGroupList=[]
+    mjdGroup=[]
+    for mjd in mjdData:
+        if mjd<startMjd+20.:
+            mjdGroup.append(mjd)
+        elif mjd>startMjd+130.:
+            startMjd=mjd
+            # calc stats
+            minMjd=min(mjdGroup)
+            maxMjd=max(mjdGroup)
+            meanMjd=numpy.mean(mjdGroup)
+            mjdGroupList.append((minMjd,meanMjd,maxMjd,len(mjdGroup)))
+            mjdGroup=[mjd]
+        else:
+            print("mjd does not fall in group, nor start new group: ",mjd,startMjd)
+    return mjdGroupList
+    
+
+
+inputTable = sys.argv[1]
+
+data= Table.read(inputTable, format='ipac')
+default_value = -999.999
+# Useful columns: cntr_01,ra,dec,w1mpro,w1sigmpro,w1snr,w2mpro,w2sigmpro,w2snr,cc_flags,mjd
+
+
+sourceIDs=sorted(list(set(data['cntr_01'])))
+outputDataList=[]
+for srcID in sourceIDs:
+    srcDataMask=numpy.nonzero(data['cntr_01']==srcID)
+    ra,dec=data['ra_01'][srcDataMask][0],data['dec_01'][srcDataMask][0]
+    mjdData= sorted(data['mjd'][srcDataMask])
+    # Group mjd values.
+    mjdRanges = getMjdRanges(mjdData) # min,mean,max
+    # Now select data for each range and average:
[…]

### 2019-06-14 tex/VHzQ.tex
tables_for_paper/output_table_top5pc.tex

@@
 Figure~\ref{fig:coverage} shows the areal coverage of the ULAS, UHS,
-VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR11
-3,700 deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
+VHS and VIKING. UHS DR1 is 12,600 deg$^{2}$ ($J$-band); ULAS DR1 3,700
+deg$^{2}$ VHS DR6 16,000 deg$^{2}$ and VIKING DR5 is 1,300
 deg$^{2}$. The overlap between UHS DR1 and VHS DR6 is 28 deg. These
-four surveys together cover 33,000 deg$^{2}$.
+four surveys together cover 33,000 deg$^{2}$. VHS, ULAS and UHS do not
+observe in the $Z$-band.
 
@@
 \begin{landscape}
-      \input{../tables_for_paper/output_table}
+      \input{../tables_for_paper/output_table_top5pc}
 \end{landscape}

### 2019-06-14 tex/VHzQ.tex
tex/VHzQ.tex

@@
 
+\citet{Secrest2015} present an all-sky sample of $\approx$1.35 million active galactic nuclei (AGNs) 
+meeting a two-color infrared photometric selection criteria for AGNs as applied to sources from the Wide-field Infrared Survey Explorer final catalog release (AllWISE) 
 Recently, \citet{Assef2018} released two large catalogues of AGN

### 2019-06-14 tex/VHzQ.tex
moved average_NEOWISE_lightcurves.py
tex/VHzQ.pdf final Friday evening push...

--- 2019-06-14 tex/VHzQ.tex
@@
 
+\citet{Secrest2015} present an all-sky sample of $\approx$1.35 million active galactic nuclei (AGNs) 
+meeting a two-color, (W1-W2) vs. (W2-W3) infrared photometric selection criteria for AGNs as applied to sources from the Wide-field Infrared Survey Explorer final catalog release (AllWISE). 
+%%
 Recently, \citet{Assef2018} released two large catalogues of AGN
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{SurfaceDensity}
+%\input{SurfaceDensity}
 
@@
 $z>5$ spectroscopically confirmed quasars. We have assembled the NIR
-($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
-objects, given their detection rates and SEDs. We find that:
+($Z, Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
+objects and given their detection rates. We find that:
 
@@
     \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
-   \item 362 ( 78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
+   \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 

### 2019-06-14 tex/VHzQ.tex
detections/ dir BIG clean-up

@@
 \title[Infrared properties Very high-$z$ Quasars]
-  {Near and Mid-infrared properties of known redshift $z\geq5$ Quasars}
+  {The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars}
 \author[Ross \& Cross]
-%\author[N. Ross, N. Cross \& C. Ross]
 {Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk} and Nicholas J. G. Cross \\ 
-%{Nicholas P. Ross\thanks{E-mail: npross@roe.ac.uk}, Nicholas J. G. Cross and Christine B. Ross \\ 
 Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh, EH9 3HJ, United Kingdom\\ }
@@
 \begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($ZYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties.
-We find that SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample and that 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth for the objects that are not detected in the NIR.
-362 (78.2\%) VH$z$Qs are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all of the $z\geq7$ quasars are detected in both unWISE W1 and W2.
-Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability in the near-infrared that might be expected from super-Eddington accretion.
-We find 32 of the quasars have sufficient NIR measurements and signal-to-noise to look for variability.
-Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529.
-Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band.
-%% 
-%% Extrapolating the known quasar luminosity function we suggest that
-%% $x$\% of the possibly detected $z\geq5$ quasars in the current
-%% datasets have been discovered.
-All the data, analysis codes and plots used and generated here can be
+We assemble a catalogue of 463 spectroscopically confirmed very high
+($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}$ and
+$K$) and mid- (WISE) infrared properties. We find that SDSS and
+Pan-STARRS1 together identified over half of the VH$z$Q sample and
+that 97.0\% of the VH$z$Q sample is detected in one or more NIR
+($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth
+for the objects that are not detected in the NIR. 362 (78.2\%) VH$z$Qs
+are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and
+all of the $z\geq7$ quasars are detected in both unWISE W1 and
+W2. Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for
+photometric variability in the near-infrared that might be expected
+from super-Eddington accretion. We find 32 of the quasars have
+sufficient NIR measurements and signal-to-noise to look for
+variability. Weak variability was detected in multiple bands of SDSS
+J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529. Two
+other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant
+differences between their WFCAM and VISTA magnitudes in one band. All
+the data, analysis codes and plots used and generated here can be
 found at: \href{https://github.com/d80b2t/VHzQ}{\tt
@@
 
-Critically, we now have available to us new W1 and W2 photometry from the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected catalogue that is based on significantly deeper imaging and has a more extensive modeling of crowded regions than the AllWISE release.
-For the first time in a catalogue, unWISE takes advantage of the ongoing mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves depths $\sim$0.7 mag deeper than AllWISE (in W1/2).
-This additional depth is a significant advantage in the detection and study of VH$z$Qs in the 3-5 micron regime.
-
-Here we present for the first time the combined near-infrared properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
-all the spectroscopically known $z\geq5.00$ quasars. Our motivations are numerous and include: {\it (i)} establishing the first complete
-catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
-available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g.
-luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.
+Critically, we now have available to us new W1 and W2 photometry from
+the `unWISE Source Catalog' \citep[][]{Schlafly2019}, a WISE-selected
+catalogue that is based on significantly deeper imaging and has a more
+extensive modeling of crowded regions than the AllWISE release. For
+the first time in a catalogue, unWISE takes advantage of the ongoing
+mid-IR Near-Earth Object Wide-Field Infrared Survey Explorer
+Reactivation mission \citep[NEOWISE-R; ][]{Mainzer2014}, and achieves
+depths $\sim$0.7 mag deeper than AllWISE (in W1/2).  This additional
+depth is a significant advantage in the detection and study of VH$z$Qs
+in the 3-5 micron regime.
+
+Here we present for the first time the combined near-infrared
+properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
+all the spectroscopically known $z\geq5.00$ quasars. Our motivations
+are numerous and include: {\it (i)} establishing the first complete
+catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
+{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
+available for the quasars; {\it (iii)} making the first study of near-
+and mid-IR variability of the VHzQ population and {\it (iv)}
+establishing the photometric properties for upcoming surveys and
+telescopes including the Large Synoptic Survey Telescope
+(LSST)\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it
+Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};}
+and the {\it James Webb Space Telescope}
+(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}.
+We
+chose redshift $z=5.00$ as our lower redshift limit due to a
+combination of garnishing a large sample, adequately spanning physical
+properties (e.g. luminosity, age of the Universe) and to highlight the
+parts of $L-z$ parameter space where $z>5$ quasars still wait to be
+discovered.
 
@@
   \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {../Nofz/Nofz_0pnt075bins_20181211.png}
+  {../Nofz/Nofz_0pnt075bins_20190614.pdf}
   \centering
@@
 The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.
-Critically, we also note that
 
@@
 \end{eqnarray*}
-For the our MIR variability investigations, we do not use the unWISE
-coadds, but instead use the
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
-catalogue and the NEOWISE
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{2019 Data
-Release}. NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2)
-single-exposure images and extracted source information that was
-acquired up until 2018 December 13 (MJD 58465) including the fifth
-year of survey operations of NEOWISE. These fifth year NEOWISE data
-products are concatenated with those from the first four years into a
-single archive from 2013 December 13 (MJD 56639).
-
-The WISE scan pattern leads to coverage of the full-sky approximately
-once every six months (a``sky pass''), but the satellite was placed in
-hibernation in 2011 February and then reactivated in 2013
-October. Hence, our light curves have a cadence of 6 months with a 32
-month sampling gap.
-
-Table~\ref{tab:output_table} represents the culmination of this
-effort, and we now exam the assembly of its contents in more detail.
-
+
+For the our MIR variability investigations, we use the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{NEOWISE-R 2019 Data Release}.
+NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was
+acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE. These fifth year NEOWISE data
+products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
+
+The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in
+hibernation in 2011 February and then reactivated in 2013 October. Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% 
+%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
+%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
+%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{landscape}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% 
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%     S E C T I O  N   3         S E C T I O  N   3           S E C T I O  N   3       S E C T I O  N   3
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 properties of the quasars.
+%%
+Table~\ref{tab:output_table} represents the culmination of this
+effort, {\it is the main
+\href{https://github.com/d80b2t/VHzQ/blob/master/data/VHzQs_ZYJHK_WISE.dat}{data
+product} of this paper} and we now exam the assembly of its contents
+in more detail.
 
 First, we will concentrate on detection rate in the infrared, go on to
-report on the colour-redshift and colour-colour properties of our sample
-and then report on how the current sample populates the
-luminosity-redshift $Lz$-plane.
+report on the colour-redshift and colour-colour properties of our sample. 
+We also investigate the photometric variability.
 
@@
 measuring properties of already known quasars. Indeed in the NIR
-WFCAM/VISTA data, using forced photometry reducing the Eddington bias
+WFCAM/VISTA data, using forced photometry reduces the Eddington bias
 to negligible levels since a flux will be measured regardless of
-whether the source is just bright enough or too faint to be detected
+whether the source is just bright enough (or too faint) to be detected
 above the background noise.
@@
       for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
-      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
+      400,000 quasars at redshift $z\lesssim3.0$ from the SDSS DR14 quasar catalogue 
+      \citep{Paris2019} are also shown
       (grey colour-scale). }
@@
 several investigations have looked at how WISE detects AGN 
-\citet[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
+\citep[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
 
@@
 Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs.
-(W2-W3) colour – colour space diagram showing the WISE colours for the 283 VH$z$Q that have reported {\tt w3mpro} values (blue to red coloured points), though we note that only 51(18\%) of these objects have {\tt w3snr} > 3.0.
-objects  400,000 quasars
-at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
-colour-scale). 
+(W2-W3) colour-colour diagram for the 283 VH$z$Qs that have reported {\tt w3mpro} values (blue to red coloured points), though we note that only 51 (18\%) of these objects have {\tt w3snr} $>$3.0.
+Approximately 400,000 quasars at redshift $z\lesssim3.0$ from the SDSS Quasar Catalog using the Fourteenth data release
+\citep[DR14Q; ][]{Paris2018} are also shown (grey colour-scale). 
 % W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
@@
 %% N.P.R. may have listened to Kris Kross during the preparation of this manuscript. 
+%% N.P.R also thanks C. B. Ross. \\
 

### 2019-06-14 Nofz/Nofz.py

@@ -57,7 +57,7 @@ colors = [ cmap(0/clrlevs),  cmap(1/clrlevs),  cmap(2/clrlevs), cmap(3/clrlevs),
            cmap(6/clrlevs),  cmap(7/clrlevs),  cmap(8/clrlevs), cmap(9/clrlevs)]
     
 ## Setting up the plot
-fig, ax = plt.subplots(figsize=(5, 3), dpi=80, facecolor='w', edgecolor='k')
+fig, ax = plt.subplots(figsize=(5, 3), dpi=280, facecolor='w', edgecolor='k')
 
 ## Adjusting the Whitespace for the plots
 left   = 0.18   # the left side of the subplots of the figure
@@ -128,6 +128,7 @@ ax.tick_params(axis='both', which='major', labelsize=labelsize, top=True, right=
 ax.tick_params(axis='both', which='minor', labelsize=labelsize, top=True, right=True, direction='in', length=ticklength/2, width=tickwidth)
 
 
-plt.savefig('Nofz_temp.png', format='png')
+#plt.savefig('Nofz_temp.png', format='png')
+plt.savefig('Nofz_temp.pdf', format='pdf')
 plt.close(fig)
 

### 2019-06-14 color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots.py

@@ -43,6 +43,8 @@ VHzQ_full = ascii.read(table)
 #VHzQ = VHzQ_full
 VHzQ = VHzQ_full[np.where(VHzQ_full['w3snr'] >3.0)]
 
+## Selec
+he = VHzQ_full[np.where((VHzQ_full['unW1mag'] >0.0) &  (VHzQ_full['unW2mag'] >0.0)) ]
 
 
 ##  Making the plot(s)

### 2019-06-14 tex/VHzQ.tex
color_color/W1W2_plots/W1W2W3_colors.py

@@
 
-\citet{Secrest2015} present an all-sky sample of $\approx$1.35 million active galactic nuclei (AGNs) 
-meeting a two-color, (W1-W2) vs. (W2-W3) infrared photometric selection criteria for AGNs as applied to sources from the Wide-field Infrared Survey Explorer final catalog release (AllWISE). 
-%%
-Recently, \citet{Assef2018} released two large catalogues of AGN
+\citet{Secrest2015} present an all-sky sample of $\approx$1.35 million
+AGN meeting a two-color, (W1-W2) vs. (W2-W3), photometric selection as
+applied to sources from AllWISE. This colour-selection is motivated by
+\citet{Mateos2012}. We investigate if this catalogue, which is tuned
+for, and noted to be highly complete at, lower, $z\lesssim2$
+redshifts, contain the VH$z$Qs. We find only 5 VH$z$Qs from our sample
+match the Secrest catalogue, but given a W3 detection is required,
+this is not surprising. Further, in addition to the relative lack of
+sensitivity in W3, the mid-IR colors are moving out of the
+\citet{Mateos2012} color criterion at high redshift. This was shown
+using an AGN SED where AGNs above a redshift of about $\sim$2 fall out
+of the colour criterion, see e.g. Figure 5 of \citet[][]{Mateos2012}
+and Figure 9 of \citet{Secrest2015}.
+%%
+\citet{Assef2018} released two large catalogues of AGN
 candidates identified across 30,000 deg$^2$ of extragalactic sky from
@@
       400,000 quasars at redshift $z\lesssim3.0$ from the SDSS DR14 quasar catalogue 
-      \citep{Paris2019} are also shown
+      \citep{Paris2018} are also shown
       (grey colour-scale). }
@@
 \citep[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
-
-The VH$z$Q with the bluest colour in (W1 - W2) is 
-DELS J1048-0109 with (W1-W2) = 0.154. 
-%(see Figure~\ref{fig:DELS_J1048}).
 
@@
 \end{figure*}
+The VH$z$Q with the bluest colour in (W1 - W2) is 
+DELS J1048-0109 with (W1-W2) = 0.154. 
+%(see Figure~\ref{fig:DELS_J1048}).
+
 The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
@@
 %%
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\input{SurfaceDensity}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
 %%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
@@
   \item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
+  \item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
   \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
   \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
-\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
   \item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
+  \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
 \end{list}

### 2019-06-14 color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots.py

@@ -43,9 +43,6 @@ VHzQ_full = ascii.read(table)
 #VHzQ = VHzQ_full
 VHzQ = VHzQ_full[np.where(VHzQ_full['w3snr'] >3.0)]
 
-## Selec
-he = VHzQ_full[np.where((VHzQ_full['unW1mag'] >0.0) &  (VHzQ_full['unW2mag'] >0.0)) ]
-
 
 ##  Making the plot(s)
 ## 

### 2019-06-14 color_color/W1W2_plots/W1W2W3_colors.py

@@ -1,0 +1,43 @@
+'''
+Just some simple W1/2/3 VHzQ numbers
+'''
+
+import numpy as np
+from astropy.io    import ascii
+
+## Read-in the data
+path      = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
+filename  = 'VHzQs_ZYJHK_WISE.dat'
+table     = path+filename
+VHzQ_full = ascii.read(table)
+
+## Selections...
+W3_goodSNR   = VHzQ_full[np.where( VHzQ_full['w3snr']   > 3.0)]
+W1andW2      = VHzQ_full[np.where((VHzQ_full['unW1mag'] > 0.0)  &  (VHzQ_full['unW2mag'] >0.0)) ]
+
+
+bluest_W1andW2  = W1andW2[np.where((W1andW2['unW1mag']-W1andW2['unW2mag'])  ==
+                                   (W1andW2['unW1mag']-W1andW2['unW2mag']).min())]
+
+reddest_W1andW2 = W1andW2[np.where((W1andW2['unW1mag']-W1andW2['unW2mag'])  ==
+                                   (W1andW2['unW1mag']-W1andW2['unW2mag']).max())]
+
+print()
+print('Number of objects with good (>0.0) unW1mag and unW2mag: ', len(W1andW2))
+print('    of which ',  bluest_W1andW2['na'][0],  bluest_W1andW2['desig'][0], '    is the bluest with (W1-W2) =  ', bluest_W1andW2['unW1mag'][0]-bluest_W1andW2['unW2mag'][0] )
+print('    of which ', reddest_W1andW2['na'][0], reddest_W1andW2['desig'][0], ' is the reddest with (W1-W2) =  ',   reddest_W1andW2['unW1mag'][0]-reddest_W1andW2['unW2mag'][0] )
+print()
+
+
+### GOOD 
+bluest_W1andW3  = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
+                                      (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).min())]
+
+reddest_W1andW3 = W3_goodSNR[np.where( (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
+                                        (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).max())]
+
+print()
[…]

### 2019-06-14 tex/VHzQ.tex
color_color/W1W2_plots/W1W2W3_colors.py update

@@
 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant
-differences between their WFCAM and VISTA magnitudes in one band. All
-the data, analysis codes and plots used and generated here can be
+differences between their WFCAM and VISTA magnitudes in one band. 
+With supermassive black hole accretion likely to be redshift invariant 
+up to very high-redshift, further monitoring of these sources is warranted. 
+All the data, analysis codes and plots used and generated here can be
 found at: \href{https://github.com/d80b2t/VHzQ}{\tt
@@
 \subsection{MIR Colours}
-Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
-several investigations have looked at how WISE detects AGN 
-\citep[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}
-
-Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs.
-(W2-W3) colour-colour diagram for the 283 VH$z$Qs that have reported {\tt w3mpro} values (blue to red coloured points), though we note that only 51 (18\%) of these objects have {\tt w3snr} $>$3.0.
-Approximately 400,000 quasars at redshift $z\lesssim3.0$ from the SDSS Quasar Catalog using the Fourteenth data release
-\citep[DR14Q; ][]{Paris2018} are also shown (grey colour-scale). 
+Due to the depth all-sky coverage of the WISE (and NEOWISE-(R))
+mission, several investigations have looked at how WISE detects AGN
+\citep[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017,
+Assef2018, Glikman2018, Hviding2018, LaMassa2019}
+
+Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour-colour
+diagram for the 283 VH$z$Qs that have reported {\tt w3mpro} values
+(blue to red coloured points), though we note that only 51 (18\%) of
+these objects have {\tt w3snr} $>$3.0. Approximately 400,000 quasars
+at redshift $z\lesssim3.0$ from the SDSS Quasar Catalog using the
+Fourteenth data release \citep[DR14Q; ][]{Paris2018} are also shown
+(grey colour-scale).
 % W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
@@
 \end{figure*}
-The VH$z$Q with the bluest colour in (W1 - W2) is 
-DELS J1048-0109 with (W1-W2) = 0.154. 
-%(see Figure~\ref{fig:DELS_J1048}).
+The VH$z$Q with the bluest colour in (W1-W2) is DELS J1048-0109 with (W1-W2) = 0.154. 
+and the reddest object in (W1-W2) is SHELLQs J2223+0326  with (W1-W2) =  1.33.
 
@@
 detected in the broad W3 filter and 10 objects that are formally detected
-in W4 ({\tt w4snr}$\geq$3.0). Four of the brightest W4 objects are
-presented in \label{fig:VHzQ_W4s}. UHS J0439+1634
-(Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
+in W4 ({\tt w4snr}$\geq$3.0). 
+%%
+Four of the W3/4 objects are presented in \label{fig:VHzQ_W4s}. 
+UHS J0439+1634 (Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
 \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
 luminosity is mostly not intrinsic, but is boosted by an intervening
-redshift $z\sim$0.7 galaxy. SDSS J0100+2802 (redshift $z=6.33$) does
-not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
-but as reported by \citet{Wu2015}, has a bright detection in the
-2MASS $J$, $H$ and $K_{\rm s}$ bands and we report it here.
-%%
+redshift $z\sim$0.7 galaxy. 
 Other high-redshift quasars that are bright W3/4 objects may well 
@@
 but high-resolution follow-up is needed to confirm. 
+%%
+SDSS J0100+2802 (redshift $z=6.33$) does
+not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
+but as reported by \citet{Wu2015}, has a bright detection in the
+2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object 
+in both (W1-W3) and (W2-W3) with values of 2.73 and 1.93, respectively, 
+so we report it here.
+%%
+PSO J075.9356-07.5061 is the reddest W3 detected object with (W1-W3) =
+5.31 and (W2-W3)= 4.65.
 
@@
 time-dilation dramatically affects the sampled rest-frame timescales
-sampled, which are $\sim300-700$ days. Indeed, when sharp changes in a accretion rate are expected
-on the system's dynamical timescale of several kiloyears
-\citep[e.g.,][]{Regan2019}, then seeing any variability signature is
-not expected. However, noting how in lower redshift quasars, which
-also have massive $>10^{8}$ M$_{\odot}$ black holes, dramatic changes
-in both continuum and line emission {\it is seen} on much shorter
-timescales, continued monitoring of these objects is warranted.
+sampled, which are $\sim$300-700 days. Indeed, when sharp changes in a
+accretion rate are expected on the system's dynamical timescale of
+several kiloyears \citep[e.g.,][]{Regan2019}, then seeing any
+variability signature is not expected. However, noting that {\it (i)} accretion onto 
+supermassive black holes should be generally time invariant, and {\it (ii)} 
+that in lower redshift quasars, which also have massive $>$$10^{8}$ M$_{\odot}$ black
+holes, dramatic changes in both continuum and line emission {\it is
+seen} on much shorter timescales, continued monitoring of these
+objects is definitely warranted.
 

### 2019-06-14 color_color/W1W2_plots/W1W2W3_colors.py

@@ -32,12 +32,24 @@ print()
 ### GOOD 
 bluest_W1andW3  = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
                                       (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).min())]
+reddest_W1andW3 = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
+                                      (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).max())]
 
-reddest_W1andW3 = W3_goodSNR[np.where( (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
-                                        (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).max())]
+
+bluest_W2andW3 = W3_goodSNR[np.where((W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
+                                     (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).min())]
+
+reddest_W2andW3 = W3_goodSNR[np.where((W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
+                                      (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).max())]
 
 print()
 print('Number of objects with good (>3.0) W3 SNR : ', len(W3_goodSNR))
-print('    of which ',  bluest_W1andW2['na'][0],  bluest_W1andW2['desig'][0], '    is the bluest with (W1-W2) =  ', bluest_W1andW2['unW1mag'][0]-bluest_W1andW2['unW2mag'][0] )
-print('    of which ', reddest_W1andW2['na'][0], reddest_W1andW2['desig'][0], ' is the reddest with (W1-W2) =  ',   reddest_W1andW2['unW1mag'][0]-reddest_W1andW2['unW2mag'][0] )
+print('    of which ',  bluest_W1andW3['na'][0],  bluest_W1andW3['desig'][0], '    is the bluest with (W1-W3) =  ', bluest_W1andW3['unW1mag'][0]  - bluest_W1andW3['w3mpro'][0] )
[…]

### 2019-06-14 tex/VHzQ.tex
So friggin nearly there...

@@
 We assemble a catalogue of 463 spectroscopically confirmed very high
-($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}$ and
-$K$) and mid- (WISE) infrared properties. We find that SDSS and
-Pan-STARRS1 together identified over half of the VH$z$Q sample and
-that 97.0\% of the VH$z$Q sample is detected in one or more NIR
-($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth
-for the objects that are not detected in the NIR. 362 (78.2\%) VH$z$Qs
-are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and
-all of the $z\geq7$ quasars are detected in both unWISE W1 and
-W2. Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for
-photometric variability in the near-infrared that might be expected
-from super-Eddington accretion. We find 32 of the quasars have
-sufficient NIR measurements and signal-to-noise to look for
-variability. Weak variability was detected in multiple bands of SDSS
-J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529. Two
-other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant
-differences between their WFCAM and VISTA magnitudes in one band. 
-With supermassive black hole accretion likely to be redshift invariant 
-up to very high-redshift, further monitoring of these sources is warranted. 
-All the data, analysis codes and plots used and generated here can be
-found at: \href{https://github.com/d80b2t/VHzQ}{\tt
-github.com/d80b2t/VHzQ}.
+($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
+and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
+is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
+coverage rather than lack of depth being the reason for the
+non-detections. 362 (78\%) of the very high redshift quasars are
+detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
+of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
+archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
+variability that might be expected from super-Eddington accretion. We
+find 32 of the quasars have sufficient NIR measurements and
+signal-to-noise to look for variability. Weak variability was detected
+in multiple bands of SDSS J0959+0227, and very marginally in the
+$Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and
+SDSS J2220-0101 had significant differences between their WFCAM and
+VISTA magnitudes in one band.  With supermassive black hole accretion
+likely to be redshift invariant up to very high-redshift, further
+monitoring of these sources is warranted.  All the data, analysis
+codes and plots used and generated here can be found at:
+\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
 \end{abstract}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
+    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
+  \vspace{-14pt}
+    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
+      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
+      400,000 quasars at redshift $z\lesssim3.0$ from the SDSS DR14 quasar catalogue 
+      \citep{Paris2018} are also shown
+      (grey colour-scale). }
+    \label{fig:W1W2W3}
+\end{figure}
+
 \citet{Secrest2015} present an all-sky sample of $\approx$1.35 million
@@
 per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
-candidates at 75\% completeness (and ($\approx$700 AGN candidates per
+candidates at 75\% completeness (and $\approx$700 AGN candidates per
 deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
@@
 not the R90 catalogue matches to the first redshift $z>7$ quasar ULAS
-J1120+0641 \citep{Mortlock2011}. Neither catalogue matches to the
+J1120+0641 \citep{Mortlock2011}. Neither the R90 or C75 catalogue matches to the
 current highest-redshift object J1342+0928 \citep{Banados2018}.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
-  \vspace{-14pt}
-    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
-      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
-      400,000 quasars at redshift $z\lesssim3.0$ from the SDSS DR14 quasar catalogue 
-      \citep{Paris2018} are also shown
-      (grey colour-scale). }
-    \label{fig:W1W2W3}
-\end{figure}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/DELS_J1048-0109.png} 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDWISE_J0306+1853.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
+    \caption{VH$z$Qs with interesting MIR properties. 
+      The thumbnails are the RGB colour outputs using the AllWISE W1W2W3 bands from the 
+      IRSA WISE Image Service, with a scale of 120'' on the side. 
+      {\it (a)} DELS J1048-0109 is the bluest in (W1-W2) colour quasar. 
+      {\it (b)} UHS J0439+1634 was discovered by \citet{Fan2019} and is a strongly lensed quasar at $z=6.51$. 
+      {\it (c)} SDWISE J0306+1853 has {\tt w3mpro} = $10.51\pm0.1$ and {\tt w4mpro } = $7.586\pm0.16$. 
+      {\it (d)} SDSS J0100+2802 is the \citet{Wu2015} object.  
+%      {\it (d)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
+  %    {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).
+}
+    \label{fig:VHzQ_W4s}
+\end{figure*}
 \subsection{MIR Colours}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
-    \caption{Four of the brightest MIR VH$z$Qs. 
-      The thumbnails are the RGB colour outputs using the AllWISE W1W2W3 bands from the 
-      IRSA WISE Image Service, with a scale of 120'' on the side. 
-      {\it (a)} UHS J0439+1634 was discovered by
-      \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. 
-      {\it (b)} SDSS J0100+2802 is the \citet{Wu2015} object. 
-      {\it (c)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
-      {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).}
-    \label{fig:VHzQ_W4s}
-\end{figure*}
-The VH$z$Q with the bluest colour in (W1-W2) is DELS J1048-0109 with (W1-W2) = 0.154. 
-and the reddest object in (W1-W2) is SHELLQs J2223+0326  with (W1-W2) =  1.33.
-
-The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are
-detected in the broad W3 filter and 10 objects that are formally detected
-in W4 ({\tt w4snr}$\geq$3.0). 
-%%
-Four of the W3/4 objects are presented in \label{fig:VHzQ_W4s}. 
-UHS J0439+1634 (Fig.~\ref{fig:VHzQ_W4s} (a)) with W4=7.165$\pm$0.12 was discovered by
-\citet{Fan2019} and is a strongly lensed quasar at $z=$6.51. This high
-luminosity is mostly not intrinsic, but is boosted by an intervening
-redshift $z\sim$0.7 galaxy. 
-Other high-redshift quasars that are bright W3/4 objects may well 
-also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, 
-but high-resolution follow-up is needed to confirm. 
-%%
-SDSS J0100+2802 (redshift $z=6.33$) does
-not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4),
-but as reported by \citet{Wu2015}, has a bright detection in the
-2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object 
-in both (W1-W3) and (W2-W3) with values of 2.73 and 1.93, respectively, 
-so we report it here.
-%%
-PSO J075.9356-07.5061 is the reddest W3 detected object with (W1-W3) =
-5.31 and (W2-W3)= 4.65.
+The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with (W1-W2) = 0.154, and the WISE W1W2W3 color image is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}.
+The reddest object in (W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 1.33.
+
+The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are detected in the broad W3 filter and 10 objects that are formally detected in W4 ({\tt w4snr}$\geq$3.0).
+Three of the W3/4 objects are presented in Figure~\ref{fig:VHzQ_W4s}.
+UHS~J0439+1634 (Fig.~\ref{fig:VHzQ_W4s} {\it (b)}) with W4=7.165$\pm$0.12 was discovered by \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51.
+This high luminosity is mostly not intrinsic, but is boosted by an intervening redshift $z\sim$0.7 galaxy.
+Other high-redshift quasars that are bright W3/4 objects e.g.
+SDWISE~J0306+1853 (Fig.~\ref{fig:VHzQ_W4s} {\it(c)}) may well also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, but high-resolution follow-up is needed to confirm.
+SDSS~J0100+2802 (redshift $z=6.33$) does not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4), but as reported by \citet{Wu2015}, has a detection in the 2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object in both (W1-W3) and (W2-W3) with values of 2.73 and 1.93, respectively, and is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(d)}.
 
@@
 \end{figure}
-One key point to note when looking at the WISE variability is 
-that AllWISE (and 2MASS) source information included in the NEOWISE Source Database 
-\href{http://wise2.ipac.caltech.edu/docs/release/neowise/expsup/sec2_1f.html}{are associations not identifications}. 
-The NEOWISE-AllWISE match radius is 3''.
-
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs
-and detections there are for each VH$z$Q, while
-Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR
-lightcurves and associated colour changes. Here we show J0100+2802
-\citep{Wu2015}, J0224-4711 and J1626+2751.
+One key point to note when looking at the WISE variability is that
+AllWISE (and 2MASS) source information included in the NEOWISE Source
+Database
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/expsup/sec2_1f.html}{are
+associations not identifications}. The NEOWISE-AllWISE match radius is
+3''.
+
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes.
+Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and J1626+2751.
 

### 2019-06-14 color_color/W1W2_plots/W1W2W3_colors.py

@@ -32,13 +32,16 @@ print()
 ### GOOD 
 bluest_W1andW3  = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
                                       (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).min())]
-reddest_W1andW3 = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
-                                      (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).max())]
-
 
 bluest_W2andW3 = W3_goodSNR[np.where((W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
                                      (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).min())]
 
+###  Argh!!!!!
+###  TAKE GREAT CARE!!
+###    PSO J075.9356-07.5061
+### 
+reddest_W1andW3 = W3_goodSNR[np.where((W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro'])  ==
+                                      (W3_goodSNR['unW1mag']-W3_goodSNR['w3mpro']).max())]
 reddest_W2andW3 = W3_goodSNR[np.where((W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro'])  ==
                                       (W3_goodSNR['unW2mag']-W3_goodSNR['w3mpro']).max())]
 
@@ -52,4 +55,4 @@ print('    of which ', reddest_W2andW3['na'][0], reddest_W2andW3['desig'][0], ' 
 print()
 
 ## bluest (W1-W3) and (W2-W3)::    SDSS J0100+2802 15.0542635 28.040532     6.33
-## reddes (W1-W3) and (W2-W3):: PSO J075.9356-07.5061 
+## reddest (W1-W3) and (W2-W3):: PSO J075.9356-07.5061 

### 2019-06-15 tex/VHzQ.tex
Massive update to color_color/W1W2_plots; light_curves/MIR_LCs; tables_for_paper and the .tex

@@
 
-We present all our photometry and magnitudes on the AB zero-point
-system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
-near-infrared, as well as the mid-infrared magnitudes. These
-magnitudes are {\it not} Galactic extinction corrected. We use a flat
+We present all our photometry and magnitudes on the AB system. For NIR, we use the \citet{Oke_Gunn1983} and \citet{Fukugita1996} system which has a zeropoint of $-48.60$. 
+For WISE, the AB-Vega offsets \href{http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab}{are calculated} using the \citet{TokunagaVacca2005} AB system, which has a zeropoint of -48.574.
+So to remain on the -48.60 system, and assuming a flux density F$_{\nu} \propto \nu^{0}$, one needs to subtract 0.026 mag from the zeropoints:
+($\Delta$W1, $\Delta$W2, $\Delta$W3) = (2.673, 3.313, 5.148). 
+For W4, we use the calibration of \citet{Brown2014b}, $\Delta$W4= 6.66. 
+These magnitudes are {\it not} Galactic extinction corrected.
+
+We use a flat
 $\Lambda$CDM cosmology with $H_{\rm 0} = 67.7$ km s$^{-1}$ Mpc$^{-1}$,
@@
 There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
-Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citet{Schlafly2019}.
+Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citep{Schlafly2019}.
 The AllWISE program combines the W1 and W2 Single-exposure data from all the WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
@@
 \begin{eqnarray*}
-        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
-        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339. 
+        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.673  \\
+       {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 +  3.313 \\
 \end{eqnarray*}
+using the \citet{TokunagaVacca2005} AB system, 
+and is slightly different to the transformations presented in 
+\citet{Schlafly2019}.
 
 For the our MIR variability investigations, we use the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{NEOWISE-R 2019 Data Release}.
-NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was
-acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE. These fifth year NEOWISE data
-products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
-
-The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in
-hibernation in 2011 February and then reactivated in 2013 October. Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
+NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE.
+These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
+%%
+The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October.
+Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
 
@@
   \vspace{-14pt}
-  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} magnitude against signal-to-noise,
+  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} Vega magnitude against signal-to-noise,
     colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
@@
 the Atlas Images).
+
 In the two shorter bands W1/2 we see the clear and expected
@@
     \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
+    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190615_AB.png} 
   \vspace{-14pt}
@@
 the WISE AllWISE Data Release. The ``R90'' catalogue, contains 4.5M
-AGN candidates at 90\% reliability (and $\approx$150 AGN candidates
+AGN candidates at 90\% reliability ($\approx$150 AGN candidates
 per deg$^2$) while the ``C75'' catalogue consists of 20.9M AGN
-candidates at 75\% completeness (and $\approx$700 AGN candidates per
+candidates at 75\% completeness ($\approx$700 AGN candidates per
 deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
@@
       {\it (b)} UHS J0439+1634 was discovered by \citet{Fan2019} and is a strongly lensed quasar at $z=6.51$. 
-      {\it (c)} SDWISE J0306+1853 has {\tt w3mpro} = $10.51\pm0.1$ and {\tt w4mpro } = $7.586\pm0.16$. 
+      {\it (c)} SDWISE J0306+1853 has {\tt w3mpro} = $15.66\pm0.1$ (AB) and {\tt w4mpro } = $14.25\pm0.16$ (AB). 
       {\it (d)} SDSS J0100+2802 is the \citet{Wu2015} object.  
@@
 
-The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with (W1-W2) = 0.154, and the WISE W1W2W3 color image is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}.
-The reddest object in (W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 1.33.
+The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with 
+(W1-W2) =  -0.458  (i.e.
+0.154 in Vega), and the WISE W1W2W3 color image is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}.
+The reddest object in (W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).
 
@@
 Other high-redshift quasars that are bright W3/4 objects e.g.
-SDWISE~J0306+1853 (Fig.~\ref{fig:VHzQ_W4s} {\it(c)}) may well also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019}, but high-resolution follow-up is needed to confirm.
-SDSS~J0100+2802 (redshift $z=6.33$) does not have a formal W4 detection (W4 $=8.98\pm0.45$ and {\tt w4snr}=2.4), but as reported by \citet{Wu2015}, has a detection in the 2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object in both (W1-W3) and (W2-W3) with values of 2.73 and 1.93, respectively, and is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(d)}.
+SDWISE~J0306+1853 (Fig.~\ref{fig:VHzQ_W4s} {\it(c)}) may well also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019, Pacucci2019}, but high-resolution follow-up is needed to confirm.
+SDSS~J0100+2802 (redshift $z=6.33$; Fig.~\ref{fig:VHzQ_W4s} {\it(d)}) does not have a formal W4 detection ({\tt w4snr}=2.4), but as reported by \citet{Wu2015}, has a detection in the 2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object in both (W1-W3) and (W2-W3).
+%% with values of 2.73 (Vega) and 1.93 (Vega), respectively.
 
@@
   \includegraphics[width=8.5cm]
-  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+  {../light_curves/MIR_LCs/NEOWISER_LC_histogram_20190606.png}
   \vspace{-16pt}
@@
 
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes.
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q.
+
+while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes. 
 Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and J1626+2751.

### 2019-06-15 color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots.py

@@ -16,6 +16,9 @@ from astropy.io    import fits
 from astropy.io    import ascii
 from astropy.table import Table
 
+import fitsio
+from fitsio import FITS,FITSHDR
+
 import matplotlib
 import matplotlib.pyplot as plt
 from matplotlib.ticker import MultipleLocator, FormatStrFormatter
@@ -27,10 +30,19 @@ path      = '/cos_pc19a_npr/data/SDSS/DR14Q/'
 filename  ='DR14Q_v4_4.fits'
 #filename ='DR14Q_v4_4_W4good.fits'
 infile    = path+filename
-data      = fits.getdata(infile, 1)
+#data      = fits.getdata(infile, 1)
+data      = fitsio.read(infile,1)
 dr14q     = Table(data)
+
+## Vega to AB conversion
+dr14q['W1MAG'] =  dr14q['W1MAG'] + 2.673
+dr14q['W2MAG'] =  dr14q['W2MAG'] + 3.313
+dr14q['W3MAG'] =  dr14q['W3MAG'] + 5.148
+dr14q['W4MAG'] =  dr14q['W4MAG'] + 6.66
+
 dr14q_W1minW2 = (dr14q['W1MAG'] - dr14q['W2MAG'])
 dr14q_W2minW3 = (dr14q['W2MAG'] - dr14q['W3MAG'])
+
 
 ##
 ##  V H z Q    data
@@ -39,9 +51,17 @@ path      = '/cos_pc19a_npr/programs/quasars/highest_z/data/'
 filename  = 'VHzQs_ZYJHK_WISE.dat'
 table     = path+filename
 VHzQ_full = ascii.read(table)
+
+## Vega to AB conversion
+VHzQ_full['unW1mag'] = VHzQ_full['unW1mag'] - 0.004 + 2.673
+VHzQ_full['unW2mag'] = VHzQ_full['unW2mag'] - 0.032 + 3.313
+VHzQ_full['w3mpro']  = VHzQ_full['w3mpro'] + 5.148
+VHzQ_full['w4mpro']  = VHzQ_full['w4mpro'] + 6.66
+
+
 ## in case you want to select on e.g. snr
-#VHzQ = VHzQ_full
-VHzQ = VHzQ_full[np.where(VHzQ_full['w3snr'] >3.0)]
+VHzQ        = VHzQ_full
+VHzQ_goodW3 = VHzQ_full[np.where(VHzQ_full['w3snr'] >3.0)]
 
 
 ##  Making the plot(s)
[…]

### 2019-06-15 color_color/W1W2_plots/W1W2W3_colors.py

@@ -11,6 +11,15 @@ filename  = 'VHzQs_ZYJHK_WISE.dat'
 table     = path+filename
 VHzQ_full = ascii.read(table)
 
+
+## Vega to AB conversion
+#VHzQ_full['unW1mag'] = VHzQ_full['unW1mag'] - 0.004 + 2.673
+#VHzQ_full['unW2mag'] = VHzQ_full['unW2mag'] - 0.032 + 3.313
+#VHzQ_full['w3mpro']  = VHzQ_full['w3mpro'] + 5.148
+#VHzQ_full['w4mpro']  = VHzQ_full['w4mpro'] + 6.66
+
+
+
 ## Selections...
 W3_goodSNR   = VHzQ_full[np.where( VHzQ_full['w3snr']   > 3.0)]
 W1andW2      = VHzQ_full[np.where((VHzQ_full['unW1mag'] > 0.0)  &  (VHzQ_full['unW2mag'] >0.0)) ]

### 2019-06-15 light_curves/MIR_LCs/NEOWISER_LCs.py

@@ -25,9 +25,10 @@ path  = '../../data/light_curves/NEOWISE-R/'
 file  = 'NEOWISER-R_SingleExposure_L1bs_20190429_averaged.tbl'
 avers = ascii.read(path+file) 
 
-
 out_pdf = 'NEOWISER_LCs_VHzQs_temp.pdf'
 pdf_pages = PdfPages(out_pdf)
+
+
 ## http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec1_2.html#phases
 ALLWISE_MJD_min = 55203.     #  2010-January-07 
 ALLWISE_MJD_max = 55593.
@@ -70,11 +71,14 @@ for x in range(upto_this):
     data_two = avers[np.where(avers['cntr_01'] == x)]
     
     if len(data_one) < 1:
-        print(x, 'No of epochs: 0')
+        ## for NoOfEpochs_perQuasar.dat 
+        print('0.01')
+        #print(x, 'No of epochs: 0')
 
     if len(data_one) > 0:
         # print(x, data_one['ra'][0], data_one['dec'][0], len(data_one))
-        print(x, 'No of epochs:', len(data_one))
+        print(len(data_one))
+        #print(x, 'No of epochs:', len(data_one))
         
         if len(data_two) > 0:
             totes = totes + len(data_one)

### 2019-06-15 tables_for_paper/format_for_tables.py

@@ -19,6 +19,13 @@ filename   = 'VHzQs_ZYJHK_WISE.dat'
 table     = path+filename
 VHzQ_list = ascii.read(table)
 
+## Vega to AB conversion
+VHzQ_list['unW1mag'] = VHzQ_list['unW1mag'] - 0.004 + 2.673
+VHzQ_list['unW2mag'] = VHzQ_list['unW2mag'] - 0.032 + 3.313
+VHzQ_list['w3mpro']  = VHzQ_list['w3mpro'] + 5.148
+VHzQ_list['w4mpro']  = VHzQ_list['w4mpro'] + 6.66
+
+
 print()
 print(type(VHzQ_list['ra']))
 print()
@@ -45,10 +52,12 @@ print(header)
 footer = """    \hline
     \hline
     \\end{tabular}
-    \caption{The first 23 (i.e. 5\%) of 463 very high-$z$ quasars in Right Ascension order with near and mid-infrared photometry. 
-                  The full table can be found \href{https://github.com/d80b2t/VHzQ/tree/master/data}{here}. 
-                  Since none of the first 23 objects have $Z$-band detections, we don't report that column here (but
-                  is reported in the main table).} 
+    \caption{The first 23 (i.e. 5\%) of 463 very high-$z$ quasars in Right Ascension order with near and mid-infrared photometry.
+                  The full table can be found \href{https://github.com/d80b2t/VHzQ/tree/master/data}{here}.
+                  The AB magnitude system is used with the WISE Vega to AB offsets being ($\Delta$W1, $\Delta$W2, $\Delta$W3 $\Delta$W4)=(2.669, 3.281, 5.148, 6.66)
+                  Since none of the first 23 objects have $Z$-band detections, we don't report that column here (but is reported in the main table).
+                  WISE AllWISE W3 and W4 values without formal errors are low-SNR detections. 
+                  } 
      \label{tab:output_table}
      \\end{table}
      \n"""

### 2019-06-17 tex/arXiV_submission/VHzQ_arXiv_submitted.tex
tex/arXiV_submission/ added

--- 2019-06-15 tex/VHzQ.tex
@@
 
-\title[Infrared properties Very high-$z$ Quasars]
+\title[Infrared properties of Very high-$z$ Quasars]
   {The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars}
@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
+  {filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {../Nofz/Nofz_0pnt075bins_20190614.pdf}
+  {Nofz_0pnt075bins_20190614.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
-  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
+  {CoverageMaps_VHzQ_forpaper.pdf}
   \centering
@@
 \begin{landscape}
-      \input{../tables_for_paper/output_table_top5pc}
+      \input{output_table_top5pc}
 \end{landscape}
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {../detections/WISEmag_vs_coverage_20190605.pdf}
+  {WISEmag_vs_coverage_20190605.pdf}
   \centering
@@
     \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190615_AB.png} 
+    {W1W2W3_hexplots_20190615_AB.png} 
   \vspace{-14pt}
@@
     \centering
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/DELS_J1048-0109.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDWISE_J0306+1853.png}
-    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
+    \includegraphics[width=0.24\textwidth]{DELS_J1048-0109.png} 
+    \includegraphics[width=0.24\textwidth]{UHS_J0439+1634.png} 
+    \includegraphics[width=0.24\textwidth]{SDWISE_J0306+1853.png}
+    \includegraphics[width=0.24\textwidth]{SDSS_J0100+2802.png}
     \caption{VH$z$Qs with interesting MIR properties. 
@@
       {\it (c)} SDWISE J0306+1853 has {\tt w3mpro} = $15.66\pm0.1$ (AB) and {\tt w4mpro } = $14.25\pm0.16$ (AB). 
-      {\it (d)} SDSS J0100+2802 is the \citet{Wu2015} object.  
-%      {\it (d)} SDSS J1443+3623 has {\tt w3mpro, w4mpro } = ($11.189\pm0.1$, $8.699\pm0.26$) and 
-  %    {\it (d)} SDSS J1623+4705 has {\tt w3mpro, w4mpro } = ($11.425\pm0.1$, $8.954\pm0.28$).
-}
+      {\it (d)} SDSS J0100+2802 is the \citet{Wu2015} object.}
     \label{fig:VHzQ_W4s}
@@
 (grey colour-scale).
-% W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
-% W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
-% W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars,
 
 The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
-(W1-W2) =  -0.458  (i.e.
-0.154 in Vega), and the WISE W1W2W3 color image is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}.
-The reddest object in (W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).
-
-The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that are detected in the broad W3 filter and 10 objects that are formally detected in W4 ({\tt w4snr}$\geq$3.0).
-Three of the W3/4 objects are presented in Figure~\ref{fig:VHzQ_W4s}.
-UHS~J0439+1634 (Fig.~\ref{fig:VHzQ_W4s} {\it (b)}) with W4=7.165$\pm$0.12 was discovered by \citet{Fan2019} and is a strongly lensed quasar at $z=$6.51.
-This high luminosity is mostly not intrinsic, but is boosted by an intervening redshift $z\sim$0.7 galaxy.
-Other high-redshift quasars that are bright W3/4 objects e.g.
-SDWISE~J0306+1853 (Fig.~\ref{fig:VHzQ_W4s} {\it(c)}) may well also so be lensed \citep[e.g.,][]{Glikman2018lens, Fan2019, Pacucci2019}, but high-resolution follow-up is needed to confirm.
-SDSS~J0100+2802 (redshift $z=6.33$; Fig.~\ref{fig:VHzQ_W4s} {\it(d)}) does not have a formal W4 detection ({\tt w4snr}=2.4), but as reported by \citet{Wu2015}, has a detection in the 2MASS $J$, $H$ and $K_{\rm s}$ bands and is also the bluest object in both (W1-W3) and (W2-W3).
-%% with values of 2.73 (Vega) and 1.93 (Vega), respectively.
+(W1-W2) = -0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
+is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
+(W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).
+
+The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that
+are detected in the broad W3 filter and 10 objects that are formally
+detected in W4 ({\tt w4snr}$\geq$3.0). Three of the W3/4 objects are
+presented in Figure~\ref{fig:VHzQ_W4s}. UHS~J0439+1634
+(Fig.~\ref{fig:VHzQ_W4s} {\it (b)}) with W4=7.165$\pm$0.12 was
+discovered by \citet{Fan2019} and is a strongly lensed quasar at
+$z=$6.51. This high luminosity is mostly not intrinsic, but is boosted
+by an intervening redshift $z\sim$0.7 galaxy. Other high-redshift
+quasars that are bright W3/4 objects e.g. SDWISE~J0306+1853
+(Fig.~\ref{fig:VHzQ_W4s} {\it(c)}) may well also so be lensed
+\citep[e.g.,][]{Glikman2018lens, Fan2019, Pacucci2019}, but
+high-resolution follow-up is needed to confirm. SDSS~J0100+2802
+(redshift $z=6.33$; Fig.~\ref{fig:VHzQ_W4s} {\it(d)}) does not have a
+formal W4 detection ({\tt w4snr}=2.4), but as reported by
+\citet{Wu2015}, has a detection in the 2MASS $J$, $H$ and $K_{\rm s}$
+bands and is also the bluest object in both (W1-W3) and (W2-W3).
 
@@
   \includegraphics[width=8.5cm]
-  {../light_curves/MIR_LCs/NEOWISER_LC_histogram_20190606.png}
+  {NEOWISER_LC_histogram_20190606.png}
   \vspace{-16pt}
@@
 \begin{figure}
-  \includegraphics[width=8.5cm]
-  {../light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
-  \centering
+  \centering
+  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J0100.png}
+  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
+  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J1621.png}
   \caption[]
-  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
-    Red points are the W1 band; cyan points the W2 band.} 
+  {Here we show the MIR NEOWISE-R for SDSS J0100+2802 (top), SDWISE   J1752+5036 (middle), and  
+    SDSS J1621+5155 (bottom). Red points are the W1 band; cyan points the W2 band.
+  For the light curves, we show weighted means for every 6 month NEOWISE-R scan.} 
   \label{fig:MIR_LC_3egs}
 \end{figure}
-One key point to note when looking at the WISE variability is that
-AllWISE (and 2MASS) source information included in the NEOWISE Source
-Database
+One key point to note is that the NEOWISE-AllWISE match radius 
+is 3.00'' and the AllWISE (and 2MASS) source information included 
+in the NEOWISE Source Database 
 \href{http://wise2.ipac.caltech.edu/docs/release/neowise/expsup/sec2_1f.html}{are
-associations not identifications}. The NEOWISE-AllWISE match radius is
-3''.
-
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q.
-
-while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes. 
-Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and J1626+2751.
+associations not identifications}.
+
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections for each VH$z$Q. 
+There are 60 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs and four with over 300.
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the brighter MIR objects with well-sampled 
+MIR lightcurves and associated colour changes; 
+SDSS J0100+2802 (Fig.~\ref{fig:MIR_LC_3egs} top), 
+SDWISE  J1752+5036    (middle), 
+SDSS J1621+5155 (bottom). 
+For the light curves, we show weighted means for every 6 month NEOWISE-R scan.
+Due to the WISE scanning pattern, objects close to the North Ecliptic Pole 
+are well sampled, and indeed this is the area for further investigation 
+time-domain investigation with upcoming large infrared space telescopes
+\citep{Jansen2018, White2019AAS}.
 
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
+    \includegraphics[width=8.5cm]{MMTJ0215-0529LC_20190613.png}
     \caption{The infrared light curve for MMT J0215-0529 with data from 
       WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
-MMT  J0215-0529 was identified by \citet{McGreer2018}, 
-% 02:15:23.27 −05:29:45.8
-%g_AB = 28.05 \pm 1.00 
-%r_AB = 22.69 \pm  0.01
-%           20.85 \pm  0.01 
-%           20.64 \pm 0.01
-% −25.7 5.13 MMT 
-}
+      MMT  J0215-0529 was identified by \citet{McGreer2018}.}
     \label{fig:MMTJ0215-0529}
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
+    \includegraphics[width=8.5cm]{CFHQSJ0216-0455LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
+    \includegraphics[width=8.5cm]{SHELLQsJ0220-0432LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
@@
     \centering
-    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
+    \includegraphics[width=8.5cm]{SDSSJ0959+0227LC_20190612.png}
     \caption{The near infrared light curve for SDSS J0959+0227. Note, 
@@
 
-\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL}
+\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL_WSA}
 Here we give the recipe and SQL that returned the near-infrared photometry 
@@
 
-\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL}
+\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL_VSA}
 In a very similar manner to the WSA, we give here the details on how to access
@@
 \end{itemize}
-Then head to the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL Query} page where the database release to use is {\tt VSERV1000v20190508}.
-The queries are the same as those used in the WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting with {\tt wserv1000} should be replaced with {\tt vserv1000}.
-
-%\onecolumn
-%\input{SQL_examples_VSA}
-%\twocolumn
+Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
+Query} page is where the database release to use is {\tt
+VSERV1000v20190508}. The queries are the same as those used in the
+WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
+with {\tt wserv1000} should be replaced with {\tt vserv1000}.
 

### 2019-07-16 data/Perger/HMS2deg.py
Added data/Perger/

@@ -1,0 +1,21 @@
+def HMS2deg(ra='', dec=''):
+  RA, DEC, rs, ds = '', '', 1, 1
+  if dec:
+    D, M, S = [float(i) for i in dec.split()]
+    if str(D)[0] == '-':
+      ds, D = -1, abs(D)
+    deg = D + (M/60) + (S/3600)
+    DEC = '{0}'.format(deg*ds)
+  
+  if ra:
+    H, M, S = [float(i) for i in ra.split()]
+    if str(H)[0] == '-':
+      rs, H = -1, abs(H)
+    deg = (H*15) + (M/4) + (S/240)
+    RA = '{0}'.format(deg*rs)
+  
+  if ra and dec:
+    return (RA, DEC)
+  else:
+    return RA or DEC
+

### 2019-07-16 tex/older_tex/VHzQ_20190615.tex
started on the reply to the referees report

--- 2019-06-17 tex/arXiV_submission/VHzQ_arXiv_submitted.tex
@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {filters_vs_QSOstars_z6pnt7.pdf}
+  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {Nofz_0pnt075bins_20190614.pdf}
+  {../Nofz/Nofz_0pnt075bins_20190614.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
-  {CoverageMaps_VHzQ_forpaper.pdf}
+  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
   \centering
@@
 \begin{landscape}
-      \input{output_table_top5pc}
+      \input{../tables_for_paper/output_table_top5pc}
 \end{landscape}
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {WISEmag_vs_coverage_20190605.pdf}
+  {../detections/WISEmag_vs_coverage_20190605.pdf}
   \centering
@@
     \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {W1W2W3_hexplots_20190615_AB.png} 
+    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190615_AB.png} 
   \vspace{-14pt}
@@
     \centering
-    \includegraphics[width=0.24\textwidth]{DELS_J1048-0109.png} 
-    \includegraphics[width=0.24\textwidth]{UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{SDWISE_J0306+1853.png}
-    \includegraphics[width=0.24\textwidth]{SDSS_J0100+2802.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/DELS_J1048-0109.png} 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDWISE_J0306+1853.png}
+    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
     \caption{VH$z$Qs with interesting MIR properties. 
@@
   \includegraphics[width=8.5cm]
-  {NEOWISER_LC_histogram_20190606.png}
+  {../light_curves/MIR_LCs/NEOWISER_LC_histogram_20190606.png}
   \vspace{-16pt}
@@
   \centering
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J0100.png}
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J1621.png}
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J0100.png}
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J1621.png}
   \caption[]
@@
     \centering
-    \includegraphics[width=8.5cm]{MMTJ0215-0529LC_20190613.png}
+    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
     \caption{The infrared light curve for MMT J0215-0529 with data from 
       WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
-      MMT  J0215-0529 was identified by \citet{McGreer2018}.}
+MMT  J0215-0529 was identified by \citet{McGreer2018}, 
+% 02:15:23.27 −05:29:45.8
+%g_AB = 28.05 \pm 1.00 
+%r_AB = 22.69 \pm  0.01
+%           20.85 \pm  0.01 
+%           20.64 \pm 0.01
+% −25.7 5.13 MMT 
+}
     \label{fig:MMTJ0215-0529}
@@
     \centering
-    \includegraphics[width=8.5cm]{CFHQSJ0216-0455LC_20190613.png}
+    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
@@
     \centering
-    \includegraphics[width=8.5cm]{SHELLQsJ0220-0432LC_20190613.png}
+    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
@@
     \centering
-    \includegraphics[width=8.5cm]{SDSSJ0959+0227LC_20190612.png}
+    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
     \caption{The near infrared light curve for SDSS J0959+0227. Note, 

### 2019-08-12 tex/MNRAS_submission/rv1/referees_reply.txt
rv1/referees_reply.txt updated

p. 1: You may want to end the first sentence of the right column of the Intro
with a statement that at z>5, relativistic time dilation also stretches the
photometric variability of the accretion disk as observed.

To Do by NPR

p. 2, Fig. 1: Is it useful here to plot both filter sets if they are sufficiently
different? Please provide larger tick-marks for better readability in any case.

Hmmm. I’m not sure what to do here; it’s going to ruin the clarity of the figure
having both ZYJHK filter sets, but, they are different.
I think adding an explicit link to:
       d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png
and
       d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png
is the way forward here.

p. 3, Fig. 3, caption or text: You should briefly comment on why the quasar
distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
sensitivity across the filter curves, and/or the onset of complete GP-troughs at
z>5.7?

This is Figure 2, not 3.
And I think this is where some of the missing objects come in??
We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.

p. 4, Fig. 3: Can you plot the small dots somewhat bigger for better visibility
without loss of information?

This is the coverage map figure
       => To Do by NJGC.

THROUGHOUT: Several occurrences of ??, i.e., where table or Appendix references
are not properly done in latex.

NPR to double check…

p. 5: [My only (minor) scientific comment]: Re: ``although possible, we consider
it highly unlikely there would be more than one MIR source contributing to the
flux of a single UV/optically bright rest-frame quasar. Investigating this in
detail is very interesting but left to a future study. ''

I think it would be better to address now the number of expected contaminating
8--25 micron sources in the apertures used, as it can be done straightforwardly.
E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures
you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph
version. The redshift distribution of the sampled 8--25 micron foreground objects
is narrow enough and their K-corrections advantageous enough, that the objects
counts sharply turnover for AB(W3, W4) > 20--18 mag (left panels), and as a
consequence the normalized differential counts (right panels) --- especially in
W4 --- have most of their EBL energy emerging at AB~18--20 mag. As a consequence,
the relative number or probability of contaminating objects at AB>20 mag inside
your apertures should be rather small. A point worth mentioning, as it helps your
case.

NPR to add this to the text.

p. 6 Table 3: Should mention that the number of significant digits listed here
for the YJHK W1--W4 mags is not always warranted, but needed to verify the small
VIRCAM-WFCAM offsets in Table 5, This table is a very useful check of your global
photometric zeropoints.

NPR to change.

p. 7, very end of 3.1.1: Quote the (effective) VSA and SDSS quasar IR observing
epochs here, in case these clearly discrepant magnitudes are due to variability.

This is for SDSS J0349+0034 and J2220-0101; NJGC to check.

p. 8 Fig 5: Make the z=0--3 quasar cloud a little lighter grey, so that the
z=5--6.5 quasar cloud is better visible.

NPR to update.

p. 9 top left: = -0.458 : All minus signs in latex should be coded up as --
(double hyphen), also in the tables, to appear as minus sign.

NPR to update.

p. 10 Fig 8: Enlarge all axes label for better readability.

NPR to update.

THROUGHOUT: signal-to-noise should always be listed as a ratio: signal-to-noise
ratio or SNR.
NPR to update.

### 2019-08-19 tex/VHzQ.tex
wee updates

@@
 surveys and papers.  Specifically, we use data from:
-\citet{Banados2014, Banados2016, Banados2018}, 
+\citet{Banados2014, Banados2016, Banados2018a, Banados2018b}, 
 \citet{Becker2015}, 
@@
 \citet{Cool2006}, 
+\citet{Douglas2007}, 
 \citet{DeRosa2011}, 
@@
 \citet{Kashikawa2015}, 
+\citet{Khorunzhev2017}, 
 \citet{Koptelova2017}, 
+\citet{Kozlowski2019}, 
 \citet{Kim2015, Kim2018},  
@@
 \citet{Reed2015, Reed2017}, 
+\citet{Saxena2018}, 
 \citet{Stern2007},  
 \citet{Tang2017}, 
+\citet{vanBreugel1999}, 
 \citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
@@
 J1120+0641 \citep{Mortlock2011}. Neither the R90 or C75 catalogue matches to the
-current highest-redshift object J1342+0928 \citep{Banados2018}.
+current highest-redshift object J1342+0928 \citep{Banados2018a}.
 
@@
 \begin{figure}
-  \includegraphics[width=8.5cm]
-  {../light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
-  \centering
+  \centering
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J0100.png}
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
+  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J1621.png}
   \caption[]
-  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
-    Red points are the W1 band; cyan points the W2 band.} 
+  {Here we show the MIR NEOWISE-R for SDSS J0100+2802 (top), SDWISE   J1752+5036 (middle), and  
+    SDSS J1621+5155 (bottom). Red points are the W1 band; cyan points the W2 band.
+  For the light curves, we show weighted means for every 6 month NEOWISE-R scan.} 
   \label{fig:MIR_LC_3egs}
 \end{figure}
-One key point to note when looking at the WISE variability is that
-AllWISE (and 2MASS) source information included in the NEOWISE Source
-Database
+One key point to note is that the NEOWISE-AllWISE match radius 
+is 3.00'' and the AllWISE (and 2MASS) source information included 
+in the NEOWISE Source Database 
 \href{http://wise2.ipac.caltech.edu/docs/release/neowise/expsup/sec2_1f.html}{are
-associations not identifications}. The NEOWISE-AllWISE match radius is
-3''.
-
-Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q.
-
-while Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lightcurves and associated colour changes. 
-Here we show J0100+2802 \citep{Wu2015}, J0224-4711 and J1626+2751.
+associations not identifications}.
+
+Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections for each VH$z$Q. 
+There are 60 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs and four with over 300.
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the brighter MIR objects with well-sampled 
+MIR lightcurves and associated colour changes; 
+SDSS J0100+2802 (Fig.~\ref{fig:MIR_LC_3egs} top), 
+SDWISE  J1752+5036    (middle), 
+SDSS J1621+5155 (bottom). 
+For the light curves, we show weighted means for every 6 month NEOWISE-R scan.
+Due to the WISE scanning pattern, objects close to the North Ecliptic Pole 
+are well sampled, and indeed this is the area for further investigation 
+time-domain investigation with upcoming large infrared space telescopes
+\citep{Jansen2018, White2019AAS}.
 
@@
 \bibliographystyle{mnras}
-\bibliography{tester_mnras}
+\bibliography{/cos_pc19a_npr/programs/quasars/highest_z/tex/tester_mnras}
 

### 2019-08-30 tex/MNRAS_submission/rv1/referees_reply.txt
tables_for_paper/LIST_OF_VHzQs.dat updated
VHzQs tidying up data/WISE

@@
+	We thank the Referee for reading our manuscript carefully and for their review and comments.
+	We address each of these in turn below (indented text).
+
+	We have also made further, key improvements to our dataset and pipeline.
+
+	We note that after the submission of the original manuscript it was brought to our attention
+	(K. Perger; priv. comm) that we were missing a handful of confirmed z>5 quasars.
+	As such, our database has increased by 25 objects for a total of 488 VHzQs.
+
+	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA Science Archive (VSA) from scratch
+	with the set of updated objects. This uncovered a small matching bug for three objects in the WSA
+        (no issues were found in the VSA rerun). One of these objects, however, is SDSSJ2220-0101, which
+	we thought had large photometric changes but now acknowledge this was due to an incorrect
+	apertureID measurement. The updated photometry for SDSSJ2220-0101 has the VSA J-band
+	magnitude 19.38+/-0.04 and a WSA magnitude 19.24+/-0.09.
+
+	Consequently, we have changed the Abstract:
+	"Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had
+	significant differences between their WFCAM and VISTA
+	magnitudes in one band."
+	to
+	"Only one quasar, SDSS J0349+0034, shows significant
+	differences between WFCAM and VISTA magnitudes in one band."
+
 p. 1: You may want to end the first sentence of the right column of the Intro
@@
 ratio or SNR.
+
 		NPR to update.

### 2019-08-30 data/WISE/unWISE/making_unWISE_v2.py

@@ -1,15 +1,19 @@
 '''
-This wee script combines, or simply makes, the unWISE files for the VHzQs.
+This wee script combines, or simply makes, the unWISE files for the
+VHzQs.
 
-v1.0::
-Starting with 'just' the original 424 VHzQs and then added
-the "Halloween" 2018 Oct objects from arXiv:1810.11924-27v1.
-Tidied up version of the Jupyter notebook making_unWISE_W1s.ipynb
+v1.0:: Starting with 'just' the original 424 VHzQs and then added the
+"Halloween" 2018 Oct objects from arXiv:1810.11924-27v1.  Tidied up
+version of the Jupyter notebook making_unWISE_W1s.ipynb
 
-v2.0::
-Takes now *both* the W1 and W2 unWISE input files (e.g. from
-Aaron Meisner and the official DR1 of the
+v1.1:: Takes now *both* the W1 and W2 unWISE input files e.g. from
+Aaron Meisner and the official unWISE Catalog DOI:
+10.3847/1538-4365/aafbea http://catalog.unwise.me/
 
+v2.0:: Takes in the W1 and W2 unWISE input files,
+high_z_qsos_24Aug19-w[1/2].fits from Aaron Meisner, and uses them to
+produce the v2 version of the VHzQ catalogue.  Changed "unWISE"
+variable to "unWISE".
 ''' 
 
 import numpy as np
@@ -18,34 +22,35 @@ from astropy.io import fits
 
 ## http://docs.astropy.org/en/stable/io/fits/index.html
 ## Reading in the unWISE W1 and W2 files::
-december_w1_hdu = fits.open("high_z_qsos_03Dec18-w1.fits")  
-december_w2_hdu = fits.open("high_z_qsos_03Dec18-w2.fits")  
+unWISE_w1_hdu = fits.open("high_z_qsos_24Aug19-w1.fits")  
+unWISE_w2_hdu = fits.open("high_z_qsos_24Aug19-w2.fits")  
 
-print('december_w1_hdu', december_w1_hdu)
+print('unWISE_w1_hdu', unWISE_w1_hdu)
+print('unWISE_w2_hdu', unWISE_w2_hdu)
 
 ## Assuming (correctly) the first extension is a table
-december_w1 = december_w1_hdu[1].data
[…]

### 2019-08-30 data/WISE/unWISE/making_unWISE_v1pnt1.py
data/WISE and data/WISE/unWISE updated

@@ -1,0 +1,78 @@
+'''
+This wee script combines, or simply makes, the unWISE files for the VHzQs.
+
+v1.0::
+Starting with 'just' the original 424 VHzQs and then added
+the "Halloween" 2018 Oct objects from arXiv:1810.11924-27v1.
+Tidied up version of the Jupyter notebook making_unWISE_W1s.ipynb
+
+v1.1::
+Takes now *both* the W1 and W2 unWISE input files (e.g. from Aaron
+Meisner and the official unWISE Catalog DOI: 10.3847/1538-4365/aafbea
+http://catalog.unwise.me/
+''' 
+
+import numpy as np
+from astropy.io import ascii
+from astropy.io import fits
+
+## http://docs.astropy.org/en/stable/io/fits/index.html
+## Reading in the unWISE W1 and W2 files::
+december_w1_hdu = fits.open("high_z_qsos_03Dec18-w1.fits")  
+december_w2_hdu = fits.open("high_z_qsos_03Dec18-w2.fits")  
+
+print('december_w1_hdu', december_w1_hdu)
+
+## Assuming (correctly) the first extension is a table
+december_w1 = december_w1_hdu[1].data
+december_w2 = december_w2_hdu[1].data
+
+## Can look at the columns of said files.
+## Should be very similiar (!!), even identical to that
+## of the offical unWISE DR1, Meisner & Schlafly (2019)
+december_w1.columns
+
+
+print("type(december_w1['RA']), len(december_w1['RA'])", type(december_w1['RA']), len(december_w1['RA']))
+print("type(december_w2['RA']), len(december_w2['RA'])", type(december_w2['RA']), len(december_w2['RA']))
+print()
+
+## Setting up the variables for flux -> magnitude (and flux error to mag error) conversions
+unWISE_W1_RA    = december_w1['RA']
+unWISE_W2_RA    = december_w2['RA']
+unWISE_W1_DEC   = december_w1['DEC']
+unWISE_W2_DEC   = december_w2['DEC']
+unWISE_W1_FLUX  = december_w1['FLUX']
+unWISE_W2_FLUX  = december_w2['FLUX']
[…]

### 2019-09-09 tex/VHzQ.tex
tables_for_paper/LIST_OF_VHzQs.dat updated
Added Appendix detailing changes to Qso input catalogue

@@
 
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
+We have compiled a list of {\bf 488} quasars with redshifts $z\geq5.00$. We
 use all the $z\geq5.00$ quasars that have been discovered,
@@
 \citet{Saxena2018}, 
+\citet{Schneider2007}, 
 \citet{Stern2007},  
@@
 \citet{Zeimann2011}.
+
+{\bf We updated our list of objects between the submitted paper and accepted due
+to feedback from other scientists. We discuss these changes in detail in
+Appendix~\ref{app:qso_sample}.}
 
@@
   \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
+  \item Krisztina Perger at \href{http://astro.elte.hu} for discussions about
+  the input catalogue. 
 \end{list}
@@
 
+\section{Qso Sample}
+\label{app:qso_sample}
+{\bf In the submitted version of this paper, we had 463 QSOs selected from the
+literature which had $z\geq5$, which we thought was the complete sample except a
+few that were published in 2019.
+
+When we posted the submitted paper onto arXiv\footnote{http://www.arxiv.org}, we
+had two responses, one from Jinyi Yang, who pointed out that we missed QSOs in
+\cite{YangJ2018a} and Krisztina Perger, who also mentioned that we had
+missed $sim40$ QSOs and pointed us to her catalogue of
+QSOs\footnote{http://astro.elte.hu/~perger/catalog.html}. We downloaded Tables
+2,3 \& 4 from \cite{YangJ2018a} using
+Vizier\footnote{http://vizier.u-strasbg.fr/} and found all matches with 
+$2\arcsec$ and added the remaining objects that had $z\geq5$, one object  from
+Table 3, SUHAWJ1016+2541, and 15 from Table 4, see Table~\ref{tab:new_qsos}. We
+also downloaded the 20190514 version of the Perger catalogue and X-matched that,
+finding all of the matches with $2\arcsec$ and looked for non-matches.
+
+However, we spotted some inconsistences between the names of some of the QSOs
+in the Perger catalogue and decimal equatorial coordinates and pointed these
+out, and very rapidly Perger responded having fixed their catalogue. After
+further checks we found 10 objects (see Table~\ref{tab:disagree_objs}) that were
+in both catalogues that there was disagreement on the coordinates. In some cases it
+was clear from the names that either we (Ross \& Cross) had made a typo, or
+Perger had. In most other cases a search of the literature gave a clear answer. 
+Two particular odd examples were SDSSJ0835+3227 and VA-13492, found in the
+Perger catalogue. In both cases the coordinates looked similar to SDSSJ0835+3217 
+and SDSSJ1040-1155 respectively and the redshifts were identical to these QSOs,
+which alerted us to a potential problem. These QSOs could be traced back in the literature: in
+the first case both QSOs are in \cite{Banados2016} and in the second case is 
+VA-13492  is in \cite{Flesch2015} which refers back to \cite{Douglas2007}
+although the latter only seems to only contain SDSSJ1040-1155.
+In the case of SDSSJ0835+3227, we checked the SDSS-z band images\footnote{https://dr15.sdss.org}, and found a bright source at
+the position of SDSSJ0835+3217 and no source at the position of SDSSJ0835+3227, see
+Figure~\ref{fig:check_obj}. In the case of VA-13492, the I-band magnitude was
+equivalent to SDSSJ1040-1155 (I=25.9 mag), so we have decided that both of these objects
+have been transcribed incorrectly sometime in the past.
+
+The objects from the submitted version of Ross \& Cross that have changed
+position are flagged in Table~\ref{tab:disagree_objs} and the difference in position is
+shown. Some of these are rounding errors using coordinates that were to the
+nearest arcsec or $4\arcsec$ if it was rounded to the nearest hour, minute,
+second in RA, some were typos from reentering coordinates and these demonstrate
+that it is always better to download electronic catalogues and use decimal coordinates.
+Perger has also updated their catalogue and the 20190724 version matches our
+catalogue. A final test of matching to with $1\arcsec$ found another difference:
+we had downloaded the OGLEJ015531-75 coordinates from the published paper and
+Perger had done so from the submitted arXiv paper, and it seems that
+\cite{Kozlowski2019} made a minor update to their values in between.
+
+We also excluded DES0141-54, that was included in the Perger catalogue, since
+this came from a conference proceedings \cite{Belladitta2018}, which did not
+have arcsecond precision in its coordinates, so our matched-aperture photometry
+may have been in an incorrect position.
+
+Altogether we found that our final catalogue has 488 $z\geq$ QSOs. The new QSOs
+are all shown in Table~\ref{tab:new_qsos}.}
+
+%% Table New QSOs --> name, ra, dec, redshift, reference, source
+%% Table QSOs in disagreement --> name, correct pos, difference, literature,
+% ErrorInCR, TypeOfError
+
+\begin{table*}   
+\begin{tabular}{l r r r r r}
+\hline  \hline
+QSO & ra & dec & redshift & reference & source  \\
+\hline  
+SUHAWJ1016+2541 & +154.1571250 & +25.6921944 & +5.64 &Yang2018 & Yang2018 \\
+PS1J0052+4556 & +13.1810417	& +45.9422306 & +5.31 & Yang2018   & Yang2018 \\
+PS1J0332+1811 & +53.1540833	& +18.1998000 & +5.12 & Yang2018   & Yang2018 \\
+PS1J0511-0754 & +77.9780417	& -7.9123056 & +5.13 & Yang2018 & Yang2018 \\
+PS1J0616-1338 & +94.1015833	& -13.6351111	& +5.58 & Yang2018 & Yang2018 \\
+PS1J0757-0002 & +119.4412500 & -0.0336361 & +5.54 &	Yang2018 & Yang2018 \\
+PS1J0817-1633 & +124.2527500 & -16.5581361 & +5.06 & Yang2018 & Yang2018 \\
+PS1J1034-1233 & +158.6535833 & -12.5618028 & +5.51 & Yang2018 & Yang2018 \\
+PS1J1057-1758 & +164.3650000 & -17.9754722 & +5.34 & Yang2018 & Yang2018 \\
+PS1J1121-0718 & +170.4318750 & -7.3110250 & +5.71 & Yang2018 & Yang2018 \\
+PS1J1137-1049 & +174.3973750 & -10.8262611 & +5.50 & Yang2018 & Yang2018 \\
+PS1J1310-0639 & +197.5546250 & -6.6643222 & +5.06 & Yang2018  & Yang2018 \\
+PS1J1313-2617 & +198.3585833 &-26.2893972 & +5.54 & Yang2018 & Yang2018 \\
+PS1J1427-0503 & +216.8398333 & -5.0647333 & +5.08 & Yang2018 & Yang2018 \\
+PS1J1533-1810 & +233.4990000 &-18.1742250 & +5.03 & Yang2018 & Yang2018 \\
+PS1J2033+1218 & +308.2936250 & +12.3143028 & +5.11 & Yang2018 & Yang2018 \\
+OGLEJ015531-752807 & +28.8792083 & -75.4686111 & +5.09 & Kozlowski2019 & Perger
+\\
+TNJ0924-2201 & +141.0830000	& -22.0281940 & +5.19 & vanBreugel1999 & Perger \\
+XMMJ125329+30 & +193.3725460 & +30.9276197 & +5.08 & Khorunzhev2017 & Perger \\
+SDSSJ141912.03+53 & +214.8001310 &+53.6775646 & +5.38 & Paris2017 & Perger \\
+TGSSJ1530+1049 & +232.7079167 & +10.8253060	& +5.72 & Saxena2018 & Perger \\
+PSOJ352.4034-15.337 & +352.4034850 & -15.3373500 & +5.84 & Banados2018 & Perger
+\\
+PSOJ0046-2837 & +11.5985420	& -28.6298170 & +5.99 & Venemans2018 & Perger \\
+VIKJ2318-3029 & +349.6379420 & -30.4926030 & +6.1458 & Venemans2018 & Perger \\
+HSC1732+6531 & +263.1796583	& +65.5204139 & +6.60 & Songaila2018 & Other \\
+\hline  \hline
+\end{tabular}
+\caption{{\bf New QSOs added to the paper since the submitted version. }
+}
+\label{tab:new_qsos}
+\end{table*}
+
+\begin{table*}
+\begin{tabular}{l r r r r r}
+\hline  \hline
+QSO & ra & dec & difference & isCRDiff & Issue \\
+ & deg & deg & arcsec & &  \\
+\hline
+OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
+%% Same name diff pos/redshift from v1
+PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
+ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
+SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
+PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
+VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
+DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
+SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
+PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
+SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
+DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
+ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
+PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
+VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
+PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
+%%Krisztina wrong\ldots
+SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
+DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
+DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
+%% More complex 
+SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
+VA-13492 & --- & --- & --- & No & 6 \\
+\hline  
+\hline  \hline
+\end{tabular}
+\caption{{\bf QSOs in disagreement between RC and Perger or which have been
+updated since the submitted paper.
+This table shows all of the QSOs where there has been a disagreement or a
+change. All of those marked 'Yes' were in the submitted paper and have been
+changed since, and the final column lists the reason(s) for inclusion in the
+table. The numbers refer to the following issues:
+\begin{itemize}
+	\item 1) Coordinate update in original reference, from submitted to accepted; 
+	\item 2) Coordinate different in RC submitted
+	\item 3) Redshift different in RC submitted, typically very small changes. 
+	\item 4) Our coords incorrect, but KP had 2 entries, one also incorrect
+	\item 5) Coordinates incorrect in KP.
+	\item 6) Two objects with similar looking coordinates and identical redshifts.
+	These appear to be incorrect entries further back in the literature. 
+\end{itemize}  
+}}
+\label{tab:disagree_objs}
+\end{table*}
+
+\begin{figure}
+  %% trim=l b r t
+  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
+  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083525+3217.jpg}
+  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083526+3227.jpg}
+  \centering
+  %\vspace{-12pt} 
+  \caption[]
+  {{\bf Cutouts from SDSS z-band images retrieved from SDSS-SkyServer for the
+  coordinates of SDSSJ083535+3217 and SDSSJ083526+3227. Both of these objects
+  appear in \cite{Banados2016} and subsequently in the Perger catalogue, but
+  only SDSSJ083535+3217 is matched to an SDSS source. Since SDSSJ083526+3227
+  has an SDSS name, and is apparently a $z=5.89$ QSO, it should have a z-band
+  detection.}}
+  \label{fig:check_obj}
+\end{figure}
+
 \section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL_WSA}
@@
 \bibliographystyle{mnras}
-\bibliography{/cos_pc19a_npr/programs/quasars/highest_z/tex/tester_mnras}
+\bibliography{./tester_mnras}
 

### 2019-09-09 tex/VHzQ.tex
Fixes to make correctly

@@
   \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
-  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
+  {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper/CoverageMaps_VHzQ_forpaper.pdf}
   \centering
@@
 VA-13492 & --- & --- & --- & No & 6 \\
-\hline  
 \hline  \hline
@@
 table. The numbers refer to the following issues:
-\begin{itemize}
-	\item 1) Coordinate update in original reference, from submitted to accepted; 
-	\item 2) Coordinate different in RC submitted
-	\item 3) Redshift different in RC submitted, typically very small changes. 
-	\item 4) Our coords incorrect, but KP had 2 entries, one also incorrect
-	\item 5) Coordinates incorrect in KP.
-	\item 6) Two objects with similar looking coordinates and identical redshifts.
-	These appear to be incorrect entries further back in the literature. 
-\end{itemize}  
-}}
+1) Coordinate update in original reference, from submitted to accepted; 
+2) Coordinate different in RC submitted;
+3) Redshift different in RC submitted, typically very small changes;
+4) Our coords incorrect, but KP had 2 entries, one also incorrect;
+5) Coordinates incorrect in KP;
+6) Two objects with similar looking coordinates and identical redshifts. These
+appear to be incorrect entries further back in the literature;}
+}
 \label{tab:disagree_objs}

### 2019-09-09 tex/VHzQ.tex
VHzQ.tex update

@@
 \begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high
+We assemble a catalogue of {\bf 488} spectroscopically confirmed very high
 ($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
@@
 This paper is organized as follows. In Section 2, we present the
-assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
+assembled list of the {\bf 488} $z\geq5.00$ VH$z$Qs that we have
 compiled. We then give a high-level overview of the photometric
@@
 \hline 
-5.00         & 1180          &  463   \\
-5.70         & 1000          &  267   \\
+5.00         & 1180          &  ---   \\
+5.70         & 1000          &  ???  \\
 6.00         &   937          &  170   \\
@@
   We query the WSA and VSA performing matched-aperture photometry at
-  the positions of our 463 VH$z$Qs. This database is world-readable and
+  the positions of our {\bf 488} VH$z$Qs. This database is world-readable and
   we give the full recipe and relevant SQL queries for accessing both
@@
 \section{Results}
-Having collated the sample of 463 VH$z$Qs, and obtained their near-
+Having collated the sample of {\bf 488} VH$z$Qs, and obtained their near-
 and mid-infrared photometry we report here the various photometric
@@
 candidates at 75\% completeness ($\approx$700 AGN candidates per
-deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
+deg$^2$). Crossmatching our catalogue of {\bf 488} VH$z$Qs with these
 catalogues, produces 42 matches with the R90 sample and 98 matches
@@
 
-We thank:
+\noindent
+NPR and NJCG thank:
 \begin{list}{$\circ$}{}  
@@
   \item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
+{\bf  \item Krisztina Perger for key discussions about missing objects after the pre-print appeared. }
+  \item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
+  \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
   \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
   \item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
-  \item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
-  \item Nathan Secrest for useful discussions on the mid-IR AGN catalogues. 
-  \item Krisztina Perger at \href{http://astro.elte.hu} for discussions about
-  the input catalogue. 
 \end{list}
@@
 
-\section{Qso Sample}
+\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL_WSA}
+Here we give the recipe and SQL that returned the near-infrared photometry 
+for the VH$z$Qs from the  WFCAM Science Archive.
+
+The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
+Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
+with these credentials::
+\begin{itemize} 
+    \item Username: {\tt WSERV1000} 
+    \item password: {\tt highzqso} 
+    \item community: {\tt nonsurvey}
+\end{itemize}
+Then going to the
+\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
+Query}} page the Database release {\tt WSERV1000v20190507} can be
+accessed which contains all the data we use here.
+
+We {\it nota bene} a few things. First, the quantity {\tt aperJky3}
+and {\tt aperJky3Err} are found in the {\tt wserv1000MapRemeasAver}
+and {\tt wserv1000MapRemeasurement}, so care has to be taken to return
+unique column names (otherwise e.g.
+\href{http://docs.astropy.org/en/stable/io/fits/}{astropy.io.fits}
+will crash).  As such, we alias {\tt aver.aperJky3} to {\tt
+aperJky3Aver} and likewise for the error quantity. Aliases will be
+necessary in some cases anyway, because some queries can be done
+sensibly on multiple instances of the same table. Other times, one may
+join tables on quantities such as {\tt catalogueID} or {\tt
+apertureID}, where you are meaning the same thing, but aliases are then necessary 
+for SQLServer to correctly comprehend the query.
+
+Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
+used directly. To return values in degrees, use a selection with an alias, e.g. 
+{\tt RA as RADeg} and {\tt DEC as DECDeg}. Other relevant query examples can be found in the
+GitHub repository, under WSA\_VSA/SAMPLE\_SQL\_QUERIES, or the SQLCookbook in the WSA or VSA.
+
+\onecolumn
+\input{SQL_examples_WSA}
+\twocolumn
+
+\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL_VSA}
+In a very similar manner to the WSA, we give here the details on how to access
+the VISTA Science Archive (VSA)
+
+At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
+with these credentials::
+\begin{itemize}
+    \item Username: {\tt VSERV1000} 
+    \item password: {\tt highzqso} 
+    \item community: {\tt proprietary}
+\end{itemize}
+Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
+Query} page is where the database release to use is {\tt
+VSERV1000v20190508}. The queries are the same as those used in the
+WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
+with {\tt wserv1000} should be replaced with {\tt vserv1000}.
+
+\section{Updated VH$z$Q Sample}
 \label{app:qso_sample}
-{\bf In the submitted version of this paper, we had 463 QSOs selected from the
-literature which had $z\geq5$, which we thought was the complete sample except a
-few that were published in 2019.
-
-When we posted the submitted paper onto arXiv\footnote{http://www.arxiv.org}, we
-had two responses, one from Jinyi Yang, who pointed out that we missed QSOs in
-\cite{YangJ2018a} and Krisztina Perger, who also mentioned that we had
-missed $sim40$ QSOs and pointed us to her catalogue of
-QSOs\footnote{http://astro.elte.hu/~perger/catalog.html}. We downloaded Tables
-2,3 \& 4 from \cite{YangJ2018a} using
-Vizier\footnote{http://vizier.u-strasbg.fr/} and found all matches with 
-$2\arcsec$ and added the remaining objects that had $z\geq5$, one object  from
-Table 3, SUHAWJ1016+2541, and 15 from Table 4, see Table~\ref{tab:new_qsos}. We
-also downloaded the 20190514 version of the Perger catalogue and X-matched that,
-finding all of the matches with $2\arcsec$ and looked for non-matches.
-
-However, we spotted some inconsistences between the names of some of the QSOs
-in the Perger catalogue and decimal equatorial coordinates and pointed these
-out, and very rapidly Perger responded having fixed their catalogue. After
-further checks we found 10 objects (see Table~\ref{tab:disagree_objs}) that were
-in both catalogues that there was disagreement on the coordinates. In some cases it
-was clear from the names that either we (Ross \& Cross) had made a typo, or
-Perger had. In most other cases a search of the literature gave a clear answer. 
-Two particular odd examples were SDSSJ0835+3227 and VA-13492, found in the
-Perger catalogue. In both cases the coordinates looked similar to SDSSJ0835+3217 
-and SDSSJ1040-1155 respectively and the redshifts were identical to these QSOs,
-which alerted us to a potential problem. These QSOs could be traced back in the literature: in
-the first case both QSOs are in \cite{Banados2016} and in the second case is 
-VA-13492  is in \cite{Flesch2015} which refers back to \cite{Douglas2007}
-although the latter only seems to only contain SDSSJ1040-1155.
-In the case of SDSSJ0835+3227, we checked the SDSS-z band images\footnote{https://dr15.sdss.org}, and found a bright source at
-the position of SDSSJ0835+3217 and no source at the position of SDSSJ0835+3227, see
-Figure~\ref{fig:check_obj}. In the case of VA-13492, the I-band magnitude was
-equivalent to SDSSJ1040-1155 (I=25.9 mag), so we have decided that both of these objects
-have been transcribed incorrectly sometime in the past.
-
-The objects from the submitted version of Ross \& Cross that have changed
-position are flagged in Table~\ref{tab:disagree_objs} and the difference in position is
-shown. Some of these are rounding errors using coordinates that were to the
-nearest arcsec or $4\arcsec$ if it was rounded to the nearest hour, minute,
-second in RA, some were typos from reentering coordinates and these demonstrate
-that it is always better to download electronic catalogues and use decimal coordinates.
-Perger has also updated their catalogue and the 20190724 version matches our
-catalogue. A final test of matching to with $1\arcsec$ found another difference:
-we had downloaded the OGLEJ015531-75 coordinates from the published paper and
-Perger had done so from the submitted arXiv paper, and it seems that
-\cite{Kozlowski2019} made a minor update to their values in between.
-
-We also excluded DES0141-54, that was included in the Perger catalogue, since
-this came from a conference proceedings \cite{Belladitta2018}, which did not
-have arcsecond precision in its coordinates, so our matched-aperture photometry
-may have been in an incorrect position.
-
-Altogether we found that our final catalogue has 488 $z\geq$ QSOs. The new QSOs
-are all shown in Table~\ref{tab:new_qsos}.}
+{\bf In the journal submitted version of this paper, as well as the
+arXiv v1, we had 463 VH$z$Qs selected from the literature which we
+thought was the complete sample.  However, there were 25 (twenty-five)
+objects which should have been in our sample but were not (priv. comm
+from Jinyi Yang and Krisztina Perger).
+
+We downloaded Tables 2, 3 \& 4 from \cite{YangJ2018a} and found all
+matches with $2\arcsec$ and added the 16 objects that had $z\geq5$;
+one object from Table 3 (SUHAW J1016+2541) and 15 from Table 4, see
+Table~\ref{tab:new_qsos}.
+
+We initially downloaded the 20190514 version of the Perger
+catalogue\footnote{http://astro.elte.hu/~perger/catalog.html} again
+matching on a $2\arcsec$ radius.  We found 10 objects (see
+Table~\ref{tab:disagree_objs}) that were in both catalogues but had
+disagreement on the coordinates.  Two particular odd examples were
+SDSSJ0835+3227 and VA-13492.  In both cases the coordinates looked
+similar to SDSSJ0835+3217 and SDSSJ1040-1155, respectively, and the
+redshifts were identical to these quasars.
+
+In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
+images\footnote{https://dr15.sdss.org}, and found a bright source at
+the position of SDSSJ0835+3217 and no source at the position of
+SDSSJ0835+3227, see Figure~\ref{fig:check_obj}. In the case of
+VA-13492, the $i$-band magnitude was equivalent to SDSS J1040-1155
+($i=25.9$ mag), so we have decided that both of these objects have
+been transcribed incorrectly sometime in the past.
+
+The objects from the submitted version of Ross \& Cross that have
+changed position are flagged in Table~\ref{tab:disagree_objs}. The
+Perger catalogue has been updated to the 20190724 version (which
+matches our catalogue). A final test of matching to with $1\arcsec$
+found another difference: we had downloaded the OGLEJ015531-75
+coordinates from the published paper and Perger had done so from the
+submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
+to the positional values in between.
+
+We exclude DES0141-54 that is in the Perger catalogue from our final
+sample. This object came from a conference proceedings
+\cite{Belladitta2018}, which did not have arcsecond precision in its
+coordinates so we could not perform our matched-aperture photometry.
+
+Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}
 
@@
 
+\iffalse
 \begin{table*}
@@
 \end{table*}
+\fi
 
@@
 
-\section{Near-Infrared WFCAM Science Archive SQL queries}\label{sec:SQL_WSA}
-Here we give the recipe and SQL that returned the near-infrared photometry 
-for the VH$z$Qs from the  WFCAM Science Archive.
-
-The data are on the WFCAM Science Archive: \href{wsa.roe.ac.uk}{\tt wsa.roe.ac.uk}. 
-Access the User Login form \href{WFCAM Science Archive}{\tt wsa.roe.ac.uk/login.html} 
-with these credentials::
-\begin{itemize} 
-    \item Username: {\tt WSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt nonsurvey}
-\end{itemize}
-Then going to the
-\href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
-Query}} page the Database release {\tt WSERV1000v20190507} can be
-accessed which contains all the data we use here.
-
-We {\it nota bene} a few things. First, the quantity {\tt aperJky3}
-and {\tt aperJky3Err} are found in the {\tt wserv1000MapRemeasAver}
-and {\tt wserv1000MapRemeasurement}, so care has to be taken to return
-unique column names (otherwise e.g.
-\href{http://docs.astropy.org/en/stable/io/fits/}{astropy.io.fits}
-will crash).  As such, we alias {\tt aver.aperJky3} to {\tt
-aperJky3Aver} and likewise for the error quantity. Aliases will be
-necessary in some cases anyway, because some queries can be done
-sensibly on multiple instances of the same table. Other times, one may
-join tables on quantities such as {\tt catalogueID} or {\tt
-apertureID}, where you are meaning the same thing, but aliases are then necessary 
-for SQLServer to correctly comprehend the query.
-
-Second, the {\tt RA} and {\tt DEC} values returned by the WSA are in radians, if
-used directly. To return values in degrees, use a selection with an alias, e.g. 
-{\tt RA as RADeg} and {\tt DEC as DECDeg}. Other relevant query examples can be found in the
-GitHub repository, under WSA\_VSA/SAMPLE\_SQL\_QUERIES, or the SQLCookbook in the WSA or VSA.
-
-\onecolumn
-\input{SQL_examples_WSA}
-\twocolumn
-
-\section{Near-Infrared VISTA Science Archive SQL queries}\label{sec:SQL_VSA}
-In a very similar manner to the WSA, we give here the details on how to access
-the VISTA Science Archive (VSA)
-
-At the \href{http://horus.roe.ac.uk/vsa/login.html}{VSA Login}, enter 
-with these credentials::
-\begin{itemize}
-    \item Username: {\tt VSERV1000} 
-    \item password: {\tt highzqso} 
-    \item community: {\tt proprietary}
-\end{itemize}
-Then the \href{http://horus.roe.ac.uk:8080/vdfs/VSQL_form.jsp}{Freeform SQL
-Query} page is where the database release to use is {\tt
-VSERV1000v20190508}. The queries are the same as those used in the
-WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
-with {\tt wserv1000} should be replaced with {\tt vserv1000}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-09 tex/VHzQ.tex
Updated the Appendix, modifying Table C2 and text

@@
 We initially downloaded the 20190514 version of the Perger
-catalogue\footnote{http://astro.elte.hu/~perger/catalog.html} again
-matching on a $2\arcsec$ radius.  We found 10 objects (see
-Table~\ref{tab:disagree_objs}) that were in both catalogues but had
-disagreement on the coordinates.  Two particular odd examples were
-SDSSJ0835+3227 and VA-13492.  In both cases the coordinates looked
-similar to SDSSJ0835+3217 and SDSSJ1040-1155, respectively, and the
-redshifts were identical to these quasars.
-
-In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
+catalogue\footnote{http://astro.elte.hu/$\sim$perger/catalog.html} again
+matching on a $2\arcsec$ radius. We found several objects that were in both
+catalogues but had disagreement on the coordinates. Most of these were
+fixed by checking the literature for the original catalogue.
+
+There were two QSOs in the Perger catalogue which could not be immediately fixed
+by looking up the original coordinates in the literature: SDSSJ0835+3227 and VA-13492.
+In both cases the coordinates looked similar to SDSSJ0835+3217 and
+SDSSJ1040-1155, respectively, and the stated redshifts were identical to these
+quasars. In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
 images\footnote{https://dr15.sdss.org}, and found a bright source at
@@
 ($i=25.9$ mag), so we have decided that both of these objects have
-been transcribed incorrectly sometime in the past.
-
-The objects from the submitted version of Ross \& Cross that have
-changed position are flagged in Table~\ref{tab:disagree_objs}. The
+been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
+transcription error seems to have occurred after \cite{Douglas2007} and is in
+\cite{Flesch2015}, so it probably occurred in the \cite{Flesch2015}.
+
+The five objects from the submitted version of Ross \& Cross that have
+changed position are in Table~\ref{tab:disagree_objs}. The
 Perger catalogue has been updated to the 20190724 version (which
-matches our catalogue). A final test of matching to with $1\arcsec$
-found another difference: we had downloaded the OGLEJ015531-75
-coordinates from the published paper and Perger had done so from the
-submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
-to the positional values in between.
+matches our catalogue). %%A final test of matching to with $1\arcsec$
+%%found another difference: we had downloaded the OGLEJ015531-75
+%%coordinates from the published paper and Perger had done so from the
+%%submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
+%%to the positional values in between.
 
@@
 coordinates so we could not perform our matched-aperture photometry.
-
 Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}
@@
 
-\iffalse
+%\iffalse
 \begin{table*}
@@
 \hline  \hline
-QSO & ra & dec & difference & isCRDiff & Issue \\
- & deg & deg & arcsec & &  \\
+QSO & ra & dec & redshift & difference \\
+ & deg & deg & & arcsec  \\
 \hline
-OGLEJ015531-752807 & +28.8792083 & -75.4686111 & 1.1 & No & 1 \\
-%% Same name diff pos/redshift from v1
-PSOJ009.7355-10.4316 & +9.7355079 & -10.4316386	& 0. & Yes & 3 \\
-ATLASJ025.6821-33.4627 & +25.6821972 & -33.4626300 & 0. & Yes & 3 \\ 
-SDWISEJ0155+0415 & +28.8886666 & +4.2518725	& 0. & Yes & 3 \\
-PSOJ065.4085-26.9543 & +65.4085370 & -26.9543351 & 0. & Yes & 3 \\ 
-VDESJ0454-4448 & +73.5074500 & -44.8086400 & 0.	& Yes & 3 \\ 
-DELSJ1048-0109 & +162.0795417 & -1.1611694 & +12.1 & Yes & 2,3,4 \\
-SDSSJ1306+0356 & +196.5344701 & +3.9406556 & 0.	& Yes & 3 \\
-PSOJ217.0891-16.0453 & +217.0891328	& -16.0453608 & 0. & Yes & 3 \\
-SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & +150.0 & Yes & 2 \\
-DELSJ1559+2212 & +239.7878750 & +22.2040083	& +3.0 & Yes & 2 \\ 
-ATLASJ332.8017-32.1036 & +332.8017500 &	-32.1035556	& +3.2 & Yes & 2,3 \\
-PSOJ340.2041-18.6621 & +340.2041700	& -18.6621700 & 0. & Yes & 3 \\ 
-VIKJ2318-3113 & +349.5764625 &-31.2295417 & 239.9 & Yes & 2,3 \\
-PSOJ359.1352-06.3831 & +359.1352149	& -6.3831264 & 0. & Yes & 3 \\
-%%Krisztina wrong\ldots
-SDSSJ1621+5155 & +245.2538300 & +51.9302200	& 0. & No & 5 \\
-DELSJ1135+5011 & +173.7872080 & +50.1924999	& 0. & No & 5 \\
-DELSJ0839+3900 & +129.9453330 & +39.0031944	& 0. & No & 5 \\
-%% More complex 
-SDSSJ0835+3227 & --- & --- & --- & No & 6 \\
-VA-13492 & --- & --- & --- & No & 6 \\
+%% QSOs where pos changed (same name)
+DELSJ1048-0109 & +162.0795417 & -1.1611694 & 6.678 & 12.1 \\
+SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & 6.04 & 150.0 \\
+DELSJ1559+2212 & +239.7878750 & +22.2040083	& 6.07 & 3.0 \\
+ATLASJ332.8017-32.1036 & +332.8017500 & -32.1035556	& 6.3394 &	3.2 \\
+VIKJ2318-3113 & +349.5764625 & -31.2295417 & 6.4435 & 239.9 \\
 \hline  \hline
 \end{tabular}
-\caption{{\bf QSOs in disagreement between RC and Perger or which have been
-updated since the submitted paper.
-This table shows all of the QSOs where there has been a disagreement or a
-change. All of those marked 'Yes' were in the submitted paper and have been
-changed since, and the final column lists the reason(s) for inclusion in the
-table. The numbers refer to the following issues:
-1) Coordinate update in original reference, from submitted to accepted; 
-2) Coordinate different in RC submitted;
-3) Redshift different in RC submitted, typically very small changes;
-4) Our coords incorrect, but KP had 2 entries, one also incorrect;
-5) Coordinates incorrect in KP;
-6) Two objects with similar looking coordinates and identical redshifts. These
-appear to be incorrect entries further back in the literature;}
-}
+\caption{{\bf QSOs where the coordinates are in  disagreement between
+the submitted (arXiv v1) and accepted version of the paper.}}
 \label{tab:disagree_objs}
 \end{table*}
-\fi
+%\fi
 

### 2019-09-10 tex/VHzQ.tex
Updated Appendix to remove SDSSJ0835+3227 details, included figure

@@
 
-There were two QSOs in the Perger catalogue which could not be immediately fixed
-by looking up the original coordinates in the literature: SDSSJ0835+3227 and VA-13492.
-In both cases the coordinates looked similar to SDSSJ0835+3217 and
-SDSSJ1040-1155, respectively, and the stated redshifts were identical to these
-quasars. In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
-images\footnote{https://dr15.sdss.org}, and found a bright source at
-the position of SDSSJ0835+3217 and no source at the position of
-SDSSJ0835+3227, see Figure~\ref{fig:check_obj}. In the case of
-VA-13492, the $i$-band magnitude was equivalent to SDSS J1040-1155
-($i=25.9$ mag), so we have decided that both of these objects have
-been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
+There was one QSO in the Perger catalogue which could not be immediately fixed
+by looking up the original coordinates in the literature: VA-13492.
+In this case the coordinates looked similar to SDSSJ1040-1155, and
+the stated redshift was identical, $z=5.44$. Additionally, in this case,
+the $i$-band magnitude was equivalent to SDSS J1040-1155
+($i=25.9$ mag), so we have decided that both of these objects are the same and 
+have been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
 transcription error seems to have occurred after \cite{Douglas2007} and is in
-\cite{Flesch2015}, so it probably occurred in the \cite{Flesch2015}.
+\cite{Flesch2015}, so it probably occurred in \cite{Flesch2015}.
 
@@
 
-\begin{figure}
-  %% trim=l b r t
-  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
-  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083525+3217.jpg}
-  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083526+3227.jpg}
-  \centering
-  %\vspace{-12pt} 
-  \caption[]
-  {{\bf Cutouts from SDSS z-band images retrieved from SDSS-SkyServer for the
-  coordinates of SDSSJ083535+3217 and SDSSJ083526+3227. Both of these objects
-  appear in \cite{Banados2016} and subsequently in the Perger catalogue, but
-  only SDSSJ083535+3217 is matched to an SDSS source. Since SDSSJ083526+3227
-  has an SDSS name, and is apparently a $z=5.89$ QSO, it should have a z-band
-  detection.}}
-  \label{fig:check_obj}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-10 tex/VHzQ.tex
VHzQ.tex updated

@@
 \label{app:qso_sample}
-{\bf In the journal submitted version of this paper, as well as the
-arXiv v1, we had 463 VH$z$Qs selected from the literature which we
-thought was the complete sample.  However, there were 25 (twenty-five)
-objects which should have been in our sample but were not (priv. comm
-from Jinyi Yang and Krisztina Perger).
-
-We downloaded Tables 2, 3 \& 4 from \cite{YangJ2018a} and found all
-matches with $2\arcsec$ and added the 16 objects that had $z\geq5$;
-one object from Table 3 (SUHAW J1016+2541) and 15 from Table 4, see
-Table~\ref{tab:new_qsos}.
-
-We initially downloaded the 20190514 version of the Perger
-catalogue\footnote{http://astro.elte.hu/$\sim$perger/catalog.html} again
-matching on a $2\arcsec$ radius. We found several objects that were in both
-catalogues but had disagreement on the coordinates. Most of these were
-fixed by checking the literature for the original catalogue.
-
-There was one QSO in the Perger catalogue which could not be immediately fixed
-by looking up the original coordinates in the literature: VA-13492.
+{\bf Between the journal submitted version of this paper (which was
+also the arXiv v1) we updated the sample of VH$z$Qs from a total of
+463 objects to 488 objects.  16 of these objects were from
+\cite{YangJ2018a} and 9 objects were added after discussions with
+Krisztina Perger, with the relevant catalog found
+\href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.
+We do not include the object DES0141-54 \citep{Belladitta2018}, since we were unable to 
+obtain arcsecond level coordinates to perform our matched-aperture photometry.
+We also update the positions of five objects, see Table~\ref{tab:disagree_objs}.
+
+One object in the Perger catalogue, VA-13492 we could not immediately cross-match. 
 In this case the coordinates looked similar to SDSSJ1040-1155, and
-the stated redshift was identical, $z=5.44$. Additionally, in this case,
-the $i$-band magnitude was equivalent to SDSS J1040-1155
-($i=25.9$ mag), so we have decided that both of these objects are the same and 
-have been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
-transcription error seems to have occurred after \cite{Douglas2007} and is in
-\cite{Flesch2015}, so it probably occurred in \cite{Flesch2015}.
-
-The five objects from the submitted version of Ross \& Cross that have
-changed position are in Table~\ref{tab:disagree_objs}. The
-Perger catalogue has been updated to the 20190724 version (which
-matches our catalogue). %%A final test of matching to with $1\arcsec$
-%%found another difference: we had downloaded the OGLEJ015531-75
-%%coordinates from the published paper and Perger had done so from the
-%%submitted arXiv paper - and \cite{Kozlowski2019} made a minor update
-%%to the positional values in between.
-
-We exclude DES0141-54 that is in the Perger catalogue from our final
-sample. This object came from a conference proceedings
-\cite{Belladitta2018}, which did not have arcsecond precision in its
-coordinates so we could not perform our matched-aperture photometry.
-Our final catalogue has 488 $z\geq$ QSOs, see Table~\ref{tab:new_qsos}.}
-
-%% Table New QSOs --> name, ra, dec, redshift, reference, source
-%% Table QSOs in disagreement --> name, correct pos, difference, literature,
-% ErrorInCR, TypeOfError
+the stated redshift was identical, $z=5.44$. Additionally the $i$-band magnitude 
+was equivalent to SDSS J1040-1155
+($i=25.9$ mag). SDSS J1040-1155 is first reported in \citet{Douglas2007} 
+and a transcription error seems to have occurred in \citet{Flesch2015}.
+}
 
@@
 \hline  \hline
-QSO & ra & dec & redshift & reference & source  \\
+Object Name                      & R.A.               & Decl.  &  redshift  & difference \\
+                                          & / deg             & / deg  &                & arcsec  \\
 \hline
-SUHAWJ1016+2541 & +154.1571250 & +25.6921944 & +5.64 &Yang2018 & Yang2018 \\
-PS1J0052+4556 & +13.1810417	& +45.9422306 & +5.31 & Yang2018   & Yang2018 \\
-PS1J0332+1811 & +53.1540833	& +18.1998000 & +5.12 & Yang2018   & Yang2018 \\
-PS1J0511-0754 & +77.9780417	& -7.9123056 & +5.13 & Yang2018 & Yang2018 \\
-PS1J0616-1338 & +94.1015833	& -13.6351111	& +5.58 & Yang2018 & Yang2018 \\
-PS1J0757-0002 & +119.4412500 & -0.0336361 & +5.54 &	Yang2018 & Yang2018 \\
-PS1J0817-1633 & +124.2527500 & -16.5581361 & +5.06 & Yang2018 & Yang2018 \\
-PS1J1034-1233 & +158.6535833 & -12.5618028 & +5.51 & Yang2018 & Yang2018 \\
-PS1J1057-1758 & +164.3650000 & -17.9754722 & +5.34 & Yang2018 & Yang2018 \\
-PS1J1121-0718 & +170.4318750 & -7.3110250 & +5.71 & Yang2018 & Yang2018 \\
-PS1J1137-1049 & +174.3973750 & -10.8262611 & +5.50 & Yang2018 & Yang2018 \\
-PS1J1310-0639 & +197.5546250 & -6.6643222 & +5.06 & Yang2018  & Yang2018 \\
-PS1J1313-2617 & +198.3585833 &-26.2893972 & +5.54 & Yang2018 & Yang2018 \\
-PS1J1427-0503 & +216.8398333 & -5.0647333 & +5.08 & Yang2018 & Yang2018 \\
-PS1J1533-1810 & +233.4990000 &-18.1742250 & +5.03 & Yang2018 & Yang2018 \\
-PS1J2033+1218 & +308.2936250 & +12.3143028 & +5.11 & Yang2018 & Yang2018 \\
-OGLEJ015531-752807 & +28.8792083 & -75.4686111 & +5.09 & Kozlowski2019 & Perger
-\\
-TNJ0924-2201 & +141.0830000	& -22.0281940 & +5.19 & vanBreugel1999 & Perger \\
-XMMJ125329+30 & +193.3725460 & +30.9276197 & +5.08 & Khorunzhev2017 & Perger \\
-SDSSJ141912.03+53 & +214.8001310 &+53.6775646 & +5.38 & Paris2017 & Perger \\
-TGSSJ1530+1049 & +232.7079167 & +10.8253060	& +5.72 & Saxena2018 & Perger \\
-PSOJ352.4034-15.337 & +352.4034850 & -15.3373500 & +5.84 & Banados2018 & Perger
-\\
-PSOJ0046-2837 & +11.5985420	& -28.6298170 & +5.99 & Venemans2018 & Perger \\
-VIKJ2318-3029 & +349.6379420 & -30.4926030 & +6.1458 & Venemans2018 & Perger \\
-HSC1732+6531 & +263.1796583	& +65.5204139 & +6.60 & Songaila2018 & Other \\
+%% QSOs where pos changed (same name)
+DELS J1048-0109               & +162.0795417 & -1.1611694        & 6.678   &     12.1 \\
+SHELLQs J1429-0002          & +217.3342500 & -0.0353889        & 6.04    &  150.0 \\
+DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
+ATLAS J332.8017-32.1036 & +332.8017500 & -32.1035556      & 6.3394  &    3.2 \\
+VIK J2318-3113                  & +349.5764625 & -31.2295417      & 6.4435  &  239.9 \\
 \hline  \hline
 \end{tabular}
-\caption{{\bf New QSOs added to the paper since the submitted version. }
+\caption{
+{\bf Five quasars with updated coordinates.}
 }
-\label{tab:new_qsos}
-\end{table*}
-
-%\iffalse
-\begin{table*}
-\begin{tabular}{l r r r r r}
-\hline  \hline
-QSO & ra & dec & redshift & difference \\
- & deg & deg & & arcsec  \\
-\hline
-%% QSOs where pos changed (same name)
-DELSJ1048-0109 & +162.0795417 & -1.1611694 & 6.678 & 12.1 \\
-SHELLQsJ1429-0002 & +217.3342500 & -0.0353889 & 6.04 & 150.0 \\
-DELSJ1559+2212 & +239.7878750 & +22.2040083	& 6.07 & 3.0 \\
-ATLASJ332.8017-32.1036 & +332.8017500 & -32.1035556	& 6.3394 &	3.2 \\
-VIKJ2318-3113 & +349.5764625 & -31.2295417 & 6.4435 & 239.9 \\
-\hline  \hline
-\end{tabular}
-\caption{{\bf QSOs where the coordinates are in  disagreement between
-the submitted (arXiv v1) and accepted version of the paper.}}
 \label{tab:disagree_objs}
 \end{table*}
-%\fi
 

### 2019-09-10 tex/VHzQ.tex
referees_reply.txt updated
Updated text in Sections 2.2 and 3.1 including Tables 2, 4 and 5

--- 2019-09-10 tex/VHzQ.tex
@@
 \hline 
-5.00         & 1180          &  ---   \\
-5.70         & 1000          &  ???  \\
-6.00         &   937          &  170   \\
-6.19         &   900          &  86   \\
+5.00         & 1180          &  488   \\
+5.70         & 1000          &  273  \\
+6.00         &   937          &  174   \\
+6.19         &   900          &  87   \\
 6.50         &    845         &  40   \\
@@
 
-  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars
-  are detected in the VISTA VSA database with 130 objects in common with
+  We detect 367 unique quasars in the WFCAM WSA database, 237 quasars
+  are detected in the VISTA VSA database with 131 objects in common with
   both WFCAM and VISTA data.  We give the necessary SQL queries syntax
@@
     \hline  
-    Any band ($ZYJHK/K_{s}$)    &  449  (97.0) \\
-    $Z$-band                            &  75  (16.2) \\
-    $Y$-band                            &  273  (59.0) \\
-    $J$-band                              &  447  (96.5) \\
-    $H$-band                            &  269  (58.1) \\
-    $K$ or $Ks$-band                &  322  (69.5) \\
+    Any band ($ZYJHK/K_{s}$)    &  473  (96.9) \\
+    $Z$-band                            &  81  (16.5) \\
+    $Y$-band                            &  289  (59.2) \\
+    $J$-band                              &  471  (96.5) \\
+    $H$-band                            &  277  (56.8) \\
+    $K$ or $Ks$-band                &  343  (70.2) \\
     \hline  \hline
@@
 
-There are 14 objects that have no NIR detections. 3 of these
+There are 15 objects that have no NIR detections. 3 of these
 (PSOJ053.9605-15.7956, PSO J056.7168-16.4769 and DELSJ0411-0907) have
@@
 $\delta<0$ deg and have not been observed (or at least the data is not
-in the VSA archive yet). 5 objects are at a declination $\delta \geq
+in the VSA archive yet). 6 objects are at a declination $\delta \geq
 +60$ deg are too far north for UKIRT and cannot be observed.
@@
   \subsubsection{Comparing WFCAM and VISTA}
-  There are 130 quasars observed in the overlapping area between WFCAM
+  There are 131 quasars observed in the overlapping area between WFCAM
   and VISTA. We used the {\tt VegaToAB} values to put these objects on
@@
   significant offset is the $Y$-band. All of the VISTA averages are
-  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
-  band comparison may be affected the different shapes of the filters,
+  negative and all of the WFCAM ones are positive except in the J-band where
+  VISTA is marginally positive and WFCAM marginally negative.
+  The $Ks$ versus $K$ band comparison may be affected the different shapes of the filters,
   with $K$ being significantly wider than $K_s$, able to detect light at
@@
       \hline
-      $Z$                 &  23.2 	& 3 \\
-      $Y$                 &  57.3 	& 53 \\
-      $J$                  &    2.1 	& 106 \\
-      $H$                 &  45.8     &  96 \\
-      $K_{\rm s}$/$K$ &  25.2     & 110 \\
+      $Z$                 &  7.2 	& 3 \\
+      $Y$                 &  59.1 	& 62 \\
+      $J$                  &    6.3 	& 111 \\
+      $H$                 &  41.7     &  103 \\
+      $K_{\rm s}$/$K$ &  15.1     & 114 \\
       \hline  \hline
@@
   < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
-  selects two quasars with large, $\delta$mag $>0.2$mag differences
-  between the WSA and VSA. These are SDSSJ0349+0034 and
-  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
-  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
-  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
-  = 19.38$\pm$0.04.
+  selects one quasar\footnote{In the submitted version arXiv:1906.06974v1, we
+  claimed a second QSO, SDSSJ2220-0101, but while updating the catalogue, see
+  App~\ref{app:qso_sample}, we found a small number of WSA matched aperture
+  photometry had been assigned to incorrect apertures, mainly for this source.} 
+  with large, $\delta$mag $>0.2$mag differences between the WSA and VSA.
+  This is SDSSJ0349+0034, which has a WSA $K$-band magnitude of 21.03$\pm$0.24
+  mag AB, while for the VSA $K_s$-band this is 20.21$\pm$0.10 mag AB\footnote{In
+  the submitted version, arXiv:1906.06974v1, these the Vega magnitudes were
+  published instead of the AB for this QSO.}.
 

### 2019-09-11 tex/MNRAS_submission/rv1/referees_reply.txt
referees_reply.txt updated
MNRAS_submission/rv1/referees_reply.txt; VHzQ.tex update

@@
 
-	We note that after the submission of the original manuscript it was brought to our attention
-	(K. Perger; priv. comm) that we were missing a handful of confirmed z>5 quasars.
-	As such, our database has increased by 25 objects for a total of 488 VHzQs.
+	We note that after the submission of the original manuscript
+	it was brought to our attention (K. Perger; priv. comm) that
+	we were missing a 25 confirmed z>5 quasars.  As such, our
+	database has increased by 25 objects for a total of 488 VHzQs.
 
-	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA Science Archive (VSA) from scratch
-	with the set of updated objects. This uncovered a small matching bug for three objects in the WSA
-        (no issues were found in the VSA rerun). One of these objects, however, is SDSSJ2220-0101, which
-	we thought had large photometric changes but now acknowledge this was due to an incorrect
-	apertureID measurement. The updated photometry for SDSSJ2220-0101 has the VSA J-band
-	magnitude 19.38+/-0.04 and a WSA magnitude 19.24+/-0.09.
+	We also fully re-ran the WFCAM Science Archive (WSA) and VISTA
+	Science Archive (VSA) from scratch with the set of updated
+	objects. This uncovered a small matching bug for three objects
+	in the WSA (no issues were found in the VSA rerun). One of
+	these objects, however, is SDSS J2220-0101, which we thought
+	had large photometric changes but now acknowledge this was due
+	to an incorrect apertureID measurement. The updated photometry
+	for SDSS J2220-0101 has the VSA J-band magnitude 19.38+/-0.04
+	and a WSA magnitude 19.24+/-0.09.
 
@@
 		differences between WFCAM and VISTA magnitudes in one band."
+
+	We have also added an Appendix to note the update to the overall catalog.
 

### 2019-09-11 tex/VHzQ.tex
MNRAS_submission/rv1/referees_reply.txt; VHzQ.tex update

--- 2019-09-10 tex/VHzQ.tex
@@
 in multiple bands of SDSS J0959+0227, and very marginally in the
-$Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and
-SDSS J2220-0101 had significant differences between their WFCAM and
-VISTA magnitudes in one band.  With supermassive black hole accretion
+$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, 
+shows significant differences between WFCAM and VISTA magnitudes in one band
+With supermassive black hole accretion
 likely to be redshift invariant up to very high-redshift, further
@@
   < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
-  selects two quasars with large, $\delta$mag $>0.2$mag differences
-  between the WSA and VSA. These are SDSSJ0349+0034 and
-  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
-  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
-  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
-  = 19.38$\pm$0.04.
+  selects one quasar, SDSS J0349+0034, 
+  with large, $\delta$mag $>0.2$mag differences between the WSA and VSA.
+  SDSS J0349+0034, has a WSA $K$-band magnitude of 21.03$\pm$0.24
+  mag AB, while for the VSA $K_s$-band this is 20.21$\pm$0.10 mag AB.
 
@@
 Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529.
-2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability.
+SDSS J0349+0034 was the only object to have significant differences between their WFCAM and VISTA magnitudes in one band, potentially indicating variability.
 \end{itemize}
@@
 \cite{YangJ2018a} and 9 objects were added after discussions with
-Krisztina Perger, with the relevant catalog found
+Krisztina Perger, with the relevant catalog found at 
 \href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.

### 2019-09-11 temp/VHzQ_pre2019/VHzQ_20181108.tex
tex/older_tex/ removed

--- 2018-11-05 tex/older_tex/WW4C_VHzQ_20181105.tex
@@
 central black hole. But understanding how dust first forms and appears
-in the central engine remains an open question.
+in the central engine remains an open question \citep{WangR2008, WangR2011}.
 
@@
 \section{Data}
-In Table~\ref{tab:THE_TABLE} we present our dataset and 
-we have assembled this in the following manner.  First
-we compile the list of all known, spectroscopically confirmed quasars
-from the literature. Most of these objects are easily identified by
-their broad Ly$\alpha$ emission line, \nv emission and characteristic
-shape blueward of 1215\AA\ rest. As we shall see, some of the more
-recently discovered objects are close to the galaxy luminosity
+In Table~\ref{tab:THE_TABLE} we present our dataset and we have
+assembled this in the following manner.  First we compile the list of
+all known, spectroscopically confirmed quasars from the
+literature. Most of these objects are easily identified by their broad
+Ly$\alpha$ emission line, \nv emission and characteristic shape
+blueward of 1215\AA\ in the rest-frame. As we shall see, some of the
+more recently discovered objects are close to the galaxy luminosity
 function characteristic luminosity $M^{*}$, and some have relatively
@@
 7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
-discussion into spectral features and line strengths, and take as given 
-the published spectra and identifications.
-
-We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset. The optical data comes from the 
-Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
-survey \citep{Chambers2016} and the Dark Energy Camera \citep{Flaugher2015}, 
-including the Dark Energy Survey \citep[DES;][]{Flaugher2005} and 
-the Dark Energy Camera Legacy Survey \citep[DECaLS]{Dey2018}.
-
-Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
-on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
-delivering exquisite multi-band photometry data
-\citep[][]{Aihara2018b} the five broad bands $grizy$.
-
-The near-infrared data comes from two primary sources. First, the Wide
-Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
-Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
-the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
-And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
-\citep[Visible and Infrared Survey Telescope for
-Astronomy;][]{Emerson2006, Dalton2006}.
-
-We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
-the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
-In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
-\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{wise2.ipac.caltech.edu/docs/release/allwise/}}.
-
-Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
+discussion into spectral features and line strengths, and take as
+given the published spectra and identifications.
+
+We then obtain optical, near-infrared and mid-infrared photometry for
+the spectral dataset. The optical data comes from the Panoramic Survey
+Telescope and Rapid Response System (Pan-STARRS) survey
+\citep{Chambers2016}. The near-infrared data comes from two sources:
+first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but
+not exclusively, as part of the UKIRT Infrared Deep Sky Survey
+\citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on
+the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared,
+$\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared
+Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+
+For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
 of the filters in question.
@@
 \subsection{Near-infrared photometry}~\label{sec:NIR_data} 
-Due to their selection of being very faint/undetected in the
-observed-frame optical but bright in the observed frame near-infrared,
-VH$z$Qs are generally detected in the near-infrared $ZYJHK(s)$-bands
-\citep[$\approx$0.83-2.38$\mu$m; e.g., ][]{Peth2011}.
-
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
@@
 
+\section{Notes on Individual Objects}
+\input{/cos_pc19a_npr/data/highest_z_QSOs/notes_on_individual_objects}
+
 \section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180703.tex
tex/older_tex/ removed

--- 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180530.tex
@@
 \end{keywords}
+
+\section*{TO DOs}
+\begin{itemize}
+\item Urgh, but almost certainly want M$_{\rm BH}$; 
+\item May well wanna try and get M$_{\star}$ too...!! ; 
+\end{itemize}
 
@@
 \section{Data}
+\begin{figure*}
+  \includegraphics[width=18.0cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180613.pdf}
+  \centering
+  \caption[]
+  {The spectral bands used by different survey telescopes and that are relevant here.}
+  \label{fig:filters}
+\end{figure*}
 
@@
 
-%    \begin{figure}
-%      \includegraphics[height=8.0cm,width=8.0cm]
-%      {pdf/SDSS_Quasar_Nofz.pdf}
-%      \centering
-%      \caption[he selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands]
-%              {The selection of $z \sim 0.7$ LRGs using the SDSS $riz$-bands.}
-%      \label{fig:fig1}
-%    \end{figure}
-
-%    \begin{table}
-%    \begin{center}
-%    \setlength{\tabcolsep}{4pt}
-%    \begin{tabular}{lrrr}
-%    Sample Description  & Number in sample & North & South   \\
-%    \hline
-%    \label{tab:The_LRG_numbers}
-%    \end{tabular}
-%    \caption{}
-%    \end{center}
-%    \end{table}
-
 %    \begin{equation}
@@
 
+\begin{table}
+  \begin{center}
+    \setlength{\tabcolsep}{4pt}
+    \begin{tabular}{lrrr}
+      Sample Description  & Number in sample & North & South   \\
+      \hline
+      \label{tab:The_Numbers}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{table}
+
     \subsection{Very High-$z$ Quasars Detected in WISE}
@@
 \subsection{Colours}
+Figure~\ref{fig:Opt_colourredshift} presents the optical
+colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
+
+\begin{figure*}
+   \includegraphics[width=18.0cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180612.pdf}
+   \centering
+   \caption[]
+   {Optical colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
+   \label{fig:Opt_colourredshift}
+ \end{figure*}
+
+Figure~\ref{fig:Opt_colourredshift} presents the near-infrared 
+colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
+\begin{figure*}
+   \includegraphics[width=18.0cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180612.pdf}
+  \centering
+   \caption[]
+   {Infrared colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
+   \label{fig:filters}
+ \end{figure*}
 
@@
 growth are in lockstep.
+
+\subsection{L-$z$ Plane}
+\begin{figure*}
+  \includegraphics[width=18.0cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
+  \centering
+  \caption[]
+  {The spectral bands used by different survey telescopes and that are relevant here.}
+  \label{fig:filters}
+\end{figure*}
+
+\subsection{SEDs and Dust properties of the VH$z$Qs}
+\begin{figure*}
+  \includegraphics[width=18.0cm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
+  \centering
+  \caption[]
+  {The rest-frame properties of the VH$z$Qs. }
+  \label{fig:filters}
+\end{figure*}
 

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180704.tex
tex/older_tex/ removed

--- 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180703.tex
@@
 \begin{itemize}
-\item Urgh, but almost certainly want M$_{\rm BH}$; 
+\item Almost certainly want to compile M$_{\rm BH}$; 
 \item May well wanna try and get M$_{\star}$ too...!! ; 
@@
 \begin{figure*}
-  \includegraphics[width=18.0cm]
-  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180613.pdf}
+%%trim=l b r t
+  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
   \centering
@@
 \section{Results}
+ Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aliquam porta sodales est, vel cursus risus porta non.
+Vivamus vel pretium velit.
+Sed fringilla suscipit felis, nec iaculis lacus convallis ac.
+Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
+Etiam interdum tristique diam eu blandit.
+Donec in lacinia libero.
 
+\subsection{Detection Rates}
 \begin{table}
@@
 
+\subsection{Variability}
+Sed elit massa, eleifend non sodales a, commodo ut felis.
+Sed id pretium felis.
+Vestibulum et turpis vitae quam aliquam convallis.
+Sed id ligula eu nulla ultrices tempus.
+Phasellus mattis erat quis metus dignissim malesuada.
+Nulla tincidunt quam volutpat nibh facilisis euismod.
+Cras vel auctor neque.
+Nam quis diam risus.
+
+Nunc semper quam et leo interdum vulputate eu quis magna.
+Sed nec arcu at orci egestas convallis.
+Aenean quam velit, aliquam vitae viverra in, elementum vel elit.
+Nunc suscipit aliquet sapien a suscipit.
+Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla.
+Nullam eu augue id purus mollis dignissim sed et libero.
+Phasellus eget justo sed neque pellentesque egestas nec id arcu.
+Donec facilisis pulvinar sapien et fringilla.
+Suspendisse vestibulum rhoncus sapien id laoreet.
+Morbi et orci vitae tortor imperdiet imperdiet.
+In hac habitasse platea dictumst.
+Vivamus vel neque id mi ultrices tristique.
+Integer quam libero, ornare vel gravida in, feugiat a ante.
+Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi.
+Vestibulum nec mi justo, eget dapibus velit.
+
 \subsection{Very High-$z$ Quasars Detected in WISE}
 \citet{Blain2013} 
+Cras in laoreet mauris.
+Vivamus nec nulla a dui commodo adipiscing.
+Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies.
+Phasellus condimentum gravida tincidunt.
+Phasellus et mauris ac nibh vestibulum vehicula.
+Morbi et augue id purus gravida sagittis quis in sem.
+Phasellus quis risus bibendum eros luctus auctor.
 
 \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
+Proin non tempus velit.
+Etiam laoreet, enim nec scelerisque dictum, tortor massa tempor enim, id pretium justo quam ac lectus.
+Maecenas diam nibh, interdum at lobortis sit amet, dignissim et quam.
+Sed tincidunt faucibus risus, congue tempus nisl consectetur eget.
+Suspendisse venenatis turpis ut risus aliquam interdum.
+In at velit sed ligula dictum dignissim ut et dui.
+Curabitur ac scelerisque purus.
 
 \subsection{Colours}
+Pellentesque vel elit neque, in interdum lacus.
+Quisque sodales, nunc et luctus convallis, nisl dui luctus dui, at congue urna velit a nisl.
+Ut sit amet sapien a risus dapibus sagittis.
+Cras sed ultricies erat.
+Donec id metus sed urna lacinia convallis vel sed enim.
+Proin nisi libero, ornare vel bibendum eu, sollicitudin sed leo.
+Cras tincidunt aliquet ultricies.
+Cras pretium velit leo, in malesuada enim.
+Duis sagittis ultricies interdum.
+Proin sit amet sem nec metus feugiat pharetra.
+
 Figure~\ref{fig:Opt_colourredshift} presents the optical
@@
    \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180612.pdf}
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
    \centering
    \caption[]
-   {Optical colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
+   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
+     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
+   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
+bigger gaps between subplots??}}
    \label{fig:Opt_colourredshift}
@@
    \includegraphics[width=18.0cm]
-   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180612.pdf}
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
   \centering
    \caption[]
-   {Infrared colour-redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.}
+   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
+     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
+There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
+the blue or red end respectively. Hmmm....}
    \label{fig:filters}
@@
 
-%%\subsection{Mullaney SEDs}
+\begin{figure*}
+   \includegraphics[width=18.0cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
+  \centering
+   \caption[]
+   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
+}
+   \label{fig:filters}
+ \end{figure*}
 
-\subsection{Number Density of High-$z$ Sources}
+%\subsection{Number Density of High-$z$ Sources}
 
@@
 \subsection{L-$z$ Plane}
+Having obtained an as-near-to-homogenous set of photometry as we can, 
+we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
+sample and in particulare the absolute magnitude at rest-frame 1450\AA'\, $M_{1450}$, 
+which is a key physical quantity and goes directly towards the quasar luminosity 
+function and thus the reionization of hydrogen calculation.
+
+At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ iobserved, 
+i.e., in the $z$-band, while at
+
 \begin{figure*}
@@
 \subsection{SEDs and Dust properties of the VH$z$Qs}
+There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
+However, they are, for our purposes all roughly the same.
+
 \begin{figure*}
@@
 
+This research has made use of the SVO Filter Profile Service
+(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
+MINECO through grant AyA2014-55216 
+%\citet{} 
+The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
+describes the Spanish VO Filter Profile Service. 
+The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html
+
 \newpage
@@
 \appendix
+\section{Filter Curves} 
+FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.
 

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180714.tex
tex/older_tex/ removed

--- 2018-12-08 tex/older_tex/WW4C_VHzQ_pre201811/WW4C_VHzQ_20180724.tex
@@
 \author[Ross \& Cross]
-       {Nicholas P. Ross$^{1}$\thanks{Corresponding Author: npross@roe.ac.uk} and Nicholas J. G. Cross$^{1}$
+       {Nicholas P. Ross$^{1}$\thanks{email: npross@roe.ac.uk} and Nicholas J. Cross$^{1}$
 \\ 
@@
 \section*{TO DOs}
-{\bf For NPR: }
 \begin{itemize}
-\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
-\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
-\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
-\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-\item Concentrate on NIR and W1/W2
-\item SED dust plot with just W1/W2...
-\item Check vs. Assef R90/C75 catalog.
-\end{itemize}
-
-\noindent
-{\bf For NJGC: }
-\begin{itemize}
-\item Write the NIR data section(s) 
-\end{itemize}
-
-\noindent
-{\bf For Both: }
-\begin{itemize}
-\item Need to decide what mags and mag system we are reporting, espeically in the 
-NIR...
-\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
+\item Almost certainly want to compile M$_{\rm BH}$; 
+\item May well wanna try and get M$_{\star}$ too...!! ; 
 \end{itemize}
@@
 
-The build-up of SMBHs via accretion is important due to the desire to
-understand the evolution of the black hole mass function (BHMF) and
-since there is a remarkable similarity between cosmic star-formation
-rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
-BHAR trace each other \citep[with a normalisation factor of
-$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
-$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
-suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
-at higher redshift, $z>4$. The physical reasons for this are currently very poorly
-understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
-have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
-$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
-][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
-in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
-where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
-stellar mass of the bulge and galaxy total stellar mass,
-respectively. The evolution and potential importance of the SFRD and BHAR 
-link is a key outstanding problem in contemporary astrophysics, 
-potentially explaining the galaxy-black hole scaling relations. 
-However, there may also simply be a non-causal origin of the black-hole 
-galaxy scaling relations \citep{Jahnke2011}.
+%The build-up of SMBHs via accretion is important due to the desire to understand the evolution of the black hole mass function (BHMF) and since there is a remarkable similarity between cosmic star-formation rate density (SFRD) and black hole accretion rate (BHAR).
+The SFRD and BHAR trace each other \citep[with a normalisation factor of $\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts $z=0-4$.
+However, new results \citet[e.g., ][]{Vito2018a, Calhau2018} suggest that the SFRD and BHAR do not have the same evolutionary form at higher, $z>4$ redshifts, for reasons that are currently poorly understood.
+For some high-$z$ QSOs we can measure BHAR and SFR: most have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at $z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g., ][]{Netzer2014}.
+%%However, we also note the potential for the non-causal origins of the
+%%black-hole galaxy scaling relations \citep{Jahnke2011}.
 
@@
 quasars. Such apparently hot-dust-free quasars have no counterparts at
-low redshift. Moreover, those authors demonstrate that the hot-dust
-abundance in the 21 quasars builds up in tandem with the growth of the
-central black hole.
+low redshift. Moreover, we demonstrate that the hot-dust abundance in
+the 21 quasars builds up in tandem with the growth of the central
+black hole,
 
-WISE mapped the sky in 4 passbands, in bands centered at wavelengths
-of 3.4, 4.6, 12, and 23$\mu$m.  In total the release all sky
-``ALLWISE'' catalog, contains nearly 750 million detections at
-high-significance\footnote{\href{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}. \citet{Assef2013},
-\citet{Stern2012}. \citet{Blain2013} presented WISE mid-infrared (MIR)
-detections of 17 (55\%) of the then known 31 quasars at $z >
-6$. However, \citet{Blain2013} was compiled with the WISE `All-Sky'
-data release, as opposed to the superior ``AllWISE'' catalogs. That
-sample only examined the 31 known $z>6$ quasars; our sample has 148
-objects with redshift $z \geq 6.00$.
+\citet{Blain2013} presented WISE mid-infrared (MIR) detections of 17
+(55\%) of the then known 31 quasars at $z > 6$. However,
+\citet{Blain2013} was compiled with the WISE `All-Sky' data release,
+as opposed to the superior ``AllWISE'' catalogs. That sample only
+examined the 31 known $z>6$ quasars; our sample has 148 objects with
+redshift $z\geq6.00$.
 
-Here we update \citet{Jiang2010} and \citet{Blain2013} \citep[along
-with Table 8 of][]{Banados2016}. Our motivations are numerous and
-include: {\it (i)} establishing the first complete catalogue of
-$z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)}
-reporting homogenous near-infrared photometry for the quasars; {\it
-(iii)} making the first study of NIR variability of the VHzQ
-population and {\it (iv)} establishing the photometric properties for
-upcoming surveys and telescopes, e.g. the Large Synoptic Survey
-Telescope (LSST) \footnote{\href{https://www.lsst.org}{{lsst.org}}},
-ESA {\it
-Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid/}}
-and the {\it James Webb Space Telescope}
-(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};
-\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};
-\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};
-\href{https://jwst.stsci.edu/}{jwst.stsci.edu}}
+Here we update \citet{Jiang2010}  and \citet{Blain2013} 
+\citep[along with Table 8 of][]{Banados2016}.
 
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
+We chose redshift $z=5.0$ as our lower redshift limit due to a combination 
 of garnishing a large sample, adequately spanning physical properties 
@@
 discovered.
+
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m.
+In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
+\citet{Assef2013}, \citet{Stern2012}
+
+In this paper, we introduce the ``WISE W4 Compendium'' (WW4C); a detailed study into the objects that were detected in the longest waveband, 20-28$\mu$m observed, on the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+This study will describe all 40 million objects that are detected in the WISE W4-band, but will concentrate on those objects most affected by radiating dust emission and well described by extragalactic, and AGN, spectral energy distributions (SEDs).
+The motivations of the WW4C are numerous, but the primary science we will pursue is the identification of bolometric luminous AGN, especially those that might not be observered in X-ray/UV/optical surveys.
+%%
+
+\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter,
 
@@
 
+$M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass, stellar mass of the bulge and 
+ galaxy total stellar mass, respectively.
+
 Because of established conventions, we report SDSS $ugriz$ magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}, while the WISE W1 − 4 magnitudes are calibrated on the Vega system (Wright et al.
@@
 For WISE bands, $m_{\rm AB} = m_{\rm Vega} + m$ where m = (2.699, 3.339, 5.174, 6.66) for W1, W2, W3 and W4, respectively \citep{Cutri2011, Brown2014b}.
-\citet{Brown2014b}, in PASA, is the paper about Recalibrating the Wide-field Infrared Survey Explorer (WISE) W4 Filter.
 We make use of the Explanatory Supplement to the WISE All-Sky Data Release, as well as the WISE AllWISE Data Release  Products online.
-All optical ($ugriz$ bands) magnitudes are given in the AB system. 
-{\bf Need to decided 
-All near-infrared  ($y/YJHK$) are also given in the AB system.
-
+All optical ($ugriz$ bands) magnitudes are given in the AB system, all near-infrared  ($y/YJHK$) are also given in the AB system.
 We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$,  $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al.
@@
 
-\begin{table}
-\begin{tabular}{l r l}
-\hline  \hline
-Survey   & \# VH$z$Qs & Notes  \\
-\hline  
-  ATLAS      &    4    &  \\
-  CFHQS     &  20    &  \\
-  DELS        &    2    &  \\
-  ELAIS       &    1    &  \\
-  FIRST       &    1    &  \\
-  HSC         &    8    &  \\
-  IMS          &   1     &  \\
-  MMT        &  12    &  \\
-  NDWFS    &  1      &  \\
-  PSO          &    84  & \\
-  RD           &  1       & \\
-  SDSS        & 156       & \\
-  SOUV       & 20       & \\
-  SDWISE    & 27& \\
-  SHELLQs  & 55 & \\
-  ULAS       & 10& \\
-  VDES       & 11& \\
-  VIK          & 9 &\\
-  VIMOS     & 1& \\
-\hline  \hline
-\end{tabular}
-\caption{ATLAS \citet{Shanks2015}; }
-      \label{tab:surveys}
-\end{table}
-
 \subsection{Very high redshift quasars}
@@
 
-\section{A. Photometric Bands and Conversions}
-    Due to the differing normalizations between the
-    SDSS and  UKIDSS photometric systems, certain corrections are required.  To present
-    our data in the  purest sense, all the NIR magnitudes from UKIDSS
-    (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett06}.
-
-    Although ULAS magnitudes are reported in terms of Vega and SDSS
-    magnitudes are reported in AB terms for the most part whenever an
-    optical-NIR color was calculated both magnitudes were left in their
-    default term.
-
-\begin{table*}[h*]
-  \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth11}. 
-CTIO/DECam, PanSTARRS/PS1, LSST
-%References: www.cfht.hawaii.edu/Instruments/Filters/wircam.html
-Filter only values. 
-}
-    \setlength{\tabcolsep}{4pt}
-    \begin{tabular}{lcllcl}
-      \hline
-      \hline
-      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & AB - Vega Transformations \\
-      \hline
-%      {\it u} & 3551  &  3005 &  4000 &  581 & $u$ = $u_{AB}$ - 0.927 \\
-%      {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
-      $g_{\rm LSST}$      &     4730   &	3877    &	   5665   &  1333   &  $g_{\rm LSST}      = g_{\rm AB} + x $ \\
-      $g_{\rm DECam}$  &     4734   & 	3939    &    5528   &   1133   &  $g_{\rm DECam}  = g_{\rm AB} + x $ \\	     
-      $g_{\rm PS1}$        &     4776   &    3943    &    5593   &   1167   &  $g_{\rm PS1}      = g_{\rm AB} + x $ \\
-      $r_{\rm PS1}$         &     6130  & 	5386    &    7036   &   1318   &  $r_{\rm PS1}       = r_{\rm AB} + y $ \\
-      $r_{\rm LSST}$       &     6139  &	5375    &    7055   &   1338   &  $r_{\rm LSST}      = r_{\rm AB} + x $ \\	
-      $r_{\rm DECam}$   &     6345  & 	5506    &	   7238   &   1379   &  $r_{\rm DECam}  = r_{\rm AB} + x $ \\	     
-      $i_{\rm PS1}$         &     7485  &     6778    &    8304   &   1243   &  $i_{\rm PS1}       = i_{\rm AB} + x $ \\
-      $i_{\rm LSST}$       &     7487  &	6765    &	   8325   &   1209   &  $i_{\rm LSST}      = i_{\rm AB} + x $ \\
-      $i_{\rm DECam}$   &     7750 &	6950    &    8646    &   1371   &  $i_{\rm DECam}  = i_{\rm AB} + x $ \\	   
-      $z_{\rm PS1}$        &     8658 &	8028    &    9346   &      966   &  $z_{\rm PS1}     = z_{\rm AB} + y $ \\
-      $z_{\rm LSST}$      &     8669 &	8035    &	   9375   &      994  &   $z_{\rm LSST}      = i_{\rm AB} + x $ \\
-
-      $z_{\rm DECam}$  &     9216 &	8360    &   10166   &   1502  &  $z_{\rm DECam}      = i_{\rm AB} + x $ \\
-      $y_{\rm LSST}$      &     9677 &	9089    &	  10859  &     810   &  $y_{\rm LSST}      = i_{\rm AB} + x $ \\
-      $Y_{\rm DECam}$   &   10061 &	9400    &   10805   &   1115  &  $Y_{\rm DECam}      = i_{\rm AB} + x $ \\
-                                        &            &                   &                 &          &  \\
-      $Y_{\rm UKIDSS}$   & 10305 &  9790 & 10810 & 1020 & $Y_{\rm UKIRT}$ = $Y_{AB}$  - 0.634           \\
-      $Y_{\rm VISTA}$   & - &  9790 & 10810 & 1020 & $Y_{\rm UKIRT}$ = $Y_{AB}$  - 0.634           \\
-      $J_{\rm UKIDSS} $ & 12483 & 11690 & 13280 & 1590 & $J$  = $J_{AB}$- 0.938           \\
-      $J_{\rm VISTA} $ & 12483 & 11690 & 13280 & 1590 & $J$  = $J_{AB}$- 0.938           \\
-      $W_{\rm Wircam}$ & 14530 &  & & 1020 & $Y$ = $Y_{AB}$  - 0.634           \\
-      $H_{\rm UKIDSS}$ & 16313 & 14920 & 17840 & 2920 & $H$ = $H_{AB}$ - 1.379          \\
-      $H_{\rm VISTA}$ & 16313 & 14920 & 17840 & 2920 & $H$ = $H_{AB}$ - 1.379          \\
-      $K_{\rm UKIDSS}$ & 22010 & 20290 & 23800 & 3510 & $K$ = $K_{AB}$ - 1.9            \\ 
-      $K_{\rm VISTA}$ & 22010 & 20290 & 23800 & 3510 & $K$ = $K_{AB}$ - 1.9            \\ 
-      \hline
-      \hline
-      \label{tab:filter_details}
-    \end{tabular}
-     \end{center}
-\end{table*}
-
 \section{PanSTARRS1 SQL queries}\label{sec:PS1_SQL}

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180817.tex
tex/older_tex/ removed

--- 2018-08-27 tex/older_tex/WW4C_VHzQ_20180729.tex
@@
 \title[Very high-$z$ Quasars]
-        {Near and mid-infrared properties of known $z\geq5$ Quasars}
+        {Near and Mid-infrared properties of known $z\geq5$ Quasars}
 \author[Ross \& Cross]
@@
 \begin{abstract}
-Very high redshift quasars are excellent probes of physics the early
-Universe.  Understanding how billion solar mass black holes
-formed, evolve and accrete in the first billion years is a key
-outstanding problem in contemporary astrophysics, and one that wil lbe
-directly addressed by upcoming missions such as ESA {\it Euclid} and
-the {\it James Webb Space Telescope}.
-%%
-We can gain a good appreciation for what these missions will discover
-by collating the datasets we currently have, and in this paper, we,
-for the first time since the discovery of $z\geq5.00$ quasars assemble all spectroscopically confirmed very high redshift quasars in
-one catalogue.
-%%
-In particular we present the near ($z/Z, y/Y, J, H, K_{s}$ and $K$)
-infrared and mid-infrared (WISE) properties of all 424
-spectroscopically known redshift $z\geq5$ quasars.  Using archival public
-WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability
-in the near-infrared and find blah.  We present a comprehensive series
-of colour-redshift and colour-colour plots and make inferences into
-the hot dust properties of the very high-redshift quasar
-population. Extrapolating the known quasar luminosity function we
-suggest that 80\% of the possibly detected $z\geq5$ quasars in the
+In this paper, we, for the first time since the discovery of $z\geq5$
+quasars, assemble all spectroscopically confirmed very high redshift
+quasars in one catalogue.  In particular we present the near
+($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties of
+all 424 spectroscopically confirmed redshift $z\geq5.00$ quasars.
+Using archival public WFCAM/UKIRT and VIRCAM/VISTA data we check for
+photometric variability in the near-infrared that might be expected
+from Super-Eddington accretion and find {\it blah}.  We present a
+comprehensive series of colour-redshift and colour-colour plots and
+make inferences into the hot dust properties of the very high-redshift
+quasar population. Extrapolating the known quasar luminosity function
+we suggest that $x$\% of the possibly detected $z\geq5$ quasars in the
 current datasets have been discovered.
@@
 \begin{itemize}
-\item Almost certainly want to compile M$_{\rm BH}$; hmmmm....
-\item May well wanna try and get M$_{\star}$ too...!! (yuck); 
+\item Concentrate on reporting NIR and W1/W2 figures and tables
+\item SED dust plots 
+\item Check vs. Assef R90/C75 catalog.
 \item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
 \item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-\item Concentrate on NIR and W1/W2
-\item SED dust plot with just W1/W2...
-\item Check vs. Assef R90/C75 catalog.
+\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
+\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
 \end{itemize}
@@
 \section{Introduction}
-Very high redshift quasars (VH$z$Q; and defined here to have redshifts
+Very high redshift quasars (VH$z$Q; defined here to have redshifts
 $z\geq5.00$) are excellent probes of the early Universe. This includes
@@
 \citep[e.g.,][]{AlexanderNatarajan2014, MadauHaardtDotti2014,
-Volonteri2015, Pezzulli2016, Lupi2016} Thus, one might well expect
-VH$z$Qs to vary in luminosity as they potentially go through phases of
-Super-Eddington accretion and these should be looked for, especially
+Volonteri2015, Pezzulli2016, Lupi2016, Pezzulli2017, Takeo2018}. Thus,
+one might well expect VH$z$Qs to vary in luminosity as they
+potentially go through phases of Super-Eddington accretion and these
+signatures of photometric variablity should be looked for, especially
 when the e.g. near-infrared $K$-band is sampling rest-frame
@@
 
-The build-up of SMBHs via accretion is important due to the desire to
-understand the evolution of the black hole mass function (BHMF) and
-since there is a remarkable similarity between cosmic star-formation
-rate density (SFRD) and black hole accretion rate (BHAR). The SFRD and
-BHAR trace each other \citep[with a normalisation factor of
-$\sim3000$,][]{Willott2013b, MadauDickinson2014} across redshifts
-$z=0-4$.  However, new results \citep[e.g., ][]{Vito2018a, Calhau2018}
-suggest that the SFRD and BHAR do {\it not} have the same evolutionary form
-at higher redshift, $z>4$. The physical reasons for this are currently very poorly
-understood.  For the high-$z$ QSOs that we can measure BHAR and SFR, most
-have BHAR $\gg 10^{-3}$ SFR, indeed {\it Herschel}-detected sources at
-$z\simeq.8$ have $L_{\rm SF} \simeq L_{\rm AGN}$ \citep[e.g.,
-][]{Netzer2014} and {\it Herschel}-detected quasars show no evolution
-in the $M_{\rm BH} - M_{\star}$ relation from $z\sim2$ to $z\sim0$.
-where $M_{\rm BH}, M_{\rm bulge}, M_{\star}$ are the SMBH mass,
-stellar mass of the bulge and galaxy total stellar mass,
-respectively. The evolution and potential importance of the SFRD and BHAR 
-link is a key outstanding problem in contemporary astrophysics, 
-potentially explaining the galaxy-black hole scaling relations. 
-However, there may also simply be a non-causal origin of the black-hole 
-galaxy scaling relations \citep{Jahnke2011}.
-
 Quasars are also known to be prodigious emitters of infrared emission,
 thought to be from the thermal emission of dust grains heated by
-continuum emission from the accretion disc \citep[][]{Hill2014,
-Hickox2017}.  Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m
-allow discrimination between AGN\footnote{Historically, ``quasars'' and
+continuum emission from the accretion disc
+\citep[e.g.,][]{Richards2006b, Leipski2014, Hill2014, Hickox2017}.
+Observations in the mid-infrared, e.g. $\sim$3-30$\mu$m allow
+discrimination between AGN\footnote{Historically, ``quasars'' and
 ``Active Galactic Nuclei (AGN)'' have described different
@@
 
-We chose redshift $z=5.00$ as our lower redshift limit due to a combination 
-of garnishing a large sample, adequately spanning physical properties 
-(e.g. luminosity, age of the Universe) and to incorporate what knowledge 
-we have gained over the last couple of decades since $z>5$ quasars were 
-discovered.
-
 This paper can be considered an update of \citet{Blain2013} and also
-an extension of parts of \citet{Banados2016}, with the latter study reporting
-WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey Telescope and Rapid Response System 1 
-\citep[Pan-STARRS1, PS1;][]{Kaiser2002, Kaiser2010}, but with no  
-further investigation into the reddest WISE waveband for the VH$z$Qs.
-%%
-\citet{Banados2016} reports and investigates the W1, W2 and W3 properties
-of quasars at $z > 5.6$.
+an extension of parts of \citet{Banados2016}, with the latter study
+reporting WISE W1, W2, W3 and W4 magnitudes for Panoramic Survey
+Telescope and Rapid Response System 1 \citep[Pan-STARRS1,
+PS1;][]{Kaiser2002, Kaiser2010}, but with no further investigation
+into the reddest WISE waveband for the VH$z$Qs.  \citet{Banados2016}
+reports and investigates the W1, W2 and W3 properties of quasars at $z
+> 5.6$. We chose redshift $z=5.00$ as our lower redshift limit due to
+a combination of garnishing a large sample, adequately spanning
+physical properties (e.g. luminosity, age of the Universe) and to
+incorporate what knowledge we have gained over the last couple of
+decades since $z>5$ quasars were discovered.
 
@@
 Specifically, we use data from: \citet{Fan2000}, \citet{Fan2001c},
-\citet{Fan2003} , \citet{Fan2004}, \citet{Mahabal2005},
+\citet{Fan2003}, \citet{Fan2004}, \citet{Mahabal2005},
 \citet{Cool2006}, \citet{Fan2006}, \citet{Goto2006},
@@
 
+%%
+We can gain a good appreciation for what these missions will discover
+by collating the datasets we currently have.
+
 \begin{itemize}
@@
     (originally AB magnitudes)  were corrected to Vega magnitudes as
-    suggested in \citet{Hewett06}.
+    suggested in \citet{Hewett2006}.
 
@@
 
-\begin{table*}[h*]
+\begin{table*}
   \begin{center}
-   \caption{Adapted from Table 9 of \citet{Peth11}. 
+   \caption{Adapted from Table 9 of \citet{Peth2011}. 
 CTIO/DECam, PanSTARRS/PS1, LSST
@@
 Filter only values. 
+%%
+%%
+From \citet{GonzalezFernandez2018} 
+$Z_{\rm AB}   -  Z_{\rm Vega}  = 0.502$;  
+$Y_{\rm AB}  -  Y_{\rm Vega}    = 0.600 $;
+$J_{\rm AB}   -  J_{\rm Vega}    = 0.916  $;
+$H_{\rm AB}  -  H_{\rm Vega}    = 1.366 $;
+$Ks_{\rm AB}  -  Ks_{\rm Vega}  = 1.827 $;
+%%
+and the CASU Vega to AB conversions v1.3:: 
+	Z,Y,J,H,Ks were: 0.524, 0.618, 0.937, 1.384, 1.839. 
+%%
+So, $\Delta$(vs. Gonzalez-Fernandez)::
+	(11.2,     1.1,    5.4,     1.6,    0.1) millimags. 
+$\Delta$(vsCASU v1.3)::
+	(-10.8, -16.9, -15.6,  -16.4, -11.9) millimags. 
 }
@@
       $g_{\rm PS1}$        &    4776    &    3943    &    5593   &   1167        &  $g_{\rm PS1}$         &$  = g_{\rm AB} + 0.080 $ \\   %% from SVO; e.g.   (-2.5)*(log10(3909.1/3631.0)) 
+      &&&&&&\\
       $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
@@
       $r_{\rm DECam}$   &      6345    &    5506    &    7238   &   1379      &  $r_{\rm DECam}$       &$   = r_{\rm AB} - 0.192 $ \\	     
+      &&&&&&\\
       $i_{\rm PS1}$         &    7485    &     6778    &    8304   &   1243      &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.369 $ \\  %% 2584.6
@@
       $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
+      &&&&&&\\
       $z_{\rm PS1}$        &    8658    &	 8028    &      9346   &      966      &  $z_{\rm PS1}   $      &$    = z_{\rm AB} - 0.508 $       \\
       $z_{\rm LSST}$      &     8669   & 	 8035    &      9375   &      994     &   $z_{\rm LSST}  $      &$    = z_{\rm AB} - 0.509 $     \\
+      $Z_{\rm VIRCAM}$  &     8762   & 	 8157    &      9400   &      978    &   $Z_{\rm VIRCAM}  $   &$    = z_{\rm AB} - 0.513 $     \\
+      $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = z_{\rm AB} - 0.514 $     \\
       $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
+      &&&&&&\\
       $y_{\rm PS1}$      &       9603    &	 9100    &    10838  &     615       &  $y_{\rm PS1}    $       &$   = y_{\rm AB} -  0.541 $ \\
@@
       $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\
-      $Y_{\rm VISTA}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
+      $Y_{\rm VIRCAM}$     &    10184    &   9427      &   10977   &    905        & $Y_{\rm VISTA} $     &$ = Y_{AB}  - 0.601 $          \\
+      &&&&&&\\
+      $J_{\rm VIRCAM} $     &   12464   &      11427   &    13759   &  1628     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.921  $         \\
       $J_{\rm WFCAM} $    &    12483   &     11690  &    13280   &   1590      & $J_{\rm WFCAM}$     & $= J_{AB}    - 0.919 $          \\
-      $J_{\rm VISTA} $     &     10184   &      9427   &    10977   &     905     &  $J_{\rm VISTA}  $     & $= J_{AB}    - 0.938  $         \\
+      &&&&&&\\
       $W_{\rm Wircam}$   &    14514    &    13890   &    15166   &   1020    & $W_{\rm Wircam} $    & $= W_{AB}  -  1.163$           \\
+      &&&&&&\\
       $H_{\rm WFCAM}$    &    16313     &    14920  &    17840   &   2920    & $H_{\rm WFCAM} $   & $= H_{AB}  - 1.379$          \\
-      $H_{\rm VISTA}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
-      $K$s$_{\rm VISTA}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K_{AB} - 1.83  $          \\ 
+      $H_{\rm VIRCAM}$      &    16310    &    14604   &    18422   &   2833     & $H_{\rm VISTA}$      & $= H_{AB}  - 1.368 $        \\
+      &&&&&&\\
+      $K$s$_{\rm VIRCAM}$     &    21337    &    19333  &    23674   &   3055     & $K$s$_{\rm VISTA}$      & $ = K$s$_{AB} - 1.83  $          \\ 
       $K_{\rm WFCAM}$     &    22010     &    20290 &    23800   &   3510     & $K_{\rm WFCAM}$     & $ = K_{AB} - 1.9  $          \\ 
+      &&&&&&\\
       WISE W1               &    33526    &    27541  &    38724   &    6626    & W1                        &   = W1$_{\rm AB} - 2.699$ \\

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180822.tex
tex/older_tex/ removed

--- 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180817.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data}
-
-\begin{figure*}
+\begin{figure}
 %%trim=l b r t
-  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
+%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
+  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
   {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
   \centering
+  \vspace{-12pt}
   \caption[]
-  {The spectral bands used by different survey telescopes and that are relevant here.}
+  {The spectral bands used by different survey telescopes and that are relevant here.
+    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
+    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
+    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
+    The WISE passbands  W1-4 are also presented.
+    The quasar spectrum is a composite based on \citet{VdB2001} and 
+    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
+  }
   \label{fig:filters}
-\end{figure*}
-
+\end{figure}
+
+\section{Data}
 We assemble our dataset in a relatively straightforwad manner.  First
@@
 We then obtain optical, near-infrared and mid-infrared photometry for the
-spectral dataset.
-
-The optical data comes from the 
+spectral dataset. The optical data comes from the 
 Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 
@@
 
-The near-infrared data comes from the Wide Field Camera (WFCAM) on 
-the United Kingdom Infra-Red Telescope
+The near-infrared data comes from two primary sources. First, the Wide
+Field Camera \citep[WFCAM; ][]{Casali2007} on the the United Kingdom
+Infra-Red Telescope (UKIRT) primarly, but not exclusively as part of
+the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.
+And second, data from the VIRCAM (VISTA InfraRed CAMera) on the VISTA
+\citep[Visible and Infrared Survey Telescope for
+Astronomy;][]{Emerson2006, Dalton2006}.
+
+Figure~\ref{fig:filters} displays the wavelength and normalised transmission 
+of the filters in question.
+
+\input{THE_TABLE_v0pnt96_TOP10_betterformat}
 
 \subsection{Very high redshift quasars}
+In Table~\ref{tab:THE_TABLE} we present our dataset. 
+We have obtained a list of 424 spectroscopically confirmed 
+quasars with redshifts $z\geq5.00$.
+
 In Table~\ref{tab:THE_TABLE}  we give the discovery reference for the
@@
 
-\input{THE_TABLE_v0pnt96_TOP10_betterformat}
-
 Table~\ref{tab:THE_TABLE} gives the salient details for the objects
@@
 and mid-infrared (WISE W1/2/3/4) photometry and give our caculcated 
-$M_{1450}$
+$M_{1450}$.
 
@@
 \hline  \hline
-Survey   & \# VH$z$Qs & Notes  \\
+Survey   & \# VH$z$Qs & Notes/Survey reference  \\
 \hline  
-  ATLAS      &    4    &  \\
-  CFHQS     &  20    &  \\
-  DELS        &    2    &  \\
-  ELAIS       &    1    &  \\
-  FIRST       &    1    &  \\
-  HSC         &    8    &  \\
-  IMS          &   1     &  \\
-  MMT        &  12    &  \\
-  NDWFS    &  1      &  \\
-  PSO          &    84  & \\
-  RD           &  1       & \\
-  SDSS        & 156       & \\
-  SOUV       & 20       & \\
-  SDWISE    & 27& \\
-  SHELLQs  & 55 & \\
-  ULAS       & 10& \\
-  VDES       & 11& \\
-  VIK          & 9 &\\
-  VIMOS     & 1& \\
+  ATLAS      &     4    &  \citet{Shanks2015} \\
+  CFHQS     &   20    &  \citet{Willott2007} \\
+  DELS        &     2    &  \citet{Dey2018} \\
+  ELAIS       &     1    &  \citet{Vaisanen2000} \\
+  FIRST       &     1    &  \citet{Becker1995} \\
+%  HSC         &     8    &  \\
+  IMS          &     1     &  \citet{Kim2015} \\
+  MMT        &   12    &  \citet{McGreer2013} \\
+  NDWFS    &     1     &  \citet{JD1999} \\
+  PSO          &   84    &   \citet{Kaiser2002, Kaiser2010} \\
+  RD           &     1       &  \cite{Mahabal2005} \\
+  SDSS        & 156       & \citet{EDR} \\
+  SDUV       &   20       & \citet{Yang2017} \\
+  SDWISE    &   27    &     \citet{Wang2016} \\
+  SHELLQs  &  $^{a}$63   &  \citet{Matsuoka2016}\\  %% includes 8 objects from the first HSC paper..
+  ULAS       &   10   & \citet{Lawrence2007} \\
+  VDES       &   11   &  \citet{Reed2017} \\
+  VIK          &     9   &  \citet{Edge2013} \\
+  VIMOS     &     1   &  \citet{LeFevre2003} \\
 \hline  \hline
 \end{tabular}
-\caption{ATLAS \citet{Shanks2015}; }
+\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference. 
+$^{a}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018}  
+designation.
+}
       \label{tab:surveys}
@@
     sample. Details of our SQL and links to the main tables are given
-    in~\ref{sec:PS1_SQL}.
+    in Appendix~\ref{sec:PS1_SQL}.
 
     \subsubsection{DECam} 
+    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
+    is a wide-field imager with a 2.2 degree diameter field of view 
+    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
+    at the Cerro Tololo International Observatory. We use data 
+    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
+    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}.
 
@@
 We will give the pertinent points of the MAP and specific details of these data sets below.
+
+\subsubsection{UKIDSS LAS} 
+In a bit more detail, use:\\
+dr10plus\\
+lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
+424 results returned. Of which...
+
+\subsubsection{VISTA VHS} 
+In a bit more detail, use:\\
+VH5DR5 \\
+sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
+424 results returned.  Of which...
+
+{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
 
@@
 
-\subsubsection{UKIDSS LAS} 
-Use:\\
-%lasDetection \\
-dr10plus\\
-lasSource table (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned. Of which...
-
-\subsubsection{VISTA VHS} 
-Use:\\
-%lasDetection \\
-VH5DR5 \\
-sourceTable (merged catalogue), nearest object only; radius 2.0'' \\
-424 results returned.  Of which...
-
-{\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
-
 \iffalse
@@
 
-%    \begin{equation}
-%      \label{equ:simple_prob}
-%      dP = n \, dV.
-%    \end{equation}
-
-%    \begin{eqnarray}
-%      \xi_{LS}(s) &=& 1 + \left(\frac{N_{rd}}{N} \right)^{2} \frac{DD(s)}{RR(s)} -
-%      2   \left( \frac{N_{rd}}{N} \right) \frac{DR(s)}{RR(s)} \\
-%      &\equiv&  \frac{DD(s)-2DR(s)+RR(s)}{RR(s)},
-%      \label{lseq}
-%    \end{eqnarray}
-
-%% http://www-astro.physics.ox.ac.uk/~kmb/latex_colour.html
-%{\color{red} ...bit of LaTeX text...}
-%an example of making an equation the colour DarkSeaGreen (rather a sophisticated shade, I think) one types the following:
-%\begin{equation}
-%{\color{DarkSeaGreen} x = \log_{10} (\nu/\rm MHz) }
-%\end{equation}
-
-%\subsection{Dust Overview}
-%http://arxiv.org/pdf/1605.06671.pdf
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
- Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam porta sodales est, vel cursus risus porta non.
-Vivamus vel pretium velit.
-Sed fringilla suscipit felis, nec iaculis lacus convallis ac.
-Fusce pellentesque condimentum dolor, quis vehicula tortor hendrerit sed.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-Etiam interdum tristique diam eu blandit.
-Donec in lacinia libero.
-
-\subsection{Detection Rates}
-%\begin{table}
- % \begin{center}
-  %  \setlength{\tabcolsep}{4pt}
-   % \begin{tabular}{lrrr}
-     % \hline       \hline
-    %  Sample Description  & Number in sample & North & South   \\
-     % \hline
-     % \hline \hline
-%      \label{tab:The_Numbers}
- %   \end{tabular}
-  %  \caption{}
-  %\end{center}
-%\end{table}
+Having collated the sample of 424 VH$z$Qs, and obtained their optical,
+near- and mid-infrared photometry we report here the various
+photometric properites of the quasars.
+
+First, we will concentrate on detection rate in the infrared, go on to
+report on the color-redshift and color-color properties of our sample
+and then report on how the current sample populates the
+luminosity-redshift $Lz$-plane.
+
+    \subsection{Detection Rates in the optical}
+
+    \subsection{Detection Rates in the NIR}
+    Table~\ref{tab:nir_detection} gives the detection rates for the 
+    VH$z$Qs in the NIR $YJHK/K_{s}$-bands. 
+    The first thing to note is that the coverage of the NIR surveys 
+    for example from the UKIDSS LAS and VISTA VHS, does
+    not overlap the full area for where the VH$z$Qs are detected.
+
+    \begin{table}
+      \begin{tabular}{l r l}
+        \hline  \hline
+        Selection   & number detected (\%) \\
+        \hline  
+        Any band ($YJHK/K_{s}$   &  394  ( ) \\
+        $Y$-band    &    ( ) \\
+        $J$-band    &    ( ) \\
+        $H$-band    &    ( ) \\
+        $K$ or $Ks$-band    &    ( ) \\
+        \hline  \hline
+      \end{tabular}
+      \caption{Detection rate of VH$z$Qs in the near-infrared.}
+      \label{tab:nir_detection}
+    \end{table}
+
+    \subsection{Detection Rates in the MIR}
+    Unlike the NIR coverage, the WISE
+    satellite and mission performed an all-sky survey, so the location of
+    evey VH$z$Q in our dataset is covered. However, the depth of the WISE
+    ALLWISE survey depends heavily on sky location, with locations near
+    the Ecliptic Poles having the highest number of exposures.
+
+    Before reporting on the detection rates, we investigate this
+    effect. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE magnitude
+    versus signal-to-noise, colour coded by {\tt w$x$cov} the mean
+    coverage depth, in each corresponding band. In the two shorter bands
+    W1/2 we see the clear and expected trend for brighter objects to have
+    larger SNR, and also for the higher signal to noise for objects with
+    more exposures at a given magnitude. The behaviour for the W3/4 bands
+    is different, with two populations clearly evident in W3 and although
+    a bit more mixed, also in W4. With the suggested split at SNR$>2$, and
+    no obvious R.A./Declination dependence seen, this behaviour is
+    explained by the fact that there are non-detectiopns in W3/4 for
+    objects (with high W1/2 SNR) that are reported in the ALLWISE
+    catalogue.
+
+    For the 278 VH$z$Q with coverage detections, the mean number of
+    exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a
+    minimum number of exposures 17 and 12, and the maximum number or
+    exposures being 114 (for both bands).  For the W3/4 filters, the
+    corresponding mean, minimum and maximum exposure are 17.4 and 17.5,
+    5.8 and 6.8 and 69 (for both bands). These values are direclty from
+    the {\tt w$x$cov} enteries in the 
+    \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{WISE ALLWISE catalogue}.
+
+    \begin{figure}
+      %% trim=l b r t
+      \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
+      {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEmag_vs_coverage_2x2_v1.pdf}
+      \centering
+      \vspace{-14pt}
+      \caption[]{WISE W1/2/3/4 magnitude against signal-to-noise, 
+        colour coded by w$x$cov the mean coverage depth, in each corresponding band.
+  }
+  \label{fig:WISEmag_vs_coverage}
+\end{figure}
+
+    Table~\ref{tab:mir_detection} gives the detection rates for the
+    VH$z$Qs in the MIR WISE W1-4 bands. 
+    \begin{table}
+      \begin{tabular}{l r l}
+        \hline  \hline
+        Selection   & number detected (\%) \\
+        \hline  
+        W1 SNR $> 2.0$   &  275  (64.9) \\
+        W2 SNR $> 2.0$   &   255 (60.1) \\
+        W1 \&\& W2 SNR $> 2.0$  &  \\
+        W3 SNR $> 2.0$   &  99    (23.3) \\
+        W4 SNR $> 2.0$   &  29    (6.8) \\
+        Any W1/2/3/4 SNR $>2.0$ & \\
+        W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
+        \hline  \hline
+      \end{tabular}
+      \caption{ATLAS \citet{Shanks2015}; }
+      \label{tab:mir_detection}
+    \end{table}
+
+\begin{figure}
+  %% trim=l b r t
+  \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
+  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
+  \centering
+  \vspace{-14pt}
+  \caption[]{WISE signal-to-noise measures for the four bands, as well
+    as for (W1-W2) colour.  The points are colour coded by redshift.}
+  \label{fig:WISEmag_vs_coverage}
+\end{figure}
 
@@
 
-\subsection{Very High-$z$ Quasars Detected in WISE}
+    \subsection{Very High-$z$ Quasars in WISE}
      \citet{Blain2013} 
-Cras in laoreet mauris.
-Vivamus nec nulla a dui commodo adipiscing.
-Proin vulputate lectus nec arcu iaculis sit amet auctor ligula ultricies.
-Phasellus condimentum gravida tincidunt.
-Phasellus et mauris ac nibh vestibulum vehicula.
-Morbi et augue id purus gravida sagittis quis in sem.
-Phasellus quis risus bibendum eros luctus auctor.
+     Cras in laoreet mauris. Vivamus nec nulla a dui commodo
+     adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
+     ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
+     et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
+     sagittis quis in sem. Phasellus quis risus bibendum eros luctus
+     auctor.
 
         \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
-Proin non tempus velit.
-Etiam laoreet, enim nec scelerisque dictum, tortor massa tempor enim, id pretium justo quam ac lectus.
-Maecenas diam nibh, interdum at lobortis sit amet, dignissim et quam.
-Sed tincidunt faucibus risus, congue tempus nisl consectetur eget.
-Suspendisse venenatis turpis ut risus aliquam interdum.
-In at velit sed ligula dictum dignissim ut et dui.
-Curabitur ac scelerisque purus.
+        Proin non tempus velit. Etiam laoreet, enim nec scelerisque
+        dictum, tortor massa tempor enim, id pretium justo quam ac
+        lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
+        et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
+        eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
+        velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
+        purus.
 
@@
 the blue or red end respectively. Hmmm....}
-   \label{fig:filters}
+   \label{fig:SpecType_vs_NIRcolors}
  \end{figure*}
@@
 }
-   \label{fig:filters}
+   \label{fig:SpecType_vs_W1W2_W2W3colors}
  \end{figure*}
-
-%\subsection{Number Density of High-$z$ Sources}
-
-\subsection{Consequences of evolution of the $M_{\rm BH} - M_{\star}$ relation}
-From a study of 69 {\it Herschel}-detected broad-line active galactic
-nuclei, \citet{Sun2015} find there is no evolution in the $M_{\rm BH}
-- M_{\star}$ relation from $z\sim2$ to $z\sim0$, with the ratio of
-$\log (M_{\rm BH} / M_{\star}$ constant at -2.85 across this redshift
-range. If this ratio holds to $z>5$, and we assume the $M_{\rm BH}$
-for the $z>6$ measured from the e.g. \mgii line, are generally
-correct, then the galaxy total stellar mass for the $z>6$ objects
-should be...
-
-\citet{YangG2018} calculate the long-term SMBH accretion rate as a
-function of $M_{\rm star}$ and redshift $[BHAR(M_{\star} ,z)]$ over
-ranges of $\log (M_{\rm star} / M_{\odot}) = 9.5–12$ and $z = 0.4–4$.
-Our BHAR(M⋆,z) is constrained by high-quality survey data
-(GOODS-South, GOODS-North and COSMOS), and by the stellar mass
-function and the X-ray luminosity function.  This BHAR/SFR dependence
-on $M_{\star}$ does not support the scenario that SMBH and galaxy
-growth are in lockstep.
 
@@
   {The spectral bands used by different survey telescopes and that are relevant here.}
-  \label{fig:filters}
+  \label{fig:Lz}
 \end{figure*}
@@
   {The rest-frame properties of the VH$z$Qs. }
-  \label{fig:filters}
+  \label{fig:RestWavelength_SEDs}
 \end{figure*}
@@
 and the Gordon and Betty Moore Foundation.
+
+This project used data obtained with the Dark Energy Camera (DECam)
+and the NOAO Data Lab, The Data Lab is operated by the National
+Optical Astronomy Observatory, the national center for ground-based
+nighttime astronomy in the United States operated by the Association
+of Universities for Research in Astronomy (AURA) under cooperative
+agreement with the National Science Foundation.
 

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180823.tex
tex/older_tex/ removed

--- 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180822.tex
@@
 \item SED dust plots 
-\item Check vs. Assef R90/C75 catalog.
 \item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
+\item Check for NIR and MIR variabilty with the Wu quasar
 \item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
-\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
-\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
+%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
+%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
 \end{itemize}
@@
 \section{Data}
-We assemble our dataset in a relatively straightforwad manner.  First
+In Table~\ref{tab:THE_TABLE} we present our dataset and 
+we have assembled this in the following manner.  First
 we compile the list of all known, spectroscopically confirmed quasars
@@
 
+Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
+on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
+delivering exquisite multi-band photometry data
+\citep[][]{Aihara2018b} the five broad bands $grizy$.
+
 The near-infrared data comes from two primary sources. First, the Wide
@@
 
-\subsection{Very high redshift quasars}
-In Table~\ref{tab:THE_TABLE} we present our dataset. 
+\subsection{Spectroscopy} 
 We have obtained a list of 424 spectroscopically confirmed 
@@
 
+    \iffalse
     \subsubsection{DECam} 
@@
     the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
-
-%\newpage
+    \fi
+
 \subsection{Near-infrared photometry}
@@
 
-\section{NIR Data}
-
+%\section{NIR Data}
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
@@
     \begin{table}
+          \centering
+
       \begin{tabular}{l r l}
@@
       \label{tab:nir_detection}
+    \end{table}
+
+        \subsubsection{Comparing WFCAM and VISTA}
+        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
+        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
+        objects on the same AB system, and for each object compared the two
+        measurements. First, the calculated weighted average (calibrated flux)
+        in each filter of both and calculated the ratio and difference between
+        each measurement and the average.  Then for each filter we calculated
+        the weighted average of the differences (in mag) for each instrument
+        to see if there were significant offsets. The results are given in
+        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
+        offset is the $Y$-band. All of the VISTA averages are negative and all
+        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
+        slightly dodgy, given the different shapes of the filters.
+        \begin{table}
+          \centering
+          \begin{tabular}{l r r}
+            \hline  \hline
+            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
+            -  WFCAM)      &                                        &  objects \\
+            \hline
+            $Z$                 &  19.3 	& 2 \\
+            $Y$                 &  66.2 	& 48 \\
+            $J$                  &    3.2 	& 105 \\
+            $H$                 &  19.3     &  89 \\
+            $K_{\rm s}$/$K$ &  12.7     & 93 \\
+            \hline  \hline
+          \end{tabular}
+          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
+          \label{tab:WFCAM_vs_VISTA}
         \end{table}
@@
 
+    Recently, \citet{Assef2018} released two large catalogues of AGN 
+    candidates identified across 30,000 deg$^2$ of extragalactic sky 
+    from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
+    contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
+    AGN candidates per deg$^2$) while the ``C75'' catalog 
+    consists of 20.9M AGN candidates at 75\% completeness (and 
+    ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
+    out catalogue of 424 VH$z$Qs with these catalogues, produces 
+    42 matches with	the R90 sample and 98 matches with the C75 sample. 
+    Both catalogues unsurprisingly match to the ultraluminous quasar 
+    SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
+    mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
+    matches J1342+0928 \citep{Banados2018}.
+
     \subsection{Variability}
-    Sed elit massa, eleifend non sodales a, commodo ut felis.
-Sed id pretium felis.
-Vestibulum et turpis vitae quam aliquam convallis.
-Sed id ligula eu nulla ultrices tempus.
-Phasellus mattis erat quis metus dignissim malesuada.
-Nulla tincidunt quam volutpat nibh facilisis euismod.
-Cras vel auctor neque.
-Nam quis diam risus.
+    Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
+pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
+id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
+dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
+euismod. Cras vel auctor neque. Nam quis diam risus.
 
@@
 Filter only values. 
+All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 
 %%
@@
       \hline
-      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
-              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 
+      Band & $\lambda_{\rm eff}  $ 
+              &  $\lambda_{\rm min} $ 
+              & $\lambda_{\rm max} $ 
+              & W$_{\rm eff}$
               & \multicolumn{2}{c}{AB - Vega  Transformations} \\
@@
       % {\it u_{\rm LSST}} &	3733 &	3182 &	4082 &	?? \\
+       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\
       $g_{\rm LSST}$      &     4730     &	  3877    &	   5665   &  1333   &  $g_{\rm LSST}$       &$ = g_{\rm AB} +  0.083 $ \\   %% from SVO 3921.4 
@@
       &&&&&&\\
+      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\
       $r_{\rm PS1}$         &    6130    & 	  5386    &    7036   &   1318       &  $r_{\rm PS1}   $       &$     = r_{\rm AB} - 0.153 $ \\ %% from SVO; e.g.   (-2.5)*(log10(3151.4/3631.0)) 
@@
       $i_{\rm LSST}$       &     7487    &	  6765    &     8325   &   1209      &  $i_{\rm LSST}   $       &$    = i_{\rm AB} - 0.369 $ \\   %% 2583.9
+      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6
       $i_{\rm DECam}$   &      7750   &	  6950    &     8646    &   1371      &  $i_{\rm DECam} $     &$  = i_{\rm AB} - 0.415 $        \\	   
@@
       $Z_{\rm WFCAM}$  &     8802   & 	 8129    &      9457   &      926    &   $Z_{\rm WFCAM}  $   &$    = z_{\rm AB} - 0.514 $     \\
+      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = z_{\rm AB} - 0.512$     \\
       $z_{\rm DECam}$  &      9216   & 	 8360    &    10166   &   1502      &  $z_{\rm DECam} $     &$   = z_{\rm AB} - 0.521 $ \\
@@
       $Y_{\rm DECam}$   &      9876   &	  9355    &      10730   &    676      &  $Y_{\rm DECam}  $   &$  =Y_{\rm AB} - 0.570 $ \\
+      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\
       $Y_{\rm WFCAM}$    &   10305    &   9790      &   10810   &   1020     & $Y_{\rm WFCAM}$     &$ =  Y_{AB}  - 0.617$           \\

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180827.tex
tex/older_tex/ removed

--- 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180823.tex
@@
 
+\vspace{-16pt}
 \section{Data}
@@
 Astronomy;][]{Emerson2006, Dalton2006}.
+
+We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
+the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
+WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
+In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.
 
@@
 
-\subsection{Near-infrared photometry}
+\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
 Due to their selection of being very faint/undetected in the
@@
 
-%\section{NIR Data}
 The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
@@
 matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
-2018, in prep, and has also been discussed in \citet{Cross2013} and \citet{Cross2017}.
+2018, in prep, and has also been discussed in \citet{Cross2013}.  
+%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS.
 We will give the pertinent points of the MAP and specific details of these data sets below.
@@
     {\it N.B.}, a few objects will have both UKIDSS LAS and VISTA VHS photometry...
-
-\subsection{Selection of NIR}
 
@@
 
-\subsection{Setup Matched Aperture Product}
+    \subsubsection{Setup Matched Aperture Product}
 
@@
 
-\subsection{Processing MAP data}
-
+    \subsubsection{Processing MAP data and Forced photometry} 
     A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
@@
 
-\subsubsection{Forced photometry}
     CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
@@
     binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
-VISTA survey products and also familiar to many astronomers through the INTWFS
-\citep{}, and VST-ATLAS and -VPHAS \citep{}. Since forced photometry can be run
+    VISTA survey products and also familiar to many astronomers through the INTWFS, 
+    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
+    Since forced photometry can be run
     in many ways on a particular image, a single science frame is not
@@
     \subsubsection{Averaging matched photometry}
-
     Unfortunately the photometry in a single epoch image often has low
@@
 
-\subsubsection{\ldots}
-
     The code to calculate variability statistics as described in \cite{Cross2009} has
@@
 
-\iffalse
-\subsection{Filter and Survey choices} 
-We make some choices when reporting our archival photometry. 
-This includes:
-\begin{itemize}
-\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
-\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
-\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
-\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
-\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
-\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
-\item Due to lack of coverage, do not report WFCAM $Z$-band. 
-\end{itemize}
-\fi
+\subsection{MIR data}
+The MIR data for this study comes exclusively from the Wide-field
+Infrared Survey Explorer (WISE) mission. Since we are only concerned
+here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
+exploration of the VH$z$Q population in e.g. the large Spitzer areal
+surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
+][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
+\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
+\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
+include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.
+
+We use data from the the beginning of the WISE mission \citep[2010
+January; ][]{Wright2010} through the fourth-year of NEOWISE-R
+operations \citep[2017 December;]{Mainzer2011}. More specifically, we
+use the data from the
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
+program and catalogue, which combines data from the WISE cryogenic and
+NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
+phases. For the our variability investigations, we supplement the
+ALLWISE data with data from the
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
+2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
+(W1 and W2) single-exposure images and extracted source information
+that were acquired between 2016 December 13 and 2017 December 13 UTC,
+which was the fourth year of survey operations of the Near-Earth
+Object Wide-field Infrared Survey Explorer Reactivation Mission
+(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
+data products are concatenated with those from the first three years
+(originally released on March 26, 2015, March 23, 2016 and June 1,
+2017) into a single archive.
+
+The WISE scan pattern leads to coverage of the full- sky approximately
+once every six months (a``sky pass''), but the satellite was placed in
+hibernation in 2011 February and then reactivated in 2013
+October. Hence, our light curves have a cadence of 6 months with a 32
+month sampling gap.
 
@@
 
-    \subsection{Detection Rates in the optical}
+    %\subsection{Detection Rates in the optical}
 
@@
 
+    \citet{Blain2013} Cras in laoreet mauris. Vivamus nec nulla a dui
+    commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet
+    auctor ligula ultricies. Phasellus condimentum gravida
+    tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et
+    augue id purus gravida sagittis quis in sem. Phasellus quis risus
+    bibendum eros luctus auctor.
+
     Recently, \citet{Assef2018} released two large catalogues of AGN 
@@
 
+    %\subsubsection{
+    Very High-$z$ Quasars Detected in WISE W3 and W4.
+    Proin non tempus velit. Etiam laoreet, enim nec scelerisque
+    dictum, tortor massa tempor enim, id pretium justo quam ac
+    lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
+    et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
+    eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
+    velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
+    purus.
+
+\begin{figure}
+   \centering
+   \includegraphics[width=8.5cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
+   \vspace{-16pt}
+   \caption[]
+   {Histogram showing the number of NEOWISE-R epochs and detections there are for each 
+    VH$z$Q.} 
+   \label{fig:MIR_LC_epochs}
+ \end{figure}
+
 \subsection{Variability}
-    Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
-pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
-id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
-dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
-euismod. Cras vel auctor neque. Nam quis diam risus.
-
-Nunc semper quam et leo interdum vulputate eu quis magna.
+VH$z$Qs, if accreting at, or above the Eddington Limit, might well
+have have large values of changing mass accretion rate, $\ddot{m_{\rm
+    accr}}$. A consequence of this would be that these quasar exhibit
+signs of variability, most likely showing up in their UV/optical
+rest-frame spectra. We look for evidence of this variability signature
+in the NIR and MIR light-curves of the VH$z$Qs. As a guide, \civ
+enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
+enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
+enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
+enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.
+
+    Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we unc semper quam et leo interdum vulputate eu quis magna.
 Sed nec arcu at orci egestas convallis.
@@
 
-    \subsection{Very High-$z$ Quasars in WISE}
-     \citet{Blain2013} 
-     Cras in laoreet mauris. Vivamus nec nulla a dui commodo
-     adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
-     ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
-     et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
-     sagittis quis in sem. Phasellus quis risus bibendum eros luctus
-     auctor.
-
-        \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
-        Proin non tempus velit. Etiam laoreet, enim nec scelerisque
-        dictum, tortor massa tempor enim, id pretium justo quam ac
-        lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
-        et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
-        eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
-        velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
-        purus.
+\begin{figure}
+   \includegraphics[width=8.5cm]
+   {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
+   \centering
+   \caption[]
+   {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
+     Red points are the W1 band; cyan points the W2 band.} 
+   \label{fig::MIR_LC_3egs}
+ \end{figure}
+
+    Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
+Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lighcurves and associated colour changes. Here we show 
+J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.
 
@@
 MINECO through grant AyA2014-55216 
-%\citet{} 
+%%
 The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}

### 2019-09-26 tex/VHzQ.tex
VHzQ tiny update

@@
   We query the WSA and VSA performing matched-aperture photometry at
-  the positions of our {\bf 488} VH$z$Qs. This database is world-readable and
-  we give the full recipe and relevant SQL queries for accessing both
-  databases in Appendix~\ref{sec:SQL} as well as online.
+  the positions of our {\bf 488} VH$z$Qs. This database is
+  world-readable and we give the full recipe and relevant SQL queries
+  for accessing both databases in Appendices~\ref{sec:SQL_WSA}
+  and~\ref{sec:SQL_VSA} as well as online.
 
@@
   total. Indeed, the standard aperture corrections work well for point
-  sources. Coadding using the matched-aperture photometry can give better results for the photometry, 
-  where the individual epochs are taken from multiple projects with different field-centres and orientations and point-spread functions since the individual epoch scattered light, pixel distortion and aperture corrections can be applied with the correct weighting.
+  sources. Coadding using the matched-aperture photometry can give
+  better results for the photometry, where the individual epochs are
+  taken from multiple projects with different field-centres and
+  orientations and point-spread functions since the individual epoch
+  scattered light, pixel distortion and aperture corrections can be
+  applied with the correct weighting.
 
@@
 time-domain investigation with upcoming large infrared space telescopes
-\citep{Jansen2018, White2019AAS}.
+\citep{Jansen2018, WhiteC2019AAS}.
 
@@
 VSERV1000v20190508}. The queries are the same as those used in the
-WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
+WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting
 with {\tt wserv1000} should be replaced with {\tt vserv1000}.

### 2020-01-09 tex/MNRAS_submission/rv1/referees_reply.txt
tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex update

@@
-	We thank the Referee for reading our manuscript carefully and for their review and comments.
-	We address each of these in turn below (indented text).
+	We thank the Referee for reading our manuscript carefully and
+	for their review and comments.  We address each and every one
+	of these in turn below (indented text).
 
-	We have also made further, key improvements to our dataset and pipeline.
+	We have also made further, key improvements to our dataset and
+	pipeline.
 
@@
 	it was brought to our attention (K. Perger; priv. comm) that
-	we were missing a 25 confirmed z>5 quasars.  As such, our
+	we were missing 25 confirmed z>5 quasars.  As such, our
 	database has increased by 25 objects for a total of 488 VHzQs.
+
+	As such, Tables 1, 2, 3, 4, 5, 6
 
@@
 
-	Consequently, we have changed the Abstract:
-		"Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had
-		significant differences between their WFCAM and VISTA
-		magnitudes in one band."
-	to
-		"Only one quasar, SDSS J0349+0034, shows significant
-		differences between WFCAM and VISTA magnitudes in one band."
+	Consequently, we have changed the approriate text (in the Abstract,
+	Section 3.1.1 Comparing WFCAM and VISTA and Conclusions).
 
@@
 
-	    To Do by NPR
+	    Now added.
 
@@
 
-	   Hmmm. I’m not sure what to do here; it’s going to ruin the clarity of the figure
-	   having both ZYJHK filter sets, but, they are different.
+	   We have enbiggened the  tick-marks.
+
+	   The ZYJHK filters for UKIRT and VISTA *are* different, but
+	   plotting both doesn't result in a clear figure.
+
 	   I think adding an explicit link to:

### 2020-01-09 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
VHzQs_23newobjects.dat and .tex update
VHzQ.tex updates
tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex update

--- 2019-06-17 tex/arXiV_submission/VHzQ_arXiv_submitted.tex
@@
 in multiple bands of SDSS J0959+0227, and very marginally in the
-$Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and
-SDSS J2220-0101 had significant differences between their WFCAM and
-VISTA magnitudes in one band.  With supermassive black hole accretion
-likely to be redshift invariant up to very high-redshift, further
-monitoring of these sources is warranted.  All the data, analysis
-codes and plots used and generated here can be found at:
+$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
+significantdifferences between WFCAM and VISTA magnitudes in one band.
+With supermassive black hole accretion likely to be redshift invariant
+up to very high-redshift, further monitoring of these sources is
+warranted.  All the data, analysis codes and plots used and generated
+here can be found at:
 \href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
@@
 optical emission is redshifted into the observed near-infrared (NIR)
-at redshifts $z>5$. Fortunately, data are now in place from deep,
-wide-field NIR instruments and surveys such as the Wide Field Camera
-(WFCAM) instrument on the United Kingdom Infra-Red Telescope (UKIRT)
-in the Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on
-the Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
+at redshifts $z>5$, and relativistic time dilation also stretches the
+photometric variability of the accretion disk as observed.
+Fortunately, data are now in place from deep, wide-field NIR
+instruments and surveys such as the Wide Field Camera (WFCAM)
+instrument on the United Kingdom Infra-Red Telescope (UKIRT) in the
+Northern Hemisphere and the VISTA InfraRed CAMera (VIRCAM) on the
+Visible and Infrared Survey Telescope for Astronomy (VISTA) in the
 Southern Hemisphere, that are necessary for identifying VH$z$Qs.
@@
   \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
-  {filters_vs_QSOstars_z6pnt7.pdf}
+%  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
+  {figures/filters_vs_QSOstars_z6pnt7.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=10mm 0mm 0mm 0mm]
-  {Nofz_0pnt075bins_20190614.pdf}
+  % {../Nofz/Nofz_0pnt075bins_20190614.pdf}
+   {figures/Nofz_0pnt075bins_20190614.pdf}
   \centering
@@
   \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
-  {CoverageMaps_VHzQ_forpaper.pdf}
+  % {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
+ {figures/CoverageMaps_VHzQ_forpaper.pdf}
   \centering
   \caption[]
-  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
+  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING
+(DR5; blue) and ULAS (DR11; red), the most recent public releases of
+the 4 main surveys. The VH$z$Qs are given by black dots.}
   \label{fig:coverage}
@@
 \begin{landscape}
+  %\input{../tables_for_paper/output_table_top5pc}
  \input{output_table_top5pc}
@@
   was $>0.$ and $>5$ average flux error. In order to account for large
-  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
-  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
-  selects two quasars with large, $\delta$mag $>0.2$mag differences
-  between the WSA and VSA. These are SDSSJ0349+0034 and
-  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
-  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
-  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
-  = 19.38$\pm$0.04.
+  errors in either the WFCAM or VISTA photometry, objects with
+  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
+  were removed. This selects one quasar with large, $\delta$mag
+  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
+  which has a WSA $K$-band magnitude of 19.13$\pm$0.24, while for the
+  VSA $K_s$-band this is 18.36$\pm$0.10 mag.
 
@@
   \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
-  {WISEmag_vs_coverage_20190605.pdf}
+  % {../detections/WISEmag_vs_coverage_20190605.pdf}
+ {figures/WISEmag_vs_coverage_20190605.pdf}
   \centering
@@
     \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
-    {W1W2W3_hexplots_20190615_AB.png} 
+    %{../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190615_AB.png}
+    {figures/W1W2W3_hexplots_20190615_AB.png}
   \vspace{-14pt}
@@
     \centering
-    \includegraphics[width=0.24\textwidth]{DELS_J1048-0109.png} 
-    \includegraphics[width=0.24\textwidth]{UHS_J0439+1634.png} 
-    \includegraphics[width=0.24\textwidth]{SDWISE_J0306+1853.png}
-    \includegraphics[width=0.24\textwidth]{SDSS_J0100+2802.png}
+%    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/DELS_J1048-0109.png} 
+ %   \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
+  %  \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDWISE_J0306+1853.png}
+  %  \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
+     \includegraphics[width=0.24\textwidth]{figures/DELS_J1048-0109.png} 
+   \includegraphics[width=0.24\textwidth]{figures/UHS_J0439+1634.png} 
+    \includegraphics[width=0.24\textwidth]{figures/SDWISE_J0306+1853.png}
+   \includegraphics[width=0.24\textwidth]{figures/SDSS_J0100+2802.png}
     \caption{VH$z$Qs with interesting MIR properties. 
@@
   \includegraphics[width=8.5cm]
-  {NEOWISER_LC_histogram_20190606.png}
+  % {../light_curves/MIR_LCs/NEOWISER_LC_histogram_20190606.png}
+   {figures/NEOWISER_LC_histogram_20190606.png}
   \vspace{-16pt}
@@
   \centering
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J0100.png}
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
-  \includegraphics[width=8.5cm]{NEOWISER_LCs_VHzQs_SDSS_J1621.png}
+%  \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J0100.png}
+ % \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
+ % \includegraphics[width=8.5cm]{../light_curves/MIR_LCs/NEOWISER_LCs_VHzQs_SDSS_J1621.png}
+  \includegraphics[width=8.5cm]{figures/NEOWISER_LCs_VHzQs_SDSS_J0100.png}
+ \includegraphics[width=8.5cm]{figures/NEOWISER_LCs_VHzQs_SDWISE_J1752.png}
+ \includegraphics[width=8.5cm]{figures/NEOWISER_LCs_VHzQs_SDSS_J1621.png}
   \caption[]
@@
     \centering
-    \includegraphics[width=8.5cm]{MMTJ0215-0529LC_20190613.png}
+    % \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/MMTJ0215-0529LC_20190613.png}
     \caption{The infrared light curve for MMT J0215-0529 with data from 
       WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
-      MMT  J0215-0529 was identified by \citet{McGreer2018}.}
+MMT  J0215-0529 was identified by \citet{McGreer2018}, 
+% 02:15:23.27 −05:29:45.8
+%g_AB = 28.05 \pm 1.00 
+%r_AB = 22.69 \pm  0.01
+%           20.85 \pm  0.01 
+%           20.64 \pm 0.01
+% −25.7 5.13 MMT 
+}
     \label{fig:MMTJ0215-0529}
@@
     \centering
-    \includegraphics[width=8.5cm]{CFHQSJ0216-0455LC_20190613.png}
+%    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/CFHQSJ0216-0455LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
@@
     \centering
-    \includegraphics[width=8.5cm]{SHELLQsJ0220-0432LC_20190613.png}
+  %  \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/SHELLQsJ0220-0432LC_20190613.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
@@
     \centering
-    \includegraphics[width=8.5cm]{SDSSJ0959+0227LC_20190612.png}
+    %\includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
+    \includegraphics[width=8.5cm]{figures/SDSSJ0959+0227LC_20190612.png}
         \caption{The near infrared light curve for SDSS J0959+0227. Note, 
@@
   \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;
-    \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though 
-      efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
-    \item 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band; 
-    \item The 14 objects that are not detected in the NIR are due to lack of coverage rather than lack of depth; 
-   \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper unWISE W1 catalog. 
- \item All of the $z\geq7$ quasars are detected in both unWISE W1 and W2. 
- \item 32 of the quasars had enough NIR measurements and sufficient NIR measurements and signal-to-noise to look for variability.
-Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the Y-band of MMT J0215-0529.
-2 other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band, also indicating variability.
+  \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though efforts are being made to address this
+    \citep[e.g.,][]{YangJ2018a};
+  \item 97.0\% of the VH$z$Q sample is detected in one or more NIR
+    ($ZYJHK/K_{s}$) band;
+  \item The 14 objects that are not detected in the NIR are due to
+    lack of coverage rather than lack of depth;
+  \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper
+    unWISE W1 catalog.
+  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and
+    W2.
+  \item 32 of the quasars had enough NIR measurements and sufficient
+    NIR measurements and signal-to-noise to look for variability. Weak
+    variability was detected in multiple bands of SDSS J0959+0227, and
+    very marginally in the Y-band of MMT J0215-0529. Only one quasar, SDSS
+    J0349+0034 had significant differences between their WFCAM and VISTA
+    magnitudes in one band, indicating variability.
  \end{itemize}
@@
 \subsection*{Author Contributions}   
-N.P.R.
-initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
-
-N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
+N.P.R. initiated the project, compiled the list of $z>5.00$ quasars,
+wrote most of the analysis code, developed the plotting scripts, and
+developed and wrote the initial and subsequent drafts of the
+manuscript.
+
+N.J.G.C. supplied the critical near-infrared expertise and database
+for which the bulk of the project relies. N.J.G.C. also contributed
+directly to the writing of the manuscript.
 

### 2020-01-09 tex/MNRAS_submission/rv1/VHzQ_MNRAS_20190917.tex
VHzQ_MNRAS_20190917.tex added

--- 2019-09-26 tex/VHzQ.tex
@@
 \begin{abstract}
-We assemble a catalogue of {\bf 488} spectroscopically confirmed very high
+We assemble a catalogue of 488 spectroscopically confirmed very high
 ($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
@@
 This paper is organized as follows. In Section 2, we present the
-assembled list of the {\bf 488} $z\geq5.00$ VH$z$Qs that we have
+assembled list of the 488 $z\geq5.00$ VH$z$Qs that we have
 compiled. We then give a high-level overview of the photometric
@@
 
-We have compiled a list of {\bf 488} quasars with redshifts $z\geq5.00$. We
+We have compiled a list of 488 quasars with redshifts $z\geq5.00$. We
 use all the $z\geq5.00$ quasars that have been discovered,
@@
 
-{\bf We updated our list of objects between the submitted paper and accepted due
+We updated our list of objects between the submitted paper and accepted due
 to feedback from other scientists. We discuss these changes in detail in
@@
   \caption[]
-  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING (DR5; blue) and ULAS (DR11; red), the most recent public releases of the 4 main surveys. The VH$z$Qs are given by black dots.}
+  {The coverage maps for VHS (DR6; orange), UHS (DR1; olive), VIKING
+    (DR5; blue) and ULAS (DR11; red), the most recent public releases of
+    the 4 main surveys. The VH$z$Qs are given by black dots.}
   \label{fig:coverage}
@@
   We query the WSA and VSA performing matched-aperture photometry at
-  the positions of our {\bf 488} VH$z$Qs. This database is
+  the positions of our 488 VH$z$Qs. This database is
   world-readable and we give the full recipe and relevant SQL queries
@@
 \section{Results}
-Having collated the sample of {\bf 488} VH$z$Qs, and obtained their near-
+Having collated the sample of 488 VH$z$Qs, and obtained their near-
 and mid-infrared photometry we report here the various photometric
@@
 \end{tabular}
-\caption{
-{\bf Five quasars with updated coordinates.}
-}
+\caption{Five quasars with updated coordinates.}
 \label{tab:disagree_objs}

### 2020-01-09 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
VHzQ_MNRAS_rv1.tex updated

@@
 \begin{abstract}
-We assemble a catalogue of 463 spectroscopically confirmed very high
+We assemble a catalogue of 488 spectroscopically confirmed very high
 ($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
@@
 This paper is organized as follows. In Section 2, we present the
-assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
+assembled list of the 488 $z\geq5.00$ VH$z$Qs that we have
 compiled. We then give a high-level overview of the photometric
@@
 
-We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
+We have compiled a list of 488 quasars with redshifts $z\geq5.00$. We
 use all the $z\geq5.00$ quasars that have been discovered,
@@
 \citet{Saxena2018},
+\citet{Schneider2007}, 
 \citet{Stern2007},  
@@
 \citet{Zeimann2011}.
+
+We updated our list of objects between the submitted paper and accepted due
+to feedback from other scientists. We discuss these changes in detail in
+Appendix~\ref{app:qso_sample}.
 
@@
 \hline 
-5.00         & 1180          &  463   \\
-5.70         & 1000          &  267   \\
-6.00         &   937          &  170   \\
-6.19         &   900          &  86   \\
+5.00         & 1180          &  488   \\
+5.70         & 1000          &  273  \\
+6.00         &   937          &  174   \\
+6.19         &   900          &  87   \\
 6.50         &    845         &  40   \\
@@
   We query the WSA and VSA performing matched-aperture photometry at
-  the positions of our 463 VH$z$Qs. This database is world-readable and
+  the positions of our 488 VH$z$Qs. This database is world-readable and
   we give the full recipe and relevant SQL queries for accessing both
-  databases in Appendix~\ref{sec:SQL} as well as online.
+  databases in Appendix~\ref{sec:SQL_WSA} as well as online.
 
@@
 \section{Results}
-Having collated the sample of 463 VH$z$Qs, and obtained their near-
+Having collated the sample of 488 VH$z$Qs, and obtained their near-
 and mid-infrared photometry we report here the various photometric
@@
 candidates at 75\% completeness ($\approx$700 AGN candidates per
-deg$^2$). Crossmatching our catalogue of 463 VH$z$Qs with these
+deg$^2$). Crossmatching our catalogue of 488 VH$z$Qs with these
 catalogues, produces 42 matches with the R90 sample and 98 matches
@@
   \item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog.
+  \item Krisztina Perger for key discussions about missing objects after the pre-print appeared. 
   \item Tim Brooke at the \href{https://irsasupport.ipac.caltech.edu/index.php}{IRSA Help Desk}; 
@@
 VSERV1000v20190508}. The queries are the same as those used in the
-WSA, see Appendix~\ref{sec:SQL}, but the names of the tables starting
+WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting
 with {\tt wserv1000} should be replaced with {\tt vserv1000}.
+
+\section{Updated VH$z$Q Sample}
+\label{app:qso_sample}
+Between the journal submitted version of this paper (which was
+also the arXiv v1) we updated the sample of VH$z$Qs from a total of
+463 objects to 488 objects.  16 of these objects were from
+\cite{YangJ2018a} and 9 objects were added after discussions with
+Krisztina Perger, with the relevant catalog found at 
+\href{http://astro.elte.hu/$\sim$perger/catalog.html}{astro.elte.hu/$\sim$perger/catalog.html}.
+We do not include the object DES0141-54 \citep{Belladitta2018}, since we were unable to 
+obtain arcsecond level coordinates to perform our matched-aperture photometry.
+We also update the positions of five objects, see Table~\ref{tab:disagree_objs}.
+
+One object in the Perger catalogue, VA-13492 we could not immediately cross-match. 
+In this case the coordinates looked similar to SDSSJ1040-1155, and
+the stated redshift was identical, $z=5.44$. Additionally the $i$-band magnitude 
+was equivalent to SDSS J1040-1155
+($i=25.9$ mag). SDSS J1040-1155 is first reported in \citet{Douglas2007} 
+and a transcription error seems to have occurred in \citet{Flesch2015}.
+
+\begin{table*}
+\begin{tabular}{l r r r r r}
+\hline  \hline
+Object Name                      & R.A.               & Decl.  &  redshift  & difference \\
+                                          & / deg             & / deg  &                & arcsec  \\
+\hline
+%% QSOs where pos changed (same name)
+DELS J1048-0109               & +162.0795417 & -1.1611694        & 6.678   &     12.1 \\
+SHELLQs J1429-0002          & +217.3342500 & -0.0353889        & 6.04    &  150.0 \\
+DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
+ATLAS J332.8017-32.1036 & +332.8017500 & -32.1035556      & 6.3394  &    3.2 \\
+VIK J2318-3113                  & +349.5764625 & -31.2295417      & 6.4435  &  239.9 \\
+\hline  \hline
+\end{tabular}
+\caption{Five quasars with updated coordinates.}
+\label{tab:disagree_objs}
+\end{table*}
 

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt
rv1/referees_reply.txt update
tex/MNRAS_submission/rv1/referees_reply.tx

@@
 
-	As such, Tables 1, 2, 3, 4, 5, 6
+	As such all six Tables have been updated accordingly, as have
+	Figures 2 and 3.
 
@@
 
+	   ....
 		I think adding an explicit link to:
@@
 
-p. 3, Fig. 3, caption or text: You should briefly comment on why the quasar
+p. 3, Fig. 2, caption or text: You should briefly comment on why the quasar
 distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
@@
 
-	This is Figure 2, not 3.
 	And I think this is where some of the missing objects come in??
@@
 
-    NPR to double check…
+    	Checked and updated.
 
@@
 
-		NPR to add this to the text.
+		NPR has added approriated words in the text to address
+		this good point.
 

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt
referees_reply.txt updated

@@
 
-	And I think this is where some of the missing objects come in??
-	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.
+	[And I think this is where some of the missing objects come in??
+	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.]
 
@@
 
-		NPR has added approriated words in the text to address
-		this good point.
+		We have added approriated words in the text to address this good point.
 
@@
 photometric zeropoints.
-
-		NPR to change.
 
@@
 
-	 	 NPR to update.
-
 p. 9 top left: = -0.458 : All minus signs in latex should be coded up as --
@@
 
-		 NPR to update.
-
 p. 10 Fig 8: Enlarge all axes label for better readability.
-
-      	        NPR to update.
 
@@
 ratio or SNR.
-
-		NPR to update.

### 2020-01-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
referees_reply.txt updated

@@
 The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
-Investigating this in detail is very interesting but left to a future study.
+As a check, we utilize data from the {\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel 4 8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density measurements from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}.
+%% address now the number of expected contaminating 8--25 micron sources in the apertures used, as it can be done straightforwardly.
+E.g., Driver et al.
+(2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this estimate are actually best given as Fig.
+A4, A5 on the astro-ph version.
+The redshift distribution of the sampled 8--24 $\mu$m foreground objects is narrow enough and their $K$-corrections advantageous enough, that the objects
+counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized differential counts --- especially in e.g.
+WISE W4 --- have most of their  extragalactic background light energy emerging at AB$\sim$18--20 mag.
+As a consequence, the relative number or probability of contaminating objects at AB$>20$mag inside our apertures should be small.
+%Investigating this in detail is very interesting but left to a future study.
 
@@
 Macleod2016, Gezari2017, Runco2016, YangQ2018, Assef2018, Stern2018,
-Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$
+Ross2018, MacLeod2019, Graham2019b}. As a guide, we note that H$\alpha$
 is redshifted to 3.94$\mu$m (i.e. W1) at $z=5.00$ and 5.57$\mu$m,

### 2020-01-10 tex/MNRAS_submission/rv1/referees_reply.txt
Modified Sec 3.11 with epoch numbers

@@
 
-	This is the coverage map figure
-	       => To Do by NJGC.
+	We have updated the plot to make the dots bigger and the revised catalogue.
 
@@
 
-              This is for SDSS J0349+0034 and J2220-0101; NJGC to check.
+SDSS J0349+0034 was observed on MJD=54062.4 by WFCAM and MJD=55540.6 (average of 
+3 epochs from 55537 to 55542) by VISTA. We have updated the text with these values.
 

### 2020-01-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Modified Fig 3, coverage maps with new QSOs and bigger symbols
Modified Sec 3.11 with epoch numbers

@@
 %%trim=l b r t
-  \includegraphics[width=8.0cm, clip, trim=0mm 25mm 0mm 40mm]
+  \includegraphics[width=8.0cm, clip, trim=0mm 0mm 0mm 10mm]
   % {../data/WSA_VSA/CoverageMaps_VHzQ_forpaper.pdf}
@@
   $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
-  which has a WSA $K$-band magnitude of 19.13$\pm$0.24, while for the
-  VSA $K_s$-band this is 18.36$\pm$0.10 mag.
+  which has a WSA $K$-band magnitude of 19.13$\pm$0.24 (observed at
+  MJD=54062.4), while for the VSA $K_s$-band this is 18.36$\pm$0.10 mag
+  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
+  observations are $\sim4$ years apart.
 

### 2020-01-13 tex/MNRAS_submission/rv1/referees_reply.txt
Fixed numbers for VegaToAB, added to referee reply

@@
 	had large photometric changes but now acknowledge this was due
-	to an incorrect apertureID measurement. The updated photometry
-	for SDSS J2220-0101 has the VSA J-band magnitude 19.38+/-0.04
-	and a WSA magnitude 19.24+/-0.09.
+	to an incorrect apertureID assignment, when the database was updated 
+	with new data. The updated photometry for SDSS J2220-0101 has the  
+	VSA J-band magnitude 20.32+/-0.07 mag AB and a WSA magnitude 20.30+/-0.15 mag AB.
 
-	Consequently, we have changed the approriate text (in the Abstract,
+	Consequently, we have changed the appropriate text (in the Abstract,
 	Section 3.1.1 Comparing WFCAM and VISTA and Conclusions).
@@
 3 epochs from 55537 to 55542) by VISTA. We have updated the text with these values.
+We have also updated the values to AB magnitudes, as we found that we had inadvertently 
+given the Vega magnitude values.
 

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Fixed numbers for VegaToAB, added to referee reply

@@
 $Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
-significantdifferences between WFCAM and VISTA magnitudes in one band.
+significant differences between WFCAM and VISTA magnitudes in one band.
 With supermassive black hole accretion likely to be redshift invariant
@@
   $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
-  which has a WSA $K$-band magnitude of 19.13$\pm$0.24 (observed at
-  MJD=54062.4), while for the VSA $K_s$-band this is 18.36$\pm$0.10 mag
+  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 AB (observed at
+  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
   (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated table 1, figure 2 and tex with up to date numbers

@@
 Pan-STARRS1 (PS1; PSO in Table~\ref{tab:surveys}) survey and alone
-identified over half (54.6\%) of the VH$z$Q population. Data from the
+identified over half (55.5\%) of the VH$z$Q population. Data from the
 Hyper Suprime-Cam (HSC) on the Subaru telescope is responsible for
-13.6\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
+13.1\% of our dataset (HSC+SHELLQs in Table~\ref{tab:surveys}). The
 combination of surveys is also vital for identifying VH$z$Qs. The
 UKIDSS Large Area Survey (ULAS) on its own, or in combination with
-other surveys is responsible for 6.5\% of the sample (SUV+ULAS)
+other surveys is responsible for 6.3\% of the sample (SUV+ULAS)
 including the highest-$z$ object. Where more than one survey is used
@@
 \hline  
-  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
-  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
-  DELS$^{a}$       &   16    &   ( 3.46)    &  \citet{Dey2018} \\
-  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
-  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
-  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
-  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
-  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
-  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
-  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
-  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
-  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
- SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
+  ATLAS             &     4    &   ( 0.82)    &  \citet{Shanks2015} \\
+  CFHQS            &   20    &   ( 4.10)    &  \citet{Willott2007} \\
+  DELS$^{a}$       &   16    &   ( 3.28)    &  \citet{Dey2018} \\
+  ELAIS              &     1    &   ( 0.20)    &  \citet{Vaisanen2000} \\
+  FIRST              &     1    &   ( 0.20)    &  \citet{Becker1995} \\
+  HSC                 &    9    &   ( 1.84)    & \citet{Miyazaki2018} \\
+  IMS                 &     5    &   ( 1.02)     &  \citet{Kim2015} \\
+  MMT               &   12    &   ( 2.46)     &  \citet{McGreer2013} \\
+  NDWFS           &     1    &   ( 0.20)    &  \citet{JD1999} \\
+  PSO                 &   100   &   (20.49)   &   \citet{Kaiser2002, Kaiser2010}
+  \\
+  RD                   &     1   &   ( 0.20)    &  \citet{Mahabal2005} \\
+  SDSS                &  171  &    (35.04)    & \citet{EDR} \\
+ SDWISE$^{b}$    &   27    &  ( 5.53)    &   \citet{WangF2016} \\
 %% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
-  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
-  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
-  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
-  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
-  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
-  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
-  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
-  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
+  SHELLQs         &    55    &   (11.27)  &  \citet{Matsuoka2016}     \\  
+  SUV$^{c}$       &   21     &    (4.30)  & \citet{YangJ2017} \\
+  TGSS				&	1		&	(0.20)	& \citet{Saxena2018} \\
+  TN				& 	1		&	(0.20)	& ?? \citet{vanBreugel1999} \\
+  UHS               &    1      &  ( 0.20)     &  \citet{WangF2017} \\
+  ULAS               &   10   &   ( 2.05)     & \citet{Lawrence2007} \\
+  VDES$^{d}$       &   17  &    ( 3.48)     &  \citet{Reed2017} \\
+  VHS                 &     1  &     ( 0.20)    & \citet{WangF2018b} \\
+  VIK                 &     10    &  ( 2.05)    &  \citet{Edge2013} \\
+  VIMOS           &    1      &  ( 0.20)     &   \citet{LeFevre2003} \\
+  XMM				& 	1	&	 (0.20)		& \citet{Khorunzhev2017} \\
 \hline  \hline
@@
   % {../Nofz/Nofz_0pnt075bins_20190614.pdf}
-   {figures/Nofz_0pnt075bins_20190614.pdf}
+   {figures/Nofz_0pnt075bins_20200113.pdf}
   \centering

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated tables 1 and 4, Figure 2

@@
   \citet{Cross2013} and with fuller details to appear in a forthcoming
-  paper (Cross et al., 2019, in prep).
+  paper (Cross et al., 2020, in prep).
 
@@
     Any band ($ZYJHK/K_{s}$)    &  473  (96.9) \\
-    $Z$-band                            &  81  (16.5) \\
+    $Z$-band                            &  81  (16.6) \\
     $Y$-band                            &  289  (59.2) \\
@@
     $H$-band                            &  277  (56.8) \\
-    $K$ or $Ks$-band                &  343  (70.2) \\
+    $K$ or $Ks$-band                &  343  (70.3) \\
     \hline  \hline
@@
   \caption{Detection rate of VH$z$Qs in the near-infrared. 
-For the 14 objects that have no NIR detections, 3 have 
+For the 15 objects that have no NIR detections, 3 have 
 been observed but are not in our queried time range, 6 have 
-not been observed yet and 5 objects are too far north to be visible 
+not been observed yet and 6 objects are too far north to be visible 
 by UKIRT. }
@@
   significant offset is the $Y$-band. All of the VISTA averages are
-  negative and all of the WFCAM ones are positive. The $Ks$ versus $K$
+  negative and all of the WFCAM ones are positive. The $K_s$ versus $K$
   band comparison may be affected the different shapes of the filters,
@@
   $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
-  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 AB (observed at
+  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 mag AB (observed at
   MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
-  (observed 3 times between MJD=55537 and 55542). The WFCAM and VISTA
-  observations are $\sim4$ years apart.
+  (observed 3 times between MJD=55537 and 55542), meaning that the WFCAM and
+  VISTA observations are $\sim4$ years apart.
 

### 2020-01-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated with new database name

@@
 \href{http://wsa.roe.ac.uk:8080/wsa/SQL_form.jsp}{{\tt Free Form SQL
-Query}} page the Database release {\tt WSERV1000v20190507} can be
+Query}} page the Database release {\tt WSERV1000v20200113} can be
 accessed which contains all the data we use here.
@@
 Query} page is where the database release to use is {\tt
-VSERV1000v20190508}. The queries are the same as those used in the
+VSERV1000v20200113}. The queries are the same as those used in the
 WSA, see Appendix~\ref{sec:SQL_WSA}, but the names of the tables starting

### 2020-01-14 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updates for table 3, SQL, parts of text

@@
   which has a WSA $K$-band magnitude of 21.03$\pm$0.35 mag AB (observed at
-  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
+  MJD=54062.4), while for the VSA $K_s$-band this is 20.20$\pm$0.14 mag AB
   (observed 3 times between MJD=55537 and 55542), meaning that the WFCAM and

### 2020-01-15 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated table 3, table 5 and some text
Updated figures and text

@@
   significant offset is the $Y$-band. All of the VISTA averages are
-  negative and all of the WFCAM ones are positive. The $K_s$ versus $K$
-  band comparison may be affected the different shapes of the filters,
-  with $K$ being significantly wider than $K_s$, able to detect light at
+  negative and all of the WFCAM ones are positive, except for J where the
+  difference is negligable. The $K_s$ versus $K$ band comparison may be affected
+  the different shapes of the filters, with $K$ being significantly wider than $K_s$, able to detect light at
   longer wavelengths.
@@
       \hline
-      $Z$                 &  7.2 	& 3 \\
-      $Y$                 &  59.1 	& 62 \\
-      $J$                  &    6.3 	& 111 \\
-      $H$                 &  41.7     &  103 \\
-      $K_{\rm s}$/$K$ &  15.1     & 114 \\
+      $Z$                 &  13.1 	& 3 \\
+      $Y$                 &  59.3 	& 63 \\
+      $J$                  &    0.9 	& 125 \\
+      $H$                 &  14.9     &  108 \\
+      $K_{\rm s}$/$K$ &  1.1     & 114 \\
       \hline  \hline
@@
 with the signal-to-noise is required to be $\geq8$ (i.e. {\tt
-aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 21 WFCAM 
-and 12 VISTA objects with 1 object (VIK J1148+0056) in common to both, 
-and this sample of 32 is our starting
+aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 18 WFCAM 
+and 12 VISTA objects with 2 objects (SDSSJ0221-0342B $\&$ VIK J1148+0056) in
+common to both, and this sample of 28 is our starting
 point for variability investigations.
@@
 SDSS J0959+0227 (see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
-for $Y$ only. The $H$-band amplitude was 0.9 mag and the $Y$-band amplitude was 1.2 mag if averaged over 6 months,
-or 0.9 mag if averaged over 1 year.
+for $Y$ only. The $H$-band amplitude was 0.7 mag and the $Y$-band amplitude was
+1.2 mag if averaged over 6 months, or 0.9 mag if averaged over 1 year.
 
@@
     % \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
-    \includegraphics[width=8.5cm]{figures/MMTJ0215-0529LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/MMTJ0215-0529LC_20200115.png}
     \caption{The infrared light curve for MMT J0215-0529 with data from 
@@
 %    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
-    \includegraphics[width=8.5cm]{figures/CFHQSJ0216-0455LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/CFHQSJ0216-0455LC_20200115.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
@@
   %  \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
-    \includegraphics[width=8.5cm]{figures/SHELLQsJ0220-0432LC_20190613.png}
+    \includegraphics[width=8.5cm]{figures/SHELLQsJ0220-0432LC_20200115.png}
     \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
@@
     %\includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
-    \includegraphics[width=8.5cm]{figures/SDSSJ0959+0227LC_20190612.png}
+    \includegraphics[width=8.5cm]{figures/SDSSJ0959+0227LC_20200115.png}
         \caption{The near infrared light curve for SDSS J0959+0227. Note, 
@@
 3515/3625\AA\ i.e. the rest-frame UV/very blue, so, so the regular
-blue QSO continuum could be emerging Thus, with the slightest hint of
+blue QSO continuum could be emerging. Thus, with the slightest hint of
 variability, this could potentially be a high-$z$ AGN transitioning
@@
     \citep[e.g.,][]{YangJ2018a};
-  \item 97.0\% of the VH$z$Q sample is detected in one or more NIR
+  \item 96.9\% of the VH$z$Q sample is detected in one or more NIR
     ($ZYJHK/K_{s}$) band;
-  \item The 14 objects that are not detected in the NIR are due to
+  \item The 15 objects that are not detected in the NIR are due to
     lack of coverage rather than lack of depth;
@@
     W2.
-  \item 32 of the quasars had enough NIR measurements and sufficient
+  \item 28 of the quasars had enough NIR measurements and sufficient
     NIR measurements and signal-to-noise to look for variability. Weak

### 2020-01-16 tex/MNRAS_submission/rv1/referees_reply.txt
Updated tables 1 and 4, Figure 2
Made last changes for now

@@
 
-	   We have enbiggened the  tick-marks.
+	   We have enlargened the  tick-marks.
 
 	   The ZYJHK filters for UKIRT and VISTA *are* different, but
-	   plotting both doesn't result in a clear figure.
-
-	   ....
-		I think adding an explicit link to:
-	          d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png
-	  and
-	         d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png
-	 is the way forward here.
+	   plotting both doesn't result in a clear figure. We have added an explicit link to:
+	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png and
+	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png.
 
@@
 
-	[And I think this is where some of the missing objects come in??
-	We’ll need to update: Tables 1, 2 and obviously 3 once we have those extra objects.]
+	Updated table 1,2 and figure 2. This gap has partly been filled in by recent (2018) 
+	discoveries e.g. Yang et al. (2018) - which includes many of the 25 new objects that 
+	we have recently added.
 
@@
 
-	We have updated the plot to make the dots bigger and the revised catalogue.
+	We have updated the plot to make the dots bigger and to use the revised catalogue.
 
@@
 
-		We have added approriated words in the text to address this good point.
+		We have added approriate words in the text to address this good point.
 
@@
 photometric zeropoints.
+
+We have updated both tables 3 and 5 with the new objects and some new VISTA photometry 
+(increasing the end time to 20170101) and have added a line in the caption to Table 3.
 
@@
 
+Still to do....
+
 p. 9 top left: = -0.458 : All minus signs in latex should be coded up as --
@@
 
+Done. Table 3 and Table C1 done.
+
 p. 10 Fig 8: Enlarge all axes label for better readability.
+
+Still to do...
 
@@
 ratio or SNR.
+
+Done.

### 2020-01-16 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Made last changes for now

@@
 find 32 of the quasars have sufficient NIR measurements and
-signal-to-noise to look for variability. Weak variability was detected
+signal-to-noise ratio to look for variability. Weak variability was detected
 in multiple bands of SDSS J0959+0227, and very marginally in the
@@
     The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
+    The main difference is the $K_s$ band in VISTA that is narrower than the
+    WFCAM K, but there are other minor differences. The two sets of filters are
+    shown in
+    \href{https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters$\_$vs$\_$QSOstars$\_$UKIRT.png}{\tt
+    github.com/d80b2t/VHzQ/SEDs/filters$\_$vs$\_$QSOstars$\_$UKIRT.png} and 
+    \href{https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters$\_$vs$\_$QSOstars$\_$VISTA.png}{\tt
+    github.com/d80b2t/VHzQ/SEDs/filters$\_$vs$\_$QSOstars$\_$VISTA.png}
+    respectively.
     The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration.
@@
 
-  The photometry in a single epoch image often has low
-  signal-to-noise.  The advantage of matched aperture photometry on
+  The photometry in a single epoch image often has a low
+  signal-to-noise ratio. The advantage of matched aperture photometry on
   quasars is that co-adding is relatively simple if each epoch is taken
@@
 
-For the our MIR variability investigations, we use the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{NEOWISE-R 2019 Data Release}.
-NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired up until 2018 December 13 (MJD 58465) including the fifth year of survey operations of NEOWISE.
-These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
+For the our MIR variability investigations, we use the 
+\href{http://wise2.ipac.caltech.edu/docs/release/neowise/}{NEOWISE-R 2019 Data
+Release}.  NEOWISE 2019 makes available the 3.4 and 4.6 μm (W1 and W2)
+single-exposure images  and extracted source information that was acquired up
+until  2018 December 13 (MJD 58465) including the fifth year of survey
+operations of  NEOWISE. These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
 %%
@@
   \caption{Detection rates in the mid-infrared bands from WISE as a function of 
-    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
+    redshift. A signal-to-noise ratio cut of {\tt w$x$snr}$>3.0$ has been used
+    for each band.}
   \label{tab:mir_detection}
@@
   \vspace{-14pt}
-  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} Vega magnitude against signal-to-noise,
-    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
+  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} Vega magnitude against signal-to-noise
+  ratio, colour coded by {\tt w$x$cov} the mean coverage depth, in each
+  corresponding band.}
   \label{fig:WISEmag_vs_coverage}
@@
 using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} 
-shows the WISE AllWISE magnitude versus signal-to-noise, colour coded
+shows the WISE AllWISE magnitude versus signal-to-noise ratio, colour coded
 by {\tt w$x$cov} the mean coverage depth, in each corresponding
@@
 trend for brighter objects to have larger SNR, and also for the higher
-signal to noise for objects with more exposures at a given
+signal-to-noise ratio for objects with more exposures at a given
 magnitude. The behaviour for the W3/4 bands is different, with two
@@
 The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
-(W1-W2) = -0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
+(W1-W2) = --0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
 is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
@@
 calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
-with the signal-to-noise is required to be $\geq8$ (i.e. {\tt
+with the signal-to-noise ratio is required to be $\geq8$ (i.e. {\tt
 aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 18 WFCAM 
@@
 where measurements have been averaged over different time-scales to improve 
-the signal-to-noise. We found that two quasars showed signs of variability:
+the signal-to-noise ratio. We found that two quasars showed signs of
+variability:
 MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
@@
   \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;
-  \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though efforts are being made to address this
-    \citep[e.g.,][]{YangJ2018a};
+  \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$,  though
+  efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
   \item 96.9\% of the VH$z$Q sample is detected in one or more NIR
@@
   \item 28 of the quasars had enough NIR measurements and sufficient
-    NIR measurements and signal-to-noise to look for variability. Weak
+    NIR measurements and signal-to-noise ratio to look for variability. Weak
     variability was detected in multiple bands of SDSS J0959+0227, and
@@
 %% QSOs where pos changed (same name)
-DELS J1048-0109               & +162.0795417 & -1.1611694        & 6.678   &     12.1 \\
-SHELLQs J1429-0002          & +217.3342500 & -0.0353889        & 6.04    &  150.0 \\
+DELS J1048-0109               & +162.0795417 & --1.1611694        & 6.678   &   
+12.1 \\
+SHELLQs J1429-0002          & +217.3342500 & --0.0353889        & 6.04    & 
+150.0 \\
 DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
-ATLAS J332.8017-32.1036 & +332.8017500 & -32.1035556      & 6.3394  &    3.2 \\
-VIK J2318-3113                  & +349.5764625 & -31.2295417      & 6.4435  &  239.9 \\
+ATLAS J332.8017-32.1036 & +332.8017500 & --32.1035556      & 6.3394  &    3.2 \\
+VIK J2318-3113                  & +349.5764625 & --31.2295417      & 6.4435  & 
+239.9 \\
 \hline  \hline

### 2020-02-05 tex/MNRAS_submission/rv1/referees_reply.txt
referees_reply.txt updated

@@
-	We thank the Referee for reading our manuscript carefully and
-	for their review and comments.  We address each and every one
-	of these in turn below (indented text).
+	We thank the Referee for reading our manuscript carefully and for their review and comments.
 
-	We have also made further, key improvements to our dataset and
-	pipeline.
+	We address each and every one of these in turn below (indented text).
+
+	We have also made further, key improvements to our dataset and pipeline.
 
@@
 	had large photometric changes but now acknowledge this was due
-	to an incorrect apertureID assignment, when the database was updated 
-	with new data. The updated photometry for SDSS J2220-0101 has the  
-	VSA J-band magnitude 20.32+/-0.07 mag AB and a WSA magnitude 20.30+/-0.15 mag AB.
+	to an incorrect apertureID assignment, when the database was
+	updated with new data. The updated photometry for SDSS
+	J2220-0101 has the VSA J-band magnitude 20.32+/-0.07 mag AB
+	and a WSA magnitude 20.30+/-0.15 mag AB.
 
@@
 	   The ZYJHK filters for UKIRT and VISTA *are* different, but
-	   plotting both doesn't result in a clear figure. We have added an explicit link to:
-	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png and
-	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png.
+	   plotting both doesn't result in a clear figure. We have
+	   added an explicit link to:
+	   https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters_vs_QSOstars_UKIRT.png
+	   and
+	   https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters_vs_QSOstars_VISTA.png
 
@@
 
-	Updated table 1,2 and figure 2. This gap has partly been filled in by recent (2018) 
-	discoveries e.g. Yang et al. (2018) - which includes many of the 25 new objects that 
-	we have recently added.
+	   We have updated Tables 1 and 2, and Figure 2. This gap has
+   	   partly been filled in by recent (2018) discoveries e.g. Yang et al. (2018) -
+	   which includes many of the 25 new objects that	we have recently added.
 
@@
 
-We have updated both tables 3 and 5 with the new objects and some new VISTA photometry 
-(increasing the end time to 20170101) and have added a line in the caption to Table 3.
+	    We have updated both tables 3 and 5 with the new objects
+	    and some new VISTA photometry (increasing the end time to
+	    20170101) and have added a line in the caption to Table 3.
 

### 2020-02-10 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated Table 6 and PDF

@@
 \subsection{MIR data}
-The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and the Near-Earth Object WISE \citep[NEOWISE; ][]{Mainzer2011} post-cryogenic and NEOWISE Reactivation Mission \citep[NEOWISE-R][]{Mainzer2014} survey phases.
-
-We use data from the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018 December;]{Mainzer2011}.
-There are several  major \href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and catalogues based on the WISE mission.
-Here we use two: the WISE \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release} and the recently released ``unWISE Catalog'' \citep{Schlafly2019}.
-The AllWISE program combines the W1 and W2 Single-exposure data from all the WISE survey phases (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01) survey phases, and the W3 and W4 from the 4-Band Cryo phase.
-The unWISE effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.
-
-For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.
-For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the AllWISE Data Release.
-Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}.
-The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.
-
-Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found that cross-matches performed with a radius of 2-3'' between the user catalogue and WISE was a good compromise between completeness and contamination \citep[see e.g.
-Figure 4 of ][]{Krawczyk2013}.
-We thus use a cross-match radius of 2.75''.
-When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE table search was set to 2.75'' for the Spatial Constraints.
-The ``One to One Match'' was ``not'' checked; although possible, we consider it highly unlikely there would be more than one MIR source contributing to the flux of a single UV/optically bright rest-frame quasar.
-As a check, we utilize data from the {\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel 4 8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density measurements from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}.
-%% address now the number of expected contaminating 8--25 micron sources in the apertures used, as it can be done straightforwardly.
-E.g., Driver et al.
-(2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this estimate are actually best given as Fig.
-A4, A5 on the astro-ph version.
-The redshift distribution of the sampled 8--24 $\mu$m foreground objects is narrow enough and their $K$-corrections advantageous enough, that the objects
-counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized differential counts --- especially in e.g.
-WISE W4 --- have most of their  extragalactic background light energy emerging at AB$\sim$18--20 mag.
-As a consequence, the relative number or probability of contaminating objects at AB$>20$mag inside our apertures should be small.
-%Investigating this in detail is very interesting but left to a future study.
-
-Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the AllWISE catalogues and also query the AllWISE Reject Table.
-However, with the exception of one object (SHELLQs  J1208-0200), the AllWISE Reject Table does not contain any further W3/W4 detection information.
+The MIR data for this study comes from the Wide-field Infrared Survey Explorer
+(WISE) mission, and we utlize data from the WISE cryogenic and the Near-Earth
+Object WISE \citep[NEOWISE; ][]{Mainzer2011} post-cryogenic and NEOWISE
+Reactivation Mission \citep[NEOWISE-R][]{Mainzer2014} survey phases.
+
+We use data from the beginning of the WISE mission \citep[2010 January;
+][]{Wright2010} through the fifth-year of NEOWISE-R operations \citep[2018
+December;]{Mainzer2011}. There are several  major
+\href{https://irsa.ipac.caltech.edu/Missions/wise.html}{data releases} and  
+catalogues based on the WISE mission. Here we use two: the WISE 
+\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE Data release}
+and the recently released ``unWISE Catalog'' \citep{Schlafly2019}. The AllWISE 
+program combines the W1 and W2 Single-exposure data from all the WISE survey
+phases  (4-Band Cryo, 3-Band Cryo and Post-Cryo; 2010-01-07 thru 2011-02-01)
+survey  phases, and the W3 and W4 from the 4-Band Cryo phase. The  unWISE
+effort\footnote{\href{http://unwise.me}{http://unwise.me}} is the unblurred 
+coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data 
+\citep{Lang2014, Meisner2018a, Meisner2018b}.
+
+For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and 
+$\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred
+unWISE  coadd data.  For the two longer WISE bands, $\lambda_{\rm
+eff}$12.1$\mu$m  and $\lambda_{\rm eff}$22.8$\mu$m we use the AllWISE Data
+Release. Most objects in the AllWISE Source Catalog are unresolved, so the best 
+photometric measurements to use are the deep detection profile-fit photometry
+measures,   {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}. The unWISE
+Catalog  absolute photometric calibration derives from the photometric
+calibration  of the unWISE coadds \citep{Meisner2017a}, which is tied to the 
+original WISE zero points through aperture fluxes in a 27.5'' radius.
+
+Previous works \citep[e.g., ][]{Krawczyk2013, Ross2015, Bilicki2016} found  that
+cross-matches performed with a radius of 2-3'' between the user catalogue and 
+WISE was a good compromise between completeness and contamination  \citep[see
+e.g. Figure 4 of ][]{Krawczyk2013}. We thus use a cross-match radius of 2.75''. 
+When querying the AllWISE catalogues, ``Cone Search Radius'' in the AllWISE 
+table search was set to 2.75'' for the Spatial Constraints. The ``One to One
+Match''  was ``not'' checked; although possible, we consider it highly unlikely 
+there would be more than one MIR source contributing to the flux of a single 
+UV/optically bright rest-frame quasar. As a check, we utilize data from the 
+{\it Spitzer} Space Telescope in IRAC Channel 2 4.5$\mu$m,  IRAC Channel4
+8$\mu$m and MIPS 24$\mu$m,  and number counts and luminosity density
+measurements  from \citet[][see their Figures 8.11, 8.12 and 8.13]{Driver2016}.
+%% address now the number of expected contaminating 8--25 micron sources in the
+% apertures used, as it can be done straightforwardly. E.g., Driver et al. 
+% (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures you need for this
+% estimate are actually best given as Fig. A4, A5 on the astro-ph version.
+The redshift distribution of the sampled 8--24 $\mu$m foreground objects is 
+narrow enough and their $K$-corrections advantageous enough, that the objects 
+counts sharply turnover for $AB(W3, W4) \gtrsim 20$mag, and the normalized 
+differential counts --- especially in e.g. WISE W4 --- have most of their  
+extragalactic background light energy emerging at AB$\sim$18--20 mag. As a 
+consequence, the relative number or probability of contaminating objects at 
+AB$>20$mag inside our apertures should be small.  %Investigating this in detail
+% is very interesting but left to a future study.
+
+Knowing we have secure detections in the near-infrared bands, and wanting  to
+boost the number of WISE W3/W4 detections, we allow ourselves to be less 
+conservative in querying the AllWISE catalogues and also query the AllWISE 
+Reject Table. However, with the exception of one object (SHELLQs  J1208-0200), 
+the AllWISE Reject Table does not contain any further W3/W4 detection information.
 
@@
     \hline
-    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
-    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
-    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
-    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
-    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
+    5.00   &   389 ( 79.7\%)   &   334 ( 68.4\%)  &    59 ( 12.1\%)  &    10 ( 
+    2.0\%) \\
+    5.70   &   194 ( 71.1\%)   &   157 ( 57.5\%)  &    16 (  5.9\%)  &     6 ( 
+    2.2\%) \\
+    6.00   &   115 ( 66.1\%)   &    96 ( 55.2\%)  &     9 (  5.2\%)  &     2 ( 
+    1.1\%) \\
+    6.19   &    65 ( 74.7\%)   &    48 ( 55.2\%)  &     3 (  3.4\%)  &     2 ( 
+    2.3\%) \\
+    6.50   &    35 ( 87.5\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 ( 
+    5.0\%) \\
     6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 

### 2020-02-12 light_curves/MIR_LCs/NEOWISER_LC_histogram.py
Updated Figure 7 and related data

@@ -2,6 +2,7 @@
 The number of NEOWISE-R epochs for the VHzQs
 '''
 
+import os
 from astropy.io import ascii
 import numpy as np
 
@@ -10,10 +11,10 @@ from matplotlib import colors
 from matplotlib.ticker import ScalarFormatter
 
 ## Reading the data file in
-path='/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/'
-file = 'NoOfEpochs_perQuasar.dat'
+path='../../light_curves/MIR_LCs/'
+file = 'NoOfEpochs_perQuasar_20200212.dat'
 
-data_in = ascii.read(path+file) 
+data_in = ascii.read(os.path.join(path,file)) 
 print(type(data_in))
 data = np.array(data_in).astype(np.float)
 

### 2020-02-12 light_curves/MIR_LCs/NEOWISER_LCs_singleObject.py

@@ -2,6 +2,7 @@
 http://blog.marmakoide.org/?p=94
 '''
 
+import os
 from astropy.io import ascii
 
 import numpy as np
@@ -15,10 +16,10 @@ from matplotlib.backends.backend_pdf import PdfPages
 import random
 
 #path='/cos_pc19a_npr/data/highest_z_QSOs/'
-path = '/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/'
-file = 'NEOWISER-R_SingleExposure_L1bs.tbl'
+path = '../../data/light_curves/NEOWISE-R'
+file = 'NEOWISER-R_SingleExposure_L1bs_20200212.tbl'
 
-data = ascii.read(path+file) 
+data = ascii.read(os.path.join(path,file)) 
 type(data)
 upto_this = data['cntr_01'].max()
 

### 2020-02-13 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated Fig5 for new data
Updated Fig4 for new data
Updated Figure 7 and related data
Recreated new figures with updated matplotlibrc

@@
 until  2018 December 13 (MJD 58465) including the fifth year of survey
-operations of  NEOWISE. These fifth year NEOWISE data products are concatenated with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
-%%
-The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October.
-Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
+operations of  NEOWISE. These fifth year NEOWISE data products are concatenated 
+with those from the first four years into a single archive from 2013 December 13 (MJD 56639).
+%%
+The WISE scan pattern leads to coverage of the full-sky approximately once every
+six months (a``sky pass''), but the satellite was placed in hibernation in 2011 
+February and then reactivated in 2013 October. Hence, our light curves have a
+cadence  of 6 months with a 32 month sampling gap.
 
@@
 \subsection{Detection Rates in the MIR}
-Unlike the NIR coverage, the WISE satellite and mission performed an all-sky survey, so the location of every VH$z$Q in our dataset is covered.
-However, the depth of the WISE survey depends heavily on sky location, with locations near the Ecliptic Poles having the highest number of exposures.
+Unlike the NIR coverage, the WISE satellite and mission performed an all-sky
+survey,  so the location of every VH$z$Q in our dataset is covered. However, the
+depth  of the WISE survey depends heavily on sky location, with locations near
+the  Ecliptic Poles having the highest number of exposures.
 
@@
   % {../detections/WISEmag_vs_coverage_20190605.pdf}
- {figures/WISEmag_vs_coverage_20190605.pdf}
+ {figures/WISEmag_vs_coverage_20200211.pdf}
   \centering
@@
 \end{figure}
+
 Before reporting on the detection rates, we investigate this effect
@@
     %{../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190615_AB.png}
-    {figures/W1W2W3_hexplots_20190615_AB.png}
+    {figures/W1W2W3_hexplots_20200211_AB.png}
   \vspace{-14pt}
     \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
-      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
+      for the 330 VH$z$Q that have reported w3mpro values (blue to red coloured
+      points).
       400,000 quasars at redshift $z\lesssim3.0$ from the SDSS DR14 quasar catalogue 
@@
   % {../light_curves/MIR_LCs/NEOWISER_LC_histogram_20190606.png}
-   {figures/NEOWISER_LC_histogram_20190606.png}
+   {figures/NEOWISER_LC_histogram_20200212.png}
   \vspace{-16pt}

### 2020-02-15 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Changed paragraph on WISE colours

@@
 
-The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
-(W1-W2) = --0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
+The VH$z$Q with the bluest colour in (W1-W2) is SDSS~J0927+2001, with
+(W1-W2) = --0.283 (i.e. 0.328 in Vega), and the WISE W1W2W3 color image
 is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
-(W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).
+(W1-W2) is PSO~J135.3860+16.2518 with (W1-W2) = 0.721 (1.33
+Vega).
 

### 2020-02-15 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated a few numbers in Sect 3.3,3.4 and Conclusions

@@
 
-The set of VH$z$Q detected in WISE W3 and W4 contains 51 objects that
+The set of VH$z$Q detected in WISE W3 and W4 contains 59 objects that
 are detected in the broad W3 filter and 10 objects that are formally
@@
 Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections for each VH$z$Q. 
-There are 60 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs and four with over 300.
+There are 74 quasars with over 100 NEOWISE-R epochs, nine with over 200 epochs
+and four with over 300.
 Figure~\ref{fig:MIR_LC_3egs} presents three examples of the brighter MIR objects with well-sampled 
@@
     lack of coverage rather than lack of depth;
-  \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper
+  \item 389 (79.7\%) VH$z$Qs are detected by WISE, e.g. in the deeper
     unWISE W1 catalog.

### 2020-02-16 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updated Assef numbers
Updated abstract

@@
 coverage rather than lack of depth being the reason for the
-non-detections. 362 (78\%) of the very high redshift quasars are
+non-detections. 389 (80\%) of the very high redshift quasars are
 detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
@@
 variability that might be expected from super-Eddington accretion. We
-find 32 of the quasars have sufficient NIR measurements and
+find 28 of the quasars have sufficient NIR measurements and
 signal-to-noise ratio to look for variability. Weak variability was detected
@@
 deg$^2$). Crossmatching our catalogue of 488 VH$z$Qs with these
-catalogues, produces 42 matches with the R90 sample and 98 matches
+catalogues, produces 49 matches with the R90 sample and 129 matches
 with the C75 sample. Both catalogues unsurprisingly match to the

### 2020-02-16 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Replaced Fig 6a, minor changes to text

@@
 catalogues. That sample only examined the 31 known $z>6$ quasars; our
-sample has 170 objects with redshift $z \geq 6.00$ (with 108 detected
+sample has 174 objects with redshift $z \geq 6.00$ (with 117 detected
 in WISE). \citet{Banados2016} reports WISE W1, W2, W3 and W4
@@
 
-We present all our photometry and magnitudes on the AB system. For NIR, we use the \citet{Oke_Gunn1983} and \citet{Fukugita1996} system which has a zeropoint of $-48.60$. 
-For WISE, the AB-Vega offsets \href{http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab}{are calculated} using the \citet{TokunagaVacca2005} AB system, which has a zeropoint of -48.574.
-So to remain on the -48.60 system, and assuming a flux density F$_{\nu} \propto \nu^{0}$, one needs to subtract 0.026 mag from the zeropoints:
+We present all our photometry and magnitudes on the AB system.  For NIR, we use
+the \citet{Oke_Gunn1983} and \citet{Fukugita1996} system which has  a zeropoint
+of $-48.60$. For WISE, the AB-Vega offsets
+\href{http://wise2.ipac.caltech.edu/docs/release/allsky/expsup/sec4_4h.html#conv2ab}{are calculated} 
+using the \citet{TokunagaVacca2005} AB system, which has a zeropoint of -48.574.
+So to remain on the -48.60 system, and assuming a flux density F$_{\nu} \propto
+\nu^{0}$,  one needs to subtract 0.026 mag from the zeropoints:
 ($\Delta$W1, $\Delta$W2, $\Delta$W3) = (2.673, 3.313, 5.148). 
@@
   $^{b}$SDWISE = SDSS+WISE; 
-  $^{c}$SUV  = SDSS-ULAS/VHS; 
+  $^{c}$SUV  = SDSS+ULAS/VHS; 
   $^{d}$VDES = VHS/VIKING+DES; 
@@
 We note that although we are often working close to the magnitude
-limits of the surveys, Eddington bias is not a significant effect on
+limits of the surveys, Eddington bias does not a significant effect on
 our measurements, since we are not discovering new sources, but
@@
   %  \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
-     \includegraphics[width=0.24\textwidth]{figures/DELS_J1048-0109.png} 
+     %\includegraphics[width=0.24\textwidth]{figures/DELS_J1048-0109.png} 
+     \includegraphics[width=0.24\textwidth]{figures/SDSS_J0927+2001.png}
    \includegraphics[width=0.24\textwidth]{figures/UHS_J0439+1634.png} 
@@
       IRSA WISE Image Service, with a scale of 120'' on the side. 
-      {\it (a)} DELS J1048-0109 is the bluest in (W1-W2) colour quasar. 
+      %{\it (a)} DELS J1048-0109 is the bluest in (W1-W2) colour quasar. 
+      {\it (a)} SDSS J0927+2001 is the bluest in (W1-W2) colour quasar.
       {\it (b)} UHS J0439+1634 was discovered by \citet{Fan2019} and is a strongly lensed quasar at $z=6.51$. 
@@
 Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour-colour
-diagram for the 283 VH$z$Qs that have reported {\tt w3mpro} values
+diagram for the 330 VH$z$Qs that have reported {\tt w3mpro} values
 (blue to red coloured points), though we note that only 51 (18\%) of
@@
 variability:
-MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
-SDSS J0959+0227 (see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
-for $Y$ only. The $H$-band amplitude was 0.7 mag and the $Y$-band amplitude was
-1.2 mag if averaged over 6 months, or 0.9 mag if averaged over 1 year.
+MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an
+average time-scale of 30 days and amplitude of 0.3 mag, and SDSS J0959+0227 
+(see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales 
+of 1 year or 6 months for $Y$ only. The $H$-band amplitude was 0.7 mag and  the
+$Y$-band amplitude was 1.2 mag if averaged over 6 months, or 0.9 mag if averaged over 1 year.
 
